### 2016-11-03 section_discussion_subsection_Emission_Physics__.tex
added section_discussion_subsection_Emission_Physics__.tex

\section{discussion}

\subsection{Emission Physics and Burst Energetics}

\subsection{Connection to Overall FRB Population}

\subsection{Observing Strategies}

### 2016-11-03 untitled.tex
edited untitled.tex

\begin{abstract}
The highly-dispersed, millisecond radio transients known as Fast Radio Bursts have recently emerged as a new class...
The discovery of repeating bursts from FRB121102 has shown that at least some FRBs are not cataclysmic and opened potential for studying a homogenous sample of bursts...
Our recent coordinated campaign with the Very Large Array and Arecibo Observatory has made the first direct, arcsecond-scale localization of an FRB and unambiguously associated it with counterparts in other observations. This campaign detected nine bursts at the VLA from 2.5 to 3.5~GHz and many more at Arecibo near 1.4~GHz. The coordination of these observations allow us to refine our picture of the physical processes in FRB121102. 
With so many bursts, we can make the first reliable measures of burst flux distribution and temporal statistics...
The connection of FRB121102 to the overall population...

\end{abstract}

### 2016-11-04 section_discussion_subsection_Emission_Physics__.tex
edited section_discussion_subsection_Emission_Physics__.tex

@@
 
+Flat luminosity distribution of FRB121102 and overall population
+
+Does local (100 Mpc) population with flat luminosity distribution reproduce observed properties?
+Imagine also how log-N/log_S cut-offs and scattering biases the intrinsic into the observed distribution (Macquart and Johnston)
+
+Constraints on repetition assuming "red spectrum"
+
 \subsection{Observing Strategies}
+
+Targeting known FRBs is optimal
+
+Wide, low-sensitivity searches are best way to conduct a blind search

### 2016-11-06 repeater-vladata.tex
moving out of authorea. renamed figures

%% This is emulateapj reformatting of the AASTEX sample document
%%
\documentclass{emulateapj}
\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref} 
\usepackage{graphicx,natbib}
\citestyle{aa}
\usepackage[space]{grffile}
\usepackage{latexsym}
\usepackage{amsfonts,amsmath,amssymb}
\usepackage{url}
\usepackage[utf8]{inputenc}
\usepackage{fancyref}
\usepackage{hyperref}
\usepackage{multirow}
\hypersetup{colorlinks=false,pdfborder={0 0 0},}

\DeclareMathOperator{\erfinv}{erfinv}

%% You can insert a short comment on the title page using the command below.
%\slugcomment{To appear in The Astrophysical Journal (ApJ)}

\begin{document}

\title{FRB 121102: Radio Bursts Seen by Very Large Array and Implications for Overall FRB Population}
\shorttitle{FRB 121102: VLA Burst Properties}
\shortauthors{Law et al.}

\author{Casey J. Law\altaffilmark{1}}
\author{et al.}
\altaffiltext{1}{Dept of Astronomy and Radio Astronomy Lab, Univ. of California, Berkeley, CA}

\begin{abstract}
The highly-dispersed, millisecond radio transients known as Fast Radio Bursts have recently emerged as a new class...
The discovery of repeating bursts from FRB121102 has shown that at least some FRBs are not cataclysmic and opened potential for studying a homogenous sample of bursts...
Our recent coordinated campaign with the Very Large Array and Arecibo Observatory has made the first direct, arcsecond-scale localization of an FRB and unambiguously associated it with counterparts in other observations. This campaign detected nine bursts at the VLA from 2.5 to 3.5~GHz and many more at Arecibo near 1.4~GHz. The coordination of these observations allow us to refine our picture of the physical processes in FRB121102. 
With so many bursts, we can make the first reliable measures of burst flux distribution and temporal statistics...
The connection of FRB121102 to the overall population...

\end{abstract}

\section{Introduction}

The discovery of Fast Radio Bursts, a new class of millisecond-duration, highly-dispersed radio transients, has opened a whole new playground in astrophysics.

- Physical processes

- Utility as probes

- Repeater as anomalous FRB

- VLA data provides new insight on role of repeater in overall FRB population

\section{Observations}

All observations in August and Septmeber were searched in quasi real-time by a prototype version of \emph{realfast}. \emph{realfast} is a real-time, fast imaging transient search system. The current, prototype runs on existing hardware of the VLA correlator backend, while the future \emph{realfast} will run on a dedicated GPU cluster.

Burst detections and localizations were made within hours of data being recorded.

\section{Results}

\subsection{Spectra}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.3\columnwidth]{sgram_57623.png}
\includegraphics[width=0.3\columnwidth]{sgram_57633_scan7.png}
\includegraphics[width=0.3\columnwidth]{sgram_57633_scan13.png}
\caption{
\label{fig:name}}
\end{center}
\end{figure}

\subsection{Circular Polarization}

\subsection{Brightness Distribution}

\subsection{Temporal Statistics}

\section{discussion}

\subsection{Emission Physics and Burst Energetics}

\subsection{Connection to Overall FRB Population}

Flat luminosity distribution of FRB121102 and overall population

Does local (100 Mpc) population with flat luminosity distribution reproduce observed properties? Imagine also how log-N/log_S cut-offs and scattering biases the intrinsic into the observed distribution (Macquart and Johnston)

Constraints on repetition assuming "red spectrum"

\subsection{Observing Strategies}

Targeting known FRBs is optimal

Wide, low-sensitivity searches are best way to conduct a blind search

\bibliographystyle{apj}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.9\columnwidth]{}
\caption{Spectra of nine bursts seen by the VLA from 2.5 to 3.5~GHz.
Spectrum of 57623. Assumed DM=561.
Spectrum of 57633, Scan 7. Assumed DM=554.
Spectrum of 57633, Scan 13. Assumed DM=559. 
Spectrum of 57638. Assumed DM=554.
Spectrum of 57643. Assumed DM=559.
Spectrum of 57645. Assumed DM=572.
Spectrum of 57646. Assumed DM=573.
Spectrum of 57648. Assumed DM=559.
Spectrum of 57649. Assumed DM=552.
\label{fig:name}}
\end{center}
\end{figure}

%\begin{figure}[htb]
%\begin{center}
%\includegraphics[width=0.9\columnwidth]{}
%\caption{
%\label{fig:name}}
%\end{center}
%\end{figure}

%\begin{table}
%\caption{Caption}
%\footnotesize
%\centering
%\begin{tabular}{l|cc|cc|c}
%\hline
%Field       & RA          & Dec   & Lon. & Lat.     & Time \\
%            & \multicolumn{2}{|c|}{(J2000)}  & \multicolumn{2}{|c|}{(Galactic; deg)} & (hrs) \\ \hline
%RA02        & 2:27:53  &  +9:13:24 & 159.0 & --46.8    & 26.25 \\
%PSR J2248-0101 & 22:48:27 & --1:1:48 & 69.3 & --50.6 & 6.5 \\ \hline
%\end{tabular}
%\label{fields}
%\end{table}

\section*{Acknowledgements}
We thank ...
This project was supported by the University of California Office of the President under Lab Fees Research Program Award 237863. The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.

\bibliography{fasttrants.bib}

\end{document}

### 2016-11-06 repeater-vladata.tex
draft for group

@@
 
-\DeclareMathOperator{\erfinv}{erfinv}
-
-%% You can insert a short comment on the title page using the command below.
-%\slugcomment{To appear in The Astrophysical Journal (ApJ)}
+\newcommand{\rf}{\emph{realfast}}
 
@@
 
-\title{FRB 121102: Radio Bursts Seen by Very Large Array and Implications for Overall FRB Population}
-\shorttitle{FRB 121102: VLA Burst Properties}
+\title{FRB 121102: Very Large Array Burst Properties and Implications for Overall FRB Population}
+\shorttitle{FRB 121102 Burst Properties}
 \shortauthors{Law et al.}
@@
 \author{Casey J. Law\altaffilmark{1}}
-\author{et al.}
+\author{Dewey}
+\author{Cheetham}
+\author{Howe}
 \altaffiltext{1}{Dept of Astronomy and Radio Astronomy Lab, Univ. of California, Berkeley, CA}
@@
 The highly-dispersed, millisecond radio transients known as Fast Radio Bursts have recently emerged as a new class...
+
 The discovery of repeating bursts from FRB121102 has shown that at least some FRBs are not cataclysmic and opened potential for studying a homogenous sample of bursts...
@@
 The coordination of these observations allow us to refine our picture of the physical processes in FRB121102.
+
 With so many bursts, we can make the first reliable measures of burst flux distribution and temporal statistics...
+
 The connection of FRB121102 to the overall population...
@@
 \section{Introduction}
-
 The discovery of Fast Radio Bursts, a new class of millisecond-duration, highly-dispersed radio transients, has opened a whole new playground in astrophysics.
 
-- Physical processes
-
-- Utility as probes
-
-- Repeater as anomalous FRB
-
-- VLA data provides new insight on role of repeater in overall FRB population
+\begin{itemize}
+ \item FRB extreme brightness and emission physics
+ \item Extragalactic counterpart and potential utility as probes
+ \item Concern that repeater is an anomalous FRB
+ \item Potential for repeater to infer properties of FRB population
+\end{itemize}
 
 \section{Observations}
+\subsection{\rf}
 
-All observations in August and Septmeber were searched in quasi real-time by a prototype version of \emph{realfast}.
-\emph{realfast} is a real-time, fast imaging transient search system.
-The current, prototype runs on existing hardware of the VLA correlator backend, while the future \emph{realfast} will run on a dedicated GPU cluster.
+All observations in August and Septmeber were searched in quasi real-time by a prototype version of \rf.
+\rf is a real-time, fast imaging transient search system.
+The current, prototype runs on existing hardware of the VLA correlator backend, while the future \rf will run on a dedicated GPU cluster.
+The transient search pipeline software is called ``rtpipe''\footnote{See \url{https://github.com/caseyjlaw/rtpipe}} and is mostly written in Python.
 
@@
 
+\subsection{Detections}
+
+Figure \ref{fig:sgram} shows the spectrograms of all nine bursts detected by \rf.
+
+Computational notebooks to reproduce the transient detection and localization can be found at \url{https://github.com/caseyjlaw/FRB121102}. Data are available at \url{https://doi.org/xxx}.
+
+\begin{figure*}[htb]
+\begin{center}
+ \begin{minipage}{2\columnwidth}
+  \includegraphics[width=0.25\columnwidth]{sgram_57623.png}
+  \includegraphics[width=0.25\columnwidth]{sgram_57633_scan7.png}
+  \includegraphics[width=0.25\columnwidth]{sgram_57633_scan13.png}
+ \end{minipage}
+
+ \begin{minipage}{2\columnwidth}
+  \includegraphics[width=0.25\columnwidth]{sgram_57638.png}
+  \includegraphics[width=0.25\columnwidth]{sgram_57643.png}
+  \includegraphics[width=0.25\columnwidth]{sgram_57645.png}
+ \end{minipage}
+
+ \begin{minipage}{2\columnwidth}
+  \includegraphics[width=0.25\columnwidth]{sgram_57646.png}
+  \includegraphics[width=0.25\columnwidth]{sgram_57648.png}
+  \includegraphics[width=0.25\columnwidth]{sgram_57649.png}
+ \end{minipage}
+ \caption{Spectrograms (time vs frequency intensity maps) for all nine VLA bursts. Note that bursts are detected in 5~ms images generated from dedispersed visibilities. **NOT SURE WHY ONE FIG LARGER**
+ \label{fig:sgram}}
+\end{center}
+\end{figure*}
+
 \section{Results}
+
+\subsection{Dispersion}
+
+After detection, we refined the analysis of each burst offline. We used a fine dispersion grid to find the best-fit DM for each burst.
+
+Table?
+57623 (DM$=561$ pc cm$^{-3}$)
+57633, Scan 7 (DM$=554$ pc cm$^{-3}$)
+57633, Scan 13 (DM$=559$ pc cm$^{-3}$)
+57638 (DM$=554$ pc cm$^{-3}$)
+57643 (DM$=559$ pc cm$^{-3}$)
+57645 (DM$=572$ pc cm$^{-3}$)
+57646 (DM$=573$ pc cm$^{-3}$)
+57648 (DM$=559$ pc cm$^{-3}$)
+57649 (DM$=552$ pc cm$^{-3}$).
+
+Dispersion measure changes between bursts significant?
 
@@
 
+Burst spectra are shown in Figure \ref{fig:spec}...
+
+\begin{figure*}[h!]
+\begin{center}
+ \begin{minipage}{2\columnwidth}
+  \includegraphics[width=0.3\columnwidth]{spec_57623.png}
+  \includegraphics[width=0.3\columnwidth]{spec_57633_scan7.png}
+  \includegraphics[width=0.3\columnwidth]{spec_57633_scan13.png}
+ \end{minipage}
+
+ \begin{minipage}{2\columnwidth}
+  \includegraphics[width=0.3\columnwidth]{spec_57638.png}
+  \includegraphics[width=0.3\columnwidth]{spec_57643.png}
+  \includegraphics[width=0.3\columnwidth]{spec_57645.png}
+ \end{minipage}
+
+ \begin{minipage}{2\columnwidth}
+  \includegraphics[width=0.3\columnwidth]{spec_57646.png}
+  \includegraphics[width=0.3\columnwidth]{spec_57648.png}
+  \includegraphics[width=0.3\columnwidth]{spec_57649.png}
+ \end{minipage}
+\caption{Spectra of nine bursts seen by the VLA from 2.5 to 3.5~GHz.  **LABELS ALL SAME FREQ. SOME SHOULD START HIGHER FOR DROPPED CHANNELS**
+ \label{fig:spec}}
+\end{center}
+\end{figure*}
+
+\subsection{Circular Polarization}
+
+The VLA S-band recievers natively measure circular polarization.
+The fast VLA interferometric data recorded only dual-circular visibilities and did not perform polarimetric calibration, so only crude polarimetric constraints are possible and only on circular polarization.
+
+Can variation in circular pol between bursts be caused by beam-dependent effects? If not, then we can claim some modest circular pol that varies burst-to-burst.
+
+\subsection{Brightness Distribution}
+
+The bursts seen by the VLA range in significance from 10 to 150$\sigma$. Offline analysis for flux scale...
+
+Figure \ref{fig:logns} shows the flux distribution of the nine VLA bursts. Flatness...
+
 \begin{figure}[htb]
 \begin{center}
-\includegraphics[width=0.3\columnwidth]{sgram_57623.png}
-\includegraphics[width=0.3\columnwidth]{sgram_57633_scan7.png}
-\includegraphics[width=0.3\columnwidth]{sgram_57633_scan13.png}
-\caption{
-\label{fig:name}}
+\includegraphics[width=0.9\columnwidth]{logns}
+\caption{Log N -- Log SNR distribution of real-time detections of FRB 121102.
+\label{fig:logns}}
 \end{center}
@@
 
-\subsection{Circular Polarization}
-
-\subsection{Brightness Distribution}
+Doubts were cast on the first FRB detection (``Lorimer burst'') due to its unusually high brightness.
+The lack of lower-significance detections suggested that this burst was unlikely to be part of any astrophysical population...
 
@@
 
+Burst detections were made very inhomogenously though the roughly 60 hours of observing toward FRB 121102.
+In the first $\sim8$\ hours of observing at L-band and the first $\sim25$\ hours observing at S-band no bursts were detected.
+Finally, in the last $\sim27$ hours of S-band observing, all nine bursts were detected.
+Data quality are relatively high and RFI did not significantly impact sensitivity, so the inhomogeneous burst distribution not an observational artifact.
+
 \section{discussion}
-
-\subsection{Emission Physics and Burst Energetics}
 
@@
 Does local (100 Mpc) population with flat luminosity distribution reproduce observed properties?
-Imagine also how log-N/log_S cut-offs and scattering biases the intrinsic into the observed distribution (Macquart and Johnston)
+Imagine also how log N/log S cut-offs and scattering biases the intrinsic into the observed distribution (Macquart and Johnston)
 
-Constraints on repetition assuming "red spectrum"
+Discussion of ``red spectrum'' and Connor \& Pen. Bursts predict bursts therefore repetition constraints of other FRBs are likely weaker than claimed...
+
+Intrinsic versus refractive scintillation
+
+Constraints on repetition assuming "red spectrum" for whole population. Simulation using observed burst temporal statistics...
+
+\subsection{Emission Physics and Burst Energetics}
 
@@
 
+\section{Conclusions}
+
 \bibliographystyle{apj}
 
-\begin{figure}[htb]
-\begin{center}
-\includegraphics[width=0.9\columnwidth]{}
-\caption{Spectra of nine bursts seen by the VLA from 2.5 to 3.5~GHz.
-Spectrum of 57623. Assumed DM=561.
-Spectrum of 57633, Scan 7. Assumed DM=554.
-Spectrum of 57633, Scan 13. Assumed DM=559. 
-Spectrum of 57638. Assumed DM=554.
-Spectrum of 57643. Assumed DM=559.
-Spectrum of 57645. Assumed DM=572.
-Spectrum of 57646. Assumed DM=573.
-Spectrum of 57648. Assumed DM=559.
-Spectrum of 57649. Assumed DM=552.
-\label{fig:name}}
-\end{center}
-\end{figure}
+\section*{Acknowledgements}
+We thank ...
+This project was supported by the University of California Office of the President under Lab Fees Research Program Award 237863.
+The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.
+
+\bibliography{fasttrants.bib}
 
@@
 
-\section*{Acknowledgements}
-We thank ...
-This project was supported by the University of California Office of the President under Lab Fees Research Program Award 237863.
-The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.
-
-\bibliography{fasttrants.bib}
-
 \end{document}

### 2016-11-09 repeater-vladata.tex
beam squint note
polarimetry dominated by systematics

@@
 Our recent coordinated campaign with the Very Large Array and Arecibo Observatory has made the first direct, arcsecond-scale localization of an FRB and unambiguously associated it with counterparts in other observations.
-This campaign detected nine bursts at the VLA from 2.5 to 3.5~GHz and many more at Arecibo near 1.4~GHz.
+This campaign detected nine bursts at the VLA from 2.5 to 3.5~GHz and many more at Arecibo, GBT, and Effelsberg.
 The coordination of these observations allow us to refine our picture of the physical processes in FRB121102.
@@
 \begin{itemize}
- \item FRB extreme brightness and emission physics
+ \item FRBs, extreme brightness, emission physics
  \item Extragalactic counterpart and potential utility as probes
- \item Concern that repeater is an anomalous FRB
- \item Potential for repeater to infer properties of FRB population
+ \item Repeating FRB as good target
+ \item Potential to infer properties of FRB population
 \end{itemize}
@@
 
-\subsection{Detections}
+\subsection{Arecibo}
+
+\subsection{Effelsberg}
+
+\subsection{Green Bank Telescope}
+
+\section{Results}
+
+\subsection{VLA Detections}
 
@@
 
-Computational notebooks to reproduce the transient detection and localization can be found at \url{https://github.com/caseyjlaw/FRB121102}. Data are available at \url{https://doi.org/xxx}.
+Computational notebooks to reproduce the transient detection and localization can be found at \url{https://github.com/caseyjlaw/FRB121102}.
+VLA data are available at \url{https://doi.org/10.7910/DVN/TLDKXG}.
 
@@
 
-\section{Results}
+\subsection{Multi-Telescope Burst Spectra}
 
-\subsection{Dispersion}
-
+\subsection{VLA Spectra}
 After detection, we refined the analysis of each burst offline. We used a fine dispersion grid to find the best-fit DM for each burst.
@@
 Dispersion measure changes between bursts significant?
-
-\subsection{Spectra}
 
@@
 
-\subsection{Circular Polarization}
-
-The VLA S-band recievers natively measure circular polarization.
-The fast VLA interferometric data recorded only dual-circular visibilities and did not perform polarimetric calibration, so only crude polarimetric constraints are possible and only on circular polarization.
-
-Can variation in circular pol between bursts be caused by beam-dependent effects? If not, then we can claim some modest circular pol that varies burst-to-burst.
+The VLA S-band recievers natively measure circular polarization, although observations did not include polarization calibration procedures.
+Crude constraints on circular polarization are possible by comparing the burst intensity in right and left-hand polarized data products.
+The apparent circular polarization fraction ($(RR-LL)/(RR+LL)$) for the most significant bursts are all less than 3\%.
+FRB121102 was located 2.3 arcmin away from pointing center, where systematic effects have been measured as large as 3\% (Perley et al 2016, VLA memo).
+We conclude that the S-band bursts seen by the VLA have a circular polarization of less than 3\%.
 
@@
 \subsection{Temporal Statistics}
-
 Burst detections were made very inhomogenously though the roughly 60 hours of observing toward FRB 121102.

### 2016-11-12 repeater-vladata.tex
added ref
added figure and makefile
added some text from first paper. details of multi-telescope coverage

@@
 All observations in August and Septmeber were searched in quasi real-time by a prototype version of \rf.
-\rf is a real-time, fast imaging transient search system.
-The current, prototype runs on existing hardware of the VLA correlator backend, while the future \rf will run on a dedicated GPU cluster.
+\rf\ is a real-time, fast imaging transient search system.
+The current, prototype runs on existing hardware of the VLA correlator backend, while the future \rf\ will run on a dedicated GPU cluster.
 The transient search pipeline software is called ``rtpipe''\footnote{See \url{https://github.com/caseyjlaw/rtpipe}} and is mostly written in Python.
@@
 
+% from the first paper
+During the joint Arecibo-VLA campaign, Arecibo observed with the L-wide receiver, which has an observational frequency range of 1.15 to 1.73~GHz and a full width at half maximum beam size of 3.3 arcmin.
+The PUPPI pulsar backend was used to record total intensity spectra with time and frequency resolutions of 10.24~$\mu$s and 1.5625~MHz, respectively, and full Stokes polarization information.
+Each frequency channel was coherently dedispersed to 557~\dmu, thereby eliminating intra-channel dispersion smearing.
+PUPPI covers a total of 800~MHz of bandwidth centred at 1380.78125~MHz, but only $\sim$ 620~MHz of this band is usable due to radio frequency interference and receiver sensitivity roll-off at the band edges.
+
 \subsection{Effelsberg}
 
-\subsection{Green Bank Telescope}
+\subsection{AMI}
 
@@
 Computational notebooks to reproduce the transient detection and localization can be found at \url{https://github.com/caseyjlaw/FRB121102}.
-VLA data are available at \url{https://doi.org/10.7910/DVN/TLDKXG}.
+Time cut-out visibility data are available at \url{https://doi.org/10.7910/DVN/TLDKXG}.
+Original visibility data are available under VLA program codes 16A-459 and 16A-496 and can be downloaded at \url{http://archive.nrao.edu}.
 
@@
 \subsection{Multi-Telescope Burst Spectra}
+
+Arecibo had coverage for 57638, 57643, 57645, 57648, and 57649. For 57643 observing was at C band only. At 57648, a burst is seen at 3757s, coincident with the VLA burst.
+
+Effelsberg had simultaneous coverage for bursts on MJD 57648 and 57649. No simultaneous detections.
+
+AMI had simultaneous coverage for bursts on 57643, 57645, 57648, and 57649.
 
@@
 
+\cite{2016MNRAS.458L..89C}
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=0.9\columnwidth]{lombscargle}
+\caption{Lomb-Scargle periodogram.
+\label{fig:ls}}
+\end{center}
+\end{figure}
+
 \section{discussion}
@@
 \subsection{Emission Physics and Burst Energetics}
+
+% from first paper
+For a nominal Gpc distance $D$ corresponding to redshifts $z\lesssim 0.3$, the received fluence $A_{\nu}$ from each burst implies  a burst energy
+$$E_{\rm burst} = 4\pi D^2 (\delta\Omega/4\pi) A_{\nu} \Delta\nu
+\approx 10^{38}\, {\rm erg}\,(\delta\Omega/4\pi) D_{\rm Gpc}^2  (A_{\nu} / 0.1\ {\rm Jy\ ms}) \Delta\nu_{\rm GHz}.$$
+The unknown  emission solid angle $\delta\Omega$
+could be very small due to relativistic beaming, and together with a distance possibly much smaller than 1~Gpc, could reduce the energy requirement significantly.
+However, the {\it total} energy emitted could be larger depending on the duration of the emission in the source frame and other model-dependent details.
+Either way, the burst energies from \frb\ are not inconsistent with those that might be expected from the magnetosphere of a compact object\cite{cw16}.
 

### 2016-11-15 repeater-vladata.tex
worked on intro

@@
 \newcommand{\rf}{\emph{realfast}}
+\newcommand{\frb}{\emph{FRB 121102}}
 
@@
 
-\title{FRB 121102: Very Large Array Burst Properties and Implications for Overall FRB Population}
-\shorttitle{FRB 121102 Burst Properties}
+\title{\frb: Very Large Array Burst Properties and Implications for Overall FRB Population}
+\shorttitle{\frb Burst Properties}
 \shortauthors{Law et al.}
@@
 
-The discovery of repeating bursts from FRB121102 has shown that at least some FRBs are not cataclysmic and opened potential for studying a homogenous sample of bursts...
+The discovery of repeating bursts from \frb has shown that at least some FRBs are not cataclysmic and opened potential for studying a homogenous sample of bursts...
 Our recent coordinated campaign with the Very Large Array and Arecibo Observatory has made the first direct, arcsecond-scale localization of an FRB and unambiguously associated it with counterparts in other observations.
 This campaign detected nine bursts at the VLA from 2.5 to 3.5~GHz and many more at Arecibo, GBT, and Effelsberg.
-The coordination of these observations allow us to refine our picture of the physical processes in FRB121102.
+The coordination of these observations allow us to refine our picture of the physical processes in \frb.
 
@@
 
-The connection of FRB121102 to the overall population...
+The connection of \frb to the overall population...
 
@@
 \section{Introduction}
-The discovery of Fast Radio Bursts, a new class of millisecond-duration, highly-dispersed radio transients, has opened a whole new playground in astrophysics.
+Fast Radio Bursts (FRBs) are a new class of millisecond-duration radio transient with a dispersion measure (DM) that implies it originate outside of our Galaxy.
+At extragalactic (and potentially cosmological) distances, they are not only unusually luminous, but they provide a new tracer of other galaxies and the intergalactic medium (IGM).
+In this way, FRBs have opened a whole new playground in astrophysics \citep{}.
+However, that potential has been hamstrung by the lack of a definitive association of an FRB to an extragalactic host.
 
+This paper is part of a series that presents the first localization and host identification of an FRB (CITE, CITE, ...).
+\frb, also known as the ``repeating FRB'', was first detected in November 2012 by the Arecibo Observatory \citep{2014ApJ...790..101S}.
+In mid 2015, new Arecibo observations revealed a series of bursts at the same DM and sky position demonstrating that FRBs are capable of repetition \citep{2016Natur.531..202S}.
+Beginning in August of 2015, we made the first of nine detections of \frb with the Very Large Array (CITE) and localized it with a precision of 0.1\arcsec.
+Deep radio and optical observing shows that \frb is unambiguously associated with a persistent radio and optical source at a redshift of 0.193 (CITE).
+
+\frb has now been localized three orders of magnitude better than any other FRB and placed at a cosmological distance.
+Its lookback (luminosity) distance is 746 (972) Mpc \citep{planck15} is orders of magnitude larger than any other millisecond transient.
+This shows that FRBs:
 \begin{itemize}
- \item FRBs, extreme brightness, emission physics
- \item Extragalactic counterpart and potential utility as probes
- \item Repeating FRB as good target
- \item Potential to infer properties of FRB population
+ \item are extremely luminous, 
+ \item have a significant DM contribution from the IGM, and
+ \item can be used to probe the IGM and their host galaxy.
 \end{itemize}
+The promise of the first reported FRB is being realized \citep{2007Sci...318..777L}.
+
+The cosmological distance for \frb could have wide-ranging implications for the FRB population as a whole.
+However, it has not been demonstrated that \frb is representative of the overall FRB population.
+In fact, the unambiguous repetition of its bursts is unique among all FRBs \citep{2015MNRAS.454..457P}, so it is natural to ask whether \frb is representative.
+An important first step is to demonstrate that the properties of \frb are consistent with the significant body of facts for the overall population \citep{2015MNRAS.451.3278M, 2016MPLA...3130013K}.
+The repeating nature of \frb provides us with several statistical tests we can use to test this connection.
+
+We can also assume that \frb is representative and use it to constrain the physical processes at play in the overall FRB population.
+Although we now know that FRBs are luminous, it is not yet clear what process generates the radio bursts themselves \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C}.
+The simultaneous \frb observing campaign with the VLA, Arecibo, Effelsberg, GBT, and AMI gives a more complete picture of the spectral structure of FRBs.
+FRB repetition also has strong implications for the number of FRB-generating systems in the universe \citep{2016MNRAS.458L..89C}.
+
+Given that FRBs are now known to be useful probes of the IGM, there is strong justification for continuing searches for new detections and localizations.
+The relatively faint counterpart to \frb argues that direct localization of the radio burst will continue to be the best way to find optical hosts to measure distances.
+Our multi-telescope constraints on burst spectra, measurement of host properties, burst rate estimates, and other properties will inform new strategies for finding FRBs...
 
 \section{Observations}
-\subsection{\rf}
+\subsection{VLA}
 
@@
 AMI had simultaneous coverage for bursts on 57643, 57645, 57648, and 57649.
+
+%\begin{table}
+%\caption{Caption}
+%\centering
+%\begin{tabular}{llll}
+%\hline
+%Field       & RA          & Dec   & Lon. \\ \hline
+%\end{tabular}
+%\label{fields}
+%\end{table}
 
@@
 
+\subsection{Extending FRB 121102 to Other FRBs}
+
+FRB 121102 has a DMhost of xx. Assuming other FRBs have a comparable DMhost, what can we infer about the population as a whole?
+
 \subsection{Observing Strategies}

### 2016-11-15 repeater-vladata.tex
working through vla observing info

@@
 \section{Observations}
+The data presented here were obtained from multiple programs and telescopes, but the central goal was to interferometrically localize \frb with the VLA.
+We ultimately settled on a strategy based on simultaneous observing between the VLA and Arecibo observatories with other observatories added on a best-effort basis.
+The hope was that Arecibo could be used to define times of bursts for which we could selectively search with the VLA.
+This would reduce the trials factor that limited sensitivity and potentially provide detections at multiple independent bands.
+Below, we summarize these observations, with a focus on those conducted simultaneous with VLA burst detections from \frb.
+
 \subsection{VLA}
+The \frb observing campaign started in late 2015 with a 10~hr campaign observed at 1.4~GHz.
+In April through May 2016, we conducted a 40~hr campaign at 3.0~GHz in coordination with Arecibo.
+We concluded with a new, 40~hr, coordinated campaign from August through September 2016.
+In this last campaign, the first 34 hours of VLA observations were made at 3.0~GHz, while the last 6 hours were observed at 6~GHz.
+
+All VLA fast-sampled data were observed with 5~ms sampling, 256 channels, and dual-circular polarization \citep[as in]{2015ApJ...807...16L}.
+To maximize sensitivity, the channel spectral width was set to maintain sensitivity to the known DM of \frb, while maximizing the total bandwidth.
+The total bandwidth at L (1.4~GHz), S (3.0~GHz), and C (6.0~GHz) bands was 256~MHz, 1.0~GHz, and 2.0~GHz, respectively.
 
@@
 The PUPPI pulsar backend was used to record total intensity spectra with time and frequency resolutions of 10.24~$\mu$s and 1.5625~MHz, respectively, and full Stokes polarization information.
-Each frequency channel was coherently dedispersed to 557~\dmu, thereby eliminating intra-channel dispersion smearing.
+Each frequency channel was coherently dedispersed to 557 pc cm$^{-3}$, thereby eliminating intra-channel dispersion smearing.
 PUPPI covers a total of 800~MHz of bandwidth centred at 1380.78125~MHz, but only $\sim$ 620~MHz of this band is usable due to radio frequency interference and receiver sensitivity roll-off at the band edges.

### 2016-11-16 repeater-vladata.tex
new event rate figure

@@
 \includegraphics[width=0.9\columnwidth]{lombscargle}
-\caption{Lomb-Scargle periodogram.
+\caption{Lomb-Scargle periodogram with 95\% limit on power from last observing campaign
 \label{fig:ls}}
+\end{center}
+\end{figure}
+
+Bursts seem to drop throughout last campaign. The nominal rate is 1e-4 per second, but a someone higher rate is inferred from modeling shown in Figure \ref{fig:rate}.
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=0.9\columnwidth]{event_rate_contours}
+\caption{Rate versus rate change during last campaign.
+\label{fig:rate}}
 \end{center}

### 2016-11-16 repeater-vladata.tex
added rate text

@@
 \subsection{Temporal Statistics}
-Burst detections were made very inhomogenously though the roughly 60 hours of observing toward FRB 121102.
-In the first $\sim8$\ hours of observing at L-band and the first $\sim25$\ hours observing at S-band no bursts were detected.
-Finally, in the last $\sim27$ hours of S-band observing, all nine bursts were detected.
+
+Burst detections were made very inhomogenously though the roughly 63 hours of observing toward FRB 121102.
 Data quality are relatively high and RFI did not significantly impact sensitivity, so the inhomogeneous burst distribution not an observational artifact.
 
-\cite{2016MNRAS.458L..89C}
+In the first $\sim25$\ hours observing at S-band no bursts were detected, while nine bursts were detected in the last $\sim30$ hours of S-band observing.
+Assuming the burst detection probability follows a stationary Poisson distribution, the nondetection in the first half of S-band limits the FRB rate to $\rm{R}<0.12$ hour$^{-1}$.
+The mean detection rate for the last part of the campaign was $\rm{R}=0.3$ hour$^{-1}$.
+The inconsistency shows that the detection probability is not stationary.
+
+Moreover, there is weak evidence that the \frb burst rate changes during the last part of the campaign.
+We modeled the event detection probability as a Poisson probability with a rate parameter that scales linearly with time as $R=a + b*(\rm{MJD} - 57623)$.
+We then calculated the probability of measuring the observed event rate as $\Pi P_i(R)$.
+Figure \ref{fig:rate} shows the ($a$, $b$) parameter space with contours of 50, 90, and 95\% confidence contours.
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=0.9\columnwidth]{event_rate_contours}
+\caption{Rate versus rate change during last campaign.
+\label{fig:rate}}
+\end{center}
+\end{figure}
+
+Figure \ref{fig:ls} shows a Lomb-Scargle periodogram...
+Lots of excess power corresponding to periods shorter than 1 hour.
 
@@
 \label{fig:ls}}
-\end{center}
-\end{figure}
-
-Bursts seem to drop throughout last campaign. The nominal rate is 1e-4 per second, but a someone higher rate is inferred from modeling shown in Figure \ref{fig:rate}.
-
-\begin{figure}[htb]
-\begin{center}
-\includegraphics[width=0.9\columnwidth]{event_rate_contours}
-\caption{Rate versus rate change during last campaign.
-\label{fig:rate}}
 \end{center}
@@
 
-Discussion of ``red spectrum'' and Connor \& Pen. Bursts predict bursts therefore repetition constraints of other FRBs are likely weaker than claimed...
+Discussion of ``red spectrum'' and \citet{2016MNRAS.458L..89C}. Bursts predict bursts therefore repetition constraints of other FRBs are likely weaker than claimed...
 
@@
 
+\cite{2016MNRAS.458L..89C}
+
 \section{Conclusions}
@@
 This project was supported by the University of California Office of the President under Lab Fees Research Program Award 237863.
-The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.
+The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc..
+This research made use of Astropy, a community-developed core Python package for Astronomy (Astropy Collaboration, 2013).
 

### 2016-11-17 repeater-vladata.tex
working through intro and observing summaries.

@@
-%% This is emulateapj reformatting of the AASTEX sample document
-%%
 \documentclass{emulateapj}
@@
 \author{Dewey}
-\author{Cheetham}
-\author{Howe}
+\author{Cheetham}\author{Howe}
 \altaffiltext{1}{Dept of Astronomy and Radio Astronomy Lab, Univ. of California, Berkeley, CA}
@@
 \section{Introduction}
-Fast Radio Bursts (FRBs) are a new class of millisecond-duration radio transient with a dispersion measure (DM) that implies it originate outside of our Galaxy.
+Fast Radio Bursts (FRBs) are a new class of millisecond-duration radio transient with a dispersion measure (DM) that implies that they originate outside of our Galaxy.
 At extragalactic (and potentially cosmological) distances, they are not only unusually luminous, but they provide a new tracer of other galaxies and the intergalactic medium (IGM).
-In this way, FRBs have opened a whole new playground in astrophysics \citep{}.
+In this way, FRBs have opened a whole new playground in astrophysics \citep[e.g.,][]{2014A&A...562A.137F, 2014ApJ...780L..33M, 2016MNRAS.457..232C}.
 However, that potential has been hamstrung by the lack of a definitive association of an FRB to an extragalactic host.
@@
 \frb has now been localized three orders of magnitude better than any other FRB and placed at a cosmological distance.
-Its lookback (luminosity) distance is 746 (972) Mpc \citep{planck15} is orders of magnitude larger than any other millisecond transient.
+Its lookback and luminosity distances are 746 and 972 Mpc \citep{planck15}, which are orders of magnitude larger than any other millisecond transient.
 This shows that FRBs:
@@
 \end{itemize}
-The promise of the first reported FRB is being realized \citep{2007Sci...318..777L}.
+The promise implied by the first reported FRB is now being realized \citep{2007Sci...318..777L}.
 
@@
 Although we now know that FRBs are luminous, it is not yet clear what process generates the radio bursts themselves \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C}.
-The simultaneous \frb observing campaign with the VLA, Arecibo, Effelsberg, GBT, and AMI gives a more complete picture of the spectral structure of FRBs.
+The simultaneous \frb observing campaign with the VLA, Arecibo, Effelsberg, GBT, and AMI gives a more complete picture of the spectral structure of FRB radio emission.
 FRB repetition also has strong implications for the number of FRB-generating systems in the universe \citep{2016MNRAS.458L..89C}.
@@
 
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=0.9\columnwidth]{}
+\caption{Summary of observing coverage during VLA bursts.
+\label{fig:multi}}
+\end{center}
+\end{figure}
+
 \subsection{VLA}
-The \frb observing campaign started in late 2015 with a 10~hr campaign observed at 1.4~GHz.
-In April through May 2016, we conducted a 40~hr campaign at 3.0~GHz in coordination with Arecibo.
-We concluded with a new, 40~hr, coordinated campaign from August through September 2016.
+The \frb observing campaign started in late 2015 with a 10~hr campaign observed at 1.4~GHz in the compact D configuration.
+In April through May 2016, we conducted a 40~hr campaign at 3.0~GHz in the C and CnB configurations in coordination with Arecibo.
+We concluded with a new, 40~hr, coordinated campaign from August through September 2016 in the B configuration and during the move to the most extended A configuration.
 In this last campaign, the first 34 hours of VLA observations were made at 3.0~GHz, while the last 6 hours were observed at 6~GHz.
@@
 All VLA fast-sampled data were observed with 5~ms sampling, 256 channels, and dual-circular polarization \citep[as in]{2015ApJ...807...16L}.
-To maximize sensitivity, the channel spectral width was set to maintain sensitivity to the known DM of \frb, while maximizing the total bandwidth.
+To maximize sensitivity, the channel frequency width was set to maintain sensitivity to the known DM of \frb, while maximizing the total bandwidth.
 The total bandwidth at L (1.4~GHz), S (3.0~GHz), and C (6.0~GHz) bands was 256~MHz, 1.0~GHz, and 2.0~GHz, respectively.
 
-All observations in August and Septmeber were searched in quasi real-time by a prototype version of \rf.
+Observations in August and Septmeber were searched in quasi real-time by a prototype version of \rf\footnote{See \url{http://realfast.io}.}.
 \rf\ is a real-time, fast imaging transient search system.
-The current, prototype runs on existing hardware of the VLA correlator backend, while the future \rf\ will run on a dedicated GPU cluster.
+The current, prototype runs on existing, CPU-based hardware of the VLA correlator backend, while the future \rf\ will run on a dedicated GPU cluster.
 The transient search pipeline software is called ``rtpipe''\footnote{See \url{https://github.com/caseyjlaw/rtpipe}} and is mostly written in Python.
+The transient search pipeline is described in \citet{2015ApJ...807...16L} and performs data calibration, flagging, dedispersion, and imaging.
+Images were formed for each integration at DMs of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$.
+Each image with a pixel higher than 6.4$\sigma$ is saved to capture both real and thermal-noise candidates as a check of data quality.
+Gain calibration is read from the "telcal" system, which uses phase-only calibration on the previous gain calibrator.
 
 Burst detections and localizations were made within hours of data being recorded.
+The transient search starts when data are recorded, but this prototype of \rf is a factor of several times slower than real-time, so we refer to the detection as "quasi real-time".
+When a candidate significance higher than 7.4$\sigma$, \rf generates a candidate visualization with an image and spectrum.
+
+More detailed analysis, including improved calibration and localization, is conducted offline.
+Computational notebooks to reproduce the transient detection and localization can be found at \url{https://github.com/caseyjlaw/FRB121102}.
+Time cut-out visibility data are available at \url{https://doi.org/10.7910/DVN/TLDKXG}.
+Original visibility data are available under VLA program codes 16A-459 and 16A-496 and can be downloaded at \url{http://archive.nrao.edu}.
 
@@
 
-% from the first paper
+% copied from the first paper
 During the joint Arecibo-VLA campaign, Arecibo observed with the L-wide receiver, which has an observational frequency range of 1.15 to 1.73~GHz and a full width at half maximum beam size of 3.3 arcmin.
@@
 
+Observations during VLA bursts:
+57643.420393  57643.478739 (PUPPI down; mock C band only)
+57648.393437  57648.463303
+57649.394722  57649.460378
+
 \subsection{Effelsberg}
 
+% copied from Laura's paper
+Observations were conducted at an observing frequency of 4.6 to 5.1~GHz.
+The S60mm receiver has a system equivalent flux density of 18 Jy and a full-width half-max (FWHM) beam size of 2.4\arcmin at 4.85~GHz.
+Pulsar search mode data were recorded with the PFFTS backend.
+Total intensity spectra were recorded with a time resolution of 65.5~$\mu$s and a bandwidth of 500~MHz divided into 128 frequency channels.
+Note, the inter-channel DM smearing time for 560~pc cm$^{-3}$\ is $\sim$0.2 msec at 4.6 GHz.
+
+100~MHz BW filter in place for two sessions coincident with VLA...
+
+Observations during VLA bursts:
+...
+
 \subsection{AMI}
+
+Observations during VLA bursts:
+57643.3351  57643.4585
+57645.3317  57645.4579
+57648.3352  57648.4580
+57649.3353  57649.4580
 
@@
 Figure \ref{fig:sgram} shows the spectrograms of all nine bursts detected by \rf.
-
-Computational notebooks to reproduce the transient detection and localization can be found at \url{https://github.com/caseyjlaw/FRB121102}.
-Time cut-out visibility data are available at \url{https://doi.org/10.7910/DVN/TLDKXG}.
-Original visibility data are available under VLA program codes 16A-459 and 16A-496 and can be downloaded at \url{http://archive.nrao.edu}.
 
@@
 
-Arecibo had coverage for 57638, 57643, 57645, 57648, and 57649. For 57643 observing was at C band only. At 57648, a burst is seen at 3757s, coincident with the VLA burst.
-
-Effelsberg had simultaneous coverage for bursts on MJD 57648 and 57649. No simultaneous detections.
-
+See Figure \ref{fig:multi} for coverage of VLA bursts...
+Arecibo had coverage for 57648 VLA burst and sees a coincident burst.
+Effelsberg had simultaneous coverage for VLA bursts on 57648 and 57649, but no detections.
 AMI had simultaneous coverage for bursts on 57643, 57645, 57648, and 57649.

### 2016-11-18 repeater-vladata.tex
added figure and makefile

@@
 
-\title{\frb: Very Large Array Burst Properties and Implications for Overall FRB Population}
+\title{\frb: Properties of VLA Bursts and Implications for Overall FRB Population}
 \shorttitle{\frb Burst Properties}
@@
 
-\begin{figure}[htb]
+\begin{figure*}[htb]
 \begin{center}
-\includegraphics[width=0.9\columnwidth]{}
-\caption{Summary of observing coverage during VLA bursts.
+\includegraphics[width=2\columnwidth]{timeline}
+\caption{Summary of observing coverage during the multi-telescope observing campaign.
+Days with an observation are marked with symbols, while detections of \frb are enclosed in a black circle.
+The black dashed line shows the VLA burst detections with simultaneous coverage with other telescopes.
 \label{fig:multi}}
 \end{center}
-\end{figure}
+\end{figure*}
 
@@
 
-Observations during VLA bursts:
-57643.420393  57643.478739 (PUPPI down; mock C band only)
-57648.393437  57648.463303
-57649.394722  57649.460378
+3 observations during VLA bursts...
 
@@
 
-Observations during VLA bursts:
-57643.3351  57643.4585
-57645.3317  57645.4579
-57648.3352  57648.4580
-57649.3353  57649.4580
+4 observations during VLA bursts...
 

### 2016-11-18 repeater-vladata.tex
observing pattern figure almost done
figure includes all arecibo observing, but not all bursts

@@
 \newcommand{\rf}{\emph{realfast}}
-\newcommand{\frb}{\emph{FRB 121102}}
+\newcommand{\frb}{FRB 121102}
 
@@
 \title{\frb: Properties of VLA Bursts and Implications for Overall FRB Population}
-\shorttitle{\frb Burst Properties}
+\shorttitle{\frb\ Burst Properties}
 \shortauthors{Law et al.}
@@
 
-The discovery of repeating bursts from \frb has shown that at least some FRBs are not cataclysmic and opened potential for studying a homogenous sample of bursts...
+The discovery of repeating bursts from \frb\ has shown that at least some FRBs are not cataclysmic and opened potential for studying a homogenous sample of bursts...
 Our recent coordinated campaign with the Very Large Array and Arecibo Observatory has made the first direct, arcsecond-scale localization of an FRB and unambiguously associated it with counterparts in other observations.
@@
 
-The connection of \frb to the overall population...
+The connection of \frb\ to the overall population...
 
@@
 In mid 2015, new Arecibo observations revealed a series of bursts at the same DM and sky position demonstrating that FRBs are capable of repetition \citep{2016Natur.531..202S}.
-Beginning in August of 2015, we made the first of nine detections of \frb with the Very Large Array (CITE) and localized it with a precision of 0.1\arcsec.
-Deep radio and optical observing shows that \frb is unambiguously associated with a persistent radio and optical source at a redshift of 0.193 (CITE).
+Beginning in August of 2015, we made the first of nine detections of \frb\ with the Very Large Array (CITE) and localized it with a precision of 0.1\arcsec.
+Deep radio and optical observing shows that \frb\ is unambiguously associated with a persistent radio and optical source at a redshift of 0.193 (CITE).
 
-\frb has now been localized three orders of magnitude better than any other FRB and placed at a cosmological distance.
+\frb\ has now been localized three orders of magnitude better than any other FRB and placed at a cosmological distance.
 Its lookback and luminosity distances are 746 and 972 Mpc \citep{planck15}, which are orders of magnitude larger than any other millisecond transient.
@@
 
-The cosmological distance for \frb could have wide-ranging implications for the FRB population as a whole.
-However, it has not been demonstrated that \frb is representative of the overall FRB population.
-In fact, the unambiguous repetition of its bursts is unique among all FRBs \citep{2015MNRAS.454..457P}, so it is natural to ask whether \frb is representative.
-An important first step is to demonstrate that the properties of \frb are consistent with the significant body of facts for the overall population \citep{2015MNRAS.451.3278M, 2016MPLA...3130013K}.
-The repeating nature of \frb provides us with several statistical tests we can use to test this connection.
+The cosmological distance for \frb\ could have wide-ranging implications for the FRB population as a whole.
+However, it has not been demonstrated that \frb\ is representative of the overall FRB population.
+In fact, the unambiguous repetition of its bursts is unique among all FRBs \citep{2015MNRAS.454..457P}, so it is natural to ask whether \frb\ is representative.
+An important first step is to demonstrate that the properties of \frb\ are consistent with the significant body of facts for the overall population \citep{2015MNRAS.451.3278M, 2016MPLA...3130013K}.
+The repeating nature of \frb\ provides us with several statistical tests we can use to test this connection.
 
-We can also assume that \frb is representative and use it to constrain the physical processes at play in the overall FRB population.
+We can also assume that \frb\ is representative and use it to constrain the physical processes at play in the overall FRB population.
 Although we now know that FRBs are luminous, it is not yet clear what process generates the radio bursts themselves \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C}.
-The simultaneous \frb observing campaign with the VLA, Arecibo, Effelsberg, GBT, and AMI gives a more complete picture of the spectral structure of FRB radio emission.
+The simultaneous \frb\ observing campaign with the VLA, Arecibo, Effelsberg, GBT, and AMI gives a more complete picture of the spectral structure of FRB radio emission.
 FRB repetition also has strong implications for the number of FRB-generating systems in the universe \citep{2016MNRAS.458L..89C}.
@@
 Given that FRBs are now known to be useful probes of the IGM, there is strong justification for continuing searches for new detections and localizations.
-The relatively faint counterpart to \frb argues that direct localization of the radio burst will continue to be the best way to find optical hosts to measure distances.
+The relatively faint counterpart to \frb\ argues that direct localization of the radio burst will continue to be the best way to find optical hosts to measure distances.
 Our multi-telescope constraints on burst spectra, measurement of host properties, burst rate estimates, and other properties will inform new strategies for finding FRBs...
@@
 \section{Observations}
-The data presented here were obtained from multiple programs and telescopes, but the central goal was to interferometrically localize \frb with the VLA.
+\begin{figure*}[t]
+\begin{center}
+\includegraphics[width=2\columnwidth]{timeline}
+\caption{Summary of observing coverage during the multi-telescope observing campaign.
+Uncircled symbols show days with observations and circles show detections of \frb.
+*Only the coincident Arecibo burst is currently circled*.
+The black dashed line shows the VLA burst detections with simultaneous coverage with other telescopes.
+\label{fig:multi}}
+\end{center}
+\end{figure*}
+
+The data presented here were obtained from multiple programs and telescopes, but the central goal was to interferometrically localize \frb\ with the VLA.
 We ultimately settled on a strategy based on simultaneous observing between the VLA and Arecibo observatories with other observatories added on a best-effort basis.
@@
 
-\begin{figure*}[htb]
-\begin{center}
-\includegraphics[width=2\columnwidth]{timeline}
-\caption{Summary of observing coverage during the multi-telescope observing campaign.
-Days with an observation are marked with symbols, while detections of \frb are enclosed in a black circle.
-The black dashed line shows the VLA burst detections with simultaneous coverage with other telescopes.
-\label{fig:multi}}
-\end{center}
-\end{figure*}
-
 \subsection{VLA}
-The \frb observing campaign started in late 2015 with a 10~hr campaign observed at 1.4~GHz in the compact D configuration.
+The \frb\ observing campaign started in late 2015 with a 10~hr campaign observed at 1.4~GHz in the compact D configuration.
 In April through May 2016, we conducted a 40~hr campaign at 3.0~GHz in the C and CnB configurations in coordination with Arecibo.
@@
 Burst detections and localizations were made within hours of data being recorded.
-The transient search starts when data are recorded, but this prototype of \rf is a factor of several times slower than real-time, so we refer to the detection as "quasi real-time".
-When a candidate significance higher than 7.4$\sigma$, \rf generates a candidate visualization with an image and spectrum.
+The transient search starts when data are recorded, but this prototype of \rf\ is a factor of several times slower than real-time, so we refer to the detection as "quasi real-time".
+When a candidate significance higher than 7.4$\sigma$, \rf\ generates a candidate visualization with an image and spectrum.
 
@@
 
-3 observations during VLA bursts...
+4 observations during VLA bursts... One simultaneous detection. Lots more activity at Arecibo overall.
 
@@
 
-Observations during VLA bursts:
-...
+2 observations during VLA bursts...
 
@@
 
-Moreover, there is weak evidence that the \frb burst rate changes during the last part of the campaign.
+Moreover, there is weak evidence that the \frb\ burst rate changes during the last part of the campaign.
 We modeled the event detection probability as a Poisson probability with a rate parameter that scales linearly with time as $R=a + b*(\rm{MJD} - 57623)$.

### 2016-11-18 timeline.py

@@ -1,0 +1,82 @@
+#! /bin/env python
+# SC 20160328 Plot detection timeline
+# CJL 20161117 Update for VLA FRB 121102 paper
+
+from numpy import *
+from matplotlib.pyplot import *
+import datetime
+from pylab import date2num
+from astropy import time
+
+# parse obs data
+(obs, t1, t2, tel, burst) = loadtxt('obs_data.txt', dtype=str, unpack=True)
+for i in range(len(obs)):
+	if obs[i] == 'mjd':
+		t1c = time.Time(float(t1[i]), format='mjd').iso
+		t2c = time.Time(float(t2[i]), format='mjd').iso
+		obs[i], t1[i] = t1c.split()
+		_, t2[i] = t2c.split()
+obsdate = array(map(lambda od: datetime.datetime.strptime(od, "%Y-%m-%d"), obs))
+
+# Define an offset and symbol type for each telescope
+telescopes = ['AO', 'VLA', 'Effelsberg', 'AMI']
+offs = [3, 2, 1, 0]
+offset = dict(zip(telescopes, offs))
+psyms = ['+', 'v', 'x', '.']
+psym = dict(zip(telescopes, psyms))
+pcols = ['g','r','b','y']
+pcol = dict(zip(telescopes, pcols))
+
+# set font properties
+rc('font', family='sans-serif')
+rc('font', serif='Times New Roman')
+rc('font', size=16)
+
+def putdot(ax, i):
+	pltx = obsdate[i]
+	plty = offset[tel[i]]
+	if int(burst[i]):
+		ax.scatter(pltx, plty, marker='o', s=300, linewidth=2, facecolor='none', edgecolor='k')
+		if int(burst[i]) > 1:
+			ax.scatter(pltx, plty, marker='o', s=600, linewidth=2, facecolor='none', edgecolor='k')
+
+	ax.scatter(pltx, plty, marker=psym[tel[i]], s=100, linewidth=3, facecolor=pcol[tel[i]], edgecolor='none')
+
+def d2n(yyyy, mm, dd):
+	return( date2num(datetime.date(yyyy, mm, dd)) )
+
+# Paint on all dots, then fiddle
+
+def labeltelleft(ax, num):
+	for teln in telescopes:
+		yval = offset[teln]
+		xval = xl - 0.5
[…]

### 2016-11-18 repeater-vladata.tex
added note about spectra
added effelsberg filter info. more complete plot with ao obs

@@
 Total intensity spectra were recorded with a time resolution of 65.5~$\mu$s and a bandwidth of 500~MHz divided into 128 frequency channels.
+Due to a configuation error, a filter was added that limited the bandwidth to 100-MHz filter centered on 4.85 GHz for Sept 16--18.
 Note, the inter-channel DM smearing time for 560~pc cm$^{-3}$\ is $\sim$0.2 msec at 4.6 GHz.
@@
 
+Given measured band for VLA/AO detection/limits, plus in-band VLA detections, we can characterize typical burst spectrum as an envelope of width xx MHz. The center frequency can fall at any GHz band.
+
 The VLA S-band recievers natively measure circular polarization, although observations did not include polarization calibration procedures.
@@
 
+Given that bursts have $<1$~GHz-scale spectra, wide bandwidths improve odds of detection.
+
 \section{Conclusions}

### 2016-11-22 repeater-vladata.tex
draft circulated with acf figure

@@
 \begin{abstract}
-The highly-dispersed, millisecond radio transients known as Fast Radio Bursts have recently emerged as a new class...
-
-The discovery of repeating bursts from \frb\ has shown that at least some FRBs are not cataclysmic and opened potential for studying a homogenous sample of bursts...
-Our recent coordinated campaign with the Very Large Array and Arecibo Observatory has made the first direct, arcsecond-scale localization of an FRB and unambiguously associated it with counterparts in other observations.
-This campaign detected nine bursts at the VLA from 2.5 to 3.5~GHz and many more at Arecibo, GBT, and Effelsberg.
-The coordination of these observations allow us to refine our picture of the physical processes in \frb.
-
-With so many bursts, we can make the first reliable measures of burst flux distribution and temporal statistics...
-
-The connection of \frb\ to the overall population...
-
+The millisecond radio transients known as Fast Radio Bursts have recently emerged as a mysterious, new class of astrophysical transient.
+The discovery of repeating bursts from \frb\ has shown that at least some FRBs are not cataclysmic and opened potential for studying a FRB properties via a homogenous sample of bursts.
+With the recent localization of \frb with the Very Large Array has helped measure its distance and intrinsic properties of the bursting source and its multiwavelength associations.
+This localization was made with 9 bursts seen by the VLA in coordination the Arecibo, Effelsberg, and AMI-LA observatories.
+We present a detailed analysis of these bursts, including the first simultaneous detection of an FRB with multiple telescopes.
+We show that the burst spectra typically have a broad Gaussian shape on the scale of $\sim500$~MHz with fine spectral structure consistent with either scintillation or nanosecond temporal structure.
+We present the first burst flux distribution and temporal statistics for \frb and argue that it is consistent with the broader FRB population...
 \end{abstract}
@@
 \end{itemize}
-The promise implied by the first reported FRB is now being realized \citep{2007Sci...318..777L}.
+The promise implied by the first reported FRB \citep{2007Sci...318..777L} is now being realized.
 
@@
 However, it has not been demonstrated that \frb\ is representative of the overall FRB population.
-In fact, the unambiguous repetition of its bursts is unique among all FRBs \citep{2015MNRAS.454..457P}, so it is natural to ask whether \frb\ is representative.
+In fact, the repetition of its bursts is unique among all FRBs \citep{2015MNRAS.454..457P}, so it is natural to ask whether \frb\ is representative.
 An important first step is to demonstrate that the properties of \frb\ are consistent with the significant body of facts for the overall population \citep{2015MNRAS.451.3278M, 2016MPLA...3130013K}.
@@
 Although we now know that FRBs are luminous, it is not yet clear what process generates the radio bursts themselves \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C}.
-The simultaneous \frb\ observing campaign with the VLA, Arecibo, Effelsberg, GBT, and AMI gives a more complete picture of the spectral structure of FRB radio emission.
+The simultaneous \frb\ observing campaign with the VLA, Arecibo, Effelsberg, GBT, and AMI-LA gives a more complete picture of the spectral structure of FRB radio emission.
 FRB repetition also has strong implications for the number of FRB-generating systems in the universe \citep{2016MNRAS.458L..89C}.
@@
 \section{Observations}
+
 \begin{figure*}[t]
@@
 Uncircled symbols show days with observations and circles show detections of \frb.
-*Only the coincident Arecibo burst is currently circled*.
+Only the coincident Arecibo burst is currently circled (**change?**).
 The black dashed line shows the VLA burst detections with simultaneous coverage with other telescopes.
@@
 The data presented here were obtained from multiple programs and telescopes, but the central goal was to interferometrically localize \frb\ with the VLA.
-We ultimately settled on a strategy based on simultaneous observing between the VLA and Arecibo observatories with other observatories added on a best-effort basis.
+The observing strategy was to ensure simultaneous observing between the VLA and Arecibo observatories and add other observatories added on a best-effort basis.
 The hope was that Arecibo could be used to define times of bursts for which we could selectively search with the VLA.
@@
 
-Observations in August and Septmeber were searched in quasi real-time by a prototype version of \rf\footnote{See \url{http://realfast.io}.}.
+Observations in August and Septmeber were searched by a prototype version of \rf\footnote{See \url{http://realfast.io}.}.
 \rf\ is a real-time, fast imaging transient search system.
@@
 Images were formed for each integration at DMs of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$.
-Each image with a pixel higher than 6.4$\sigma$ is saved to capture both real and thermal-noise candidates as a check of data quality.
 Gain calibration is read from the "telcal" system, which uses phase-only calibration on the previous gain calibrator.
@@
 The transient search starts when data are recorded, but this prototype of \rf\ is a factor of several times slower than real-time, so we refer to the detection as "quasi real-time".
-When a candidate significance higher than 7.4$\sigma$, \rf\ generates a candidate visualization with an image and spectrum.
+Each image with a pixel higher than 6.4$\sigma$ has some rudimentary data saved to capture both real and thermal-noise candidates as a check of data quality.
+For each image with a pixel higher than 7.4$\sigma$, \rf\ generates a candidate visualization with an image and spectrum.
+More detailed analysis, including improved calibration and localization, is conducted offline.
 
-More detailed analysis, including improved calibration and localization, is conducted offline.
 Computational notebooks to reproduce the transient detection and localization can be found at \url{https://github.com/caseyjlaw/FRB121102}.
@@
 4 observations during VLA bursts...
+Upper limit on burst flux density limits any significant "afterglow".
+Deep image sensitivity is limited by confusion and is approximately equal to the flux density observed by VLA (CITE).
 
@@
 
-\subsection{VLA Detections}
+\subsection{VLA Bursts}
 
+\subsubsection{Dynamic Spectra}
 Figure \ref{fig:sgram} shows the spectrograms of all nine bursts detected by \rf.
@@
  \end{minipage}
- \caption{Spectrograms (time vs frequency intensity maps) for all nine VLA bursts. Note that bursts are detected in 5~ms images generated from dedispersed visibilities. **NOT SURE WHY ONE FIG LARGER**
+ \caption{Spectrograms (time vs frequency intensity maps) for all nine VLA bursts. Note that bursts are detected in 5~ms images generated from dedispersed visibilities.
  \label{fig:sgram}}
@@
 
-\subsection{Multi-Telescope Burst Spectra}
-
-See Figure \ref{fig:multi} for coverage of VLA bursts...
-Arecibo had coverage for 57648 VLA burst and sees a coincident burst.
-Effelsberg had simultaneous coverage for VLA bursts on 57648 and 57649, but no detections.
-AMI had simultaneous coverage for bursts on 57643, 57645, 57648, and 57649.
+We used a fine dispersion grid to find the best-fit DM for each burst. Table \ref{tab:spec} shows the best-fit DM values... Dispersion measure changes between bursts significant?
 
@@
 %\end{tabular}
-%\label{fields}
+%\label{tab:spec}
 %\end{table}
 
-\subsection{VLA Spectra}
-After detection, we refined the analysis of each burst offline. We used a fine dispersion grid to find the best-fit DM for each burst.
-
-Table?
-57623 (DM$=561$ pc cm$^{-3}$)
-57633, Scan 7 (DM$=554$ pc cm$^{-3}$)
-57633, Scan 13 (DM$=559$ pc cm$^{-3}$)
-57638 (DM$=554$ pc cm$^{-3}$)
-57643 (DM$=559$ pc cm$^{-3}$)
-57645 (DM$=572$ pc cm$^{-3}$)
-57646 (DM$=573$ pc cm$^{-3}$)
-57648 (DM$=559$ pc cm$^{-3}$)
-57649 (DM$=552$ pc cm$^{-3}$).
-
-Dispersion measure changes between bursts significant?
-
-Burst spectra are shown in Figure \ref{fig:spec}...
+\subsubsection{Spectral modeling}
+After detection, we refined the analysis of each burst offline. Burst spectra are shown in Figure \ref{fig:spec}...
 
@@
 \caption{Spectra of nine bursts seen by the VLA from 2.5 to 3.5~GHz.  **LABELS ALL SAME FREQ. SOME SHOULD START HIGHER FOR DROPPED CHANNELS**
+%Table?
+%57623 (DM$=561$ pc cm$^{-3}$)
+%57633, Scan 7 (DM$=554$ pc cm$^{-3}$)
+%57633, Scan 13 (DM$=559$ pc cm$^{-3}$)
+%57638 (DM$=554$ pc cm$^{-3}$)
+%57643 (DM$=559$ pc cm$^{-3}$)
+%57645 (DM$=572$ pc cm$^{-3}$)
+%57646 (DM$=573$ pc cm$^{-3}$)
+%57648 (DM$=559$ pc cm$^{-3}$)
+%57649 (DM$=552$ pc cm$^{-3}$).
 \label{fig:spec}}
@@
 
-Given measured band for VLA/AO detection/limits, plus in-band VLA detections, we can characterize typical burst spectrum as an envelope of width xx MHz. The center frequency can fall at any GHz band.
+We fit a Gaussian model to each burst to estimate their characteristic width and peak flux... As shown in Table \ref{tab:spec}, the typical frequency scale is xx MHz...
 
+\subsubsection{Spectral Autocorrelation}
+The spectral autocorrelation is used to infer both intrinsic and scintillation properties \citep{}.
+Figure \ref{fig:acf} shows the spectral autocorrellation for the MJD 57633, scan 7 burst.
+Some marginal evidence of spectral correlation on the scale of the channel resolution (4~MHz)?
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=0.9\columnwidth]{acf_57633_scan7}
+\caption{
+\label{fig:acf}}
+\end{center}
+\end{figure}
+
+\subsubsection{Circular Polarization}
 The VLA S-band recievers natively measure circular polarization, although observations did not include polarization calibration procedures.
@@
 
+\subsection{Multi-Telescope Burst Spectra}
+See Figure \ref{fig:multi} for coverage of VLA bursts...
+Arecibo had coverage for 57648 VLA burst and sees a coincident burst.
+No other coincident bursts seen.
+**Make figure of VLA/AO dynamic spectrum on 57648**
+
+%\begin{figure}[htb]
+%\begin{center}
+%\includegraphics[width=0.9\columnwidth]{}
+%\caption{
+%\label{fig:}}
+%\end{center}
+%\end{figure}
+
+Given measured band for VLA/AO detection/limits, plus in-band VLA detections, we can characterize typical burst spectrum as an envelope of width xx MHz. The center frequency can fall at any GHz band.
+
 \subsection{Brightness Distribution}
 
-The bursts seen by the VLA range in significance from 10 to 150$\sigma$. Offline analysis for flux scale...
+The bursts seen by the VLA range in significance from 10 to 150$\sigma$. Table \ref{tab:spec} shows the estimated burst luminosity from spectral modeling...
 
-Figure \ref{fig:logns} shows the flux distribution of the nine VLA bursts. Flatness...
+Figure \ref{fig:logns} shows the flux distribution of the nine VLA bursts. Quantify flatness...
 
@@
 \includegraphics[width=0.9\columnwidth]{logns}
-\caption{Log N -- Log SNR distribution of real-time detections of FRB 121102.
+\caption{Log N -- Log SNR distribution of real-time detections of FRB 121102. **Update to luminosity distribution**
 \label{fig:logns}}
@@
 
-Doubts were cast on the first FRB detection (``Lorimer burst'') due to its unusually high brightness.
-The lack of lower-significance detections suggested that this burst was unlikely to be part of any astrophysical population...
+Compare luminosity distribution to flux distribution measured by \citep{2016ApJ...830...75V}...
 
 \subsection{Temporal Statistics}
-
 Burst detections were made very inhomogenously though the roughly 63 hours of observing toward FRB 121102.
@@
 
-\subsection{Connection to Overall FRB Population}
+\subsection{Luminosity Distribution}
+Doubts were cast on the first FRB detection (``Lorimer burst'') due to its unusually high brightness.
+The lack of lower-significance detections suggested that this burst was unlikely to be part of any astrophysical population.
+With more detections, it has become clear that the FRB population has a relatively flat flux distribution \citep{2016ApJ...830...75V, 2016arXiv161100458L}.
+This fact was demonstrated with yet another detection of an extremely bright FRB \citep{2016arXiv161105758R}.
 
-Flat luminosity distribution of FRB121102 and overall population
+Discuss comparison FRB 121102 luminosity distribution to that of FRB population...
+Imagine physical log N/log S with cut-offs and scattering can bias the intrinsic into the observed distribution (Macquart and Johnston)...
 
-Does local (100 Mpc) population with flat luminosity distribution reproduce observed properties?
-Imagine also how log N/log S cut-offs and scattering biases the intrinsic into the observed distribution (Macquart and Johnston)
-
+\subsection{Repetition}
 Discussion of ``red spectrum'' and \citet{2016MNRAS.458L..89C}. Bursts predict bursts therefore repetition constraints of other FRBs are likely weaker than claimed...
 
-Intrinsic versus refractive scintillation
+Constraints on repetition assuming "red spectrum" for whole population. Simulation using observed burst temporal statistics...
 
-Constraints on repetition assuming "red spectrum" for whole population. Simulation using observed burst temporal statistics...
+Intrinsic versus refractive scintillation...
+
+Fewer FRBs out there...
 
@@
 
-\subsection{Extending FRB 121102 to Other FRBs}
-
-FRB 121102 has a DMhost of xx. Assuming other FRBs have a comparable DMhost, what can we infer about the population as a whole?
-
 \subsection{Observing Strategies}
 
-Targeting known FRBs is optimal
+Repetition implies that targeting known FRBs is optimal.
 
-Wide, low-sensitivity searches are best way to conduct a blind search
-
-\cite{2016MNRAS.458L..89C}
+Repetition and shallow luminosity distribution show that shallow and wide is the best way to blindly find FRBs.
 

### 2016-11-23 repeater-vladata.tex
obs figure looking good. working in spectral modeling

@@
 \includegraphics[width=2\columnwidth]{timeline}
-\caption{Summary of observing coverage during the multi-telescope observing campaign.
-Uncircled symbols show days with observations and circles show detections of \frb.
-Only the coincident Arecibo burst is currently circled (**change?**).
-The black dashed line shows the VLA burst detections with simultaneous coverage with other telescopes.
+\caption{Summary of observing coverage and detections of \frb\ during the multi-telescope observing campaign.
+Symbols show days with observations and symbols with circles show detections of \frb.
+Multiple circles indicate multiple burst detections, except for Arecibo, which typically has multiple detections per observing session (a detailed analysis is left for a future paper).
+The black dashed lines show the VLA burst detections with simultaneous coverage at other telescopes.
+The solid black line shows the simultaneous burst detection at VLA and Arecibo.
 \label{fig:multi}}
@@
 
-%\begin{table}
-%\caption{Caption}
-%\centering
-%\begin{tabular}{llll}
-%\hline
-%Field       & RA          & Dec   & Lon. \\ \hline
-%\end{tabular}
-%\label{tab:spec}
-%\end{table}
+\begin{table}
+\caption{Spectral Modeling of Bursts}
+\centering
+\begin{tabular}{llll}
+\hline
+Burst & Peak & Center & Width \\
+(MJD) & (Jy *not normed yet*) & (ch) & (ch) \\ \hline
+57623 & 33 & 69 & 32 \\
+57633, scan 7 & 260 & 163 & 55 \\
+57633, scan 13 & & & \\
+57638 & & & \\
+57643 & 55 & 69 & 56 \\
+57645 & & & \\
+57646 & & & \\
+57648 & & & \\
+57649 & & & \\ \hline
+\end{tabular}
+\label{tab:spec}
+\end{table}
 

### 2016-11-23 timeline.py

@@ -39,6 +39,8 @@ def putdot(ax, i):
 		ax.scatter(pltx, plty, marker='o', s=300, linewidth=2, facecolor='none', edgecolor='k')
 		if int(burst[i]) > 1:
 			ax.scatter(pltx, plty, marker='o', s=600, linewidth=2, facecolor='none', edgecolor='k')
+			if int(burst[i]) > 2:
+				ax.scatter(pltx, plty, marker='o', s=900, linewidth=2, facecolor='none', edgecolor='k')
 
 	ax.scatter(pltx, plty, marker=psym[tel[i]], s=100, linewidth=3, facecolor=pcol[tel[i]], edgecolor='none')
 
@@ -69,9 +71,11 @@ ax.set_ylim( (-0.4, 3.4) )
 ax.tick_params(labelright='off', labelleft='off')
 
 # boxes for simultaneous coverage of VLA bursts
-axhspan(-0.2, 3.2, 0.67, 0.701, fill=False, linestyle='dashed') # 57643
-axhspan(-0.2, 3.2, 0.726, 0.757, fill=False, linestyle='dashed') # 57645
-axhspan(-0.2, 3.2, 0.812, 0.873, fill=False, linestyle='dashed') # 57648 57649
+axhspan(0., 3., 0.6855, 0.6855, fill=False, linestyle='dashed') # 57643
+axhspan(0., 3., 0.743, 0.743, fill=False, linestyle='dashed') # 57645
+axhspan(0., 3., 0.8285, 0.8285, fill=False, linestyle='dashed') # 57648 57649
+axhspan(2., 3., 0.8285, 0.8285, fill=False, lw=3, linestyle='solid') # 57648 57649
+axhspan(0., 3., 0.857, 0.857, fill=False, linestyle='dashed') # 57648 57649
 
 ax.set_yticks( [0, 1, 2, 3] )
 #ax0.spines['left'].set_visible(True)

### 2016-11-24 repeater-vladata.tex
added red text notes. added table. text on dm range

@@
-\documentclass{emulateapj}
-\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref} 
+\documentclass[twocolumn]{aastex61}
+%\documentclass{emulateapj}
+%\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref} 
 \usepackage{graphicx,natbib}
@@
 
-\title{\frb: Properties of VLA Bursts and Implications for Overall FRB Population}
+\title{\frb: Multi-Telescope Burst Properties and Implications for FRB Population}
 \shorttitle{\frb\ Burst Properties}
@@
 
-\author{Casey J. Law\altaffilmark{1}}
-\author{Dewey}
-\author{Cheetham}\author{Howe}
-\altaffiltext{1}{Dept of Astronomy and Radio Astronomy Lab, Univ. of California, Berkeley, CA}
+\author[0000-0002-4119-9963]{C.~J.~Law}
+\affiliation{Dept of Astronomy and Radio Astronomy Lab, University of California, Berkeley, CA 94720, USA}
+
+\author{R.~S.~Wharton}
+\affiliation{Cornell Center for Astrophysics and Planetary Science and Department of Astronomy, Cornell University, Ithaca, NY 14853, USA}
+
+\author{M.~A.~McLaughlin}
+\affiliation{Department of Physics and Astronomy, West Virginia University, Morgantown, WV 26506, USA}
+\affiliation{Center for Gravitational Waves and Cosmology, West Virginia University, Chestnut Ridge Research Building, Morgantown, WV 26505}
+
+\author{J.~M.~Cordes}
+\affiliation{Cornell Center for Astrophysics and Planetary Science and Department of Astronomy, Cornell University, Ithaca, NY 14853, USA}
+
+%\author{M.~W.~Abruzzo}
+%\affiliation{Haverford College, 370 Lancaster Ave, Haverford, PA 19041, USA}
+
+%\author{C.~G.~Bassa}
+%\affiliation{ASTRON, Netherlands Institute for Radio Astronomy, Postbus 2, 7990 AA, Dwingeloo, The Netherlands}
+
+%\author{S.~Bogdanov}
+%\affiliation{Columbia Astrophysics Laboratory, Columbia University,  New York, NY 10027, USA}
+
+\author{G.~C.~Bower}
+\affiliation{Academia Sinica Institute of Astronomy and Astrophysics, 645 N. A'ohoku Place, Hilo, HI 96720, USA}
+
+\author{S.~Burke-Spolaor}
+\affiliation{National Radio Astronomy Observatory, Socorro, NM 87801, USA}
+\affiliation{Department of Physics and Astronomy, West Virginia University, Morgantown, WV 26506, USA}
+\affiliation{Center for Gravitational Waves and Cosmology, West Virginia University, Chestnut Ridge Research Building, Morgantown, WV 26505}
+
+\author{B.~J.~Butler}
+\affiliation{National Radio Astronomy Observatory, Socorro, NM 87801, USA}
+\author{S.~Chatterjee}
+\affiliation{Cornell Center for Astrophysics and Planetary Science and Department of Astronomy, Cornell University, Ithaca, NY 14853, USA}
+
+\author{P.~Demorest}
+\affiliation{National Radio Astronomy Observatory, Socorro, NM 87801, USA}
+
+\author{J.~W.~T.~Hessels}
+\affiliation{ASTRON, Netherlands Institute for Radio Astronomy, Postbus 2, 7990 AA, Dwingeloo, The Netherlands}
+\affiliation{Anton Pannekoek Institute for Astronomy, University of Amsterdam, Science Park 904, 1098 XH Amsterdam, The Netherlands}
+
+\author{R.~Fender}
+\affiliation{University of Oxford, UK}
+
+%\author{V.~M.~Kaspi}
+%\affiliation{Department of Physics and McGill Space Institute, McGill University, 3600 University St., Montreal, QC H3A 2T8, Canada}
+
+%\author{A.~Keimpema}
+%\affiliation{Joint Institute for VLBI ERIC, Postbus 2, 7990 AA Dwingeloo, The Netherlands}
+
+%\author{H.~J.~van~Langevelde}
+%\affiliation{Joint Institute for VLBI ERIC, Postbus 2, 7990 AA Dwingeloo, The Netherlands}
+%\affiliation{Sterrewacht Leiden, Leiden University, Postbus 9513, 2300 RA, Leiden, the Netherlands}
+
+\author{T.~J.~W.~Lazio}
+\affiliation{Jet Propulsion Laboratory, California Institute of Technology, Pasadena, CA 91109, USA}
+
+%\author[0000-0001-9814-2354]{B.~Marcote}
+%\affiliation{Joint Institute for VLBI ERIC, Postbus 2, 7990 AA Dwingeloo, The Netherlands}
+
+\author{K.~Mooley}
+\affiliation{University of Oxford, UK}
+
+%\author{Z.~Paragi}
+%\affiliation{Joint Institute for VLBI ERIC, Postbus 2, 7990 AA Dwingeloo, The Netherlands}
+
+%\author{S.~M.~Ransom}
+%\affiliation{National Radio Astronomy Observatory, Charlottesville, VA 22903, USA}
+
+\author{M.~Rupen}
+\affiliation{National Research Council of Canada, Herzberg Astronomy and Astrophysics, Dominion Radio Astrophysical Observatory, P.O. Box 248, Penticton, BC V2A 6J9, Canada}
+
+\author{L.~G.~Spitler}
+\affiliation{Max-Planck-Institut f\"ur Radioastronomie, Auf dem H\"ugel 69, D-53121 Bonn, Germany}
+
+\author{P.~Scholz}
+\affiliation{National Research Council of Canada, Herzberg Astronomy and Astrophysics, Dominion Radio Astrophysical Observatory, P.O. Box 248, Penticton, BC V2A 6J9, Canada}
+
+\author{A.~Seymour}
+\affiliation{Arecibo Observatory, HC3 Box 53995, Arecibo, PR 00612, USA}
+\affiliation{Max-Planck-Institut f\"ur Radioastronomie, Auf dem H\"ugel 69, Bonn, D-53121, Germany}
+
+%\author{S.~P.~Tendulkar}
+%\affiliation{Department of Physics and McGill Space Institute, McGill University, 3600 University St., Montreal, QC H3A 2T8, Canada}
 
@@
 The millisecond radio transients known as Fast Radio Bursts have recently emerged as a mysterious, new class of astrophysical transient.
-The discovery of repeating bursts from \frb\ has shown that at least some FRBs are not cataclysmic and opened potential for studying a FRB properties via a homogenous sample of bursts.
-With the recent localization of \frb with the Very Large Array has helped measure its distance and intrinsic properties of the bursting source and its multiwavelength associations.
+The discovery of repeating bursts from \frb\ has shown that at least some FRBs are not cataclysmic and opened potential for studying FRB properties via a homogenous sample of bursts.
+The recent localization of \frb\ with the Very Large Array has helped measure its distance and a host of intrinsic properties.
 This localization was made with 9 bursts seen by the VLA in coordination the Arecibo, Effelsberg, and AMI-LA observatories.
 We present a detailed analysis of these bursts, including the first simultaneous detection of an FRB with multiple telescopes.
-We show that the burst spectra typically have a broad Gaussian shape on the scale of $\sim500$~MHz with fine spectral structure consistent with either scintillation or nanosecond temporal structure.
-We present the first burst flux distribution and temporal statistics for \frb and argue that it is consistent with the broader FRB population...
+We show that the burst spectra typically have a broad Gaussian shape on the scale of $\sim500$~MHz with fine spectral structure consistent with either scintillation or unresolved temporal structure.
+We present the luminosity distribution and temporal statistics for \frb\ and argue that the whole FRB population is adequately described by a single class similar to \frb.
+We close with thoughts on optimal strategies to make new interferometric localizations of FRBs.
 \end{abstract}
@@
 The observing strategy was to ensure simultaneous observing between the VLA and Arecibo observatories and add other observatories added on a best-effort basis.
-The hope was that Arecibo could be used to define times of bursts for which we could selectively search with the VLA.
-This would reduce the trials factor that limited sensitivity and potentially provide detections at multiple independent bands.
+We coordinated observing between the VLA, Arecibo, Effelsberg, and AMI-LA telescopes, as shown in figure \ref{fig:multi}.
 Below, we summarize these observations, with a focus on those conducted simultaneous with VLA burst detections from \frb.
@@
 The \frb\ observing campaign started in late 2015 with a 10~hr campaign observed at 1.4~GHz in the compact D configuration.
-In April through May 2016, we conducted a 40~hr campaign at 3.0~GHz in the C and CnB configurations in coordination with Arecibo.
+In April through May 2016, we conducted a 40~hr campaign at 3~GHz in the C and CnB configurations in coordination with Arecibo.
 We concluded with a new, 40~hr, coordinated campaign from August through September 2016 in the B configuration and during the move to the most extended A configuration.
-In this last campaign, the first 34 hours of VLA observations were made at 3.0~GHz, while the last 6 hours were observed at 6~GHz.
+In this last campaign, the first 34 hours of VLA observations were made at 3~GHz, while the last 6 hours were observed at 6~GHz.
+This paper focuses on the data collected at 3~GHz, which includes all burst detections.
 
@@
 To maximize sensitivity, the channel frequency width was set to maintain sensitivity to the known DM of \frb, while maximizing the total bandwidth.
-The total bandwidth at L (1.4~GHz), S (3.0~GHz), and C (6.0~GHz) bands was 256~MHz, 1.0~GHz, and 2.0~GHz, respectively.
+The total bandwidth at L (1.4~GHz), S (3~GHz), and C (6~GHz) bands was 256~MHz, 1024~MHz, and 2048~MHz, respectively.
+The 3~GHz data recorded data in 8 spectral windows with 32 channels each.
 
@@
 The current, prototype runs on existing, CPU-based hardware of the VLA correlator backend, while the future \rf\ will run on a dedicated GPU cluster.
-The transient search pipeline software is called ``rtpipe''\footnote{See \url{https://github.com/caseyjlaw/rtpipe}} and is mostly written in Python.
+The transient search pipeline software is called \emph{rtpipe}\footnote{See \url{https://github.com/caseyjlaw/rtpipe}} and is mostly written in Python.
 The transient search pipeline is described in \citet{2015ApJ...807...16L} and performs data calibration, flagging, dedispersion, and imaging.
@@
 Gain calibration is read from the "telcal" system, which uses phase-only calibration on the previous gain calibrator.
+A flux scale is calculated for each spectral window from an observation on *xx* and applied to all burst spectra.
 
@@
 
-4 observations during VLA bursts... One simultaneous detection. Lots more activity at Arecibo overall.
+In total, twelve Arecibo observations had some simultaneous coverage with the VLA.
+Four of those observations were simultaneous with bursts detected with the VLA and one of those observations detected the same VLA burst.
+During the first VLA burst with Arecibo coverage (MJD 57643), the PUPPI system failed so data were recorded with {\color{red} xx (Jason?)} at C band.
+No detection was made in that Arecibo data.
+Overall, there were many more bursts detected at Arecibo and a more detailed analysis will be presented in a future paper.
 
@@
 Total intensity spectra were recorded with a time resolution of 65.5~$\mu$s and a bandwidth of 500~MHz divided into 128 frequency channels.
-Due to a configuation error, a filter was added that limited the bandwidth to 100-MHz filter centered on 4.85 GHz for Sept 16--18.
 Note, the inter-channel DM smearing time for 560~pc cm$^{-3}$\ is $\sim$0.2 msec at 4.6 GHz.
 
-100~MHz BW filter in place for two sessions coincident with VLA...
-
-2 observations during VLA bursts...
+Five Effelsberg observations had some simultaneous coverage with the VLA, of which two were simultaneous with VLA bursts.
+Unfortunately, due to a configuration error, a 100~MHz bandwidth filter centered at 4.85~GHz was in place for both of these sessions.
+The sensitivity was about two times worse than the nominal value.
+No burst was detected in either observation.
 
@@
 
-4 observations during VLA bursts...
-Upper limit on burst flux density limits any significant "afterglow".
+{\color{red} Kunal to provide description of AMI-LA}
+
+Six AMI-LA observations had some simultaneous coverage with the VLA, of which four covered VLA bursts.
+The upper limit on burst flux density limits any significant "afterglow".
 Deep image sensitivity is limited by confusion and is approximately equal to the flux density observed by VLA (CITE).
+{\color{red} Details from Kunal}
 
 \section{Results}
+
+\subsection{Multi-Telescope Burst Spectrum}
+As shown in Figure \ref{fig:multi}, only one burst from \frb\ was detected simultaneously at more than one observatory.
+The VLA burst on 57648 was detected at Arecibo with a significance of {\color{red} xx$\sigma$ (Jason)} The relative time delay between the VLA and Arecibo is {\color{red} xx (Jason)} ms...
+
+Figure **to do** shows the dynamic spectrum formed from the phased VLA and Arecibo data... 
+This simultaneous detection of a burst from roughly 1 to 4~GHz shows that some bursts cover more than an octave of frequency.
+This is one of three bursts with similar spectral coverage at Arecibo, so the other nondetections imply that those bursts had a smaller spectral coverage.
+In fact, as described in \S \ref{sec:spec}, most of the VLA bursts appear to be fully contained in the band from 2.5 to 3.5~GHz, which implies a much smaller spectral coverage for typical bursts.
+
+**Insert figure of VLA/AO dynamic spectrum on 57648**
+
+%\begin{figure}[htb]
+%\begin{center}
+%\includegraphics[width=0.9\columnwidth]{}
+%\caption{
+%\label{fig:}}
+%\end{center}
+%\end{figure}
 
@@
 \subsubsection{Dynamic Spectra}
-Figure \ref{fig:sgram} shows the spectrograms of all nine bursts detected by \rf.
+\label{sec:spec}
+Figure \ref{fig:sgram} shows the spectrograms of all nine bursts detected by the VLA.
+We improved on the initial analysis presented in (CITE) by using a better calibration scheme and optimizing the image SNR over a fine DM grid.
+Table \ref{tab:spec} shows the improved burst parameters using this new scheme.
 
@@
  \begin{minipage}{2\columnwidth}
-  \includegraphics[width=0.25\columnwidth]{sgram_57623.png}
-  \includegraphics[width=0.25\columnwidth]{sgram_57633_scan7.png}
-  \includegraphics[width=0.25\columnwidth]{sgram_57633_scan13.png}
+  \includegraphics[width=0.18\columnwidth]{sgram_57623.png}
+  \includegraphics[width=0.18\columnwidth]{sgram_57633_scan7.png}
+  \includegraphics[width=0.18\columnwidth]{sgram_57633_scan13.png}
+  \includegraphics[width=0.18\columnwidth]{sgram_57638.png}
+  \includegraphics[width=0.18\columnwidth]{sgram_57643.png}
  \end{minipage}
@@
  \begin{minipage}{2\columnwidth}
-  \includegraphics[width=0.25\columnwidth]{sgram_57638.png}
-  \includegraphics[width=0.25\columnwidth]{sgram_57643.png}
-  \includegraphics[width=0.25\columnwidth]{sgram_57645.png}
+  \includegraphics[width=0.18\columnwidth]{sgram_57645.png}
+  \includegraphics[width=0.18\columnwidth]{sgram_57646.png}
+  \includegraphics[width=0.18\columnwidth]{sgram_57648.png}
+  \includegraphics[width=0.18\columnwidth]{sgram_57649.png}
  \end{minipage}
 
- \begin{minipage}{2\columnwidth}
-  \includegraphics[width=0.25\columnwidth]{sgram_57646.png}
-  \includegraphics[width=0.25\columnwidth]{sgram_57648.png}
-  \includegraphics[width=0.25\columnwidth]{sgram_57649.png}
- \end{minipage}
- \caption{Spectrograms (time vs frequency intensity maps) for all nine VLA bursts. Note that bursts are detected in 5~ms images generated from dedispersed visibilities.
+ \caption{Spectrograms (time vs frequency intensity maps) for the nine VLA bursts.
+Starting at the top left, the correspond to bursts 57623, 57633.68, 57633.70, 57638, 57643, 57645, 57646, 57648, and 57649.
+Note that bursts are detected in 5~ms images generated from dedispersed visibilities.
  \label{fig:sgram}}
@@
 
-We used a fine dispersion grid to find the best-fit DM for each burst. Table \ref{tab:spec} shows the best-fit DM values... Dispersion measure changes between bursts significant?
+The optimal DM values range from 552 to 572 pc cm$^{-3}$ for all bursts and from 552 to 561 pc cm$^{-3}$ for bursts with SNR$>30$.
+The expectation is that the VLA 3~GHz observing band will lose 10\% of its sensitivity for DM in error by roughly 10 pc cm$^{-3}$ \citep{2003ApJ...596.1142C}.
+However, the peak DM can be determined with a much higher precision (scaling linearly with the significance of the burst).
+We tested this model by simulating a burst with SNR$=30$ and measuring its detection significance as a function of DM.
+The simulation parameters were reproduced at the known DM with a precision of roughly 1 pc cm$^{-3}$.
+This suggests that the measured variation in DM for \frb is intrinsic to the bursts, rather than due to measurement uncertainty.
+This is consistent with the observation of intrinsic burst spectrotemporal structure that varies between bursts (CITE: WEIRD BURST).
 
-\begin{table}
-\caption{Spectral Modeling of Bursts}
+\begin{table*}
+\caption{Properties of Bursts from \frb}
 \centering
-\begin{tabular}{llll}
+\begin{tabular}{lcccccc}
 \hline
-Burst & Peak & Center & Width \\
-(MJD) & (Jy *not normed yet*) & (ch) & (ch) \\ \hline
-57623 & 33 & 69 & 32 \\
-57633, scan 7 & 260 & 163 & 55 \\
-57633, scan 13 & & & \\
-57638 & & & \\
-57643 & 55 & 69 & 56 \\
-57645 & & & \\
-57646 & & & \\
-57648 & & & \\
-57649 & & & \\ \hline
+Date     & S$_{\rm{int}}$ & Image SNR & DM$_{\rm{opt}}$ & S$_{\rm{peak}}$ & Center & FWHM \\
+(MJD)    & (mJy) &  & (pc cm$^{-3})$ & (mJy) & (GHz) & (MHz) \\ \hline
+57623    & 258 & 38 & 561 & 0.41             & 2.8 & 300 \\
+57633.68 & 2000 & 179 & 554 & 1.90           & 3.2 & 520 \\
+57633.70 & 105 & 15 & 559 & $>$0.188          & $<$2.5 & $>$350 \\
+57638    & 65  & 12 & 556 & 0.07             & 3.1 & 410 \\
+57643    & 375 & 100 & 560 & 0.39            & 2.8 & 520 \\
+57645    & 38  & 13 & 572 & 0.06             & 2.8 & 210 \\
+57646    & 69  & 20 & 555 & $>$0.16          & $<$2.5 & $>$400 \\
+57648\tablenotemark{a}    & 97  & 25 & 559 & 0.11 & 2.9 & 420 \\
+57649    & 110 & 36 & 552 & 0.07             & 2.9 & 880 \\ \hline
 \end{tabular}
+\tablenotetext{a}{Detected simultaneously with Arecibo between 1.15 and 1.73~GHz.}
 \label{tab:spec}
-\end{table}
+\end{table*}
 
 \subsubsection{Spectral modeling}
-After detection, we refined the analysis of each burst offline. Burst spectra are shown in Figure \ref{fig:spec}...
+After finding an optimal burst DM, we extract a spectrum from the integration with peak SNR. **need to confirm that bursts were unresolved in time**
+
+Burst spectra are shown in Figure \ref{fig:spec}...
 
@@
  \end{minipage}
-\caption{Spectra of nine bursts seen by the VLA from 2.5 to 3.5~GHz.  **LABELS ALL SAME FREQ. SOME SHOULD START HIGHER FOR DROPPED CHANNELS**
-%Table?
-%57623 (DM$=561$ pc cm$^{-3}$)
-%57633, Scan 7 (DM$=554$ pc cm$^{-3}$)
-%57633, Scan 13 (DM$=559$ pc cm$^{-3}$)
-%57638 (DM$=554$ pc cm$^{-3}$)
-%57643 (DM$=559$ pc cm$^{-3}$)
-%57645 (DM$=572$ pc cm$^{-3}$)
-%57646 (DM$=573$ pc cm$^{-3}$)
-%57648 (DM$=559$ pc cm$^{-3}$)
-%57649 (DM$=552$ pc cm$^{-3}$).
+\caption{Spectra of nine bursts seen by the VLA from 2.5 to 3.5~GHz.
+Orthongonal circular polarizations (RR and LL) are plotted separately.
+**LABELS ALL SAME FREQ.
+SOME SHOULD START HIGHER FOR DROPPED CHANNELS**
 \label{fig:spec}}
@@
 The spectral autocorrelation is used to infer both intrinsic and scintillation properties \citep{}.
-Figure \ref{fig:acf} shows the spectral autocorrellation for the MJD 57633, scan 7 burst.
+Figure \ref{fig:acf} shows the spectral autocorrellation for the MJD 57633.68 burst.
 Some marginal evidence of spectral correlation on the scale of the channel resolution (4~MHz)?
@@
 
-\subsection{Multi-Telescope Burst Spectra}
-See Figure \ref{fig:multi} for coverage of VLA bursts...
-Arecibo had coverage for 57648 VLA burst and sees a coincident burst.
-No other coincident bursts seen.
-**Make figure of VLA/AO dynamic spectrum on 57648**
-
-%\begin{figure}[htb]
-%\begin{center}
-%\includegraphics[width=0.9\columnwidth]{}
-%\caption{
-%\label{fig:}}
-%\end{center}
-%\end{figure}
-
-Given measured band for VLA/AO detection/limits, plus in-band VLA detections, we can characterize typical burst spectrum as an envelope of width xx MHz. The center frequency can fall at any GHz band.
-
 \subsection{Brightness Distribution}
-
 The bursts seen by the VLA range in significance from 10 to 150$\sigma$. Table \ref{tab:spec} shows the estimated burst luminosity from spectral modeling...
@@
 However, the {\it total} energy emitted could be larger depending on the duration of the emission in the source frame and other model-dependent details.
-Either way, the burst energies from \frb\ are not inconsistent with those that might be expected from the magnetosphere of a compact object\cite{cw16}.
+Either way, the burst energies from \frb\ are not inconsistent with those that might be expected from the magnetosphere of a compact object\cite{2016MNRAS.457..232C}.
 
@@
 \section{Conclusions}
+
+ % include timeline and science scope for new localizations? realfast plug and reference cosmology papers, contingency on DMhost, etc.
 

### 2016-11-25 repeater-vladata.tex
refining text down to temporal section

@@
 
-\author{R.~S.~Wharton}
-\affiliation{Cornell Center for Astrophysics and Planetary Science and Department of Astronomy, Cornell University, Ithaca, NY 14853, USA}
-
-\author{M.~A.~McLaughlin}
-\affiliation{Department of Physics and Astronomy, West Virginia University, Morgantown, WV 26506, USA}
-\affiliation{Center for Gravitational Waves and Cosmology, West Virginia University, Chestnut Ridge Research Building, Morgantown, WV 26505}
-
-\author{J.~M.~Cordes}
-\affiliation{Cornell Center for Astrophysics and Planetary Science and Department of Astronomy, Cornell University, Ithaca, NY 14853, USA}
-
 %\author{M.~W.~Abruzzo}
@@
 \author{S.~Chatterjee}
+\affiliation{Cornell Center for Astrophysics and Planetary Science and Department of Astronomy, Cornell University, Ithaca, NY 14853, USA}
+
+\author{J.~M.~Cordes}
 \affiliation{Cornell Center for Astrophysics and Planetary Science and Department of Astronomy, Cornell University, Ithaca, NY 14853, USA}
@@
 
+\author{M.~A.~McLaughlin}
+\affiliation{Department of Physics and Astronomy, West Virginia University, Morgantown, WV 26506, USA}
+\affiliation{Center for Gravitational Waves and Cosmology, West Virginia University, Chestnut Ridge Research Building, Morgantown, WV 26505}
+
 \author{K.~Mooley}
@@
 
+\author{R.~S.~Wharton}
+\affiliation{Cornell Center for Astrophysics and Planetary Science and Department of Astronomy, Cornell University, Ithaca, NY 14853, USA}
+
 \begin{abstract}
@@
 
-This paper is part of a series that presents the first localization and host identification of an FRB (CITE, CITE, ...).
+This paper is part of a series that presents the first localization and host identification of an FRB (CITE: LOC, OPT, EVN, RADIO CPART, XRAY, EFF, WEIRD).
 \frb, also known as the ``repeating FRB'', was first detected in November 2012 by the Arecibo Observatory \citep{2014ApJ...790..101S}.
 In mid 2015, new Arecibo observations revealed a series of bursts at the same DM and sky position demonstrating that FRBs are capable of repetition \citep{2016Natur.531..202S}.
-Beginning in August of 2015, we made the first of nine detections of \frb\ with the Very Large Array (CITE) and localized it with a precision of 0.1\arcsec.
-Deep radio and optical observing shows that \frb\ is unambiguously associated with a persistent radio and optical source at a redshift of 0.193 (CITE).
+Beginning in August of 2015, we made the first of nine detections of \frb\ with the Very Large Array (CITE: LOC) and localized it with a precision of 0.1\arcsec.
+Deep radio and optical observing shows that \frb\ is unambiguously associated with a persistent radio and optical source at a redshift of 0.193 (CITE: OPT, EVN).
 
@@
 Gain calibration is read from the "telcal" system, which uses phase-only calibration on the previous gain calibrator.
-A flux scale is calculated for each spectral window from an observation on *xx* and applied to all burst spectra.
+A flux scale is calculated for each spectral window from an observation on {\color{red} xx (Bryan)} and applied to all burst spectra.
 
@@
 The upper limit on burst flux density limits any significant "afterglow".
-Deep image sensitivity is limited by confusion and is approximately equal to the flux density observed by VLA (CITE).
+Deep image sensitivity is limited by confusion and is approximately equal to the flux density observed by VLA (CITE: RADIO CPART).
 {\color{red} Details from Kunal}
@@
 \subsection{Multi-Telescope Burst Spectrum}
-As shown in Figure \ref{fig:multi}, only one burst from \frb\ was detected simultaneously at more than one observatory.
+Of the four VLA burst detections from \frb with simultaneous observations \frb (Figure \ref{fig:multi}), one was detected with a consistent dedispersed time.
 The VLA burst on 57648 was detected at Arecibo with a significance of {\color{red} xx$\sigma$ (Jason)} The relative time delay between the VLA and Arecibo is {\color{red} xx (Jason)} ms...
@@
 \subsection{VLA Bursts}
-
-\subsubsection{Dynamic Spectra}
-\label{sec:spec}
-Figure \ref{fig:sgram} shows the spectrograms of all nine bursts detected by the VLA.
-We improved on the initial analysis presented in (CITE) by using a better calibration scheme and optimizing the image SNR over a fine DM grid.
-Table \ref{tab:spec} shows the improved burst parameters using this new scheme.
 
@@
 
-The optimal DM values range from 552 to 572 pc cm$^{-3}$ for all bursts and from 552 to 561 pc cm$^{-3}$ for bursts with SNR$>30$.
-The expectation is that the VLA 3~GHz observing band will lose 10\% of its sensitivity for DM in error by roughly 10 pc cm$^{-3}$ \citep{2003ApJ...596.1142C}.
-However, the peak DM can be determined with a much higher precision (scaling linearly with the significance of the burst).
-We tested this model by simulating a burst with SNR$=30$ and measuring its detection significance as a function of DM.
-The simulation parameters were reproduced at the known DM with a precision of roughly 1 pc cm$^{-3}$.
-This suggests that the measured variation in DM for \frb is intrinsic to the bursts, rather than due to measurement uncertainty.
-This is consistent with the observation of intrinsic burst spectrotemporal structure that varies between bursts (CITE: WEIRD BURST).
+\subsubsection{Dynamic Spectra}
+\label{sec:spec}
+Figure \ref{fig:sgram} shows the spectrograms of all nine bursts detected by the VLA.
+We improved on the initial analysis presented in (CITE: LOC) by using a better calibration scheme and optimizing the image SNR over a fine DM grid.
+Table \ref{tab:spec} shows the improved burst parameters using this new scheme.
 
@@
 \centering
-\begin{tabular}{lcccccc}
+\begin{tabular}{lccccccc}
 \hline
-Date     & S$_{\rm{int}}$ & Image SNR & DM$_{\rm{opt}}$ & S$_{\rm{peak}}$ & Center & FWHM \\
-(MJD)    & (mJy) &  & (pc cm$^{-3})$ & (mJy) & (GHz) & (MHz) \\ \hline
-57623    & 258 & 38 & 561 & 0.41             & 2.8 & 300 \\
-57633.68 & 2000 & 179 & 554 & 1.90           & 3.2 & 520 \\
-57633.70 & 105 & 15 & 559 & $>$0.188          & $<$2.5 & $>$350 \\
-57638    & 65  & 12 & 556 & 0.07             & 3.1 & 410 \\
-57643    & 375 & 100 & 560 & 0.39            & 2.8 & 520 \\
-57645    & 38  & 13 & 572 & 0.06             & 2.8 & 210 \\
-57646    & 69  & 20 & 555 & $>$0.16          & $<$2.5 & $>$400 \\
-57648\tablenotemark{a}    & 97  & 25 & 559 & 0.11 & 2.9 & 420 \\
-57649    & 110 & 36 & 552 & 0.07             & 2.9 & 880 \\ \hline
+Date     & S$_{\rm{int}}$ & Image SNR & L$_{\rm{int}}$ & DM$_{\rm{opt}}$ & S$_{\rm{peak}}$ & Center & FWHM \\
+(MJD)    & (mJy) &  & (ergs?) & (pc cm$^{-3})$ & (mJy?) & (GHz) & (MHz) \\ \hline
+57623    & 258 & 38 & & 561 & 0.41             & 2.8 & 300 \\
+57633.68 & 2000 & 179 & & 554 & 1.90           & 3.2 & 520 \\
+57633.70 & 105 & 15 & & 559 & $>$0.188          & $<$2.5 & $>$350 \\
+57638    & 65  & 12 & & 556 & 0.07             & 3.1 & 410 \\
+57643    & 375 & 100 & & 560 & 0.39            & 2.8 & 520 \\
+57645    & 38  & 13 & & 572 & 0.06             & 2.8 & 210 \\
+57646    & 69  & 20 & & 555 & $>$0.16          & $<$2.5 & $>$400 \\
+57648\tablenotemark{a}    & 97 & 25 & & 559 & 0.11 & 2.9 & 420 \\
+57649    & 110 & 36 & & 552 & 0.07             & 2.9 & 880 \\ \hline
 \end{tabular}
@@
 
+\subsubsection{Dispersion Meausres}
+The initial VLA detections were made by searching a DM grid that allowed inter-DM sensitivity losses up to roughly 10\%.
+For the VLA 3~GHz observing band, we estimated that trials could be separated by at most 10 pc cm$^{-3}$ \citep{2003ApJ...596.1142C}.
+We refined that analysis by maximizing the image SNR for DMs spaced by 1 pc cm$^{-3}$.
+The optimal DM values range from 552 to 572 pc cm$^{-3}$ for all bursts and from 552 to 561 pc cm$^{-3}$ for bursts with SNR$>30$.
+
+The uncertainty in the peak DM measurement is defined by the DM sensitivity loss curve and the significance of the burst.
+We tested this model by simulating a burst with SNR$=30$ and measuring its detection significance as a function of DM.
+The simulation parameters were reproduced at the known DM with a precision of roughly 1 pc cm$^{-3}$.
+This suggests that the measured variation in DM for \frb is intrinsic to the bursts, rather than due to measurement uncertainty.
+This is consistent with the observation of intrinsic burst spectrotemporal structure that varies between bursts (CITE: WEIRD).
+
 \subsubsection{Spectral modeling}
-After finding an optimal burst DM, we extract a spectrum from the integration with peak SNR. **need to confirm that bursts were unresolved in time**
-
-Burst spectra are shown in Figure \ref{fig:spec}...
+After finding an optimal burst DM, we extract a spectrum from the integration with peak SNR (Figure \ref{fig:spec}).
+After DM optimization, all bursts appear unresolved at the 5~ms time resolution of the VLA data (except maybe 57633.68, brightest burst).
 
@@
 
-We fit a Gaussian model to each burst to estimate their characteristic width and peak flux... As shown in Table \ref{tab:spec}, the typical frequency scale is xx MHz...
+The burst spectra are generally characterized by a broad, Gaussian shape that with strong modulation between channels.
+We fit a Gaussian shape to each burst to estimate their characteristic width and peak flux, as summarized in Table \ref{tab:spec}.
+The channel-scale modulation is as high as 100\% (see \S \ref{sec:auto}) and is consistent with an exponential distribution.
+While this introduces a strong bias to the best-fit Gaussian, the typical burst spectral width has a characteristic width of 500~MHz.
+
+All but two of the best-fit Gaussians are centered inside the 3~GHz band and most are fully contained by the 1~GHz wide band.
+This is consistent with previous detections of \frb by Arecibo, which showed quasi-broadband structure \citep{2016arXiv160308880S} and large variation in the implied spectral index \citep{2014ApJ...790..101S}.
+A detailed discussion of \frb\ burst spectra is presented in (CITE: WEIRD).
 
 \subsubsection{Spectral Autocorrelation}
-The spectral autocorrelation is used to infer both intrinsic and scintillation properties \citep{}.
-Figure \ref{fig:acf} shows the spectral autocorrellation for the MJD 57633.68 burst.
-Some marginal evidence of spectral correlation on the scale of the channel resolution (4~MHz)?
+\label{sec:auto}
+Autocorrelation of the burst signal (both temporal and spectral) can be used to infer both intrinsic properties and modulation due to scintillation (CITE: Cordes et al?).
+The VLA data have a channel resolution of 4~MHz, which is relatively coarse compared to single-dish data (e.g., CITE: WEIRD).
+However, diffractive scintillation observed for other FRBs \citep{} {\color{red}could/could not (Jim?)} induce structure on this scale near 3~GHz.
+
+Figure \ref{fig:acf} shows the spectral autocorrellation for the strongest burst (MJD 57633.68). (Marginal evidence of spectral correlation on the scale of 4~MHz) {\color{red} Comment, Jim?}
 
@@
 \includegraphics[width=0.9\columnwidth]{acf_57633_scan7}
-\caption{
+\caption{The spectral autocorrelation for the burst from \frb\ at MJD 57633.68.
+Blue shows the autocorrelation for the burst and green shows an autocorrelation of a representative spectrum with no burst.
 \label{fig:acf}}
@@
 
+\subsection{Temporal Statistics}
+Periodicity search...
+Figure \ref{fig:ls} shows a Lomb-Scargle periodogram...
+Lots of excess power corresponding to periods shorter than 1 hour...
+Assuming periods with power peaks, we find clusters of bursts with same rotational phase...
+Possible that we are seeing an underlying period with a very wide pulse phase window...
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=0.9\columnwidth]{lombscargle}
+\caption{Lomb-Scargle periodogram with 95\% limit on power from last observing campaign
+\label{fig:ls}}
+\end{center}
+\end{figure}
+
+Burst detections were made very inhomogenously through the roughly 63 hours of observing toward FRB 121102.
+In the first 30 hours of observing at S-band no bursts were detected, while nine bursts were detected in the last 27 hours of S-band observing.
+The data quality is high and RFI did not significantly impact sensitivity, so the inhomogeneous burst distribution is not an observational artifact, but rather an indication of a non-stationary burst detection probability.
+Assuming that the burst detection probability follows a Poisson distribution, the nondetection in the first half of S-band limits the FRB rate to $\rm{R}<0.1$ hour$^{-1}$ (95\% confidence limit).
+The mean detection rate for the last part of the campaign was $\rm{R}=0.3$ hour$^{-1}$.
+
+Moreover, there is weak evidence that the \frb\ burst rate changes during the last part of the campaign.
+We modeled the event detection probability as a Poisson probability with a rate parameter that scales linearly with time (relative to first burst detection) as $\lambda = a + b * (\rm{MJD} - 57623)$.
+We then calculated the probability of measuring the observed event rate as $\prod_{i} P_i(R)$.
+Figure \ref{fig:rate} shows the ($a$, $b$) parameter space with contours of 50, 90, and 95\% confidence contours.
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=0.9\columnwidth]{event_rate_contours}
+\caption{Rate versus rate change during last campaign.
+\label{fig:rate}}
+\end{center}
+\end{figure}
+
 \subsection{Brightness Distribution}
-The bursts seen by the VLA range in significance from 10 to 150$\sigma$. Table \ref{tab:spec} shows the estimated burst luminosity from spectral modeling...
+Table \ref{tab:spec} shows burst luminosities...
+The significance of the nine bursts span more than an order of magnitude (12 to 179$\sigma$). This highlights the fact that the bursts have a relatively flat luminosity distribution.
 
@@
 Compare luminosity distribution to flux distribution measured by \citep{2016ApJ...830...75V}...
-
-\subsection{Temporal Statistics}
-Burst detections were made very inhomogenously though the roughly 63 hours of observing toward FRB 121102.
-Data quality are relatively high and RFI did not significantly impact sensitivity, so the inhomogeneous burst distribution not an observational artifact.
-
-In the first $\sim25$\ hours observing at S-band no bursts were detected, while nine bursts were detected in the last $\sim30$ hours of S-band observing.
-Assuming the burst detection probability follows a stationary Poisson distribution, the nondetection in the first half of S-band limits the FRB rate to $\rm{R}<0.12$ hour$^{-1}$.
-The mean detection rate for the last part of the campaign was $\rm{R}=0.3$ hour$^{-1}$.
-The inconsistency shows that the detection probability is not stationary.
-
-Moreover, there is weak evidence that the \frb\ burst rate changes during the last part of the campaign.
-We modeled the event detection probability as a Poisson probability with a rate parameter that scales linearly with time as $R=a + b*(\rm{MJD} - 57623)$.
-We then calculated the probability of measuring the observed event rate as $\Pi P_i(R)$.
-Figure \ref{fig:rate} shows the ($a$, $b$) parameter space with contours of 50, 90, and 95\% confidence contours.
-
-\begin{figure}[htb]
-\begin{center}
-\includegraphics[width=0.9\columnwidth]{event_rate_contours}
-\caption{Rate versus rate change during last campaign.
-\label{fig:rate}}
-\end{center}
-\end{figure}
-
-Figure \ref{fig:ls} shows a Lomb-Scargle periodogram...
-Lots of excess power corresponding to periods shorter than 1 hour.
-
-\begin{figure}[htb]
-\begin{center}
-\includegraphics[width=0.9\columnwidth]{lombscargle}
-\caption{Lomb-Scargle periodogram with 95\% limit on power from last observing campaign
-\label{fig:ls}}
-\end{center}
-\end{figure}
 

### 2016-11-28 repeater-vladata.tex
worked in new lum disn figure. luminosities in table. added more red text to get input

@@
 
-This paper is part of a series that presents the first localization and host identification of an FRB (CITE: LOC, OPT, EVN, RADIO CPART, XRAY, EFF, WEIRD).
+This paper is part of a series that presents the first localization and unambiguous identification of an FRB host (CITE: LOC, OPT, EVN, RADIO CPART, XRAY, EFF, WEIRD).
 \frb, also known as the ``repeating FRB'', was first detected in November 2012 by the Arecibo Observatory \citep{2014ApJ...790..101S}.
@@
 Its lookback and luminosity distances are 746 and 972 Mpc \citep{planck15}, which are orders of magnitude larger than any other millisecond transient.
-This shows that FRBs:
-\begin{itemize}
- \item are extremely luminous, 
- \item have a significant DM contribution from the IGM, and
- \item can be used to probe the IGM and their host galaxy.
-\end{itemize}
+This shows that FRBs are more luminous than any other millisecond radio transient, have a significant DM contribution from the IGM, and can be used to probe the IGM and their host galaxy.
 The promise implied by the first reported FRB \citep{2007Sci...318..777L} is now being realized.
 
-The cosmological distance for \frb\ could have wide-ranging implications for the FRB population as a whole.
+The confirmation of a cosmological distance for \frb\ could have wide-ranging implications for the FRB population as a whole.
 However, it has not been demonstrated that \frb\ is representative of the overall FRB population.
@@
 
-Given that FRBs are now known to be useful probes of the IGM, there is strong justification for continuing searches for new detections and localizations.
+Given that FRBs are now known to be useful probes of the IGM, there is even more motivation to make new detections and localizations.
 The relatively faint counterpart to \frb\ argues that direct localization of the radio burst will continue to be the best way to find optical hosts to measure distances.
-Our multi-telescope constraints on burst spectra, measurement of host properties, burst rate estimates, and other properties will inform new strategies for finding FRBs...
+Our multi-telescope constraints on burst spectra, measurement of host properties, burst rate estimates, and other properties will inform new strategies for finding FRBs.
 
@@
 \includegraphics[width=2\columnwidth]{timeline}
-\caption{Summary of observing coverage and detections of \frb\ during the multi-telescope observing campaign.
-Symbols show days with observations and symbols with circles show detections of \frb.
+\caption{Summary of observing coverage and detections of \frb\ during the multi-telescope observing campaign in August and September 2016.
+Symbols show days with observations and circles highlight observations that detected bursts from \frb.
 Multiple circles indicate multiple burst detections, except for Arecibo, which typically has multiple detections per observing session (a detailed analysis is left for a future paper).
@@
 
-% copied from the first paper
+(copied from the first paper) 
 During the joint Arecibo-VLA campaign, Arecibo observed with the L-wide receiver, which has an observational frequency range of 1.15 to 1.73~GHz and a full width at half maximum beam size of 3.3 arcmin.
@@
 
-% copied from Laura's paper
+(copied from Laura's paper)
 Observations were conducted at an observing frequency of 4.6 to 5.1~GHz.
@@
 Figure \ref{fig:sgram} shows the spectrograms of all nine bursts detected by the VLA.
-We improved on the initial analysis presented in (CITE: LOC) by using a better calibration scheme and optimizing the image SNR over a fine DM grid.
+We improved on the initial analysis presented in (CITE: LOC) by using a better calibration scheme and optimizing the detection signifnance by optimizing over a range of DM.
 Table \ref{tab:spec} shows the improved burst parameters using this new scheme.
@@
 Date     & S$_{\rm{int}}$ & Image SNR & L$_{\rm{int}}$ & DM$_{\rm{opt}}$ & S$_{\rm{peak}}$ & Center & FWHM \\
-(MJD)    & (mJy) &  & (ergs?) & (pc cm$^{-3})$ & (mJy?) & (GHz) & (MHz) \\ \hline
-57623    & 258 & 38 & & 561 & 0.41             & 2.8 & 300 \\
-57633.68 & 2000 & 179 & & 554 & 1.90           & 3.2 & 520 \\
-57633.70 & 105 & 15 & & 559 & $>$0.188          & $<$2.5 & $>$350 \\
-57638    & 65  & 12 & & 556 & 0.07             & 3.1 & 410 \\
-57643    & 375 & 100 & & 560 & 0.39            & 2.8 & 520 \\
-57645    & 38  & 13 & & 572 & 0.06             & 2.8 & 210 \\
-57646    & 69  & 20 & & 555 & $>$0.16          & $<$2.5 & $>$400 \\
-57648\tablenotemark{a}    & 97 & 25 & & 559 & 0.11 & 2.9 & 420 \\
-57649    & 110 & 36 & & 552 & 0.07             & 2.9 & 880 \\ \hline
+(MJD)    & (mJy) &  & ($10^{39}$\ erg) & (pc cm$^{-3})$ & (mJy?) & (GHz) & (MHz) \\ \hline
+57623    & 258 & 38 & 1.5 & 561 & 0.41             & 2.8 & 300 \\
+57633.68 & 2000 & 179 & 12 & 554 & 1.90           & 3.2 & 520 \\
+57633.70\tablenotemark{a} & 105 & 15 & 0.6 & 559 & $>$0.188          & $<$2.5 & $>$350 \\
+57638    & 65  & 12 & 0.4 & 556 & 0.07             & 3.1 & 410 \\
+57643    & 375 & 100 & 2.1 & 560 & 0.39            & 2.8 & 520 \\
+57645    & 38  & 13 & 0.2 & 572 & 0.06             & 2.8 & 210 \\
+57646\tablenotemark{a}    & 69  & 20 & 0.4 & 555 & $>$0.16          & $<$2.5 & $>$400 \\
+57648\tablenotemark{b}    & 97 & 25 & 0.6 & 559 & 0.11 & 2.9 & 420 \\
+57649    & 110 & 36 & 0.6 & 552 & 0.07             & 2.9 & 880 \\ \hline
 \end{tabular}
-\tablenotetext{a}{Detected simultaneously with Arecibo between 1.15 and 1.73~GHz.}
+\tablenotetext{a}{Best-fit Gaussian is not centered in 3~GHz band, so spectral parameters are limits.}
+\tablenotetext{b}{Detected simultaneously with Arecibo between 1.15 and 1.73~GHz.}
 \label{tab:spec}
@@
 The uncertainty in the peak DM measurement is defined by the DM sensitivity loss curve and the significance of the burst.
-We tested this model by simulating a burst with SNR$=30$ and measuring its detection significance as a function of DM.
+We tested the precision of the peak DM measuremet by simulating a burst with SNR$=30$ and measuring its detection significance as a function of DM.
 The simulation parameters were reproduced at the known DM with a precision of roughly 1 pc cm$^{-3}$.
@@
 
-\begin{figure*}[h!]
+\begin{figure*}[ht]
 \begin{center}
@@
 The channel-scale modulation is as high as 100\% (see \S \ref{sec:auto}) and is consistent with an exponential distribution.
-While this introduces a strong bias to the best-fit Gaussian, the typical burst spectral width has a characteristic width of 500~MHz.
+This introduces a strong bias to the best-fit Gaussian, but the models are reliable enough to show that the typical burst has a spectral width of 500~MHz.
 
@@
 \subsubsection{Circular Polarization}
-The VLA S-band recievers natively measure circular polarization, although observations did not include polarization calibration procedures.
+The VLA S-band recievers natively measure circular polarization, although for observing efficiency we chose not include polarization calibration procedures.
 Crude constraints on circular polarization are possible by comparing the burst intensity in right and left-hand polarized data products.
@@
 \subsection{Temporal Statistics}
-Periodicity search...
-Figure \ref{fig:ls} shows a Lomb-Scargle periodogram...
-Lots of excess power corresponding to periods shorter than 1 hour...
+The VLA detected nine bursts during the month-long campaign in August--September 2016.
+The typical observation lasted about two hours and was sampled with a 5~ms cadence, so we used the Lomb-Scargle periodogram \citep{} to search for periodic structure over a wide range of timescales.
+The input "lightcurve" was mde as a one-dimensional array for all times with observations; times with a detection are set to 1 and other times are set to 0 \citep[see also]{2011MNRAS.417.1871P}.
+The lightcurve time resolution was set to {\color{red} 100~ms (check)} to keep the computation manageable.
+The 95\% confidence upper limit on periodic power is estimated by randomly selecting the 9 burst times from the same observing times.
+The limit is set as the 95\% highest point at each period (5th highest value in 100 simulations).
+
+Figure \ref{fig:ls} shows the Lomb-Scargle periodogram for the bursts for periods from **xx to xx** s.
+No significant excess power is seen at long periods, but the periodogram shows a steady increase in power at shorter periods.
+The periodogram exceeds the 95\% power limit for periods from xx to xx s (**limited by binning time?**).
+This is consistent with the idea that the bursts imperfectly trace an underlying rotational period, as has been observed from many classes of neutron star.
+Examples include magnetars, which typically have wide pulse phase windows \citep{}, pulsars with glitches that change their periods \citep{}, and {\color{red} Maura?
+also refs for previous points would be welcome}.
+However, we can show with simulations that nine bursts drawn from a simple rotational would produce a strong, narrow peak in \ref{fig:ls}.
+
 Assuming periods with power peaks, we find clusters of bursts with same rotational phase...
-Possible that we are seeing an underlying period with a very wide pulse phase window...
 
@@
 \includegraphics[width=0.9\columnwidth]{lombscargle}
-\caption{Lomb-Scargle periodogram with 95\% limit on power from last observing campaign
+\caption{Dots show the Lomb-Scargle periodogram of burst arrival times for \frb.
+The solid line show the 95\% confidence upper limit on the power expected from bursts with random arrival times.
+(**New version being compiled**)
 \label{fig:ls}}
@@
 
-Burst detections were made very inhomogenously through the roughly 63 hours of observing toward FRB 121102.
+Burst detections were made very inhomogenously through the larger (63 hours) observing campaign of FRB 121102.
 In the first 30 hours of observing at S-band no bursts were detected, while nine bursts were detected in the last 27 hours of S-band observing.
-The data quality is high and RFI did not significantly impact sensitivity, so the inhomogeneous burst distribution is not an observational artifact, but rather an indication of a non-stationary burst detection probability.
+The data quality is high and RFI did not significantly impact sensitivity, so the inhomogeneous burst distribution shows that the burst detection probability was not stationary.
 Assuming that the burst detection probability follows a Poisson distribution, the nondetection in the first half of S-band limits the FRB rate to $\rm{R}<0.1$ hour$^{-1}$ (95\% confidence limit).
@@
 Moreover, there is weak evidence that the \frb\ burst rate changes during the last part of the campaign.
-We modeled the event detection probability as a Poisson probability with a rate parameter that scales linearly with time (relative to first burst detection) as $\lambda = a + b * (\rm{MJD} - 57623)$.
-We then calculated the probability of measuring the observed event rate as $\prod_{i} P_i(R)$.
-Figure \ref{fig:rate} shows the ($a$, $b$) parameter space with contours of 50, 90, and 95\% confidence contours.
+We modeled the event detection probability as a Poisson probability with a rate parameter that evolves linearly with time relative to first burst detection.
+We directly sampled the model by calculating the joint probability $\prod_{i} P_i$, where $P_i$ follows a Poisson probability with rate $\lambda = a + b * (\rm{MJD}_i - 57623)$.
+Figure \ref{fig:rate} shows that the probability distribution excludes a constant rate with $\sim$85\% confidence.
+This weak constraint is consistent with the broader trend seen by the VLA and Arecibo (CITE: WEIRD?).
 
@@
 \includegraphics[width=0.9\columnwidth]{event_rate_contours}
-\caption{Rate versus rate change during last campaign.
+\caption{Color scale and contours show the relative probability for a time-evolving Poisson detection probability for \frb.
+Contours show the 50, 90, and 95\% confidence contours on the rate $a$\ (bursts s$^{-1}$) and rate change $b$\ (bursts s$^{-1}$ day$^{-1}$) during the August--September 2016 campaign in which bursts were detected.
 \label{fig:rate}}
@@
 \subsection{Brightness Distribution}
-Table \ref{tab:spec} shows burst luminosities...
-The significance of the nine bursts span more than an order of magnitude (12 to 179$\sigma$). This highlights the fact that the bursts have a relatively flat luminosity distribution.
+Knowing the burst distance, we calculate their mean luminosity across a single 5~ms integration and the 1~GHz bandwidth (Table \ref{tab:spec}).
+The VLA has also shown for the first time that most bursts are contained within the 3~GHz band.
+That means that the mean S-band flux density can be converted to a luminosity in units of ergs with no assumptions about its spectral properties.
 
-Figure \ref{fig:logns} shows the flux distribution of the nine VLA bursts. Quantify flatness...
+With a uniform sample of burst luminosities, we can use their distribution to infer more general properties for \frb.
+Figure \ref{fig:lumd} shows the luminosity distribution of the VLA bursts with a best-fit powerlaw model.
+Fitting a powerlaw model to the cumulative luminosity distribution gives an index of --0.5.
+The flatness of the distribution is also clear from range of significance of the nine bursts (12 to 179$\sigma$).
+All bursts are much brighter than the sensitivity limit (weakest is $\sim10\sigma$), so the distribution is not affected by a completeness limit.
 
@@
 \begin{center}
-\includegraphics[width=0.9\columnwidth]{logns}
-\caption{Log N -- Log SNR distribution of real-time detections of FRB 121102. **Update to luminosity distribution**
-\label{fig:logns}}
+\includegraphics[width=0.9\columnwidth]{luminosity_disn}
+\caption{Cumulative luminosity distribution and best-fit powerlaw model for the nine VLA bursts from \frb.
+\label{fig:lumd}}
 \end{center}
 \end{figure}
-
-Compare luminosity distribution to flux distribution measured by \citep{2016ApJ...830...75V}...
 
@@
 Discuss comparison FRB 121102 luminosity distribution to that of FRB population...
+
 Imagine physical log N/log S with cut-offs and scattering can bias the intrinsic into the observed distribution (Macquart and Johnston)...
+
+Simulate cosmic volume uniformly filled with \frb...
 

### 2016-11-29 repeater-vladata.tex
added kunal text

@@
 
-{\color{red} Kunal to provide description of AMI-LA}
+We observed FRB121102 with the Arcminute MicroKelvin Imager Large Array (AMI-LA; Zwart et al.
+2008) for 3 hours each on four epochs starting MJDs 57643.3351, 57645.3317, 57648.3352, 57649.3353.
+Observations were made with the new digital correlator having 4096 channels across a 5 GHz bandwidth between 13--18 GHz with a 1s dump time.
+The phase calibrator, J0518+3306, was observed every 12 minutes for about 1.5 minutes.
+The AMI-LA data were binned to eight 0.625 GHz channels and processed (RFI excision and calibration) with a fully-automated pipeline, AMI-REDUCE (e.g.
+Davies et al.
+2009; Perrott et al.
+2013).
+Daily measurements of 3C48 and 3C286 were used for the absolute flux calibration, which is good to about 10\%.
 
-Six AMI-LA observations had some simultaneous coverage with the VLA, of which four covered VLA bursts.
-The upper limit on burst flux density limits any significant "afterglow".
-Deep image sensitivity is limited by confusion and is approximately equal to the flux density observed by VLA (CITE: RADIO CPART).
-{\color{red} Details from Kunal}
+**find a place for this elsewhere**
+We inspected the calibrated visibilities, and did not find any signal above 20 mJy in the 1s samples at and in the vicinity of the detected bursts (MJDs 57643.45730263, 57645.42958602, 57648.4369149, and 57649.45175697 **add two more with VLA coverage**).
+Concatenating and imaging the 12 hours of calibrated data with the CASA tasks {\it concat} and {\it clean} also does not yield any significant detection at the FRB location.
+Although the statistical 3sigma upper limit is 60 uJy, extended mJy-level sources in the field cause sidelobe confusion (the AMI-LA angular resolution is $\sim$30 arcsec), and the actual upper limit is larger.
+We introduced artificial point sources at the FRB location using the CASA {\it sm} tool, and found that these sources can be recovered as long as their peak flux densities are more than $\sim$100 uJy.
+Hence, we place an upper limit of 100$\pm$10 uJy on any quiescent or possible radio "afterglow" (on $\sim$days timescale) signal from the FRB.
+
+Deep image sensitivity is limited by confusion and is approximately equal to the flux density observed by VLA (CITE: RADIO CPAR
 

### 2016-12-10 repeater-vladata.tex
adding notes on naming, simulations.

@@
 
+\frb\ is detectable with the VLA out to $z=0.7$ and much farther with Arecibo...
+
 Discuss comparison FRB 121102 luminosity distribution to that of FRB population...
@@
 
-Simulate cosmic volume uniformly filled with \frb...
+Simulate cosmic volume uniformly filled with \frb... Also once done with a theoretical model based on young pulsars \citep{2016MNRAS.462..941L}
+
+Scaling up assumes that this source is representative.
+Propagation effects may amplify or alter burst brightness statistical properties.
+Some such effects are possible near the burst source (e.g., Jim's caustic analysis), which would effectively be intrinsid in this context.
 
@@
 Given that bursts have $<1$~GHz-scale spectra, wide bandwidths improve odds of detection.
+
+\subsection{Naming Convention}
+
+The cosmological distance for \frb\ and consistency with the overall population suggests that most FRBs repeat.
+The current naming convention for FRBs is analogous to supernovae, with six numbers defining the year, month, and day of detection.
+If all FRBs repeat, then this naming convention is only useful for identifying its discovery.
+A more useful convention would be the more common one that uses the coordinates.
+But there are already two FRBs that have consistent celestial positions and different DMs.
+
+We suggest a convention of referring to FRBs as Jhhmm+dd or appending DM...
 

### 2016-12-17 repeater-vladata.tex
added dm confidence interval figure. working on non-lambda2 fits

@@
 
-\title{\frb: Multi-Telescope Burst Properties and Implications for FRB Population}
-\shorttitle{\frb\ Burst Properties}
+\title{The \frb Observing Campaign: Multi-Telescope Radio Burst and Implications for the FRB Population}
+%\title{Multi-Telescope Burst Properties and Implications for FRB Population}
+\shorttitle{\frb\ Observing Campaign}
 \shortauthors{Law et al.}
@@
 
-This paper is part of a series that presents the first localization and unambiguous identification of an FRB host (CITE: LOC, OPT, EVN, RADIO CPART, XRAY, EFF, WEIRD).
+This paper is part of a series that presents the first localization and unambiguous identification of an FRB host (CITE: LOC, OPT, EVN).
 \frb, also known as the ``repeating FRB'', was first detected in November 2012 by the Arecibo Observatory \citep{2014ApJ...790..101S}.
@@
 
-\frb\ has now been localized three orders of magnitude better than any other FRB and placed at a cosmological distance.
+\frb\ has now been localized four orders of magnitude better than any other FRB and placed at a cosmological distance.
 Its lookback and luminosity distances are 746 and 972 Mpc \citep{planck15}, which are orders of magnitude larger than any other millisecond transient.
@@
 We coordinated observing between the VLA, Arecibo, Effelsberg, and AMI-LA telescopes, as shown in figure \ref{fig:multi}.
-Below, we summarize these observations, with a focus on those conducted simultaneous with VLA burst detections from \frb.
+Below, we summarize these observations, with a focus on those conducted simultaneously with VLA burst detections from \frb.
 
@@
 In this last campaign, the first 34 hours of VLA observations were made at 3~GHz, while the last 6 hours were observed at 6~GHz.
-This paper focuses on the data collected at 3~GHz, which includes all burst detections.
+This paper focuses on the data collected at 3~GHz, which includes all nine burst detections.
 
@@
 The total bandwidth at L (1.4~GHz), S (3~GHz), and C (6~GHz) bands was 256~MHz, 1024~MHz, and 2048~MHz, respectively.
-The 3~GHz data recorded data in 8 spectral windows with 32 channels each.
+The 3~GHz data were recorded data in 8 spectral windows with 32 channels each.
 
@@
 The current, prototype runs on existing, CPU-based hardware of the VLA correlator backend, while the future \rf\ will run on a dedicated GPU cluster.
-The transient search pipeline software is called \emph{rtpipe}\footnote{See \url{https://github.com/caseyjlaw/rtpipe}} and is mostly written in Python.
-The transient search pipeline is described in \citet{2015ApJ...807...16L} and performs data calibration, flagging, dedispersion, and imaging.
+The transient search pipeline software is called \emph{rtpipe}\footnote{See \url{https://github.com/caseyjlaw/rtpipe}} and is mostly written in Python (detail in \citet{2015ApJ...807...16L}).
 Images were formed for each integration at DMs of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$.
@@
 The transient search starts when data are recorded, but this prototype of \rf\ is a factor of several times slower than real-time, so we refer to the detection as "quasi real-time".
-Each image with a pixel higher than 6.4$\sigma$ has some rudimentary data saved to capture both real and thermal-noise candidates as a check of data quality.
-For each image with a pixel higher than 7.4$\sigma$, \rf\ generates a candidate visualization with an image and spectrum.
+Each image with a pixel higher than 6.4$\sigma$ is saved in a summary form as a check of data quality.
+For each image with a pixel higher than 7.4$\sigma$, \rf\ generates a more detailed candidate visualization with an image and spectrum.
 More detailed analysis, including improved calibration and localization, is conducted offline.
@@
 
-(copied from the first paper) 
+{\color{red} copied from the first paper}
 During the joint Arecibo-VLA campaign, Arecibo observed with the L-wide receiver, which has an observational frequency range of 1.15 to 1.73~GHz and a full width at half maximum beam size of 3.3 arcmin.
@@
 No detection was made in that Arecibo data.
-Overall, there were many more bursts detected at Arecibo and a more detailed analysis will be presented in a future paper.
+Overall, there were many more bursts detected at Arecibo than with the VLA and a more detailed analysis of those bursts will be presented in a future paper.
 
@@
 
-(copied from Laura's paper)
+{\color{red} copied from Laura's paper}
 Observations were conducted at an observing frequency of 4.6 to 5.1~GHz.
@@
 
-We observed FRB121102 with the Arcminute MicroKelvin Imager Large Array (AMI-LA; Zwart et al.
-2008) for 3 hours each on four epochs starting MJDs 57643.3351, 57645.3317, 57648.3352, 57649.3353.
+We observed \frb with the Arcminute MicroKelvin Imager Large Array (AMI-LA; Zwart et al.
+2008) for 3 hours each on four epochs starting at MJDs 57643.3351, 57645.3317, 57648.3352, and 57649.3353.
 Observations were made with the new digital correlator having 4096 channels across a 5 GHz bandwidth between 13--18 GHz with a 1s dump time.
 The phase calibrator, J0518+3306, was observed every 12 minutes for about 1.5 minutes.
-The AMI-LA data were binned to eight 0.625 GHz channels and processed (RFI excision and calibration) with a fully-automated pipeline, AMI-REDUCE (e.g.
-Davies et al.
-2009; Perrott et al.
-2013).
+The AMI-LA data were binned to eight 0.625 GHz channels and processed (RFI excision and calibration) with a fully-automated pipeline, AMI-REDUCE \citep[e.g.,][]{2013MNRAS.429.3330P}.
 Daily measurements of 3C48 and 3C286 were used for the absolute flux calibration, which is good to about 10\%.
 
-**find a place for this elsewhere**
-We inspected the calibrated visibilities, and did not find any signal above 20 mJy in the 1s samples at and in the vicinity of the detected bursts (MJDs 57643.45730263, 57645.42958602, 57648.4369149, and 57649.45175697 **add two more with VLA coverage**).
+We inspected the calibrated visibilities, and did not find any signal above 20 mJy in the 1s samples at and in the vicinity of the detected bursts.
 Concatenating and imaging the 12 hours of calibrated data with the CASA tasks {\it concat} and {\it clean} also does not yield any significant detection at the FRB location.
@@
 Hence, we place an upper limit of 100$\pm$10 uJy on any quiescent or possible radio "afterglow" (on $\sim$days timescale) signal from the FRB.
-
-Deep image sensitivity is limited by confusion and is approximately equal to the flux density observed by VLA (CITE: RADIO CPAR
+This limit is close to the flux density measured by the VLA (CITE: LOC)
 
@@
 \subsection{Multi-Telescope Burst Spectrum}
-Of the four VLA burst detections from \frb with simultaneous observations \frb (Figure \ref{fig:multi}), one was detected with a consistent dedispersed time.
-The VLA burst on 57648 was detected at Arecibo with a significance of {\color{red} xx$\sigma$ (Jason)} The relative time delay between the VLA and Arecibo is {\color{red} xx (Jason)} ms...
+Four of the VLA bursts were observed simultaneously with Arecibo and AMI-LA (Figure \ref{fig:multi}).
+Of these, the burst on 57648 was detected by Arecibo at the same time (after correcting for the known DM of \frb).
+The Arecibo detection of this burst had a significance of {\color{red} xx$\sigma$ (Jason)}.
 
-Figure **to do** shows the dynamic spectrum formed from the phased VLA and Arecibo data... 
+Figure {\color{red} **to do**} shows the dynamic spectrum formed from the phased VLA and Arecibo data... **Discuss dispersion correction, time alignment, chance of false association**
+
 This simultaneous detection of a burst from roughly 1 to 4~GHz shows that some bursts cover more than an octave of frequency.
-This is one of three bursts with similar spectral coverage at Arecibo, so the other nondetections imply that those bursts had a smaller spectral coverage.
-In fact, as described in \S \ref{sec:spec}, most of the VLA bursts appear to be fully contained in the band from 2.5 to 3.5~GHz, which implies a much smaller spectral coverage for typical bursts.
-
-**Insert figure of VLA/AO dynamic spectrum on 57648**
+However, this is one of three VLA bursts with coverage by Arecibo, so the other nondetections imply that those bursts had a smaller spectral width.
+In fact, as described in \S \ref{sec:spec}, many of the VLA bursts appear to be fully contained in the band from 2.5 to 3.5~GHz, which implies a much smaller spectral coverage for typical bursts.
 
@@
 
- \caption{Spectrograms (time vs frequency intensity maps) for the nine VLA bursts.
-Starting at the top left, the correspond to bursts 57623, 57633.68, 57633.70, 57638, 57643, 57645, 57646, 57648, and 57649.
+ \caption{Dynamic spectra (time vs frequency intensity maps) for the nine VLA bursts.
+Starting at the top left, they correspond to bursts 57623, 57633.68, 57633.70, 57638, 57643, 57645, 57646, 57648, and 57649.
 Note that bursts are detected in 5~ms images generated from dedispersed visibilities.
@@
 \label{sec:spec}
-Figure \ref{fig:sgram} shows the spectrograms of all nine bursts detected by the VLA.
-We improved on the initial analysis presented in (CITE: LOC) by using a better calibration scheme and optimizing the detection signifnance by optimizing over a range of DM.
+Figure \ref{fig:sgram} shows the dynamic spectra of all nine bursts detected by the VLA.
+We improved on the initial analysis presented in (CITE: LOC) by using a better calibration scheme and optimizing the detection signifnance over a range of DM.
 Table \ref{tab:spec} shows the improved burst parameters using this new scheme.
@@
 We refined that analysis by maximizing the image SNR for DMs spaced by 1 pc cm$^{-3}$.
-The optimal DM values range from 552 to 572 pc cm$^{-3}$ for all bursts and from 552 to 561 pc cm$^{-3}$ for bursts with SNR$>30$.
+The optimal DM values range from 552 to 572 pc cm$^{-3}$.
 
 The uncertainty in the peak DM measurement is defined by the DM sensitivity loss curve and the significance of the burst.
-We tested the precision of the peak DM measuremet by simulating a burst with SNR$=30$ and measuring its detection significance as a function of DM.
-The simulation parameters were reproduced at the known DM with a precision of roughly 1 pc cm$^{-3}$.
-This suggests that the measured variation in DM for \frb is intrinsic to the bursts, rather than due to measurement uncertainty.
-This is consistent with the observation of intrinsic burst spectrotemporal structure that varies between bursts (CITE: WEIRD).
+We estimate the DM likelihood distribution for each burst by using a generative model for the burst spectra \citep{2010arXiv1008.4686H}.
+The burst spectra as a function of frequency were fixed according to the broad Gaussian shape defined below (\S \ref{sec:specmod}) and made into dynamic spectra by applying a frequency-dependent delay.
+We assume a Gaussian error distribution for channels with low signal and error up to 100\% of the model amplitude for channels with high signal.
+This is consistent with the large channel-to-channel variations observed (potentially due to diffractive scintillation).
+
+Figure \ref{fig:dmmodel} compares the 68\% ($1\sigma$) bounds on the DM for all nine VLA bursts.
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=0.9\columnwidth]{dmmodel}
+\caption{Comparison of 68\% ($\1sigma$) confidence intervals for DM for nine bursts detected by the VLA.
+\label{fig:dmmodel}}
+\end{center}
+\end{figure}
 
 \subsubsection{Spectral modeling}
+\label{sec:specmod}
 After finding an optimal burst DM, we extract a spectrum from the integration with peak SNR (Figure \ref{fig:spec}).

### 2016-12-18 repeater-vladata.tex
restructured. added rate stuff bumped from gemini paper

@@
 
-\subsubsection{Dynamic Spectra}
+\subsubsection{Spectra}
 \label{sec:spec}
 Figure \ref{fig:sgram} shows the dynamic spectra of all nine bursts detected by the VLA.
-We improved on the initial analysis presented in (CITE: LOC) by using a better calibration scheme and optimizing the detection signifnance over a range of DM.
+We improved on the initial analysis presented in (CITE: LOC) by using a better calibration scheme and optimizing the detection significance over a find grid of DM ($\Delta DM=1$ \rm{pc} \rm{cm}^{-3}$).
 Table \ref{tab:spec} shows the improved burst parameters using this new scheme.
@@
 
-\subsubsection{Dispersion Meausres}
-The initial VLA detections were made by searching a DM grid that allowed inter-DM sensitivity losses up to roughly 10\%.
-For the VLA 3~GHz observing band, we estimated that trials could be separated by at most 10 pc cm$^{-3}$ \citep{2003ApJ...596.1142C}.
-We refined that analysis by maximizing the image SNR for DMs spaced by 1 pc cm$^{-3}$.
-The optimal DM values range from 552 to 572 pc cm$^{-3}$.
-
-The uncertainty in the peak DM measurement is defined by the DM sensitivity loss curve and the significance of the burst.
-We estimate the DM likelihood distribution for each burst by using a generative model for the burst spectra \citep{2010arXiv1008.4686H}.
-The burst spectra as a function of frequency were fixed according to the broad Gaussian shape defined below (\S \ref{sec:specmod}) and made into dynamic spectra by applying a frequency-dependent delay.
-We assume a Gaussian error distribution for channels with low signal and error up to 100\% of the model amplitude for channels with high signal.
-This is consistent with the large channel-to-channel variations observed (potentially due to diffractive scintillation).
-
-Figure \ref{fig:dmmodel} compares the 68\% ($1\sigma$) bounds on the DM for all nine VLA bursts.
-
-\begin{figure}[htb]
-\begin{center}
-\includegraphics[width=0.9\columnwidth]{dmmodel}
-\caption{Comparison of 68\% ($\1sigma$) confidence intervals for DM for nine bursts detected by the VLA.
-\label{fig:dmmodel}}
-\end{center}
-\end{figure}
-
-\subsubsection{Spectral modeling}
-\label{sec:specmod}
-After finding an optimal burst DM, we extract a spectrum from the integration with peak SNR (Figure \ref{fig:spec}).
-After DM optimization, all bursts appear unresolved at the 5~ms time resolution of the VLA data (except maybe 57633.68, brightest burst).
+Figure \ref{fig:spec} shows the spectrum of the integration and DM that maximizes the burst detection significance.
+After DM optimization, all bursts appear unresolved at the 5~ms time resolution of the VLA data.
+One possible exception is the brightest burst at 57633.68, for which roughly 10\% of the peak flux density is seen in adjacent 5~ms integrations.
 
@@
 
-The burst spectra are generally characterized by a broad, Gaussian shape that with strong modulation between channels.
+The burst spectra are generally characterized by a broad, Gaussian shape that with strong inter-channel modulation.
 We fit a Gaussian shape to each burst to estimate their characteristic width and peak flux, as summarized in Table \ref{tab:spec}.
 The channel-scale modulation is as high as 100\% (see \S \ref{sec:auto}) and is consistent with an exponential distribution.
-This introduces a strong bias to the best-fit Gaussian, but the models are reliable enough to show that the typical burst has a spectral width of 500~MHz.
+This introduces a strong bias to the best-fit Gaussian, but these simple fits are reliable enough to show that the typical burst has a spectral width of 500~MHz.
 
-All but two of the best-fit Gaussians are centered inside the 3~GHz band and most are fully contained by the 1~GHz wide band.
+All but two of the best-fit Gaussians are centered inside the 3~GHz band and most appear contained by the 1~GHz wide band.
 This is consistent with previous detections of \frb by Arecibo, which showed quasi-broadband structure \citep{2016arXiv160308880S} and large variation in the implied spectral index \citep{2014ApJ...790..101S}.
-A detailed discussion of \frb\ burst spectra is presented in (CITE: WEIRD).
+A detailed discussion of high-resolution \frb\ burst spectra seen by the Arecibo Observatory will be presented elsewhere (CITE: WEIRD).
+
+\subsubsection{Dispersion}
+The initial VLA detections were made by searching a DM grid that allowed inter-DM sensitivity losses up to roughly 10\% \citep[$\Delta DM=10 \rm{pc} \rm{cm}^{-3}$][]{2003ApJ...596.1142C}.
+In optimizing detection significance over a fine DM grid, we find optimal DM values range from 552 to 572 pc cm$^{-3}$.
+However, the uncertainty in the peak DM measurement is defined by the DM sensitivity loss curve and the significance of the burst.
+
+Given that the apparent DM can potentially change due to intrinsic or extrinsic effects, we developed a more sophisticated system for modeling dispersion.
+We created a generative model to sample the likelihood distribution of a class of dispersion models \citep{2010arXiv1008.4686H}.
+Since the goal is to study dispersion rather than spectral structure, we create a model by applying a dispersion delay to the observed spectrum.
+The observed spectrum is calculated from 3 integrations centered at the peak integration to ensure all burst emission is included.
+The likelihood is directly sampled by calculating the product of probabilities on a per-pixel basis with uniform errors that follow a Gaussian error distribution.
+
+Figure \ref{fig:dmmodel} compares the 68\% ($1\sigma$) bounds on the DM for all nine VLA bursts.
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=0.9\columnwidth]{dmmodel}
+\caption{Comparison of 68\% ($\1sigma$) confidence intervals for DM for nine bursts detected by the VLA.
+\label{fig:dmmodel}}
+\end{center}
+\end{figure}
+
+Non-lambda$^{2}$ dispersion...
 
@@
 Autocorrelation of the burst signal (both temporal and spectral) can be used to infer both intrinsic properties and modulation due to scintillation (CITE: Cordes et al?).
-The VLA data have a channel resolution of 4~MHz, which is relatively coarse compared to single-dish data (e.g., CITE: WEIRD).
-However, diffractive scintillation observed for other FRBs \citep{} {\color{red}could/could not (Jim?)} induce structure on this scale near 3~GHz.
+While VLA spectral resolution of 4~MHz is relatively coarse, diffractive scintillation observed for other FRBs \citep{} {\color{red}could/could not (Jim?)} induce structure on this scale near 3~GHz.
 
-Figure \ref{fig:acf} shows the spectral autocorrellation for the strongest burst (MJD 57633.68). (Marginal evidence of spectral correlation on the scale of 4~MHz) {\color{red} Comment, Jim?}
+Figure \ref{fig:acf} shows the spectral autocorrellation for the strongest burst (MJD 57633.68). {\color{red} Comment, Jim?}
 
@@
 The apparent circular polarization fraction ($(RR-LL)/(RR+LL)$) for the most significant bursts are all less than 3\%.
-FRB121102 was located 2.3 arcmin away from pointing center, where systematic effects have been measured as large as 3\% (Perley et al 2016, VLA memo).
-We conclude that the S-band bursts seen by the VLA have a circular polarization of less than 3\%.
+\frb was located 2.3 arcmin away from pointing center, where systematic effects have been measured as large as 3\% (Perley et al 2016, VLA memo).
+Given that systematic effects dominate the apparent circular polarization, we conclude that the true fractional circular polarization is less than 3\%.
 
@@
 
+\subsection{Emission Physics and Burst Energetics}
+**Cut from gemini paper**
+The redshift measurement allows us to put FRB 121102’s energetics on a firmer footing, confirming the energy scale of 1038 erg (δΩ/4π)(Aν/0.1 Jy ms)(∆ν/1 GHz) calculated by Chatterjee et al.
+(2017) using a distance scale of 1 Gpc.
+Here Aν and ∆ν are the fluence and bandwidth, respectively, at observing frequency ν and δΩ is the opening angle of the bursts.
+
+% from first paper
+For a nominal Gpc distance $D$ corresponding to redshifts $z\lesssim 0.3$, the received fluence $A_{\nu}$ from each burst implies  a burst energy
+$$E_{\rm burst} = 4\pi D^2 (\delta\Omega/4\pi) A_{\nu} \Delta\nu
+\approx 10^{38}\, {\rm erg}\,(\delta\Omega/4\pi) D_{\rm Gpc}^2  (A_{\nu} / 0.1\ {\rm Jy\ ms}) \Delta\nu_{\rm GHz}.$$
+The unknown  emission solid angle $\delta\Omega$
+could be very small due to relativistic beaming, and together with a distance possibly much smaller than 1~Gpc, could reduce the energy requirement significantly.
+However, the {\it total} energy emitted could be larger depending on the duration of the emission in the source frame and other model-dependent details.
+Either way, the burst energies from \frb\ are not inconsistent with those that might be expected from the magnetosphere of a compact object\cite{2016MNRAS.457..232C}.
+
 \subsection{Luminosity Distribution}
+
 Doubts were cast on the first FRB detection (``Lorimer burst'') due to its unusually high brightness.
@@
 
-\subsection{Emission Physics and Burst Energetics}
+\subsection{FRB Rate}
+**cut from gemini paper**
+Assuming that FRB 121102 is from the same population as the other FRBs, the measurement of a distance for the host of FRB 121102 allows us to re-evaluate the cosmic volume and event rate per galaxy for the FRB population.
+For an estimated projected FRB rate Rp, comoving volume V (z), and galaxy number density Φ(M), the rate per galaxy is RFRB = Rp/(Φ(M)V (z)), assuming isotropic radiation.
+(**parameterize beaming**)
 
-% from first paper
-For a nominal Gpc distance $D$ corresponding to redshifts $z\lesssim 0.3$, the received fluence $A_{\nu}$ from each burst implies  a burst energy
-$$E_{\rm burst} = 4\pi D^2 (\delta\Omega/4\pi) A_{\nu} \Delta\nu
-\approx 10^{38}\, {\rm erg}\,(\delta\Omega/4\pi) D_{\rm Gpc}^2  (A_{\nu} / 0.1\ {\rm Jy\ ms}) \Delta\nu_{\rm GHz}.$$
-The unknown  emission solid angle $\delta\Omega$
-could be very small due to relativistic beaming, and together with a distance possibly much smaller than 1~Gpc, could reduce the energy requirement significantly.
-However, the {\it total} energy emitted could be larger depending on the duration of the emission in the source frame and other model-dependent details.
-Either way, the burst energies from \frb\ are not inconsistent with those that might be expected from the magnetosphere of a compact object\cite{2016MNRAS.457..232C}.
+The first such rate estimate was made by Thornton et al.
+(2013), who used the measured DM to estimate a characteristic distance for their sample of 4 FRBs.
+They assumed that all of the extragalactic component of the DM was caused by the IGM and scaled as DM ∼ z × 1200 pc cm−3 (Ioka 2003; Inoue 2004).
+They also calculated the number of galaxies by assuming a characteristic L∗ galaxy (corresponding to stellar mass M∗ ≈ 1010.66 M ; Baldry et al.
+2012).
+
+Our calculation differs in that we have better estimates of all three parameters.
+First, the projected FRB rate is now believed to be closer to 2×103 sky−1 day−1 at high Galactic latitudes and flux densities brighter than 1 Jy ms (Lawrence et al.
+2016; Champion et al.
+2016; Rane et al.
+2016).
+FRB 121102 is associated with a relatively small galaxy, which are roughly a factor of 100 more abundant than L∗ galaxies (φ(M) ∼ 10−2 Mpc−3; Faber et al.
+2007).
+Finally, the measured distance for FRB 121102 suggests that roughly half of the extragalactic DM is intrinsic to the host and half is from the IGM.
+
+This reduces the characteristic distance by a factor of two and the volume by an order of magnitude.
+Considering these factors, we assume a characteristic FRB redshift of 0.4 to estimate RFRB ≈ 10−5 galaxy−1 year−1.
+This is lower than previously estimated (RFRB ∼ 10−3 galaxy−1 year−1 , Thornton et al.
+2013).
+
+There are significant caveats to the comparison of this rate to the rates of other classes of transient.
+This isotropic FRB rate assumes a projected FRB rate at a single (observationally defined) flux limit and that no bursts repeat.
+Using this calculation with data from more sensitive telescopes, we might infer a higher rate.
+However, if we assume that FRB 121102 is representative of the overall FRB population, then more sensitive observations would be more likely to find repeating FRBs that would effectively depress the estimate of the underlying isotropic rate per source.
+In this model, these two effects partially cancel, although without a physical model it is difficult to say how well.
+Finally, the bursts are known to be generated by a coherent emission process and does not emit isotropically.
+Assuming beaming angles typical of pulsars (e.g., Tauris & Manchester 1998), we expect a true FRB rate that is higher by a factor of 10.
 

### 2016-12-18 repeater-vladata.tex
working on dm analysis. added coauthor. using citations for new papers

@@
 
+\author{D.~Michilli}
+\affiliation{Anton Pannekoek Institute for Astronomy, University of Amsterdam, Science Park 904, 1098 XH Amsterdam, The Netherlands}
+
 \author{M.~A.~McLaughlin}
@@
 
-This paper is part of a series that presents the first localization and unambiguous identification of an FRB host (CITE: LOC, OPT, EVN).
+This paper is part of a series that presents the first localization and unambiguous identification of an FRB host \citep{LOC, OPT, EVN}.
 \frb, also known as the ``repeating FRB'', was first detected in November 2012 by the Arecibo Observatory \citep{2014ApJ...790..101S}.
 In mid 2015, new Arecibo observations revealed a series of bursts at the same DM and sky position demonstrating that FRBs are capable of repetition \citep{2016Natur.531..202S}.
-Beginning in August of 2015, we made the first of nine detections of \frb\ with the Very Large Array (CITE: LOC) and localized it with a precision of 0.1\arcsec.
-Deep radio and optical observing shows that \frb\ is unambiguously associated with a persistent radio and optical source at a redshift of 0.193 (CITE: OPT, EVN).
+Beginning in August of 2015, we made the first of nine detections of \frb\ with the Very Large Array \citep{LOC} and localized it with a precision of 0.1\arcsec.
+Deep radio and optical observing shows that \frb\ is unambiguously associated with a persistent radio and optical source at a redshift of 0.193 \citep{OPT, EVN}.
 
 \frb\ has now been localized four orders of magnitude better than any other FRB and placed at a cosmological distance.
-Its lookback and luminosity distances are 746 and 972 Mpc \citep{planck15}, which are orders of magnitude larger than any other millisecond transient.
+Its lookback and luminosity distances are 746 and 972 Mpc \citep{2016A&A...594A..13P}, which are orders of magnitude larger than any other millisecond transient.
 This shows that FRBs are more luminous than any other millisecond radio transient, have a significant DM contribution from the IGM, and can be used to probe the IGM and their host galaxy.
@@
 Hence, we place an upper limit of 100$\pm$10 uJy on any quiescent or possible radio "afterglow" (on $\sim$days timescale) signal from the FRB.
-This limit is close to the flux density measured by the VLA (CITE: LOC)
+This limit is close to the flux density measured by the VLA \citep{LOC}.
 
@@
 Figure \ref{fig:sgram} shows the dynamic spectra of all nine bursts detected by the VLA.
-We improved on the initial analysis presented in (CITE: LOC) by using a better calibration scheme and optimizing the detection significance over a find grid of DM ($\Delta DM=1$ \rm{pc} \rm{cm}^{-3}$).
+We improved on the initial analysis presented in \citet{LOC} by using a better calibration scheme and optimizing the detection significance over a find grid of DM ($\Delta DM=1 \rm{pc} \rm{cm}^{-3}$).
 Table \ref{tab:spec} shows the improved burst parameters using this new scheme.
@@
 Date                & S$_{\rm{int}}$  & Image SNR & L$_{\rm{int}}$ & DM$_{\rm{opt}}$ & S$_{\rm{peak}}$  & Center & FWHM \\
-(MJD)    & (mJy) &  & ($10^{39}$\ erg) & (pc cm$^{-3})$ & (mJy?) & (GHz) & (MHz) \\ \hline
-57623    & 258 & 38 & 1.5 & 561 & 0.41             & 2.8 & 300 \\
-57633.68 & 2000 & 179 & 12 & 554 & 1.90           & 3.2 & 520 \\
-57633.70\tablenotemark{a} & 105 & 15 & 0.6 & 559 & $>$0.188          & $<$2.5 & $>$350 \\
-57638    & 65  & 12 & 0.4 & 556 & 0.07             & 3.1 & 410 \\
-57643    & 375 & 100 & 2.1 & 560 & 0.39            & 2.8 & 520 \\
-57645    & 38  & 13 & 0.2 & 572 & 0.06             & 2.8 & 210 \\
-57646\tablenotemark{a}    & 69  & 20 & 0.4 & 555 & $>$0.16          & $<$2.5 & $>$400 \\
-57648\tablenotemark{b}    & 97 & 25 & 0.6 & 559 & 0.11 & 2.9 & 420 \\
-57649    & 110 & 36 & 0.6 & 552 & 0.07             & 2.9 & 880 \\ \hline
+(MJD)               & (mJy)           &           & ($10^{38}$\ erg) & (pc cm$^{-3})$ & (Jy) & (GHz)  & (MHz) \\ \hline
+57623               & 258             & 38        & 15   & 561 & 0.41                                    & 2.8 & 300 \\
+57633.68            & 2000            & 179       & 120  & 554 & 1.90                                    & 3.2 & 520 \\
+57633.70\tablenotemark{a} & 105       & 15        & 6    & 559 & $>$0.188                                & $<$2.5 & $>$350 \\
+57638               & 65              & 12        & 4    & 556 & 0.07                                    & 3.1 & 410 \\
+57643               & 375             & 100       & 21   & 560 & 0.39                                    & 2.8 & 520 \\
+57645               & 38              & 13        & 2    & 572 & 0.06                                    & 2.8 & 210 \\
+57646\tablenotemark{a} & 69           & 20        & 4    & 555 & $>$0.16                                 & $<$2.5 & $>$400 \\
+57648\tablenotemark{b} & 97           & 25        & 6    & 559 & 0.11                                    & 2.9 & 420 \\
+57649               & 110             & 36        & 6    & 552 & 0.07                                    & 2.9 & 880 \\ \hline
 \end{tabular}
@@
 This introduces a strong bias to the best-fit Gaussian, but these simple fits are reliable enough to show that the typical burst has a spectral width of 500~MHz.
+% TODO: fit with generative model with 100% amplitude modulations (emcee?)
 
@@
 This is consistent with previous detections of \frb by Arecibo, which showed quasi-broadband structure \citep{2016arXiv160308880S} and large variation in the implied spectral index \citep{2014ApJ...790..101S}.
-A detailed discussion of high-resolution \frb\ burst spectra seen by the Arecibo Observatory will be presented elsewhere (CITE: WEIRD).
+A detailed discussion of high-resolution \frb\ burst spectra seen by the Arecibo Observatory will be presented elsewhere \citep{WEIRD}.
 
@@
 We created a generative model to sample the likelihood distribution of a class of dispersion models \citep{2010arXiv1008.4686H}.
-Since the goal is to study dispersion rather than spectral structure, we create a model by applying a dispersion delay to the observed spectrum.
-The observed spectrum is calculated from 3 integrations centered at the peak integration to ensure all burst emission is included.
-The likelihood is directly sampled by calculating the product of probabilities on a per-pixel basis with uniform errors that follow a Gaussian error distribution.
+We use the Gaussian shape (see \S \ref{sec:spec}) along the spectral axis and apply a frequency-depndent delay for a given dispersion model.
+The likelihood is directly sampled by calculating the product of probabilities on a per-pixel basis of the 2-dimensional dynamic spectrum.
+Uncertainties in each pixel are drawn from a uniform Gaussian error distribution that is estimated from the data.
 
-Figure \ref{fig:dmmodel} compares the 68\% ($1\sigma$) bounds on the DM for all nine VLA bursts.
+Figure \ref{fig:dmmodel} compares the 95\% confidence intervals on the DM for all nine VLA bursts.
+Some of the confidence intervals do not overlap, which suggests that there are apparent DM changes between bursts.
+This change could be caused by intrinsic burst structure \citep{WEIRD} or actual changes to the DM column density.
+**Preliminary**
 
@@
 \includegraphics[width=0.9\columnwidth]{dmmodel}
-\caption{Comparison of 68\% ($\1sigma$) confidence intervals for DM for nine bursts detected by the VLA.
+\caption{**Preliminary** Comparison of 95\% ($1sigma$) confidence intervals for DM for nine bursts detected by the VLA.
 \label{fig:dmmodel}}
@@
 
-Non-lambda$^{2}$ dispersion...
+% TODO: Non-lambda$^{2}$ dispersion...
 
@@
 Figure \ref{fig:rate} shows that the probability distribution excludes a constant rate with $\sim$85\% confidence.
-This weak constraint is consistent with the broader trend seen by the VLA and Arecibo (CITE: WEIRD?).
+This weak constraint is consistent with the broader trend seen by the VLA and Arecibo \citep{WEIRD}.
 
@@
 **Cut from gemini paper**
-The redshift measurement allows us to put FRB 121102’s energetics on a firmer footing, confirming the energy scale of 1038 erg (δΩ/4π)(Aν/0.1 Jy ms)(∆ν/1 GHz) calculated by Chatterjee et al.
-(2017) using a distance scale of 1 Gpc.
-Here Aν and ∆ν are the fluence and bandwidth, respectively, at observing frequency ν and δΩ is the opening angle of the bursts.
+The redshift measurement allows us to put FRB 121102’s energetics on a firmer footing, confirming \citet{LOC}.
 
@@
 \subsection{FRB Rate}
-**cut from gemini paper**
-Assuming that FRB 121102 is from the same population as the other FRBs, the measurement of a distance for the host of FRB 121102 allows us to re-evaluate the cosmic volume and event rate per galaxy for the FRB population.
-For an estimated projected FRB rate Rp, comoving volume V (z), and galaxy number density Φ(M), the rate per galaxy is RFRB = Rp/(Φ(M)V (z)), assuming isotropic radiation.
-(**parameterize beaming**)
+% cut from gemini paper. TODO: incorporate referee comments on rate scale
+Assuming that \frb is from the same population as the other FRBs, the measurement of a distance for the host of \frb allows us to re-evaluate the cosmic volume and event rate per galaxy for the FRB population.
+The estimated projected FRB rate $R_p$ understates the true rate by a beaming fraction $\Omega_b$ \citep[$\sim$10\%;][]{1998MNRAS.298..625T}..
+For a comoving volume $V(z)$ and galaxy number density $\Phi(M)$, the rate per galaxy is $R_{FRB} = R_p \Omega_b /(\Phi(M)V (z))$.
 
-The first such rate estimate was made by Thornton et al.
-(2013), who used the measured DM to estimate a characteristic distance for their sample of 4 FRBs.
-They assumed that all of the extragalactic component of the DM was caused by the IGM and scaled as DM ∼ z × 1200 pc cm−3 (Ioka 2003; Inoue 2004).
-They also calculated the number of galaxies by assuming a characteristic L∗ galaxy (corresponding to stellar mass M∗ ≈ 1010.66 M ; Baldry et al.
-2012).
+The first such rate estimate was made by \citet{2013Sci...341...53T}, who used the measured DM to estimate a characteristic distance for their sample of 4 FRBs.
+They assumed that all of the extragalactic component of the DM was caused by the IGM and scaled as $DM\approx z\times1200 \rm{pc} \rm{cm}^{-3}$ \citep{2003ApJ...598L..79I,2004MNRAS.348..999I}.
+They also calculated the number of galaxies by assuming a characteristic $L_*$ galaxy \citep[corresponding to stellar mass $M_* \approx 1010.66 M$][]{2012MNRAS.421..621B}.
 
 Our calculation differs in that we have better estimates of all three parameters.
-First, the projected FRB rate is now believed to be closer to 2×103 sky−1 day−1 at high Galactic latitudes and flux densities brighter than 1 Jy ms (Lawrence et al.
-2016; Champion et al.
-2016; Rane et al.
-2016).
-FRB 121102 is associated with a relatively small galaxy, which are roughly a factor of 100 more abundant than L∗ galaxies (φ(M) ∼ 10−2 Mpc−3; Faber et al.
-2007).
+First, the projected FRB rate is now believed to be closer to $2\times10^3 \rm{sky}^{-1} \rm{day}^{-1}$\ at high Galactic latitudes and flux densities brighter than 1 Jy ms \citep{2016arXiv161100458L,2016MNRAS.460L..30C}.
+\frb\ is associated with a relatively small galaxy, which are roughly a factor of 100 more abundant \citep[$\Phi(M) \approx 10^{-2} \rm{Mpc}^{-3}$][]{2007ApJ...665..265F}.
 Finally, the measured distance for FRB 121102 suggests that roughly half of the extragalactic DM is intrinsic to the host and half is from the IGM.
@@
 This reduces the characteristic distance by a factor of two and the volume by an order of magnitude.
-Considering these factors, we assume a characteristic FRB redshift of 0.4 to estimate RFRB ≈ 10−5 galaxy−1 year−1.
-This is lower than previously estimated (RFRB ∼ 10−3 galaxy−1 year−1 , Thornton et al.
-2013).
+Considering these factors, we assume a characteristic FRB redshift of 0.4 to estimate $R_{FRB} \approx 10^{-4} (0.1/\Omega_b) \rm{galaxy}^{-1} \rm{year}^{-1}$, which is two orders of magnitude lower than previously estimated \citep[assuming isotropic radiation;]{2013Sci...341...53T}.
 
@@
 Using this calculation with data from more sensitive telescopes, we might infer a higher rate.
-However, if we assume that FRB 121102 is representative of the overall FRB population, then more sensitive observations would be more likely to find repeating FRBs that would effectively depress the estimate of the underlying isotropic rate per source.
+However, if we assume that \frb\ is representative of the overall FRB population, then more sensitive observations would be more likely to find repeating FRBs that would effectively depress the estimate of the underlying isotropic rate per source.
 In this model, these two effects partially cancel, although without a physical model it is difficult to say how well.
-Finally, the bursts are known to be generated by a coherent emission process and does not emit isotropically.
-Assuming beaming angles typical of pulsars (e.g., Tauris & Manchester 1998), we expect a true FRB rate that is higher by a factor of 10.
 

### 2016-12-18 repeater-vladata.tex
working through emission physics, flux distribution.

@@
 
-\title{The \frb Observing Campaign: Multi-Telescope Radio Burst and Implications for the FRB Population}
+\title{The \frb\ Observing Campaign: Multi-Telescope Radio Burst and Implications for the FRB Population}
 %\title{Multi-Telescope Burst Properties and Implications for FRB Population}
@@
 
-Figure \ref{fig:dmmodel} compares the 95\% confidence intervals on the DM for all nine VLA bursts.
-Some of the confidence intervals do not overlap, which suggests that there are apparent DM changes between bursts.
-This change could be caused by intrinsic burst structure \citep{WEIRD} or actual changes to the DM column density.
-**Preliminary**
+ **Preliminary** Figure \ref{fig:dmmodel} compares the 95\% confidence intervals on the DM for all nine VLA bursts.
+The DM confidence intervals are not consistent with a single DM, which suggests that there are apparent DM changes between bursts.
+This change could be caused by intrinsic burst structure or actual changes to the DM column density.
+
+High-resolution dynamic spectra at 1.4~GHz have discovered spectro-temporal structure that can bias the apparent DM differently from burst to burst \citep{WEIRD}.
+Observations at 1.4~GHz have measured DM in the range from xx to yy pc cm$^{-3}$, which is **smaller than/consistent with** the range of observed values seen by the VLA at 3~GHz.
+The FRB emission process has not yet been defined, so it is not clear how the intrinsic structure can bias DM as a function of frequency.
+{\color{red} Laura, any input from DM at higher frequencies?}
 
@@
 \includegraphics[width=0.9\columnwidth]{dmmodel}
-\caption{**Preliminary** Comparison of 95\% ($1sigma$) confidence intervals for DM for nine bursts detected by the VLA.
+\caption{**Preliminary** Comparison of 95\% ($1\sigma$) confidence intervals for DM for nine bursts detected by the VLA.
 \label{fig:dmmodel}}
@@
 \label{sec:auto}
-Autocorrelation of the burst signal (both temporal and spectral) can be used to infer both intrinsic properties and modulation due to scintillation (CITE: Cordes et al?).
-While VLA spectral resolution of 4~MHz is relatively coarse, diffractive scintillation observed for other FRBs \citep{} {\color{red}could/could not (Jim?)} induce structure on this scale near 3~GHz.
-
-Figure \ref{fig:acf} shows the spectral autocorrellation for the strongest burst (MJD 57633.68). {\color{red} Comment, Jim?}
+Autocorrelation of the burst signal (both temporal and spectral) can be used to infer both intrinsic properties and modulation due to scintillation \citep{CORDES}.
+While VLA spectral resolution of 4~MHz is relatively coarse, the Galactic electron density model predicts a diffractive scintillation bandwidth of {\color{red} xx MHz at 3~GHz (Jim?)} \citep{2002astro.ph..7156C}.
+Figure \ref{fig:acf} shows the spectral autocorrellation for the strongest burst (MJD 57633.68).
+No excess correlation is found near the channel resolution, which limits the correlation width to less than 4~MHz.
 
@@
 \subsection{Temporal Statistics}
-The VLA detected nine bursts during the month-long campaign in August--September 2016.
-The typical observation lasted about two hours and was sampled with a 5~ms cadence, so we used the Lomb-Scargle periodogram \citep{} to search for periodic structure over a wide range of timescales.
-The input "lightcurve" was mde as a one-dimensional array for all times with observations; times with a detection are set to 1 and other times are set to 0 \citep[see also]{2011MNRAS.417.1871P}.
-The lightcurve time resolution was set to {\color{red} 100~ms (check)} to keep the computation manageable.
-The 95\% confidence upper limit on periodic power is estimated by randomly selecting the 9 burst times from the same observing times.
-The limit is set as the 95\% highest point at each period (5th highest value in 100 simulations).
-
-Figure \ref{fig:ls} shows the Lomb-Scargle periodogram for the bursts for periods from **xx to xx** s.
-No significant excess power is seen at long periods, but the periodogram shows a steady increase in power at shorter periods.
-The periodogram exceeds the 95\% power limit for periods from xx to xx s (**limited by binning time?**).
-This is consistent with the idea that the bursts imperfectly trace an underlying rotational period, as has been observed from many classes of neutron star.
-Examples include magnetars, which typically have wide pulse phase windows \citep{}, pulsars with glitches that change their periods \citep{}, and {\color{red} Maura?
-also refs for previous points would be welcome}.
-However, we can show with simulations that nine bursts drawn from a simple rotational would produce a strong, narrow peak in \ref{fig:ls}.
-
-Assuming periods with power peaks, we find clusters of bursts with same rotational phase...
-
-\begin{figure}[htb]
-\begin{center}
-\includegraphics[width=0.9\columnwidth]{lombscargle}
-\caption{Dots show the Lomb-Scargle periodogram of burst arrival times for \frb.
-The solid line show the 95\% confidence upper limit on the power expected from bursts with random arrival times.
-(**New version being compiled**)
-\label{fig:ls}}
-\end{center}
-\end{figure}
-
 Burst detections were made very inhomogenously through the larger (63 hours) observing campaign of FRB 121102.
 In the first 30 hours of observing at S-band no bursts were detected, while nine bursts were detected in the last 27 hours of S-band observing.
-The data quality is high and RFI did not significantly impact sensitivity, so the inhomogeneous burst distribution shows that the burst detection probability was not stationary.
+The data quality is high, so the inhomogeneous burst distribution shows that the burst detection probability was not stationary.
 Assuming that the burst detection probability follows a Poisson distribution, the nondetection in the first half of S-band limits the FRB rate to $\rm{R}<0.1$ hour$^{-1}$ (95\% confidence limit).
@@
 
-Moreover, there is weak evidence that the \frb\ burst rate changes during the last part of the campaign.
+There is weak evidence that the \frb\ burst rate changed during the last 27 hours of the S-band campaign.
 We modeled the event detection probability as a Poisson probability with a rate parameter that evolves linearly with time relative to first burst detection.
@@
 Figure \ref{fig:rate} shows that the probability distribution excludes a constant rate with $\sim$85\% confidence.
-This weak constraint is consistent with the broader trend seen by the VLA and Arecibo \citep{WEIRD}.
+This weak constraint is consistent with the broader trend seen by the VLA and Arecibo.
 
@@
 
-\subsection{Brightness Distribution}
+During the August--September 2016 observing campaign, the typical observation lasted about two hours and was sampled with a 5~ms cadence.
+We used the Lomb-Scargle periodogram \citep{1982ApJ...263..835S} to search for periodic structure over a wide range of timescales.
+The time series is calculated by binning the burst detection rate per 10~ms \citep[i.e., 0 or 1, see also]{2011MNRAS.417.1871P}.
+**in progress**
+No significant excess spectral power is seen for periods from xx to xx s... 
+%The periodogram exceeds the 95\% power limit for periods from xx to xx s (**limited by binning time?**).
+This is consistent with the idea that the bursts imperfectly trace an underlying rotational period, as has been observed from many classes of neutron star.
+Examples include magnetars, which typically have wide pulse phase windows \citep{}, pulsars with glitches that change their periods \citep{}, and {\color{red} Maura?
+also refs for previous points would be welcome}.
+However, we can show with simulations that nine bursts drawn from a simple rotational would produce a strong, narrow peak in \ref{fig:ls}.
+
+\subsection{Luminosity and Brightness Distribution}
+\label{sec:disn}
 Knowing the burst distance, we calculate their mean luminosity across a single 5~ms integration and the 1~GHz bandwidth (Table \ref{tab:spec}).
@@
 
-With a uniform sample of burst luminosities, we can use their distribution to infer more general properties for \frb.
-Figure \ref{fig:lumd} shows the luminosity distribution of the VLA bursts with a best-fit powerlaw model.
-Fitting a powerlaw model to the cumulative luminosity distribution gives an index of --0.5.
+This uniform sample of burst luminosities can be used to infer more general properties of \frb.
+We treat the detection probability as a Poisson process with a rate that scales with the luminosity as a powerlaw.
+Figure \ref{fig:lumd} shows the probability distribution for the powerlaw amplitude and index for the sample of nine VLA bursts.
+The luminosity powerlaw index $1\sigma$ bounds range from --0.5 to +0.4; for a cumulative luminosity distribution, this corresponds to a powerlaw index of roughly --0.6.
 The flatness of the distribution is also clear from range of significance of the nine bursts (12 to 179$\sigma$).
-All bursts are much brighter than the sensitivity limit (weakest is $\sim10\sigma$), so the distribution is not affected by a completeness limit.
+All bursts are much brighter than the sensitivity limit, so the distribution is not affected by a completeness limit.
 
@@
 \includegraphics[width=0.9\columnwidth]{luminosity_disn}
-\caption{Cumulative luminosity distribution and best-fit powerlaw model for the nine VLA bursts from \frb.
+\caption{Probability distribution of powerlaw luminosity model for the nine VLA bursts from \frb. Powerlaw referenced to $L=2\times10^{38}$\ erg.
 \label{fig:lumd}}
@@
 
+Assuming that \frb\ is representative of the overall FRB population, we can use the luminosity distribution of the former to infer properties of the latter.
+The primary observable of the FRB population is the flux distribution.
+We use a Monte-Carlo technique to simulate an FRB population with a given luminosity and spatial distribution.
+To reproduce the observed FRB sample, we select the brightest $N$\ bursts and fit their fluxes with a powerlaw.
+The tail of this distribution selects for extrema, such cut-offs in the intrinsic distribution or propagation effects \citep{2015MNRAS.451.3278M, CORDES}.
+Therefore, we sample 100 such populations and measure 95\% bounds on the distribution of cumulative flux distribution index.
+
+These simulations confirm previous work that shows that in many circumstances the cumulative flux distribution follows a Euclidean distribution \citep[index = --1.5;][]{2016MNRAS.462..941L}.
+To reproduce the flatness (index$\approx-1$) of the observed flux distribution, we need to incorporate other effects.
+**in progress** (new figure?)
+
 \section{discussion}
@@
 \subsection{Emission Physics and Burst Energetics}
-**Cut from gemini paper**
-The redshift measurement allows us to put FRB 121102’s energetics on a firmer footing, confirming \citet{LOC}.
+The measurement of a redshift to the host of \frb allows us to measure the burst luminosity.
+We now know that \frb\ is detectable with the VLA out to $z=0.7$ and much farther with Arecibo.
+This confirms the results presented in \citet{LOC}, which quoted a luminosity on the order of $10^{38}$\ erg.
+The more refined analysis presented here measures somewhat higher burst fluxes, so the brightest VLA burst luminosity is now on the order of $10^{40}$\ erg.
 
-% from first paper
-For a nominal Gpc distance $D$ corresponding to redshifts $z\lesssim 0.3$, the received fluence $A_{\nu}$ from each burst implies  a burst energy
-$$E_{\rm burst} = 4\pi D^2 (\delta\Omega/4\pi) A_{\nu} \Delta\nu
-\approx 10^{38}\, {\rm erg}\,(\delta\Omega/4\pi) D_{\rm Gpc}^2  (A_{\nu} / 0.1\ {\rm Jy\ ms}) \Delta\nu_{\rm GHz}.$$
-The unknown  emission solid angle $\delta\Omega$
-could be very small due to relativistic beaming, and together with a distance possibly much smaller than 1~Gpc, could reduce the energy requirement significantly.
-However, the {\it total} energy emitted could be larger depending on the duration of the emission in the source frame and other model-dependent details.
-Either way, the burst energies from \frb\ are not inconsistent with those that might be expected from the magnetosphere of a compact object\cite{2016MNRAS.457..232C}.
+However, the total energy emitted by \frb\ can be orders of magnitude larger or smaller than this value.
+While the emission process is not yet known, it is neccessarily coherent \citep{2016Natur.531..202S, WEIRD}, so relativistical beaming will amplify the apparent brightness.
+Propagation effects (e.g., scintillation, scattering) can also modify the radio signal in a variety of ways \citep{CORDES} and the duration of the emission in the source frame is not known.
+For these reasons, the luminosities described here are best described as isotropic, apparent luminosities.
 
-\subsection{Luminosity Distribution}
+**coherent emission from neutron stars** **extreme luminosities**
+\citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}
 
+\subsection{FRB Flux Distribution}
 Doubts were cast on the first FRB detection (``Lorimer burst'') due to its unusually high brightness.
 The lack of lower-significance detections suggested that this burst was unlikely to be part of any astrophysical population.
-With more detections, it has become clear that the FRB population has a relatively flat flux distribution \citep{2016ApJ...830...75V, 2016arXiv161100458L}.
+With more detections, it has become clear that the FRB population has a relatively flat flux distribution \citep{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}.
 This fact was demonstrated with yet another detection of an extremely bright FRB \citep{2016arXiv161105758R}.
 
-\frb\ is detectable with the VLA out to $z=0.7$ and much farther with Arecibo...
-
-Discuss comparison FRB 121102 luminosity distribution to that of FRB population...
-
-Imagine physical log N/log S with cut-offs and scattering can bias the intrinsic into the observed distribution (Macquart and Johnston)...
-
-Simulate cosmic volume uniformly filled with \frb... Also once done with a theoretical model based on young pulsars \citep{2016MNRAS.462..941L}
-
+Flux distribution... (\S \ref{sec:disn})
 Scaling up assumes that this source is representative.

### 2016-12-18 repeater-vladata.tex
l-s power discussion

@@
 There is weak evidence that the \frb\ burst rate changed during the last 27 hours of the S-band campaign.
-We modeled the event detection probability as a Poisson probability with a rate parameter that evolves linearly with time relative to first burst detection.
-We directly sampled the model by calculating the joint probability $\prod_{i} P_i$, where $P_i$ follows a Poisson probability with rate $\lambda = a + b * (\rm{MJD}_i - 57623)$.
-Figure \ref{fig:rate} shows that the probability distribution excludes a constant rate with $\sim$85\% confidence.
+We modeled the event detection probability as a Poisson probability with a rate parameter that evolves linearly with time relative to first burst detection, $\lambda = a + b * (\rm{MJD}_i - 57623)$.
+By directly sampling the joint probability distribution, $\prod_{i} P_i$, we can exclude a constant rate with $\sim$85\% confidence.
 This weak constraint is consistent with the broader trend seen by the VLA and Arecibo.
 
-\begin{figure}[htb]
-\begin{center}
-\includegraphics[width=0.9\columnwidth]{event_rate_contours}
-\caption{Color scale and contours show the relative probability for a time-evolving Poisson detection probability for \frb.
+%\begin{figure}[htb]
+%\begin{center}
+%\includegraphics[width=0.9\columnwidth]{event_rate_contours}
+%\caption{Color scale and contours show the relative probability for a time-evolving Poisson detection probability for \frb.
 Contours show the 50, 90, and 95\% confidence contours on the rate $a$\ (bursts s$^{-1}$) and rate change $b$\ (bursts s$^{-1}$ day$^{-1}$) during the August--September 2016 campaign in which bursts were detected.
-\label{fig:rate}}
-\end{center}
-\end{figure}
+%\label{fig:rate}}
+%\end{center}
+%\end{figure}
 
@@
 We used the Lomb-Scargle periodogram \citep{1982ApJ...263..835S} to search for periodic structure over a wide range of timescales.
-The time series is calculated by binning the burst detection rate per 10~ms \citep[i.e., 0 or 1, see also]{2011MNRAS.417.1871P}.
-**in progress**
-No significant excess spectral power is seen for periods from xx to xx s... 
-%The periodogram exceeds the 95\% power limit for periods from xx to xx s (**limited by binning time?**).
-This is consistent with the idea that the bursts imperfectly trace an underlying rotational period, as has been observed from many classes of neutron star.
-Examples include magnetars, which typically have wide pulse phase windows \citep{}, pulsars with glitches that change their periods \citep{}, and {\color{red} Maura?
-also refs for previous points would be welcome}.
-However, we can show with simulations that nine bursts drawn from a simple rotational would produce a strong, narrow peak in \ref{fig:ls}.
+The time series is calculated by binning the burst detection rate per 100~ms \citep[always either 0 or 1, see also]{2011MNRAS.417.1871P}.
+The spectral power is calculated for periods between 0.8 and 80 s and a 95\% confidence bound is estimated from a sample of 100 random shuffles of the data.
+
+Figure \ref{fig:ls} shows that while no single period dominates the spectral power, there is excess power for periods shorter than {\color{red}xx s}.
+It is easy to generate excess power in a Lomb-Scargle periodogram with a non-stationary noise process.
+However, that tends to create spectral power on low frequencies \citep["red noise"][]{}.
+We verified that simulating nine bursts drawn from a simple rotational model would produce a strong, narrow peak in \ref{fig:ls}.
+If astrophysical, this excess power is consistent with the idea that the bursts imperfectly trace an underlying rotational period, as has been observed from many classes of neutron star.
+Examples include magnetars, which typically have wide pulse phase windows \citep{2007ApJ...663..497C} and glitches that change their periods \citep{2013Natur.497..591A}.
 

### 2016-12-18 repeater-vladata.tex
removed l-s excess power. obs strat and naming conv discussed

@@
 The time series is calculated by binning the burst detection rate per 100~ms \citep[always either 0 or 1, see also]{2011MNRAS.417.1871P}.
-The spectral power is calculated for periods between 0.8 and 80 s and a 95\% confidence bound is estimated from a sample of 100 random shuffles of the data.
-
-Figure \ref{fig:ls} shows that while no single period dominates the spectral power, there is excess power for periods shorter than {\color{red}xx s}.
-It is easy to generate excess power in a Lomb-Scargle periodogram with a non-stationary noise process.
-However, that tends to create spectral power on low frequencies \citep["red noise"][]{}.
-We verified that simulating nine bursts drawn from a simple rotational model would produce a strong, narrow peak in \ref{fig:ls}.
-If astrophysical, this excess power is consistent with the idea that the bursts imperfectly trace an underlying rotational period, as has been observed from many classes of neutron star.
-Examples include magnetars, which typically have wide pulse phase windows \citep{2007ApJ...663..497C} and glitches that change their periods \citep{2013Natur.497..591A}.
+The spectral power calculated for periods between 0.8 and 80 s shows no power in excess of the typical 95\% confidence bound estimated from shuffled data.
+We verified that simulating nine bursts drawn from a simple rotational model would produce excess power using this approach.
+However, it is difficult to put strong constraints on more complex rotational models \citep[e.g., with wide pulse phase windows or glitches][]{2007ApJ...663..497C, 2013Natur.497..591A}
 
@@
 
-However, the total energy emitted by \frb\ can be orders of magnitude larger or smaller than this value.
+However, the total energy emitted by \frb\ can be orders of magnitude different than this isotropic, apparent luminosity.
 While the emission process is not yet known, it is neccessarily coherent \citep{2016Natur.531..202S, WEIRD}, so relativistical beaming will amplify the apparent brightness.
 Propagation effects (e.g., scintillation, scattering) can also modify the radio signal in a variety of ways \citep{CORDES} and the duration of the emission in the source frame is not known.
-For these reasons, the luminosities described here are best described as isotropic, apparent luminosities.
-
-**coherent emission from neutron stars** **extreme luminosities**
-\citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}
+In any case, the luminosity scale is still larger than any Galactic class of fast radio transient and requires either a new process or dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}.
 
@@
 \subsection{FRB Rate}
-% cut from gemini paper. TODO: incorporate referee comments on rate scale
+% cut from gemini paper. TODO: incorporate referee comments on rate scale. Sarah?
 Assuming that \frb is from the same population as the other FRBs, the measurement of a distance for the host of \frb allows us to re-evaluate the cosmic volume and event rate per galaxy for the FRB population.
@@
 First, the projected FRB rate is now believed to be closer to $2\times10^3 \rm{sky}^{-1} \rm{day}^{-1}$\ at high Galactic latitudes and flux densities brighter than 1 Jy ms \citep{2016arXiv161100458L,2016MNRAS.460L..30C}.
-\frb\ is associated with a relatively small galaxy, which are roughly a factor of 100 more abundant \citep[$\Phi(M) \approx 10^{-2} \rm{Mpc}^{-3}$][]{2007ApJ...665..265F}.
+\frb\ is associated with a relatively small galaxy, which are roughly a factor of 100 more abundant \citep[$\Phi(M) \approx 10^{-2} \rm{Mpc}^{-3}$;][]{2007ApJ...665..265F}.
 Finally, the measured distance for FRB 121102 suggests that roughly half of the extragalactic DM is intrinsic to the host and half is from the IGM.
@@
 \subsection{Observing Strategies}
-
-Repetition implies that targeting known FRBs is optimal.
-
-Repetition and shallow luminosity distribution show that shallow and wide is the best way to blindly find FRBs.
-
-Given that bursts have $<1$~GHz-scale spectra, wide bandwidths improve odds of detection.
+As discussed above, \citet{2016MNRAS.458L..89C} note that the FRB repetition implies that the number of FRB-generating sources is smaller than the number of bursts.
+In some scenarios, this means that there are areas on the sky that may contain no FRBs.
+Wide, shallow surveys are the preferred strategy for blind detection of FRBs.
+However, future efforts to localize FRBs are still most likely to success by targeting known FRBs to catch repetitions.
+Finally, we note that the spectral coverage of bursts from \frb\ are relatively narrow ($<1$~GHz) and change dramatically between bursts.
+Thus, the odds of detecting a burst will improve linearly with bandwidth for bandwidths wider than this characteristic scale.
 
 \subsection{Naming Convention}
-
-The cosmological distance for \frb\ and consistency with the overall population suggests that most FRBs repeat.
-The current naming convention for FRBs is analogous to supernovae, with six numbers defining the year, month, and day of detection.
-If all FRBs repeat, then this naming convention is only useful for identifying its discovery.
-A more useful convention would be the more common one that uses the coordinates.
-But there are already two FRBs that have consistent celestial positions and different DMs.
-
-We suggest a convention of referring to FRBs as Jhhmm+dd or appending DM...
+The consistency of \frb\ properties (e.g., luminosity distribution) with the overall population suggests other FRBs likely repeat.
+If so, the current naming convention for FRBs (analogous to cataclysmic supernovae), will likely become uninformative, especially as large FRB survey projects come online \citep{2014SPIE.9145E..22B}.
+If all FRBs repeat, then a more useful convention would be based on coordinates.
+However, there are already two FRBs that have consistent celestial positions and different DMs.
+Therefore, we suggest an FRB naming convention as Jhhmm+ddDMmmmm.
 
 \section{Conclusions}
+Prior to being established as a cosmological source, the low Galactic latitude of \frb\ made it a somewhat compromised member of the FRB class.
+With its cosmological distance firmly established, \frb\ now serves as a new kind of standard by which FRBs are defined.
 

### 2016-12-18 repeater-vladata.tex
fixing axis label on spectra

@@
 Figure \ref{fig:sgram} shows the dynamic spectra of all nine bursts detected by the VLA.
-We improved on the initial analysis presented in \citet{LOC} by using a better calibration scheme and optimizing the detection significance over a find grid of DM ($\Delta DM=1 \rm{pc} \rm{cm}^{-3}$).
+We improved on the initial analysis presented in \citet{LOC} by using a better calibration scheme and optimizing the detection significance over a fine grid of DM ($\Delta \rm{DM}=1 \rm{pc} \rm{cm}^{-3}$).
 Table \ref{tab:spec} shows the improved burst parameters using this new scheme.
@@
 There is weak evidence that the \frb\ burst rate changed during the last 27 hours of the S-band campaign.
-We modeled the event detection probability as a Poisson probability with a rate parameter that evolves linearly with time relative to first burst detection, $\lambda = a + b * (\rm{MJD}_i - 57623)$.
+We modeled the event detection probability as a Poisson probability function, $P_i(\lambda)$, with rate parameter that evolves linearly in time relative to the first VLA burst $\lambda = a + b (\rm{MJD}_i - 57623)$.
 By directly sampling the joint probability distribution, $\prod_{i} P_i$, we can exclude a constant rate with $\sim$85\% confidence.

### 2016-12-19 repeater-vladata.tex
repetition disc. flux disn disc

@@
  \caption{Dynamic spectra (time vs frequency intensity maps) for the nine VLA bursts.
-Starting at the top left, they correspond to bursts 57623, 57633.68, 57633.70, 57638, 57643, 57645, 57646, 57648, and 57649.
+Starting at the top left, they correspond to bursts 57623, 57633.68, 57633.70, 57638, 57643, (bottom left) 57645, 57646, 57648, and 57649.
 Note that bursts are detected in 5~ms images generated from dedispersed visibilities.
@@
 \caption{Spectra of nine bursts seen by the VLA from 2.5 to 3.5~GHz.
-Orthongonal circular polarizations (RR and LL) are plotted separately.
-**LABELS ALL SAME FREQ.
-SOME SHOULD START HIGHER FOR DROPPED CHANNELS**
+Orthongonal circular polarizations (RR and LL) are plotted separately and example errorbars are shown at the top right of each panel.
+A binned spectrum is overplotted with a solid line.
 \label{fig:spec}}
@@
 \subsection{Temporal Statistics}
+\label{sec:temp}
 Burst detections were made very inhomogenously through the larger (63 hours) observing campaign of FRB 121102.
@@
 With more detections, it has become clear that the FRB population has a relatively flat flux distribution \citep{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}.
-This fact was demonstrated with yet another detection of an extremely bright FRB \citep{2016arXiv161105758R}.
+This fact was recently demonstrated by yet another detection of an extremely bright FRB \citep{2016arXiv161105758R}.
 
-Flux distribution... (\S \ref{sec:disn})
-Scaling up assumes that this source is representative.
-Propagation effects may amplify or alter burst brightness statistical properties.
-Some such effects are possible near the burst source (e.g., Jim's caustic analysis), which would effectively be intrinsid in this context.
+**Discussion of luminosity/flux distribution analysis presented in \S \ref{sec:disn})**
+
+It is not yet clear whether \frb\ can be treated as a representative of the broader FRB population.
+\citet{2016Natur.531..202S} describes burst spectral structure that is intrinsic, or at least dominated by propagation effects close to the emitting region.
+On the other hand, \citep{CORDES} have identified a variety of propagation effects in our own Galaxy that can plausibly modify the observed brightness distribution.
 
 \subsection{Repetition}
-Discussion of ``red spectrum'' and \citet{2016MNRAS.458L..89C}. Bursts predict bursts therefore repetition constraints of other FRBs are likely weaker than claimed...
+The burst rate analysis presented in \S \ref{sec:temp} shows that the detection probability of \frb\ is not stationary.
+As mentioned above, this could be caused by intrinsic events (e.g., magnetar outburst) or propagation effects.
+In either case, it demonstrates that \frb\ has a kind of "red spectrum" temporally, in which bursts tend to cluster in time \citep{2016MNRAS.458L..89C}.
+The detection of a burst improves odds of finding more bursts in near-future observations.
 
-Constraints on repetition assuming "red spectrum" for whole population. Simulation using observed burst temporal statistics...
-
-Intrinsic versus refractive scintillation...
-
-Fewer FRBs out there...
+If this statistical property describes other FRBs, it weakens previous constraints on repetition \citep{2015MNRAS.454..457P,2015ApJ...807...16L}.
+It is possible that other FRBs have repeating bursts, although calculating a limit requires knowing the temporal powerlaw that defines the repetition.
+Observations of \frb\ have not yet detected enough bursts to reliably measure that index.
+This repetition also implies that there are fewer phyiscal sources of FRBs than implied by the burst detection rate.
 

### 2016-12-19 repeater-vladata.tex
reworking dm changes

@@
 \author{D.~Michilli}
+\affiliation{ASTRON, Netherlands Institute for Radio Astronomy, Postbus 2, 7990 AA, Dwingeloo, The Netherlands}
 \affiliation{Anton Pannekoek Institute for Astronomy, University of Amsterdam, Science Park 904, 1098 XH Amsterdam, The Netherlands}
@@
 Figure \ref{fig:sgram} shows the dynamic spectra of all nine bursts detected by the VLA.
-We improved on the initial analysis presented in \citet{LOC} by using a better calibration scheme and optimizing the detection significance over a fine grid of DM ($\Delta \rm{DM}=1 \rm{pc} \rm{cm}^{-3}$).
+We improved on the initial analysis presented in \citet{LOC} by using a better calibration scheme and optimizing the detection significance over a fine grid of DM ($\Delta \rm{DM}=1 \rm{pc}\ \rm{cm}^{-3}$).
 Table \ref{tab:spec} shows the improved burst parameters using this new scheme.
@@
 \subsubsection{Dispersion}
-The initial VLA detections were made by searching a DM grid that allowed inter-DM sensitivity losses up to roughly 10\% \citep[$\Delta DM=10 \rm{pc} \rm{cm}^{-3}$][]{2003ApJ...596.1142C}.
+The initial VLA detections were made by searching a DM grid that allowed inter-DM sensitivity losses up to roughly 10\% \citep[$\Delta DM=10 \rm{pc}\ \rm{cm}^{-3}$][]{2003ApJ...596.1142C}.
 In optimizing detection significance over a fine DM grid, we find optimal DM values range from 552 to 572 pc cm$^{-3}$.
@@
  **Preliminary** Figure \ref{fig:dmmodel} compares the 95\% confidence intervals on the DM for all nine VLA bursts.
-The DM confidence intervals are not consistent with a single DM, which suggests that there are apparent DM changes between bursts.
+The DM confidence intervals {\color{red} are/are not} consistent with a single DM...
+%, which suggests that there are apparent DM changes between bursts.
 This change could be caused by intrinsic burst structure or actual changes to the DM column density.
@@
 The estimated projected FRB rate $R_p$ understates the true rate by a beaming fraction $\Omega_b$ \citep[$\sim$10\%;][]{1998MNRAS.298..625T}..
-For a comoving volume $V(z)$ and galaxy number density $\Phi(M)$, the rate per galaxy is $R_{FRB} = R_p \Omega_b /(\Phi(M)V (z))$.
+For a comoving volume $V(z)$ and galaxy number density $\Phi(M)$, the rate per galaxy is $R_{FRB} = R_p /(\Omega_b \Phi(M)V (z))$.
 
 The first such rate estimate was made by \citet{2013Sci...341...53T}, who used the measured DM to estimate a characteristic distance for their sample of 4 FRBs.
-They assumed that all of the extragalactic component of the DM was caused by the IGM and scaled as $DM\approx z\times1200 \rm{pc} \rm{cm}^{-3}$ \citep{2003ApJ...598L..79I,2004MNRAS.348..999I}.
+They assumed that all of the extragalactic component of the DM was caused by the IGM and scaled as $DM\approx z\times1200 \rm{pc}\ \rm{cm}^{-3}$ \citep{2003ApJ...598L..79I,2004MNRAS.348..999I}.
 They also calculated the number of galaxies by assuming a characteristic $L_*$ galaxy \citep[corresponding to stellar mass $M_* \approx 1010.66 M$][]{2012MNRAS.421..621B}.

### 2016-12-19 repeater-vladata.tex
added ami coauthors. reworked abstract

@@
 
+\author{T.~Cantwell}
+\affiliation{University of Manchester, UK}
+
+\author{S.~H.~Carey}
+\affiliation{University of Cambridge, UK}
+
 \author{J.~M.~Cordes}
@@
 
+\author{K.~Grainge}
+\affiliation{University of Manchester, UK}
+
 \author{J.~W.~T.~Hessels}
@@
 \affiliation{Anton Pannekoek Institute for Astronomy, University of Amsterdam, Science Park 904, 1098 XH Amsterdam, The Netherlands}
+
+\author{J.~Hickish}
+\affiliation{Dept of Astronomy and Radio Astronomy Lab, University of California, Berkeley, CA 94720, USA}
+\affiliation{University of Cambridge, UK}
 
@@
 
+\author{Y.~C.~Perrott}
+\affiliation{University of Cambridge, UK}
+
 %\author{S.~M.~Ransom}
@@
 
+\author{N.~Razavi-Ghods}
+\affiliation{University of Cambridge, UK}
+
 \author{M.~Rupen}
 \affiliation{National Research Council of Canada, Herzberg Astronomy and Astrophysics, Dominion Radio Astrophysical Observatory, P.O. Box 248, Penticton, BC V2A 6J9, Canada}
+
+\author{A.~Scaife}
+\affiliation{University of Manchester, UK}
+
+\author{P.~Scott}
+\affiliation{University of Cambridge, UK}
 
@@
 
+\author{D.~Titterington}
+\affiliation{University of Cambridge, UK}
+
 \author{R.~S.~Wharton}
@@
 The millisecond radio transients known as Fast Radio Bursts have recently emerged as a mysterious, new class of astrophysical transient.
-The discovery of repeating bursts from \frb\ has shown that at least some FRBs are not cataclysmic and opened potential for studying FRB properties via a homogenous sample of bursts.
-The recent localization of \frb\ with the Very Large Array has helped measure its distance and a host of intrinsic properties.
-This localization was made with 9 bursts seen by the VLA in coordination the Arecibo, Effelsberg, and AMI-LA observatories.
+The recent localization of \frb\ has helped identify its host galaxy, measure its distance, and infer intrinsic properties that comment on the broader FRB population.
 We present a detailed analysis of these bursts, including the first simultaneous detection of an FRB with multiple telescopes.
@@
 The FRB emission process has not yet been defined, so it is not clear how the intrinsic structure can bias DM as a function of frequency.
-{\color{red} Laura, any input from DM at higher frequencies?}
 
@@
 \section*{Acknowledgements}
-We thank ...
 This project was supported by the University of California Office of the President under Lab Fees Research Program Award 237863.

### 2016-12-19 repeater-vladata.tex
draft circulated to group. has conclusions. fixed latex formatting issues.

@@
 Gain calibration is read from the "telcal" system, which uses phase-only calibration on the previous gain calibrator.
-A flux scale is calculated for each spectral window from an observation on {\color{red} xx (Bryan)} and applied to all burst spectra.
+A flux scale is calculated for each spectral window from an observation on {\color{red}xx (Bryan)} and applied to all burst spectra.
 
@@
 The transient search starts when data are recorded, but this prototype of \rf\ is a factor of several times slower than real-time, so we refer to the detection as "quasi real-time".
-Each image with a pixel higher than 6.4$\sigma$ is saved in a summary form as a check of data quality.
+Each image with a pixel higher than 6.4$\sigma$\ is saved in a summary form as a check of data quality.
 For each image with a pixel higher than 7.4$\sigma$, \rf\ generates a more detailed candidate visualization with an image and spectrum.
@@
 
-{\color{red} copied from the first paper}
+{\color{red}Jason/Shami: ok if copied from the first paper?}
 During the joint Arecibo-VLA campaign, Arecibo observed with the L-wide receiver, which has an observational frequency range of 1.15 to 1.73~GHz and a full width at half maximum beam size of 3.3 arcmin.
@@
 Each frequency channel was coherently dedispersed to 557 pc cm$^{-3}$, thereby eliminating intra-channel dispersion smearing.
-PUPPI covers a total of 800~MHz of bandwidth centred at 1380.78125~MHz, but only $\sim$ 620~MHz of this band is usable due to radio frequency interference and receiver sensitivity roll-off at the band edges.
+PUPPI covers a total of 800~MHz of bandwidth centred at 1380.78125~MHz, but only $\sim 620$\ MHz of this band is usable due to radio frequency interference and receiver sensitivity roll-off at the band edges.
 
@@
 
-We observed \frb with the Arcminute MicroKelvin Imager Large Array (AMI-LA; Zwart et al.
+We observed \frb\ with the Arcminute MicroKelvin Imager Large Array (AMI-LA; Zwart et al.
 2008) for 3 hours each on four epochs starting at MJDs 57643.3351, 57645.3317, 57648.3352, and 57649.3353.
@@
 All but two of the best-fit Gaussians are centered inside the 3~GHz band and most appear contained by the 1~GHz wide band.
-This is consistent with previous detections of \frb by Arecibo, which showed quasi-broadband structure \citep{2016arXiv160308880S} and large variation in the implied spectral index \citep{2014ApJ...790..101S}.
+This is consistent with previous detections of \frb\ by Arecibo, which showed quasi-broadband structure \citep{2016arXiv160308880S} and large variation in the implied spectral index \citep{2014ApJ...790..101S}.
 A detailed discussion of high-resolution \frb\ burst spectra seen by the Arecibo Observatory will be presented elsewhere \citep{WEIRD}.
@@
 
- **Preliminary** Figure \ref{fig:dmmodel} compares the 95\% confidence intervals on the DM for all nine VLA bursts.
-The DM confidence intervals {\color{red} are/are not} consistent with a single DM...
-%, which suggests that there are apparent DM changes between bursts.
-This change could be caused by intrinsic burst structure or actual changes to the DM column density.
-
-High-resolution dynamic spectra at 1.4~GHz have discovered spectro-temporal structure that can bias the apparent DM differently from burst to burst \citep{WEIRD}.
-Observations at 1.4~GHz have measured DM in the range from xx to yy pc cm$^{-3}$, which is **smaller than/consistent with** the range of observed values seen by the VLA at 3~GHz.
+Figure \ref{fig:dmmodel} compares the 95\% confidence intervals on the DM for all nine VLA bursts to the range of DM previous observed \citep{2014ApJ...790..101S,2016arXiv160308880S}.
+The DM confidence intervals are not consistent with each other or a single DM.
+This suggests that there are apparent DM changes between bursts, either due to intrinsic burst structure or actual changes to the DM column density.
+Elsewhere, we present high-resolution dynamic spectra at 1.4~GHz that show how intrinsic spectral structure can bias the apparent DM of individual bursts \citep{WEIRD}.
 The FRB emission process has not yet been defined, so it is not clear how the intrinsic structure can bias DM as a function of frequency.
@@
 \includegraphics[width=0.9\columnwidth]{dmmodel}
-\caption{**Preliminary** Comparison of 95\% ($1\sigma$) confidence intervals for DM for nine bursts detected by the VLA.
+\caption{DM 95\% confidence intervals of the nine 3~GHz bursts detected by the VLA. The grey band shows the range of DM previously detected at 1.4~GHz ($\pm3$\ pc cm$^{-3}$).
 \label{fig:dmmodel}}
@@
 Autocorrelation of the burst signal (both temporal and spectral) can be used to infer both intrinsic properties and modulation due to scintillation \citep{CORDES}.
-While VLA spectral resolution of 4~MHz is relatively coarse, the Galactic electron density model predicts a diffractive scintillation bandwidth of {\color{red} xx MHz at 3~GHz (Jim?)} \citep{2002astro.ph..7156C}.
+While VLA spectral resolution of 4~MHz is relatively coarse, the Galactic electron density model predicts a diffractive scintillation bandwidth of {\color{red}Jim: xx MHz at 3~GHz} \citep{2002astro.ph..7156C}.
 Figure \ref{fig:acf} shows the spectral autocorrellation for the strongest burst (MJD 57633.68).
@@
 \includegraphics[width=0.9\columnwidth]{acf_57633_scan7}
-\caption{The spectral autocorrelation for the burst from \frb\ at MJD 57633.68.
+\caption{ {\color{red} Jim: worth keeping?} The spectral autocorrelation for the burst from \frb\ at MJD 57633.68.
 Blue shows the autocorrelation for the burst and green shows an autocorrelation of a representative spectrum with no burst.
@@
 The apparent circular polarization fraction ($(RR-LL)/(RR+LL)$) for the most significant bursts are all less than 3\%.
-\frb was located 2.3 arcmin away from pointing center, where systematic effects have been measured as large as 3\% (Perley et al 2016, VLA memo).
+\frb\ was located 2.3 arcmin away from pointing center, where systematic effects have been measured as large as 3\% (Perley et al 2016, VLA memo).
 Given that systematic effects dominate the apparent circular polarization, we conclude that the true fractional circular polarization is less than 3\%.
@@
 The data quality is high, so the inhomogeneous burst distribution shows that the burst detection probability was not stationary.
-Assuming that the burst detection probability follows a Poisson distribution, the nondetection in the first half of S-band limits the FRB rate to $\rm{R}<0.1$ hour$^{-1}$ (95\% confidence limit).
-The mean detection rate for the last part of the campaign was $\rm{R}=0.3$ hour$^{-1}$.
+Assuming that the burst detection probability follows a Poisson distribution, the nondetection in the first half of S-band limits the FRB rate to $\rm{R}<0.1$\ hour$^{-1}$\ (95\% confidence limit).
+The mean detection rate for the last part of the campaign was $\rm{R}=0.3$\ hour$^{-1}$.
 
@@
 Figure \ref{fig:lumd} shows the probability distribution for the powerlaw amplitude and index for the sample of nine VLA bursts.
-The luminosity powerlaw index $1\sigma$ bounds range from --0.5 to +0.4; for a cumulative luminosity distribution, this corresponds to a powerlaw index of roughly --0.6.
+The luminosity powerlaw index $1\sigma$\ bounds range from --0.5 to +0.4; for a cumulative luminosity distribution, this corresponds to a powerlaw index of roughly --0.6.
 The flatness of the distribution is also clear from range of significance of the nine bursts (12 to 179$\sigma$).
@@
 \includegraphics[width=0.9\columnwidth]{luminosity_disn}
-\caption{Probability distribution of powerlaw luminosity model for the nine VLA bursts from \frb. Powerlaw referenced to $L=2\times10^{38}$\ erg.
+\caption{Probability distribution of powerlaw luminosity model for the nine VLA bursts from \frb. The powerlaw is referenced to $L=2\times10^{38}$\ erg.
 \label{fig:lumd}}
@@
 
-These simulations confirm previous work that shows that in many circumstances the cumulative flux distribution follows a Euclidean distribution \citep[index = --1.5;][]{2016MNRAS.462..941L}.
-To reproduce the flatness (index$\approx-1$) of the observed flux distribution, we need to incorporate other effects.
+These simulations confirm previous work that shows that in many circumstances the cumulative flux distribution follows a Euclidean distribution \citep[index $=-1.5$;][]{2016MNRAS.462..941L}.
+To reproduce the flatness (index $\approx-1$) of the observed flux distribution, we need to incorporate other effects.
 **in progress** (new figure?)
@@
 \subsection{Emission Physics and Burst Energetics}
-The measurement of a redshift to the host of \frb allows us to measure the burst luminosity.
-We now know that \frb\ is detectable with the VLA out to $z=0.7$ and much farther with Arecibo.
+The measurement of a redshift to the host of \frb\ allows us to measure the burst luminosity.
+We now know that \frb\ is detectable with the VLA out to $z=0.7$\ and much farther with Arecibo.
 This confirms the results presented in \citet{LOC}, which quoted a luminosity on the order of $10^{38}$\ erg.
@@
 % cut from gemini paper. TODO: incorporate referee comments on rate scale. Sarah?
-Assuming that \frb is from the same population as the other FRBs, the measurement of a distance for the host of \frb allows us to re-evaluate the cosmic volume and event rate per galaxy for the FRB population.
-The estimated projected FRB rate $R_p$ understates the true rate by a beaming fraction $\Omega_b$ \citep[$\sim$10\%;][]{1998MNRAS.298..625T}..
-For a comoving volume $V(z)$ and galaxy number density $\Phi(M)$, the rate per galaxy is $R_{FRB} = R_p /(\Omega_b \Phi(M)V (z))$.
+{\color{red} Sarah: can you update this as a per-SFR rate?}
+Assuming that \frb\ is from the same population as the other FRBs, the measurement of a distance for the host of \frb\ allows us to re-evaluate the cosmic volume and event rate per galaxy for the FRB population.
+The estimated projected FRB rate $R_p$\ understates the true rate by a beaming fraction $\Omega_b$\ \citep[$\sim$10\%;][]{1998MNRAS.298..625T}..
+For a comoving volume $V(z)$\ and galaxy number density $\Phi(M)$, the rate per galaxy is $R_{FRB} = R_p /(\Omega_b \Phi(M)V (z))$.
 
 The first such rate estimate was made by \citet{2013Sci...341...53T}, who used the measured DM to estimate a characteristic distance for their sample of 4 FRBs.
-They assumed that all of the extragalactic component of the DM was caused by the IGM and scaled as $DM\approx z\times1200 \rm{pc}\ \rm{cm}^{-3}$ \citep{2003ApJ...598L..79I,2004MNRAS.348..999I}.
-They also calculated the number of galaxies by assuming a characteristic $L_*$ galaxy \citep[corresponding to stellar mass $M_* \approx 1010.66 M$][]{2012MNRAS.421..621B}.
+They assumed that all of the extragalactic component of the DM was caused by the IGM and scaled as $DM\approx z\times1200 \rm{pc}\ \rm{cm}^{-3}$\ \citep{2003ApJ...598L..79I,2004MNRAS.348..999I}.
+They also calculated the number of galaxies by assuming a characteristic $L_*$\ galaxy \citep[corresponding to stellar mass $M_* \approx 1010.66 M$;][]{2012MNRAS.421..621B}.
 
@@
 With its cosmological distance firmly established, \frb\ now serves as a new kind of standard by which FRBs are defined.
+That fact, combined with an abundance of data collected during its high activity state, allows us to think more generally about the physics of broader FRB population.
 
- % include timeline and science scope for new localizations? realfast plug and reference cosmology papers, contingency on DMhost, etc.
+We presented the first multi-telescope detection (Arecibo and VLA) of a FRB.
+By detecting this burst from 1.2 to 4.5~GHz, we have demonstrated that some bursts have broad spectral structure.
+However, three other VLA bursts are undetected by Arecibo.
+That, combined with the measurement of spectra within the VLA band, suggest that the typical burst has a characteristic Gaussian spectral shape with width $\sim500$\ MHz.
+
+**Flux/lum distribution**
+
+Analysis of the VLA burst times shows that the burst rate is highly variable.
+This shows that past constraints on FRB repetition are weaker than previously inferred.
+The combination of relatively narrow spectral structure, flat luminosity and flux distributions, and variable burst rate suggests that repeated observations, wide bandwidth, and large instantaneous field of view all improve the chance of detection.
+
+New, arcsecond-scale localizations will continue to be highly informative, given that FRB hosts may be faint and can confuse the inference of a properties of the intergalactic medium \citep{2014ApJ...783L..35D}.
+\frb\ was localized within hours by a prototype version of \rf, but an expanded \rf\ system is now under construction.
+This platform will search a TB/hour data stream in real time in parallel with ongoing VLA observations, potentially detecting and localizing multiple FRBs per year.
+{\color{red} Sarah: any refinement to this statement?}
 

### 2016-12-21 repeater-vladata.tex
coauthor update
working through maura comments. updated table 1.

@@
 
-%\author{S.~M.~Ransom}
-%\affiliation{National Radio Astronomy Observatory, Charlottesville, VA 22903, USA}
+\author{S.~M.~Ransom}
+\affiliation{National Radio Astronomy Observatory, Charlottesville, VA 22903, USA}
 
@@
 We present a detailed analysis of these bursts, including the first simultaneous detection of an FRB with multiple telescopes.
-We show that the burst spectra typically have a broad Gaussian shape on the scale of $\sim500$~MHz with fine spectral structure consistent with either scintillation or unresolved temporal structure.
+We show that the burst spectra typically have a broad Gaussian shape on the scale of $\sim500$~MHz with fine spectral structure consistent with either scintillation or unresolved intrinsic temporal structure.
 We present the luminosity distribution and temporal statistics for \frb\ and argue that the whole FRB population is adequately described by a single class similar to \frb.
@@
 In mid 2015, new Arecibo observations revealed a series of bursts at the same DM and sky position demonstrating that FRBs are capable of repetition \citep{2016Natur.531..202S}.
-Beginning in August of 2015, we made the first of nine detections of \frb\ with the Very Large Array \citep{LOC} and localized it with a precision of 0.1\arcsec.
+Beginning in August of 2015, we made the first of nine detections of \frb\ with the Very Large Array \citep{LOC} and localized it to (RA, Dec) of (05h31m58.70s, +33d08m52.5s) with a precision of 0.1\arcsec.
 Deep radio and optical observing shows that \frb\ is unambiguously associated with a persistent radio and optical source at a redshift of 0.193 \citep{OPT, EVN}.
@@
 We can also assume that \frb\ is representative and use it to constrain the physical processes at play in the overall FRB population.
-Although we now know that FRBs are luminous, it is not yet clear what process generates the radio bursts themselves \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C}.
+In this case, we know that FRBs are luminous, but it is not yet clear what process generates the radio bursts themselves \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C}.
 The simultaneous \frb\ observing campaign with the VLA, Arecibo, Effelsberg, GBT, and AMI-LA gives a more complete picture of the spectral structure of FRB radio emission.
@@
 The data presented here were obtained from multiple programs and telescopes, but the central goal was to interferometrically localize \frb\ with the VLA.
-The observing strategy was to ensure simultaneous observing between the VLA and Arecibo observatories and add other observatories added on a best-effort basis.
-We coordinated observing between the VLA, Arecibo, Effelsberg, and AMI-LA telescopes, as shown in figure \ref{fig:multi}.
+The observing strategy was to ensure simultaneous observing between the VLA and Arecibo observatories and add other observatories on a best-effort basis.
+We coordinated observing between the VLA, Arecibo, Effelsberg, and AMI-LA telescopes, as shown in Figure \ref{fig:multi}.
 Below, we summarize these observations, with a focus on those conducted simultaneously with VLA burst detections from \frb.
@@
 In this last campaign, the first 34 hours of VLA observations were made at 3~GHz, while the last 6 hours were observed at 6~GHz.
-This paper focuses on the data collected at 3~GHz, which includes all nine burst detections.
+This paper focuses on the data collected at 3~GHz, which include all nine burst detections.
 
@@
 The total bandwidth at L (1.4~GHz), S (3~GHz), and C (6~GHz) bands was 256~MHz, 1024~MHz, and 2048~MHz, respectively.
-The 3~GHz data were recorded data in 8 spectral windows with 32 channels each.
+The 3~GHz data were recorded data in eight spectral windows with 32 channels each.
 
-Observations in August and Septmeber were searched by a prototype version of \rf\footnote{See \url{http://realfast.io}.}.
+Observations in August and September were searched by a prototype version of \rf\footnote{See \url{http://realfast.io}.}.
 \rf\ is a real-time, fast imaging transient search system.
-The current, prototype runs on existing, CPU-based hardware of the VLA correlator backend, while the future \rf\ will run on a dedicated GPU cluster.
-The transient search pipeline software is called \emph{rtpipe}\footnote{See \url{https://github.com/caseyjlaw/rtpipe}} and is mostly written in Python (detail in \citet{2015ApJ...807...16L}).
-Images were formed for each integration at DMs of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$.
-Gain calibration is read from the "telcal" system, which uses phase-only calibration on the previous gain calibrator.
+The current prototype runs on existing, CPU-based hardware of the VLA correlator backend with transient search pipeline software called \emph{rtpipe} \citep[\url{https://github.com/caseyjlaw/rtpipe};][]{2015ApJ...807...16L}.
+Images were formed for each integration with a DM grid of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$ and a time resampling grid of 5, 10, 20, 40, and 80 ms.
+This DM grid was chosen to maintain 90\% sensitivity to the nominal DM range of 554--560 pc cm$^{-3}$.
+Gain calibration is read from the ''telcal'' system, which uses phase-only calibration on the previous gain calibrator.
 A flux scale is calculated for each spectral window from an observation on {\color{red}xx (Bryan)} and applied to all burst spectra.
@@
 Burst detections and localizations were made within hours of data being recorded.
-The transient search starts when data are recorded, but this prototype of \rf\ is a factor of several times slower than real-time, so we refer to the detection as "quasi real-time".
-Each image with a pixel higher than 6.4$\sigma$\ is saved in a summary form as a check of data quality.
-For each image with a pixel higher than 7.4$\sigma$, \rf\ generates a more detailed candidate visualization with an image and spectrum.
+The transient search starts when data are recorded and proceeds slower than real-time, so we refer to it as ''quasi real-time''.
+For each trial DM, integration, and time scale, we form an image and calculate the S/N ratio for the peak pixel in the dirty image.
+Summary statistics are saved for images with S/N higher than 6.4, which captures the tail of the thermal noise distribution without adding significant computational or data volume burden.
+Each image with a pixel with S/N higher than 7.4 is relatively unlikely to be triggered by thermal noise in this configuration, so \rf\ generates a more detailed candidate visualization with an image and spectrum.
 More detailed analysis, including improved calibration and localization, is conducted offline.
@@
 
-{\color{red}Jason/Shami: ok if copied from the first paper?}
-During the joint Arecibo-VLA campaign, Arecibo observed with the L-wide receiver, which has an observational frequency range of 1.15 to 1.73~GHz and a full width at half maximum beam size of 3.3 arcmin.
-The PUPPI pulsar backend was used to record total intensity spectra with time and frequency resolutions of 10.24~$\mu$s and 1.5625~MHz, respectively, and full Stokes polarization information.
+During the joint Arecibo-VLA campaign, Arecibo observed with the L-wide receiver using the PUPPI pulsar backend.
+The observational frequency range was 1.15 to 1.73~GHz and frequency resolution was 1.5625~MHz.
+We recorded total full Stokes polarization intensity spectra with time at a resolution of 10.24~$\mu$s.
 Each frequency channel was coherently dedispersed to 557 pc cm$^{-3}$, thereby eliminating intra-channel dispersion smearing.
-PUPPI covers a total of 800~MHz of bandwidth centred at 1380.78125~MHz, but only $\sim 620$\ MHz of this band is usable due to radio frequency interference and receiver sensitivity roll-off at the band edges.
+The ull width at half maximum (FWHM) beam size at band center is 3.3\arcmin.
 
@@
 During the first VLA burst with Arecibo coverage (MJD 57643), the PUPPI system failed so data were recorded with {\color{red} xx (Jason?)} at C band.
-No detection was made in that Arecibo data.
+No detection was made in those Arecibo data.
 Overall, there were many more bursts detected at Arecibo than with the VLA and a more detailed analysis of those bursts will be presented in a future paper.
@@
 
-{\color{red} copied from Laura's paper}
-Observations were conducted at an observing frequency of 4.6 to 5.1~GHz.
-The S60mm receiver has a system equivalent flux density of 18 Jy and a full-width half-max (FWHM) beam size of 2.4\arcmin at 4.85~GHz.
-Pulsar search mode data were recorded with the PFFTS backend.
-Total intensity spectra were recorded with a time resolution of 65.5~$\mu$s and a bandwidth of 500~MHz divided into 128 frequency channels.
-Note, the inter-channel DM smearing time for 560~pc cm$^{-3}$\ is $\sim$0.2 msec at 4.6 GHz.
+Effelsberg observations were conducted with the S60mm receiver at an observing frequency of 4.6 to 5.1~GHz.
+Total intensity spectra were recorded by the PFFTS backend in pulsar search mode with a time resolution of 65.5~$\mu$s and 128 frequency channels.
+The system equivalent flux density is 18 Jy and a FWHM beam size of 2.4\arcmin at 4.85~GHz.
 
@@
 We observed \frb\ with the Arcminute MicroKelvin Imager Large Array (AMI-LA; Zwart et al.
-2008) for 3 hours each on four epochs starting at MJDs 57643.3351, 57645.3317, 57648.3352, and 57649.3353.
-Observations were made with the new digital correlator having 4096 channels across a 5 GHz bandwidth between 13--18 GHz with a 1s dump time.
+2008) for 3 hours each on four epochs starting at MJDs 57643, 57645, 57648, and 57649.
+Observations were made with the new digital correlator having 4096 channels across a 5~GHz bandwidth between 13--18~GHz with a 1~s integration time.
 The phase calibrator, J0518+3306, was observed every 12 minutes for about 1.5 minutes.
-The AMI-LA data were binned to eight 0.625 GHz channels and processed (RFI excision and calibration) with a fully-automated pipeline, AMI-REDUCE \citep[e.g.,][]{2013MNRAS.429.3330P}.
+The AMI-LA data were binned to eight 0.625~GHz channels and processed (RFI excision and calibration) with a fully-automated pipeline, AMI-REDUCE \citep[e.g.,][]{2013MNRAS.429.3330P}.
 Daily measurements of 3C48 and 3C286 were used for the absolute flux calibration, which is good to about 10\%.
@@
 Concatenating and imaging the 12 hours of calibrated data with the CASA tasks {\it concat} and {\it clean} also does not yield any significant detection at the FRB location.
-Although the statistical 3sigma upper limit is 60 uJy, extended mJy-level sources in the field cause sidelobe confusion (the AMI-LA angular resolution is $\sim$30 arcsec), and the actual upper limit is larger.
-We introduced artificial point sources at the FRB location using the CASA {\it sm} tool, and found that these sources can be recovered as long as their peak flux densities are more than $\sim$100 uJy.
-Hence, we place an upper limit of 100$\pm$10 uJy on any quiescent or possible radio "afterglow" (on $\sim$days timescale) signal from the FRB.
+Although the statistical $3\sigma$\ upper limit is 60 $\mu$Jy, extended mJy-level sources in the field cause sidelobe confusion (the AMI-LA angular resolution is $\sim$30\arcsec), and the actual upper limit is larger.
+We introduced artificial point sources at the FRB location using the CASA {\it sm} tool, and found that these sources can be recovered as long as their peak flux densities are more than $\sim100\mu$Jy.
+Hence, we place an upper limit of $100\pm10 \mu$Jy on any quiescent or possible radio ''afterglow'' (on $\sim$days timescale) signal from the FRB.
 This limit is close to the flux density measured by the VLA \citep{LOC}.
@@
 
-This simultaneous detection of a burst from roughly 1 to 4~GHz shows that some bursts cover more than an octave of frequency.
-However, this is one of three VLA bursts with coverage by Arecibo, so the other nondetections imply that those bursts had a smaller spectral width.
-In fact, as described in \S \ref{sec:spec}, many of the VLA bursts appear to be fully contained in the band from 2.5 to 3.5~GHz, which implies a much smaller spectral coverage for typical bursts.
+This simultaneous detection of a burst from roughly 1 to 4~GHz shows that some bursts emit over more than an octave of frequency.
+However, this is one of three VLA bursts with L-band coverage by Arecibo, which implies that those bursts had a smaller spectral width.
+However, all three VLA bursts with L-band Arecibo observations were relatively weak, so it is difficult to rule out L-band emission entirely.
+However, as described in \S \ref{sec:spec}, some of the VLA bursts appear to be fully contained in the band from 2.5 to 3.5~GHz, which implies a much smaller spectral coverage for typical bursts.
 
@@
 \begin{center}
- \begin{minipage}{2\columnwidth}
-  \includegraphics[width=0.18\columnwidth]{sgram_57623.png}
-  \includegraphics[width=0.18\columnwidth]{sgram_57633_scan7.png}
-  \includegraphics[width=0.18\columnwidth]{sgram_57633_scan13.png}
-  \includegraphics[width=0.18\columnwidth]{sgram_57638.png}
-  \includegraphics[width=0.18\columnwidth]{sgram_57643.png}
- \end{minipage}
-
- \begin{minipage}{2\columnwidth}
-  \includegraphics[width=0.18\columnwidth]{sgram_57645.png}
-  \includegraphics[width=0.18\columnwidth]{sgram_57646.png}
-  \includegraphics[width=0.18\columnwidth]{sgram_57648.png}
-  \includegraphics[width=0.18\columnwidth]{sgram_57649.png}
- \end{minipage}
-
- \caption{Dynamic spectra (time vs frequency intensity maps) for the nine VLA bursts.
+% \begin{minipage}{2\columnwidth}
+%  \includegraphics[width=0.18\columnwidth]{sgram_57623.png}
+%  \includegraphics[width=0.18\columnwidth]{sgram_57633_scan7.png}
+%  \includegraphics[width=0.18\columnwidth]{sgram_57633_scan13.png}
+%  \includegraphics[width=0.18\columnwidth]{sgram_57638.png}
+%  \includegraphics[width=0.18\columnwidth]{sgram_57643.png}
+% \end{minipage}
+%
+% \begin{minipage}{2\columnwidth}
+%  \includegraphics[width=0.18\columnwidth]{sgram_57645.png}
+%  \includegraphics[width=0.18\columnwidth]{sgram_57646.png}
+%  \includegraphics[width=0.18\columnwidth]{sgram_57648.png}
+%  \includegraphics[width=0.18\columnwidth]{sgram_57649.png}
+% \end{minipage}
+%
+% \caption{Dynamic spectra (time vs frequency intensity maps) for the nine VLA bursts.
 Starting at the top left, they correspond to bursts 57623, 57633.68, 57633.70, 57638, 57643, (bottom left) 57645, 57646, 57648, and 57649.
 Note that bursts are detected in 5~ms images generated from dedispersed visibilities.
+ \includegraphics[width=0.9\columnwidth]{sgram_57623.png}
+ \caption{**Placeholder** Fill in with AO+VLA dynamic spectrum.
  \label{fig:sgram}}
@@
 Figure \ref{fig:sgram} shows the dynamic spectra of all nine bursts detected by the VLA.
-We improved on the initial analysis presented in \citet{LOC} by using a better calibration scheme and optimizing the detection significance over a fine grid of DM ($\Delta \rm{DM}=1 \rm{pc}\ \rm{cm}^{-3}$).
+We improved on the initial analysis presented in \citet{LOC} by using a better calibration scheme and optimizing the detection significance over a fine grid of DM ($\Delta \rm{DM}=1\ \rm{pc}\ \rm{cm}^{-3}$).
 Table \ref{tab:spec} shows the improved burst parameters using this new scheme.
@@
 \hline
-Date                & S$_{\rm{int}}$  & Image SNR & L$_{\rm{int}}$ & DM$_{\rm{opt}}$ & S$_{\rm{peak}}$  & Center & FWHM \\
+Date                & S$_{\rm{int}}$  & Image S/N & E$_{\rm{int}}$ & DM$_{\rm{opt}}$ & S$_{\rm{peak}}$  & Center & FWHM \\
 (MJD)               & (mJy)           &           & ($10^{38}$\ erg) & (pc cm$^{-3})$ & (Jy) & (GHz)  & (MHz) \\ \hline
-57623               & 258             & 38        & 15   & 561 & 0.41                                    & 2.8 & 300 \\
-57633.68            & 2000            & 179       & 120  & 554 & 1.90                                    & 3.2 & 520 \\
-57633.70\tablenotemark{a} & 105       & 15        & 6    & 559 & $>$0.188                                & $<$2.5 & $>$350 \\
-57638               & 65              & 12        & 4    & 556 & 0.07                                    & 3.1 & 410 \\
-57643               & 375             & 100       & 21   & 560 & 0.39                                    & 2.8 & 520 \\
-57645               & 38              & 13        & 2    & 572 & 0.06                                    & 2.8 & 210 \\
-57646\tablenotemark{a} & 69           & 20        & 4    & 555 & $>$0.16                                 & $<$2.5 & $>$400 \\
-57648\tablenotemark{b} & 97           & 25        & 6    & 559 & 0.11                                    & 2.9 & 420 \\
-57649               & 110             & 36        & 6    & 552 & 0.07                                    & 2.9 & 880 \\ \hline
+57623               & 258             & 38        & 7.1  & 561 & 0.41                                    & 2.8 & 300 \\
+57633.68            & 2000            & 179       & 56   & 554 & 1.89                                    & 3.1 & 520 \\
+57633.70\tablenotemark{a} & 105       & 15        & 5.5  & 559 & $>$0.28                                & $<$2.5 & $>$350 \\
+57638               & 65              & 12        & 1.7  & 556 & 0.07                                    & 3.1 & 430 \\
+57643               & 375             & 100       & 11   & 560 & 0.39                                    & 2.8 & 530 \\
+57645               & 38              & 13        & 1.0  & 572 & 0.05                                    & 2.8 & 350 \\
+57646\tablenotemark{a} & 69           & 20        & 3.4  & 555 & $>$0.16                                 & $<$2.5 & $>$380 \\
+57648\tablenotemark{b} & 97           & 25        & 2.6  & 559 & 0.11                                    & 2.8 & 420 \\
+57649               & 110             & 36        & 3.7  & 552 & 0.07                                    & 2.9 & 870 \\ \hline
 \end{tabular}
@@
 Figure \ref{fig:spec} shows the spectrum of the integration and DM that maximizes the burst detection significance.
-After DM optimization, all bursts appear unresolved at the 5~ms time resolution of the VLA data.
-One possible exception is the brightest burst at 57633.68, for which roughly 10\% of the peak flux density is seen in adjacent 5~ms integrations.
+After DM optimization, most bursts appear unresolved at the 5~ms time resolution of the VLA data.
+One exception is the brightest burst at 57633.68, for which roughly 10\% of the peak flux density is seen in adjacent 5~ms integrations.
+**elaborate on 57633.68 time width**
 
@@
  \begin{minipage}{2\columnwidth}
-  \includegraphics[width=0.3\columnwidth]{spec_57623.png}
-  \includegraphics[width=0.3\columnwidth]{spec_57633_scan7.png}
-  \includegraphics[width=0.3\columnwidth]{spec_57633_scan13.png}
+  \includegraphics[width=0.4\columnwidth]{spec_57623.png}
+  \includegraphics[width=0.4\columnwidth]{spec_57633_scan7.png}
+  \includegraphics[width=0.4\columnwidth]{spec_57633_scan13.png}
  \end{minipage}
@@
  \begin{minipage}{2\columnwidth}
-  \includegraphics[width=0.3\columnwidth]{spec_57638.png}
-  \includegraphics[width=0.3\columnwidth]{spec_57643.png}
-  \includegraphics[width=0.3\columnwidth]{spec_57645.png}
+  \includegraphics[width=0.4\columnwidth]{spec_57638.png}
+  \includegraphics[width=0.4\columnwidth]{spec_57643.png}
+  \includegraphics[width=0.4\columnwidth]{spec_57645.png}
  \end{minipage}
@@
  \begin{minipage}{2\columnwidth}
-  \includegraphics[width=0.3\columnwidth]{spec_57646.png}
-  \includegraphics[width=0.3\columnwidth]{spec_57648.png}
-  \includegraphics[width=0.3\columnwidth]{spec_57649.png}
+  \includegraphics[width=0.4\columnwidth]{spec_57646.png}
+  \includegraphics[width=0.4\columnwidth]{spec_57648.png}
+  \includegraphics[width=0.4\columnwidth]{spec_57649.png}
  \end{minipage}
 \caption{Spectra of nine bursts seen by the VLA from 2.5 to 3.5~GHz.
-Orthongonal circular polarizations (RR and LL) are plotted separately and example errorbars are shown at the top right of each panel.
-A binned spectrum is overplotted with a solid line.
+Starting at the top left (moving right and then down), they correspond to bursts on MJDs 57623, 57633.68, 57633.70, 57638, 57643, 57645, 57646, 57648, and 57649.
+Note that bursts are detected in 5~ms images generated from dedispersed visibilities.
+The solid line is a best-fit Gaussian model derived from spectra binned by a factor of 4.
 \label{fig:spec}}
@@
 
-The burst spectra are generally characterized by a broad, Gaussian shape that with strong inter-channel modulation.
-We fit a Gaussian shape to each burst to estimate their characteristic width and peak flux, as summarized in Table \ref{tab:spec}.
+The burst spectra are generally characterized by a broad, Gaussian shape with strong inter-channel modulation.
+We fit a Gaussian shape to each burst to estimate its characteristic width and peak flux (Table \ref{tab:spec}).
 The channel-scale modulation is as high as 100\% (see \S \ref{sec:auto}) and is consistent with an exponential distribution.
@@
 The apparent circular polarization fraction ($(RR-LL)/(RR+LL)$) for the most significant bursts are all less than 3\%.
-\frb\ was located 2.3 arcmin away from pointing center, where systematic effects have been measured as large as 3\% (Perley et al 2016, VLA memo).
+\frb\ was located 2.3\arcmin away from pointing center, where systematic effects have been measured as large as 3\% (Perley et al 2016, VLA memo).
 Given that systematic effects dominate the apparent circular polarization, we conclude that the true fractional circular polarization is less than 3\%.
@@
 \begin{center}
+\includegraphics[width=0.9\columnwidth]{luminosity_cdisn}
+
 \includegraphics[width=0.9\columnwidth]{luminosity_disn}
-\caption{Probability distribution of powerlaw luminosity model for the nine VLA bursts from \frb. The powerlaw is referenced to $L=2\times10^{38}$\ erg.
+\caption{\emph{Top:} Cumulative luminosity distribution with powerlaw fit for the nine VLA bursts from \frb.
+\emph{Bottom:} Probability distribution of luminosity model of the differential luminisotiy distribution.
+The powerlaw is referenced to $L=2\times10^{38}$\ erg.
 \label{fig:lumd}}

### 2016-12-21 timeline.py

@@ -41,8 +41,11 @@ def putdot(ax, i):
 			ax.scatter(pltx, plty, marker='o', s=600, linewidth=2, facecolor='none', edgecolor='k')
 			if int(burst[i]) > 2:
 				ax.scatter(pltx, plty, marker='o', s=900, linewidth=2, facecolor='none', edgecolor='k')
-
-	ax.scatter(pltx, plty, marker=psym[tel[i]], s=100, linewidth=3, facecolor=pcol[tel[i]], edgecolor='none')
+	if tel[i] == 'AMI':
+		s = 250
+	else:
+		s = 80
+	ax.scatter(pltx, plty, marker=psym[tel[i]], s=s, linewidth=3, facecolor=pcol[tel[i]], edgecolor='none')
 
 def d2n(yyyy, mm, dd):
 	return( date2num(datetime.date(yyyy, mm, dd)) )

### 2016-12-21 repeater-vladata.tex
through maura comments. need to redo dm change analysis

@@
 We show that the burst spectra typically have a broad Gaussian shape on the scale of $\sim500$~MHz with fine spectral structure consistent with either scintillation or unresolved intrinsic temporal structure.
-We present the luminosity distribution and temporal statistics for \frb\ and argue that the whole FRB population is adequately described by a single class similar to \frb.
+We present the burst energy distribution and temporal statistics for \frb\ and argue that the whole FRB population is adequately described by a single class similar to \frb.
 We close with thoughts on optimal strategies to make new interferometric localizations of FRBs.
@@
 Its lookback and luminosity distances are 746 and 972 Mpc \citep{2016A&A...594A..13P}, which are orders of magnitude larger than any other millisecond transient.
-This shows that FRBs are more luminous than any other millisecond radio transient, have a significant DM contribution from the IGM, and can be used to probe the IGM and their host galaxy.
+This shows that FRBs are more energetic than any other millisecond radio transient, have a significant DM contribution from the IGM, and can be used to probe the IGM and their host galaxy.
 The promise implied by the first reported FRB \citep{2007Sci...318..777L} is now being realized.
@@
 We can also assume that \frb\ is representative and use it to constrain the physical processes at play in the overall FRB population.
-In this case, we know that FRBs are luminous, but it is not yet clear what process generates the radio bursts themselves \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C}.
+In this case, we know that FRBs are apparently luminous, but it is not yet clear what processes are responsible.
+Possibilities include intrinsic processes, such as coherent, pulsar-like emission \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C}, or extrinsic effects like scintillation \citep{CORDES}.
 The simultaneous \frb\ observing campaign with the VLA, Arecibo, Effelsberg, GBT, and AMI-LA gives a more complete picture of the spectral structure of FRB radio emission.
-FRB repetition also has strong implications for the number of FRB-generating systems in the universe \citep{2016MNRAS.458L..89C}.
+FRB repetition also has strong implications for calculations of their rate of occurrence \citep{2016MNRAS.458L..89C} and comparison to other classes of transient, such as superluminous supernovae \citep{OPT}.
 
@@
  \begin{minipage}{2\columnwidth}
-  \includegraphics[width=0.4\columnwidth]{spec_57623.png}
-  \includegraphics[width=0.4\columnwidth]{spec_57633_scan7.png}
-  \includegraphics[width=0.4\columnwidth]{spec_57633_scan13.png}
+  \includegraphics[width=0.33\columnwidth]{spec_57623.png}
+  \includegraphics[width=0.33\columnwidth]{spec_57633_scan7.png}
+  \includegraphics[width=0.33\columnwidth]{spec_57633_scan13.png}
  \end{minipage}
@@
  \begin{minipage}{2\columnwidth}
-  \includegraphics[width=0.4\columnwidth]{spec_57638.png}
-  \includegraphics[width=0.4\columnwidth]{spec_57643.png}
-  \includegraphics[width=0.4\columnwidth]{spec_57645.png}
+  \includegraphics[width=0.33\columnwidth]{spec_57638.png}
+  \includegraphics[width=0.33\columnwidth]{spec_57643.png}
+  \includegraphics[width=0.33\columnwidth]{spec_57645.png}
  \end{minipage}
@@
  \begin{minipage}{2\columnwidth}
-  \includegraphics[width=0.4\columnwidth]{spec_57646.png}
-  \includegraphics[width=0.4\columnwidth]{spec_57648.png}
-  \includegraphics[width=0.4\columnwidth]{spec_57649.png}
+  \includegraphics[width=0.33\columnwidth]{spec_57646.png}
+  \includegraphics[width=0.33\columnwidth]{spec_57648.png}
+  \includegraphics[width=0.33\columnwidth]{spec_57649.png}
  \end{minipage}
@@
 \subsubsection{Dispersion}
-The initial VLA detections were made by searching a DM grid that allowed inter-DM sensitivity losses up to roughly 10\% \citep[$\Delta DM=10 \rm{pc}\ \rm{cm}^{-3}$][]{2003ApJ...596.1142C}.
+The initial VLA detections were made by searching a DM grid that allowed inter-DM sensitivity losses up to roughly 10\% \citep[$\Delta DM=10\ \rm{pc}\ \rm{cm}^{-3}$][]{2003ApJ...596.1142C}.
 In optimizing detection significance over a fine DM grid, we find optimal DM values range from 552 to 572 pc cm$^{-3}$.
-However, the uncertainty in the peak DM measurement is defined by the DM sensitivity loss curve and the significance of the burst.
+However, the uncertainty in the peak DM measurement is defined by the signal-to-noise of the burst and how this changes with DM.
 
 Given that the apparent DM can potentially change due to intrinsic or extrinsic effects, we developed a more sophisticated system for modeling dispersion.
-We created a generative model to sample the likelihood distribution of a class of dispersion models \citep{2010arXiv1008.4686H}.
-We use the Gaussian shape (see \S \ref{sec:spec}) along the spectral axis and apply a frequency-depndent delay for a given dispersion model.
+We created a generative model to sample the likelihood distribution as a function of DM \citep{2010arXiv1008.4686H}.
+We use the Gaussian shape (see \S \ref{sec:spec}) along the spectral axis and apply a frequency-dependent delay for a given dispersion model.
 The likelihood is directly sampled by calculating the product of probabilities on a per-pixel basis of the 2-dimensional dynamic spectrum.
@@
 Autocorrelation of the burst signal (both temporal and spectral) can be used to infer both intrinsic properties and modulation due to scintillation \citep{CORDES}.
-While VLA spectral resolution of 4~MHz is relatively coarse, the Galactic electron density model predicts a diffractive scintillation bandwidth of {\color{red}Jim: xx MHz at 3~GHz} \citep{2002astro.ph..7156C}.
 Figure \ref{fig:acf} shows the spectral autocorrellation for the strongest burst (MJD 57633.68).
-No excess correlation is found near the channel resolution, which limits the correlation width to less than 4~MHz.
+The is no strong excess correlation near the channel resolution, which limits the correlation width to less than roughly 4~MHz.
+This is broadly consistent with expectations of Galactic diffractive scintillation bandwidth \citep[3--9~MHz near 3~GHz][]{2002astro.ph..7156C}.
 
@@
 \includegraphics[width=0.9\columnwidth]{acf_57633_scan7}
-\caption{ {\color{red} Jim: worth keeping?} The spectral autocorrelation for the burst from \frb\ at MJD 57633.68.
-Blue shows the autocorrelation for the burst and green shows an autocorrelation of a representative spectrum with no burst.
+\caption{The spectral autocorrelation as a function of frequency for the burst from \frb\ at MJD 57633.68.
+Black dots show the autocorrelation for the burst and cyan shows the autocorrelation of a representative spectrum with no burst.
 \label{fig:acf}}
@@
 
-\subsection{Luminosity and Brightness Distribution}
+\subsection{Energy and Brightness Distribution}
 \label{sec:disn}
-Knowing the burst distance, we calculate their mean luminosity across a single 5~ms integration and the 1~GHz bandwidth (Table \ref{tab:spec}).
-The VLA has also shown for the first time that most bursts are contained within the 3~GHz band.
-That means that the mean S-band flux density can be converted to a luminosity in units of ergs with no assumptions about its spectral properties.
+Knowing the burst distance, we calculate their total energy by integrating flux in time and frequency (Table \ref{tab:spec}).
+The VLA has also shown for the first time that many bursts are contained within the 3~GHz band.
+For those bursts, the mean S-band flux density can be converted to an energy with no assumptions about its spectral properties.
 
-This uniform sample of burst luminosities can be used to infer more general properties of \frb.
-We treat the detection probability as a Poisson process with a rate that scales with the luminosity as a powerlaw.
+This uniform sample of burst energies can be used to infer more general properties of \frb.
+We treat the detection probability as a Poisson process with a rate that scales with the energy as a powerlaw.
 Figure \ref{fig:lumd} shows the probability distribution for the powerlaw amplitude and index for the sample of nine VLA bursts.
-The luminosity powerlaw index $1\sigma$\ bounds range from --0.5 to +0.4; for a cumulative luminosity distribution, this corresponds to a powerlaw index of roughly --0.6.
+The energy powerlaw index $1\sigma$\ bounds range from --0.5 to +0.4; for a cumulative energy distribution, this corresponds to a powerlaw index of roughly --0.6.
 The flatness of the distribution is also clear from range of significance of the nine bursts (12 to 179$\sigma$).
 All bursts are much brighter than the sensitivity limit, so the distribution is not affected by a completeness limit.
+**elaborate on limit and completeness**
 
@@
 \includegraphics[width=0.9\columnwidth]{luminosity_disn}
-\caption{\emph{Top:} Cumulative luminosity distribution with powerlaw fit for the nine VLA bursts from \frb.
-\emph{Bottom:} Probability distribution of luminosity model of the differential luminisotiy distribution.
+\caption{\emph{Top:} Cumulative energy distribution with powerlaw fit for the nine VLA bursts from \frb.
+\emph{Bottom:} Probability distribution of energy model of the differential luminisotiy distribution.
 The powerlaw is referenced to $L=2\times10^{38}$\ erg.
@@
 
-Assuming that \frb\ is representative of the overall FRB population, we can use the luminosity distribution of the former to infer properties of the latter.
+Assuming that \frb\ is representative of the overall FRB population, we can use the energy distribution of the former to infer properties of the latter.
 The primary observable of the FRB population is the flux distribution.
-We use a Monte-Carlo technique to simulate an FRB population with a given luminosity and spatial distribution.
+We use a Monte-Carlo technique to simulate an FRB population with a given energy/luminosity and spatial distribution.
 To reproduce the observed FRB sample, we select the brightest $N$\ bursts and fit their fluxes with a powerlaw.
@@
 \subsection{Emission Physics and Burst Energetics}
-The measurement of a redshift to the host of \frb\ allows us to measure the burst luminosity.
+The measurement of a redshift to the host of \frb\ allows us to measure the burst luminosity and energy.
 We now know that \frb\ is detectable with the VLA out to $z=0.7$\ and much farther with Arecibo.
-This confirms the results presented in \citet{LOC}, which quoted a luminosity on the order of $10^{38}$\ erg.
-The more refined analysis presented here measures somewhat higher burst fluxes, so the brightest VLA burst luminosity is now on the order of $10^{40}$\ erg.
+This confirms the results presented in \citet{LOC}, which quoted a energy on the order of $10^{38}$\ erg.
+The more refined analysis presented here results in somewhat higher burst fluxes, so the brightest VLA burst energy ranges as high as $5\times10^{39}$\ erg.
 
-However, the total energy emitted by \frb\ can be orders of magnitude different than this isotropic, apparent luminosity.
+However, the total energy emitted by \frb\ can be orders of magnitude different than this isotropic, apparent energy.
 While the emission process is not yet known, it is neccessarily coherent \citep{2016Natur.531..202S, WEIRD}, so relativistical beaming will amplify the apparent brightness.
 Propagation effects (e.g., scintillation, scattering) can also modify the radio signal in a variety of ways \citep{CORDES} and the duration of the emission in the source frame is not known.
-In any case, the luminosity scale is still larger than any Galactic class of fast radio transient and requires either a new process or dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}.
+In any case, the energy scale is still larger than any Galactic class of fast radio transient and requires either a new process or dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}.
 
@@
 
-**Discussion of luminosity/flux distribution analysis presented in \S \ref{sec:disn})**
+**Discussion of energy/flux distribution analysis presented in \S \ref{sec:disn})**
 
@@
 As mentioned above, this could be caused by intrinsic events (e.g., magnetar outburst) or propagation effects.
-In either case, it demonstrates that \frb\ has a kind of "red spectrum" temporally, in which bursts tend to cluster in time \citep{2016MNRAS.458L..89C}.
-The detection of a burst improves odds of finding more bursts in near-future observations.
+While a detailed analysis of temporal correlation will require more bursts and/or more sophistication, it is clear that \frb\ has significant correlation on short timescales \citep[sometimes called a ''red spectrum'';][]{2016MNRAS.458L..89C}.
+Another way of stating this is that the detection of a burst improves odds of finding more bursts in near-future observations.
 
 If this statistical property describes other FRBs, it weakens previous constraints on repetition \citep{2015MNRAS.454..457P,2015ApJ...807...16L}.
-It is possible that other FRBs have repeating bursts, although calculating a limit requires knowing the temporal powerlaw that defines the repetition.
-Observations of \frb\ have not yet detected enough bursts to reliably measure that index.
-This repetition also implies that there are fewer phyiscal sources of FRBs than implied by the burst detection rate.
+It is possible that other FRBs have repeating bursts, although calculating a limit requires knowing the temporal correlation function that defines the repetition.
+Repetition also implies that there are fewer phyiscal sources of FRBs than implied by the burst detection rate.
 
@@
 Assuming that \frb\ is from the same population as the other FRBs, the measurement of a distance for the host of \frb\ allows us to re-evaluate the cosmic volume and event rate per galaxy for the FRB population.
-The estimated projected FRB rate $R_p$\ understates the true rate by a beaming fraction $\Omega_b$\ \citep[$\sim$10\%;][]{1998MNRAS.298..625T}..
+The estimated projected FRB rate $R_p$\ understates the true rate by a beaming fraction $\Omega_b$\ \citep[$\sim$10\%;][]{1998MNRAS.298..625T}.
 For a comoving volume $V(z)$\ and galaxy number density $\Phi(M)$, the rate per galaxy is $R_{FRB} = R_p /(\Omega_b \Phi(M)V (z))$.
@@
 They assumed that all of the extragalactic component of the DM was caused by the IGM and scaled as $DM\approx z\times1200 \rm{pc}\ \rm{cm}^{-3}$\ \citep{2003ApJ...598L..79I,2004MNRAS.348..999I}.
-They also calculated the number of galaxies by assuming a characteristic $L_*$\ galaxy \citep[corresponding to stellar mass $M_* \approx 1010.66 M$;][]{2012MNRAS.421..621B}.
+They also calculated the number of galaxies by assuming a characteristic $L_*$\ galaxy \citep[corresponding to stellar mass $M_* \approx 1011 M$;][]{2012MNRAS.421..621B}.
 
 Our calculation differs in that we have better estimates of all three parameters.
-First, the projected FRB rate is now believed to be closer to $2\times10^3 \rm{sky}^{-1} \rm{day}^{-1}$\ at high Galactic latitudes and flux densities brighter than 1 Jy ms \citep{2016arXiv161100458L,2016MNRAS.460L..30C}.
-\frb\ is associated with a relatively small galaxy, which are roughly a factor of 100 more abundant \citep[$\Phi(M) \approx 10^{-2} \rm{Mpc}^{-3}$;][]{2007ApJ...665..265F}.
-Finally, the measured distance for FRB 121102 suggests that roughly half of the extragalactic DM is intrinsic to the host and half is from the IGM.
+First, the projected FRB rate is now believed to be closer to $2\times10^3\ \rm{sky}^{-1} \rm{day}^{-1}$\ at high Galactic latitudes and flux densities brighter than 1 Jy ms \citep{2016arXiv161100458L,2016MNRAS.460L..30C, 2016MNRAS.455.2207R}.
+\frb\ is associated with a relatively small galaxy ($5\times10^7$\ Msun), which are roughly a factor of 100 more abundant \citep[$\Phi(M) \approx 10^{-2} \rm{Mpc}^{-3}$;][]{2007ApJ...665..265F}.
+Finally, the measured distance for FRB 121102 suggests that the extragalactic DM has comparable contributions from the IGM and host galaxy.
 
 This reduces the characteristic distance by a factor of two and the volume by an order of magnitude.
-Considering these factors, we assume a characteristic FRB redshift of 0.4 to estimate $R_{FRB} \approx 10^{-4} (0.1/\Omega_b) \rm{galaxy}^{-1} \rm{year}^{-1}$, which is two orders of magnitude lower than previously estimated \citep[assuming isotropic radiation;]{2013Sci...341...53T}.
+Considering these factors, we assume a characteristic redshift of the population that is twice that of \frb\ to estimate $R_{FRB} \approx 10^{-4} (0.1/\Omega_b) \rm{galaxy}^{-1} \rm{year}^{-1}$, which is two orders of magnitude lower than previously estimated \citep[assuming isotropic radiation;]{2013Sci...341...53T}.
 
@@
 \subsection{Observing Strategies}
-As discussed above, \citet{2016MNRAS.458L..89C} note that the FRB repetition implies that the number of FRB-generating sources is smaller than the number of bursts.
+As discussed above, \citet{2016MNRAS.458L..89C} note that the FRB repetition implies that the number of FRB-generating sources is smaller than implied by the number of bursts.
 In some scenarios, this means that there are areas on the sky that may contain no FRBs.
 Wide, shallow surveys are the preferred strategy for blind detection of FRBs.
-However, future efforts to localize FRBs are still most likely to success by targeting known FRBs to catch repetitions.
-Finally, we note that the spectral coverage of bursts from \frb\ are relatively narrow ($<1$~GHz) and change dramatically between bursts.
+However, future efforts to localize FRBs are still most likely to succeed by targeting known FRBs to catch repetitions, assuming that all FRBs repeat.
+Finally, we note that the average spectral coverage of bursts from \frb\ are relatively narrow ($<1$~GHz) and the coverage changes dramatically between bursts.
 Thus, the odds of detecting a burst will improve linearly with bandwidth for bandwidths wider than this characteristic scale.
 
-\subsection{Naming Convention}
-The consistency of \frb\ properties (e.g., luminosity distribution) with the overall population suggests other FRBs likely repeat.
+%\subsection{Naming Convention}
+%The consistency of \frb\ properties (e.g., energy distribution) with the overall population suggests other FRBs likely repeat.
 If so, the current naming convention for FRBs (analogous to cataclysmic supernovae), will likely become uninformative, especially as large FRB survey projects come online \citep{2014SPIE.9145E..22B}.
@@
 
-We presented the first multi-telescope detection (Arecibo and VLA) of a FRB.
+We presented the first multi-telescope detection (Arecibo and VLA) of an FRB.
 By detecting this burst from 1.2 to 4.5~GHz, we have demonstrated that some bursts have broad spectral structure.
@@
 This shows that past constraints on FRB repetition are weaker than previously inferred.
-The combination of relatively narrow spectral structure, flat luminosity and flux distributions, and variable burst rate suggests that repeated observations, wide bandwidth, and large instantaneous field of view all improve the chance of detection.
+The combination of relatively narrow spectral structure, flat energy and flux distributions, and variable burst rate suggests that repeated observations, wide bandwidth, and large instantaneous field of view all improve the chance of detection.
 
@@
 \section*{Acknowledgements}
-This project was supported by the University of California Office of the President under Lab Fees Research Program Award 237863.
 The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc..
+This project was supported by the University of California Office of the President under Lab Fees Research Program Award 237863. MAM is supported by NSF award \#1458952.
 This research made use of Astropy, a community-developed core Python package for Astronomy (Astropy Collaboration, 2013).

### 2017-01-12 repeater-vladata.tex
new figures for latest mcmc fits and new acf. updated captions.

@@
 Note that bursts are detected in 5~ms images generated from dedispersed visibilities.
- \includegraphics[width=0.9\columnwidth]{sgram_57623.png}
+ \includegraphics[width=1.9\columnwidth]{spec_57648.png}
  \caption{**Placeholder** Fill in with AO+VLA dynamic spectrum.
@@
 (MJD)               & (mJy)           &           & ($10^{38}$\ erg) & (pc cm$^{-3})$ & (Jy) & (GHz)  & (MHz) \\ \hline
-57623               & 258             & 38        & 7.1  & 561 & 0.41                                    & 2.8 & 300 \\
-57633.68            & 2000            & 179       & 56   & 554 & 1.89                                    & 3.1 & 520 \\
-57633.70\tablenotemark{a} & 105       & 15        & 5.5  & 559 & $>$0.28                                & $<$2.5 & $>$350 \\
-57638               & 65              & 12        & 1.7  & 556 & 0.07                                    & 3.1 & 430 \\
-57643               & 375             & 100       & 11   & 560 & 0.39                                    & 2.8 & 530 \\
-57645               & 38              & 13        & 1.0  & 572 & 0.05                                    & 2.8 & 350 \\
-57646\tablenotemark{a} & 69           & 20        & 3.4  & 555 & $>$0.16                                 & $<$2.5 & $>$380 \\
-57648\tablenotemark{b} & 97           & 25        & 2.6  & 559 & 0.11                                    & 2.8 & 420 \\
-57649               & 110             & 36        & 3.7  & 552 & 0.07                                    & 2.9 & 870 \\ \hline
+57623               & 258             & 38        & 7.8  & 562.5 & 0.46 & 2.8 & 300 \\
+57633.68            & 2000            & 179       & 65   & 561.4 & 2.20 & 3.2 & 520 \\
+57633.70\tablenotemark{a} & 105       & 15        & 5.9  & 555.4 & $>$0.32 & $<$2.5 & $>$320 \\
+57638               & 65              & 12        & 1.8  & 554.9 & 0.07 & 3.1 & 440 \\
+57643               & 375             & 100       & 13   & 559.3 & 0.44 & 2.8 & 530 \\
+57645               & 38              & 13        & 2.6  & 554.1 & 0.05 & 2.7 & 970 \\
+57646\tablenotemark{a} & 69           & 20        & 3.9  & 568.1 & $>$0.19 & $<$2.5 & $>$360 \\
+57648\tablenotemark{b} & 97           & 25        & 2.9  & 557.8 & 0.11 & 2.8 & 440 \\
+57649               & 110             & 36        & 6.3  & 559.9 & 0.08 & 2.9 & 1400 \\ \hline
 \end{tabular}
@@
  \end{minipage}
-\caption{Spectra of nine bursts seen by the VLA from 2.5 to 3.5~GHz.
+\caption{Spectra and best-fit model for nine bursts seen by the VLA from 2.5 to 3.5~GHz.
 Starting at the top left (moving right and then down), they correspond to bursts on MJDs 57623, 57633.68, 57633.70, 57638, 57643, 57645, 57646, 57648, and 57649.
+The solid line is a best-fit Gaussian model found through probabilistic modeling.
 Note that bursts are detected in 5~ms images generated from dedispersed visibilities.
-The solid line is a best-fit Gaussian model derived from spectra binned by a factor of 4.
 \label{fig:spec}}
@@
 \includegraphics[width=0.9\columnwidth]{dmmodel}
-\caption{DM 95\% confidence intervals of the nine 3~GHz bursts detected by the VLA. The grey band shows the range of DM previously detected at 1.4~GHz ($\pm3$\ pc cm$^{-3}$).
+\caption{DM as a function of time for nine 3~GHz bursts detected by the VLA.
+The 95\% confidence interval on DM is shown with a bar and the dahsed line shows the best-fit DM$=560.5$\ pc cm$^{-3}$ inferred for Arecibo observations at 1.4~GHz (CITE: WEIRD).
 \label{fig:dmmodel}}
@@
 \caption{The spectral autocorrelation as a function of frequency for the burst from \frb\ at MJD 57633.68.
-Black dots show the autocorrelation for the burst and cyan shows the autocorrelation of a representative spectrum with no burst.
+The largest black dots show the autocorrelation for the data, smaller dots show the autocorrelation for the best Gaussian model, and dashed line shows the autocorrelation of an off-burst spectrum.
 \label{fig:acf}}

### 2017-01-26 repeater-vladata.tex
incorporated comments from geoff, uk, shami

@@
 
-\title{The \frb\ Observing Campaign: Multi-Telescope Radio Burst and Implications for the FRB Population}
+\title{The \frb\ Campaign: Multi-Observatory Radio Burst and Implications for the FRB Population}
 %\title{Multi-Telescope Burst Properties and Implications for FRB Population}
@@
 \author[0000-0002-4119-9963]{C.~J.~Law}
-\affiliation{Dept of Astronomy and Radio Astronomy Lab, University of California, Berkeley, CA 94720, USA}
+\affiliation{Department of Astronomy and Radio Astronomy Lab, University of California, Berkeley, CA 94720, USA}
 
@@
 \author{T.~Cantwell}
-\affiliation{University of Manchester, UK}
+\affiliation{Jodrell Bank Centre for Astrophysics, Alan Turning Building, School of Physics \& Astronomy ,The University of Manchester, Oxford Road, Manchester M13 9PL, UK}
 
 \author{S.~H.~Carey}
-\affiliation{University of Cambridge, UK}
+\affiliation{Astrophysics Group, Cavendish Laboratory, 19 J. J. Thomson Avenue, Cambridge CB3 0HE, UK}
 
@@
 \author{K.~Grainge}
-\affiliation{University of Manchester, UK}
+\affiliation{Jodrell Bank Centre for Astrophysics, Alan Turning Building, School of Physics \& Astronomy ,The University of Manchester, Oxford Road, Manchester M13 9PL, UK}
 
@@
 \affiliation{Dept of Astronomy and Radio Astronomy Lab, University of California, Berkeley, CA 94720, USA}
-\affiliation{University of Cambridge, UK}
+\affiliation{Astrophysics Group, Cavendish Laboratory, 19 J. J. Thomson Avenue, Cambridge CB3 0HE, UK}
 
 \author{R.~Fender}
-\affiliation{University of Oxford, UK}
+\affiliation{Centre for Astrophysical Surveys, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford OX1 3RH, UK}
 
@@
 \author{K.~Mooley}
-\affiliation{University of Oxford, UK}
+\affiliation{Centre for Astrophysical Surveys, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford OX1 3RH, UK}
 
@@
 \author{Y.~C.~Perrott}
-\affiliation{University of Cambridge, UK}
+\affiliation{Astrophysics Group, Cavendish Laboratory, 19 J. J. Thomson Avenue, Cambridge CB3 0HE, UK}
 
@@
 \author{N.~Razavi-Ghods}
-\affiliation{University of Cambridge, UK}
+\affiliation{Astrophysics Group, Cavendish Laboratory, 19 J. J. Thomson Avenue, Cambridge CB3 0HE, UK}
 
@@
 \author{A.~Scaife}
-\affiliation{University of Manchester, UK}
+\affiliation{Jodrell Bank Centre for Astrophysics, Alan Turning Building, School of Physics \& Astronomy ,The University of Manchester, Oxford Road, Manchester M13 9PL, UK}
 
@@
 
+\author{P.~K.~G.~Williams}
+\affiliation{Harvard-Smithsonian Center for Astrophysics, Cambridge, MA, USA}
+
 \begin{abstract}
-The millisecond radio transients known as Fast Radio Bursts have recently emerged as a mysterious, new class of astrophysical transient.
-The recent localization of \frb\ has helped identify its host galaxy, measure its distance, and infer intrinsic properties that comment on the broader FRB population.
-We present a detailed analysis of these bursts, including the first simultaneous detection of an FRB with multiple telescopes.
-We show that the burst spectra typically have a broad Gaussian shape on the scale of $\sim500$~MHz with fine spectral structure consistent with either scintillation or unresolved intrinsic temporal structure.
-We present the burst energy distribution and temporal statistics for \frb\ and argue that the whole FRB population is adequately described by a single class similar to \frb.
-We close with thoughts on optimal strategies to make new interferometric localizations of FRBs.
+The recent precision localization of \frb\ has helped identify its host galaxy, measure its distance, and establish it as a member of a truly new class of astrophysical source.
+We present results of the coordinated observing campaign that made this localization, including the first simultaneous detection of an FRB burst with multiple telescopes.
+Of the nine bursts detected by the Very Large Array at 3~GHz, four had simultaneous observing coverage at other observatories, and one was detected by the Arecibo Observatory at 1.4~GHz.
+We show that the burst spectra typically have a broad shape that tapers off on scales of $\sim500$~MHz, plus fine spectral structure on MHz-frequency scales.
+We present the first FRB energy distribution and temporal statistics for \frb\ and argue that the whole FRB population is adequately described by a single class similar to \frb.
+**This source shows that optimal FRB survey strategies should...**
 \end{abstract}
@@
 \section{Introduction}
-Fast Radio Bursts (FRBs) are a new class of millisecond-duration radio transient with a dispersion measure (DM) that implies that they originate outside of our Galaxy.
-At extragalactic (and potentially cosmological) distances, they are not only unusually luminous, but they provide a new tracer of other galaxies and the intergalactic medium (IGM).
-In this way, FRBs have opened a whole new playground in astrophysics \citep[e.g.,][]{2014A&A...562A.137F, 2014ApJ...780L..33M, 2016MNRAS.457..232C}.
-However, that potential has been hamstrung by the lack of a definitive association of an FRB to an extragalactic host.
+Fast Radio Bursts (FRBs) were discovered ten years ago as a millisecond-duration radio transient with an anomalously high dispersion measure \citep[DM; ][]{2007Sci...318..777L}.
+Their large DM implied that they originated outside of our Galaxy, potentially at cosmological distances, and were orders of magnitude more luminous than any other millisecond radio transient \citep{2013Sci...341...53T}.
+Both their energetics and distance have inspired a wide variety of models and astrophysical applications \citep[e.g.,][]{2014ApJ...780L..33M, 2016MNRAS.458L..19C, 2016MNRAS.457..232C}.
+However, that potential was limited by the lack of a definitive association of an FRB to an extragalactic host.
 
-This paper is part of a series that presents the first localization and unambiguous identification of an FRB host \citep{LOC, OPT, EVN}.
+This paper is part of a series that presents the first localization of an FRB and its unambiguous association to an extragalactic host \citep{LOC, OPT, EVN}.
 \frb, also known as the ``repeating FRB'', was first detected in November 2012 by the Arecibo Observatory \citep{2014ApJ...790..101S}.
-In mid 2015, new Arecibo observations revealed a series of bursts at the same DM and sky position demonstrating that FRBs are capable of repetition \citep{2016Natur.531..202S}.
+In mid 2015, new Arecibo observations revealed a series of bursts at the same DM ($\sim559$\ pc cm$^{-3}$) and sky position demonstrating that it repeats \citep{2016Natur.531..202S}.
 Beginning in August of 2015, we made the first of nine detections of \frb\ with the Very Large Array \citep{LOC} and localized it to (RA, Dec) of (05h31m58.70s, +33d08m52.5s) with a precision of 0.1\arcsec.
-Deep radio and optical observing shows that \frb\ is unambiguously associated with a persistent radio and optical source at a redshift of 0.193 \citep{OPT, EVN}.
+Subsequent radio and optical observing discovered more bursts from \frb\ and associated them with a persistent radio and optical source at a redshift of 0.193 with a precision of 0.01" \citep[$\sim40$\ pc]{OPT, EVN}.
 
 \frb\ has now been localized four orders of magnitude better than any other FRB and placed at a cosmological distance.
-Its lookback and luminosity distances are 746 and 972 Mpc \citep{2016A&A...594A..13P}, which are orders of magnitude larger than any other millisecond transient.
-This shows that FRBs are more energetic than any other millisecond radio transient, have a significant DM contribution from the IGM, and can be used to probe the IGM and their host galaxy.
+Its lookback and luminosity distances are 746 and 972 Mpc, assuming a concordance cosmology with parameters given by \citet{2016A&A...594A..13P}.
+This association means that \frb\ is orders of magnitude more luminous than any other millisecond transient and that its DM traces both the host and intergalactic medium \citep{OPT}.
 The promise implied by the first reported FRB \citep{2007Sci...318..777L} is now being realized.
@@
 The confirmation of a cosmological distance for \frb\ could have wide-ranging implications for the FRB population as a whole.
+If \frb\ is representative of all FRBs, then we should expect them to be useful as probes of the intergalactic medium and their host galaxies.
 However, it has not been demonstrated that \frb\ is representative of the overall FRB population.
@@
 An important first step is to demonstrate that the properties of \frb\ are consistent with the significant body of facts for the overall population \citep{2015MNRAS.451.3278M, 2016MPLA...3130013K}.
-The repeating nature of \frb\ provides us with several statistical tests we can use to test this connection.
+The repeating nature of \frb\ provides us with a sample of bursts covering a range of spectral properties, temporal properties, and luminosities that can be used to test its connection to the larger FRB population.
 
-We can also assume that \frb\ is representative and use it to constrain the physical processes at play in the overall FRB population.
+We can also assume that \frb\ is representative of all FRBs and use it to constrain the physical processes at play in the overall FRB population.
 In this case, we know that FRBs are apparently luminous, but it is not yet clear what processes are responsible.
 Possibilities include intrinsic processes, such as coherent, pulsar-like emission \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C}, or extrinsic effects like scintillation \citep{CORDES}.
-The simultaneous \frb\ observing campaign with the VLA, Arecibo, Effelsberg, GBT, and AMI-LA gives a more complete picture of the spectral structure of FRB radio emission.
-FRB repetition also has strong implications for calculations of their rate of occurrence \citep{2016MNRAS.458L..89C} and comparison to other classes of transient, such as superluminous supernovae \citep{OPT}.
+The paper presents an analysis of the spectral properties of VLA bursts implied by simultaneous observing at Effelsberg, GBT, AMI-LA, and Arecibo, including the first simultaneous detection of an FRB at two observatories.
+The repetition of \frb\ also has strong implications for calculations of their rate of occurrence \citep{2016MNRAS.458L..89C} and comparison to other classes of transient, such as superluminous supernovae \citep{OPT}.
 
-Given that FRBs are now known to be useful probes of the IGM, there is even more motivation to make new detections and localizations.
-The relatively faint counterpart to \frb\ argues that direct localization of the radio burst will continue to be the best way to find optical hosts to measure distances.
-Our multi-telescope constraints on burst spectra, measurement of host properties, burst rate estimates, and other properties will inform new strategies for finding FRBs.
+This paper opens by describing the multi-telescope observing campaign and a refined analysis of the nine VLA bursts.
+Next, we present the spectrum of a burst from \frb\ that was simultaneously detected by the VLA and Arecibo observatories.
+**Simulations of temporal statistics and luminosity distribution...** **New estimate of FRB rate and comparison to other transient populations** We close with a discussion of how the \frb\ burst spectra, host properties, burst rate estimates, and other properties inform new strategies for finding FRBs.
 
@@
 In April through May 2016, we conducted a 40~hr campaign at 3~GHz in the C and CnB configurations in coordination with Arecibo.
-We concluded with a new, 40~hr, coordinated campaign from August through September 2016 in the B configuration and during the move to the most extended A configuration.
+We concluded with a 40~hr, coordinated campaign from August through September 2016 in the B configuration and during the move to the most extended A configuration.
 In this last campaign, the first 34 hours of VLA observations were made at 3~GHz, while the last 6 hours were observed at 6~GHz.
-This paper focuses on the data collected at 3~GHz, which include all nine burst detections.
+This paper focuses on the data collected at 3~GHz, which include all nine burst detections and is the widest bandwidth to have ever detected an FRB.
 
-All VLA fast-sampled data were observed with 5~ms sampling, 256 channels, and dual-circular polarization \citep[as in]{2015ApJ...807...16L}.
-To maximize sensitivity, the channel frequency width was set to maintain sensitivity to the known DM of \frb, while maximizing the total bandwidth.
+All VLA fast-sampled data were observed with 5~ms sampling, 256 channels, and dual-circular polarization \citep{2015ApJ...807...16L}.
+The channel frequency width was set to maximize sensitivity to the known DM of \frb, with the largest total bandwidth.
 The total bandwidth at L (1.4~GHz), S (3~GHz), and C (6~GHz) bands was 256~MHz, 1024~MHz, and 2048~MHz, respectively.
@@
 Images were formed for each integration with a DM grid of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$ and a time resampling grid of 5, 10, 20, 40, and 80 ms.
-This DM grid was chosen to maintain 90\% sensitivity to the nominal DM range of 554--560 pc cm$^{-3}$.
-Gain calibration is read from the ''telcal'' system, which uses phase-only calibration on the previous gain calibrator.
+This DM grid was chosen to maintain 90\% sensitivity to the nominal DM range of 540--570 pc cm$^{-3}$, which includes the known \frb\ DM of 559 pc cm$^{-3}$.
+Gain calibration was made from observations of J0555+3948 by the ''telcal'' system, which uses phase-only calibration.
 A flux scale is calculated for each spectral window from an observation on {\color{red}xx (Bryan)} and applied to all burst spectra.
@@
 For each trial DM, integration, and time scale, we form an image and calculate the S/N ratio for the peak pixel in the dirty image.
-Summary statistics are saved for images with S/N higher than 6.4, which captures the tail of the thermal noise distribution without adding significant computational or data volume burden.
-Each image with a pixel with S/N higher than 7.4 is relatively unlikely to be triggered by thermal noise in this configuration, so \rf\ generates a more detailed candidate visualization with an image and spectrum.
-More detailed analysis, including improved calibration and localization, is conducted offline.
+We empirically identified S/N thresholds of 6.4 and 7.4 as useful to capture data quality statistics and candidates for inspection, respectively.
+The higher threshold is relatively unlikely to be triggered by thermal noise in this configuration, so \rf\ generates a more detailed candidate visualization with an image and spectrum.
+All visibilities are recorded so detailed analysis, including improved calibration and localization, can be conducted offline.
 
-Computational notebooks to reproduce the transient detection and localization can be found at \url{https://github.com/caseyjlaw/FRB121102}.
-Time cut-out visibility data are available at \url{https://doi.org/10.7910/DVN/TLDKXG}.
+Computational notebooks to reproduce the transient detection, localization, and analysis presented here can be found at \url{https://github.com/caseyjlaw/FRB121102}.
+Time cut-out visibility data and calibration products are available at \url{https://doi.org/10.7910/DVN/TLDKXG}.
 Original visibility data are available under VLA program codes 16A-459 and 16A-496 and can be downloaded at \url{http://archive.nrao.edu}.
@@
 Each frequency channel was coherently dedispersed to 557 pc cm$^{-3}$, thereby eliminating intra-channel dispersion smearing.
-The ull width at half maximum (FWHM) beam size at band center is 3.3\arcmin.
+The full width at half maximum (FWHM) beam size at band center is 3.3\arcmin.
 
@@
 
-\subsection{AMI}
+\subsection{AMI-LA}
 
@@
 
-We inspected the calibrated visibilities, and did not find any signal above 20 mJy in the 1s samples at and in the vicinity of the detected bursts.
+We inspected the calibrated visibilities, and did not find any signal above 30 mJy in the 1s samples at and in the vicinity of the detected bursts.
 Concatenating and imaging the 12 hours of calibrated data with the CASA tasks {\it concat} and {\it clean} also does not yield any significant detection at the FRB location.
@@
 We introduced artificial point sources at the FRB location using the CASA {\it sm} tool, and found that these sources can be recovered as long as their peak flux densities are more than $\sim100\mu$Jy.
-Hence, we place an upper limit of $100\pm10 \mu$Jy on any quiescent or possible radio ''afterglow'' (on $\sim$days timescale) signal from the FRB.
-This limit is close to the flux density measured by the VLA \citep{LOC}.
+Hence, we place an upper limit of $100\pm10 \mu$Jy on any quiescent or possible radio flaring on $\sim$days timescales from the FRB.
+This limit is similar to the flux density measured by the VLA \citep{LOC}.
 
@@
 
-\subsection{Multi-Telescope Burst Spectrum}
+\subsection{Multi-Observatory Burst Spectrum}
 Four of the VLA bursts were observed simultaneously with Arecibo and AMI-LA (Figure \ref{fig:multi}).
@@
 
-This simultaneous detection of a burst from roughly 1 to 4~GHz shows that some bursts emit over more than an octave of frequency.
-However, this is one of three VLA bursts with L-band coverage by Arecibo, which implies that those bursts had a smaller spectral width.
+This simultaneous detection of a burst from roughly 1.2 to 3.5~GHz shows that some bursts emit over more than an octave of frequency. However, the other three...**
+**
+ is one of three VLA bursts with L-band coverage by Arecibo, which implies that those bursts had a smaller spectral width.
 However, all three VLA bursts with L-band Arecibo observations were relatively weak, so it is difficult to rule out L-band emission entirely.
-However, as described in \S \ref{sec:spec}, some of the VLA bursts appear to be fully contained in the band from 2.5 to 3.5~GHz, which implies a much smaller spectral coverage for typical bursts.
+However, as described in \S \ref{sec:spec}, some of the VLA bursts peak within the band from 2.5 to 3.5~GHz, which implies a much smaller spectral coverage for typical bursts.
 
@@
 We improved on the initial analysis presented in \citet{LOC} by using a better calibration scheme and optimizing the detection significance over a fine grid of DM ($\Delta \rm{DM}=1\ \rm{pc}\ \rm{cm}^{-3}$).
-Table \ref{tab:spec} shows the improved burst parameters using this new scheme.
+Table \ref{tab:spec} shows the optimal image integrated flux density, image S/N, and Stokes V using this new scheme.
+Improved burst spectral parameters are also measured from MCMC modeling of the dynamic spectra.
 
@@
 \centering
-\begin{tabular}{lccccccc}
+\begin{tabular}{lcccccccc}
 \hline
-Date                & S$_{\rm{int}}$  & Image S/N & E$_{\rm{int}}$ & DM$_{\rm{opt}}$ & S$_{\rm{peak}}$  & Center & FWHM \\
-(MJD)               & (mJy)           &           & ($10^{38}$\ erg) & (pc cm$^{-3})$ & (Jy) & (GHz)  & (MHz) \\ \hline
-57623               & 258             & 38        & 7.8  & 562.5 & 0.46 & 2.8 & 300 \\
-57633.68            & 2000            & 179       & 65   & 561.4 & 2.20 & 3.2 & 520 \\
-57633.70\tablenotemark{a} & 105       & 15        & 5.9  & 555.4 & $>$0.32 & $<$2.5 & $>$320 \\
-57638               & 65              & 12        & 1.8  & 554.9 & 0.07 & 3.1 & 440 \\
-57643               & 375             & 100       & 13   & 559.3 & 0.44 & 2.8 & 530 \\
-57645               & 38              & 13        & 2.6  & 554.1 & 0.05 & 2.7 & 970 \\
-57646\tablenotemark{a} & 69           & 20        & 3.9  & 568.1 & $>$0.19 & $<$2.5 & $>$360 \\
-57648\tablenotemark{b} & 97           & 25        & 2.9  & 557.8 & 0.11 & 2.8 & 440 \\
-57649               & 110             & 36        & 6.3  & 559.9 & 0.08 & 2.9 & 1400 \\ \hline
+Date                & S$_{\rm{int}}$  & Image S/N & E$_{\rm{int}}$ & DM$_{\rm{opt}}$ & S$_{\rm{peak}}$ & Center & FWHM & S$_{\rm{V}}$ \\
+(MJD)               & (mJy)           &           & ($10^{38}$\ erg) & (pc cm$^{-3})$ & (mJy) & (GHz)  & (MHz) & (mJy) \\ \hline
+57623.74402686      & 258             & 38        & 7.8  & 562.5 & 460 & 2.8 & 300 & --2 \\
+57633.67986367      & 2000            & 179       & 65   & 561.4 & 2200 & 3.2 & 520 & --44 \\
+57633.69515938\tablenotemark{a} & 105       & 15        & 5.9  & 555.4 & $>$320 & $<$2.5 & $>$320 & +9 \\
+57638.49937435      & 65              & 12        & 1.8  & 554.9 & 70 & 3.1 & 440 & +4 \\
+57643.45730263      & 375             & 100       & 13   & 559.3 & 440 & 2.8 & 530 & +9 \\
+57645.42958602      & 38              & 13        & 2.6  & 554.1 & 50 & 2.7 & 970 & +3 \\
+57646.46600650\tablenotemark{a} & 69           & 20        & 3.9  & 568.1 & $>$190 & $<$2.5 & $>$360 & +3 \\
+57648.43691490\tablenotemark{b} & 97           & 25        & 2.9  & 557.8 & 110 & 2.8 & 440 & +7 \\
+57649.45175697      & 110             & 36        & 6.3  & 559.9 & 80 & 2.9 & 1400 & --1 \\ \hline
 \end{tabular}
@@
 We fit a Gaussian shape to each burst to estimate its characteristic width and peak flux (Table \ref{tab:spec}).
-The channel-scale modulation is as high as 100\% (see \S \ref{sec:auto}) and is consistent with an exponential distribution.
+There is strong structure on smaller scales with channel-to-channel modulation is as high as 100\% (see \S \ref{sec:auto}).
 This introduces a strong bias to the best-fit Gaussian, but these simple fits are reliable enough to show that the typical burst has a spectral width of 500~MHz.
@@
 
-All but two of the best-fit Gaussians are centered inside the 3~GHz band and most appear contained by the 1~GHz wide band.
+All but two of the best-fit Gaussians are centered inside the 3~GHz band and some appear contained by the 1~GHz wide band.
 This is consistent with previous detections of \frb\ by Arecibo, which showed quasi-broadband structure \citep{2016arXiv160308880S} and large variation in the implied spectral index \citep{2014ApJ...790..101S}.
@@
 Uncertainties in each pixel are drawn from a uniform Gaussian error distribution that is estimated from the data.
+
+**Does DM correlate with other spectral/flux properties?**
 
@@
 
+**Does channel-scale structure only appear around 3~GHz?**
+
 \begin{figure}[htb]
@@
 \subsubsection{Circular Polarization}
-The VLA S-band recievers natively measure circular polarization, although for observing efficiency we chose not include polarization calibration procedures.
-Crude constraints on circular polarization are possible by comparing the burst intensity in right and left-hand polarized data products.
-The apparent circular polarization fraction ($(RR-LL)/(RR+LL)$) for the most significant bursts are all less than 3\%.
+The VLA S-band recievers measure circular polarization, although for observing efficiency we choose not to include polarization calibration procedures.
+Constraints on circular polarization are possible since the gain calibrator is a well-known polarization calibrator with little Stokes V flux.
+In that case, the apparent circular polarization fraction is $(RR-LL)/(RR+LL)$, which for the most significant bursts is at most 3\%.
 \frb\ was located 2.3\arcmin away from pointing center, where systematic effects have been measured as large as 3\% (Perley et al 2016, VLA memo).
@@
 \label{sec:temp}
+Geoff comments:
+-- need to clarify that burst rate change is significant
+-- what is "last/first part of campaign"?
+-- not clear how significant nondetections are, since observational details not obvious yet
+
 Burst detections were made very inhomogenously through the larger (63 hours) observing campaign of FRB 121102.
@@
 Assuming that the burst detection probability follows a Poisson distribution, the nondetection in the first half of S-band limits the FRB rate to $\rm{R}<0.1$\ hour$^{-1}$\ (95\% confidence limit).
-The mean detection rate for the last part of the campaign was $\rm{R}=0.3$\ hour$^{-1}$.
+The mean detection rate for the last part of the campaign was $\rm{R}=0.33\pm0.1$\ hour$^{-1}$.
 
-There is weak evidence that the \frb\ burst rate changed during the last 27 hours of the S-band campaign.
+There is weak evidence that the \frb\ burst rate decreased through the last 27 hours of the S-band campaign.
 We modeled the event detection probability as a Poisson probability function, $P_i(\lambda)$, with rate parameter that evolves linearly in time relative to the first VLA burst $\lambda = a + b (\rm{MJD}_i - 57623)$.
 By directly sampling the joint probability distribution, $\prod_{i} P_i$, we can exclude a constant rate with $\sim$85\% confidence.
-This weak constraint is consistent with the broader trend seen by the VLA and Arecibo.
+This weak constraint is consistent with the broader trend of a changing rate seen on month timescales by Arecibo.
 
@@
 We used the Lomb-Scargle periodogram \citep{1982ApJ...263..835S} to search for periodic structure over a wide range of timescales.
-The time series is calculated by binning the burst detection rate per 100~ms \citep[always either 0 or 1, see also]{2011MNRAS.417.1871P}.
+The time series is calculated by binning the burst detection rate per 100~ms \citep[always either 0 or 1, see also][]{2011MNRAS.417.1871P}.
 The spectral power calculated for periods between 0.8 and 80 s shows no power in excess of the typical 95\% confidence bound estimated from shuffled data.
 We verified that simulating nine bursts drawn from a simple rotational model would produce excess power using this approach.
-However, it is difficult to put strong constraints on more complex rotational models \citep[e.g., with wide pulse phase windows or glitches][]{2007ApJ...663..497C, 2013Natur.497..591A}
+However, it is difficult to put strong constraints on more complex rotational models \citep[e.g., with wide pulse phase windows or glitches;][]{2007ApJ...663..497C, 2013Natur.497..591A}
 
@@
 Knowing the burst distance, we calculate their total energy by integrating flux in time and frequency (Table \ref{tab:spec}).
-The VLA has also shown for the first time that many bursts are contained within the 3~GHz band.
-For those bursts, the mean S-band flux density can be converted to an energy with no assumptions about its spectral properties.
+The VLA burst spectra suggest that some bursts may be contained by the 2.5 to 3.5~GHz band.
+If those bursts truly only emit in this band, the mean S-band flux density can be converted to a total energy with no further assumptions about their spectral properties.
 
@@
 
-Assuming that \frb\ is representative of the overall FRB population, we can use the energy distribution of the former to infer properties of the latter.
-The primary observable of the FRB population is the flux distribution.
+Assuming that \frb\ is representative of the overall FRB population, we can use the energy distribution of the former to explore the flux distribution of the latter.
 We use a Monte-Carlo technique to simulate an FRB population with a given energy/luminosity and spatial distribution.
@@
 \subsection{Emission Physics and Burst Energetics}
+**compare to crab GP energy and Tb** **how to scale it up?**
+
 The measurement of a redshift to the host of \frb\ allows us to measure the burst luminosity and energy.
@@
 \subsection{FRB Flux Distribution}
-Doubts were cast on the first FRB detection (``Lorimer burst'') due to its unusually high brightness.
-The lack of lower-significance detections suggested that this burst was unlikely to be part of any astrophysical population.
+The first FRB detection (``Lorimer burst'') was surprising for its unusually high brightness with a lack of lower-significance detections.
 With more detections, it has become clear that the FRB population has a relatively flat flux distribution \citep{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}.
@@
 
+**add error bar?**
 Our calculation differs in that we have better estimates of all three parameters.
@@
 This platform will search a TB/hour data stream in real time in parallel with ongoing VLA observations, potentially detecting and localizing multiple FRBs per year.
-{\color{red} Sarah: any refinement to this statement?}
+{\color{red} Sarah: any refinement to this statement?} VLASS+\rf?
 
@@
 \section*{Acknowledgements}
+% observatories
 The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc..
-This project was supported by the University of California Office of the President under Lab Fees Research Program Award 237863. MAM is supported by NSF award \#1458952.
+% systems
 This research made use of Astropy, a community-developed core Python package for Astronomy (Astropy Collaboration, 2013).
+%individuals
+CJL is supported by the University of California Office of the President under Lab Fees Research Program Award 237863 and NSF award **number**.
+MAM is supported by NSF award \#1458952. 
+KPM's research is supported by the Oxford Centre for Astrophysical Surveys which is funded through the Hintze Family Charitable Foundation.
+AS gratefully acknowledges support from the European Research Council under grant ERC-2012- StG-307215 LODESTONE.
+The AMI-LA telescope gratefully acknowledges support from the European Research Council under grant ERC-2012- StG-307215 LODESTONE, the UK Science and Technology Facilities Council (STFC) and the University of Cambridge.
 

### 2017-01-30 repeater-vladata.tex
author list update
better rephasing bumps fluxes up quite a bit

@@
 \title{The \frb\ Campaign: Multi-Observatory Radio Burst and Implications for the FRB Population}
-%\title{Multi-Telescope Burst Properties and Implications for FRB Population}
 \shorttitle{\frb\ Observing Campaign}
@@
 
-%\author{M.~W.~Abruzzo}
-%\affiliation{Haverford College, 370 Lancaster Ave, Haverford, PA 19041, USA}
-
-%\author{C.~G.~Bassa}
-%\affiliation{ASTRON, Netherlands Institute for Radio Astronomy, Postbus 2, 7990 AA, Dwingeloo, The Netherlands}
-
-%\author{S.~Bogdanov}
-%\affiliation{Columbia Astrophysics Laboratory, Columbia University,  New York, NY 10027, USA}
+\author{C.~G.~Bassa}
+\affiliation{ASTRON, Netherlands Institute for Radio Astronomy, Postbus 2, 7990 AA, Dwingeloo, The Netherlands}
 
@@
 \affiliation{National Radio Astronomy Observatory, Socorro, NM 87801, USA}
-\author{S.~Chatterjee}
-\affiliation{Cornell Center for Astrophysics and Planetary Science and Department of Astronomy, Cornell University, Ithaca, NY 14853, USA}
 
@@
 
+\author{S.~Chatterjee}
+\affiliation{Cornell Center for Astrophysics and Planetary Science and Department of Astronomy, Cornell University, Ithaca, NY 14853, USA}
+
 \author{J.~M.~Cordes}
@@
 \affiliation{National Radio Astronomy Observatory, Socorro, NM 87801, USA}
+
+\author{R.~Fender}
+\affiliation{Centre for Astrophysical Surveys, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford OX1 3RH, UK}
 
@@
 
-\author{R.~Fender}
-\affiliation{Centre for Astrophysical Surveys, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford OX1 3RH, UK}
-
-%\author{V.~M.~Kaspi}
-%\affiliation{Department of Physics and McGill Space Institute, McGill University, 3600 University St., Montreal, QC H3A 2T8, Canada}
-
-%\author{A.~Keimpema}
-%\affiliation{Joint Institute for VLBI ERIC, Postbus 2, 7990 AA Dwingeloo, The Netherlands}
-
-%\author{H.~J.~van~Langevelde}
-%\affiliation{Joint Institute for VLBI ERIC, Postbus 2, 7990 AA Dwingeloo, The Netherlands}
-%\affiliation{Sterrewacht Leiden, Leiden University, Postbus 9513, 2300 RA, Leiden, the Netherlands}
+\author{V.~M.~Kaspi}
+\affiliation{Department of Physics and McGill Space Institute, McGill University, 3600 University St., Montreal, QC H3A 2T8, Canada}
 
@@
 
-%\author[0000-0001-9814-2354]{B.~Marcote}
-%\affiliation{Joint Institute for VLBI ERIC, Postbus 2, 7990 AA Dwingeloo, The Netherlands}
+\author{M.~A.~McLaughlin}
+\affiliation{Department of Physics and Astronomy, West Virginia University, Morgantown, WV 26506, USA}
+\affiliation{Center for Gravitational Waves and Cosmology, West Virginia University, Chestnut Ridge Research Building, Morgantown, WV 26505}
 
@@
 
-\author{M.~A.~McLaughlin}
-\affiliation{Department of Physics and Astronomy, West Virginia University, Morgantown, WV 26506, USA}
-\affiliation{Center for Gravitational Waves and Cosmology, West Virginia University, Chestnut Ridge Research Building, Morgantown, WV 26505}
-
 \author{K.~Mooley}
 \affiliation{Centre for Astrophysical Surveys, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford OX1 3RH, UK}
-
-%\author{Z.~Paragi}
-%\affiliation{Joint Institute for VLBI ERIC, Postbus 2, 7990 AA Dwingeloo, The Netherlands}
 
@@
 
-\author{L.~G.~Spitler}
-\affiliation{Max-Planck-Institut f\"ur Radioastronomie, Auf dem H\"ugel 69, D-53121 Bonn, Germany}
-
 \author{P.~Scholz}
@@
 
-%\author{S.~P.~Tendulkar}
-%\affiliation{Department of Physics and McGill Space Institute, McGill University, 3600 University St., Montreal, QC H3A 2T8, Canada}
+\author{L.~G.~Spitler}
+\affiliation{Max-Planck-Institut f\"ur Radioastronomie, Auf dem H\"ugel 69, D-53121 Bonn, Germany}
+
+\author{S.~P.~Tendulkar}
+\affiliation{Department of Physics and McGill Space Institute, McGill University, 3600 University St., Montreal, QC H3A 2T8, Canada}
 
@@
 In this last campaign, the first 34 hours of VLA observations were made at 3~GHz, while the last 6 hours were observed at 6~GHz.
-This paper focuses on the data collected at 3~GHz, which include all nine burst detections and is the widest bandwidth to have ever detected an FRB.
+This paper focuses on the data collected at 3~GHz, which includes all nine burst detections and is the widest bandwidth to have ever detected an FRB.
 
 All VLA fast-sampled data were observed with 5~ms sampling, 256 channels, and dual-circular polarization \citep{2015ApJ...807...16L}.
-The channel frequency width was set to maximize sensitivity to the known DM of \frb, with the largest total bandwidth.
+The channel frequency width was set to maximize sensitivity to the known DM of \frb with the largest total bandwidth.
 The total bandwidth at L (1.4~GHz), S (3~GHz), and C (6~GHz) bands was 256~MHz, 1024~MHz, and 2048~MHz, respectively.
@@
 \rf\ is a real-time, fast imaging transient search system.
-The current prototype runs on existing, CPU-based hardware of the VLA correlator backend with transient search pipeline software called \emph{rtpipe} \citep[\url{https://github.com/caseyjlaw/rtpipe};][]{2015ApJ...807...16L}.
+The current prototype runs on CPU-based hardware that is normally dedicated to the VLA correlator; for this experiment, it runs the transient search pipeline software called \emph{rtpipe} \citep[\url{https://github.com/caseyjlaw/rtpipe};][]{2015ApJ...807...16L}.
 Images were formed for each integration with a DM grid of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$ and a time resampling grid of 5, 10, 20, 40, and 80 ms.
@@
 We empirically identified S/N thresholds of 6.4 and 7.4 as useful to capture data quality statistics and candidates for inspection, respectively.
-The higher threshold is relatively unlikely to be triggered by thermal noise in this configuration, so \rf\ generates a more detailed candidate visualization with an image and spectrum.
+The higher threshold is relatively unlikely to be triggered by thermal noise in this configuration, so \rf\ generates a more detailed (and computationally intensive) candidate visualization that includes an image and spectrum.
 All visibilities are recorded so detailed analysis, including improved calibration and localization, can be conducted offline.
@@
 
-\subsubsection{Spectra}
+\subsubsection{Spectral Modeling}
 \label{sec:spec}
-Figure \ref{fig:sgram} shows the dynamic spectra of all nine bursts detected by the VLA.
-We improved on the initial analysis presented in \citet{LOC} by using a better calibration scheme and optimizing the detection significance over a fine grid of DM ($\Delta \rm{DM}=1\ \rm{pc}\ \rm{cm}^{-3}$).
-Table \ref{tab:spec} shows the optimal image integrated flux density, image S/N, and Stokes V using this new scheme.
-Improved burst spectral parameters are also measured from MCMC modeling of the dynamic spectra.
+We used two techniques to refine the analysis of the nine VLA radio burst spectra presented in \citet{LOC}.
+First, we improved on the initial analysis by using a better calibration scheme and optimizing the detection significance over a fine grid of DM ($\Delta \rm{DM}=1\ \rm{pc}\ \rm{cm}^{-3}$).
+In Table \ref{tab:spec}, the integrated burst flux density, image S/N, and Stokes V are measured from this optimized detection.
+
+Second, we extracted dynamic radio spectra (time versus frequency) to quantify the spectral structure and dispersion for all nine VLA bursts.
+After calibration and flagging, the visibility phases were rotated to the best-fit location for \frb \citep{LOC}.
+The Stokes I dynamic spectrum were formed by calculating the real part of the mean visibility over all baselines and both polarizations.
+
+The best model of the dynamic spectrum is described in Table \ref{tab:spec}.
+These values were calculated using a generative model to draw 2d dynamic spectra with the MCMC sampler \emph{emcee} \citep{2013PASP..125..306F}.
+The model consisted of a spectral component defined as a Gaussian shape with a temporal component (a delay as a function of frequency) defined by a start time, DM, and width.
+All parameters are calculated at floating point precision and then rounded to channel/integration units before calculating the log-likelihood.
+A flat prior was used over all parameters, including a prior that the Gaussian integral must produce a detection significance higher than 8$\sigma$.
+Since the spectral power shows up to 100\% modulation between channels, we estimate the model error as the maximum of the modeled flux and the measured, off-burst noise value.
+The off-burst noise is estimated from the median absolute deviation of time-frequency data before the start of the burst and is typically 70 mJy.
 
@@
 (MJD)               & (mJy)           &           & ($10^{38}$\ erg) & (pc cm$^{-3})$ & (mJy) & (GHz)  & (MHz) & (mJy) \\ \hline
-57623.74402686      & 258             & 38        & 7.8  & 562.5 & 460 & 2.8 & 300 & --2 \\
-57633.67986367      & 2000            & 179       & 65   & 561.4 & 2200 & 3.2 & 520 & --44 \\
-57633.69515938\tablenotemark{a} & 105       & 15        & 5.9  & 555.4 & $>$320 & $<$2.5 & $>$320 & +9 \\
-57638.49937435      & 65              & 12        & 1.8  & 554.9 & 70 & 3.1 & 440 & +4 \\
-57643.45730263      & 375             & 100       & 13   & 559.3 & 440 & 2.8 & 530 & +9 \\
-57645.42958602      & 38              & 13        & 2.6  & 554.1 & 50 & 2.7 & 970 & +3 \\
-57646.46600650\tablenotemark{a} & 69           & 20        & 3.9  & 568.1 & $>$190 & $<$2.5 & $>$360 & +3 \\
-57648.43691490\tablenotemark{b} & 97           & 25        & 2.9  & 557.8 & 110 & 2.8 & 440 & +7 \\
-57649.45175697      & 110             & 36        & 6.3  & 559.9 & 80 & 2.9 & 1400 & --1 \\ \hline
+57623.74402686      & 194             & 38        & 11 & 562.1 & 700 & 2.8 & 290 & +3 \\ % 7.8  & 562.5 & 460 & 2.8 & 300 & +3 \\
+57633.67986367      & 1500            & 179       & 97 & 561.3 & 3340 & 3.2 & 510 & --35 \\ % 65   & 561.4 & 2200 & 3.2 & 520 & --35 \\
+57633.69515938\tablenotemark{a} & 69  & 15        & 7 & 555.8 & $>$430 & $<$2.5 & 290 & +2 \\ % 5.9  & 555.4 & $>$320 & $<$2.5 & $>$320 & +2 \\
+57638.49937435      & 55              & 12        & 3 & 559.2 & 130 & 3.1 & 420 & +5 \\ % 1.8  & 554.9 & 70 & 3.1 & 440 & +5 \\
+57643.45730263      & 508             & 100       & 34 & 558.7 & 1170 & 2.8 & 510 & --5 \\ % 13   & 559.3 & 440 & 2.8 & 530 & --5 \\
+57645.42958602      & 64              & 13        & 4 & 555.9 & 170 & 2.8 & 380 & +3 \\ % 2.6  & 554.1 & 50 & 2.7 & 970 & +3 \\
+57646.46600650\tablenotemark{a} & 87  & 20        & 10 & 562.7 & $>$420 & $<$2.5 & 420 & +1 \\ % 3.9  & 568.1 & $>$190 & $<$2.5 & $>$360 & +1 \\
+57648.43691490\tablenotemark{b} & 111 & 25        & 7 & 557.4 & 260 & 2.8 & 470 & +9 \\ % 2.9  & 557.8 & 110 & 2.8 & 440 & +9 \\
+57649.45175697      & 167             & 36        & 12 & 559.9 & 290 & 3.0 & 690 & +1 \\ \hline % 6.3  & 559.9 & 80 & 2.9 & 1400 & +1 \\ \hline
 \end{tabular}
@@
 
-Figure \ref{fig:spec} shows the spectrum of the integration and DM that maximizes the burst detection significance.
-After DM optimization, most bursts appear unresolved at the 5~ms time resolution of the VLA data.
-One exception is the brightest burst at 57633.68, for which roughly 10\% of the peak flux density is seen in adjacent 5~ms integrations.
+Figure \ref{fig:spec} shows the spectra
+
 **elaborate on 57633.68 time width**

### 2017-01-31 repeater-vladata.tex
mcmc modeling text ok now

@@
 \label{sec:spec}
-We used two techniques to refine the analysis of the nine VLA radio burst spectra presented in \citet{LOC}.
+We used two techniques to refine the analysis of the nine VLA radio burst spectra described in \citet{LOC}.
 First, we improved on the initial analysis by using a better calibration scheme and optimizing the detection significance over a fine grid of DM ($\Delta \rm{DM}=1\ \rm{pc}\ \rm{cm}^{-3}$).
-In Table \ref{tab:spec}, the integrated burst flux density, image S/N, and Stokes V are measured from this optimized detection.
-
-Second, we extracted dynamic radio spectra (time versus frequency) to quantify the spectral structure and dispersion for all nine VLA bursts.
-After calibration and flagging, the visibility phases were rotated to the best-fit location for \frb \citep{LOC}.
-The Stokes I dynamic spectrum were formed by calculating the real part of the mean visibility over all baselines and both polarizations.
-
-The best model of the dynamic spectrum is described in Table \ref{tab:spec}.
-These values were calculated using a generative model to draw 2d dynamic spectra with the MCMC sampler \emph{emcee} \citep{2013PASP..125..306F}.
-The model consisted of a spectral component defined as a Gaussian shape with a temporal component (a delay as a function of frequency) defined by a start time, DM, and width.
-All parameters are calculated at floating point precision and then rounded to channel/integration units before calculating the log-likelihood.
-A flat prior was used over all parameters, including a prior that the Gaussian integral must produce a detection significance higher than 8$\sigma$.
-Since the spectral power shows up to 100\% modulation between channels, we estimate the model error as the maximum of the modeled flux and the measured, off-burst noise value.
-The off-burst noise is estimated from the median absolute deviation of time-frequency data before the start of the burst and is typically 70 mJy.
+After calibration and flagging, the visibility phases were rotated to the best-fit location to extract a Stokes I spectrum that maximizes the image S/N for each burst.
+Table \ref{tab:spec} gives the resulting integrated burst flux density, image S/N, and Stokes V, while Figure \ref{fig:spec} shows the Stokes I spectra.
+Generally, the burst spectra are characterized by a broad, Gaussian shape with inter-channel modulation as high as 100\%.
 
@@
 
-Figure \ref{fig:spec} shows the spectra
+To better understand the spectra, we extracted dynamic radio spectra (time versus frequency) for 2d modeling with the MCMC sampler \emph{emcee} \citep{2013PASP..125..306F}.
+These dynamic spectral were modeled as the product of a Gaussian shape (amplitude, center, width) and a temporal shape (start time, DM, and width).
+These 6-dimensional fits were sampled with 100 walkers taking 500 steps; typically, the first 200 steps were used to burn in the walkers and were ignored.
+A flat prior was used over all ranges with valid data, including a requirement that the Gaussian integral produce a detection significance higher than 8$\sigma$.
+To represent the strong inter-channel modulation, the model error was estimated as the maximum of the modeled flux and the measured, off-burst noise value (typically 70 mJy per 5~ms integration and 4~MHz channel).
 
-**elaborate on 57633.68 time width**
+The parameters for the best model of the dynamic spectrum are given in Table \ref{tab:spec} and the resulting Gaussian model overlaid on Figure \ref{fig:spec}.
+The typical burst has a spectral width of 500~MHz.
+All but two of the best-fit Gaussians are centered inside the 3~GHz band and some appear contained by the 1~GHz wide band.
+This is consistent with previous detections of \frb\ by Arecibo, which showed quasi-broadband structure \citep{2016arXiv160308880S} and large variation in the implied spectral index \citep{2014ApJ...790..101S}.
+A detailed discussion of high-resolution \frb\ burst spectra seen by the Arecibo Observatory will be presented elsewhere \citep{WEIRD}.
 
@@
 \end{figure*}
-
-The burst spectra are generally characterized by a broad, Gaussian shape with strong inter-channel modulation.
-We fit a Gaussian shape to each burst to estimate its characteristic width and peak flux (Table \ref{tab:spec}).
-There is strong structure on smaller scales with channel-to-channel modulation is as high as 100\% (see \S \ref{sec:auto}).
-This introduces a strong bias to the best-fit Gaussian, but these simple fits are reliable enough to show that the typical burst has a spectral width of 500~MHz.
-% TODO: fit with generative model with 100% amplitude modulations (emcee?)
-
-All but two of the best-fit Gaussians are centered inside the 3~GHz band and some appear contained by the 1~GHz wide band.
-This is consistent with previous detections of \frb\ by Arecibo, which showed quasi-broadband structure \citep{2016arXiv160308880S} and large variation in the implied spectral index \citep{2014ApJ...790..101S}.
-A detailed discussion of high-resolution \frb\ burst spectra seen by the Arecibo Observatory will be presented elsewhere \citep{WEIRD}.
 

### 2017-01-31 repeater-vladata.tex
small table updates

@@
 (MJD)               & (mJy)           &           & ($10^{38}$\ erg) & (pc cm$^{-3})$ & (mJy) & (GHz)  & (MHz) & (mJy) \\ \hline
-57623.74402686      & 194             & 38        & 11 & 562.1 & 700 & 2.8 & 290 & +3 \\ % 7.8  & 562.5 & 460 & 2.8 & 300 & +3 \\
-57633.67986367      & 1500            & 179       & 97 & 561.3 & 3340 & 3.2 & 510 & --35 \\ % 65   & 561.4 & 2200 & 3.2 & 520 & --35 \\
+57623.74402686      & 194             & 38        & 11 & 562.1 & 690 & 2.8 & 290 & +3 \\ % 7.8  & 562.5 & 460 & 2.8 & 300 & +3 \\
+57633.67986367      & 1500            & 179       & 97 & 561.3 & 3350 & 3.2 & 510 & --35 \\ % 65   & 561.4 & 2200 & 3.2 & 520 & --35 \\
 57633.69515938\tablenotemark{a} & 69  & 15        & 7 & 555.8 & $>$430 & $<$2.5 & 290 & +2 \\ % 5.9  & 555.4 & $>$320 & $<$2.5 & $>$320 & +2 \\
-57638.49937435      & 55              & 12        & 3 & 559.2 & 130 & 3.1 & 420 & +5 \\ % 1.8  & 554.9 & 70 & 3.1 & 440 & +5 \\
+57638.49937435      & 55              & 12        & 3 & 558.6 & 130 & 3.1 & 410 & +5 \\ % 1.8  & 554.9 & 70 & 3.1 & 440 & +5 \\
 57643.45730263      & 508             & 100       & 34 & 558.7 & 1170 & 2.8 & 510 & --5 \\ % 13   & 559.3 & 440 & 2.8 & 530 & --5 \\
 57645.42958602      & 64              & 13        & 4 & 555.9 & 170 & 2.8 & 380 & +3 \\ % 2.6  & 554.1 & 50 & 2.7 & 970 & +3 \\
-57646.46600650\tablenotemark{a} & 87  & 20        & 10 & 562.7 & $>$420 & $<$2.5 & 420 & +1 \\ % 3.9  & 568.1 & $>$190 & $<$2.5 & $>$360 & +1 \\
+57646.46600650\tablenotemark{a} & 87  & 20        & 10 & 562.4 & $>$420 & $<$2.5 & 420 & +1 \\ % 3.9  & 568.1 & $>$190 & $<$2.5 & $>$360 & +1 \\
 57648.43691490\tablenotemark{b} & 111 & 25        & 7 & 557.4 & 260 & 2.8 & 470 & +9 \\ % 2.9  & 557.8 & 110 & 2.8 & 440 & +9 \\

### 2017-02-01 repeater-vladata.tex
moved example intro in

@@
 \section{Introduction}
+% cut from vla slsn proposal
+%In the ten years since their discovery, the study of Fast Radio Bursts (FRBs) has followed a winding road.
+The first recognized FRB \citep[the ''Lorimer burst'';][]{2007Sci...318..777L} presented a cosmic curiosity with profound implications.
+That millisecond transient had an anomalously high dispersion \citep[$DM >> DM_{\rm{Milky Way}}$;][]{2002astro.ph..7156C} that implied its source was at cosmological distances ($z\sim0.5$).
+At that distance, the radio bursts must have a luminosity several orders of magnitude larger than the Crab pulsar \citep{2016MNRAS.457..232C}.
+%
+%The FRB story took several dramatic turns with the discovery of a new kind of terrestrial interference \citep[''perytons'';][]{2011ApJ...727...18B} and another 17 FRBs by telescopes around the world \citep{2013Sci...341...53T, 2014ApJ...790..101S, 2015Natur.528..523M}.
+However, FRB models ranged from the profound \citep{2014A&A...562A.137F} to the trivial \citep{2014ApJ...797...70K}.
+The discovery of a repeating FRB by the Arecibo Observatory \citep[\frb;][]{2016Natur.531..202S} demonstrated that at least some FRBs are not cataclysmic.
+It also suggested that the bursts could be an energetic cousin of well-known neutron star radio transient phenomena.
+%
+%At this point, FRB models were poorly constrained by the single-dish telescopes that were discovering the bursts.
+Those observatories localized bursts to an area of tens of arcminutes, which is far too large to identify unique multiwavelength counterparts.
+The \emph{realfast}\footnote{See \url{http://realfast.io}.} project was designed to solve that problem by enabling large-scale interferometric surveys for FRBs with the VLA \citep{2015ApJ...807...16L}.
+As of January 2017, the fruits of that effort have become clear: the VLA has made the first direct localization of an FRB and uniquely associated it with a galaxy at $z=0.1973$\ \citep{2017Natur.541...58C, 2017ApJ...834L...7T}.
+With a cosmological distance firmly established, the initial promise of \citet{2007Sci...318..777L} is beginning to be realized.
+
 Fast Radio Bursts (FRBs) were discovered ten years ago as a millisecond-duration radio transient with an anomalously high dispersion measure \citep[DM; ][]{2007Sci...318..777L}.

### 2017-02-04 repeater-vladata.tex
rework intro, lensing, energy disn

--- 2017-01-31 repeater-vladata.tex
@@
 We present the first FRB energy distribution and temporal statistics for \frb\ and argue that the whole FRB population is adequately described by a single class similar to \frb.
+*population models* *slsn*
 **This source shows that optimal FRB survey strategies should...**
@@
 \section{Introduction}
-Fast Radio Bursts (FRBs) were discovered ten years ago as a millisecond-duration radio transient with an anomalously high dispersion measure \citep[DM; ][]{2007Sci...318..777L}.
-Their large DM implied that they originated outside of our Galaxy, potentially at cosmological distances, and were orders of magnitude more luminous than any other millisecond radio transient \citep{2013Sci...341...53T}.
-Both their energetics and distance have inspired a wide variety of models and astrophysical applications \citep[e.g.,][]{2014ApJ...780L..33M, 2016MNRAS.458L..19C, 2016MNRAS.457..232C}.
+
+Fast Radio Bursts (FRBs) were discovered ten years ago as a millisecond-duration radio transient with an anomalously high dispersion measure \citep[the ``Lorimer burst'';][]{2007Sci...318..777L}.
+Their large dispersion measure (DM) implied that they originated outside of our Galaxy, potentially at cosmological distances, and were orders of magnitude more luminous than any other millisecond radio transient \citep{2013Sci...341...53T}.
+Both their energetics and distance have inspired a wide variety of models and astrophysical applications \citep[e.g.,][]{2014ApJ...780L..33M, 2014ApJ...797...70K, 2016MNRAS.458L..19C, 2016MNRAS.457..232C}.
 However, that potential was limited by the lack of a definitive association of an FRB to an extragalactic host.
 
-This paper is part of a series that presents the first localization of an FRB and its unambiguous association to an extragalactic host \citep{LOC, OPT, EVN}.
+This paper is part of a series based on the first localization of an FRB and its unambiguous association to an extragalactic host \citep{LOC, OPT, EVN}.
 \frb, also known as the ``repeating FRB'', was first detected in November 2012 by the Arecibo Observatory \citep{2014ApJ...790..101S}.
 In mid 2015, new Arecibo observations revealed a series of bursts at the same DM ($\sim559$\ pc cm$^{-3}$) and sky position demonstrating that it repeats \citep{2016Natur.531..202S}.
-Beginning in August of 2015, we made the first of nine detections of \frb\ with the Very Large Array \citep{LOC} and localized it to (RA, Dec) of (05h31m58.70s, +33d08m52.5s) with a precision of 0.1\arcsec.
+Beginning in August of 2015, we made the first of nine detections of \frb\ with the Very Large Array \citep{LOC} and localized it with a precision of 0.1\arcsec.
 Subsequent radio and optical observing discovered more bursts from \frb\ and associated them with a persistent radio and optical source at a redshift of 0.193 with a precision of 0.01" \citep[$\sim40$\ pc]{OPT, EVN}.
@@
 This association means that \frb\ is orders of magnitude more luminous than any other millisecond transient and that its DM traces both the host and intergalactic medium \citep{OPT}.
-The promise implied by the first reported FRB \citep{2007Sci...318..777L} is now being realized.
+If \frb\ is representative of all FRBs, then we should expect them to be useful as probes of the intergalactic medium and their host galaxies.
+Thus, the confirmation of a cosmological distance for \frb\ has begun to fulfil the promise implied by the Lorimer burst.
 
-The confirmation of a cosmological distance for \frb\ could have wide-ranging implications for the FRB population as a whole.
-If \frb\ is representative of all FRBs, then we should expect them to be useful as probes of the intergalactic medium and their host galaxies.
-However, it has not been demonstrated that \frb\ is representative of the overall FRB population.
+Although new models of FRB origin have been already been developed \citep{2017arXiv170104815K, 2017arXiv170102370M, 2017arXiv170104094Z, 2017arXiv170102492D}, we still do not know what causes them. 
+**magnetar birth?**
+Also, it has not been demonstrated that \frb\ is representative of the overall FRB population.
 In fact, the repetition of its bursts is unique among all FRBs \citep{2015MNRAS.454..457P}, so it is natural to ask whether \frb\ is representative.
@@
 We can also assume that \frb\ is representative of all FRBs and use it to constrain the physical processes at play in the overall FRB population.
-In this case, we know that FRBs are apparently luminous, but it is not yet clear what processes are responsible.
-Possibilities include intrinsic processes, such as coherent, pulsar-like emission \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C}, or extrinsic effects like scintillation \citep{CORDES}.
+In this case, we know that FRBs are apparently luminous, but if that is due to intrinsic processes, such as coherent, pulsar-like emission \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C}, or extrinsic effects like scintillation \citep{CORDES}.
 The paper presents an analysis of the spectral properties of VLA bursts implied by simultaneous observing at Effelsberg, GBT, AMI-LA, and Arecibo, including the first simultaneous detection of an FRB at two observatories.
@@
 \includegraphics[width=2\columnwidth]{timeline}
-\caption{Summary of observing coverage and detections of \frb\ during the multi-telescope observing campaign in August and September 2016.
+
+\includegraphics[width=2\columnwidth]{timeline}
+
+\includegraphics[width=2\columnwidth]{timeline}
+\caption{Summary of coverage and detections of \frb\ during the the three VLA observing campaigns
+ %multi-telescope observing campaign in August and September 2016. 
 Symbols show days with observations and circles highlight observations that detected bursts from \frb.
@@
 First, we improved on the initial analysis by using a better calibration scheme and optimizing the detection significance over a fine grid of DM ($\Delta \rm{DM}=1\ \rm{pc}\ \rm{cm}^{-3}$).
-After calibration and flagging, the visibility phases were rotated to the best-fit location to extract a Stokes I spectrum that maximizes the image S/N for each burst.
+After calibration and flagging, the visibility phases were rotated to the best-fit location \citep[(RA, Dec) $=$ (05h31m58.70s, +33d08m52.5s);][]{LOC} to extract a Stokes I spectrum that maximizes the image S/N for each burst.
 Table \ref{tab:spec} gives the resulting integrated burst flux density, image S/N, and Stokes V, while Figure \ref{fig:spec} shows the Stokes I spectra.
@@
 
-**Does channel-scale structure only appear around 3~GHz?**
+%**Does channel-scale structure only appear around 3~GHz?**
 
@@
 The VLA burst spectra suggest that some bursts may be contained by the 2.5 to 3.5~GHz band.
-If those bursts truly only emit in this band, the mean S-band flux density can be converted to a total energy with no further assumptions about their spectral properties.
+If those bursts only emit in this band, the mean S-band flux density can be converted to a total energy with no further assumptions about their spectral properties.
+We proceed under this assumption here and discuss caveats later.
 
-This uniform sample of burst energies can be used to infer more general properties of \frb.
-We treat the detection probability as a Poisson process with a rate that scales with the energy as a powerlaw.
+The \frb\ burst energy distribution is relatively flat, as seen in the range of significance of the nine bursts (12 to 179$\sigma$).
+All bursts are much brighter than the sensitivity limit ($8\sigma$) and data quality are relatively uniform and good, so the distribution is not affected by a completeness limit.
+
+We visualize and model the burst energy distribution in two ways.
+First, the top panel of Figure \ref{fig:lumd} shows the \emph{cumulative} energy distribution and its best-fit powerlaw index of --0.6.
+Second, we use probabilistic modeling to the energies to quantify it directly.
+We model the energy distribution as a Poisson probability with rate function $\lambda=a\ E^\alpha$.
 Figure \ref{fig:lumd} shows the probability distribution for the powerlaw amplitude and index for the sample of nine VLA bursts.
-The energy powerlaw index $1\sigma$\ bounds range from --0.5 to +0.4; for a cumulative energy distribution, this corresponds to a powerlaw index of roughly --0.6.
-The flatness of the distribution is also clear from range of significance of the nine bursts (12 to 179$\sigma$).
-All bursts are much brighter than the sensitivity limit, so the distribution is not affected by a completeness limit.
-**elaborate on limit and completeness**
+The energy powerlaw index $1\sigma$\ bounds range from --0.5 to +0.4.
 
@@
 \emph{Bottom:} Probability distribution of energy model of the differential luminisotiy distribution.
-The powerlaw is referenced to $L=2\times10^{38}$\ erg.
+The powerlaw is referenced to $L=3\times10^{38}$\ erg.
 \label{fig:lumd}}
@@
 \end{figure}
+
+**Does this flat distribution explain FRB flux flatness?**
 
@@
 
+**caveats of S-band assumption**
+
 \section{discussion}
@@
 \subsection{Emission Physics and Burst Energetics}
-**compare to crab GP energy and Tb** **how to scale it up?**
+The refined analysis shows that \frb\ has even higher isotropic energies than previously reported, reaching energies $E_{\rm{max}}\approx10^{40}$\ erg.
+We now know that \frb\ is detectable with the VLA out to $z=0.7$\ and much farther with Arecibo.
+\frb\ has isotropic energies orders of magnitude higher than the strongest Crab pulsar pulses ($\sim10^{35}\ erg) and comparable brightness temperatures \citep[$T_b^{\rm{Crab}}\sim10^{41}$~K versus $T_b^{\rm{FRB 121102}}\sim10^{38}$~K]{2003Natur.422..141H,2014PhRvD..89j3009K}.
+While this emission is coherent and strongly beamed \citep{2016Natur.531..202S, WEIRD}, the energy scale is still larger than any Galactic class of fast radio transient and requires either a new process or dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}.
 
-The measurement of a redshift to the host of \frb\ allows us to measure the burst luminosity and energy.
-We now know that \frb\ is detectable with the VLA out to $z=0.7$\ and much farther with Arecibo.
-This confirms the results presented in \citet{LOC}, which quoted a energy on the order of $10^{38}$\ erg.
-The more refined analysis presented here results in somewhat higher burst fluxes, so the brightest VLA burst energy ranges as high as $5\times10^{39}$\ erg.
-
-However, the total energy emitted by \frb\ can be orders of magnitude different than this isotropic, apparent energy.
-While the emission process is not yet known, it is neccessarily coherent \citep{2016Natur.531..202S, WEIRD}, so relativistical beaming will amplify the apparent brightness.
-Propagation effects (e.g., scintillation, scattering) can also modify the radio signal in a variety of ways \citep{CORDES} and the duration of the emission in the source frame is not known.
-In any case, the energy scale is still larger than any Galactic class of fast radio transient and requires either a new process or dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}.
+Propagation effects (e.g., scintillation, scattering) can also modify the radio signal in a variety of ways and the duration of the emission in the source frame is not known \citep{2016arXiv160505890C}.
+\citet{CORDES} describe a model where plasma lensing near the source of an FRB can magnify radio emission by orders of mangitude.
+That model argues that the simultaneous appearance of a burst from 1.2 to 3.5~GHz requires a lens with the focal frequency be $\gtrsim 3.5$~GHz.
+This gives a constraint on the combination $\frac{\rm DM_0}{a_{\rm AU}^2} \frac{d_{sl}d_{lo}/d_{so}}{1\, \rm kpc} \gtrsim (3.5 / 39.1)^2$, where $DM_0$, $a$, and $d_*$\ are the electron column density of the lens, size of the lens, and lensing distances, respectively.
+A lens placed at $d_{sl}\approx1$~kpc is consistent with typical properties of the interstellar medium.
+Lenses that are influenced by the source would be much nearer to the source $d_{\sl} \ll 1$~kpc, requiring large values of ${\rm DM_0 / a_{\rm AU}^2$.
 
 \subsection{FRB Flux Distribution}
-The first FRB detection (``Lorimer burst'') was surprising for its unusually high brightness with a lack of lower-significance detections.
+The Lorimer burst was surprising for its unusually high brightness with a lack of lower-significance detections.
 With more detections, it has become clear that the FRB population has a relatively flat flux distribution \citep{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}.
@@
 Repetition also implies that there are fewer phyiscal sources of FRBs than implied by the burst detection rate.
+
+FRBs like SGRs? 2016ApJ...826..226K
 

### 2017-02-06 repeater-vladata.tex
flux dist

@@
 
-**Does this flat distribution explain FRB flux flatness?**
-
-Assuming that \frb\ is representative of the overall FRB population, we can use the energy distribution of the former to explore the flux distribution of the latter.
-We use a Monte-Carlo technique to simulate an FRB population with a given energy/luminosity and spatial distribution.
-To reproduce the observed FRB sample, we select the brightest $N$\ bursts and fit their fluxes with a powerlaw.
-The tail of this distribution selects for extrema, such cut-offs in the intrinsic distribution or propagation effects \citep{2015MNRAS.451.3278M, CORDES}.
-Therefore, we sample 100 such populations and measure 95\% bounds on the distribution of cumulative flux distribution index.
-
-These simulations confirm previous work that shows that in many circumstances the cumulative flux distribution follows a Euclidean distribution \citep[index $=-1.5$;][]{2016MNRAS.462..941L}.
-To reproduce the flatness (index $\approx-1$) of the observed flux distribution, we need to incorporate other effects.
-**in progress** (new figure?)
-
-**caveats of S-band assumption**
-
 \section{discussion}
@@
 \subsection{FRB Flux Distribution}
-The Lorimer burst was surprising for its unusually high brightness with a lack of lower-significance detections.
-With more detections, it has become clear that the FRB population has a relatively flat flux distribution \citep{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}.
+The Lorimer burst was surprising for its unusually large flux with a lack of lower-significance detections.
+As more FRBs have been detected, it has become clear that the FRB population has a relatively flat flux distribution \citep[cumulative flux distribution index $-0.5<\alpha<-1$;][]{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}.
 This fact was recently demonstrated by yet another detection of an extremely bright FRB \citep{2016arXiv161105758R}.
 
-**Discussion of energy/flux distribution analysis presented in \S \ref{sec:disn})**
+Assuming that the \frb\ energy distribution is typical of FRBs, we can use it to simulate FRB populations and compare their flux distributions to the observed distribution.
+First, we assume an FRB population that is uniformly distributed in space from redshifts $z1$\ to $z2$.
+For each FRB source, we sample one FRB burst luminosity from a powerlaw distribution and calculate its flux.
+%(uniform for energies from $10^{38}$\ to $10^{40}$; \S \ref{sec:disn} 
+We sample 100 such populations and measure 95\% bounds on the distribution of cumulative flux distribution index.
+We can show that the flux distribution powerlaw is --1.5 for a standard candle-like luminosity distribution at low redshift.
+For distributions out to $z2>1$, the distribution flattens slightly ($sim0.3$ in the index) due to cosmological space distortions.
+For a large ($N\sim2000) population of such bursts, we select the brightest $M\sim20$\ to represent the flux-limited FRB sample of known FRBs...
+The tail of this distribution selects for extrema, such cut-offs in the intrinsic distribution or propagation effects \citep{2015MNRAS.451.3278M, CORDES}. 
+We then fit the flux distribution of those $M$\ events with a powerlaw.
+
+These simulations confirm previous work that shows that...
+The cumulative flux distribution follows a Euclidean distribution \citep[index $=-1.5$;][]{2016MNRAS.462..941L} when...
+Flatness has been observed...
+This requires...
 
@@
 On the other hand, \citep{CORDES} have identified a variety of propagation effects in our own Galaxy that can plausibly modify the observed brightness distribution.
+
+**caveats of S-band assumption**
 

### 2017-02-06 repeater-vladata.tex
figure changed to energy dist

@@
 
-We visualize and model the burst energy distribution in two ways.
-First, the top panel of Figure \ref{fig:lumd} shows the \emph{cumulative} energy distribution and its best-fit powerlaw index of --0.6.
-Second, we use probabilistic modeling to the energies to quantify it directly.
-We model the energy distribution as a Poisson probability with rate function $\lambda=a\ E^\alpha$.
-Figure \ref{fig:lumd} shows the probability distribution for the powerlaw amplitude and index for the sample of nine VLA bursts.
-The energy powerlaw index $1\sigma$\ bounds range from --0.5 to +0.4.
+We visualize perform a simple modeling the burst energy distribution distribution and cumulative distribution in Figure \ref{fig:ed}.
+The energy distribution powerlaw index is --0.5, while its cumulative energy distribution powerlaw index is --0.6.
 
@@
 \begin{center}
-\includegraphics[width=0.9\columnwidth]{luminosity_cdisn}
-
-\includegraphics[width=0.9\columnwidth]{luminosity_disn}
-\caption{\emph{Top:} Cumulative energy distribution with powerlaw fit for the nine VLA bursts from \frb.
-\emph{Bottom:} Probability distribution of energy model of the differential luminisotiy distribution.
-The powerlaw is referenced to $L=3\times10^{38}$\ erg.
-\label{fig:lumd}}
+\includegraphics[width=0.9\columnwidth]{energy_disn}
+\caption{The \frb\ burst energy distribution and cumulative distributino with powerlaw fits \label{fig:ed}}
 \end{center}

### 2017-02-06 repeater-vladata.tex
coverage shows observing bands

--- 2017-02-04 repeater-vladata.tex
@@
 We present the first FRB energy distribution and temporal statistics for \frb\ and argue that the whole FRB population is adequately described by a single class similar to \frb.
-*population models* *slsn*
 **This source shows that optimal FRB survey strategies should...**
@@
 \section{Introduction}
+% cut from vla slsn proposal
+%In the ten years since their discovery, the study of Fast Radio Bursts (FRBs) has followed a winding road.
+The first recognized FRB \citep[the ''Lorimer burst'';][]{2007Sci...318..777L} presented a cosmic curiosity with profound implications.
+That millisecond transient had an anomalously high dispersion \citep[$DM >> DM_{\rm{Milky Way}}$;][]{2002astro.ph..7156C} that implied its source was at cosmological distances ($z\sim0.5$).
+At that distance, the radio bursts must have a luminosity several orders of magnitude larger than the Crab pulsar \citep{2016MNRAS.457..232C}.
+%
+%The FRB story took several dramatic turns with the discovery of a new kind of terrestrial interference \citep[''perytons'';][]{2011ApJ...727...18B} and another 17 FRBs by telescopes around the world \citep{2013Sci...341...53T, 2014ApJ...790..101S, 2015Natur.528..523M}.
+However, FRB models ranged from the profound \citep{2014A&A...562A.137F} to the trivial \citep{2014ApJ...797...70K}.
+The discovery of a repeating FRB by the Arecibo Observatory \citep[\frb;][]{2016Natur.531..202S} demonstrated that at least some FRBs are not cataclysmic.
+It also suggested that the bursts could be an energetic cousin of well-known neutron star radio transient phenomena.
+%
+%At this point, FRB models were poorly constrained by the single-dish telescopes that were discovering the bursts.
+Those observatories localized bursts to an area of tens of arcminutes, which is far too large to identify unique multiwavelength counterparts.
+The \emph{realfast}\footnote{See \url{http://realfast.io}.} project was designed to solve that problem by enabling large-scale interferometric surveys for FRBs with the VLA \citep{2015ApJ...807...16L}.
+As of January 2017, the fruits of that effort have become clear: the VLA has made the first direct localization of an FRB and uniquely associated it with a galaxy at $z=0.1973$\ \citep{2017Natur.541...58C, 2017ApJ...834L...7T}.
+With a cosmological distance firmly established, the initial promise of \citet{2007Sci...318..777L} is beginning to be realized.
 
-Fast Radio Bursts (FRBs) were discovered ten years ago as a millisecond-duration radio transient with an anomalously high dispersion measure \citep[the ``Lorimer burst'';][]{2007Sci...318..777L}.
-Their large dispersion measure (DM) implied that they originated outside of our Galaxy, potentially at cosmological distances, and were orders of magnitude more luminous than any other millisecond radio transient \citep{2013Sci...341...53T}.
-Both their energetics and distance have inspired a wide variety of models and astrophysical applications \citep[e.g.,][]{2014ApJ...780L..33M, 2014ApJ...797...70K, 2016MNRAS.458L..19C, 2016MNRAS.457..232C}.
+Fast Radio Bursts (FRBs) were discovered ten years ago as a millisecond-duration radio transient with an anomalously high dispersion measure \citep[DM; ][]{2007Sci...318..777L}.
+Their large DM implied that they originated outside of our Galaxy, potentially at cosmological distances, and were orders of magnitude more luminous than any other millisecond radio transient \citep{2013Sci...341...53T}.
+Both their energetics and distance have inspired a wide variety of models and astrophysical applications \citep[e.g.,][]{2014ApJ...780L..33M, 2016MNRAS.458L..19C, 2016MNRAS.457..232C}.
 However, that potential was limited by the lack of a definitive association of an FRB to an extragalactic host.
 
-This paper is part of a series based on the first localization of an FRB and its unambiguous association to an extragalactic host \citep{LOC, OPT, EVN}.
+This paper is part of a series that presents the first localization of an FRB and its unambiguous association to an extragalactic host \citep{LOC, OPT, EVN}.
 \frb, also known as the ``repeating FRB'', was first detected in November 2012 by the Arecibo Observatory \citep{2014ApJ...790..101S}.
 In mid 2015, new Arecibo observations revealed a series of bursts at the same DM ($\sim559$\ pc cm$^{-3}$) and sky position demonstrating that it repeats \citep{2016Natur.531..202S}.
-Beginning in August of 2015, we made the first of nine detections of \frb\ with the Very Large Array \citep{LOC} and localized it with a precision of 0.1\arcsec.
+Beginning in August of 2015, we made the first of nine detections of \frb\ with the Very Large Array \citep{LOC} and localized it to (RA, Dec) of (05h31m58.70s, +33d08m52.5s) with a precision of 0.1\arcsec.
 Subsequent radio and optical observing discovered more bursts from \frb\ and associated them with a persistent radio and optical source at a redshift of 0.193 with a precision of 0.01" \citep[$\sim40$\ pc]{OPT, EVN}.
@@
 This association means that \frb\ is orders of magnitude more luminous than any other millisecond transient and that its DM traces both the host and intergalactic medium \citep{OPT}.
+The promise implied by the first reported FRB \citep{2007Sci...318..777L} is now being realized.
+
+The confirmation of a cosmological distance for \frb\ could have wide-ranging implications for the FRB population as a whole.
 If \frb\ is representative of all FRBs, then we should expect them to be useful as probes of the intergalactic medium and their host galaxies.
-Thus, the confirmation of a cosmological distance for \frb\ has begun to fulfil the promise implied by the Lorimer burst.
-
-Although new models of FRB origin have been already been developed \citep{2017arXiv170104815K, 2017arXiv170102370M, 2017arXiv170104094Z, 2017arXiv170102492D}, we still do not know what causes them. 
-**magnetar birth?**
-Also, it has not been demonstrated that \frb\ is representative of the overall FRB population.
+However, it has not been demonstrated that \frb\ is representative of the overall FRB population.
 In fact, the repetition of its bursts is unique among all FRBs \citep{2015MNRAS.454..457P}, so it is natural to ask whether \frb\ is representative.
@@
 We can also assume that \frb\ is representative of all FRBs and use it to constrain the physical processes at play in the overall FRB population.
-In this case, we know that FRBs are apparently luminous, but if that is due to intrinsic processes, such as coherent, pulsar-like emission \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C}, or extrinsic effects like scintillation \citep{CORDES}.
+In this case, we know that FRBs are apparently luminous, but it is not yet clear what processes are responsible.
+Possibilities include intrinsic processes, such as coherent, pulsar-like emission \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C}, or extrinsic effects like scintillation \citep{CORDES}.
 The paper presents an analysis of the spectral properties of VLA bursts implied by simultaneous observing at Effelsberg, GBT, AMI-LA, and Arecibo, including the first simultaneous detection of an FRB at two observatories.
@@
 \includegraphics[width=2\columnwidth]{timeline}
-
-\includegraphics[width=2\columnwidth]{timeline}
-
-\includegraphics[width=2\columnwidth]{timeline}
-\caption{Summary of coverage and detections of \frb\ during the the three VLA observing campaigns
- %multi-telescope observing campaign in August and September 2016. 
+\caption{Summary of late-2016 observing coverage and detections of \frb\ during the multi-telescope observing campaign.
 Symbols show days with observations and circles highlight observations that detected bursts from \frb.
@@
 
-The data presented here were obtained from multiple programs and telescopes, but the central goal was to interferometrically localize \frb\ with the VLA.
-The observing strategy was to ensure simultaneous observing between the VLA and Arecibo observatories and add other observatories on a best-effort basis.
+The data presented here were obtained from multiple programs and telescopes, but focuses on an observing campaign in August/September 2016.
+The central goal was to interferometrically localize \frb\ with the VLA in coordination with Arecibo Observatory, with others included on a best-effort basis.
 We coordinated observing between the VLA, Arecibo, Effelsberg, and AMI-LA telescopes, as shown in Figure \ref{fig:multi}.
@@
 We concluded with a 40~hr, coordinated campaign from August through September 2016 in the B configuration and during the move to the most extended A configuration.
-In this last campaign, the first 34 hours of VLA observations were made at 3~GHz, while the last 6 hours were observed at 6~GHz.
+In the late-2016 campaign, the first 34 hours of VLA observations were made at 3~GHz, while the last 6 hours were observed at 6~GHz.
 This paper focuses on the data collected at 3~GHz, which includes all nine burst detections and is the widest bandwidth to have ever detected an FRB.
@@
 This DM grid was chosen to maintain 90\% sensitivity to the nominal DM range of 540--570 pc cm$^{-3}$, which includes the known \frb\ DM of 559 pc cm$^{-3}$.
-Gain calibration was made from observations of J0555+3948 by the ''telcal'' system, which uses phase-only calibration.
+Gain calibration was made from observations of J0555+3948 by the ``telcal'' system, which uses phase-only calibration.
 A flux scale is calculated for each spectral window from an observation on {\color{red}xx (Bryan)} and applied to all burst spectra.
@@
 Burst detections and localizations were made within hours of data being recorded.
-The transient search starts when data are recorded and proceeds slower than real-time, so we refer to it as ''quasi real-time''.
+The transient search starts when data are recorded and proceeds slower than real-time, so we refer to it as ``quasi real-time''.
 For each trial DM, integration, and time scale, we form an image and calculate the S/N ratio for the peak pixel in the dirty image.
@@
 
-During the joint Arecibo-VLA campaign, Arecibo observed with the L-wide receiver using the PUPPI pulsar backend.
+During the late-2016 campaign, Arecibo observed with the L-wide receiver using the PUPPI pulsar backend.
 The observational frequency range was 1.15 to 1.73~GHz and frequency resolution was 1.5625~MHz.
@@
 
-%\begin{figure}[htb]
-%\begin{center}
-%\includegraphics[width=0.9\columnwidth]{}
-%\caption{
-%\label{fig:}}
-%\end{center}
-%\end{figure}
-
 \subsection{VLA Bursts}
@@
 First, we improved on the initial analysis by using a better calibration scheme and optimizing the detection significance over a fine grid of DM ($\Delta \rm{DM}=1\ \rm{pc}\ \rm{cm}^{-3}$).
-After calibration and flagging, the visibility phases were rotated to the best-fit location \citep[(RA, Dec) $=$ (05h31m58.70s, +33d08m52.5s);][]{LOC} to extract a Stokes I spectrum that maximizes the image S/N for each burst.
+After calibration and flagging, the visibility phases were rotated to the best-fit location to extract a Stokes I spectrum that maximizes the image S/N for each burst.
 Table \ref{tab:spec} gives the resulting integrated burst flux density, image S/N, and Stokes V, while Figure \ref{fig:spec} shows the Stokes I spectra.
@@
 \hline
-Date                & S$_{\rm{int}}$  & Image S/N & E$_{\rm{int}}$ & DM$_{\rm{opt}}$ & S$_{\rm{peak}}$ & Center & FWHM & S$_{\rm{V}}$ \\
+Date                & S$_{\rm{I,int}}$  & Image S/N & E$_{\rm{int}}$ & DM$_{\rm{opt}}$ & S$_{\rm{I,peak}}$ & Center & FWHM & S$_{\rm{V}}$ \\
 (MJD)               & (mJy)           &           & ($10^{38}$\ erg) & (pc cm$^{-3})$ & (mJy) & (GHz)  & (MHz) & (mJy) \\ \hline
@@
 
-%**Does channel-scale structure only appear around 3~GHz?**
+**Does channel-scale structure only appear around 3~GHz?**
 
@@
 -- need to clarify that burst rate change is significant
--- what is "last/first part of campaign"?
 -- not clear how significant nondetections are, since observational details not obvious yet
 
-Burst detections were made very inhomogenously through the larger (63 hours) observing campaign of FRB 121102.
-In the first 30 hours of observing at S-band no bursts were detected, while nine bursts were detected in the last 27 hours of S-band observing.
-The data quality is high, so the inhomogeneous burst distribution shows that the burst detection probability was not stationary.
+Burst detections were made very inhomogenously through the 2016 observing campaign and total 63 hours.
+In the early-2016 campaign, we observed for 30 hours at S-band and no bursts were detected.
+In the late-2016 observing campaign, nine bursts were detected in the last 27 hours of S-band observing.
+Overall, the data quality is uniform and high, so the inhomogeneous burst distribution shows that the burst detection probability was not stationary.
 Assuming that the burst detection probability follows a Poisson distribution, the nondetection in the first half of S-band limits the FRB rate to $\rm{R}<0.1$\ hour$^{-1}$\ (95\% confidence limit).
-The mean detection rate for the last part of the campaign was $\rm{R}=0.33\pm0.1$\ hour$^{-1}$.
+The mean detection rate for S-band observing during the late-2016 campaign was $\rm{R}=0.33\pm0.1$\ hour$^{-1}$.
 
-There is weak evidence that the \frb\ burst rate decreased through the last 27 hours of the S-band campaign.
+There is weak evidence that the \frb\ burst rate decreased through the S-band observing in the late-2016 campaign.
 We modeled the event detection probability as a Poisson probability function, $P_i(\lambda)$, with rate parameter that evolves linearly in time relative to the first VLA burst $\lambda = a + b (\rm{MJD}_i - 57623)$.
@@
 
-During the August--September 2016 observing campaign, the typical observation lasted about two hours and was sampled with a 5~ms cadence.
+During the late-2016 observing campaign, the typical observation lasted about two hours and was sampled with a 5~ms cadence.
 We used the Lomb-Scargle periodogram \citep{1982ApJ...263..835S} to search for periodic structure over a wide range of timescales.
@@
 The VLA burst spectra suggest that some bursts may be contained by the 2.5 to 3.5~GHz band.
-If those bursts only emit in this band, the mean S-band flux density can be converted to a total energy with no further assumptions about their spectral properties.
-We proceed under this assumption here and discuss caveats later.
+If those bursts truly only emit in this band, the mean S-band flux density can be converted to a total energy with no further assumptions about their spectral properties.
 
-The \frb\ burst energy distribution is relatively flat, as seen in the range of significance of the nine bursts (12 to 179$\sigma$).
-All bursts are much brighter than the sensitivity limit ($8\sigma$) and data quality are relatively uniform and good, so the distribution is not affected by a completeness limit.
-
-We visualize and model the burst energy distribution in two ways.
-First, the top panel of Figure \ref{fig:lumd} shows the \emph{cumulative} energy distribution and its best-fit powerlaw index of --0.6.
-Second, we use probabilistic modeling to the energies to quantify it directly.
-We model the energy distribution as a Poisson probability with rate function $\lambda=a\ E^\alpha$.
+This uniform sample of burst energies can be used to infer more general properties of \frb.
+We treat the detection probability as a Poisson process with a rate that scales with the energy as a powerlaw.
 Figure \ref{fig:lumd} shows the probability distribution for the powerlaw amplitude and index for the sample of nine VLA bursts.
-The energy powerlaw index $1\sigma$\ bounds range from --0.5 to +0.4.
+The energy powerlaw index $1\sigma$\ bounds range from --0.5 to +0.4; for a cumulative energy distribution, this corresponds to a powerlaw index of roughly --0.6.
+The flatness of the distribution is also clear from range of significance of the nine bursts (12 to 179$\sigma$).
+All bursts are much brighter than the sensitivity limit, so the distribution is not affected by a completeness limit.
+**elaborate on limit and completeness**
 
@@
 \emph{Bottom:} Probability distribution of energy model of the differential luminisotiy distribution.
-The powerlaw is referenced to $L=3\times10^{38}$\ erg.
+The powerlaw is referenced to $L=2\times10^{38}$\ erg.
 \label{fig:lumd}}
@@
 \end{figure}
-
-**Does this flat distribution explain FRB flux flatness?**
 
@@
 
-**caveats of S-band assumption**
-
 \section{discussion}
@@
 \subsection{Emission Physics and Burst Energetics}
-The refined analysis shows that \frb\ has even higher isotropic energies than previously reported, reaching energies $E_{\rm{max}}\approx10^{40}$\ erg.
+**compare to crab GP energy and Tb** **how to scale it up?**
+
+The measurement of a redshift to the host of \frb\ allows us to measure the burst luminosity and energy.
 We now know that \frb\ is detectable with the VLA out to $z=0.7$\ and much farther with Arecibo.
-\frb\ has isotropic energies orders of magnitude higher than the strongest Crab pulsar pulses ($\sim10^{35}\ erg) and comparable brightness temperatures \citep[$T_b^{\rm{Crab}}\sim10^{41}$~K versus $T_b^{\rm{FRB 121102}}\sim10^{38}$~K]{2003Natur.422..141H,2014PhRvD..89j3009K}.
-While this emission is coherent and strongly beamed \citep{2016Natur.531..202S, WEIRD}, the energy scale is still larger than any Galactic class of fast radio transient and requires either a new process or dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}.
+This confirms the results presented in \citet{LOC}, which quoted a energy on the order of $10^{38}$\ erg.
+The more refined analysis presented here results in somewhat higher burst fluxes, so the brightest VLA burst energy ranges as high as $5\times10^{39}$\ erg.
 
-Propagation effects (e.g., scintillation, scattering) can also modify the radio signal in a variety of ways and the duration of the emission in the source frame is not known \citep{2016arXiv160505890C}.
-\citet{CORDES} describe a model where plasma lensing near the source of an FRB can magnify radio emission by orders of mangitude.
-That model argues that the simultaneous appearance of a burst from 1.2 to 3.5~GHz requires a lens with the focal frequency be $\gtrsim 3.5$~GHz.
-This gives a constraint on the combination $\frac{\rm DM_0}{a_{\rm AU}^2} \frac{d_{sl}d_{lo}/d_{so}}{1\, \rm kpc} \gtrsim (3.5 / 39.1)^2$, where $DM_0$, $a$, and $d_*$\ are the electron column density of the lens, size of the lens, and lensing distances, respectively.
-A lens placed at $d_{sl}\approx1$~kpc is consistent with typical properties of the interstellar medium.
-Lenses that are influenced by the source would be much nearer to the source $d_{\sl} \ll 1$~kpc, requiring large values of ${\rm DM_0 / a_{\rm AU}^2$.
+However, the total energy emitted by \frb\ can be orders of magnitude different than this isotropic, apparent energy.
+While the emission process is not yet known, it is neccessarily coherent \citep{2016Natur.531..202S, WEIRD}, so relativistical beaming will amplify the apparent brightness.
+Propagation effects (e.g., scintillation, scattering) can also modify the radio signal in a variety of ways \citep{CORDES} and the duration of the emission in the source frame is not known.
+In any case, the energy scale is still larger than any Galactic class of fast radio transient and requires either a new process or dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}.
 
 \subsection{FRB Flux Distribution}
-The Lorimer burst was surprising for its unusually high brightness with a lack of lower-significance detections.
+The first FRB detection (``Lorimer burst'') was surprising for its unusually high brightness with a lack of lower-significance detections.
 With more detections, it has become clear that the FRB population has a relatively flat flux distribution \citep{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}.
@@
 As mentioned above, this could be caused by intrinsic events (e.g., magnetar outburst) or propagation effects.
-While a detailed analysis of temporal correlation will require more bursts and/or more sophistication, it is clear that \frb\ has significant correlation on short timescales \citep[sometimes called a ''red spectrum'';][]{2016MNRAS.458L..89C}.
+While a detailed analysis of temporal correlation will require more bursts and/or more sophistication, it is clear that \frb\ has significant correlation on short timescales \citep[sometimes called a ``red spectrum'';][]{2016MNRAS.458L..89C}.
 Another way of stating this is that the detection of a burst improves odds of finding more bursts in near-future observations.
@@
 Repetition also implies that there are fewer phyiscal sources of FRBs than implied by the burst detection rate.
-
-FRBs like SGRs? 2016ApJ...826..226K
 

### 2017-02-06 timeline.py

@@ -9,7 +9,7 @@ from pylab import date2num
 from astropy import time
 
 # parse obs data
-(obs, t1, t2, tel, burst) = loadtxt('obs_data.txt', dtype=str, unpack=True)
+(obs, t1, t2, tel, burst, band) = loadtxt('obs_data.txt', dtype=str, unpack=True)
 for i in range(len(obs)):
 	if obs[i] == 'mjd':
 		t1c = time.Time(float(t1[i]), format='mjd').iso
@@ -36,16 +36,17 @@ def putdot(ax, i):
 	pltx = obsdate[i]
 	plty = offset[tel[i]]
 	if int(burst[i]):
-		ax.scatter(pltx, plty, marker='o', s=300, linewidth=2, facecolor='none', edgecolor='k')
+		ax.scatter(pltx, plty, marker='o', s=400, linewidth=2, facecolor='none', edgecolor='k')
 		if int(burst[i]) > 1:
-			ax.scatter(pltx, plty, marker='o', s=600, linewidth=2, facecolor='none', edgecolor='k')
+			ax.scatter(pltx, plty, marker='o', s=800, linewidth=2, facecolor='none', edgecolor='k')
 			if int(burst[i]) > 2:
-				ax.scatter(pltx, plty, marker='o', s=900, linewidth=2, facecolor='none', edgecolor='k')
+				ax.scatter(pltx, plty, marker='o', s=1200, linewidth=2, facecolor='none', edgecolor='k')
 	if tel[i] == 'AMI':
 		s = 250
 	else:
 		s = 80
-	ax.scatter(pltx, plty, marker=psym[tel[i]], s=s, linewidth=3, facecolor=pcol[tel[i]], edgecolor='none')
+	ax.text(pltx, plty, s=band[i], verticalalignment='center', horizontalalignment='center')
+#	ax.scatter(pltx, plty, marker=psym[tel[i]], s=s, linewidth=3, facecolor=pcol[tel[i]], edgecolor='none')
 
 def d2n(yyyy, mm, dd):
 	return( date2num(datetime.date(yyyy, mm, dd)) )
@@ -74,11 +75,11 @@ ax.set_ylim( (-0.4, 3.4) )
 ax.tick_params(labelright='off', labelleft='off')
 
 # boxes for simultaneous coverage of VLA bursts
[…]

### 2017-02-06 repeater-vladata.tex
clean up for tex

@@
 We now know that \frb\ is detectable with the VLA out to $z=0.7$\ and much farther with Arecibo.
-\frb\ has isotropic energies orders of magnitude higher than the strongest Crab pulsar pulses ($\sim10^{35}\ erg) and comparable brightness temperatures \citep[$T_b^{\rm{Crab}}\sim10^{41}$~K versus $T_b^{\rm{FRB 121102}}\sim10^{38}$~K]{2003Natur.422..141H,2014PhRvD..89j3009K}.
+\frb\ has isotropic energies orders of magnitude higher than the strongest Crab pulsar pulses ($\sim10^{35}$~erg) and comparable brightness temperatures \citep[$T_b^{\rm{Crab}}\sim10^{41}$~K versus $T_b^{\rm{FRB 121102}}\sim10^{38}$~K;][]{2003Natur.422..141H,2014PhRvD..89j3009K}.
 While this emission is coherent and strongly beamed \citep{2016Natur.531..202S, WEIRD}, the energy scale is still larger than any Galactic class of fast radio transient and requires either a new process or dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}.
@@
 That model argues that the simultaneous appearance of a burst from 1.2 to 3.5~GHz requires a lens with the focal frequency be $\gtrsim 3.5$~GHz.
-This gives a constraint on the combination $\frac{\rm DM_0}{a_{\rm AU}^2} \frac{d_{sl}d_{lo}/d_{so}}{1\, \rm kpc} \gtrsim (3.5 / 39.1)^2$, where $DM_0$, $a$, and $d_*$\ are the electron column density of the lens, size of the lens, and lensing distances, respectively.
+This gives a constraint on the combination
+$$\frac{\rm DM_0}{a_{\rm AU}^2} \frac{d_{sl}d_{lo}/d_{so}}{1\, \rm kpc} \gtrsim (3.5 / 39.1)^2$$
+where $DM_0$, $a$, and $d_*$\ are the electron column density of the lens, size of the lens, and lensing distances, respectively.
 A lens placed at $d_{sl}\approx1$~kpc is consistent with typical properties of the interstellar medium.
-Lenses that are influenced by the source would be much nearer to the source $d_{\sl} \ll 1$~kpc, requiring large values of ${\rm DM_0 / a_{\rm AU}^2$.
+Lenses that are influenced by the source would be much nearer to the source $d_{\sl} \ll 1$~kpc, requiring large values of $\frac{\rm DM_0}{a_{\rm AU}^2}$.
 
@@
 For distributions out to $z2>1$, the distribution flattens slightly ($sim0.3$ in the index) due to cosmological space distortions.
-For a large ($N\sim2000) population of such bursts, we select the brightest $M\sim20$\ to represent the flux-limited FRB sample of known FRBs...
+For a large ($N\sim2000$) population of such bursts, we select the brightest $M\sim20$\ to represent the flux-limited FRB sample of known FRBs...
 The tail of this distribution selects for extrema, such cut-offs in the intrinsic distribution or propagation effects \citep{2015MNRAS.451.3278M, CORDES}. 

### 2017-02-08 repeater-vladata.tex
new cumulative plot
energy dist model makes sense

@@
 Knowing the burst distance, we calculate their total energy by integrating flux in time and frequency (Table \ref{tab:spec}).
-The VLA burst spectra suggest that some bursts may be contained by the 2.5 to 3.5~GHz band.
-If those bursts only emit in this band, the mean S-band flux density can be converted to a total energy with no further assumptions about their spectral properties.
+Some VLA burst spectra seem to be contained by the 2.5 to 3.5~GHz band and most of them seem to have Gaussian envelopes that are well modeled by the emission within the 2.5 to 3.5~GHz band.
+Assuming that the Gaussian shape defines the emission window, the mean S-band flux density can be converted to a total energy with no further assumptions about their spectral properties.
 We proceed under this assumption here and discuss caveats later.
 
-The \frb\ burst energy distribution is relatively flat, as seen in the range of significance of the nine bursts (12 to 179$\sigma$).
-All bursts are much brighter than the sensitivity limit ($8\sigma$) and data quality are relatively uniform and good, so the distribution is not affected by a completeness limit.
-
-We visualize perform a simple modeling the burst energy distribution distribution and cumulative distribution in Figure \ref{fig:ed}.
-The energy distribution powerlaw index is --0.5, while its cumulative energy distribution powerlaw index is --0.6.
+The \frb\ burst energy distribution (Figure \ref{fig:ed}) is relatively flat, as seen in the range of significance of the nine bursts (12 to 179$\sigma$).
+We modeled the differential energy distribution, $dN/d\log{E}$, as a Poisson probability distribution with a rate function $\lambda\proptoE^{\alpha}$.
+Using a maximum likelihood technique, we estimate the best powerlaw index of $\alpha=-0.6^{+0.4}_{-0.6}$.
+This is equivalent to a differential energy distribution, $dN/dE \propto E^{-1.6}$.
+Note that all VLA bursts are much brighter than the sensitivity limit ($8\sigma$) and data quality are relatively uniform and good, so the distribution is not affected by a completeness limit.
 
@@
 \includegraphics[width=0.9\columnwidth]{energy_disn}
-\caption{The \frb\ burst energy distribution and cumulative distributino with powerlaw fits \label{fig:ed}}
+\caption{Dots and solid line show the  \frb\ burst energy cumulative distribution.
+The dashed line shows the best fit from a maximum likelihood analysis using the powerlaw model $dN/d\log{E} \propto E^{\alpha}$.
+The 95\% bounds on the best-fit powerlaw index is $\alpha=-1.6^{+0.4}_{-0.6}$.
+\label{fig:ed}}
 \end{center}

### 2017-02-09 repeater-vladata.tex
working in new figs and text on frb pop sim

@@
 \affiliation{Department of Astronomy and Radio Astronomy Lab, University of California, Berkeley, CA 94720, USA}
+
+\author{R.~S.~Wharton}
+\affiliation{Cornell Center for Astrophysics and Planetary Science and Department of Astronomy, Cornell University, Ithaca, NY 14853, USA}
 
@@
 \affiliation{University of Cambridge, UK}
-
-\author{R.~S.~Wharton}
-\affiliation{Cornell Center for Astrophysics and Planetary Science and Department of Astronomy, Cornell University, Ithaca, NY 14853, USA}
 
@@
 Assuming that the Gaussian shape defines the emission window, the mean S-band flux density can be converted to a total energy with no further assumptions about their spectral properties.
-We proceed under this assumption here and discuss caveats later.
+We proceed under this assumption here and discuss caveats is \S \ref{sec:disc}.
 
-The \frb\ burst energy distribution (Figure \ref{fig:ed}) is relatively flat, as seen in the range of significance of the nine bursts (12 to 179$\sigma$).
-We modeled the differential energy distribution, $dN/d\log{E}$, as a Poisson probability distribution with a rate function $\lambda\proptoE^{\alpha}$.
-Using a maximum likelihood technique, we estimate the best powerlaw index of $\alpha=-0.6^{+0.4}_{-0.6}$.
-This is equivalent to a differential energy distribution, $dN/dE \propto E^{-1.6}$.
-Note that all VLA bursts are much brighter than the sensitivity limit ($8\sigma$) and data quality are relatively uniform and good, so the distribution is not affected by a completeness limit.
+Figure \ref{fig:ed} shows the \frb\ burst energy cumulative distribution and best-fit model.
+We modeled the differential energy distribution, $dN/d\log{E}$, as a Poisson probability distribution with a rate function $\lambda\propto E^{\alpha}$.
+Using a maximum likelihood technique, we estimate the best powerlaw index of $\alpha=-0.6^{+0.4}_{-0.6}$, which is equivalent to a $dN/dE$\ powerlaw index of --1.6.
+This model assumes a completeness limit for a luminosity equivalent to an $8\sigma$\ flux density limit.
+This is consistent with the high and uniform data quality and the false positive rate in this observing campaign.
 
@@
 The dashed line shows the best fit from a maximum likelihood analysis using the powerlaw model $dN/d\log{E} \propto E^{\alpha}$.
-The 95\% bounds on the best-fit powerlaw index is $\alpha=-1.6^{+0.4}_{-0.6}$.
+The 95\% bounds on the best-fit powerlaw index is $\alpha=-0.6^{+0.4}_{-0.6}$.
 \label{fig:ed}}
@@
 \section{discussion}
-
+\label{sec:disc}
 \subsection{Emission Physics and Burst Energetics}
@@
 \frb\ has isotropic energies orders of magnitude higher than the strongest Crab pulsar pulses ($\sim10^{35}$~erg) and comparable brightness temperatures \citep[$T_b^{\rm{Crab}}\sim10^{41}$~K versus $T_b^{\rm{FRB 121102}}\sim10^{38}$~K;][]{2003Natur.422..141H,2014PhRvD..89j3009K}.
-While this emission is coherent and strongly beamed \citep{2016Natur.531..202S, WEIRD}, the energy scale is still larger than any Galactic class of fast radio transient and requires either a new process or dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}.
+While this emission is coherent and strongly beamed \citep{2016Natur.531..202S, WEIRD}, the energy scale is still larger than any known Galactic radio transient and requires either a new process or dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}.
+
+-- Self-organized criticality in the sun. energy powerlaw=-1.7 \citep{2011SoPh..274...99A}
+-- **Similarity to magnetar energy distribution**
 
@@
 The Lorimer burst was surprising for its unusually large flux with a lack of lower-significance detections.
-As more FRBs have been detected, it has become clear that the FRB population has a relatively flat flux distribution \citep[cumulative flux distribution index $-0.5<\alpha<-1$;][]{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}.
-This fact was recently demonstrated by yet another detection of an extremely bright FRB \citep{2016arXiv161105758R}.
+As more FRBs have been detected, we continue to be surprised by the apparent brightness of FRB \citep{2016arXiv161105758R}.
+This perception has been validated with analysis of the FRB fluence distribution, which when modeled as a powerlaw, $dN/dF \propto F^{\alpha}$, has $-0.5<\alpha<-0.9$ \citep{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}.
+For a uniform distribution of sources with a single luminosity, the nominal flux distribution index shoudl be --1.5 \citep[the ``Euclidean'' distribution, e.g.,][]{2016MNRAS.462..941L}.
 
-Assuming that the \frb\ energy distribution is typical of FRBs, we can use it to simulate FRB populations and compare their flux distributions to the observed distribution.
+The energy distribution of \frb\ bursts has also produced some surprises.
+Although the source clearly has episodes of activity (Section \label{sec:temp}), the nine bursts were detected with a wide range of significance (12 to 179$\sigma$).
+If all FRBs luminosities are drawn from a distribution (rather than having a single luminosity), then the flux distribution will be modified by that underlying distribution and its interplay with redshift space distortions of a cosmological population.
+
+We tested this idea by simulating populations of FRB sources and bursts and measuring the properties of a flux-limited sub-sample.
 First, we assume an FRB population that is uniformly distributed in space from redshifts $z1$\ to $z2$.
-For each FRB source, we sample one FRB burst luminosity from a powerlaw distribution and calculate its flux.
-%(uniform for energies from $10^{38}$\ to $10^{40}$; \S \ref{sec:disn} 
-We sample 100 such populations and measure 95\% bounds on the distribution of cumulative flux distribution index.
-We can show that the flux distribution powerlaw is --1.5 for a standard candle-like luminosity distribution at low redshift.
-For distributions out to $z2>1$, the distribution flattens slightly ($sim0.3$ in the index) due to cosmological space distortions.
-For a large ($N\sim2000$) population of such bursts, we select the brightest $M\sim20$\ to represent the flux-limited FRB sample of known FRBs...
-The tail of this distribution selects for extrema, such cut-offs in the intrinsic distribution or propagation effects \citep{2015MNRAS.451.3278M, CORDES}. 
-We then fit the flux distribution of those $M$\ events with a powerlaw.
+For each FRB source, we generate one FRB burst with a luminosity drawn from the \frb\ energy distribution and calculate its flux.
+Typically, a large ($N>10000$) population of such bursts is needed to avoid edge effects in the luminosity or redshift distribution.
+We then select the brightest 15 \citep[equal to the current sample size used in modeling;][]{2016ApJ...830...75V} and fit a powerlaw to the $dN/dF$\ distribution.
+%The tail of this distribution selects for extrema, such cut-offs in the intrinsic distribution or propagation effects \citep{2015MNRAS.451.3278M, CORDES}.
 
-These simulations confirm previous work that shows that...
-The cumulative flux distribution follows a Euclidean distribution \citep[index $=-1.5$;][]{2016MNRAS.462..941L} when...
-Flatness has been observed...
-This requires...
+Figure \ref{fig:sim} shows an example of an FRB population simulation with a $dN/dE$\ distribution like \frb.
+We simulated a population for a range of parameters to ensure that the flux distribution measurements were not affected by edge effects.
+We can show that the flux distribution index is --1.5 for a standard candle-like luminosity distribution at low redshift.
+For distributions out to $z2\sim2$, the index flattens by $sim0.2$\ due to redshift space distortions.
+
+\begin{figure*}[htb]
+\begin{center}
+\includegraphics[width=0.9\columnwidth]{sim_L1.6}
+\caption{Example simulation of an FRB population.
+\label{fig:sim}}
+\end{center}
+\end{figure*}
+
+We sample 100 such populations and measure 68\% bounds on the distribution of cumulative flux distribution index.
+Flux distribution index is flat for flatter input luminosity (energy) distributions...
+Best constraint on the FRB flux distribution is consistent with an FRB populalation with a luminosity distribution similar to that of \frb.
+This implies a mean redshift and luminosity of detections... DM distribution in this case?
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=0.9\columnwidth]{sim_index_scaling}
+\caption{Scaling of apparent flux distribution index for given luminosity (or energy) distribution index.
+\label{fig:ind}}
+\end{center}
+\end{figure}
 

### 2017-02-10 repeater-vladata.tex
two panel obs figure. using 68% ci for energy distribution

@@
 \begin{center}
+\includegraphics[width=2\columnwidth]{timeline0}
+
 \includegraphics[width=2\columnwidth]{timeline}
-\caption{Summary of late-2016 observing coverage and detections of \frb\ during the multi-telescope observing campaign.
+\caption{The top and bottom panels summarize the observing coverage and detections of \frb\ in the 2015 and 2016 campaigns.
 Symbols show days with observations and circles highlight observations that detected bursts from \frb.
@@
 We modeled the differential energy distribution, $dN/d\log{E}$, as a Poisson probability distribution with a rate function $\lambda\propto E^{\alpha}$.
-Using a maximum likelihood technique, we estimate the best powerlaw index of $\alpha=-0.6^{+0.4}_{-0.6}$, which is equivalent to a $dN/dE$\ powerlaw index of --1.6.
+Using a maximum likelihood technique, we estimate the best powerlaw index of $\alpha=-0.6^{+0.2}_{-0.4}$ (68\% confidence interval), which is equivalent to a $dN/dE$\ powerlaw index of --1.6.
 This model assumes a completeness limit for a luminosity equivalent to an $8\sigma$\ flux density limit.
@@
 The dashed line shows the best fit from a maximum likelihood analysis using the powerlaw model $dN/d\log{E} \propto E^{\alpha}$.
-The 95\% bounds on the best-fit powerlaw index is $\alpha=-0.6^{+0.4}_{-0.6}$.
+The 95\% bounds on the best-fit powerlaw index is $\alpha=-0.6^{+0.2}_{-0.4}$.
 \label{fig:ed}}

### 2017-02-10 timeline.py

@@ -4,19 +4,22 @@
 
 from numpy import *
 from matplotlib.pyplot import *
+from matplotlib.dates import DateFormatter
 import datetime
 from pylab import date2num
 from astropy import time
 
 # parse obs data
-(obs, t1, t2, tel, burst, band) = loadtxt('obs_data.txt', dtype=str, unpack=True)
+(obs, t1, t2, tel, burst, band) = loadtxt(sys.argv[1], dtype=str, unpack=True)
+ymds = []
 for i in range(len(obs)):
-	if obs[i] == 'mjd':
-		t1c = time.Time(float(t1[i]), format='mjd').iso
-		t2c = time.Time(float(t2[i]), format='mjd').iso
-		obs[i], t1[i] = t1c.split()
-		_, t2[i] = t2c.split()
-obsdate = array(map(lambda od: datetime.datetime.strptime(od, "%Y-%m-%d"), obs))
+    if obs[i] == 'mjd':
+        t1c = time.Time(float(t1[i]), format='mjd').iso
+	ymd = t1c.split()[0]
+	ymds.append(ymd)
+    else:
+        ymds.append(obs[i])
+obsdate = list(map(lambda od: datetime.datetime.strptime(od, "%Y-%m-%d"), ymds))
 
 # Define an offset and symbol type for each telescope
 telescopes = ['AO', 'VLA', 'Effelsberg', 'AMI']
@@ -45,6 +48,7 @@ def putdot(ax, i):
 		s = 250
 	else:
 		s = 80
+#	ax.plot_date(pltx, plty)#, s=band[i], verticalalignment='center', horizontalalignment='center')
 	ax.text(pltx, plty, s=band[i], verticalalignment='center', horizontalalignment='center')
 #	ax.scatter(pltx, plty, marker=psym[tel[i]], s=s, linewidth=3, facecolor=pcol[tel[i]], edgecolor='none')
 
@@ -65,26 +69,34 @@ def labeltelright(ax, num):
 		xval = xr + 0.5
 		ax.text(xval, yval, teln, horizontalalignment='left', verticalalignment='center')
 
-xl = d2n(2016, 8, 19)
-xr = d2n(2016, 9, 23)
-fig, ax = subplots(1, 1, figsize=(15, 4))
+if obsdate[0].year == 2016:
[…]

### 2017-02-11 repeater-vladata.tex
finished frb flux discussion

@@
 \affiliation{Department of Astronomy and Radio Astronomy Lab, University of California, Berkeley, CA 94720, USA}
+
+\author{J.~W.~T.~Hessels}
+\affiliation{ASTRON, Netherlands Institute for Radio Astronomy, Postbus 2, 7990 AA, Dwingeloo, The Netherlands}
+\affiliation{Anton Pannekoek Institute for Astronomy, University of Amsterdam, Science Park 904, 1098 XH Amsterdam, The Netherlands}
 
@@
 \affiliation{Jodrell Bank Centre for Astrophysics, Alan Turning Building, School of Physics \& Astronomy ,The University of Manchester, Oxford Road, Manchester M13 9PL, UK}
-
-\author{J.~W.~T.~Hessels}
-\affiliation{ASTRON, Netherlands Institute for Radio Astronomy, Postbus 2, 7990 AA, Dwingeloo, The Netherlands}
-\affiliation{Anton Pannekoek Institute for Astronomy, University of Amsterdam, Science Park 904, 1098 XH Amsterdam, The Netherlands}
 
@@
 
-\subsubsection{Spectral Autocorrelation}
-\label{sec:auto}
-Autocorrelation of the burst signal (both temporal and spectral) can be used to infer both intrinsic properties and modulation due to scintillation \citep{CORDES}.
-Figure \ref{fig:acf} shows the spectral autocorrellation for the strongest burst (MJD 57633.68).
-The is no strong excess correlation near the channel resolution, which limits the correlation width to less than roughly 4~MHz.
-This is broadly consistent with expectations of Galactic diffractive scintillation bandwidth \citep[3--9~MHz near 3~GHz][]{2002astro.ph..7156C}.
-
-%**Does channel-scale structure only appear around 3~GHz?**
-
-\begin{figure}[htb]
-\begin{center}
-\includegraphics[width=0.9\columnwidth]{acf_57633_scan7}
-\caption{The spectral autocorrelation as a function of frequency for the burst from \frb\ at MJD 57633.68.
-The largest black dots show the autocorrelation for the data, smaller dots show the autocorrelation for the best Gaussian model, and dashed line shows the autocorrelation of an off-burst spectrum.
-\label{fig:acf}}
-\end{center}
-\end{figure}
-
-\subsubsection{Circular Polarization}
-The VLA S-band recievers measure circular polarization, although for observing efficiency we choose not to include polarization calibration procedures.
-Constraints on circular polarization are possible since the gain calibrator is a well-known polarization calibrator with little Stokes V flux.
-In that case, the apparent circular polarization fraction is $(RR-LL)/(RR+LL)$, which for the most significant bursts is at most 3\%.
-\frb\ was located 2.3\arcmin away from pointing center, where systematic effects have been measured as large as 3\% (Perley et al 2016, VLA memo).
-Given that systematic effects dominate the apparent circular polarization, we conclude that the true fractional circular polarization is less than 3\%.
-
 \subsection{Temporal Statistics}
@@
 
+\subsubsection{Spectral Autocorrelation}
+\label{sec:auto}
+Autocorrelation of the burst signal (both temporal and spectral) can be used to infer both intrinsic properties and modulation due to scintillation \citep{CORDES}.
+Figure \ref{fig:acf} shows the spectral autocorrellation for the strongest burst (MJD 57633.68).
+The is no strong excess correlation near the channel resolution, which limits the correlation width to less than roughly 4~MHz.
+This is broadly consistent with expectations of Galactic diffractive scintillation bandwidth \citep[3--9~MHz near 3~GHz][]{2002astro.ph..7156C}.
+
+%**Does channel-scale structure only appear around 3~GHz?**
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=0.9\columnwidth]{acf_57633_scan7}
+\caption{The spectral autocorrelation as a function of frequency for the burst from \frb\ at MJD 57633.68.
+The largest black dots show the autocorrelation for the data, smaller dots show the autocorrelation for the best Gaussian model, and dashed line shows the autocorrelation of an off-burst spectrum.
+\label{fig:acf}}
+\end{center}
+\end{figure}
+
+\subsubsection{Circular Polarization}
+The VLA S-band recievers measure circular polarization, although for observing efficiency we choose not to include polarization calibration procedures.
+Constraints on circular polarization are possible since the gain calibrator is a well-known polarization calibrator with little Stokes V flux.
+In that case, the apparent circular polarization fraction is $(RR-LL)/(RR+LL)$, which for the most significant bursts is at most 3\%.
+\frb\ was located 2.3\arcmin away from pointing center, where systematic effects have been measured as large as 3\% (Perley et al 2016, VLA memo).
+Given that systematic effects dominate the apparent circular polarization, we conclude that the true fractional circular polarization is less than 3\%.
+
 \section{discussion}
@@
 The Lorimer burst was surprising for its unusually large flux with a lack of lower-significance detections.
-As more FRBs have been detected, we continue to be surprised by the apparent brightness of FRB \citep{2016arXiv161105758R}.
-This perception has been validated with analysis of the FRB fluence distribution, which when modeled as a powerlaw, $dN/dF \propto F^{\alpha}$, has $-0.5<\alpha<-0.9$ \citep{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}.
-For a uniform distribution of sources with a single luminosity, the nominal flux distribution index shoudl be --1.5 \citep[the ``Euclidean'' distribution, e.g.,][]{2016MNRAS.462..941L}.
+As more FRBs have been detected, we continue to be surprised by their apparent brightness of FRBs \citep{2016arXiv161105758R}.
+This perception has been validated with analysis of the FRB cumulative fluence distribution, which when modeled as a powerlaw ($dN/dF \propto F^{\alpha}$) has an index $-0.5<\alpha<-0.9$\ \citep{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}.
+For a uniform distribution of sources with a single luminosity, this index should be --1.5 \citep[the ``Euclidean'' distribution, e.g.,][]{2016MNRAS.462..941L}.
 
 The energy distribution of \frb\ bursts has also produced some surprises.
-Although the source clearly has episodes of activity (Section \label{sec:temp}), the nine bursts were detected with a wide range of significance (12 to 179$\sigma$).
-If all FRBs luminosities are drawn from a distribution (rather than having a single luminosity), then the flux distribution will be modified by that underlying distribution and its interplay with redshift space distortions of a cosmological population.
+The nine bursts were detected with a wide range of significance (12 to 179$\sigma$) and the apparent burst energy distribution can be characterized as a powerlaw $dN/dE\propto E^{-1.6}$.
+If all FRBs luminosities are drawn from such a distribution, then their flux distribution will be determined by the underlying energy distribution and its interplay with redshift space distortions.
 
-We tested this idea by simulating populations of FRB sources and bursts and measuring the properties of a flux-limited sub-sample.
+We tested this idea by simulating FRB populations and measuring the properties of a flux-limited sub-sample.
 First, we assume an FRB population that is uniformly distributed in space from redshifts $z1$\ to $z2$.
 For each FRB source, we generate one FRB burst with a luminosity drawn from the \frb\ energy distribution and calculate its flux.
-Typically, a large ($N>10000$) population of such bursts is needed to avoid edge effects in the luminosity or redshift distribution.
 We then select the brightest 15 \citep[equal to the current sample size used in modeling;][]{2016ApJ...830...75V} and fit a powerlaw to the $dN/dF$\ distribution.
-%The tail of this distribution selects for extrema, such cut-offs in the intrinsic distribution or propagation effects \citep{2015MNRAS.451.3278M, CORDES}.
+Typically, a large ($N>10000$) population of such bursts is needed to avoid edge effects in the properties of the flux-limited subsample.
 
 Figure \ref{fig:sim} shows an example of an FRB population simulation with a $dN/dE$\ distribution like \frb.
-We simulated a population for a range of parameters to ensure that the flux distribution measurements were not affected by edge effects.
-We can show that the flux distribution index is --1.5 for a standard candle-like luminosity distribution at low redshift.
-For distributions out to $z2\sim2$, the index flattens by $sim0.2$\ due to redshift space distortions.
+We use visualizations like this to verify that the simulations are not affected by edge effects.
+We can also reproduce a Euclidean flux distribution for a standard candle-like luminosity distribution at low redshift and that distributions out to $z2\sim2$ have a flatter index ($\Delta\alpha\sim0.2$) due to redshift space distortions.
 
@@
 \begin{center}
-\includegraphics[width=0.9\columnwidth]{sim_L1.6}
-\caption{Example simulation of an FRB population.
+\includegraphics[width=1.8\columnwidth]{sim_L1.6}
+\caption{An example of a simulated FRB population.
+(Top left) The input luminosity distribution, which follows the \frb\ distribution of $dN/dE\propto E^{-1.6}$.
+(Top right) The input redshift space distribution of a uniform distribution of FRB sources.
+(Bottom left) The measured flux distribution of the simulation with red lines showing fits to the whole population and brightest 15 FRBs.
+(Bottom right) The flux-redshift distribution of the simulated population.
+The dahsed line shows the limiting flux that includes the brightest 15 sources.
 \label{fig:sim}}
@@
 
-We sample 100 such populations and measure 68\% bounds on the distribution of cumulative flux distribution index.
-Flux distribution index is flat for flatter input luminosity (energy) distributions...
-Best constraint on the FRB flux distribution is consistent with an FRB populalation with a luminosity distribution similar to that of \frb.
-This implies a mean redshift and luminosity of detections... DM distribution in this case?
+To study how the input parameters affect the measured flux distribution, so we generated 100 populations to measure 68\% confidence intervals on the cumulative flux distribution index.
+Figure \ref{fig:ind} shows the result of several such measurements for input luminosity distribution index ranging from --2.2 to --1.2.
+Generally, the measured flux distribution index flattens as the input luminosity distributions flattens.
+The best constraint on the flux distribution index \citep{2016ApJ...830...75V} requires an input energy distribution index between roughly --2.1 and --1.4, which is consistent with the measured energy distribution for \frb.
+These simulations predict a mean a mean redshift between 0.9 and 1.8, which is in weak tension with the mean FRB redshift inferred from DM.
+For a mean total DM of $750$\ pc cm$^{-3}$ and a mean host DM of 200 pc cm$^{-3}$, we expect a mean redshift of $\sim0.5$ \citep{2004MNRAS.348..999I}.
 
@@
 
-It is not yet clear whether \frb\ can be treated as a representative of the broader FRB population.
-\citet{2016Natur.531..202S} describes burst spectral structure that is intrinsic, or at least dominated by propagation effects close to the emitting region.
-On the other hand, \citep{CORDES} have identified a variety of propagation effects in our own Galaxy that can plausibly modify the observed brightness distribution.
-
-**caveats of S-band assumption**
+While the \frb\ burst energy distribution is consistent with the overall FRB population, this simulation ignores many observational biases (scattering, observing coverage) and the effects of galaxy evolution, which is likely significant over the range of redshifts to which \frb is detectable \citep[e.g.,][]{2010ApJ...709..644I}.
+The burst energies are estimated from observations from 2.5 to 3.5~GHz, which may be a biased selection of all bursts or may not include all burst emission.
+If the simulation is revealing a connection between \frb and the broader FRB population, it does not explain the physical mechanism that drives it.
+The burst energy distribution of the population could be dominated by intrinsic or extrinsic effects \citep{2015MNRAS.451.3278M,2016Natur.531..202S,CORDES}.
+More FRB detections will improve the quality of this inference as sample variance drops, while more burst detetions from \frb\ will improve the measurement of the intrinsic energy distribution.
 

### 2017-03-10 repeater-vladata.tex
fixed label on timeline figure

@@
 \author{P.~Scott}
-\affiliation{University of Cambridge, UK}
+\affiliation{Astrophysics Group, Cavendish Laboratory, 19 J. J. Thomson Avenue, Cambridge CB3 0HE, UK}
 
@@
 \author{D.~Titterington}
-\affiliation{University of Cambridge, UK}
+\affiliation{Astrophysics Group, Cavendish Laboratory, 19 J. J. Thomson Avenue, Cambridge CB3 0HE, UK}
 
@@
 
+**Burst temporal width**
+
+**Corner plot?**
+
+**Does DM correlate with other spectral/flux properties?**
+
 \subsubsection{Dispersion}
@@
 Uncertainties in each pixel are drawn from a uniform Gaussian error distribution that is estimated from the data.
-
-**Does DM correlate with other spectral/flux properties?**
 
@@
 These simulations predict a mean a mean redshift between 0.9 and 1.8, which is in weak tension with the mean FRB redshift inferred from DM.
-For a mean total DM of $750$\ pc cm$^{-3}$ and a mean host DM of 200 pc cm$^{-3}$, we expect a mean redshift of $\sim0.5$ \citep{2004MNRAS.348..999I}.
+For a mean total DM of $750$\ pc cm$^{-3}$ and a mean host DM of 200 pc cm$^{-3}$, we expect a mean redshift of $\sim0.6$ \citep[$z=DM/900$\ pc cm$^{-3}$;][]{2004MNRAS.348..999I}.
 

### 2017-03-10 timeline.py

@@ -73,7 +73,7 @@ if obsdate[0].year == 2016:
     xl = d2n(2016, 8, 19)
     xr = d2n(2016, 9, 23)
 else:
-    xl = d2n(2015, 11, 23)
+    xl = d2n(2015, 11, 22)
     xr = d2n(2016, 5, 30)
 
 fig, ax = subplots(1, 1, figsize=(15, 4.5))
@@ -82,6 +82,7 @@ for i in range(len(obsdate)):
 ax.set_xlim( (xl, xr) )
 ax.set_ylim( (-0.4, 3.4) )
 ax.tick_params(labelright='off', labelleft='off')
+ax.xaxis.set_major_formatter(DateFormatter('%Y-%m-%d'))
 ax.fmt_xdata = DateFormatter('%Y-%m-%d %H:%M:%S')
 
 # boxes for simultaneous coverage of VLA bursts

### 2017-03-11 repeater-vladata.tex
added tmp ao/vla spec.

@@
 \begin{abstract}
-The recent precision localization of \frb\ has helped identify its host galaxy, measure its distance, and establish it as a member of a truly new class of astrophysical source.
+The recent precision localization of \frb\ has helped identify a host galaxy, measure its distance, and establish it as a member of a truly new class of astrophysical source.
 We present results of the coordinated observing campaign that made this localization, including the first simultaneous detection of an FRB burst with multiple telescopes.
 Of the nine bursts detected by the Very Large Array at 3~GHz, four had simultaneous observing coverage at other observatories, and one was detected by the Arecibo Observatory at 1.4~GHz.
-We show that the burst spectra typically have a broad shape that tapers off on scales of $\sim500$~MHz, plus fine spectral structure on MHz-frequency scales.
-We present the first FRB energy distribution and temporal statistics for \frb\ and argue that the whole FRB population is adequately described by a single class similar to \frb.
+We show that the burst spectra typically have a $\sim500$~MHz-scale envelope, plus fine spectral structure on MHz-frequency scales.
+We also calculate the energy distribution and temporal statistics for \frb...
+%\ and argue that the whole FRB population is adequately described by a single class similar to \frb. 
 *population models* *slsn*
@@
 \caption{The top and bottom panels summarize the observing coverage and detections of \frb\ in the 2015 and 2016 campaigns.
-Symbols show days with observations and circles highlight observations that detected bursts from \frb.
-Multiple circles indicate multiple burst detections, except for Arecibo, which typically has multiple detections per observing session (a detailed analysis is left for a future paper).
+Symbols show days with observations with letters L, S, C, K referring to radio frequencies of 1.4, 3, 5, and 12~GHz.
+Circles highlight observations that detected bursts from \frb.
+Multiple circles indicate multiple burst detections, except for Arecibo, which typically has multiple detections per observing session.
 The black dashed lines show the VLA burst detections with simultaneous coverage at other telescopes.
@@
 Images were formed for each integration with a DM grid of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$ and a time resampling grid of 5, 10, 20, 40, and 80 ms.
-This DM grid was chosen to maintain 90\% sensitivity to the nominal DM range of 540--570 pc cm$^{-3}$, which includes the known \frb\ DM of 559 pc cm$^{-3}$.
+This DM grid was chosen to maintain 90\% sensitivity to the nominal DM range of 540--570 pc cm$^{-3}$, which includes the known \frb\ DM of 559 pc cm$^{-3}$ \citep{2016arXiv160308880S}.
 Gain calibration was made from observations of J0555+3948 by the ``telcal'' system, which uses phase-only calibration.
@@
 
-Computational notebooks to reproduce the transient detection, localization, and analysis presented here can be found at \url{https://github.com/caseyjlaw/FRB121102}.
+Computational (Jupyter) notebooks to reproduce the transient detection, localization, and analysis presented here can be found at \url{https://github.com/caseyjlaw/FRB121102}.
 Time cut-out visibility data and calibration products are available at \url{https://doi.org/10.7910/DVN/TLDKXG}.
@@
 Four of those observations were simultaneous with bursts detected with the VLA and one of those observations detected the same VLA burst.
-During the first VLA burst with Arecibo coverage (MJD 57643), the PUPPI system failed so data were recorded with {\color{red} xx (Jason?)} at C band.
+During the first VLA burst with Arecibo coverage (MJD 57643), the PUPPI 1.4~GHz recording system failed so data were recorded at C band.
 No detection was made in those Arecibo data.
@@
 \subsection{Multi-Observatory Burst Spectrum}
-Four of the VLA bursts were observed simultaneously with Arecibo and AMI-LA (Figure \ref{fig:multi}).
-Of these, the burst on 57648 was detected by Arecibo at the same time (after correcting for the known DM of \frb).
-The Arecibo detection of this burst had a significance of {\color{red} xx$\sigma$ (Jason)}.
+Four of the VLA bursts were observed simultaneously with Arecibo and AMI-LA, while two were observed simultaneously with all four observatories (Figure \ref{fig:multi}).
+Of these bursts, only the VLA burst on MJD 57648 was simultaneously detected by another observatory, Arecibo.
+The VLA and Arecibo burst detections had significances of 25$\sigma$\ and xx$\sigma$, respectively.
 
-Figure {\color{red} **to do**} shows the dynamic spectrum formed from the phased VLA and Arecibo data... **Discuss dispersion correction, time alignment, chance of false association**
+Figure \ref{fig:sgram} shows a dynamic spectrum for the 57648 burst with the VLA and AO bursts resampled to the same grid.
+The temporal resolution of the VLA data (5~ms) is much coarser than that of Arecibo and barycentric corrections, so we only need to correct for DM to align the bursts in time.
 
 This simultaneous detection of a burst from roughly 1.2 to 3.5~GHz shows that some bursts emit over more than an octave of frequency. However, the other three...**
-**
- is one of three VLA bursts with L-band coverage by Arecibo, which implies that those bursts had a smaller spectral width.
+** is one of three VLA bursts with L-band coverage by Arecibo, which implies that those bursts had a smaller spectral width.
 However, all three VLA bursts with L-band Arecibo observations were relatively weak, so it is difficult to rule out L-band emission entirely.
@@
 \begin{center}
-% \begin{minipage}{2\columnwidth}
-%  \includegraphics[width=0.18\columnwidth]{sgram_57623.png}
-%  \includegraphics[width=0.18\columnwidth]{sgram_57633_scan7.png}
-%  \includegraphics[width=0.18\columnwidth]{sgram_57633_scan13.png}
-%  \includegraphics[width=0.18\columnwidth]{sgram_57638.png}
-%  \includegraphics[width=0.18\columnwidth]{sgram_57643.png}
-% \end{minipage}
-%
-% \begin{minipage}{2\columnwidth}
-%  \includegraphics[width=0.18\columnwidth]{sgram_57645.png}
-%  \includegraphics[width=0.18\columnwidth]{sgram_57646.png}
-%  \includegraphics[width=0.18\columnwidth]{sgram_57648.png}
-%  \includegraphics[width=0.18\columnwidth]{sgram_57649.png}
-% \end{minipage}
-%
-% \caption{Dynamic spectra (time vs frequency intensity maps) for the nine VLA bursts.
-Starting at the top left, they correspond to bursts 57623, 57633.68, 57633.70, 57638, 57643, (bottom left) 57645, 57646, 57648, and 57649.
-Note that bursts are detected in 5~ms images generated from dedispersed visibilities.
- \includegraphics[width=1.9\columnwidth]{spec_57648.png}
- \caption{**Placeholder** Fill in with AO+VLA dynamic spectrum.
+ \includegraphics[width=1.9\columnwidth]{aovla_spec.png}
+ \caption{
  \label{fig:sgram}}

### 2017-03-15 repeater-vladata.tex
ao/vla burst spectrum pretty nice. discussion going

@@
 Four of the VLA bursts were observed simultaneously with Arecibo and AMI-LA, while two were observed simultaneously with all four observatories (Figure \ref{fig:multi}).
-Of these bursts, only the VLA burst on MJD 57648 was simultaneously detected by another observatory, Arecibo.
-The VLA and Arecibo burst detections had significances of 25$\sigma$\ and xx$\sigma$, respectively.
+Of these bursts, only one VLA burst (on MJD 57648) was simultaneously detected by another observatory (Arecibo).
+The VLA and Arecibo burst detections had significances of 25$\sigma$\ and 39$\sigma$, respectively.
+The VLA and Arecibo integrated flux densities were 111 mJy and 14 mJy, respectively.
 
-Figure \ref{fig:sgram} shows a dynamic spectrum for the 57648 burst with the VLA and AO bursts resampled to the same grid.
-The temporal resolution of the VLA data (5~ms) is much coarser than that of Arecibo and barycentric corrections, so we only need to correct for DM to align the bursts in time.
+Figure \ref{fig:sgram} shows a dynamic spectrum for the 57648 burst with the VLA and AO data aligned in time.
+The temporal resolution of the VLA data (5~ms) is much coarser than that of Arecibo, so data were resampled to the same temporal grid after correcting for barycentric and dispersion measure offsets.
+The dispersion correction for both data sets assumed a DM of 560.5 pc cm$^{-3}$, which was typical of the source during the observing campaign \citep{WEIRD}.
+The regridded dynamic spectrum has an apparent DM error that is evident either as a frequency-dependent time drift within the Arecibo observation or in the relative alignment of Arecibo and the VLA bursts.
+Both of these drifts are consistent with an effective DM (i.e., one that maximizes the detection S/N ratio) of $sim$562 pc cm$^{-3}$.
 
-This simultaneous detection of a burst from roughly 1.2 to 3.5~GHz shows that some bursts emit over more than an octave of frequency. However, the other three...**
-** is one of three VLA bursts with L-band coverage by Arecibo, which implies that those bursts had a smaller spectral width.
-However, all three VLA bursts with L-band Arecibo observations were relatively weak, so it is difficult to rule out L-band emission entirely.
-However, as described in \S \ref{sec:spec}, some of the VLA bursts peak within the band from 2.5 to 3.5~GHz, which implies a much smaller spectral coverage for typical bursts.
+Three of the four VLA bursts with simultaneous observing coverage by Arecibo were not detected at Arecibo.
+Even the one simultaneous detection at Arecibo was an order of magnitude fainter than seen by the VLA, so it is clear that the 3~GHz burst flux is not correlated with that at 1.4~GHz.
 
@@
  \includegraphics[width=1.9\columnwidth]{aovla_spec.png}
- \caption{
+ \caption{Composite dynamic specrum for the burst from \frb\ on MJD 57648 with data from the VLA and Arecibo observatories.
+Both data sets have been barycentered and corrected for an assumed dispersion measure of 560.5 pc $^{-3}$.
+The black line separates data from the VLA (2.5 to 3.5~GHz) and Arecibo (1.0 to 1.8~GHz).
+The Arecibo to VLA gain ratio is assumed to be 10.
  \label{fig:sgram}}
@@
 \label{sec:disc}
-\subsection{Emission Physics and Burst Energetics}
-The refined analysis shows that \frb\ has even higher isotropic energies than previously reported, reaching energies $E_{\rm{max}}\approx10^{40}$\ erg.
-We now know that \frb\ is detectable with the VLA out to $z=0.7$\ and much farther with Arecibo.
-\frb\ has isotropic energies orders of magnitude higher than the strongest Crab pulsar pulses ($\sim10^{35}$~erg) and comparable brightness temperatures \citep[$T_b^{\rm{Crab}}\sim10^{41}$~K versus $T_b^{\rm{FRB 121102}}\sim10^{38}$~K;][]{2003Natur.422..141H,2014PhRvD..89j3009K}.
-While this emission is coherent and strongly beamed \citep{2016Natur.531..202S, WEIRD}, the energy scale is still larger than any known Galactic radio transient and requires either a new process or dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}.
+\subsection{Burst Spectra}
+We present the first simultaneous detection of an FRB with multiple telescopes and over frequencies from 1.2 to 3.5~GHz.
+After correcting for barycentric and dispersion delays, we find a residual temporal drift in the burst spectrum.
+This is consistent with \citet{WEIRD}, which uses bright, coherently-dedispersed bursts to define a heuristic that distinguishes between intrinsic and extrinsic dispersion-like effects.
+The low-resolution dynamic spectra presented here cannot distinguish between these two effects.
+However, by assuming that the extrinsic (true) DM is consistent with the long-term average of 560.5 pc cm$^{-3}$, we can ascribe the observed burst drift (Figure \ref{fig:sgram}) to intrinsic effects.
+Under this assumption, the burst drift is intrinsic and consistent with the intrinsic drft rate measured in \citet[$\sim$100~MHz/ms;][]{WEIRD}.
 
--- Self-organized criticality in the sun. energy powerlaw=-1.7 \citep{2011SoPh..274...99A}
--- **Similarity to magnetar energy distribution**
+The 57648 burst is nearly an order of magnitude brighter near 3~GHz than at 1.4~GHz.
+Expressed as a spectral index ($S_{\nu} \propto \nu^{\alpha}$), we find $\alpha\approx2.7$.
+However, the bursts detected here and described in \citet{WEIRD} make it clear that burst spectral power is not well described by a powerlaw.
+
+Given the high sensitivity of Arecibo...
+Even the one AO detection is 10x fainter...
+** is one of three VLA bursts with L-band coverage by Arecibo, which implies that those bursts had a smaller spectral width.
+However, all three VLA bursts with L-band Arecibo observations were relatively weak, so it is difficult to rule out L-band emission entirely.
+However, as described in \S \ref{sec:spec}, some of the VLA bursts peak within the band from 2.5 to 3.5~GHz, which implies a much smaller spectral coverage for typical bursts.
+
+burst rate is correlated between vla and ao, but not the intensity of individual bursts...
 
@@
 
-\subsection{FRB Flux Distribution}
+\subsection{Energy and Flux Distribution}
+The refined analysis shows that \frb\ has even higher isotropic energies than previously reported, reaching energies $E_{\rm{max}}\approx10^{40}$\ erg.
+We now know that \frb\ is detectable with the VLA out to $z=0.7$\ and much farther with Arecibo.
+\frb\ has isotropic energies orders of magnitude higher than the strongest Crab pulsar pulses ($\sim10^{35}$~erg) and comparable brightness temperatures \citep[$T_b^{\rm{Crab}}\sim10^{41}$~K versus $T_b^{\rm{FRB 121102}}\sim10^{38}$~K;][]{2003Natur.422..141H,2014PhRvD..89j3009K}.
+While this emission is coherent and strongly beamed \citep{2016Natur.531..202S, WEIRD}, the energy scale is still larger than any known Galactic radio transient and requires either a new process or dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}.
+
+-- Self-organized criticality in the sun. energy powerlaw=-1.7 \citep{2011SoPh..274...99A}
+-- **Similarity to magnetar energy distribution**
+
 The Lorimer burst was surprising for its unusually large flux with a lack of lower-significance detections.

### 2017-03-17 repeater-vladata.tex
results in good order. table needs update

@@
 \label{sec:spec}
-We used two techniques to refine the analysis of the nine VLA radio burst spectra described in \citet{LOC}.
-First, we improved on the initial analysis by using a better calibration scheme and optimizing the detection significance over a fine grid of DM ($\Delta \rm{DM}=1\ \rm{pc}\ \rm{cm}^{-3}$).
+This paper refine the analysis of the nine VLA radio burst spectra described in \citet{LOC} in a few ways.
+We use a better calibration scheme and have optimized the detection significance over a fine grid of DM ($\Delta \rm{DM}=1\ \rm{pc}\ \rm{cm}^{-3}$).
 After calibration and flagging, the visibility phases were rotated to the best-fit location \citep[(RA, Dec) $=$ (05h31m58.70s, +33d08m52.5s);][]{LOC} to extract a Stokes I spectrum that maximizes the image S/N for each burst.
-Table \ref{tab:spec} gives the resulting integrated burst flux density, image S/N, and Stokes V, while Figure \ref{fig:spec} shows the Stokes I spectra.
-Generally, the burst spectra are characterized by a broad, Gaussian shape with inter-channel modulation as high as 100\%.
+
+Table \ref{tab:spec} summarizes the properties of all nine VLA bursts.
+Parameters such as integrated flux density, S/N, and Stokes V were measured from the burst properties integrated in frequency.
+Stokes V values estimated from the dual-circular feeds ($(RR-LL)/(RR+LL)\approx3\%$ and are comparble to the systematic error expected from the primary beam (Perley et al 2016, VLA memo).
+Given that systematic effects dominate the apparent circular polarization, we conclude that the true fractional circular polarization is less than 3\%.
 
 \begin{table*}
-\caption{Properties of Bursts from \frb}
+\caption{Properties of Bursts from \frb **update**}
 \centering
-\begin{tabular}{lcccccccc}
+\begin{tabular}{lccccccccc}
 \hline
-Date                & S$_{\rm{I,int}}$  & Image S/N & E$_{\rm{int}}$ & DM$_{\rm{opt}}$ & S$_{\rm{I,peak}}$ & Center & FWHM & S$_{\rm{V}}$ \\
-(MJD)               & (mJy)           &           & ($10^{38}$\ erg) & (pc cm$^{-3})$ & (mJy) & (GHz)  & (MHz) & (mJy) \\ \hline
-57623.74402686      & 194             & 38        & 11 & 562.1 & 690 & 2.8 & 290 & +3 \\ % 7.8  & 562.5 & 460 & 2.8 & 300 & +3 \\
-57633.67986367      & 1500            & 179       & 97 & 561.3 & 3350 & 3.2 & 510 & --35 \\ % 65   & 561.4 & 2200 & 3.2 & 520 & --35 \\
-57633.69515938\tablenotemark{a} & 69  & 15        & 7 & 555.8 & $>$430 & $<$2.5 & 290 & +2 \\ % 5.9  & 555.4 & $>$320 & $<$2.5 & $>$320 & +2 \\
-57638.49937435      & 55              & 12        & 3 & 558.6 & 130 & 3.1 & 410 & +5 \\ % 1.8  & 554.9 & 70 & 3.1 & 440 & +5 \\
-57643.45730263      & 508             & 100       & 34 & 558.7 & 1170 & 2.8 & 510 & --5 \\ % 13   & 559.3 & 440 & 2.8 & 530 & --5 \\
-57645.42958602      & 64              & 13        & 4 & 555.9 & 170 & 2.8 & 380 & +3 \\ % 2.6  & 554.1 & 50 & 2.7 & 970 & +3 \\
-57646.46600650\tablenotemark{a} & 87  & 20        & 10 & 562.4 & $>$420 & $<$2.5 & 420 & +1 \\ % 3.9  & 568.1 & $>$190 & $<$2.5 & $>$360 & +1 \\
-57648.43691490\tablenotemark{b} & 111 & 25        & 7 & 557.4 & 260 & 2.8 & 470 & +9 \\ % 2.9  & 557.8 & 110 & 2.8 & 440 & +9 \\
-57649.45175697      & 167             & 36        & 12 & 559.9 & 290 & 3.0 & 690 & +1 \\ \hline % 6.3  & 559.9 & 80 & 2.9 & 1400 & +1 \\ \hline
+Date                & S$_{\rm{I,int}}$  & Image S/N & E$_{\rm{int}}$ & DM$_{\rm{opt}}$ & dt & S$_{\rm{I,peak}}$ & Center & FWHM & S$_{\rm{V}}$ \\
+(MJD)               & (mJy)           &           & ($10^{38}$\ erg) & (pc cm$^{-3})$ & (ms) & (mJy) & (GHz)  & (MHz) & (mJy) \\ \hline
+57623.74402686      & 194             & 38        & 11 & 562.1 & & 690 & 2.8 & 290 & +3 \\ % 7.8  & 562.5 & 460 & 2.8 & 300 & +3 \\
+57633.67986367      & 1500            & 179       & 97 & 561.3 & & 3350 & 3.2 & 510 & --35 \\ % 65   & 561.4 & 2200 & 3.2 & 520 & --35 \\
+57633.69515938\tablenotemark{a} & 69  & 15        & 7 & 555.8 & & $>$430 & $<$2.5 & 290 & +2 \\ % 5.9  & 555.4 & $>$320 & $<$2.5 & $>$320 & +2 \\
+57638.49937435      & 55              & 12        & 3 & 558.6 & & 130 & 3.1 & 410 & +5 \\ % 1.8  & 554.9 & 70 & 3.1 & 440 & +5 \\
+57643.45730263      & 508             & 100       & 34 & 558.7 & & 1170 & 2.8 & 510 & --5 \\ % 13   & 559.3 & 440 & 2.8 & 530 & --5 \\
+57645.42958602      & 64              & 13        & 4 & 555.9 & & 170 & 2.8 & 380 & +3 \\ % 2.6  & 554.1 & 50 & 2.7 & 970 & +3 \\
+57646.46600650\tablenotemark{a} & 87  & 20        & 10 & 562.4 & & $>$420 & $<$2.5 & 420 & +1 \\ % 3.9  & 568.1 & $>$190 & $<$2.5 & $>$360 & +1 \\
+57648.43691490\tablenotemark{b} & 111 & 25        & 7 & 557.4 & & 260 & 2.8 & 470 & +9 \\ % 2.9  & 557.8 & 110 & 2.8 & 440 & +9 \\
+57649.45175697      & 167             & 36        & 12 & 559.9 & & 290 & 3.0 & 690 & +1 \\ \hline % 6.3  & 559.9 & 80 & 2.9 & 1400 & +1 \\ \hline
 \end{tabular}
@@
 
+Figure \ref{fig:spec} shows that the Stokes I spectra are generally characterized by a broad, Gaussian shape with inter-channel modulation as high as 100\%.
 To better understand the spectra, we extracted dynamic radio spectra (time versus frequency) for 2d modeling with the MCMC sampler \emph{emcee} \citep{2013PASP..125..306F}.
-These dynamic spectral were modeled as the product of a Gaussian shape (amplitude, center, width) and a temporal shape (start time, DM, and width).
-These 6-dimensional fits were sampled with 100 walkers taking 500 steps; typically, the first 200 steps were used to burn in the walkers and were ignored.
-A flat prior was used over all ranges with valid data, including a requirement that the Gaussian integral produce a detection significance higher than 8$\sigma$.
-To represent the strong inter-channel modulation, the model error was estimated as the maximum of the modeled flux and the measured, off-burst noise value (typically 70 mJy per 5~ms integration and 4~MHz channel).
+MCMC sampling requires a generative model for the data, so we wrote functions in Python to create 2d dynamic spectra.
+The dynamic spectra are modeled in the spectral domain as a Gaussian envelope and in the temporal domain by a dispersive delay (scaling as frequency squared).
+We further allow the pulses to have a finite temporal width.
+This brings the total number of parameters to 6 (Gaussian amplitude, center, width, start time, time width, and DM).
+
+The 6-dimensional models were sampled with 100 walkers taking 500 steps.
+Typically, the first 200 steps were used to burn in the walkers and were ignored.
+A flat prior was used over all ranges with valid data.
+An additional requirement was that the integrated burst signal must have a detection significance higher than 8$\sigma$.
+The inter-channel modulation (scintillation) was ignored in the model.
+The measured, off-burst noise value was typically 70 mJy per 5~ms integration and 4~MHz channel.
 
@@
 This is consistent with previous detections of \frb\ by Arecibo, which showed quasi-broadband structure \citep{2016arXiv160308880S} and large variation in the implied spectral index \citep{2014ApJ...790..101S}.
-A detailed discussion of high-resolution \frb\ burst spectra seen by the Arecibo Observatory will be presented elsewhere \citep{WEIRD}.
 
@@
 
-**Burst temporal width**
+This analysis differs from traditional analysis in that it simultaneously models the spectral and temporal evolution of the burst.
+Since the burst crosses many time-frequency pixel boundaries, the temporal modeling is sensitive to temporal properties smaller than the 5~ms integration time.
+Table \ref{tab:spec} shows that the typical burst width is measured as $2\pm1$~ms (95\% confidence interval); the brightest burst (57633.68) has a temporal width of $2.05\pm0.05$~ms.
+The burst arrival times are typically measured with a precision of 1~ms; the brightest burst arrival time is measured with a precision of $\sim50\mu$s.
+Note that these errors are only accurate to the degree that the model represents the data.
+One potential bias in the model is that we do not model scintillation effects.
 
-**Corner plot?**
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=0.9\columnwidth]{corner57646}
+\caption{A scatterplot matrix that shows the correlation of every pair of parameters in the MCMC run for burst 57646.
+The equivalent plot for the other bursts show normally-distributed samples, but this burst shows significant structure in the samples.
+\label{fig:corner}}
+\end{center}
+\end{figure}
 
-**Does DM correlate with other spectral/flux properties?**
+While most bursts are modeled with well-defined parameter probability distributions, one burst is an outlier.
+Figure \ref{fig:corner} shows the scatterplot matrix for the MCMC run on burst 57646 \citep{corner}.
+Two clusters of samples are identified for this burst: one narrow, low-DM and one wide, high-DM.
+The model seems to be too simple for this burst.
+This is consistent with high-resolution Arecibo burst spectra \citep{WEIRD}, which show that bursts are composed of "sub-bursts" that drift in frequency.
 
 \subsubsection{Dispersion}
-The initial VLA detections were made by searching a DM grid that allowed inter-DM sensitivity losses up to roughly 10\% \citep[$\Delta DM=10\ \rm{pc}\ \rm{cm}^{-3}$][]{2003ApJ...596.1142C}.
-In optimizing detection significance over a fine DM grid, we find optimal DM values range from 552 to 572 pc cm$^{-3}$.
+The initial VLA detections were made with a matched-filter approach that allowed inter-DM sensitivity losses up to roughly 10\% \citep[$\Delta DM=10\ \rm{pc}\ \rm{cm}^{-3}$][]{2003ApJ...596.1142C}. 
+%In optimizing detection significance over a fine DM grid, we find optimal DM values range from 552 to 572 pc cm$^{-3}$.
 However, the uncertainty in the peak DM measurement is defined by the signal-to-noise of the burst and how this changes with DM.
+The MCMC modeling is more sophsticated in that it considers a wider range of parameters and models both data and observing effects (frequency-time pixel boundaries) simultaneously.
 
-Given that the apparent DM can potentially change due to intrinsic or extrinsic effects, we developed a more sophisticated system for modeling dispersion.
-We created a generative model to sample the likelihood distribution as a function of DM \citep{2010arXiv1008.4686H}.
-We use the Gaussian shape (see \S \ref{sec:spec}) along the spectral axis and apply a frequency-dependent delay for a given dispersion model.
-The likelihood is directly sampled by calculating the product of probabilities on a per-pixel basis of the 2-dimensional dynamic spectrum.
-Uncertainties in each pixel are drawn from a uniform Gaussian error distribution that is estimated from the data.
+The top panel of Figure \ref{fig:dmmodel} shows the 95\% confidence intervals on the DM for all nine VLA bursts as a function of burst time.
+The burst DMs are not consistent with any single value and tend to be larger than the reference value of 560.5 pc cm$^{-3}$.
+The range and variance in DM observed by the VLA is similar to that reported for \frb\ in \citet{2016arXiv160308880S}.
+As noted before, this is consistent with the idea that the DM measured at low resolution (e.g., by the VLA) is defined by true dispersion and some intrinsic structure that changes between bursts.
+The VLA data demonstrate that this intrinsic DM effect is visible at frequencies near 3~GHz.
+Assuming a "true" DM of 560.5 pc cm$^{-3}$, the excess DM can be thought of as a frequency-dependent delay that is intrinsic to the burst with a delay rate of 1--2~ms GHz$^{-1}$.
 
-Figure \ref{fig:dmmodel} compares the 95\% confidence intervals on the DM for all nine VLA bursts to the range of DM previous observed \citep{2014ApJ...790..101S,2016arXiv160308880S}.
-The DM confidence intervals are not consistent with each other or a single DM.
-This suggests that there are apparent DM changes between bursts, either due to intrinsic burst structure or actual changes to the DM column density.
-Elsewhere, we present high-resolution dynamic spectra at 1.4~GHz that show how intrinsic spectral structure can bias the apparent DM of individual bursts \citep{WEIRD}.
-The FRB emission process has not yet been defined, so it is not clear how the intrinsic structure can bias DM as a function of frequency.
+The bottom panel of Figure \ref{fig:dmmodel} compares the DM to the modeled temporal width of the bursts.
+There is a weak correlation between burst width and apparent DM.
+A change in width of $\sim1$~ms correlates with a change in apparent DM of approximately $5$~pc cm$^{-3}$.
+If the excess DM is
 
@@
 \includegraphics[width=0.9\columnwidth]{dmmodel}
-\caption{DM as a function of time for nine 3~GHz bursts detected by the VLA.
-The 95\% confidence interval on DM is shown with a bar and the dahsed line shows the best-fit DM$=560.5$\ pc cm$^{-3}$ inferred for Arecibo observations at 1.4~GHz (CITE: WEIRD).
+
+\includegraphics[width=0.9\columnwidth]{burst_dmdt}
+
+\caption{(Top) DM as a function of time for nine 3~GHz bursts detected by the VLA.
+The 95\% confidence interval on DM is shown with a bar and the dahsed line shows the best-fit DM$=560.5$\ pc cm$^{-3}$ inferred for Arecibo observations at 1.4~GHz.
+(Bottom) Burst DM versus temporal width for all nine VLA bursts.
 \label{fig:dmmodel}}
@@
 
-% TODO: Non-lambda$^{2}$ dispersion...
-
 \subsection{Temporal Statistics}
 \label{sec:temp}
-Geoff comments:
--- need to clarify that burst rate change is significant
--- not clear how significant nondetections are, since observational details not obvious yet
-
-Burst detections were made very inhomogenously through the 2016 observing campaign and total 63 hours.
+The burst rate for \frb\ varied dramatically throughout the 2016 observing campaign (Figure \cite{fig:multi}).
 In the early-2016 campaign, we observed for 30 hours at S-band and no bursts were detected.
@@
 Assuming that the burst detection probability follows a Poisson distribution, the nondetection in the first half of S-band limits the FRB rate to $\rm{R}<0.1$\ hour$^{-1}$\ (95\% confidence limit).
-The mean detection rate for S-band observing during the late-2016 campaign was $\rm{R}=0.33\pm0.1$\ hour$^{-1}$.
+The S-band burst rate was much higher during the late-2016 campaign, $\rm{R}=0.33\pm0.1$\ hour$^{-1}$.
 
-There is weak evidence that the \frb\ burst rate decreased through the S-band observing in the late-2016 campaign.
+%There is weak evidence that the \frb\ burst rate decreased through the S-band observing in the late-2016 campaign.
 We modeled the event detection probability as a Poisson probability function, $P_i(\lambda)$, with rate parameter that evolves linearly in time relative to the first VLA burst $\lambda = a + b (\rm{MJD}_i - 57623)$.
@@
 This weak constraint is consistent with the broader trend of a changing rate seen on month timescales by Arecibo.
-
+%
 %\begin{figure}[htb]
@@
 %\end{figure}
-
-During the late-2016 observing campaign, the typical observation lasted about two hours and was sampled with a 5~ms cadence.
+%
+%During the late-2016 observing campaign, the typical observation lasted about two hours and was sampled with a 5~ms cadence.
 We used the Lomb-Scargle periodogram \citep{1982ApJ...263..835S} to search for periodic structure over a wide range of timescales.
 The time series is calculated by binning the burst detection rate per 100~ms \citep[always either 0 or 1, see also][]{2011MNRAS.417.1871P}.
-The spectral power calculated for periods between 0.8 and 80 s shows no power in excess of the typical 95\% confidence bound estimated from shuffled data.
+%The spectral power calculated for periods between 0.8 and 80 s shows no power in excess of the typical 95\% confidence bound estimated from shuffled data.
 We verified that simulating nine bursts drawn from a simple rotational model would produce excess power using this approach.
@@
 \label{sec:disn}
-Knowing the burst distance, we calculate their total energy by integrating flux in time and frequency (Table \ref{tab:spec}).
+Knowing the source distance, we calculate the burst energy by integrating flux in time and frequency (Table \ref{tab:spec}).
 Some VLA burst spectra seem to be contained by the 2.5 to 3.5~GHz band and most of them seem to have Gaussian envelopes that are well modeled by the emission within the 2.5 to 3.5~GHz band.
 Assuming that the Gaussian shape defines the emission window, the mean S-band flux density can be converted to a total energy with no further assumptions about their spectral properties.
-We proceed under this assumption here and discuss caveats is \S \ref{sec:disc}.
+We proceed under this assumption here and discuss caveats in \S \ref{sec:disc}.
 
@@
 Using a maximum likelihood technique, we estimate the best powerlaw index of $\alpha=-0.6^{+0.2}_{-0.4}$ (68\% confidence interval), which is equivalent to a $dN/dE$\ powerlaw index of --1.6.
-This model assumes a completeness limit for a luminosity equivalent to an $8\sigma$\ flux density limit.
-This is consistent with the high and uniform data quality and the false positive rate in this observing campaign.
+This model assumes a completeness limit for a luminosity equivalent to an $8\sigma$\ flux density limit, which is consistent with the high and uniform data quality.
 
@@
 
-\subsubsection{Spectral Autocorrelation}
-\label{sec:auto}
-Autocorrelation of the burst signal (both temporal and spectral) can be used to infer both intrinsic properties and modulation due to scintillation \citep{CORDES}.
+%\subsubsection{Spectral Autocorrelation}
+%\label{sec:auto}
+%Autocorrelation of the burst signal (both temporal and spectral) can be used to infer both intrinsic properties and modulation due to scintillation \citep{CORDES}.
 Figure \ref{fig:acf} shows the spectral autocorrellation for the strongest burst (MJD 57633.68).
@@
 This is broadly consistent with expectations of Galactic diffractive scintillation bandwidth \citep[3--9~MHz near 3~GHz][]{2002astro.ph..7156C}.
-
+%
 %**Does channel-scale structure only appear around 3~GHz?**
-
-\begin{figure}[htb]
-\begin{center}
-\includegraphics[width=0.9\columnwidth]{acf_57633_scan7}
-\caption{The spectral autocorrelation as a function of frequency for the burst from \frb\ at MJD 57633.68.
+%
+%\begin{figure}[htb]
+%\begin{center}
+%\includegraphics[width=0.9\columnwidth]{acf_57633_scan7}
+%\caption{The spectral autocorrelation as a function of frequency for the burst from \frb\ at MJD 57633.68.
 The largest black dots show the autocorrelation for the data, smaller dots show the autocorrelation for the best Gaussian model, and dashed line shows the autocorrelation of an off-burst spectrum.
-\label{fig:acf}}
-\end{center}
-\end{figure}
-
-\subsubsection{Circular Polarization}
-The VLA S-band recievers measure circular polarization, although for observing efficiency we choose not to include polarization calibration procedures.
-Constraints on circular polarization are possible since the gain calibrator is a well-known polarization calibrator with little Stokes V flux.
-In that case, the apparent circular polarization fraction is $(RR-LL)/(RR+LL)$, which for the most significant bursts is at most 3\%.
-\frb\ was located 2.3\arcmin away from pointing center, where systematic effects have been measured as large as 3\% (Perley et al 2016, VLA memo).
-Given that systematic effects dominate the apparent circular polarization, we conclude that the true fractional circular polarization is less than 3\%.
+%\label{fig:acf}}
+%\end{center}
+%\end{figure}
 

### 2017-03-17 repeater-vladata.tex
reworking table. adding errors to dm, dt

@@
 Of these bursts, only one VLA burst (on MJD 57648) was simultaneously detected by another observatory (Arecibo).
-The VLA and Arecibo burst detections had significances of 25$\sigma$\ and 39$\sigma$, respectively.
-The VLA and Arecibo integrated flux densities were 111 mJy and 14 mJy, respectively.
+The VLA and Arecibo burst detections had significances of 25$\sigma$\ and 39$\sigma$ with integrated flux densities of 111 mJy and 14 mJy, respectively.
 
@@
 The dispersion correction for both data sets assumed a DM of 560.5 pc cm$^{-3}$, which was typical of the source during the observing campaign \citep{WEIRD}.
-The regridded dynamic spectrum has an apparent DM error that is evident either as a frequency-dependent time drift within the Arecibo observation or in the relative alignment of Arecibo and the VLA bursts.
-Both of these drifts are consistent with an effective DM (i.e., one that maximizes the detection S/N ratio) of $sim$562 pc cm$^{-3}$.
+The regridded dynamic spectrum has an apparent DM error that is evident both as a frequency-dependent time drift within the Arecibo observation and as an offset between the Arecibo and VLA bursts.
+Both of these drifts are consistent with an effective DM (i.e., one that maximizes the detection S/N ratio) of $sim$565 pc cm$^{-3}$.
+This is consistent with modeling of the VLA spectrum described in \S \ref{sec:spec}.
 
@@
 The black line separates data from the VLA (2.5 to 3.5~GHz) and Arecibo (1.0 to 1.8~GHz).
-The Arecibo to VLA gain ratio is assumed to be 10.
+The amplitude scale is normalized by assuming the Arecibo to VLA gain ratio is 10.
  \label{fig:sgram}}
@@
 \begin{table*}
-\caption{Properties of Bursts from \frb **update**}
+\caption{Properties of Bursts from \frb}
 \centering
@@
 \hline
-Date                & S$_{\rm{I,int}}$  & Image S/N & E$_{\rm{int}}$ & DM$_{\rm{opt}}$ & dt & S$_{\rm{I,peak}}$ & Center & FWHM & S$_{\rm{V}}$ \\
-(MJD)               & (mJy)           &           & ($10^{38}$\ erg) & (pc cm$^{-3})$ & (ms) & (mJy) & (GHz)  & (MHz) & (mJy) \\ \hline
-57623.74402686      & 194             & 38        & 11 & 562.1 & & 690 & 2.8 & 290 & +3 \\ % 7.8  & 562.5 & 460 & 2.8 & 300 & +3 \\
-57633.67986367      & 1500            & 179       & 97 & 561.3 & & 3350 & 3.2 & 510 & --35 \\ % 65   & 561.4 & 2200 & 3.2 & 520 & --35 \\
-57633.69515938\tablenotemark{a} & 69  & 15        & 7 & 555.8 & & $>$430 & $<$2.5 & 290 & +2 \\ % 5.9  & 555.4 & $>$320 & $<$2.5 & $>$320 & +2 \\
-57638.49937435      & 55              & 12        & 3 & 558.6 & & 130 & 3.1 & 410 & +5 \\ % 1.8  & 554.9 & 70 & 3.1 & 440 & +5 \\
-57643.45730263      & 508             & 100       & 34 & 558.7 & & 1170 & 2.8 & 510 & --5 \\ % 13   & 559.3 & 440 & 2.8 & 530 & --5 \\
-57645.42958602      & 64              & 13        & 4 & 555.9 & & 170 & 2.8 & 380 & +3 \\ % 2.6  & 554.1 & 50 & 2.7 & 970 & +3 \\
-57646.46600650\tablenotemark{a} & 87  & 20        & 10 & 562.4 & & $>$420 & $<$2.5 & 420 & +1 \\ % 3.9  & 568.1 & $>$190 & $<$2.5 & $>$360 & +1 \\
-57648.43691490\tablenotemark{b} & 111 & 25        & 7 & 557.4 & & 260 & 2.8 & 470 & +9 \\ % 2.9  & 557.8 & 110 & 2.8 & 440 & +9 \\
-57649.45175697      & 167             & 36        & 12 & 559.9 & & 290 & 3.0 & 690 & +1 \\ \hline % 6.3  & 559.9 & 80 & 2.9 & 1400 & +1 \\ \hline
+Date                & Image S/N & S$_{\rm{I,int}}$	& S$_{\rm{V}}$ 	& E$_{\rm{int}}$ & DM$_{\rm{opt}}$ & dt 	 & S$_{\rm{I,peak}}$ & Center & FWHM \\
+(MJD)               &           & (mJy) 			& (mJy) 		& ($10^{38}$\ erg)& (pc cm$^{-3})$ & (ms) & (mJy) 	& (GHz)  & (MHz) \\ \hline
+57623.74402686      & 38 		& 194				& +3			& 11 			& 567$\pm2$ 		& 2.0$\pm0.2$	 		& 690 		& 2.8 		& 290 \\
+57633.67986367      & 179 		& 1500				& --35 			& 98				& 568.2$\pm0.2$ 	& 2.05$\pm0.02$			& 3340 	& 3.2 		& 510 \\
+57633.69515938\tablenotemark{a} & 15 & 69			& +2			& 7  			& 562$^{+4}_{-6}$ 	& 2.5$^{+0.9}_{-0.6}$	& $>$430 	& $<$2.5	& 290 \\
+57638.49937435      & 12 		& 55				& +5 			& 3  			& 567$^{+7}_{-9}$ 	& 1.3$^{+1.4}_{-0.8}$	& 130 		& 3.1 		& 420 \\
+57643.45730263      & 100 		& 508				& --5 			& 34 			& 565.6$^{+0.6}_{-0.5}$ & 1.9$\pm0.1$		& 1170 	& 2.8 		& 510 \\
+57645.42958602      & 13 		& 64 				& +3			& 4  			& 563$^{+5}_{-4}$ 	& 1.0$\pm0.7$		 	& 170 		& 2.8 		& 380 \\
+57646.46600650\tablenotemark{a} & 20 & 87			& +1			& 10 			& 569$\pm5$ 		& 2.7$^{+0.9}_{-1.4}$	& $>$420 	& $<$2.5 	& 430 \\
+57648.43691490\tablenotemark{b} & 25 & 111			& +9			& 7  			& 564$\pm2$ 		& 1.4$^{+0.3}_{-0.4}$	& 260 		& 2.8 		& 470 \\
+57649.45175697      & 36 		& 167				& +1			& 12 			& 567$\pm2$ 		& 2.1$\pm0.5$		 	& 290 		& 3.0 		& 690 \\ \hline
 \end{tabular}
@@
 MCMC sampling requires a generative model for the data, so we wrote functions in Python to create 2d dynamic spectra.
-The dynamic spectra are modeled in the spectral domain as a Gaussian envelope and in the temporal domain by a dispersive delay (scaling as frequency squared).
+The dynamic spectra are generated in the spectral domain as a Gaussian envelope and in the temporal domain by a dispersive delay that scales as frequency squared.
 We further allow the pulses to have a finite temporal width.
@@
 Starting at the top left (moving right and then down), they correspond to bursts on MJDs 57623, 57633.68, 57633.70, 57638, 57643, 57645, 57646, 57648, and 57649.
-The solid line is a best-fit Gaussian model found through probabilistic modeling.
+The solid line is a best-fit Gaussian model found through MCMC modeling.
 Note that bursts are detected in 5~ms images generated from dedispersed visibilities.
@@
 Since the burst crosses many time-frequency pixel boundaries, the temporal modeling is sensitive to temporal properties smaller than the 5~ms integration time.
-Table \ref{tab:spec} shows that the typical burst width is measured as $2\pm1$~ms (95\% confidence interval); the brightest burst (57633.68) has a temporal width of $2.05\pm0.05$~ms.
+Table \ref{tab:spec} shows that the typical burst width is measured as $2\pm1$~ms (95\% confidence interval); the brightest burst (57633.68) has a temporal width of $2.05\pm0.02$~ms.
 The burst arrival times are typically measured with a precision of 1~ms; the brightest burst arrival time is measured with a precision of $\sim50\mu$s.
@@
 The top panel of Figure \ref{fig:dmmodel} shows the 95\% confidence intervals on the DM for all nine VLA bursts as a function of burst time.
-The burst DMs are not consistent with any single value and tend to be larger than the reference value of 560.5 pc cm$^{-3}$.
-The range and variance in DM observed by the VLA is similar to that reported for \frb\ in \citet{2016arXiv160308880S}.
-As noted before, this is consistent with the idea that the DM measured at low resolution (e.g., by the VLA) is defined by true dispersion and some intrinsic structure that changes between bursts.
-The VLA data demonstrate that this intrinsic DM effect is visible at frequencies near 3~GHz.
-Assuming a "true" DM of 560.5 pc cm$^{-3}$, the excess DM can be thought of as a frequency-dependent delay that is intrinsic to the burst with a delay rate of 1--2~ms GHz$^{-1}$.
+The burst DMs are not consistent with any single value and tend to be larger than the long-term average of 560.5 pc cm$^{-3}$.
+The range and variance in DM observed by the VLA is similar to that reported for Arecibo observations of \frb\ in \citet{2016arXiv160308880S}.
+As noted before, this is consistent with the idea that the DM measured at low resolution (e.g., by the VLA) is defined by true (extrinsic) dispersion and some spectral structure that changes between bursts.
+The VLA data demonstrate that the burst-dependent DM effect is visible at frequencies near 3~GHz.
+Assuming a "true" DM of 560.5 pc cm$^{-3}$, the excess DM can be thought of as a frequency-dependent delay that varies between bursts with a delay rate up to 2~ms GHz$^{-1}$.
 

### 2017-03-18 repeater-vladata.tex
restructured table. spectrum discussion ok

@@
 The VLA and Arecibo burst detections had significances of 25$\sigma$\ and 39$\sigma$ with integrated flux densities of 111 mJy and 14 mJy, respectively.
+Assuming a powerlaw flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha\approx2.7$.
 
@@
 The regridded dynamic spectrum has an apparent DM error that is evident both as a frequency-dependent time drift within the Arecibo observation and as an offset between the Arecibo and VLA bursts.
-Both of these drifts are consistent with an effective DM (i.e., one that maximizes the detection S/N ratio) of $sim$565 pc cm$^{-3}$.
+Both of these drifts are consistent with an apparent DM of $sim$565 pc cm$^{-3}$.
 This is consistent with modeling of the VLA spectrum described in \S \ref{sec:spec}.
@@
 Three of the four VLA bursts with simultaneous observing coverage by Arecibo were not detected at Arecibo.
-Even the one simultaneous detection at Arecibo was an order of magnitude fainter than seen by the VLA, so it is clear that the 3~GHz burst flux is not correlated with that at 1.4~GHz.
+Numerous bursts were also detected by Arecibo during VLA observing, but were not detected by the VLA at 3~GHz.
+Considering this, and the order of magnitude difference in flux density for the one simultaneous burst detection, we conclude that the 3~GHz burst flux is not correlated with that at 1.4~GHz.
 
@@
 \centering
-\begin{tabular}{lccccccccc}
+\begin{tabular}{l|ccc|cccccc}
 \hline
-Date                & Image S/N & S$_{\rm{I,int}}$	& S$_{\rm{V}}$ 	& E$_{\rm{int}}$ & DM$_{\rm{opt}}$ & dt 	 & S$_{\rm{I,peak}}$ & Center & FWHM \\
-(MJD)               &           & (mJy) 			& (mJy) 		& ($10^{38}$\ erg)& (pc cm$^{-3})$ & (ms) & (mJy) 	& (GHz)  & (MHz) \\ \hline
-57623.74402686      & 38 		& 194				& +3			& 11 			& 567$\pm2$ 		& 2.0$\pm0.2$	 		& 690 		& 2.8 		& 290 \\
-57633.67986367      & 179 		& 1500				& --35 			& 98				& 568.2$\pm0.2$ 	& 2.05$\pm0.02$			& 3340 	& 3.2 		& 510 \\
-57633.69515938\tablenotemark{a} & 15 & 69			& +2			& 7  			& 562$^{+4}_{-6}$ 	& 2.5$^{+0.9}_{-0.6}$	& $>$430 	& $<$2.5	& 290 \\
-57638.49937435      & 12 		& 55				& +5 			& 3  			& 567$^{+7}_{-9}$ 	& 1.3$^{+1.4}_{-0.8}$	& 130 		& 3.1 		& 420 \\
-57643.45730263      & 100 		& 508				& --5 			& 34 			& 565.6$^{+0.6}_{-0.5}$ & 1.9$\pm0.1$		& 1170 	& 2.8 		& 510 \\
-57645.42958602      & 13 		& 64 				& +3			& 4  			& 563$^{+5}_{-4}$ 	& 1.0$\pm0.7$		 	& 170 		& 2.8 		& 380 \\
-57646.46600650\tablenotemark{a} & 20 & 87			& +1			& 10 			& 569$\pm5$ 		& 2.7$^{+0.9}_{-1.4}$	& $>$420 	& $<$2.5 	& 430 \\
-57648.43691490\tablenotemark{b} & 25 & 111			& +9			& 7  			& 564$\pm2$ 		& 1.4$^{+0.3}_{-0.4}$	& 260 		& 2.8 		& 470 \\
-57649.45175697      & 36 		& 167				& +1			& 12 			& 567$\pm2$ 		& 2.1$\pm0.5$		 	& 290 		& 3.0 		& 690 \\ \hline
+Date                & Image S/N & S$_{\rm{I,int}}$	& S$_{\rm{V}}$ 	& DM$_{\rm{opt}}$ 	& dt 			& S$_{\rm{I,peak}}$ & Center & FWHM & E$_{\rm{int}}$ \\
+(MJD)               &           & (mJy) 			& (mJy) 		& (pc cm$^{-3})$ 	& (ms) 			& (mJy) 			& (GHz)  & (MHz) & ($10^{38}$\ erg)\\ \hline
+57623.74402686      & 38 		& 194				& +3			& 567$\pm2$ 		& 2.0$\pm0.2$	 		& 690 		& 2.8 		& 290 & 11 			\\
+57633.67986367      & 179 		& 1500				& --35 			& 568.2$\pm0.2$ 	& 2.05$\pm0.02$			& 3340 		& 3.2 		& 510 & 98				\\
+57633.69515938\tablenotemark{a} & 15 & 69			& +2			& 562$^{+4}_{-6}$ 	& 2.5$^{+0.9}_{-0.6}$	& $>$430 	& $<$2.5	& 290 & 7  			\\
+57638.49937435      & 12 		& 55				& +5 			& 567$^{+7}_{-9}$ 	& 1.3$^{+1.4}_{-0.8}$	& 130 		& 3.1 		& 420 & 3  			\\
+57643.45730263      & 100 		& 508				& --5 			& 565.6$^{+0.6}_{-0.5}$ & 1.9$\pm0.1$		& 1170 		& 2.8 		& 510 & 34 			\\
+57645.42958602      & 13 		& 64 				& +3			& 563$^{+5}_{-4}$ 	& 1.0$\pm0.7$		 	& 170 		& 2.8 		& 380 & 4  			\\
+57646.46600650\tablenotemark{a} & 20 & 87			& +1			& 569$\pm5$ 		& 2.7$^{+0.9}_{-1.4}$	& $>$420 	& $<$2.5 	& 430 & 10 			\\
+57648.43691490\tablenotemark{b} & 25 & 111			& +9			& 564$\pm2$ 		& 1.4$^{+0.3}_{-0.4}$	& 260 		& 2.8 		& 470 & 7  			\\
+57649.45175697      & 36 		& 167				& +1			& 567$\pm2$ 		& 2.1$\pm0.5$		 	& 290 		& 3.0 		& 690 & 12 			\\ \hline
 \end{tabular}
@@
 We present the first simultaneous detection of an FRB with multiple telescopes and over frequencies from 1.2 to 3.5~GHz.
-After correcting for barycentric and dispersion delays, we find a residual temporal drift in the burst spectrum.
-This is consistent with \citet{WEIRD}, which uses bright, coherently-dedispersed bursts to define a heuristic that distinguishes between intrinsic and extrinsic dispersion-like effects.
-The low-resolution dynamic spectra presented here cannot distinguish between these two effects.
-However, by assuming that the extrinsic (true) DM is consistent with the long-term average of 560.5 pc cm$^{-3}$, we can ascribe the observed burst drift (Figure \ref{fig:sgram}) to intrinsic effects.
-Under this assumption, the burst drift is intrinsic and consistent with the intrinsic drft rate measured in \citet[$\sim$100~MHz/ms;][]{WEIRD}.
+At the same time, three other bursts had similar observing coverage but were not detected simultaneously.
+Given that the Arecibo detection is an order of magntude weaker than the VLA detection and that multiple VLA bursts appear largely within the 3~GHz band, we conclude that \frb\ burst spectra are not well described by a powerlaw.
+Instead, bursts spectrally are well-described by a Gaussian-like shape with a 500~MHz-scale envelope.
+This is consistent with \citet{WEIRD}, which uses high-resolution Arecibo spectra to identify rich spectral structure ("sub-bursts") intrinsic to each burst.
 
-The 57648 burst is nearly an order of magnitude brighter near 3~GHz than at 1.4~GHz.
-Expressed as a spectral index ($S_{\nu} \propto \nu^{\alpha}$), we find $\alpha\approx2.7$.
-However, the bursts detected here and described in \citet{WEIRD} make it clear that burst spectral power is not well described by a powerlaw.
+After correcting for barycentric and typical dispersion delays, the VLA/Arecibo burst spectrum shows a residual temporal drift.
+This drift can be interpreted as an excess DM of roughly 5 pc cm$^{-3}$.
+This excess DM is similar in size to the burst-to-burst variation in DM measured for the whole sample of VLA 3~GHz bursts and had been noted in earlier 1.4~GHz Arecibo observations of \frb \citep{2016arXiv160308880S}.
+The VLA bursts demonstrate that this ''excess'', burst-specific DM is seen up to 3~GHz.
+The simultaneous VLA/Arecibo burst shows that the (instantaneous) burst properties from 1.2 to 3.5~GHz are consistent with a single excess.
 
-Given the high sensitivity of Arecibo...
-Even the one AO detection is 10x fainter...
-** is one of three VLA bursts with L-band coverage by Arecibo, which implies that those bursts had a smaller spectral width.
-However, all three VLA bursts with L-band Arecibo observations were relatively weak, so it is difficult to rule out L-band emission entirely.
-However, as described in \S \ref{sec:spec}, some of the VLA bursts peak within the band from 2.5 to 3.5~GHz, which implies a much smaller spectral coverage for typical bursts.
+These features are generally consistent with intrinsic burst properties described in \citet{WEIRD}.
+That work uses bright, coherently-dedispersed bursts to define a heuristic that distinguishes between burst-specific and time-stationary dispersion-like effects.
+They show that the bursts are composed of "sub-bursts" that preferentially drift to lower frequencies at later times, which systematically biases DM measurements that maximize S/N ratio.
+Interestingly, our MCMC modeling of the VLA bursts shows a weak correlation between larger apparent DM and pulse width.
+This could be a signature of blending of many unresovled sub-bursts in a single VLA burst spectrum.
+Assuming a long-term average DM of 560.5 pc cm$^{-3}$, we can ascribe the observed excess DM to an intrinsic burst drift rate measured on the order of $\sim100$~MHz/ms.
 
-burst rate is correlated between vla and ao, but not the intensity of individual bursts...
-
-Propagation effects (e.g., scintillation, scattering) can also modify the radio signal in a variety of ways and the duration of the emission in the source frame is not known \citep{2016arXiv160505890C}.
+The burst-specific DM structure could be intrinsic to the emission mechanism or induced during propagation.
+Radio waves can be modified in a variety of ways (e.g., scintillation, scattering) and the duration of the emission in the source frame is not known \citep{2016arXiv160505890C}.
 \citet{CORDES} describe a model where plasma lensing near the source of an FRB can magnify radio emission by orders of mangitude.
@@
 
--- Self-organized criticality in the sun. energy powerlaw=-1.7 \citep{2011SoPh..274...99A}
--- **Similarity to magnetar energy distribution**
+The nine bursts were detected with a wide range of significance (12 to 179$\sigma$) and the apparent burst energy distribution can be characterized as a powerlaw $dN/dE\propto E^{-1.6}$.
+With only 9 VLA bursts, it is difficult to draw strong inferences, but a similar energy index has been observed in X-ray fluxes of solar flares \citep{2011SoPh..274...99A} and gamma-ray fluence for soft-gamma repeaters \citep{2000ApJ...532L.121G, 2011ApJ...739...94S}.
+This distribution is similar to that seen in earthquakes and other phenomena generally termed ''self-organized criticality'' \citep{2011SoPh..274...99A}.
 
-The Lorimer burst was surprising for its unusually large flux with a lack of lower-significance detections.
-As more FRBs have been detected, we continue to be surprised by their apparent brightness of FRBs \citep{2016arXiv161105758R}.
-This perception has been validated with analysis of the FRB cumulative fluence distribution, which when modeled as a powerlaw ($dN/dF \propto F^{\alpha}$) has an index $-0.5<\alpha<-0.9$\ \citep{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}.
-For a uniform distribution of sources with a single luminosity, this index should be --1.5 \citep[the ``Euclidean'' distribution, e.g.,][]{2016MNRAS.462..941L}.
-
-The energy distribution of \frb\ bursts has also produced some surprises.
-The nine bursts were detected with a wide range of significance (12 to 179$\sigma$) and the apparent burst energy distribution can be characterized as a powerlaw $dN/dE\propto E^{-1.6}$.
+FRB detections have often been far brighter than the limiting brightness of telescopes detecting them \citep{2007Sci...318..777L, 2016arXiv161105758R}.
+This perception has been supported by analysis that suggests that the cumulative flux distribution ($dN/dF \propto F^{\alpha}$) is relatively flat \citep[$-0.5<\alpha<-0.9$;][]{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}.
+For a uniform distribution of sources, we expect a ''Euclidean distribution'' with $\alpha=-1.5$ \citep{2016MNRAS.462..941L}.
+V/Vmax
 If all FRBs luminosities are drawn from such a distribution, then their flux distribution will be determined by the underlying energy distribution and its interplay with redshift space distortions.
@@
 
+Studying a cosmological source population will require making redshift corrections.
+The limited envelope of bursts from \frb\ suggest that spectral extrapolations based on a spectral index are not likely to be reliable.
+It is more reasonable to treat the FRB rate as a frequency-dependent property, than to scaling from a single rate via a spectral index.
+
+burst rate is correlated between vla and ao, but not the intensity of individual bursts...
+
 %\subsection{Naming Convention}

### 2017-03-22 repeater-vladata.tex
removing most simulation work. energy distribution figure looking good

@@
 A change in width of $\sim1$~ms correlates with a change in apparent DM of approximately $5$~pc cm$^{-3}$.
-If the excess DM is
 
@@
 Knowing the source distance, we calculate the burst energy by integrating flux in time and frequency (Table \ref{tab:spec}).
-Some VLA burst spectra seem to be contained by the 2.5 to 3.5~GHz band and most of them seem to have Gaussian envelopes that are well modeled by the emission within the 2.5 to 3.5~GHz band.
+Some VLA burst spectra seem to be contained by the 2.5 to 3.5~GHz band and most of them seem to have Gaussian envelopes that are well modeled by the emission within that band.
 Assuming that the Gaussian shape defines the emission window, the mean S-band flux density can be converted to a total energy with no further assumptions about their spectral properties.
-We proceed under this assumption here and discuss caveats in \S \ref{sec:disc}.
 
-Figure \ref{fig:ed} shows the \frb\ burst energy cumulative distribution and best-fit model.
-We modeled the differential energy distribution, $dN/d\log{E}$, as a Poisson probability distribution with a rate function $\lambda\propto E^{\alpha}$.
-Using a maximum likelihood technique, we estimate the best powerlaw index of $\alpha=-0.6^{+0.2}_{-0.4}$ (68\% confidence interval), which is equivalent to a $dN/dE$\ powerlaw index of --1.6.
-This model assumes a completeness limit for a luminosity equivalent to an $8\sigma$\ flux density limit, which is consistent with the high and uniform data quality.
+Figure \ref{fig:ed} shows the \frb\ burst energy cumulative distribution as seen by the VLA and calculated from prior observations by Arecibo and the GBT \citep{2016Natur.531..202S,2016arXiv160308880S}.
+The latter two energy distributions are scaled from the fluence by assuming that all burst energy is included by the observation.
+This likely underestimates the burst energy for some bursts by a factor of a few, but should not affect the slope of the distribution.
+The Arecibo and GBT energies were scaled by factors of {\color{red} 2 and 1 (help)}, respectively, to correct for the sensitivity loss due to the primary beam.
+
+Broadly, the range of energies shown in Figure \ref{fig:ed} is defined by the sensitivity of the telescope and the duration of the observing campaign.
+The VLA distribution shown represents the 27-hour, late-2016 campaign, which is longer than the single-dish campaigns presented here.
+However, since the VLA observations have a relatively coarse time resolution, it is not as sensitive as Arecibo and the GBT, so no bursts were detected weaker than $3\times10^{38}$~erg.
+The rate upper limit (95\% confidence) from the early-2016 VLA campaign shows that even identical observing campaigns have different detection rates.
+
+We modeled the differential energy distribution, $dN/d\log{E}$, using a Poisson probability distribution with a rate function $\lambda = A E^{\alpha}$.
+Rather than trying to estimate a completeness limit for each energy distribution, we assume an effective detection limit of 0.9 times the weakest burst detected; the best-fit slope is weakly dependent on this, but general conclusions are robust.
+We directly sampled the likelihood distribution to estimate a best slope of $\alpha_{\rm{VLA}}=-0.7^{+0.3}_{-0.4}$, $\alpha_{\rm{AO}}=-0.8^{+0.3}_{-0.5}$, and $\alpha_{\rm{GBT}}=-0.8^{+0.4}_{-0.5}$ (68\% confidence interval).
+Expressed as a powerlaw function in $dN/dE$, the slope index is approximately --1.7.
 
@@
 \includegraphics[width=0.9\columnwidth]{energy_disn}
-\caption{Dots and solid line show the  \frb\ burst energy cumulative distribution.
-The dashed line shows the best fit from a maximum likelihood analysis using the powerlaw model $dN/d\log{E} \propto E^{\alpha}$.
-The 95\% bounds on the best-fit powerlaw index is $\alpha=-0.6^{+0.2}_{-0.4}$.
+\caption{The cumulative burst energy distributions for the VLA, Arecibo, and GBT are shown with dots connected by solid, dashed, and dotted lines, respectively.
+The Arecibo distribution is derived from the 11 1.4~GHz bursts reported in \citet{2016Natur.531..202S} and the GBT distribution is derived from the 5 1.4~GHz bursts reported in \citet{2016arXiv160308880S}.
+An upper limit from the VLA nondetection in early 2016 is shown as a triangle.
 \label{fig:ed}}
@@
 The refined analysis shows that \frb\ has even higher isotropic energies than previously reported, reaching energies $E_{\rm{max}}\approx10^{40}$\ erg.
-We now know that \frb\ is detectable with the VLA out to $z=0.7$\ and much farther with Arecibo.
+We now know that \frb\ is detectable with the VLA out to $z=0.7$.
 \frb\ has isotropic energies orders of magnitude higher than the strongest Crab pulsar pulses ($\sim10^{35}$~erg) and comparable brightness temperatures \citep[$T_b^{\rm{Crab}}\sim10^{41}$~K versus $T_b^{\rm{FRB 121102}}\sim10^{38}$~K;][]{2003Natur.422..141H,2014PhRvD..89j3009K}.
@@
 
-The nine bursts were detected with a wide range of significance (12 to 179$\sigma$) and the apparent burst energy distribution can be characterized as a powerlaw $dN/dE\propto E^{-1.6}$.
-With only 9 VLA bursts, it is difficult to draw strong inferences, but a similar energy index has been observed in X-ray fluxes of solar flares \citep{2011SoPh..274...99A} and gamma-ray fluence for soft-gamma repeaters \citep{2000ApJ...532L.121G, 2011ApJ...739...94S}.
-This distribution is similar to that seen in earthquakes and other phenomena generally termed ''self-organized criticality'' \citep{2011SoPh..274...99A}.
+In \S \ref{sec:disn} we compare the energy distribution of the 9 VLA bursts to those reported earlier by Arecibo and the GBT.
+In all cases, bursts are detected over a wide range of significance that is indicative of a relatively flat distribution.
+All three energy distributions can be characterized as a powerlaw in $dN/dE$ with slope $\sim-1.7$.
+This slope is seen even though the burst rate varies by almost an order of magnitude between observations and frequencies cover both 1.4 and 3~GHz bands.
+This suggests that the slope is related to the underlying physical process, rather than the state at any given time.
+The value of the energy distribution slope is similar to that observed in X-ray fluxes of solar flares \citep{2011SoPh..274...99A} and gamma-ray fluence of bursts from soft-gamma repeaters \citep{2000ApJ...532L.121G, 2011ApJ...739...94S}.
+In these cases, the value of the slope is close to the theoretical expectation for self-regulated critical phenomena \citep[slope$=-5/3$;][]{2011SoPh..274...99A}.
 
+This work expands the redshift horizon for detectability of \frb, suggesting that cosmological effects are even more important for understanding properites of the FRB population.
+An early observable property of the FRB population is the flux distribution, $dN/dF \propto F^{\alpha}$.
+For a uniform distribution of sources, the powerlaw index, $\alpha$, takes on the special value of --1.5 \citep[the ''Euclidean distribution'';][]{2016MNRAS.462..941L}.
+Deviations from the Euclidean distribution have been used to suggest that GRBs were indeed a cosmological distribution.
+Multiple studies have suggested that FRBs have a ''flat'' flux distribution \citep[$-0.5<\alpha<-0.9$;][]{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}, although others have cautioned that a powerlaw distribution is an approximation that can confuse any meaningful inferences \citep{2017arXiv170208040C}.
+
+\citet{2017arXiv170208040C} describe show how the measured flux distribution is sensitive to the maximum distance...
 FRB detections have often been far brighter than the limiting brightness of telescopes detecting them \citep{2007Sci...318..777L, 2016arXiv161105758R}. 
-This perception has been supported by analysis that suggests that the cumulative flux distribution ($dN/dF \propto F^{\alpha}$) is relatively flat \citep[$-0.5<\alpha<-0.9$;][]{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}.
-For a uniform distribution of sources, we expect a ''Euclidean distribution'' with $\alpha=-1.5$ \citep{2016MNRAS.462..941L}.
-V/Vmax
-If all FRBs luminosities are drawn from such a distribution, then their flux distribution will be determined by the underlying energy distribution and its interplay with redshift space distortions.
+This is well known in the study of GRBs, which used the $V/V_{\rm{max}}$\ test (ratio of maximum to limiting brightness) to first infer that that population was cosmological \citep{1992ApJ...388L..45M}.
 
-We tested this idea by simulating FRB populations and measuring the properties of a flux-limited sub-sample.
-First, we assume an FRB population that is uniformly distributed in space from redshifts $z1$\ to $z2$.
-For each FRB source, we generate one FRB burst with a luminosity drawn from the \frb\ energy distribution and calculate its flux.
-We then select the brightest 15 \citep[equal to the current sample size used in modeling;][]{2016ApJ...830...75V} and fit a powerlaw to the $dN/dF$\ distribution.
-Typically, a large ($N>10000$) population of such bursts is needed to avoid edge effects in the properties of the flux-limited subsample.
+Effects relevant to FRBs:
+- redshift space distortion
+- time dilation (rate calculation correction scales as $1+z$)
+- frequency-dependent FRB rate
+All tend to flatten the $dN/dF$\ distribution with increasing z.
 
-Figure \ref{fig:sim} shows an example of an FRB population simulation with a $dN/dE$\ distribution like \frb.
-We use visualizations like this to verify that the simulations are not affected by edge effects.
-We can also reproduce a Euclidean flux distribution for a standard candle-like luminosity distribution at low redshift and that distributions out to $z2\sim2$ have a flatter index ($\Delta\alpha\sim0.2$) due to redshift space distortions.
+The VLA and Arecibo observed intensively during the late-2016 campaign, but a complete search for bursts from the Arecibo is ongoing.
+Soon we will be able to calculate a frequency-dependent burst rate, but early results suggest that the burst rate at a fixed energy is much higher at 1.4~GHz than at 3~GHz.
+If so, we should expect an additional redshift-dependent effect that will flatten the $dN/dF$\ distribution.
 
-\begin{figure*}[htb]
-\begin{center}
-\includegraphics[width=1.8\columnwidth]{sim_L1.6}
-\caption{An example of a simulated FRB population.
-(Top left) The input luminosity distribution, which follows the \frb\ distribution of $dN/dE\propto E^{-1.6}$.
-(Top right) The input redshift space distribution of a uniform distribution of FRB sources.
-(Bottom left) The measured flux distribution of the simulation with red lines showing fits to the whole population and brightest 15 FRBs.
-(Bottom right) The flux-redshift distribution of the simulated population.
-The dahsed line shows the limiting flux that includes the brightest 15 sources.
-\label{fig:sim}}
-\end{center}
-\end{figure*}
-
-To study how the input parameters affect the measured flux distribution, so we generated 100 populations to measure 68\% confidence intervals on the cumulative flux distribution index.
-Figure \ref{fig:ind} shows the result of several such measurements for input luminosity distribution index ranging from --2.2 to --1.2.
-Generally, the measured flux distribution index flattens as the input luminosity distributions flattens.
-The best constraint on the flux distribution index \citep{2016ApJ...830...75V} requires an input energy distribution index between roughly --2.1 and --1.4, which is consistent with the measured energy distribution for \frb.
-These simulations predict a mean a mean redshift between 0.9 and 1.8, which is in weak tension with the mean FRB redshift inferred from DM.
-For a mean total DM of $750$\ pc cm$^{-3}$ and a mean host DM of 200 pc cm$^{-3}$, we expect a mean redshift of $\sim0.6$ \citep[$z=DM/900$\ pc cm$^{-3}$;][]{2004MNRAS.348..999I}.
-
-\begin{figure}[htb]
-\begin{center}
-\includegraphics[width=0.9\columnwidth]{sim_index_scaling}
-\caption{Scaling of apparent flux distribution index for given luminosity (or energy) distribution index.
-\label{fig:ind}}
-\end{center}
-\end{figure}
-
-While the \frb\ burst energy distribution is consistent with the overall FRB population, this simulation ignores many observational biases (scattering, observing coverage) and the effects of galaxy evolution, which is likely significant over the range of redshifts to which \frb is detectable \citep[e.g.,][]{2010ApJ...709..644I}.
+%While the \frb\ burst energy distribution is consistent with the overall FRB population, this simulation ignores many observational biases (scattering, observing coverage) and the effects of galaxy evolution, which is likely significant over the range of redshifts to which \frb is detectable \citep[e.g.,][]{2010ApJ...709..644I}.
 The burst energies are estimated from observations from 2.5 to 3.5~GHz, which may be a biased selection of all bursts or may not include all burst emission.
@@
 The AMI-LA telescope gratefully acknowledges support from the European Research Council under grant ERC-2012- StG-307215 LODESTONE, the UK Science and Technology Facilities Council (STFC) and the University of Cambridge.
+We acknowledge...
+Aspen Center for Physics
+Liam Connor
 

### 2017-03-22 repeater-vladata.tex
reasonable spectral and rate discussion sections

@@
 \subsection{Burst Spectra}
+
 We present the first simultaneous detection of an FRB with multiple telescopes and over frequencies from 1.2 to 3.5~GHz.
-At the same time, three other bursts had similar observing coverage but were not detected simultaneously.
-Given that the Arecibo detection is an order of magntude weaker than the VLA detection and that multiple VLA bursts appear largely within the 3~GHz band, we conclude that \frb\ burst spectra are not well described by a powerlaw.
-Instead, bursts spectrally are well-described by a Gaussian-like shape with a 500~MHz-scale envelope.
-This is consistent with \citet{WEIRD}, which uses high-resolution Arecibo spectra to identify rich spectral structure ("sub-bursts") intrinsic to each burst.
+The Arecibo burst flux density is an order of magntude less than that seen by the VLA.
+At the same time, three other bursts from \frb\ had similar observing coverage but were not detected simultaneously.
+This is consistent with the spectral structure observed within the 3~GHz VLA band, which is typically limited to a Gaussian envelope with width of roughly 500~MHz.
+The center frequency of this envelope is a unique property of each burst and does not show an obvious pattern between bursts.
+
+If \frb\ burst spectra are typical of the larger FRB population, then population models need to be generalized beyond the assumption of a spectral powerlaw.
+Most obviously, \frb\ implies that future multi-telescope searches for bursts are unlikely to simultaneously detect bursts in different bands.
+Second, since burst spectra have limited bands, the burst detection rate at one frequency may not represent that at another.
+That will require rate estimates for the FRB population to be made explicitly frequency-dependent.
+Finally, we note that the odds of detecting a burst will improve with bandwidth for bandwidths wider than their characteristic scale.
 
@@
 This drift can be interpreted as an excess DM of roughly 5 pc cm$^{-3}$.
-This excess DM is similar in size to the burst-to-burst variation in DM measured for the whole sample of VLA 3~GHz bursts and had been noted in earlier 1.4~GHz Arecibo observations of \frb \citep{2016arXiv160308880S}.
-The VLA bursts demonstrate that this ''excess'', burst-specific DM is seen up to 3~GHz.
-The simultaneous VLA/Arecibo burst shows that the (instantaneous) burst properties from 1.2 to 3.5~GHz are consistent with a single excess.
+We also measure a burst-to-burst variation in DM within the whole sample of VLA 3~GHz bursts of a similar scale.
+This variation had been noted in earlier 1.4~GHz Arecibo observations of \frb \citep{2016arXiv160308880S}, but the VLA bursts demonstrate that this ''excess'', burst-specific DM is seen up to 3~GHz.
+The simultaneous VLA/Arecibo burst also shows that an individual burst's properties from 1.2 to 3.5~GHz are consistent with a single excess.
 
 These features are generally consistent with intrinsic burst properties described in \citet{WEIRD}.
-That work uses bright, coherently-dedispersed bursts to define a heuristic that distinguishes between burst-specific and time-stationary dispersion-like effects.
-They show that the bursts are composed of "sub-bursts" that preferentially drift to lower frequencies at later times, which systematically biases DM measurements that maximize S/N ratio.
-Interestingly, our MCMC modeling of the VLA bursts shows a weak correlation between larger apparent DM and pulse width.
+That work uses bright, coherently-dedispersed bursts to identify ''sub-bursts'' that preferentially drift to lower frequencies at later times.
+With high-resolution dynamic spectra, one can define a heuristic that distinguishes between a burst-specific dispersion-like effect and a more stable (''true'') dispersion.
+Since the sub-bursts tend to drift to lower frequencies, they systematically bias DM measurements made with low-resolution data (like the VLA and earlier Arecibo and GBT obsrevaitons).
+Interestingly, our modeling of the VLA burst dynamic spectra show a weak correlation between larger apparent DM and pulse width.
 This could be a signature of blending of many unresovled sub-bursts in a single VLA burst spectrum.
-Assuming a long-term average DM of 560.5 pc cm$^{-3}$, we can ascribe the observed excess DM to an intrinsic burst drift rate measured on the order of $\sim100$~MHz/ms.
 
@@
 \subsection{Energy and Flux Distribution}
+
 The refined analysis shows that \frb\ has even higher isotropic energies than previously reported, reaching energies $E_{\rm{max}}\approx10^{40}$\ erg.
-We now know that \frb\ is detectable with the VLA out to $z=0.7$.
 \frb\ has isotropic energies orders of magnitude higher than the strongest Crab pulsar pulses ($\sim10^{35}$~erg) and comparable brightness temperatures \citep[$T_b^{\rm{Crab}}\sim10^{41}$~K versus $T_b^{\rm{FRB 121102}}\sim10^{38}$~K;][]{2003Natur.422..141H,2014PhRvD..89j3009K}.
-While this emission is coherent and strongly beamed \citep{2016Natur.531..202S, WEIRD}, the energy scale is still larger than any known Galactic radio transient and requires either a new process or dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}.
+%While this emission is coherent and strongly beamed \citep{2016Natur.531..202S, WEIRD}, the energy scale is still larger than any known Galactic radio transient and requires either a new process or dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}.
 
 In \S \ref{sec:disn} we compare the energy distribution of the 9 VLA bursts to those reported earlier by Arecibo and the GBT.
-In all cases, bursts are detected over a wide range of significance that is indicative of a relatively flat distribution.
 All three energy distributions can be characterized as a powerlaw in $dN/dE$ with slope $\sim-1.7$.
@@
 This suggests that the slope is related to the underlying physical process, rather than the state at any given time.
-The value of the energy distribution slope is similar to that observed in X-ray fluxes of solar flares \citep{2011SoPh..274...99A} and gamma-ray fluence of bursts from soft-gamma repeaters \citep{2000ApJ...532L.121G, 2011ApJ...739...94S}.
-In these cases, the value of the slope is close to the theoretical expectation for self-regulated critical phenomena \citep[slope$=-5/3$;][]{2011SoPh..274...99A}.
+The value of the energy distribution slope is similar to that observed in gamma-ray fluence of bursts from soft-gamma repeaters \citep{2000ApJ...532L.121G, 2011ApJ...739...94S}.
+This similarity has been used to argue that bursts are driven by self-regulated critical phenomena \citep[slope$=-5/3$;][]{2011SoPh..274...99A}.
 
-This work expands the redshift horizon for detectability of \frb, suggesting that cosmological effects are even more important for understanding properites of the FRB population.
-An early observable property of the FRB population is the flux distribution, $dN/dF \propto F^{\alpha}$.
-For a uniform distribution of sources, the powerlaw index, $\alpha$, takes on the special value of --1.5 \citep[the ''Euclidean distribution'';][]{2016MNRAS.462..941L}.
-Deviations from the Euclidean distribution have been used to suggest that GRBs were indeed a cosmological distribution.
-Multiple studies have suggested that FRBs have a ''flat'' flux distribution \citep[$-0.5<\alpha<-0.9$;][]{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}, although others have cautioned that a powerlaw distribution is an approximation that can confuse any meaningful inferences \citep{2017arXiv170208040C}.
+While the surprising brightness of new FRB discoveries was once seen as a cause for concern (i.e., a sign of terrestrial interference), we may be able to use this to infer properties of the overall population \citep{2007Sci...318..777L, 2016arXiv161105758R}.
+When modeling the flux distribution as a powerlaw, an isotropic distribution of sources will have a powerlaw index, $\alpha$, of --1.5 \citep[the ''Euclidean distribution'';][]{2016MNRAS.462..941L}.
+Prior to the measurement of the first GRB redshift, deviations from the Euclidean distribution were used to infer their cosmological distribution \citep[e.g., the $V/V_{\rm{max}}$\ test;][]{1992ApJ...388L..45M, 1995ApJ...453...25F}.
+Multiple studies have suggested that FRBs have a ''flat'' flux distribution \citep[$-0.5<\alpha<-0.9$;][]{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}.
+Others have noted that the flux distribution is not well modeled as a powerlaw, such that $\alpha$\ is effectively sensitivity (and telescope) dependent \citep{2016MNRAS.461..984O, 2017arXiv170208040C}.
 
-\citet{2017arXiv170208040C} describe show how the measured flux distribution is sensitive to the maximum distance...
-FRB detections have often been far brighter than the limiting brightness of telescopes detecting them \citep{2007Sci...318..777L, 2016arXiv161105758R}. 
-This is well known in the study of GRBs, which used the $V/V_{\rm{max}}$\ test (ratio of maximum to limiting brightness) to first infer that that population was cosmological \citep{1992ApJ...388L..45M}.
+We now know that \frb\ is detectable with the VLA out to $z=0.7$, which suggests that cosmological effects are even more important for understanding properites of the FRB population.
+\citet{2017arXiv170208040C} demonstrate how redshift space distortions, time dilation, and spectral index (''k-correction'') effects can flatten the flux distribution.
+To this complex scene, we add the fact that \frb\ burst spectra are not defined by a spectral index, which suggests that k-corrections are likely to be very difficult to calculate in practice.
+Rather than using wide band burst spectra to measure a single ''typical'' spectral index, we now must measure the burst rate as a function of frequency.
+These need not be measured simultaneously, but rather contemporaneously to insure they represent a similar state of activitity of the FRB.
 
-Effects relevant to FRBs:
-- redshift space distortion
-- time dilation (rate calculation correction scales as $1+z$)
-- frequency-dependent FRB rate
-All tend to flatten the $dN/dF$\ distribution with increasing z.
-
-The VLA and Arecibo observed intensively during the late-2016 campaign, but a complete search for bursts from the Arecibo is ongoing.
-Soon we will be able to calculate a frequency-dependent burst rate, but early results suggest that the burst rate at a fixed energy is much higher at 1.4~GHz than at 3~GHz.
-If so, we should expect an additional redshift-dependent effect that will flatten the $dN/dF$\ distribution.
+If we assume \frb\ is representative of the FRB population, we can estimate this frequency-dependent burst rate.
+The VLA and Arecibo observed intensively in a coordinated fashion during the late-2016 campaign.
+A complete search for bursts from the Arecibo is ongoing, but early results suggest that the burst rate at a fixed energy is much higher at 1.4~GHz than at 3~GHz.
+This suggests that high-redshift FRBs will have an apparently lower rate that flattens the $dN/dF$\ distribution in a manner similar to a k-correction.
+We can only infer the presence of this effect for observations near 1.4~GHz, since we have no estimate of the \frb\ burst rate outside the frequency range from 1.4 to 3~GHz.
+Propagation effects suggest that the rate will be lower at sub-GHz frequencies \citep{2017MNRAS.465.2286R}.
+If so, the tension between constraints on $\alpha$\ near 800~MHz and 1.4~GHz may be resolved by a frequency-dependent FRB rate that peaks near 1.4~GHz.
 
@@
 \subsection{Repetition}
+
 The burst rate analysis presented in \S \ref{sec:temp} shows that the detection probability of \frb\ is not stationary.
@@
 However, future efforts to localize FRBs are still most likely to succeed by targeting known FRBs to catch repetitions, assuming that all FRBs repeat.
-Finally, we note that the average spectral coverage of bursts from \frb\ are relatively narrow ($<1$~GHz) and the coverage changes dramatically between bursts.
-Thus, the odds of detecting a burst will improve linearly with bandwidth for bandwidths wider than this characteristic scale.
-
-Studying a cosmological source population will require making redshift corrections.
-The limited envelope of bursts from \frb\ suggest that spectral extrapolations based on a spectral index are not likely to be reliable.
-It is more reasonable to treat the FRB rate as a frequency-dependent property, than to scaling from a single rate via a spectral index.
-
-burst rate is correlated between vla and ao, but not the intensity of individual bursts...
 

### 2017-03-23 repeater-vladata.tex
working on volumetric rate and slsn connection

@@
 
-The burst rate analysis presented in \S \ref{sec:temp} shows that the detection probability of \frb\ is not stationary.
-As mentioned above, this could be caused by intrinsic events (e.g., magnetar outburst) or propagation effects.
-While a detailed analysis of temporal correlation will require more bursts and/or more sophistication, it is clear that \frb\ has significant correlation on short timescales \citep[sometimes called a ``red spectrum'';][]{2016MNRAS.458L..89C}.
-Another way of stating this is that the detection of a burst improves odds of finding more bursts in near-future observations.
+The chance of detecting a burst with the VLA changes substantially on day--month timescales.
+A major outstanding question is whether this time-variable rate is driven by an intrinsic process \citep{2016ApJ...826..226K} or extrinsic (propagation) effects \citep{CORDES}.
+However, the temporal distribution of VLA detections alone shows that \frb\ has significant correlation on short timescales.
+That is, detecting a burst predicts you are more likely to find another burst soon thereafter and not detecting a burst predicts you will likey not detect another burst soon thereafter.
+While this is sometimes referred to as a ''red spectrum'' \citep{2016MNRAS.458L..89C}, the observations presented here are only sensitive to timescales of days (time between observations) and months (time between campaigns).
 
 If this statistical property describes other FRBs, it weakens previous constraints on repetition \citep{2015MNRAS.454..457P,2015ApJ...807...16L}.
-It is possible that other FRBs have repeating bursts, although calculating a limit requires knowing the temporal correlation function that defines the repetition.
-Repetition also implies that there are fewer phyiscal sources of FRBs than implied by the burst detection rate.
+It is possible that other FRBs have repeating bursts, but calculating a limit requires knowing their temporal correlation function.
+Wide, shallow surveys are the preferred strategy for blind detection of FRBs.
+Also, since ''bursts predict bursts'', many short observations are more likely to blindly detect an FRB than a single long observation of the same total length.
 
-FRBs like SGRs? 2016ApJ...826..226K
+\subsection{Rate Comparison}
 
-\subsection{FRB Rate}
-% cut from gemini paper. TODO: incorporate referee comments on rate scale. Sarah?
-{\color{red} Sarah: can you update this as a per-SFR rate?}
-Assuming that \frb\ is from the same population as the other FRBs, the measurement of a distance for the host of \frb\ allows us to re-evaluate the cosmic volume and event rate per galaxy for the FRB population.
-The estimated projected FRB rate $R_p$\ understates the true rate by a beaming fraction $\Omega_b$\ \citep[$\sim$10\%;][]{1998MNRAS.298..625T}.
-For a comoving volume $V(z)$\ and galaxy number density $\Phi(M)$, the rate per galaxy is $R_{FRB} = R_p /(\Omega_b \Phi(M)V (z))$.
+The calculation of a volumetric rate has been used to identify classes of transient and their defining physical processes \citep{2006ARA&A..44..507W, 2012Sci...337..927G}.
+\citet{2013Sci...341...53T} used this approach to estimate an isotropic rate of $10^{-3}$\ galaxy$^{-1}$\ yr$^{-1}$ by assuming a characteristic redshift horizon of 0.9.
+This rate is high \citep[comparable to the rate of core-collapse supernovae;][]{2006Natur.439...45D}, which has been used to argue that FRBs are likely not associated with other classes of transient, such as GRBs or rarer SNe.
 
-The first such rate estimate was made by \citet{2013Sci...341...53T}, who used the measured DM to estimate a characteristic distance for their sample of 4 FRBs.
-They assumed that all of the extragalactic component of the DM was caused by the IGM and scaled as $DM\approx z\times1200 \rm{pc}\ \rm{cm}^{-3}$\ \citep{2003ApJ...598L..79I,2004MNRAS.348..999I}.
-They also calculated the number of galaxies by assuming a characteristic $L_*$\ galaxy \citep[corresponding to stellar mass $M_* \approx 1011 M$;][]{2012MNRAS.421..621B}.
+This conclusion is in tension with new models inspired by multi-wavelength associations to \frb.
+Its coincidence with a compact, persistent radio source is consistent with \frb as a young magnetar in a luminous pulsar wind nebula \citep{2017arXiv170104815K}.
+At the same time, \frb is found in a low-metallicity dwarf galaxy, which is the preferred environment for long GRBs and Type-I superluminous supernovae \citep[LGRB and SLSN-I, respectively;][]{2017arXiv170102370M}.
 
-**add error bar?**
-Our calculation differs in that we have better estimates of all three parameters.
-First, the projected FRB rate is now believed to be closer to $2\times10^3\ \rm{sky}^{-1} \rm{day}^{-1}$\ at high Galactic latitudes and flux densities brighter than 1 Jy ms \citep{2016arXiv161100458L,2016MNRAS.460L..30C, 2016MNRAS.455.2207R}.
-\frb\ is associated with a relatively small galaxy ($5\times10^7$\ Msun), which are roughly a factor of 100 more abundant \citep[$\Phi(M) \approx 10^{-2} \rm{Mpc}^{-3}$;][]{2007ApJ...665..265F}.
-Finally, the measured distance for FRB 121102 suggests that the extragalactic DM has comparable contributions from the IGM and host galaxy.
+We now reevaluate this rate using the properties of \frb\ as a prototype FRB.
+First, we recast this estimate as a beamed, volumetric rate, $R_{FRB} = R_p /(\Omega_b V (z))$, where $R_p$\ is the projected FRB rate, $\Omega_b$\ is the beaming fraction \citep[$\sim0.1$;][]{1998MNRAS.298..625T} and $V(z)$\ is the volume out to redshift $z$.
+Second, the projected FRB rate is now believed to be lower than initially believed \citep[$2\times10^3\ \rm{sky}^{-1} \rm{day}^{-1}$\ at high Galactic latitudes and flux densities brighter than 1 Jy ms; ][]{2016arXiv161100458L, 2016MNRAS.460L..30C, 2016MNRAS.455.2207R}.
+Including these effects, we estimate a volumetric rate of $6\times10^{-5} (0.1/\Omega_b)$\ Mpc$^{-3}$\ yr$^{-1}$, assuming a typical FRB horizon redshift of 0.9.
+For comparison, the LGRB and SLSN-I rates are orders of magnitude lower, near $10^{-8}$ Mpc$^{-3}$\ yr$^{-1}$ \citep{2012Sci...337..927G}.
 
-This reduces the characteristic distance by a factor of two and the volume by an order of magnitude.
-Considering these factors, we assume a characteristic redshift of the population that is twice that of \frb\ to estimate $R_{FRB} \approx 10^{-4} (0.1/\Omega_b) \rm{galaxy}^{-1} \rm{year}^{-1}$, which is two orders of magnitude lower than previously estimated \citep[assuming isotropic radiation;]{2013Sci...341...53T}.
+The revised FRB rate is an improvement, but it still ignores multiple effects.
+The burst spectral structure discussed here shows that this estimate likely underestimates the FRB rate by missing bursts that fall outside the observing band (typically a few hundred MHz near 1.4~GHz).
+For a typical burst envelope width of 500~MHz centered at GHz-scale frequencies, this could underestimate the rate by a factor of a few.
+The horizon scale ($z=0.9$) is not well defined and can change the implied rate by an order of magnitude.
 
-There are significant caveats to the comparison of this rate to the rates of other classes of transient.
-This isotropic FRB rate assumes a projected FRB rate at a single (observationally defined) flux limit and that no bursts repeat.
+sensitivity is the biggest awkward factor!
+an out: use luminosity distribution for absolute rate scale?
+
+calculate number of repetitions and compare to Metzger limit
+
+%DM dominated by the IGM \citep[$DM\approx z\times1200 \rm{pc}\ \rm{cm}^{-3}$ for fully ionized hydrogen or $DM\approx z\times900 \rm{pc}\ \rm{cm}^{-3}$ for more realistic ionization state;][]{2003ApJ...598L..79I,2004MNRAS.348..999I}.
+%galaxy number density $\Phi(M)$
+%They also calculated the number of galaxies by assuming a characteristic $L_*$\ galaxy \citep[corresponding to stellar mass $M_* \approx 1011 M$;][]{2012MNRAS.421..621B}.
+%
+%This isotropic FRB rate assumes a projected FRB rate at a single (observationally defined) flux limit and that no bursts repeat.
 Using this calculation with data from more sensitive telescopes, we might infer a higher rate.
@@
 In this model, these two effects partially cancel, although without a physical model it is difficult to say how well.
-
-\subsection{Observing Strategies}
-As discussed above, \citet{2016MNRAS.458L..89C} note that the FRB repetition implies that the number of FRB-generating sources is smaller than implied by the number of bursts.
-In some scenarios, this means that there are areas on the sky that may contain no FRBs.
-Wide, shallow surveys are the preferred strategy for blind detection of FRBs.
-However, future efforts to localize FRBs are still most likely to succeed by targeting known FRBs to catch repetitions, assuming that all FRBs repeat.
 

### 2017-03-23 repeater-vladata.tex
refining frb rate discussion

@@
 
-The calculation of a volumetric rate has been used to identify classes of transient and their defining physical processes \citep{2006ARA&A..44..507W, 2012Sci...337..927G}.
-\citet{2013Sci...341...53T} used this approach to estimate an isotropic rate of $10^{-3}$\ galaxy$^{-1}$\ yr$^{-1}$ by assuming a characteristic redshift horizon of 0.9.
+The calculation of a volumetric rate has been used to identify classes of transient and their defining physical processes \citep{2006ARA&A..44..507W}.
+\citet{2013Sci...341...53T} used this approach to estimate an isotropic rate of $10^{-3}$\ galaxy$^{-1}$\ yr$^{-1}$ by assuming a characteristic redshift horizon of 0.9 and a typical Milky Way-like galaxy host.
 This rate is high \citep[comparable to the rate of core-collapse supernovae;][]{2006Natur.439...45D}, which has been used to argue that FRBs are likely not associated with other classes of transient, such as GRBs or rarer SNe.
@@
 At the same time, \frb is found in a low-metallicity dwarf galaxy, which is the preferred environment for long GRBs and Type-I superluminous supernovae \citep[LGRB and SLSN-I, respectively;][]{2017arXiv170102370M}.
+**biased tracer of star formation**
 
 We now reevaluate this rate using the properties of \frb\ as a prototype FRB.
-First, we recast this estimate as a beamed, volumetric rate, $R_{FRB} = R_p /(\Omega_b V (z))$, where $R_p$\ is the projected FRB rate, $\Omega_b$\ is the beaming fraction \citep[$\sim0.1$;][]{1998MNRAS.298..625T} and $V(z)$\ is the volume out to redshift $z$.
+First, we recast this estimate as volumetric rate of FRB sources by including beaming and repetition effects.
+The volumetric source rate is $R_{FRB} = R_p /(N_r \Omega_b V (z))$, where $R_p$\ is the projected FRB rate, $N_r$\ is the number of bursts per source, $\Omega_b$\ is the beaming fraction \citep[$\sim0.1$;][]{1998MNRAS.298..625T} and $V(z)$\ is the volume out to redshift $z$.
 Second, the projected FRB rate is now believed to be lower than initially believed \citep[$2\times10^3\ \rm{sky}^{-1} \rm{day}^{-1}$\ at high Galactic latitudes and flux densities brighter than 1 Jy ms; ][]{2016arXiv161100458L, 2016MNRAS.460L..30C, 2016MNRAS.455.2207R}.
-Including these effects, we estimate a volumetric rate of $6\times10^{-5} (0.1/\Omega_b)$\ Mpc$^{-3}$\ yr$^{-1}$, assuming a typical FRB horizon redshift of 0.9.
+
+% alternatively
+% Third, the measured energy distributions for \frb\ allow us to estimate their detectability out to the distances implied by their DMs.
+% 
+% what is the energy distribution of known FRBs assuming their DM measures distance?
+
+Third, the largest published DM \citep[$\sim1500$\ pc cm$^{-3}$ and much higher values rumored;][]{2016MNRAS.460L..30C} may imply a larger cosmic volume for FRBs.
+Assuming a DM dominated by the IGM \citep[$DM\approx z\times900 \rm{pc}\ \rm{cm}^{-3}$ for realistic ionization state;][]{2003ApJ...598L..79I,2004MNRAS.348..999I}, this places a maximum FRB redshift on the order of 2, near the peak the in the cosmic star formation history \citep{2014ARA&A..52..415M}.
+While this is consistent with magnetar models proposed for \frb, the DM may include significant contributions from the host galaxy and intervening galaxy halos \citep{2014ApJ...780L..33M}.
+Using an assumed horizon redshift of 2, we estimate a rate of $R_p = 10^{-5} N_r^{-1} (0.1/\Omega_b)$\ Mpc$^{-3}$\ yr$^{-1}$.
+
+This revised FRB rate still ignores multiple effects.
+Narrow burst spectral structure implies that observations underestimate by missing bursts that fall outside the observing band.
+For a typical burst envelope width of 500~MHz centered at GHz-scale frequencies, past observations (typically using bandwidths of a few hundred MHz near 1.4~GHz) would underestimate the rate by a factor of a few.
+The horizon scale is not well defined and can change the implied rate by a factor of $\sim5$.
+
 For comparison, the LGRB and SLSN-I rates are orders of magnitude lower, near $10^{-8}$ Mpc$^{-3}$\ yr$^{-1}$ \citep{2012Sci...337..927G}.
 
-The revised FRB rate is an improvement, but it still ignores multiple effects.
-The burst spectral structure discussed here shows that this estimate likely underestimates the FRB rate by missing bursts that fall outside the observing band (typically a few hundred MHz near 1.4~GHz).
-For a typical burst envelope width of 500~MHz centered at GHz-scale frequencies, this could underestimate the rate by a factor of a few.
-The horizon scale ($z=0.9$) is not well defined and can change the implied rate by an order of magnitude.
-
-sensitivity is the biggest awkward factor!
-an out: use luminosity distribution for absolute rate scale?
-
-calculate number of repetitions and compare to Metzger limit
-
-%DM dominated by the IGM \citep[$DM\approx z\times1200 \rm{pc}\ \rm{cm}^{-3}$ for fully ionized hydrogen or $DM\approx z\times900 \rm{pc}\ \rm{cm}^{-3}$ for more realistic ionization state;][]{2003ApJ...598L..79I,2004MNRAS.348..999I}.
 %galaxy number density $\Phi(M)$

### 2017-03-24 repeater-vladata.tex
looking good on the rate!

@@
 **magnetar birth?**
+Its coincidence with a compact, persistent radio source is consistent with \frb as a young magnetar powering a luminous pulsar wind nebula \citep{2017arXiv170104815K}.
+At the same time, \frb is found in a low-metallicity dwarf galaxy, which is the preferred environment for long GRBs and Type-I superluminous supernovae \citep[LGRB and SLSN-I, respectively;][]{2017arXiv170102370M}.
+It has been suggested that these other classes of transient are signatures of the birth of magnetars that are only born in low-metallicity environments.
 Also, it has not been demonstrated that \frb\ is representative of the overall FRB population.
@@
 
-The calculation of a volumetric rate has been used to identify classes of transient and their defining physical processes \citep{2006ARA&A..44..507W}.
-\citet{2013Sci...341...53T} used this approach to estimate an isotropic rate of $10^{-3}$\ galaxy$^{-1}$\ yr$^{-1}$ by assuming a characteristic redshift horizon of 0.9 and a typical Milky Way-like galaxy host.
+The calculation of a volumetric rate has been used to study classes of optical and high-energy transient \citep{2006ARA&A..44..507W}.
+\citet{2013Sci...341...53T} used this approach to estimate a rate of $10^{-3}$\ galaxy$^{-1}$\ yr$^{-1}$ by assuming an isotropic emitter in a Milky Way-type galaxy out to a characteristic redshift horizon of 0.9.
 This rate is high \citep[comparable to the rate of core-collapse supernovae;][]{2006Natur.439...45D}, which has been used to argue that FRBs are likely not associated with other classes of transient, such as GRBs or rarer SNe.
 
-This conclusion is in tension with new models inspired by multi-wavelength associations to \frb.
-Its coincidence with a compact, persistent radio source is consistent with \frb as a young magnetar in a luminous pulsar wind nebula \citep{2017arXiv170104815K}.
-At the same time, \frb is found in a low-metallicity dwarf galaxy, which is the preferred environment for long GRBs and Type-I superluminous supernovae \citep[LGRB and SLSN-I, respectively;][]{2017arXiv170102370M}.
-**biased tracer of star formation**
+However, inferences based on this and related rates are difficult, since they are strongly dependent on the sensitivity of the telescopes.
+Here we reevaluate the FRB volumetric rate by assuming \frb\ is a prototype of the class.
+We also update the volumetric rate to use the latest projected FRB rate \citep[$2\times10^3\ \rm{sky}^{-1} \rm{day}^{-1}$\ at high Galactic latitudes and flux densities brighter than 1 Jy ms; ][]{2016arXiv161100458L, 2016MNRAS.460L..30C, 2016MNRAS.455.2207R}.
 
-We now reevaluate this rate using the properties of \frb\ as a prototype FRB.
-First, we recast this estimate as volumetric rate of FRB sources by including beaming and repetition effects.
-The volumetric source rate is $R_{FRB} = R_p /(N_r \Omega_b V (z))$, where $R_p$\ is the projected FRB rate, $N_r$\ is the number of bursts per source, $\Omega_b$\ is the beaming fraction \citep[$\sim0.1$;][]{1998MNRAS.298..625T} and $V(z)$\ is the volume out to redshift $z$.
-Second, the projected FRB rate is now believed to be lower than initially believed \citep[$2\times10^3\ \rm{sky}^{-1} \rm{day}^{-1}$\ at high Galactic latitudes and flux densities brighter than 1 Jy ms; ][]{2016arXiv161100458L, 2016MNRAS.460L..30C, 2016MNRAS.455.2207R}.
+We recast the estimate as volumetric rate of FRB sources by including beaming and repetition effects.
+The volumetric source rate is $R_{FRB} = R_p /(N_r \Omega_b V (z))$, where $R_p$\ is the projected FRB rate, $N_r$\ is the number of bursts per source, $\Omega_b$\ is the beaming fraction, and $V(z)$\ is the volume out to redshift $z$.
 
-% alternatively
-% Third, the measured energy distributions for \frb\ allow us to estimate their detectability out to the distances implied by their DMs.
-% 
-% what is the energy distribution of known FRBs assuming their DM measures distance?
+The characteristic distance scale for FRBs can be inferred from the detectability of \frb.
+The projected FRB rate is defined for a fluence limit of 1 Jy ms which is detectable out to $z=2\ for the Parkes surveys that have detected the most FRBs.
+This distance is consistent with that inferred from the largest DMs observed \citep[$\sim1500$\ pc cm$^{-3}$;][]{2016MNRAS.460L..30C}.
+This assumes that DM is dominated by the IGM \citep[$DM\approx z\times900 \rm{pc}\ \rm{cm}^{-3}$\ for realistic ionization state;][]{2003ApJ...598L..79I,2004MNRAS.348..999I}, although other contributions are likely significant \citep{2014ApJ...780L..33M}.
+An independent argument for a characteristic distance of $z=2$\ is that it corresponds to the peak the in the cosmic star formation history \citep{2014ARA&A..52..415M} and most leading models for FRBs are driven by star formation \citep{2016MNRAS.462..941L,2016ApJ...826..226K,2017arXiv170104815K}.
 
-Third, the largest published DM \citep[$\sim1500$\ pc cm$^{-3}$ and much higher values rumored;][]{2016MNRAS.460L..30C} may imply a larger cosmic volume for FRBs.
-Assuming a DM dominated by the IGM \citep[$DM\approx z\times900 \rm{pc}\ \rm{cm}^{-3}$ for realistic ionization state;][]{2003ApJ...598L..79I,2004MNRAS.348..999I}, this places a maximum FRB redshift on the order of 2, near the peak the in the cosmic star formation history \citep{2014ARA&A..52..415M}.
-While this is consistent with magnetar models proposed for \frb, the DM may include significant contributions from the host galaxy and intervening galaxy halos \citep{2014ApJ...780L..33M}.
 Using an assumed horizon redshift of 2, we estimate a rate of $R_p = 10^{-5} N_r^{-1} (0.1/\Omega_b)$\ Mpc$^{-3}$\ yr$^{-1}$.
-
-This revised FRB rate still ignores multiple effects.
 Narrow burst spectral structure implies that observations underestimate by missing bursts that fall outside the observing band.
 For a typical burst envelope width of 500~MHz centered at GHz-scale frequencies, past observations (typically using bandwidths of a few hundred MHz near 1.4~GHz) would underestimate the rate by a factor of a few.
-The horizon scale is not well defined and can change the implied rate by a factor of $\sim5$.
+There is also relatively little constraint on the beaming factor \citep[$\sim0.1$ for pulsars;][]{1998MNRAS.298..625T}.
+This estimate also assumes that propagation effects do not significantly affect the detectability of FRBs, although scintillation likely plays a significant role \citep{2015MNRAS.451.3278M, CORDES}.
 
-For comparison, the LGRB and SLSN-I rates are orders of magnitude lower, near $10^{-8}$ Mpc$^{-3}$\ yr$^{-1}$ \citep{2012Sci...337..927G}.
-
-%galaxy number density $\Phi(M)$
-%They also calculated the number of galaxies by assuming a characteristic $L_*$\ galaxy \citep[corresponding to stellar mass $M_* \approx 1011 M$;][]{2012MNRAS.421..621B}.
-%
-%This isotropic FRB rate assumes a projected FRB rate at a single (observationally defined) flux limit and that no bursts repeat.
-Using this calculation with data from more sensitive telescopes, we might infer a higher rate.
-However, if we assume that \frb\ is representative of the overall FRB population, then more sensitive observations would be more likely to find repeating FRBs that would effectively depress the estimate of the underlying isotropic rate per source.
-In this model, these two effects partially cancel, although without a physical model it is difficult to say how well.
+This revised volumetric estimate makes many assumptions, but is now appropriate for comparison to rates used for other classes of transient.
+The LGRB and SLSN-I rates are {\color{red}xx} and $10^{-8}$ Mpc$^{-3}$\ yr$^{-1}$, respectively \citep{?,2012Sci...337..927G}.
+These higher-energy transients can be considered sources of FRB-generating systems if all FRBs repeat with $N_r\approx10^3$\ with burst energies near $10^{40}$\ erg.
+\citep{2017arXiv170102370M} calculate the maximum number of bursts that can be powered the magnetic field of a magnetar as $\approx300$, assmuming $\Omega_b=0.1$\ and $E_b=10^{40}$\ erg.
+This is in rough agreement, given the assumptions required in both both the observations and modeling.
 

### 2017-03-24 repeater-vladata.tex
better rate discussion

@@
 
-\subsection{Rate Comparison}
+\subsection{Revised Volumetric Rate}
 
-The calculation of a volumetric rate has been used to study classes of optical and high-energy transient \citep{2006ARA&A..44..507W}.
-\citet{2013Sci...341...53T} used this approach to estimate a rate of $10^{-3}$\ galaxy$^{-1}$\ yr$^{-1}$ by assuming an isotropic emitter in a Milky Way-type galaxy out to a characteristic redshift horizon of 0.9.
-This rate is high \citep[comparable to the rate of core-collapse supernovae;][]{2006Natur.439...45D}, which has been used to argue that FRBs are likely not associated with other classes of transient, such as GRBs or rarer SNe.
+%The calculation of a volumetric rate has been used to study classes of optical and high-energy transient \citep{2006ARA&A..44..507W}. 
+\citet{2013Sci...341...53T} estimated an isotropic FRB rate of $10^{-3}$\ galaxy$^{-1}$\ yr$^{-1}$ by calculating the number of Milky Way-type galaxies out to a distance implied by assming all extragalactic DM originates in the IGM \citep[$z\approx0.9$\ for $DM\approx z\times900 \rm{pc}\ \rm{cm}^{-3}$;][]{2003ApJ...598L..79I,2004MNRAS.348..999I}.
+This rate is high \citep[comparable to the rate of core-collapse supernovae;][]{2006Natur.439...45D}, which has been used to argue that FRBs are likely not associated with other classes of transient, such as LGRBs or rarer SNe \citep{2006ARA&A..44..507W}.
+However, this estimate depends on the telescope sensitivity, so is not easy to compare to other estimates based on source counts.
+Here we reevaluate the FRB volumetric rate by assuming \frb\ is a prototype of the class.
 
-However, inferences based on this and related rates are difficult, since they are strongly dependent on the sensitivity of the telescopes.
-Here we reevaluate the FRB volumetric rate by assuming \frb\ is a prototype of the class.
-We also update the volumetric rate to use the latest projected FRB rate \citep[$2\times10^3\ \rm{sky}^{-1} \rm{day}^{-1}$\ at high Galactic latitudes and flux densities brighter than 1 Jy ms; ][]{2016arXiv161100458L, 2016MNRAS.460L..30C, 2016MNRAS.455.2207R}.
+First, we recast the estimate as volumetric rate of FRB sources by including beaming and repetition effects.
+The volumetric source rate is $R_{FRB} = R_p /(N_r \Omega_b V (z))$, where $R_p$\ is the projected FRB rate, $N_r$\ is the number of bursts per source, $\Omega_b$\ is the beaming fraction, and $V(z)$\ is the volume out to redshift $z$.
+The newest estimates of the projected FRB rate are lower by a factor of 5 \citep[$2\times10^3\ \rm{sky}^{-1} \rm{day}^{-1}$\ at high Galactic latitudes and flux densities brighter than 1~Jy~ms; ][]{2016arXiv161100458L, 2016MNRAS.460L..30C, 2016MNRAS.455.2207R}.
 
-We recast the estimate as volumetric rate of FRB sources by including beaming and repetition effects.
-The volumetric source rate is $R_{FRB} = R_p /(N_r \Omega_b V (z))$, where $R_p$\ is the projected FRB rate, $N_r$\ is the number of bursts per source, $\Omega_b$\ is the beaming fraction, and $V(z)$\ is the volume out to redshift $z$.
+The burst rate depends on the fluence limit of past FRB surveys, but \frb\ has an absolute energy scale that can be used to estimate FRB fluence at a given distance.
+At the typical Parkes survey parameters \citep{}, a fluence limit of 1~Jy~ms is detectable at $z\approx1$.
+The distance inferred from the largest DMs observed \citep[$\sim1500$\ pc cm$^{-3}$;][]{2016MNRAS.460L..30C} is somewhat higher, but it is likely that DM has significant contributions from the host galaxy and intervening galaxies \citep{OPT, 2014ApJ...780L..33M}.
+For reference, we note that cosmic star formation rate peaks between redshift of 2 and 3\citep{2014ARA&A..52..415M}.
 
-The characteristic distance scale for FRBs can be inferred from the detectability of \frb.
-The projected FRB rate is defined for a fluence limit of 1 Jy ms which is detectable out to $z=2\ for the Parkes surveys that have detected the most FRBs.
-This distance is consistent with that inferred from the largest DMs observed \citep[$\sim1500$\ pc cm$^{-3}$;][]{2016MNRAS.460L..30C}.
-This assumes that DM is dominated by the IGM \citep[$DM\approx z\times900 \rm{pc}\ \rm{cm}^{-3}$\ for realistic ionization state;][]{2003ApJ...598L..79I,2004MNRAS.348..999I}, although other contributions are likely significant \citep{2014ApJ...780L..33M}.
-An independent argument for a characteristic distance of $z=2$\ is that it corresponds to the peak the in the cosmic star formation history \citep{2014ARA&A..52..415M} and most leading models for FRBs are driven by star formation \citep{2016MNRAS.462..941L,2016ApJ...826..226K,2017arXiv170104815K}.
-
-Using an assumed horizon redshift of 2, we estimate a rate of $R_p = 10^{-5} N_r^{-1} (0.1/\Omega_b)$\ Mpc$^{-3}$\ yr$^{-1}$.
-Narrow burst spectral structure implies that observations underestimate by missing bursts that fall outside the observing band.
-For a typical burst envelope width of 500~MHz centered at GHz-scale frequencies, past observations (typically using bandwidths of a few hundred MHz near 1.4~GHz) would underestimate the rate by a factor of a few.
+Using an assumed horizon redshift of 1, we estimate a rate of $R_p \approx 5\times10^{-5} N_r^{-1} (0.1/\Omega_b)$\ Mpc$^{-3}$\ yr$^{-1}$.
+The narrow burst spectral structure seen for \frb\ implies that observations have undercounted the rate by a factor of a few by ignoring bursts outside the band.
 There is also relatively little constraint on the beaming factor \citep[$\sim0.1$ for pulsars;][]{1998MNRAS.298..625T}.
@@
 
-This revised volumetric estimate makes many assumptions, but is now appropriate for comparison to rates used for other classes of transient.
+Despite its many assumptions, this is the first volumetric rate appropriate for comparison to rates used for other classes of transient.
 The LGRB and SLSN-I rates are {\color{red}xx} and $10^{-8}$ Mpc$^{-3}$\ yr$^{-1}$, respectively \citep{?,2012Sci...337..927G}.
-These higher-energy transients can be considered sources of FRB-generating systems if all FRBs repeat with $N_r\approx10^3$\ with burst energies near $10^{40}$\ erg.
-\citep{2017arXiv170102370M} calculate the maximum number of bursts that can be powered the magnetic field of a magnetar as $\approx300$, assmuming $\Omega_b=0.1$\ and $E_b=10^{40}$\ erg.
-This is in rough agreement, given the assumptions required in both both the observations and modeling.
+Comparing the FRB rate to these rates implies that FRB-emitting sources can be generated in LGRBs and SLSN-I if FRBs repeat with $xx$\ and $5\times10^3$, respectively (assuming burst energies of $10^{40}$\ erg).
+\citet{2017arXiv170102370M} use the young magnetar model for FRBs to calculate the maximum number of bursts that can be powered its magnetic field as $\approx300$.
+Under the magnetar mdoel for FRBs, LGRBs, and SLSN-I, this rate comparison suggests that the LGRB rate is most consistent with the FRB rate.
 
@@
 
-%\begin{figure}[htb]
-%\begin{center}
-%\includegraphics[width=0.9\columnwidth]{}
-%\caption{
-%\label{fig:name}}
-%\end{center}
-%\end{figure}
-
-%\begin{table}
-%\caption{Caption}
-%\footnotesize
-%\centering
-%\begin{tabular}{l|cc|cc|c}
-%\hline
-%Field       & RA          & Dec   & Lon. & Lat.     & Time \\
-%            & \multicolumn{2}{|c|}{(J2000)}  & \multicolumn{2}{|c|}{(Galactic; deg)} & (hrs) \\ \hline
-%RA02        & 2:27:53  &  +9:13:24 & 159.0 & --46.8    & 26.25 \\
-%PSR J2248-0101 & 22:48:27 & --1:1:48 & 69.3 & --50.6 & 6.5 \\ \hline
-%\end{tabular}
-%\label{fields}
-%\end{table}
-
 \end{document}

### 2017-03-24 repeater-vladata.tex
ready to distribute!

@@
 
-\title{The \frb\ Campaign: Multi-Observatory Radio Burst and Implications for the FRB Population}
+\title{The \frb\ Campaign, a Multi-Telescope Burst Detection, and Implications for the FRB Population}
 \shorttitle{\frb\ Observing Campaign}
@@
 \affiliation{Department of Astronomy and Radio Astronomy Lab, University of California, Berkeley, CA 94720, USA}
-
-\author{J.~W.~T.~Hessels}
-\affiliation{ASTRON, Netherlands Institute for Radio Astronomy, Postbus 2, 7990 AA, Dwingeloo, The Netherlands}
-\affiliation{Anton Pannekoek Institute for Astronomy, University of Amsterdam, Science Park 904, 1098 XH Amsterdam, The Netherlands}
-
-\author{R.~S.~Wharton}
-\affiliation{Cornell Center for Astrophysics and Planetary Science and Department of Astronomy, Cornell University, Ithaca, NY 14853, USA}
 
@@
 \affiliation{Jodrell Bank Centre for Astrophysics, Alan Turning Building, School of Physics \& Astronomy ,The University of Manchester, Oxford Road, Manchester M13 9PL, UK}
+
+\author{J.~W.~T.~Hessels}
+\affiliation{ASTRON, Netherlands Institute for Radio Astronomy, Postbus 2, 7990 AA, Dwingeloo, The Netherlands}
+\affiliation{Anton Pannekoek Institute for Astronomy, University of Amsterdam, Science Park 904, 1098 XH Amsterdam, The Netherlands}
 
@@
 
+\author{R.~S.~Wharton}
+\affiliation{Cornell Center for Astrophysics and Planetary Science and Department of Astronomy, Cornell University, Ithaca, NY 14853, USA}
+
 \author{P.~K.~G.~Williams}
@@
 \begin{abstract}
-The recent precision localization of \frb\ has helped identify a host galaxy, measure its distance, and establish it as a member of a truly new class of astrophysical source.
-We present results of the coordinated observing campaign that made this localization, including the first simultaneous detection of an FRB burst with multiple telescopes.
+We present results of the coordinated observing campaign that made the first localization of a Fast Radio Burst, FRB 121102.
 Of the nine bursts detected by the Very Large Array at 3~GHz, four had simultaneous observing coverage at other observatories, and one was detected by the Arecibo Observatory at 1.4~GHz.
-We show that the burst spectra typically have a $\sim500$~MHz-scale envelope, plus fine spectral structure on MHz-frequency scales.
-We also calculate the energy distribution and temporal statistics for \frb...
-%\ and argue that the whole FRB population is adequately described by a single class similar to \frb. 
-*population models* *slsn*
-**This source shows that optimal FRB survey strategies should...**
+We use this simultaneous detection, plus modeling of bursts only seen at 3~GHz to show that burst spectra are not well characterized by a powerlaw.
+Instead, bursts typically have a $\sim500$~MHz-scale envelope and total energies as high as $10^{40}$\ erg.
+The dispersion measure apparently changes significantly ($\sim5$\ pc cm$^{-3}$) between bursts, which suggests that they have intrinsic spectral structure that can bias the estimate of DM.
+We use \frb\ as a prototype of the FRB class to estimate the first flux-independent volumetric rate of $R_{\rm{FRB}} \approx 5\times10^{-5}$\ Mpc$^{-3}$\ yr$^{-1}$ for the cosmic volume out to redshift of 1.
+This rate is broadly consistent with models of FRBs from young magnetars or fast pulsars, if the typical FRB repeats on the order of $10^3$\ times in its life.
 \end{abstract}
@@
 Beginning in August of 2015, we made the first of nine detections of \frb\ with the Very Large Array \citep{LOC} and localized it with a precision of 0.1\arcsec.
-Subsequent radio and optical observing discovered more bursts from \frb\ and associated them with a persistent radio and optical source at a redshift of 0.193 with a precision of 0.01" \citep[$\sim40$\ pc]{OPT, EVN}.
+Subsequent radio and optical observing discovered more bursts from \frb\ and associated them with a persistent radio and optical source at a redshift of 0.193 with a precision of 0.01\arcsec \citep[$\sim40$\ pc]{OPT, EVN}.
 
@@
 Although new models of FRB origin have been already been developed \citep{2017arXiv170104815K, 2017arXiv170102370M, 2017arXiv170104094Z, 2017arXiv170102492D}, we still do not know what causes them.
-**magnetar birth?**
-Its coincidence with a compact, persistent radio source is consistent with \frb as a young magnetar powering a luminous pulsar wind nebula \citep{2017arXiv170104815K}.
-At the same time, \frb is found in a low-metallicity dwarf galaxy, which is the preferred environment for long GRBs and Type-I superluminous supernovae \citep[LGRB and SLSN-I, respectively;][]{2017arXiv170102370M}.
-It has been suggested that these other classes of transient are signatures of the birth of magnetars that are only born in low-metallicity environments.
-Also, it has not been demonstrated that \frb\ is representative of the overall FRB population.
+Its coincidence with a compact, persistent radio source is consistent with \frb\ as a young magnetar powering a luminous pulsar wind nebula \citep{2017arXiv170104815K}.
+At the same time, \frb\ is found in a low-metallicity dwarf galaxy, which is the preferred environment for long GRBs and Type-I superluminous supernovae \citep[LGRB and SLSN-I, respectively;][]{2017arXiv170102370M}.
+It has been suggested that these other classes of transient are signatures of the birth of magnetars that are only born in low-metallicity environments \citep{2014ApJ...787..138L}.
+
+%Also, it has not been demonstrated that \frb\ is representative of the overall FRB population.
 In fact, the repetition of its bursts is unique among all FRBs \citep{2015MNRAS.454..457P}, so it is natural to ask whether \frb\ is representative.
@@
 
-We can also assume that \frb\ is representative of all FRBs and use it to constrain the physical processes at play in the overall FRB population.
-In this case, we know that FRBs are apparently luminous, but if that is due to intrinsic processes, such as coherent, pulsar-like emission \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C}, or extrinsic effects like scintillation \citep{CORDES}.
+If we assume that \frb\ is representative of all FRBs, we use it to constrain the physical processes at play in the overall FRB population.
+We know that FRBs are apparently luminous, but more data is needed to distinguish between intrinsic processes, such as coherent, pulsar-like emission \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C} and extrinsic effects like scintillation \citep{CORDES}.
 The paper presents an analysis of the spectral properties of VLA bursts implied by simultaneous observing at Effelsberg, GBT, AMI-LA, and Arecibo, including the first simultaneous detection of an FRB at two observatories.
@@
 Next, we present the spectrum of a burst from \frb\ that was simultaneously detected by the VLA and Arecibo observatories.
-**Simulations of temporal statistics and luminosity distribution...** **New estimate of FRB rate and comparison to other transient populations** We close with a discussion of how the \frb\ burst spectra, host properties, burst rate estimates, and other properties inform new strategies for finding FRBs.
+We then discuss modeling of the dynamic spectra that simultaneously considers the spectral and temporal evolution of the bursts.
+The burst temporal and energy distributions are presented and compared to those of bursts detected in earlier observing campaigns of \frb.
+We use the new properties defined for \frb\ to make the first flux-independent estimate of the FRB volumetric rate.
+Finally, we close with a discussion of how the \frb\ burst spectra, host properties, burst rate estimates, and other properties inform new strategies for finding FRBs.
 
@@
 \subsection{VLA}
+
 The \frb\ observing campaign started in late 2015 with a 10~hr campaign observed at 1.4~GHz in the compact D configuration.
@@
 All VLA fast-sampled data were observed with 5~ms sampling, 256 channels, and dual-circular polarization \citep{2015ApJ...807...16L}.
-The channel frequency width was set to maximize sensitivity to the known DM of \frb with the largest total bandwidth.
+The channel frequency width was set to maximize sensitivity to the known DM of \frb\ with the largest total bandwidth.
 The total bandwidth at L (1.4~GHz), S (3~GHz), and C (6~GHz) bands was 256~MHz, 1024~MHz, and 2048~MHz, respectively.
@@
 This DM grid was chosen to maintain 90\% sensitivity to the nominal DM range of 540--570 pc cm$^{-3}$, which includes the known \frb\ DM of 559 pc cm$^{-3}$ \citep{2016arXiv160308880S}.
-Gain calibration was made from observations of J0555+3948 by the ``telcal'' system, which uses phase-only calibration.
-A flux scale is calculated for each spectral window from an observation on {\color{red}xx (Bryan)} and applied to all burst spectra.
+Gain calibration was made from observations of J0555+3948 by the telcal system, which uses phase-only calibration.
+A flux scale is calculated for each spectral window from an observation of 3C48 and applied to all burst spectra.
 
@@
 Total intensity spectra were recorded by the PFFTS backend in pulsar search mode with a time resolution of 65.5~$\mu$s and 128 frequency channels.
-The system equivalent flux density is 18 Jy and a FWHM beam size of 2.4\arcmin at 4.85~GHz.
+The system equivalent flux density is 18 Jy and a FWHM beam size of 2.4\arcmin\ at 4.85~GHz.
 
@@
 \subsection{Multi-Observatory Burst Spectrum}
+
 Four of the VLA bursts were observed simultaneously with Arecibo and AMI-LA, while two were observed simultaneously with all four observatories (Figure \ref{fig:multi}).
 Of these bursts, only one VLA burst (on MJD 57648) was simultaneously detected by another observatory (Arecibo).
-The VLA and Arecibo burst detections had significances of 25$\sigma$\ and 39$\sigma$ with integrated flux densities of 111 mJy and 14 mJy, respectively.
+The VLA and Arecibo burst detections had significances of 25$\sigma$\ and 39$\sigma$\ with integrated flux densities of 111 mJy and 14 mJy, respectively.
 Assuming a powerlaw flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha\approx2.7$.
@@
 \label{sec:spec}
+
 This paper refine the analysis of the nine VLA radio burst spectra described in \citet{LOC} in a few ways.
@@
 Two clusters of samples are identified for this burst: one narrow, low-DM and one wide, high-DM.
-The model seems to be too simple for this burst.
-This is consistent with high-resolution Arecibo burst spectra \citep{WEIRD}, which show that bursts are composed of "sub-bursts" that drift in frequency.
+The model seems to be too simple for this burst or that it can be decomposed into two bursts.
 
 \subsubsection{Dispersion}
-The initial VLA detections were made with a matched-filter approach that allowed inter-DM sensitivity losses up to roughly 10\% \citep[$\Delta DM=10\ \rm{pc}\ \rm{cm}^{-3}$][]{2003ApJ...596.1142C}. 
+
+The initial VLA detections were made with a matched-filter approach that allowed inter-DM sensitivity losses up to roughly 10\% \citep[$\Delta \rm{DM}=10\ \rm{pc}\ \rm{cm}^{-3}$][]{2003ApJ...596.1142C}.
 %In optimizing detection significance over a fine DM grid, we find optimal DM values range from 552 to 572 pc cm$^{-3}$.
@@
 \label{sec:temp}
-The burst rate for \frb\ varied dramatically throughout the 2016 observing campaign (Figure \cite{fig:multi}).
+
+The burst rate for \frb\ varied dramatically throughout the 2016 observing campaign (Figure \ref{fig:multi}).
 In the early-2016 campaign, we observed for 30 hours at S-band and no bursts were detected.
@@
 
-%There is weak evidence that the \frb\ burst rate decreased through the S-band observing in the late-2016 campaign.
-We modeled the event detection probability as a Poisson probability function, $P_i(\lambda)$, with rate parameter that evolves linearly in time relative to the first VLA burst $\lambda = a + b (\rm{MJD}_i - 57623)$.
-By directly sampling the joint probability distribution, $\prod_{i} P_i$, we can exclude a constant rate with $\sim$85\% confidence.
-This weak constraint is consistent with the broader trend of a changing rate seen on month timescales by Arecibo.
-%
-%\begin{figure}[htb]
-%\begin{center}
-%\includegraphics[width=0.9\columnwidth]{event_rate_contours}
-%\caption{Color scale and contours show the relative probability for a time-evolving Poisson detection probability for \frb.
-Contours show the 50, 90, and 95\% confidence contours on the rate $a$\ (bursts s$^{-1}$) and rate change $b$\ (bursts s$^{-1}$ day$^{-1}$) during the August--September 2016 campaign in which bursts were detected.
-%\label{fig:rate}}
-%\end{center}
-%\end{figure}
-%
-%During the late-2016 observing campaign, the typical observation lasted about two hours and was sampled with a 5~ms cadence.
-We used the Lomb-Scargle periodogram \citep{1982ApJ...263..835S} to search for periodic structure over a wide range of timescales.
-The time series is calculated by binning the burst detection rate per 100~ms \citep[always either 0 or 1, see also][]{2011MNRAS.417.1871P}.
-%The spectral power calculated for periods between 0.8 and 80 s shows no power in excess of the typical 95\% confidence bound estimated from shuffled data.
-We verified that simulating nine bursts drawn from a simple rotational model would produce excess power using this approach.
-However, it is difficult to put strong constraints on more complex rotational models \citep[e.g., with wide pulse phase windows or glitches;][]{2007ApJ...663..497C, 2013Natur.497..591A}
-
 \subsection{Energy and Brightness Distribution}
 \label{sec:disn}
+
 Knowing the source distance, we calculate the burst energy by integrating flux in time and frequency (Table \ref{tab:spec}).
@@
 This likely underestimates the burst energy for some bursts by a factor of a few, but should not affect the slope of the distribution.
-The Arecibo and GBT energies were scaled by factors of {\color{red} 2 and 1 (help)}, respectively, to correct for the sensitivity loss due to the primary beam.
+The Arecibo and GBT energies were scaled by factors of {\color{red} 2 and 1 (anyone?)}, respectively, to correct for the sensitivity loss due to the primary beam.
 
@@
 
-%\subsubsection{Spectral Autocorrelation}
-%\label{sec:auto}
-%Autocorrelation of the burst signal (both temporal and spectral) can be used to infer both intrinsic properties and modulation due to scintillation \citep{CORDES}.
-Figure \ref{fig:acf} shows the spectral autocorrellation for the strongest burst (MJD 57633.68).
-The is no strong excess correlation near the channel resolution, which limits the correlation width to less than roughly 4~MHz.
-This is broadly consistent with expectations of Galactic diffractive scintillation bandwidth \citep[3--9~MHz near 3~GHz][]{2002astro.ph..7156C}.
-%
-%**Does channel-scale structure only appear around 3~GHz?**
-%
-%\begin{figure}[htb]
-%\begin{center}
-%\includegraphics[width=0.9\columnwidth]{acf_57633_scan7}
-%\caption{The spectral autocorrelation as a function of frequency for the burst from \frb\ at MJD 57633.68.
-The largest black dots show the autocorrelation for the data, smaller dots show the autocorrelation for the best Gaussian model, and dashed line shows the autocorrelation of an off-burst spectrum.
-%\label{fig:acf}}
-%\end{center}
-%\end{figure}
-
 \section{discussion}
@@
 We also measure a burst-to-burst variation in DM within the whole sample of VLA 3~GHz bursts of a similar scale.
-This variation had been noted in earlier 1.4~GHz Arecibo observations of \frb \citep{2016arXiv160308880S}, but the VLA bursts demonstrate that this ''excess'', burst-specific DM is seen up to 3~GHz.
+This variation had been noted in earlier 1.4~GHz Arecibo observations of \frb\ \citep{2016arXiv160308880S}, but the VLA bursts demonstrate that this burst-specific DM is seen up to 3~GHz.
 The simultaneous VLA/Arecibo burst also shows that an individual burst's properties from 1.2 to 3.5~GHz are consistent with a single excess.
@@
 These features are generally consistent with intrinsic burst properties described in \citet{WEIRD}.
-That work uses bright, coherently-dedispersed bursts to identify ''sub-bursts'' that preferentially drift to lower frequencies at later times.
-With high-resolution dynamic spectra, one can define a heuristic that distinguishes between a burst-specific dispersion-like effect and a more stable (''true'') dispersion.
+That work uses bright, coherently-dedispersed bursts to identify sub-bursts that preferentially drift to lower frequencies at later times.
+With high-resolution dynamic spectra, one can define a heuristic that distinguishes between a burst-specific dispersion-like effect and a more stable (``true'') dispersion.
 Since the sub-bursts tend to drift to lower frequencies, they systematically bias DM measurements made with low-resolution data (like the VLA and earlier Arecibo and GBT obsrevaitons).
@@
 While the surprising brightness of new FRB discoveries was once seen as a cause for concern (i.e., a sign of terrestrial interference), we may be able to use this to infer properties of the overall population \citep{2007Sci...318..777L, 2016arXiv161105758R}.
-When modeling the flux distribution as a powerlaw, an isotropic distribution of sources will have a powerlaw index, $\alpha$, of --1.5 \citep[the ''Euclidean distribution'';][]{2016MNRAS.462..941L}.
+When modeling the flux distribution as a powerlaw, an isotropic distribution of sources will have a powerlaw index, $\alpha$, of --1.5 \citep[the ``Euclidean distribution'';][]{2016MNRAS.462..941L}.
 Prior to the measurement of the first GRB redshift, deviations from the Euclidean distribution were used to infer their cosmological distribution \citep[e.g., the $V/V_{\rm{max}}$\ test;][]{1992ApJ...388L..45M, 1995ApJ...453...25F}.
-Multiple studies have suggested that FRBs have a ''flat'' flux distribution \citep[$-0.5<\alpha<-0.9$;][]{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}.
+Multiple studies have suggested that FRBs have a sub-Euclidean flux distribution \citep[$-0.5<\alpha<-0.9$;][]{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}.
 Others have noted that the flux distribution is not well modeled as a powerlaw, such that $\alpha$\ is effectively sensitivity (and telescope) dependent \citep{2016MNRAS.461..984O, 2017arXiv170208040C}.
@@
 We now know that \frb\ is detectable with the VLA out to $z=0.7$, which suggests that cosmological effects are even more important for understanding properites of the FRB population.
-\citet{2017arXiv170208040C} demonstrate how redshift space distortions, time dilation, and spectral index (''k-correction'') effects can flatten the flux distribution.
+\citet{2017arXiv170208040C} demonstrate how redshift space distortions, time dilation, and spectral index (``k-correction'') effects can flatten the flux distribution.
 To this complex scene, we add the fact that \frb\ burst spectra are not defined by a spectral index, which suggests that k-corrections are likely to be very difficult to calculate in practice.
-Rather than using wide band burst spectra to measure a single ''typical'' spectral index, we now must measure the burst rate as a function of frequency.
-These need not be measured simultaneously, but rather contemporaneously to insure they represent a similar state of activitity of the FRB.
+Rather than using wide band burst spectra to measure a single spectral index, we now must measure the burst rate as a function of frequency.
+These need to be measured at similar times to insure they represent a similar state of activitity of the FRB.
 
@@
 
-%While the \frb\ burst energy distribution is consistent with the overall FRB population, this simulation ignores many observational biases (scattering, observing coverage) and the effects of galaxy evolution, which is likely significant over the range of redshifts to which \frb is detectable \citep[e.g.,][]{2010ApJ...709..644I}.
+%While the \frb\ burst energy distribution is consistent with the overall FRB population, this simulation ignores many observational biases (scattering, observing coverage) and the effects of galaxy evolution, which is likely significant over the range of redshifts to which \frb\ is detectable \citep[e.g.,][]{2010ApJ...709..644I}.
 The burst energies are estimated from observations from 2.5 to 3.5~GHz, which may be a biased selection of all bursts or may not include all burst emission.
-If the simulation is revealing a connection between \frb and the broader FRB population, it does not explain the physical mechanism that drives it.
+If the simulation is revealing a connection between \frb\ and the broader FRB population, it does not explain the physical mechanism that drives it.
 The burst energy distribution of the population could be dominated by intrinsic or extrinsic effects \citep{2015MNRAS.451.3278M,2016Natur.531..202S,CORDES}.
@@
 That is, detecting a burst predicts you are more likely to find another burst soon thereafter and not detecting a burst predicts you will likey not detect another burst soon thereafter.
-While this is sometimes referred to as a ''red spectrum'' \citep{2016MNRAS.458L..89C}, the observations presented here are only sensitive to timescales of days (time between observations) and months (time between campaigns).
+While this is sometimes referred to as a ``red spectrum'' \citep{2016MNRAS.458L..89C}, the observations presented here are only sensitive to timescales of days (time between observations) and months (time between campaigns).
 
@@
 Wide, shallow surveys are the preferred strategy for blind detection of FRBs.
-Also, since ''bursts predict bursts'', many short observations are more likely to blindly detect an FRB than a single long observation of the same total length.
+Also, since ``bursts predict bursts'', many short observations are more likely to blindly detect an FRB than a single long observation of the same total length.
 
@@
 This rate is high \citep[comparable to the rate of core-collapse supernovae;][]{2006Natur.439...45D}, which has been used to argue that FRBs are likely not associated with other classes of transient, such as LGRBs or rarer SNe \citep{2006ARA&A..44..507W}.
-However, this estimate depends on the telescope sensitivity, so is not easy to compare to other estimates based on source counts.
-Here we reevaluate the FRB volumetric rate by assuming \frb\ is a prototype of the class.
+This challenges models for FRBs based on magnetars or young, fast pulsars, which are believed to power these rarer subclasses of optical/gamma-ray transient.
+However, since the FRB rate estimate depends on the telescope sensitivity, it is not appropriate to compare to other estimates based on source counts.
 
+Here, we reevaluate the FRB volumetric rate by assuming \frb\ is a prototype of the class.
 First, we recast the estimate as volumetric rate of FRB sources by including beaming and repetition effects.
-The volumetric source rate is $R_{FRB} = R_p /(N_r \Omega_b V (z))$, where $R_p$\ is the projected FRB rate, $N_r$\ is the number of bursts per source, $\Omega_b$\ is the beaming fraction, and $V(z)$\ is the volume out to redshift $z$.
+The volumetric source rate is $R_{\rm{FRB}} = R_p /(N_r \Omega_b V (z))$, where $R_p$\ is the projected FRB rate, $N_r$\ is the number of bursts per source, $\Omega_b$\ is the beaming fraction, and $V(z)$\ is the volume out to redshift $z$.
 The newest estimates of the projected FRB rate are lower by a factor of 5 \citep[$2\times10^3\ \rm{sky}^{-1} \rm{day}^{-1}$\ at high Galactic latitudes and flux densities brighter than 1~Jy~ms; ][]{2016arXiv161100458L, 2016MNRAS.460L..30C, 2016MNRAS.455.2207R}.
 
-The burst rate depends on the fluence limit of past FRB surveys, but \frb\ has an absolute energy scale that can be used to estimate FRB fluence at a given distance.
-At the typical Parkes survey parameters \citep{}, a fluence limit of 1~Jy~ms is detectable at $z\approx1$.
-The distance inferred from the largest DMs observed \citep[$\sim1500$\ pc cm$^{-3}$;][]{2016MNRAS.460L..30C} is somewhat higher, but it is likely that DM has significant contributions from the host galaxy and intervening galaxies \citep{OPT, 2014ApJ...780L..33M}.
-For reference, we note that cosmic star formation rate peaks between redshift of 2 and 3\citep{2014ARA&A..52..415M}.
+\frb\ has an absolute energy scale that can be used to convert the observation-dependent fluence limit into a characteristic FRB distance.
+At the typical Parkes survey parameters \citep[e.g.,][]{2016MNRAS.460L..30C}, a fluence limit of 1~Jy~ms is detectable at $z\approx1$.
+The distance inferred from the largest DMs observed \citep[$\sim1500$\ pc cm$^{-3}$;][]{2016MNRAS.460L..30C} is somewhat higher, but that likely overestimates distance since DM will have significant contributions from the host galaxy and intervening galaxies \citep{OPT, 2014ApJ...780L..33M}.
+%For reference, we note that cosmic star formation rate peaks between redshift of 2 and 3\citep{2014ARA&A..52..415M}.
 
-Using an assumed horizon redshift of 1, we estimate a rate of $R_p \approx 5\times10^{-5} N_r^{-1} (0.1/\Omega_b)$\ Mpc$^{-3}$\ yr$^{-1}$.
+Using an assumed horizon redshift of 1, we estimate a rate of $R_{\rm{FRB}} \approx 5\times10^{-5} N_r^{-1} (0.1/\Omega_b)$\ Mpc$^{-3}$\ yr$^{-1}$.
 The narrow burst spectral structure seen for \frb\ implies that observations have undercounted the rate by a factor of a few by ignoring bursts outside the band.
 There is also relatively little constraint on the beaming factor \citep[$\sim0.1$ for pulsars;][]{1998MNRAS.298..625T}.
-This estimate also assumes that propagation effects do not significantly affect the detectability of FRBs, although scintillation likely plays a significant role \citep{2015MNRAS.451.3278M, CORDES}.
+Finally, we note that this estimate assumes that propagation effects do not significantly affect the detectability of FRBs, although scintillation and scattering likely play significant roles \citep{2015MNRAS.451.3278M, CORDES}.
 
 Despite its many assumptions, this is the first volumetric rate appropriate for comparison to rates used for other classes of transient.
-The LGRB and SLSN-I rates are {\color{red}xx} and $10^{-8}$ Mpc$^{-3}$\ yr$^{-1}$, respectively \citep{?,2012Sci...337..927G}.
-Comparing the FRB rate to these rates implies that FRB-emitting sources can be generated in LGRBs and SLSN-I if FRBs repeat with $xx$\ and $5\times10^3$, respectively (assuming burst energies of $10^{40}$\ erg).
+The LGRB and SLSN-I rates are $10^{-7}$\ and $10^{-8}$\ Mpc$^{-3}$\ yr$^{-1}$, respectively \citep{2007ApJ...657L..73G,2012Sci...337..927G}.
+Comparing the FRB rate to these rates implies that FRB-emitting sources can be generated in LGRBs and SLSN-I if FRBs repeat $5\times10^2$\ and $5\times10^3$, respectively (assuming burst energies of $10^{40}$\ erg).
 \citet{2017arXiv170102370M} use the young magnetar model for FRBs to calculate the maximum number of bursts that can be powered its magnetic field as $\approx300$.
-Under the magnetar mdoel for FRBs, LGRBs, and SLSN-I, this rate comparison suggests that the LGRB rate is most consistent with the FRB rate.
+Assuming this model for FRBs, LGRBs, and SLSN-I, the rate comparison suggests that the LGRB rate is most consistent with the FRB rate, although it is entirely possible that there are multiple channels to produce FRB-generating magnetars.
 
@@
 \section{Conclusions}
-Prior to being established as a cosmological source, the low Galactic latitude of \frb\ made it a somewhat compromised member of the FRB class.
+
+The recent precision localization of \frb\ has helped identify a host galaxy, measure its distance, and establish it as a member of a truly new class of astrophysical source.
 With its cosmological distance firmly established, \frb\ now serves as a new kind of standard by which FRBs are defined.
-That fact, combined with an abundance of data collected during its high activity state, allows us to think more generally about the physics of broader FRB population.
+That fact, combined with an abundance of data collected during its high activity state, allows us to apply this source to more general questions about the FRB population.
 
@@
 By detecting this burst from 1.2 to 4.5~GHz, we have demonstrated that some bursts have broad spectral structure.
-However, three other VLA bursts are undetected by Arecibo.
-That, combined with the measurement of spectra within the VLA band, suggest that the typical burst has a characteristic Gaussian spectral shape with width $\sim500$\ MHz.
+However, the energy of that burst was dominated by the VLA 3~GHz observing band and three other VLA bursts are undetected by Arecibo.
+That demonstrates the burst spectra cannot be characterized by a spectral index.
+Independently, we modelled dynamic spectra within the VLA 3~GHz band and show that most burst can be characterized by a Gaussian envelope of width $\sim500$\ MHz.
+This modeling also shows that the apparent DM changes from burst to burst.
+DM values are biased above the long-term average, which argues that bursts have intrinsic spectral structure that mimics DM.
+This confirms analysis of high-resolution Arecibo dynamic spectra and extends this phenomenology to the 3~GHz band.
 
-**Flux/lum distribution**
+With a characteristic width of a spectrum, we can estimate total (apparent) radio energy per bust.
+The cumulative energy distribution is characterized by a powerlaw in $dN/dE$ with slope of $\sim-1.7$.
+The amplitude of this powerlaw changes significantly between observational campaigns.
+The stochastic nature of the burst rate suggestts that past constraints on FRB repetition are weaker than previously inferred.
+The relatively narrow spectral structure, flat energy distribution, and variable burst rate of \frb\ suggests that repeated observations, wide bandwidth, and large instantaneous field of view all improve the chance of making new FRB detections.
 
-Analysis of the VLA burst times shows that the burst rate is highly variable.
-This shows that past constraints on FRB repetition are weaker than previously inferred.
-The combination of relatively narrow spectral structure, flat energy and flux distributions, and variable burst rate suggests that repeated observations, wide bandwidth, and large instantaneous field of view all improve the chance of detection.
+Assuming that \frb\ is reprentative of the FRB population, its burst energy distribution makes it possible to calculate the first volumetric FRB rate that does not depend on telescope sensitivity.
+We estimate a volumetric rate of $R_{\rm{FRB}} \approx 5\times10^{-5} (0.1/\Omega_b)$\ Mpc$^{-3}$\ yr$^{-1}$, which is appropriate for \frb-like energies of $10^{40}$\ erg that are detectable out to $z=1$.
+This rate is broadly consistent with models of FRBs from young magnetars or fast pulsars if the typical FRB repeats on the order of $10^3$\ times in its life.
 
-New, arcsecond-scale localizations will continue to be highly informative, given that FRB hosts may be faint and can confuse the inference of a properties of the intergalactic medium \citep{2014ApJ...783L..35D}.
-\frb\ was localized within hours by a prototype version of \rf, but an expanded \rf\ system is now under construction.
+New, arcsecond-scale localizations will be critical to refining the picture presented here and constraining models of FRB origin.
+\frb\ was localized within hours by a prototype version of \rf\ and an expanded \rf\ system is now under construction.
 This platform will search a TB/hour data stream in real time in parallel with ongoing VLA observations, potentially detecting and localizing multiple FRBs per year.
-{\color{red} Sarah: any refinement to this statement?} VLASS+\rf?
 
@@
 %individuals
-CJL is supported by the University of California Office of the President under Lab Fees Research Program Award 237863 and NSF award **number**.
+CJL is supported by the University of California Office of the President under Lab Fees Research Program Award 237863 and NSF award 1611606.
 MAM is supported by NSF award \#1458952.
@@
 The AMI-LA telescope gratefully acknowledges support from the European Research Council under grant ERC-2012- StG-307215 LODESTONE, the UK Science and Technology Facilities Council (STFC) and the University of Cambridge.
-We acknowledge...
-Aspen Center for Physics
-Liam Connor
+
+We thank Liam Connor for useful feedback and the VLA staff for their support of \rf\ development.
+We acknowledge partial support from the Research Corporation for Scientific Advancement (RCSA) for participation in the meeting Fast Radio Bursts: New Probes of Fundamental Physics and Cosmology at the Aspen Center for Physics (February 12-17, 2017).
 

### 2017-04-05 timeline.py
split 2015 plot in two. added some eff coverage

@@ -30,6 +30,9 @@ psym = dict(zip(telescopes, psyms))
 pcols = ['g','r','b','y']
 pcol = dict(zip(telescopes, pcols))
 
+if obsdate[0].year == 2015:
+    telescopes = telescopes[:-1]
+
 # set font properties
 rc('font', family='sans-serif')
 rc('font', serif='Times New Roman')
@@ -60,44 +63,82 @@ def d2n(yyyy, mm, dd):
 def labeltelleft(ax, num):
 	for teln in telescopes:
 		yval = offset[teln]
-		xval = xl - 0.5
-		ax.text(xval, yval, teln, horizontalalignment='right', verticalalignment='center')
+		xval = xl[num] - 0.5
+   		ax.text(xval, yval, teln, horizontalalignment='right', verticalalignment='center')
 
 def labeltelright(ax, num):
 	for teln in telescopes:
 		yval = offset[teln]
-		xval = xr + 0.5
-		ax.text(xval, yval, teln, horizontalalignment='left', verticalalignment='center')
+		xval = xr[num] + 0.5
+   		ax.text(xval, yval, teln, horizontalalignment='left', verticalalignment='center')
 
 if obsdate[0].year == 2016:
-    xl = d2n(2016, 8, 19)
-    xr = d2n(2016, 9, 23)
+    xl = [d2n(2016, 8, 22)]
+    xr = [d2n(2016, 9, 23)]
 else:
-    xl = d2n(2015, 11, 22)
-    xr = d2n(2016, 5, 30)
+    xl = [d2n(2015, 11, 22), d2n(2016, 4, 23)]
+    xr = [d2n(2015, 12, 21), d2n(2016, 5, 29)]
 
-fig, ax = subplots(1, 1, figsize=(15, 4.5))
-for i in range(len(obsdate)):
+if obsdate[0].year == 2016:
+    fig, ax = subplots(1, 1, figsize=(15, 4.5))
+    for i in range(len(obsdate)):
 	putdot(ax, i)
-ax.set_xlim( (xl, xr) )
-ax.set_ylim( (-0.4, 3.4) )
-ax.tick_params(labelright='off', labelleft='off')
-ax.xaxis.set_major_formatter(DateFormatter('%Y-%m-%d'))
-ax.fmt_xdata = DateFormatter('%Y-%m-%d %H:%M:%S')
+    axs = [ax]
+else:
+    fig, ax = subplots(1, 1, figsize=(15, 4.5))
[…]

### 2017-04-06 repeater-vladata.tex
new figure. spectral index limits

@@
 \affiliation{Arecibo Observatory, HC3 Box 53995, Arecibo, PR 00612, USA}
-\affiliation{Max-Planck-Institut f\"ur Radioastronomie, Auf dem H\"ugel 69, Bonn, D-53121, Germany}
+\affiliation{Max-Planck-Institut f\"ur Radioastronomie, Auf dem H\"ugel 69, D-53121 Bonn, Germany}
 
@@
 The solid black line shows the simultaneous burst detection at VLA and Arecibo.
-\label{fig:multi}}
+\label{fig:sched}}
 \end{center}
@@
 The central goal was to interferometrically localize \frb\ with the VLA in coordination with Arecibo Observatory, with others included on a best-effort basis.
-We coordinated observing between the VLA, Arecibo, Effelsberg, and AMI-LA telescopes, as shown in Figure \ref{fig:multi}.
+We coordinated observing between the VLA, Arecibo, Effelsberg, and AMI-LA telescopes, as shown in Figure \ref{fig:sched}.
 Below, we summarize these observations, with a focus on those conducted simultaneously with VLA burst detections from \frb.
@@
 During the late-2016 campaign, Arecibo observed with the L-wide receiver using the PUPPI pulsar backend.
-The observational frequency range was 1.15 to 1.73~GHz and frequency resolution was 1.5625~MHz.
+The observational frequency range was 1.15 to 1.73~GHz and frequency resolution was 1.5625~MHz, which has a typical sensitivity of 2~mJy in 2~ms ($1\sigma$).
 We recorded total full Stokes polarization intensity spectra with time at a resolution of 10.24~$\mu$s.
-Each frequency channel was coherently dedispersed to 557 pc cm$^{-3}$, thereby eliminating intra-channel dispersion smearing.
+Each frequency channel was coherently dedispersed to 557~pc cm$^{-3}$, thereby eliminating intra-channel dispersion smearing.
 The full width at half maximum (FWHM) beam size at band center is 3.3\arcmin.
@@
 Four of those observations were simultaneous with bursts detected with the VLA and one of those observations detected the same VLA burst.
-During the first VLA burst with Arecibo coverage (MJD 57643), the PUPPI 1.4~GHz recording system failed so data were recorded at C band.
+During the first VLA burst with Arecibo coverage (MJD 57643), the PUPPI 1.4~GHz recording system failed so data were recorded at C band with the mock spectrometer.
+The C-band observations were recorded at frequencies from 4078 to 4245~MHz and had a sensitivity of 3.6~mJy in 2~ms ($1\sigma$).
 No detection was made in those Arecibo data.
@@
 Unfortunately, due to a configuration error, a 100~MHz bandwidth filter centered at 4.85~GHz was in place for both of these sessions.
-The sensitivity was about two times worse than the nominal value.
+The sensitivity was about 28 mJy in 2 ms ($1\sigma$), which is two times worse than the nominal value.
 No burst was detected in either observation.
@@
 
-Four of the VLA bursts were observed simultaneously with Arecibo and AMI-LA, while two were observed simultaneously with all four observatories (Figure \ref{fig:multi}).
+Four of the VLA bursts were observed simultaneously with Arecibo and AMI-LA, while two were observed simultaneously with all four observatories (Figure \ref{fig:sched}).
 Of these bursts, only one VLA burst (on MJD 57648) was simultaneously detected by another observatory (Arecibo).
-The VLA and Arecibo burst detections had significances of 25$\sigma$\ and 39$\sigma$\ with integrated flux densities of 111 mJy and 14 mJy, respectively.
-Assuming a powerlaw flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha\approx2.7$.
 
@@
 
-Three of the four VLA bursts with simultaneous observing coverage by Arecibo were not detected at Arecibo.
-Numerous bursts were also detected by Arecibo during VLA observing, but were not detected by the VLA at 3~GHz.
-Considering this, and the order of magnitude difference in flux density for the one simultaneous burst detection, we conclude that the 3~GHz burst flux is not correlated with that at 1.4~GHz.
+Figure \ref{fig:multi} shows broadband spectra (including upper limits) measured for the four burst with simultaneous observing at multiple telescopes.
+The burst on 17 Sep 2016 was detected with Arecibo and the VLA with significances of 25$\sigma$\ and 39$\sigma$\ with integrated flux densities of 111 mJy and 14 mJy, respectively.
+Assuming a powerlaw flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha\approx2.7$.
+This is inconsistent with the spectral index limit implied by the Effelsberg nondetection at 4.5~GHz ($\alpha<0.6$\ for a 2~ms burst and $5\sigma$ limit).
+
+Overall, the bursts with simultaneous observing coverage are not consistent with a powerlaw model for the burst spectra.
+Three Arecibo nondetections and two Effelsberg nondetections of VLA bursts place mutually inconsistent lower and upper limits on the spectral index.
+The Arecibo upper limits at 1.4~GHz imply that burst spectral indices $\alpha_{1.4}>+3.7$, while the Arecibo upper limit at 4~GHz requires $\alpha_4<-11.6$.
+At Effelsberg, the flux limits require $\alpha_{4.5}<-0.4$.
+The limits on $\alpha_{1.4}$\ and $\alpha_{4.5}$ are both derived from the burst on 18 Sep 2016, which shows that a powerlaw model is inappropriate even for a single burst.
+
+\begin{figure}[htb]
+\begin{center}
+ \includegraphics[width=\columnwidth]{multispec.png}
+ \caption{Broadband spectra for four bursts of \frb\ with simultaneous multi-telescope observing coverage.
+Measurements are shown with dots and upper limits with triangles.
+Upper limits assume a pulse width of 2~ms and a $5\sigma$ detection threshold.
+Limits symbols that would overlap are are offset by a few tens of MHz in frequency.
+ \label{fig:multi}}
+\end{center}
+\end{figure}
 
@@
 \centering
-\begin{tabular}{l|ccc|cccccc}
+\begin{tabular}{lc|ccc|cccccc}
 \hline
-Date                & Image S/N & S$_{\rm{I,int}}$	& S$_{\rm{V}}$ 	& DM$_{\rm{opt}}$ 	& dt 			& S$_{\rm{I,peak}}$ & Center & FWHM & E$_{\rm{int}}$ \\
-(MJD)               &           & (mJy) 			& (mJy) 		& (pc cm$^{-3})$ 	& (ms) 			& (mJy) 			& (GHz)  & (MHz) & ($10^{38}$\ erg)\\ \hline
-57623.74402686      & 38 		& 194				& +3			& 567$\pm2$ 		& 2.0$\pm0.2$	 		& 690 		& 2.8 		& 290 & 11 			\\
-57633.67986367      & 179 		& 1500				& --35 			& 568.2$\pm0.2$ 	& 2.05$\pm0.02$			& 3340 		& 3.2 		& 510 & 98				\\
-57633.69515938\tablenotemark{a} & 15 & 69			& +2			& 562$^{+4}_{-6}$ 	& 2.5$^{+0.9}_{-0.6}$	& $>$430 	& $<$2.5	& 290 & 7  			\\
-57638.49937435      & 12 		& 55				& +5 			& 567$^{+7}_{-9}$ 	& 1.3$^{+1.4}_{-0.8}$	& 130 		& 3.1 		& 420 & 3  			\\
-57643.45730263      & 100 		& 508				& --5 			& 565.6$^{+0.6}_{-0.5}$ & 1.9$\pm0.1$		& 1170 		& 2.8 		& 510 & 34 			\\
-57645.42958602      & 13 		& 64 				& +3			& 563$^{+5}_{-4}$ 	& 1.0$\pm0.7$		 	& 170 		& 2.8 		& 380 & 4  			\\
-57646.46600650\tablenotemark{a} & 20 & 87			& +1			& 569$\pm5$ 		& 2.7$^{+0.9}_{-1.4}$	& $>$420 	& $<$2.5 	& 430 & 10 			\\
-57648.43691490\tablenotemark{b} & 25 & 111			& +9			& 564$\pm2$ 		& 1.4$^{+0.3}_{-0.4}$	& 260 		& 2.8 		& 470 & 7  			\\
-57649.45175697      & 36 		& 167				& +1			& 567$\pm2$ 		& 2.1$\pm0.5$		 	& 290 		& 3.0 		& 690 & 12 			\\ \hline
+Calendar day & MJD   & Image S/N & S$_{\rm{I,int}}$	& S$_{\rm{V}}$ 	& DM$_{\rm{opt}}$ 	& dt 			& S$_{\rm{I,peak}}$ & Center & FWHM & E$_{\rm{int}}$ \\
+(2016)       &       &           & (mJy) 			& (mJy) 		& (pc cm$^{-3})$ 	& (ms) 			& (mJy) 			& (GHz)  & (MHz) & ($10^{38}$\ erg)\\ \hline
+23 Aug & 57623.74402686      & 38 		& 194				& +3			& 567$\pm2$ 		& 2.0$\pm0.2$	 		& 690 		& 2.8 		& 290 & 11 			\\
+2 Sep & 57633.67986367      & 179 		& 1500				& --35 			& 568.2$\pm0.2$ 	& 2.05$\pm0.02$			& 3340 		& 3.2 		& 510 & 98				\\
+2 Sep & 57633.69515938\tablenotemark{a} & 15 & 69			& +2			& 562$^{+4}_{-6}$ 	& 2.5$^{+0.9}_{-0.6}$	& $>$430 	& $<$2.5	& 290 & 7  			\\
+7 Sep & 57638.49937435      & 12 		& 55				& +5 			& 567$^{+7}_{-9}$ 	& 1.3$^{+1.4}_{-0.8}$	& 130 		& 3.1 		& 420 & 3  			\\
+12 Sep & 57643.45730263      & 100 		& 508				& --5 			& 565.6$^{+0.6}_{-0.5}$ & 1.9$\pm0.1$		& 1170 		& 2.8 		& 510 & 34 			\\
+14 Sep & 57645.42958602      & 13 		& 64 				& +3			& 563$^{+5}_{-4}$ 	& 1.0$\pm0.7$		 	& 170 		& 2.8 		& 380 & 4  			\\
+15 Sep & 57646.46600650\tablenotemark{a} & 20 & 87			& +1			& 569$\pm5$ 		& 2.7$^{+0.9}_{-1.4}$	& $>$420 	& $<$2.5 	& 430 & 10 			\\
+17 Sep & 57648.43691490\tablenotemark{b} & 25 & 111			& +9			& 564$\pm2$ 		& 1.4$^{+0.3}_{-0.4}$	& 260 		& 2.8 		& 470 & 7  			\\
+18 Sep & 57649.45175697      & 36 		& 167				& +1			& 567$\pm2$ 		& 2.1$\pm0.5$		 	& 290 		& 3.0 		& 690 & 12 			\\ \hline
 \end{tabular}
@@
 \begin{center}
-\includegraphics[width=0.9\columnwidth]{corner57646}
+\includegraphics[width=\columnwidth]{corner57646}
 \caption{A scatterplot matrix that shows the correlation of every pair of parameters in the MCMC run for burst 57646.
@@
 \begin{center}
-\includegraphics[width=0.9\columnwidth]{dmmodel}
+\includegraphics[width=\columnwidth]{dmmodel}
 
-\includegraphics[width=0.9\columnwidth]{burst_dmdt}
+\includegraphics[width=\columnwidth]{burst_dmdt}
 
@@
 
-The burst rate for \frb\ varied dramatically throughout the 2016 observing campaign (Figure \ref{fig:multi}).
+The burst rate for \frb\ varied dramatically throughout the 2016 observing campaign (Figure \ref{fig:sched}).
 In the early-2016 campaign, we observed for 30 hours at S-band and no bursts were detected.
@@
 \begin{center}
-\includegraphics[width=0.9\columnwidth]{energy_disn}
+\includegraphics[width=\columnwidth]{energy_disn}
 \caption{The cumulative burst energy distributions for the VLA, Arecibo, and GBT are shown with dots connected by solid, dashed, and dotted lines, respectively.
@@
 
+**correct for time dilation?**
+
 %The calculation of a volumetric rate has been used to study classes of optical and high-energy transient \citep{2006ARA&A..44..507W}. 

### 2017-04-07 repeater-vladata.tex
updated figure label size. editing for laura comments. removed pbcorr for ao energies

@@
 \author{T.~Cantwell}
-\affiliation{Jodrell Bank Centre for Astrophysics, Alan Turning Building, School of Physics \& Astronomy ,The University of Manchester, Oxford Road, Manchester M13 9PL, UK}
+\affiliation{Jodrell Bank Centre for Astrophysics, Alan Turing Building, School of Physics \& Astronomy ,The University of Manchester, Oxford Road, Manchester M13 9PL, UK}
 
@@
 \author{K.~Grainge}
-\affiliation{Jodrell Bank Centre for Astrophysics, Alan Turning Building, School of Physics \& Astronomy ,The University of Manchester, Oxford Road, Manchester M13 9PL, UK}
+\affiliation{Jodrell Bank Centre for Astrophysics, Alan Turing Building, School of Physics \& Astronomy ,The University of Manchester, Oxford Road, Manchester M13 9PL, UK}
 
@@
 \author{A.~Scaife}
-\affiliation{Jodrell Bank Centre for Astrophysics, Alan Turning Building, School of Physics \& Astronomy ,The University of Manchester, Oxford Road, Manchester M13 9PL, UK}
+\affiliation{Jodrell Bank Centre for Astrophysics, Alan Turing Building, School of Physics \& Astronomy ,The University of Manchester, Oxford Road, Manchester M13 9PL, UK}
 
@@
 We present results of the coordinated observing campaign that made the first localization of a Fast Radio Burst, FRB 121102.
-Of the nine bursts detected by the Very Large Array at 3~GHz, four had simultaneous observing coverage at other observatories, and one was detected by the Arecibo Observatory at 1.4~GHz.
-We use this simultaneous detection, plus modeling of bursts only seen at 3~GHz to show that burst spectra are not well characterized by a powerlaw.
-Instead, bursts typically have a $\sim500$~MHz-scale envelope and total energies as high as $10^{40}$\ erg.
-The dispersion measure apparently changes significantly ($\sim5$\ pc cm$^{-3}$) between bursts, which suggests that they have intrinsic spectral structure that can bias the estimate of DM.
-We use \frb\ as a prototype of the FRB class to estimate the first flux-independent volumetric rate of $R_{\rm{FRB}} \approx 5\times10^{-5}$\ Mpc$^{-3}$\ yr$^{-1}$ for the cosmic volume out to redshift of 1.
+Of the nine bursts detected by the Very Large Array at 3~GHz, three had simultaneous observing coverage at other observatories, of which one was detected by the Arecibo Observatory at 1.4~GHz.
+We use multi-observatory detection and constraints with modeling of bursts only seen at 3~GHz to show that burst spectra are not well characterized by a powerlaw.
+Instead, bursts typically have a $\sim500$~MHz-scale envelope in which the apparent radio energy emitted is as high as $10^{40}$\ erg.
+The dispersion measure apparently changes significantly between bursts, which suggests that they have intrinsic spectral structure that can bias the estimate of DM by as much as 5 pc cm$^{-3}$.
+We use \frb\ as a prototype of the FRB class to estimate a volumetric rate of $R_{\rm{FRB}} \approx 5\times10^{-5}$\ Mpc$^{-3}$\ yr$^{-1}$ for the cosmic volume out to redshift of 1.
 This rate is broadly consistent with models of FRBs from young magnetars or fast pulsars, if the typical FRB repeats on the order of $10^3$\ times in its life.
@@
 Fast Radio Bursts (FRBs) were discovered ten years ago as a millisecond-duration radio transient with an anomalously high dispersion measure \citep[the ``Lorimer burst'';][]{2007Sci...318..777L}.
-Their large dispersion measure (DM) implied that they originated outside of our Galaxy, potentially at cosmological distances, and were orders of magnitude more luminous than any other millisecond radio transient \citep{2013Sci...341...53T}.
+Their large dispersion measures (DM) implied that they originated outside of our Galaxy, potentially at cosmological distances, and were orders of magnitude more luminous than any other millisecond radio transient \citep{2013Sci...341...53T}.
 Both their energetics and distance have inspired a wide variety of models and astrophysical applications \citep[e.g.,][]{2014ApJ...780L..33M, 2014ApJ...797...70K, 2016MNRAS.458L..19C, 2016MNRAS.457..232C}.
@@
 \frb, also known as the ``repeating FRB'', was first detected in November 2012 by the Arecibo Observatory \citep{2014ApJ...790..101S}.
-In mid 2015, new Arecibo observations revealed a series of bursts at the same DM ($\sim559$\ pc cm$^{-3}$) and sky position demonstrating that it repeats \citep{2016Natur.531..202S}.
+In mid 2015, new Arecibo observations revealed a series of bursts at the same DM ($\sim559$\ pc cm$^{-3}$) and sky position that rules out cataclymic models for this source \citep{2016Natur.531..202S}.
 Beginning in August of 2015, we made the first of nine detections of \frb\ with the Very Large Array \citep{LOC} and localized it with a precision of 0.1\arcsec.
@@
 If we assume that \frb\ is representative of all FRBs, we use it to constrain the physical processes at play in the overall FRB population.
-We know that FRBs are apparently luminous, but more data is needed to distinguish between intrinsic processes, such as coherent, pulsar-like emission \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C} and extrinsic effects like scintillation \citep{CORDES}.
+We know that FRBs are extremely energetic, more data is needed to determine if that traces intrinsic processes, such as coherent, pulsar-like emission \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C} or if extrinsic effect also play a role \citep{2015MNRAS.451.3278M, CORDES}.
 The paper presents an analysis of the spectral properties of VLA bursts implied by simultaneous observing at Effelsberg, GBT, AMI-LA, and Arecibo, including the first simultaneous detection of an FRB at two observatories.
@@
 
-This paper opens by describing the multi-telescope observing campaign and a refined analysis of the nine VLA bursts.
-Next, we present the spectrum of a burst from \frb\ that was simultaneously detected by the VLA and Arecibo observatories.
-We then discuss modeling of the dynamic spectra that simultaneously considers the spectral and temporal evolution of the bursts.
-The burst temporal and energy distributions are presented and compared to those of bursts detected in earlier observing campaigns of \frb.
-We use the new properties defined for \frb\ to make the first flux-independent estimate of the FRB volumetric rate.
+In Section \ref{sec:obs}, we describe the multi-telescope observing campaign and a refined analysis of the nine VLA bursts.
+Section \ref{sec:res} presents the first spectrum of an FRB simultaneously detected at multiple telescopes and show that burst spectra cannot be modeled with a single spectral index.
+We then model the dynamic spectra to characterize the burst spectra, energies, and dispersion properties.
+\ref{sec:disc} discusses implications of the properties of \frb\ bursts on inferences about the overall FRB population, including an estimate of the FRB volumetric rate.
 Finally, we close with a discussion of how the \frb\ burst spectra, host properties, burst rate estimates, and other properties inform new strategies for finding FRBs.
@@
 \section{Observations}
-
+\label{sec:obs}
 \begin{figure*}[t]
@@
 \caption{The top and bottom panels summarize the observing coverage and detections of \frb\ in the 2015 and 2016 campaigns.
-Symbols show days with observations with letters L, S, C, K referring to radio frequencies of 1.4, 3, 5, and 12~GHz.
+Symbols show days with observations with letters L, S, C, K referring to radio frequencies of 1.4, 3, 4.5, and 12~GHz, respectively.
 Circles highlight observations that detected bursts from \frb.
@@
 
-The data presented here were obtained from multiple programs and telescopes, but focuses on an observing campaign in August/September 2016.
-The central goal was to interferometrically localize \frb\ with the VLA in coordination with Arecibo Observatory, with others included on a best-effort basis.
+The data presented here were obtained from multiple programs and telescopes with a goal of interferometrically localizing \frb\ with the VLA.
 We coordinated observing between the VLA, Arecibo, Effelsberg, and AMI-LA telescopes, as shown in Figure \ref{fig:sched}.
@@
 
-The \frb\ observing campaign started in late 2015 with a 10~hr campaign observed at 1.4~GHz in the compact D configuration.
-In April through May 2016, we conducted a 40~hr campaign at 3~GHz in the C and CnB configurations in coordination with Arecibo.
-We concluded with a 40~hr, coordinated campaign from August through September 2016 in the B configuration and during the move to the most extended A configuration.
+The \frb\ observing campaign started in late 2015 with a 10~hr campaign ($\sim1$~hr per session) observed at 1.4~GHz in the compact D configuration.
+In April through May 2016, we conducted a 40~hr campaign ($\sim2$~hr per session) at 3~GHz in the C and CnB configurations in coordination with Arecibo \citep{2016arXiv160308880S}.
+We concluded with a 40~hr, coordinated campaign ($\sim2$~hr per session) from August through September 2016 in the B configuration and during the move to the most extended A configuration.
 In the late-2016 campaign, the first 34 hours of VLA observations were made at 3~GHz, while the last 6 hours were observed at 6~GHz.
@@
 The observational frequency range was 1.15 to 1.73~GHz and frequency resolution was 1.5625~MHz, which has a typical sensitivity of 2~mJy in 2~ms ($1\sigma$).
-We recorded total full Stokes polarization intensity spectra with time at a resolution of 10.24~$\mu$s.
+We recorded total full Stokes polarization intensity spectra with a time resolution of 10.24~$\mu$s.
 Each frequency channel was coherently dedispersed to 557~pc cm$^{-3}$, thereby eliminating intra-channel dispersion smearing.
@@
 
-In total, twelve Arecibo observations had some simultaneous coverage with the VLA.
-Four of those observations were simultaneous with bursts detected with the VLA and one of those observations detected the same VLA burst.
-During the first VLA burst with Arecibo coverage (MJD 57643), the PUPPI 1.4~GHz recording system failed so data were recorded at C band with the mock spectrometer.
+In total, 11 Arecibo observations had some simultaneous coverage with the VLA.
+All of these observations were conducted while pointing at the location of \frb\ measured by the VLA.
+Three of those observations had simultaneous coverage of VLA bursts and one of those Arecibo observations detected the VLA burst.
+% During the first VLA burst with Arecibo coverage (MJD 57643), the PUPPI 1.4~GHz recording system failed so data were recorded at C band with the mock spectrometer.
 The C-band observations were recorded at frequencies from 4078 to 4245~MHz and had a sensitivity of 3.6~mJy in 2~ms ($1\sigma$).
 No detection was made in those Arecibo data.
-Overall, there were many more bursts detected at Arecibo than with the VLA and a more detailed analysis of those bursts will be presented in a future paper.
+% levels set wrong.
+useless c-band ao data.
+Overall, there were many more bursts detected at Arecibo than with the VLA and a more detailed analysis of those bursts will be presented elsewhere (Michilli et al, in prep).
 
@@
 Total intensity spectra were recorded by the PFFTS backend in pulsar search mode with a time resolution of 65.5~$\mu$s and 128 frequency channels.
-The system equivalent flux density is 18 Jy and a FWHM beam size of 2.4\arcmin\ at 4.85~GHz.
+The receiver has a system equivalent flux density is 18 Jy and a FWHM beam size of 2.4\arcmin\ at 4.85~GHz.
 
-Five Effelsberg observations had some simultaneous coverage with the VLA, of which two were simultaneous with VLA bursts.
+Five Effelsberg observations were made pointing at the known location of \frb\ and had some simultaneous coverage with the VLA; two observations were simultaneous with VLA bursts.
 Unfortunately, due to a configuration error, a 100~MHz bandwidth filter centered at 4.85~GHz was in place for both of these sessions.
@@
 \section{Results}
+\label{sec:res}
 
@@
 
-Four of the VLA bursts were observed simultaneously with Arecibo and AMI-LA, while two were observed simultaneously with all four observatories (Figure \ref{fig:sched}).
-Of these bursts, only one VLA burst (on MJD 57648) was simultaneously detected by another observatory (Arecibo).
+Four of the VLA bursts were observed simultaneously with either Arecibo, Effelsberg, or AMI-LA, and two were observed simultaneously with all four observatories (Figure \ref{fig:sched}).
+Of these bursts, only one VLA burst (on 17 Sep 2016) was simultaneously detected by another observatory (Arecibo).
 
-Figure \ref{fig:sgram} shows a dynamic spectrum for the 57648 burst with the VLA and AO data aligned in time.
+Figure \ref{fig:sgram} shows a dynamic spectrum for this burst with both VLA and AO data.
 The temporal resolution of the VLA data (5~ms) is much coarser than that of Arecibo, so data were resampled to the same temporal grid after correcting for barycentric and dispersion measure offsets.
@@
 The regridded dynamic spectrum has an apparent DM error that is evident both as a frequency-dependent time drift within the Arecibo observation and as an offset between the Arecibo and VLA bursts.
-Both of these drifts are consistent with an apparent DM of $sim$565 pc cm$^{-3}$.
+Both of these drifts are consistent with an apparent DM of $\sim$565 pc cm$^{-3}$.
 This is consistent with modeling of the VLA spectrum described in \S \ref{sec:spec}.
 
-Figure \ref{fig:multi} shows broadband spectra (including upper limits) measured for the four burst with simultaneous observing at multiple telescopes.
+Figure \ref{fig:multi} shows spectra built from integrated flux densities measured (or limited) during three burst with multi-telescope observing coverage.
 The burst on 17 Sep 2016 was detected with Arecibo and the VLA with significances of 25$\sigma$\ and 39$\sigma$\ with integrated flux densities of 111 mJy and 14 mJy, respectively.
-Assuming a powerlaw flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha\approx2.7$.
+Assuming a powerlaw flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha=2.7$.
 This is inconsistent with the spectral index limit implied by the Effelsberg nondetection at 4.5~GHz ($\alpha<0.6$\ for a 2~ms burst and $5\sigma$ limit).
@@
 Overall, the bursts with simultaneous observing coverage are not consistent with a powerlaw model for the burst spectra.
-Three Arecibo nondetections and two Effelsberg nondetections of VLA bursts place mutually inconsistent lower and upper limits on the spectral index.
-The Arecibo upper limits at 1.4~GHz imply that burst spectral indices $\alpha_{1.4}>+3.7$, while the Arecibo upper limit at 4~GHz requires $\alpha_4<-11.6$.
-At Effelsberg, the flux limits require $\alpha_{4.5}<-0.4$.
-The limits on $\alpha_{1.4}$\ and $\alpha_{4.5}$ are both derived from the burst on 18 Sep 2016, which shows that a powerlaw model is inappropriate even for a single burst.
+Two Arecibo nondetections and two Effelsberg nondetections of VLA bursts place mutually inconsistent lower and upper limits on the spectral index.
+The Arecibo upper limits at 1.4~GHz imply that burst spectral indices $\alpha_{1.4/3}>+3.7$, while at Effelsberg the flux limits require $\alpha_{3/4.5}<-0.4$.
+The strictest limits on $\alpha_{1.4/3}$\ and $\alpha_{3/4.5}$\ are both derived from the burst on 18 Sep 2016, which shows that a powerlaw model is inappropriate even for a single burst.
 
@@
  \includegraphics[width=\columnwidth]{multispec.png}
- \caption{Broadband spectra for four bursts of \frb\ with simultaneous multi-telescope observing coverage.
+ \caption{Broadband spectra for three bursts of \frb\ with simultaneous multi-telescope observing coverage.
 Measurements are shown with dots and upper limits with triangles.
 Upper limits assume a pulse width of 2~ms and a $5\sigma$ detection threshold.
-Limits symbols that would overlap are are offset by a few tens of MHz in frequency.
+Overlapping points are offset by a few tens of MHz in frequency for visualization.
  \label{fig:multi}}
@@
 
-This paper refine the analysis of the nine VLA radio burst spectra described in \citet{LOC} in a few ways.
+This paper refines the analysis of the nine VLA radio burst spectra described in \citet{LOC} in a few ways.
 We use a better calibration scheme and have optimized the detection significance over a fine grid of DM ($\Delta \rm{DM}=1\ \rm{pc}\ \rm{cm}^{-3}$).
@@
 Stokes V values estimated from the dual-circular feeds ($(RR-LL)/(RR+LL)\approx3\%$ and are comparble to the systematic error expected from the primary beam (Perley et al 2016, VLA memo).
-Given that systematic effects dominate the apparent circular polarization, we conclude that the true fractional circular polarization is less than 3\%.
+Given that systematic effects dominate the apparent circular polarization, this observation limits the fractional circular polarization is less than 3\%.
 
@@
 \centering
-\begin{tabular}{lc|ccc|cccccc}
-\hline
-Calendar day & MJD   & Image S/N & S$_{\rm{I,int}}$	& S$_{\rm{V}}$ 	& DM$_{\rm{opt}}$ 	& dt 			& S$_{\rm{I,peak}}$ & Center & FWHM & E$_{\rm{int}}$ \\
-(2016)       &       &           & (mJy) 			& (mJy) 		& (pc cm$^{-3})$ 	& (ms) 			& (mJy) 			& (GHz)  & (MHz) & ($10^{38}$\ erg)\\ \hline
+\begin{tabular}{cc|ccc|cccccc}
+\multicolumn{2}{c|}{Time} & \multicolumn{3}{c|}{Observered properties} & \multicolumn{6}{c}{Modeled properties} \\ \hline
+Calendar day & Burst time   & Image S/N & S$_{\rm{I,int}}$	& S$_{\rm{V}}$ 	& DM$_{\rm{opt}}$ 	& dt 			& S$_{\rm{I,peak}}$ & Center & FWHM & E$_{\rm{int}}$ \\
+(2016)       &  (MJD)     &           & (mJy) 			& (mJy) 		& (pc cm$^{-3})$ 	& (ms) 			& (mJy) 			& (GHz)  & (MHz) & ($10^{38}$\ erg)\\ \hline
 23 Aug & 57623.74402686      & 38 		& 194				& +3			& 567$\pm2$ 		& 2.0$\pm0.2$	 		& 690 		& 2.8 		& 290 & 11 			\\
 2 Sep & 57633.67986367      & 179 		& 1500				& --35 			& 568.2$\pm0.2$ 	& 2.05$\pm0.02$			& 3340 		& 3.2 		& 510 & 98				\\
-2 Sep & 57633.69515938\tablenotemark{a} & 15 & 69			& +2			& 562$^{+4}_{-6}$ 	& 2.5$^{+0.9}_{-0.6}$	& $>$430 	& $<$2.5	& 290 & 7  			\\
+2 Sep\tablenotemark{a} & 57633.69515938 & 15 & 69			& +2			& 562$^{+4}_{-6}$ 	& 2.5$^{+0.9}_{-0.6}$	& $>$430 	& $<$2.5	& 290 & 7  			\\
 7 Sep & 57638.49937435      & 12 		& 55				& +5 			& 567$^{+7}_{-9}$ 	& 1.3$^{+1.4}_{-0.8}$	& 130 		& 3.1 		& 420 & 3  			\\
@@
 14 Sep & 57645.42958602      & 13 		& 64 				& +3			& 563$^{+5}_{-4}$ 	& 1.0$\pm0.7$		 	& 170 		& 2.8 		& 380 & 4  			\\
-15 Sep & 57646.46600650\tablenotemark{a} & 20 & 87			& +1			& 569$\pm5$ 		& 2.7$^{+0.9}_{-1.4}$	& $>$420 	& $<$2.5 	& 430 & 10 			\\
-17 Sep & 57648.43691490\tablenotemark{b} & 25 & 111			& +9			& 564$\pm2$ 		& 1.4$^{+0.3}_{-0.4}$	& 260 		& 2.8 		& 470 & 7  			\\
+15 Sep\tablenotemark{a} & 57646.46600650 & 20 & 87			& +1			& 569$\pm5$ 		& 2.7$^{+0.9}_{-1.4}$	& $>$420 	& $<$2.5 	& 430 & 10 			\\
+17 Sep\tablenotemark{b} & 57648.43691490 & 25 & 111			& +9			& 564$\pm2$ 		& 1.4$^{+0.3}_{-0.4}$	& 260 		& 2.8 		& 470 & 7  			\\
 18 Sep & 57649.45175697      & 36 		& 167				& +1			& 567$\pm2$ 		& 2.1$\pm0.5$		 	& 290 		& 3.0 		& 690 & 12 			\\ \hline
@@
 MCMC sampling requires a generative model for the data, so we wrote functions in Python to create 2d dynamic spectra.
-The dynamic spectra are generated in the spectral domain as a Gaussian envelope and in the temporal domain by a dispersive delay that scales as frequency squared.
-We further allow the pulses to have a finite temporal width.
-This brings the total number of parameters to 6 (Gaussian amplitude, center, width, start time, time width, and DM).
+The dynamic spectra are generated in the spectral domain as a Gaussian envelope (with amplitude, center, and width) and in the temporal domain by a start time, temporal width, and DM.
+We assume a dispersive delay that scales as frequency squared.
 
@@
 
-\begin{figure}[htb]
+**how does interchannel DM smearing compare to measured width?**
+
+\begin{figure*}[htb]
 \begin{center}
-\includegraphics[width=\columnwidth]{corner57646}
+\includegraphics[width=2\columnwidth]{corner57646}
 \caption{A scatterplot matrix that shows the correlation of every pair of parameters in the MCMC run for burst 57646.
@@
 \end{center}
-\end{figure}
+\end{figure*}
 
@@
 The range and variance in DM observed by the VLA is similar to that reported for Arecibo observations of \frb\ in \citet{2016arXiv160308880S}.
-As noted before, this is consistent with the idea that the DM measured at low resolution (e.g., by the VLA) is defined by true (extrinsic) dispersion and some spectral structure that changes between bursts.
+As noted before, this is consistent with the idea that the DM measured at low temporal resolution (e.g., by the VLA or by single-dish observatories without coherent dedispersion) is determined by extrinsic (an electron column) dispersion and some spectral structure that changes between bursts.
 The VLA data demonstrate that the burst-dependent DM effect is visible at frequencies near 3~GHz.
-Assuming a "true" DM of 560.5 pc cm$^{-3}$, the excess DM can be thought of as a frequency-dependent delay that varies between bursts with a delay rate up to 2~ms GHz$^{-1}$.
+Assuming a ``true'' DM of 560.5 pc cm$^{-3}$, the excess DM can be thought of as a frequency-dependent delay that varies between bursts with a delay rate up to 2~ms GHz$^{-1}$ or an effective DM of $\sim5$~pc cm$^{-3}$.
 
@@
 In the early-2016 campaign, we observed for 30 hours at S-band and no bursts were detected.
-In the late-2016 observing campaign, nine bursts were detected in the last 27 hours of S-band observing.
+In the late-2016 observing campaign, we observed for 27 hours at S-band an detected nine bursts.
 Overall, the data quality is uniform and high, so the inhomogeneous burst distribution shows that the burst detection probability was not stationary.
 Assuming that the burst detection probability follows a Poisson distribution, the nondetection in the first half of S-band limits the FRB rate to $\rm{R}<0.1$\ hour$^{-1}$\ (95\% confidence limit).
-The S-band burst rate was much higher during the late-2016 campaign, $\rm{R}=0.33\pm0.1$\ hour$^{-1}$.
+The S-band burst rate was much higher during the late-2016 campaign, $\rm{R}=0.3\pm0.1$\ hour$^{-1}$.
 

### 2017-04-07 timeline.py

@@ -111,7 +111,7 @@ for ax in axs:
 # boxes for simultaneous coverage of VLA bursts
 for ax in axs:
     if obsdate[0].year == 2016:
-        axhspan(0.1, 2.9, 0.657, 0.657, fill=False, linestyle='dashed') # 57643
+        axhspan(0.1, 1.8, 0.657, 0.657, fill=False, linestyle='dashed') # 57643
         axhspan(0.1, 2.9, 0.718, 0.718, fill=False, linestyle='dashed') # 57645
         axhspan(0.1, 2.9, 0.813, 0.813, fill=False, linestyle='dashed') # 57648 57649
         axhspan(2.1, 2.9, 0.813, 0.813, fill=False, lw=3, linestyle='solid') # 57648 57649

### 2017-04-07 repeater-vladata.tex
worked through paul s, geoff b, laura s comments

@@
 
-\title{The \frb\ Campaign, a Multi-Telescope Burst Detection, and Implications for the FRB Population}
+\title{The \frb\ Campaign: A Multi-Telescope Burst Detection and Implications for the FRB Population}
 \shorttitle{\frb\ Observing Campaign}
@@
 \begin{abstract}
-We present results of the coordinated observing campaign that made the first localization of a Fast Radio Burst, FRB 121102.
+We present results of the coordinated observing campaign that made the first arcsecond localization of a Fast Radio Burst, FRB 121102.
 Of the nine bursts detected by the Very Large Array at 3~GHz, three had simultaneous observing coverage at other observatories, of which one was detected by the Arecibo Observatory at 1.4~GHz.
@@
 Instead, bursts typically have a $\sim500$~MHz-scale envelope in which the apparent radio energy emitted is as high as $10^{40}$\ erg.
-The dispersion measure apparently changes significantly between bursts, which suggests that they have intrinsic spectral structure that can bias the estimate of DM by as much as 5 pc cm$^{-3}$.
+The dispersion measure apparently changes significantly between bursts, which suggests that they have spectral structure that can bias the estimate of DM by as much as 5 pc cm$^{-3}$.
 We use \frb\ as a prototype of the FRB class to estimate a volumetric rate of $R_{\rm{FRB}} \approx 5\times10^{-5}$\ Mpc$^{-3}$\ yr$^{-1}$ for the cosmic volume out to redshift of 1.
@@
 
-Fast Radio Bursts (FRBs) were discovered ten years ago as a millisecond-duration radio transient with an anomalously high dispersion measure \citep[the ``Lorimer burst'';][]{2007Sci...318..777L}.
-Their large dispersion measures (DM) implied that they originated outside of our Galaxy, potentially at cosmological distances, and were orders of magnitude more luminous than any other millisecond radio transient \citep{2013Sci...341...53T}.
-Both their energetics and distance have inspired a wide variety of models and astrophysical applications \citep[e.g.,][]{2014ApJ...780L..33M, 2014ApJ...797...70K, 2016MNRAS.458L..19C, 2016MNRAS.457..232C}.
+Fast Radio Bursts (FRBs) were discovered ten years ago with the detection of a millisecond-duration radio transient with an anomalously high dispersion measure \citep{2007Sci...318..777L}.
+There are now 21 FRBs publicly known \footnote{See \url{http://www.astronomy.swin.edu.au/pulsar/frbcat}.} with dispersion measures (DMs) as high as 1600 pc cm$^{-3}$ and intrinsic temporal widths of order 2~ms.
+Their large DM implied that they originated outside of our Galaxy, potentially at cosmological distances, and were orders of magnitude more luminous than any other millisecond radio transient \citep{2013Sci...341...53T}.
+Both their energetics and distance have inspired a wide variety of models and astrophysical applications \citep[e.g.,][]{2014ApJ...780L..33M, 2014ApJ...797...70K, 2015MNRAS.450L..71F, 2016MNRAS.458L..19C, 2016MNRAS.457..232C, 2016MNRAS.462L..16P}.
 However, that potential was limited by the lack of a definitive association of an FRB to an extragalactic host.
@@
 In mid 2015, new Arecibo observations revealed a series of bursts at the same DM ($\sim559$\ pc cm$^{-3}$) and sky position that rules out cataclymic models for this source \citep{2016Natur.531..202S}.
-Beginning in August of 2015, we made the first of nine detections of \frb\ with the Very Large Array \citep{LOC} and localized it with a precision of 0.1\arcsec.
-Subsequent radio and optical observing discovered more bursts from \frb\ and associated them with a persistent radio and optical source at a redshift of 0.193 with a precision of 0.01\arcsec \citep[$\sim40$\ pc]{OPT, EVN}.
+Beginning in August of 2015 (MJD 57623), we made the first of nine detections of \frb\ with the Very Large Array \citep{LOC} and localized it with a precision of 0.1\arcsec.
+Subsequent radio and optical observing discovered more bursts from \frb\ and associated them with a persistent radio and optical source at a $z=0.193$\ with a precision of 0.01\arcsec\ \citep[$\sim40$\ pc]{OPT, EVN}.
 
@@
 If \frb\ is representative of all FRBs, then we should expect them to be useful as probes of the intergalactic medium and their host galaxies.
-Thus, the confirmation of a cosmological distance for \frb\ has begun to fulfil the promise implied by the Lorimer burst.
+Thus, the confirmation of a cosmological distance for \frb\ has begun to fulfil the promise implied by the first FRB detection.
 
-Although new models of FRB origin have been already been developed \citep{2017arXiv170104815K, 2017arXiv170102370M, 2017arXiv170104094Z, 2017arXiv170102492D}, we still do not know what causes them.
-Its coincidence with a compact, persistent radio source is consistent with \frb\ as a young magnetar powering a luminous pulsar wind nebula \citep{2017arXiv170104815K}.
-At the same time, \frb\ is found in a low-metallicity dwarf galaxy, which is the preferred environment for long GRBs and Type-I superluminous supernovae \citep[LGRB and SLSN-I, respectively;][]{2017arXiv170102370M}.
-It has been suggested that these other classes of transient are signatures of the birth of magnetars that are only born in low-metallicity environments \citep{2014ApJ...787..138L}.
+Although new models of FRB origin have been already been developed \citep{2017arXiv170104815K, 2017arXiv170102370M, 2017arXiv170104094Z, 2017arXiv170102492D}, observations do not strongly constrain these models.
+The coincidence of \frb\ with a compact, persistent radio source is consistent with bursts coming from a young magnetar that powers a luminous pulsar wind nebula \citep{2017arXiv170104815K}.
+At the same time, \frb\ is found in a low-metallicity dwarf galaxy \citep{OPT, 2017arXiv170102370M}, which is the preferred environment for long GRBs and Type-I superluminous supernovae (LGRB and SLSN-I, respectively).
+It has been suggested that these other classes of transient are signatures of the birth of magnetars that are only born in low-metallicity environments \citep{2008AJ....135.1136M, 2014ApJ...787..138L}.
 
@@
 \caption{The top and bottom panels summarize the observing coverage and detections of \frb\ in the 2015 and 2016 campaigns.
-Symbols show days with observations with letters L, S, C, K referring to radio frequencies of 1.4, 3, 4.5, and 12~GHz, respectively.
+Symbols show days with observations with letters L, S, C, U referring to radio frequencies of 1.4, 3, 4.5, and 12~GHz, respectively.
 Circles highlight observations that detected bursts from \frb.
@@
 
-The \frb\ observing campaign started in late 2015 with a 10~hr campaign ($\sim1$~hr per session) observed at 1.4~GHz in the compact D configuration.
+The \frb\ observing campaign started in November 2015 with a 10~hr campaign ($\sim1$~hr per session) observed at 1.4~GHz in the compact D configuration.
 In April through May 2016, we conducted a 40~hr campaign ($\sim2$~hr per session) at 3~GHz in the C and CnB configurations in coordination with Arecibo \citep{2016arXiv160308880S}.
@@
 The total bandwidth at L (1.4~GHz), S (3~GHz), and C (6~GHz) bands was 256~MHz, 1024~MHz, and 2048~MHz, respectively.
-The 3~GHz data were recorded data in eight spectral windows with 32 channels each.
+The 3~GHz data were recorded data in eight spectral windows with 32 channels each and had sensitivity of 5~mJy in 5~ms ($1\sigma$).
 
@@
 \rf\ is a real-time, fast imaging transient search system.
-The current prototype runs on CPU-based hardware that is normally dedicated to the VLA correlator; for this experiment, it runs the transient search pipeline software called \emph{rtpipe} \citep[\url{https://github.com/caseyjlaw/rtpipe};][]{2015ApJ...807...16L}.
-Images were formed for each integration with a DM grid of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$ and a time resampling grid of 5, 10, 20, 40, and 80 ms.
+The current prototype runs on CPU-based hardware that is normally dedicated to the VLA correlator; for this experiment, it runs the transient search pipeline software called \emph{rtpipe}\footnote{See \url{https://github.com/caseyjlaw/rtpipe} and \citet{2015ApJ...807...16L}.}.
+Images were formed for each integration with DMs of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$ and a time resampling grid of 5, 10, 20, 40, and 80 ms.
 This DM grid was chosen to maintain 90\% sensitivity to the nominal DM range of 540--570 pc cm$^{-3}$, which includes the known \frb\ DM of 559 pc cm$^{-3}$ \citep{2016arXiv160308880S}.
-Gain calibration was made from observations of J0555+3948 by the telcal system, which uses phase-only calibration.
+Gain calibration was made from observations of J0555+3948 by an automated system (telcal), which uses phase-only calibration.
 A flux scale is calculated for each spectral window from an observation of 3C48 and applied to all burst spectra.
@@
 We observed \frb\ with the Arcminute MicroKelvin Imager Large Array (AMI-LA; Zwart et al.
-2008) for 3 hours each on four epochs starting at MJDs 57643, 57645, 57648, and 57649.
+2008) for 3 hours each on four epochs starting at MJDs 57638, 57643, 57645, 57646, 57648, and 57649.
 Observations were made with the new digital correlator having 4096 channels across a 5~GHz bandwidth between 13--18~GHz with a 1~s integration time.
@@
 We inspected the calibrated visibilities, and did not find any signal above 30 mJy in the 1s samples at and in the vicinity of the detected bursts.
+This corresponds to a sensitivity of 15~Jy for an assumed pulse width of 2~ms.
 Concatenating and imaging the 12 hours of calibrated data with the CASA tasks {\it concat} and {\it clean} also does not yield any significant detection at the FRB location.
@@
 Hence, we place an upper limit of $100\pm10 \mu$Jy on any quiescent or possible radio flaring on $\sim$days timescales from the FRB.
-This limit is similar to the flux density measured by the VLA \citep{LOC}.
+This limit is similar to the flux density measured by the VLA for the persistent source \citep{LOC}.
 
@@
 
+\begin{figure}[htb]
+\begin{center}
+ \includegraphics[width=\columnwidth]{aovla_spec.png}
+ \caption{Composite dynamic specrum for the burst from \frb\ on MJD 57648 with data from the VLA and Arecibo observatories.
+Both data sets have been barycentered and corrected for an assumed dispersion measure of 560.5 pc $^{-3}$.
+The black line separates data from the VLA (2.5 to 3.5~GHz) and Arecibo (1.0 to 1.8~GHz) and flagged data is grey.
+The amplitude scale is normalized by assuming the Arecibo to VLA gain ratio is 10.
+ \label{fig:sgram}}
+\end{center}
+\end{figure}
+
+**integrated flux is assuming 5 ms width!**
+
+**confirm arecibo integrated flux and sensitivity**
+
 Figure \ref{fig:multi} shows spectra built from integrated flux densities measured (or limited) during three burst with multi-telescope observing coverage.
-The burst on 17 Sep 2016 was detected with Arecibo and the VLA with significances of 25$\sigma$\ and 39$\sigma$\ with integrated flux densities of 111 mJy and 14 mJy, respectively.
+The burst on 17 Sep 2016 was detected with VLA and Arecibo with significances of 25$\sigma$\ and 39$\sigma$\ with integrated flux densities of 111 mJy and 14 mJy at 3 and 1.4~GHz, respectively.
+The VLA integration time of 5~ms underresolves the pulse and the true integrated flux density would be 280 mJy for an assumed pulse width of 2~ms.
+% correct the followign for estimated integrated flux
 Assuming a powerlaw flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha=2.7$.
@@
 The strictest limits on $\alpha_{1.4/3}$\ and $\alpha_{3/4.5}$\ are both derived from the burst on 18 Sep 2016, which shows that a powerlaw model is inappropriate even for a single burst.
+% could note that these limits are understated by VLA integrated flux underestimate
 
@@
 \subsection{VLA Bursts}
-
-\begin{figure*}[htb]
-\begin{center}
- \includegraphics[width=1.9\columnwidth]{aovla_spec.png}
- \caption{Composite dynamic specrum for the burst from \frb\ on MJD 57648 with data from the VLA and Arecibo observatories.
-Both data sets have been barycentered and corrected for an assumed dispersion measure of 560.5 pc $^{-3}$.
-The black line separates data from the VLA (2.5 to 3.5~GHz) and Arecibo (1.0 to 1.8~GHz).
-The amplitude scale is normalized by assuming the Arecibo to VLA gain ratio is 10.
- \label{fig:sgram}}
-\end{center}
-\end{figure*}
-
 \subsubsection{Spectral Modeling}
@@
 We use a better calibration scheme and have optimized the detection significance over a fine grid of DM ($\Delta \rm{DM}=1\ \rm{pc}\ \rm{cm}^{-3}$).
-After calibration and flagging, the visibility phases were rotated to the best-fit location \citep[(RA, Dec) $=$ (05h31m58.70s, +33d08m52.5s);][]{LOC} to extract a Stokes I spectrum that maximizes the image S/N for each burst.
+After calibration and flagging, the visibility phases were rotated to the best-fit location \citep[RA, Dec $=$ 05h31m58.70s, +33d08m52.5s;][]{LOC} to extract a Stokes I spectrum that maximizes the image S/N for each burst.
 
@@
 \multicolumn{2}{c|}{Time} & \multicolumn{3}{c|}{Observered properties} & \multicolumn{6}{c}{Modeled properties} \\ \hline
-Calendar day & Burst time   & Image S/N & S$_{\rm{I,int}}$	& S$_{\rm{V}}$ 	& DM$_{\rm{opt}}$ 	& dt 			& S$_{\rm{I,peak}}$ & Center & FWHM & E$_{\rm{int}}$ \\
+Calendar day & Burst time   & Image S/N & $S_{\rm{I,int}}$	& $S_{\rm{V}}$ 	& DM 	& dt 			& $S_{\rm{I,peak}}$ & Center & FWHM & $E_{\rm{int}}$ \\
 (2016)       &  (MJD)     &           & (mJy) 			& (mJy) 		    & (pc cm$^{-3})$ 	& (ms) 			& (mJy) 			& (GHz)  & (MHz) & ($10^{38}$\ erg)\\ \hline
@@
 2 Sep & 57633.67986367      & 179 		& 1500			& --35 				& 568.2$\pm0.2$ 	& 2.05$\pm0.02$			& 3340 		& 3.2 		& 510 & 98				\\
-2 Sep\tablenotemark{a} & 57633.69515938 & 15 & 69			& +2			& 562$^{+4}_{-6}$ 	& 2.5$^{+0.9}_{-0.6}$	& $>$430 	& $<$2.5	& 290 & 7  			\\
+2 Sep\tablenotemark{c} & 57633.69515938 & 15 & 69		& +2				& 562$^{+4}_{-6}$ 	& 2.5$^{+0.9}_{-0.6}$	& $>$430 	& $<$2.5	& 290 & 7  			\\
 7 Sep & 57638.49937435      & 12 		& 55			& +5 				& 567$^{+7}_{-9}$ 	& 1.3$^{+1.4}_{-0.8}$	& 130 		& 3.1 		& 420 & 3  			\\
-12 Sep & 57643.45730263      & 100 		& 508				& --5 			& 565.6$^{+0.6}_{-0.5}$ & 1.9$\pm0.1$		& 1170 		& 2.8 		& 510 & 34 			\\
-14 Sep & 57645.42958602      & 13 		& 64 				& +3			& 563$^{+5}_{-4}$ 	& 1.0$\pm0.7$		 	& 170 		& 2.8 		& 380 & 4  			\\
-15 Sep\tablenotemark{a} & 57646.46600650 & 20 & 87			& +1			& 569$\pm5$ 		& 2.7$^{+0.9}_{-1.4}$	& $>$420 	& $<$2.5 	& 430 & 10 			\\
-17 Sep\tablenotemark{b} & 57648.43691490 & 25 & 111			& +9			& 564$\pm2$ 		& 1.4$^{+0.3}_{-0.4}$	& 260 		& 2.8 		& 470 & 7  			\\
-18 Sep & 57649.45175697      & 36 		& 167				& +1			& 567$\pm2$ 		& 2.1$\pm0.5$		 	& 290 		& 3.0 		& 690 & 12 			\\ \hline
+12 Sep\tablenotemark{a} & 57643.45730263  & 100 		& 508				& --5 			& 565.6$^{+0.6}_{-0.5}$ & 1.9$\pm0.1$		& 1170 		& 2.8 		& 510 & 34 			\\
+14 Sep\tablenotemark{a} & 57645.42958602   & 13 		& 64 				& +3			& 563$^{+5}_{-4}$ 	& 1.0$\pm0.7$		 	& 170 		& 2.8 		& 380 & 4  			\\
+15 Sep\tablenotemark{c} & 57646.46600650 & 20 & 87		& +1				& 569$\pm5$ 		& 2.7$^{+0.9}_{-1.4}$	& $>$420 	& $<$2.5 	& 430 & 10 			\\	
+17 Sep\tablenotemark{a,b} & 57648.43691490 & 25 & 111	& +9				& 564$\pm2$ 		& 1.4$^{+0.3}_{-0.4}$	& 260 		& 2.8 		& 470 & 7  			\\
+18 Sep\tablenotemark{a} & 57649.45175697   & 36 		& 167				& +1			& 567$\pm2$ 		& 2.1$\pm0.5$		 	& 290 		& 3.0 		& 690 & 12 			\\ \hline
 \end{tabular}
-\tablenotetext{a}{Best-fit Gaussian is not centered in 3~GHz band, so spectral parameters are limits.}
-\tablenotetext{b}{Detected simultaneously with Arecibo between 1.15 and 1.73~GHz.}
+\tablenotetext{a}{Simultaneously observed by either Arecibo, Effelsberg, or AMI-LA.}
+\tablenotetext{b}{Detected simultaneously with Arecibo.}
+\tablenotetext{c}{Best-fit Gaussian is not centered in 3~GHz band, so spectral parameters are limits.}
 \label{tab:spec}
@@
 Figure \ref{fig:spec} shows that the Stokes I spectra are generally characterized by a broad, Gaussian shape with inter-channel modulation as high as 100\%.
+Diffractive scintillation from the Milky Way has a typical bandwidth of 7~MHz along this line of sight \citep{2002astro.ph..7156C}, which is similar to the channel size of 4~MHz.
+
 To better understand the spectra, we extracted dynamic radio spectra (time versus frequency) for 2d modeling with the MCMC sampler \emph{emcee} \citep{2013PASP..125..306F}.
-MCMC sampling requires a generative model for the data, so we wrote functions in Python to create 2d dynamic spectra.
-The dynamic spectra are generated in the spectral domain as a Gaussian envelope (with amplitude, center, and width) and in the temporal domain by a start time, temporal width, and DM.
-We assume a dispersive delay that scales as frequency squared.
-
-The 6-dimensional models were sampled with 100 walkers taking 500 steps.
-Typically, the first 200 steps were used to burn in the walkers and were ignored.
-A flat prior was used over all ranges with valid data.
-An additional requirement was that the integrated burst signal must have a detection significance higher than 8$\sigma$.
+We modeled the dynamic spectra with a broad gaussian envelope (amplitude, center, width), a time delay according to the $\nu^2$\ dispersion law, and a temporal width.
+The 6-dimensional models were sampled with 100 walkers taking 500 steps; we ignored the first 200 steps to allow the walkers to properly sample the posterior distributions.
+A flat prior was used over all ranges with valid data with the requirement that the integrated signal must have a detection significance higher than 8$\sigma$.
 The inter-channel modulation (scintillation) was ignored in the model.
@@
  \begin{minipage}{2\columnwidth}
-  \includegraphics[width=0.33\columnwidth]{spec_57623.png}
-  \includegraphics[width=0.33\columnwidth]{spec_57633_scan7.png}
-  \includegraphics[width=0.33\columnwidth]{spec_57633_scan13.png}
+  \includegraphics[width=0.5\columnwidth]{spec_57623.png}
+  \includegraphics[width=0.5\columnwidth]{spec_57633_scan7.png}
  \end{minipage}
@@
  \begin{minipage}{2\columnwidth}
-  \includegraphics[width=0.33\columnwidth]{spec_57638.png}
-  \includegraphics[width=0.33\columnwidth]{spec_57643.png}
-  \includegraphics[width=0.33\columnwidth]{spec_57645.png}
+  \includegraphics[width=0.5\columnwidth]{spec_57633_scan13.png}
+  \includegraphics[width=0.5\columnwidth]{spec_57638.png}
  \end{minipage}
@@
  \begin{minipage}{2\columnwidth}
-  \includegraphics[width=0.33\columnwidth]{spec_57646.png}
-  \includegraphics[width=0.33\columnwidth]{spec_57648.png}
-  \includegraphics[width=0.33\columnwidth]{spec_57649.png}
+  \includegraphics[width=0.5\columnwidth]{spec_57643.png}
+  \includegraphics[width=0.5\columnwidth]{spec_57645.png}
+ \end{minipage}
+
+ \begin{minipage}{2\columnwidth}
+  \includegraphics[width=0.5\columnwidth]{spec_57646.png}
+  \includegraphics[width=0.5\columnwidth]{spec_57648.png}
+ \end{minipage}
+
+ \begin{minipage}{2\columnwidth}
+  \includegraphics[width=0.5\columnwidth]{spec_57649.png}
  \end{minipage}
@@
 While most bursts are modeled with well-defined parameter probability distributions, one burst is an outlier.
-Figure \ref{fig:corner} shows the scatterplot matrix for the MCMC run on burst 57646 \citep{corner}.
+Figure \ref{fig:corner} shows the scatter plot matrix \citep{corner} for the MCMC run on burst 57646.
 Two clusters of samples are identified for this burst: one narrow, low-DM and one wide, high-DM.
-The model seems to be too simple for this burst or that it can be decomposed into two bursts.
+Assuming that the model is appropriate, this implies that it can be decomposed into two bursts.
 
@@
 
-The top panel of Figure \ref{fig:dmmodel} shows the 95\% confidence intervals on the DM for all nine VLA bursts as a function of burst time.
+The top panel of Figure \ref{fig:dmmodel} shows the 68\% confidence intervals on the DM for all nine VLA bursts as a function of burst time.
 The burst DMs are not consistent with any single value and tend to be larger than the long-term average of 560.5 pc cm$^{-3}$.
 The range and variance in DM observed by the VLA is similar to that reported for Arecibo observations of \frb\ in \citet{2016arXiv160308880S}.
-As noted before, this is consistent with the idea that the DM measured at low temporal resolution (e.g., by the VLA or by single-dish observatories without coherent dedispersion) is determined by extrinsic (an electron column) dispersion and some spectral structure that changes between bursts.
+As noted before, this is consistent with the idea that the DM measured at low temporal resolution (e.g., by the VLA or by single-dish observatories without coherent dedispersion) is determined by extrinsic (an electron column) dispersion and some spectrotemporal structure that changes between bursts.
 The VLA data demonstrate that the burst-dependent DM effect is visible at frequencies near 3~GHz.
@@
 \caption{(Top) DM as a function of time for nine 3~GHz bursts detected by the VLA.
-The 95\% confidence interval on DM is shown with a bar and the dahsed line shows the best-fit DM$=560.5$\ pc cm$^{-3}$ inferred for Arecibo observations at 1.4~GHz.
+The 68\% confidence interval on DM is shown with a bar and the dahsed line shows the best-fit DM$=560.5$\ pc cm$^{-3}$ inferred for Arecibo observations at 1.4~GHz.
 (Bottom) Burst DM versus temporal width for all nine VLA bursts.
@@
 Overall, the data quality is uniform and high, so the inhomogeneous burst distribution shows that the burst detection probability was not stationary.
-Assuming that the burst detection probability follows a Poisson distribution, the nondetection in the first half of S-band limits the FRB rate to $\rm{R}<0.1$\ hour$^{-1}$\ (95\% confidence limit).
-The S-band burst rate was much higher during the late-2016 campaign, $\rm{R}=0.3\pm0.1$\ hour$^{-1}$.
+
+Assuming that the burst detection probability follows a Poisson distribution, the mean VLA burst rate is $R=0.16\pm0.05\ \rm{hr}^{-1}$ above a fluence of 0.2 Jy ms.
+The nondetection in the first half of S-band limits the FRB rate to $R<0.1$\ hour$^{-1}$\ (95\% confidence limit).
+The S-band burst rate was much higher during the late-2016 campaign, $R=0.3\pm0.1$\ hour$^{-1}$.
 
@@
 This likely underestimates the burst energy for some bursts by a factor of a few, but should not affect the slope of the distribution.
-The Arecibo and GBT energies were scaled by factors of {\color{red} 2 and 1 (anyone?)}, respectively, to correct for the sensitivity loss due to the primary beam.
 
@@
 
-We modeled the differential energy distribution, $dN/d\log{E}$, using a Poisson probability distribution with a rate function $\lambda = A E^{\alpha}$.
+We modeled the differential energy distribution, $dN/d\log{E}$, again using a Poisson detection probability with a rate function $\lambda = A E^{\alpha}$.
 Rather than trying to estimate a completeness limit for each energy distribution, we assume an effective detection limit of 0.9 times the weakest burst detected; the best-fit slope is weakly dependent on this, but general conclusions are robust.
@@
 That will require rate estimates for the FRB population to be made explicitly frequency-dependent.
-Finally, we note that the odds of detecting a burst will improve with bandwidth for bandwidths wider than their characteristic scale.
+Finally, we note that the odds of detecting a burst will improve with bandwidth beyond the gain in sensitivity, since bandwidths wider than the FRB characteristic width can find otherwise undetectable bursts.
+However, this does require that FRB search algorithms search for bursts with a width equal to the characteristic width.
 
@@
 This variation had been noted in earlier 1.4~GHz Arecibo observations of \frb\ \citep{2016arXiv160308880S}, but the VLA bursts demonstrate that this burst-specific DM is seen up to 3~GHz.
-The simultaneous VLA/Arecibo burst also shows that an individual burst's properties from 1.2 to 3.5~GHz are consistent with a single excess.
+The simultaneous VLA/Arecibo burst also shows that this excess is evident in an individual burst at 1.2 to 3.5~GHz.
 
@@
 $$\frac{\rm DM_0}{a_{\rm AU}^2} \frac{d_{sl}d_{lo}/d_{so}}{1\, \rm kpc} \gtrsim (3.5 / 39.1)^2$$
-where $DM_0$, $a$, and $d_*$\ are the electron column density of the lens, size of the lens, and lensing distances, respectively.
+where DM$_0$, $a$, and $d_{sl, lo, so}$\ are the electron column density of the lens, size of the lens, and lensing distances, respectively.
 A lens placed at $d_{sl}\approx1$~kpc is consistent with typical properties of the interstellar medium.
@@
 
-\subsection{Energy and Flux Distribution}
+\subsection{Energy Distribution}
 
-The refined analysis shows that \frb\ has even higher isotropic energies than previously reported, reaching energies $E_{\rm{max}}\approx10^{40}$\ erg.
-\frb\ has isotropic energies orders of magnitude higher than the strongest Crab pulsar pulses ($\sim10^{35}$~erg) and comparable brightness temperatures \citep[$T_b^{\rm{Crab}}\sim10^{41}$~K versus $T_b^{\rm{FRB 121102}}\sim10^{38}$~K;][]{2003Natur.422..141H,2014PhRvD..89j3009K}.
+The refined analysis shows that \frb\ has even higher isotropic energies than previously reported for \frb, reaching energies $E_{\rm{max}}\approx10^{40}$\ erg.
+\frb\ has isotropic energies orders of magnitude higher than the strongest Crab giant pulses ($\sim10^{35}$~erg) and comparable brightness temperatures \citep[$T_{b,\rm{Crab}}\sim10^{41}$~K versus $T_{b, \rm{FRB 121102}}\sim10^{38}$~K;][]{2003Natur.422..141H,2014PhRvD..89j3009K}.
 %While this emission is coherent and strongly beamed \citep{2016Natur.531..202S, WEIRD}, the energy scale is still larger than any known Galactic radio transient and requires either a new process or dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}.
@@
 This slope is seen even though the burst rate varies by almost an order of magnitude between observations and frequencies cover both 1.4 and 3~GHz bands.
-This suggests that the slope is related to the underlying physical process, rather than the state at any given time.
+This suggests that the slope is related to the underlying physical process, rather than the burst detection rate at any given time.
 The value of the energy distribution slope is similar to that observed in gamma-ray fluence of bursts from soft-gamma repeaters \citep{2000ApJ...532L.121G, 2011ApJ...739...94S}.
 This similarity has been used to argue that bursts are driven by self-regulated critical phenomena \citep[slope$=-5/3$;][]{2011SoPh..274...99A}.
+
+\subsection{Flux Distribution}
 
@@
 
+**how to include new result on freq-dependent burst rate?**
+
 If we assume \frb\ is representative of the FRB population, we can estimate this frequency-dependent burst rate.
@@
 This suggests that high-redshift FRBs will have an apparently lower rate that flattens the $dN/dF$\ distribution in a manner similar to a k-correction.
-We can only infer the presence of this effect for observations near 1.4~GHz, since we have no estimate of the \frb\ burst rate outside the frequency range from 1.4 to 3~GHz.
-Propagation effects suggest that the rate will be lower at sub-GHz frequencies \citep{2017MNRAS.465.2286R}.
+We can only infer the presence of this effect for observations near 1.4~GHz, since we have no estimate of the \frb\ burst rate outside the frequency range from 1.4 to 3~GHz in the observed frame.
+Propagation effects suggest that the rate will be lower at sub-GHz frequencies \citep{2017MNRAS.465.2286R, 2017arXiv170107457C}.
 If so, the tension between constraints on $\alpha$\ near 800~MHz and 1.4~GHz may be resolved by a frequency-dependent FRB rate that peaks near 1.4~GHz.
@@
 
-The chance of detecting a burst with the VLA changes substantially on day--month timescales.
-A major outstanding question is whether this time-variable rate is driven by an intrinsic process \citep{2016ApJ...826..226K} or extrinsic (propagation) effects \citep{CORDES}.
+The chance of detecting a burst from \frb\ with the VLA changes substantially on day--month timescales.
+A major outstanding question is whether this time-variable rate is driven by an intrinsic process \citep{2016ApJ...826..226K} or extrinsic (propagation) effects in the host galaxy or intergalactic medium \citep{CORDES}.
 However, the temporal distribution of VLA detections alone shows that \frb\ has significant correlation on short timescales.
-That is, detecting a burst predicts you are more likely to find another burst soon thereafter and not detecting a burst predicts you will likey not detect another burst soon thereafter.
+That is, detecting a burst predicts that you are more likely to find another burst soon thereafter and not detecting a burst predicts you will likey not detect another burst soon thereafter.
 While this is sometimes referred to as a ``red spectrum'' \citep{2016MNRAS.458L..89C}, the observations presented here are only sensitive to timescales of days (time between observations) and months (time between campaigns).
+As has been noted elsewhere, this statistical property would weaken previous constraints on repetition \citep{2015MNRAS.454..457P,2015ApJ...807...16L}.
 
-If this statistical property describes other FRBs, it weakens previous constraints on repetition \citep{2015MNRAS.454..457P,2015ApJ...807...16L}.
-It is possible that other FRBs have repeating bursts, but calculating a limit requires knowing their temporal correlation function.
-Wide, shallow surveys are the preferred strategy for blind detection of FRBs.
-Also, since ``bursts predict bursts'', many short observations are more likely to blindly detect an FRB than a single long observation of the same total length.
+If this statistical property describes other FRBs, then wide, shallow surveys are the preferred strategy for blind detection of FRBs.
+Also, since ``bursts predict bursts'', many short observations are more likely to detect an FRB than a single long observation of the same total length.
 
@@
 %The calculation of a volumetric rate has been used to study classes of optical and high-energy transient \citep{2006ARA&A..44..507W}. 
-\citet{2013Sci...341...53T} estimated an isotropic FRB rate of $10^{-3}$\ galaxy$^{-1}$\ yr$^{-1}$ by calculating the number of Milky Way-type galaxies out to a distance implied by assming all extragalactic DM originates in the IGM \citep[$z\approx0.9$\ for $DM\approx z\times900 \rm{pc}\ \rm{cm}^{-3}$;][]{2003ApJ...598L..79I,2004MNRAS.348..999I}.
+\citet{2013Sci...341...53T} estimated an isotropic FRB rate of $10^{-3}$\ galaxy$^{-1}$\ yr$^{-1}$ by calculating the number of Milky Way-type galaxies out to a distance implied by assming all extragalactic DM originates in the IGM \citep[$z\approx0.9$\ for DM$\approx z\times900 \rm{pc}\ \rm{cm}^{-3}$;][]{2003ApJ...598L..79I,2004MNRAS.348..999I}.
 This rate is high \citep[comparable to the rate of core-collapse supernovae;][]{2006Natur.439...45D}, which has been used to argue that FRBs are likely not associated with other classes of transient, such as LGRBs or rarer SNe \citep{2006ARA&A..44..507W}.
@@
 First, we recast the estimate as volumetric rate of FRB sources by including beaming and repetition effects.
-The volumetric source rate is $R_{\rm{FRB}} = R_p /(N_r \Omega_b V (z))$, where $R_p$\ is the projected FRB rate, $N_r$\ is the number of bursts per source, $\Omega_b$\ is the beaming fraction, and $V(z)$\ is the volume out to redshift $z$.
+The volumetric birth rate of FRB sources is $R_{\rm{FRB}} = R_p /(N_r \Omega_b V (z))$, where $R_p$\ is the projected FRB rate, $N_r$\ is the number of bursts per source, $\Omega_b$\ is the beaming fraction, and $V(z)$\ is the comoving volume out to redshift $z$.
 The newest estimates of the projected FRB rate are lower by a factor of 5 \citep[$2\times10^3\ \rm{sky}^{-1} \rm{day}^{-1}$\ at high Galactic latitudes and flux densities brighter than 1~Jy~ms; ][]{2016arXiv161100458L, 2016MNRAS.460L..30C, 2016MNRAS.455.2207R}.
@@
 \frb\ has an absolute energy scale that can be used to convert the observation-dependent fluence limit into a characteristic FRB distance.
-At the typical Parkes survey parameters \citep[e.g.,][]{2016MNRAS.460L..30C}, a fluence limit of 1~Jy~ms is detectable at $z\approx1$.
+At the typical Parkes survey parameters \citep[e.g.,][]{2016MNRAS.460L..30C}, a survey with a fluence limit of 1~Jy~ms can detect \frb\ at $z\approx1$.
 The distance inferred from the largest DMs observed \citep[$\sim1500$\ pc cm$^{-3}$;][]{2016MNRAS.460L..30C} is somewhat higher, but that likely overestimates distance since DM will have significant contributions from the host galaxy and intervening galaxies \citep{OPT, 2014ApJ...780L..33M}.
@@
 \citet{2017arXiv170102370M} use the young magnetar model for FRBs to calculate the maximum number of bursts that can be powered its magnetic field as $\approx300$.
-Assuming this model for FRBs, LGRBs, and SLSN-I, the rate comparison suggests that the LGRB rate is most consistent with the FRB rate, although it is entirely possible that there are multiple channels to produce FRB-generating magnetars.
+Assuming this model for FRBs, LGRBs, and SLSN-I, the rate comparison suggests that the LGRB rate is most consistent with the FRB rate, although there might be multiple channels to producing FRB sources.
 
@@
 We presented the first multi-telescope detection (Arecibo and VLA) of an FRB.
-By detecting this burst from 1.2 to 4.5~GHz, we have demonstrated that some bursts have broad spectral structure.
+By detecting this burst from 1.2 to 3.5~GHz, we have demonstrated that some bursts have broad spectral structure.
 However, the energy of that burst was dominated by the VLA 3~GHz observing band and three other VLA bursts are undetected by Arecibo.
@@
 This modeling also shows that the apparent DM changes from burst to burst.
-DM values are biased above the long-term average, which argues that bursts have intrinsic spectral structure that mimics DM.
+DM values are biased above the long-term average, which argues that bursts have intrinsic spectrotemporal structure that mimics DM.
 This confirms analysis of high-resolution Arecibo dynamic spectra and extends this phenomenology to the 3~GHz band.
@@
 Assuming that \frb\ is reprentative of the FRB population, its burst energy distribution makes it possible to calculate the first volumetric FRB rate that does not depend on telescope sensitivity.
-We estimate a volumetric rate of $R_{\rm{FRB}} \approx 5\times10^{-5} (0.1/\Omega_b)$\ Mpc$^{-3}$\ yr$^{-1}$, which is appropriate for \frb-like energies of $10^{40}$\ erg that are detectable out to $z=1$.
+We estimate a volumetric rate of FRB sources of $R_{\rm{FRB}} \approx 5\times10^{-5} (0.1/\Omega_b)$\ Mpc$^{-3}$\ yr$^{-1}$, which is appropriate for \frb-like energies of $10^{40}$\ erg that are detectable out to $z=1$.
 This rate is broadly consistent with models of FRBs from young magnetars or fast pulsars if the typical FRB repeats on the order of $10^3$\ times in its life.

### 2017-04-07 timeline.py

@@ -22,7 +22,7 @@ for i in range(len(obs)):
 obsdate = list(map(lambda od: datetime.datetime.strptime(od, "%Y-%m-%d"), ymds))
 
 # Define an offset and symbol type for each telescope
-telescopes = ['AO', 'VLA', 'Effelsberg', 'AMI']
+telescopes = ['Arecibo', 'VLA', 'Effelsberg', 'AMI-LA']
 offs = [3, 2, 1, 0]
 offset = dict(zip(telescopes, offs))
 psyms = ['+', 'v', 'x', '.']

### 2017-04-11 repeater-vladata.tex
first pass at comments included. combined dmdt figs. new bib style from peter. longer mcmc chains. major issues noted with **

@@
 %\documentclass{emulateapj}
-%\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref} 
+\usepackage{hyperref} 
 \usepackage{graphicx,natbib}
@@
 \usepackage{fancyref}
-\usepackage{hyperref}
 \usepackage{multirow}
@@
 \affiliation{Department of Astronomy and Radio Astronomy Lab, University of California, Berkeley, CA 94720, USA}
+
+\author{M.~W.~Abruzzo}
+\affiliation{Haverford College, 370 Lancaster Ave, Haverford, PA 19041, USA}
 
@@
 Of the nine bursts detected by the Very Large Array at 3~GHz, three had simultaneous observing coverage at other observatories, of which one was detected by the Arecibo Observatory at 1.4~GHz.
-We use multi-observatory detection and constraints with modeling of bursts only seen at 3~GHz to show that burst spectra are not well characterized by a powerlaw.
-Instead, bursts typically have a $\sim500$~MHz-scale envelope in which the apparent radio energy emitted is as high as $10^{40}$\ erg.
-The dispersion measure apparently changes significantly between bursts, which suggests that they have spectral structure that can bias the estimate of DM by as much as 5 pc cm$^{-3}$.
-We use \frb\ as a prototype of the FRB class to estimate a volumetric rate of $R_{\rm{FRB}} \approx 5\times10^{-5}$\ Mpc$^{-3}$\ yr$^{-1}$ for the cosmic volume out to redshift of 1.
-This rate is broadly consistent with models of FRBs from young magnetars or fast pulsars, if the typical FRB repeats on the order of $10^3$\ times in its life.
+We use multi-observatory detection and constraints with modeling of bursts only seen at 3~GHz to confirm earlier results showing that burst spectra are not well characterized by a power law.
+We characterize burst spectra with a $\sim500$~MHz envelope and apparent radio energy as high as $10^{40}$\ erg.
+The dispersion measure apparently changes significantly between bursts, which suggests that bursts have spectral structure that randomly biases the estimate of DM by as much as 5 pc cm$^{-3}$.
+We use \frb\ as a prototype of the FRB class to estimate a volumetric birth rate of FRB sources $R_{\rm{FRB}} \approx 5\times10^{-5}$\ Mpc$^{-3}$\ yr$^{-1}$ for the cosmic volume out to redshift of 1.
+This rate is broadly consistent with models of FRBs from young magnetars or pulsars, if the typical FRB repeats on the order of $10^3$\ times in its life.
 \end{abstract}
@@
 There are now 21 FRBs publicly known \footnote{See \url{http://www.astronomy.swin.edu.au/pulsar/frbcat}.} with dispersion measures (DMs) as high as 1600 pc cm$^{-3}$ and intrinsic temporal widths of order 2~ms.
-Their large DM implied that they originated outside of our Galaxy, potentially at cosmological distances, and were orders of magnitude more luminous than any other millisecond radio transient \citep{2013Sci...341...53T}.
+The large measured DM implied that FRBs originated outside of our Galaxy, potentially at cosmological distances, and were orders of magnitude more luminous than any other millisecond radio transient \citep{2013Sci...341...53T}.
 Both their energetics and distance have inspired a wide variety of models and astrophysical applications \citep[e.g.,][]{2014ApJ...780L..33M, 2014ApJ...797...70K, 2015MNRAS.450L..71F, 2016MNRAS.458L..19C, 2016MNRAS.457..232C, 2016MNRAS.462L..16P}.
@@
 In mid 2015, new Arecibo observations revealed a series of bursts at the same DM ($\sim559$\ pc cm$^{-3}$) and sky position that rules out cataclymic models for this source \citep{2016Natur.531..202S}.
-Beginning in August of 2015 (MJD 57623), we made the first of nine detections of \frb\ with the Very Large Array \citep{LOC} and localized it with a precision of 0.1\arcsec.
-Subsequent radio and optical observing discovered more bursts from \frb\ and associated them with a persistent radio and optical source at a $z=0.193$\ with a precision of 0.01\arcsec\ \citep[$\sim40$\ pc]{OPT, EVN}.
+Beginning in August of 2015 (MJD 57623), we made the first of nine detections of \frb\ with the Karl G.\ Jansky Very Large Array \citep[VLA;][]{LOC} and localized it with a precision of 0.1\arcsec.
+Deep optical observing with the Gemini Observatory associated the FRB with a host galaxy at $z=0.193$\ \citep{OPT} and the European VLBI Network detected four more bursts to localize the source with a precision of 0.01\arcsec\ \citep[$\sim40$\ pc]{EVN}.
 
@@
 
-Although new models of FRB origin have been already been developed \citep{2017arXiv170104815K, 2017arXiv170102370M, 2017arXiv170104094Z, 2017arXiv170102492D}, observations do not strongly constrain these models.
-The coincidence of \frb\ with a compact, persistent radio source is consistent with bursts coming from a young magnetar that powers a luminous pulsar wind nebula \citep{2017arXiv170104815K}.
-At the same time, \frb\ is found in a low-metallicity dwarf galaxy \citep{OPT, 2017arXiv170102370M}, which is the preferred environment for long GRBs and Type-I superluminous supernovae (LGRB and SLSN-I, respectively).
-It has been suggested that these other classes of transient are signatures of the birth of magnetars that are only born in low-metallicity environments \citep{2008AJ....135.1136M, 2014ApJ...787..138L}.
+Several new models of FRB origin have been been developed in response to the localization of \frb\ \citep{2017arXiv170104815K, 2017arXiv170102370M, 2017arXiv170104094Z, 2017arXiv170102492D, 2017arXiv170208644B, 2017arXiv170300393T}.
+The association of \frb\ with a compact, persistent radio source is consistent with bursts coming from a young magnetar that powers a luminous pulsar wind nebula \citep{2017arXiv170104815K}.
+At the same time, \frb\ is found in a low-metallicity dwarf galaxy \citep{OPT, 2017arXiv170102370M}, which is not a prediction of models that scale with stellar mass or star formation \citep{2017arXiv170400022N}.
+These galaxies are the preferred environment for long GRBs and Type-I superluminous supernovae (LGRB and SLSN-I, respectively), which have been suggested are signatures of the magnetar birth \citep{2008AJ....135.1136M, 2014ApJ...787..138L}.
 
@@
 If we assume that \frb\ is representative of all FRBs, we use it to constrain the physical processes at play in the overall FRB population.
-We know that FRBs are extremely energetic, more data is needed to determine if that traces intrinsic processes, such as coherent, pulsar-like emission \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C} or if extrinsic effect also play a role \citep{2015MNRAS.451.3278M, CORDES}.
+More data is needed to determine if bursts trace intrinsic processes, such as coherent, pulsar-like emission \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C} or if extrinsic effects also play a role \citep{2015MNRAS.451.3278M, CORDES}.
 The paper presents an analysis of the spectral properties of VLA bursts implied by simultaneous observing at Effelsberg, GBT, AMI-LA, and Arecibo, including the first simultaneous detection of an FRB at two observatories.
@@
 We then model the dynamic spectra to characterize the burst spectra, energies, and dispersion properties.
-\ref{sec:disc} discusses implications of the properties of \frb\ bursts on inferences about the overall FRB population, including an estimate of the FRB volumetric rate.
-Finally, we close with a discussion of how the \frb\ burst spectra, host properties, burst rate estimates, and other properties inform new strategies for finding FRBs.
+Section \ref{sec:disc} discusses the properties of \frb\ bursts and its impact on inferences about the birth rate of FRB sources and strategies to find and/or localize new FRBs.
 
@@
 \includegraphics[width=2\columnwidth]{timeline}
-\caption{The top and bottom panels summarize the observing coverage and detections of \frb\ in the 2015 and 2016 campaigns.
+\caption{The top and bottom panels summarize the observations and detections of \frb\ in the 2015 and 2016 campaigns.
+Circles highlight observations that detected bursts from \frb with multiple burst detections indicated with a heavy line.
+The black dashed lines show the VLA burst detections with simultaneous coverage at other telescopes and the solid line shows the simultaneous burst detection.
+Circled observations with no line indicate observations on the same day that did not overlap.
 Symbols show days with observations with letters L, S, C, U referring to radio frequencies of 1.4, 3, 4.5, and 12~GHz, respectively.
-Circles highlight observations that detected bursts from \frb.
-Multiple circles indicate multiple burst detections, except for Arecibo, which typically has multiple detections per observing session.
-The black dashed lines show the VLA burst detections with simultaneous coverage at other telescopes.
-The solid black line shows the simultaneous burst detection at VLA and Arecibo.
 \label{fig:sched}}
@@
 
+Computational (Jupyter) notebooks to reproduce the transient detection, localization, and analysis presented here can be found at \url{https://github.com/caseyjlaw/FRB121102}.
+Time cut-out visibility data and calibration products are available at \url{https://doi.org/10.7910/DVN/TLDKXG}.
+Original VLA visibility data are available under NRAO program codes 16A-459 and 16A-496 and can be downloaded at \url{http://archive.nrao.edu}.
+
 \subsection{VLA}
@@
 In the late-2016 campaign, the first 34 hours of VLA observations were made at 3~GHz, while the last 6 hours were observed at 6~GHz.
-This paper focuses on the data collected at 3~GHz, which includes all nine burst detections and is the widest bandwidth to have ever detected an FRB.
 
@@
 Gain calibration was made from observations of J0555+3948 by an automated system (telcal), which uses phase-only calibration.
-A flux scale is calculated for each spectral window from an observation of 3C48 and applied to all burst spectra.
+A flux scale was calculated for each spectral window from an observation of 3C48 and applied to all burst spectra.
 
@@
 All visibilities are recorded so detailed analysis, including improved calibration and localization, can be conducted offline.
-
-Computational (Jupyter) notebooks to reproduce the transient detection, localization, and analysis presented here can be found at \url{https://github.com/caseyjlaw/FRB121102}.
-Time cut-out visibility data and calibration products are available at \url{https://doi.org/10.7910/DVN/TLDKXG}.
-Original visibility data are available under VLA program codes 16A-459 and 16A-496 and can be downloaded at \url{http://archive.nrao.edu}.
 
@@
 useless c-band ao data.
-Overall, there were many more bursts detected at Arecibo than with the VLA and a more detailed analysis of those bursts will be presented elsewhere (Michilli et al, in prep).
+Overall, there were many more bursts detected at Arecibo than with the VLA, including some Arecibo bursts with simultaneous VLA upper limits.
+A more detailed analysis of those bursts will be presented elsewhere (Michilli et al, in prep).
 
@@
 Although the statistical $3\sigma$\ upper limit is 60 $\mu$Jy, extended mJy-level sources in the field cause sidelobe confusion (the AMI-LA angular resolution is $\sim$30\arcsec), and the actual upper limit is larger.
-We introduced artificial point sources at the FRB location using the CASA {\it sm} tool, and found that these sources can be recovered as long as their peak flux densities are more than $\sim100\mu$Jy.
+We introduced artificial point sources at the FRB location using the CASA {\it sm} tool, and found that these sources can be recovered at $3\sigma$\ as long as their peak flux densities are more than $\sim100\mu$Jy.
 Hence, we place an upper limit of $100\pm10 \mu$Jy on any quiescent or possible radio flaring on $\sim$days timescales from the FRB.
-This limit is similar to the flux density measured by the VLA for the persistent source \citep{LOC}.
+This limit is similar to the flux density measured by the VLA at 12~GHz for the persistent source \citep{LOC}.
 
@@
 
-Figure \ref{fig:sgram} shows a dynamic spectrum for this burst with both VLA and AO data.
-The temporal resolution of the VLA data (5~ms) is much coarser than that of Arecibo, so data were resampled to the same temporal grid after correcting for barycentric and dispersion measure offsets.
-The dispersion correction for both data sets assumed a DM of 560.5 pc cm$^{-3}$, which was typical of the source during the observing campaign \citep{WEIRD}.
+Figure \ref{fig:sgram} shows a dynamic spectrum for this burst with both VLA and Arecibo data.
+The temporal resolution of the VLA data (5~ms) is much coarser than that of Arecibo, so data were resampled to the Arecibo temporal grid after correcting for barycentric and dispersion measure offsets.
+We assumed a DM of 560.5 pc cm$^{-3}$ (Hessels et al., in prep) to calculate a dispersion delay of 189 and 734~ms from the top of the VLA and Arecibo bands, respectively.
+We used PRESTO \citep{2001PhDT.......123R} to calculate a barycentric time offset of 3.8~ms between the VLA and Arecibo data.
+
 The regridded dynamic spectrum has an apparent DM error that is evident both as a frequency-dependent time drift within the Arecibo observation and as an offset between the Arecibo and VLA bursts.
 Both of these drifts are consistent with an apparent DM of $\sim$565 pc cm$^{-3}$.
-This is consistent with modeling of the VLA spectrum described in \S \ref{sec:spec}.
+More refined modeling of the VLA dynamic spectrum alone (\S \ref{sec:spec} and Table \ref{tab:spec}) are consistent with this higher DM value.
 
@@
 Both data sets have been barycentered and corrected for an assumed dispersion measure of 560.5 pc $^{-3}$.
-The black line separates data from the VLA (2.5 to 3.5~GHz) and Arecibo (1.0 to 1.8~GHz) and flagged data is grey.
+The thick black line separates data from the VLA (2.5 to 3.5~GHz) and Arecibo (1.1 to 1.8~GHz) and flagged data is grey.
 The amplitude scale is normalized by assuming the Arecibo to VLA gain ratio is 10.
@@
 % correct the followign for estimated integrated flux
-Assuming a powerlaw flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha=2.7$.
+Assuming a power law flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha=2.7$.
 This is inconsistent with the spectral index limit implied by the Effelsberg nondetection at 4.5~GHz ($\alpha<0.6$\ for a 2~ms burst and $5\sigma$ limit).
 
-Overall, the bursts with simultaneous observing coverage are not consistent with a powerlaw model for the burst spectra.
+Overall, the bursts with simultaneous observing coverage are not consistent with a power law model for the burst spectra.
 Two Arecibo nondetections and two Effelsberg nondetections of VLA bursts place mutually inconsistent lower and upper limits on the spectral index.
 The Arecibo upper limits at 1.4~GHz imply that burst spectral indices $\alpha_{1.4/3}>+3.7$, while at Effelsberg the flux limits require $\alpha_{3/4.5}<-0.4$.
-The strictest limits on $\alpha_{1.4/3}$\ and $\alpha_{3/4.5}$\ are both derived from the burst on 18 Sep 2016, which shows that a powerlaw model is inappropriate even for a single burst.
+The strictest limits on $\alpha_{1.4/3}$\ and $\alpha_{3/4.5}$\ are both derived from the burst on 18 Sep 2016, which shows that a power law model is inappropriate even for a single burst.
 % could note that these limits are understated by VLA integrated flux underestimate
@@
 Parameters such as integrated flux density, S/N, and Stokes V were measured from the burst properties integrated in frequency.
-Stokes V values estimated from the dual-circular feeds ($(RR-LL)/(RR+LL)\approx3\%$ and are comparble to the systematic error expected from the primary beam (Perley et al 2016, VLA memo).
+Stokes V values estimated from the dual-circular feeds as $(RR-LL)/(RR+LL)\approx3\%$, which is comparble to the systematic error induced by the primary beam\footnote{See EVLA memo \#195 at \url{https://library.nrao.edu/public/memos/evla/EVLAM_195.pdf}.}.
 Given that systematic effects dominate the apparent circular polarization, this observation limits the fractional circular polarization is less than 3\%.
@@
 \centering
-\begin{tabular}{cc|ccc|cccccc}
+\begin{tabular}{cc|rrr|ccrrrr}
 \multicolumn{2}{c|}{Time} & \multicolumn{3}{c|}{Observered properties} & \multicolumn{6}{c}{Modeled properties} \\ \hline
-Calendar day & Burst time   & Image S/N & $S_{\rm{I,int}}$	& $S_{\rm{V}}$ 	& DM 	& dt 			& $S_{\rm{I,peak}}$ & Center & FWHM & $E_{\rm{int}}$ \\
-(2016)       &  (MJD)     &           & (mJy) 			& (mJy) 		    & (pc cm$^{-3})$ 	& (ms) 			& (mJy) 			& (GHz)  & (MHz) & ($10^{38}$\ erg)\\ \hline
+Calendar day & Burst time   & S/N & $S_{\rm{I, 5~ms}}$	& $S_{\rm{V}}$ 	& DM 			& dt 			& $S_{\rm{I,peak}}$ & Center & FWHM & $E_{\rm{int}}$ \\
+(2016)       &  (MJD)     &   (image)    & (mJy) 			& (mJy) 		    & (pc cm$^{-3})$ 	& (ms) 			& (mJy) 			& (GHz)  & (MHz) & ($10^{38}$\ erg)\\ \hline
 23 Aug & 57623.74402686      & 38 		& 194			& +3				& 567$\pm2$ 		& 2.0$\pm0.2$	 		& 690 		& 2.8 		& 290 & 11 			\\
 2 Sep & 57633.67986367      & 179 		& 1500			& --35 				& 568.2$\pm0.2$ 	& 2.05$\pm0.02$			& 3340 		& 3.2 		& 510 & 98				\\
-2 Sep\tablenotemark{c} & 57633.69515938 & 15 & 69		& +2				& 562$^{+4}_{-6}$ 	& 2.5$^{+0.9}_{-0.6}$	& $>$430 	& $<$2.5	& 290 & 7  			\\
+2 Sep\tablenotemark{c} & 57633.69515938 & 15 & 69		& +2				& 562$^{+4}_{-6}$ 	& 2.5$^{+0.9}_{-0.6}$	& $>$430 	& $<$2.5	& $<$290 & 7  			\\
 7 Sep & 57638.49937435      & 12 		& 55			& +5 				& 567$^{+7}_{-9}$ 	& 1.3$^{+1.4}_{-0.8}$	& 130 		& 3.1 		& 420 & 3  			\\
 12 Sep\tablenotemark{a} & 57643.45730263  & 100 		& 508 & --5 		& 565.6$^{+0.6}_{-0.5}$ & 1.9$\pm0.1$		& 1170 		& 2.8 		& 510 & 34 			\\
-14 Sep\tablenotemark{a} & 57645.42958602   & 13 		& 64 				& +3			& 563$^{+5}_{-4}$ 	& 1.0$\pm0.7$		 	& 170 		& 2.8 		& 380 & 4  			\\
-15 Sep\tablenotemark{c} & 57646.46600650 & 20 & 87		& +1				& 569$\pm5$ 		& 2.7$^{+0.9}_{-1.4}$	& $>$420 	& $<$2.5 	& 430 & 10 			\\	
+14 Sep\tablenotemark{a} & 57645.42958602   & 13 		& 64 & +3			& 563$^{+5}_{-4}$ 	& 1.1$\pm0.7$		 	& 170 		& 2.8 		& 380 & 4  			\\
+15 Sep\tablenotemark{c} & 57646.46600650 & 20 & 87		& +1				& 569$\pm5$ 		& 2.5$^{+0.9}_{-1.4}$	& $>$420 	& $<$2.5 	& $<$430 & 10 			\\	
 17 Sep\tablenotemark{a,b} & 57648.43691490 & 25 & 111	& +9				& 564$\pm2$ 		& 1.4$^{+0.3}_{-0.4}$	& 260 		& 2.8 		& 470 & 7  			\\
@@
 Diffractive scintillation from the Milky Way has a typical bandwidth of 7~MHz along this line of sight \citep{2002astro.ph..7156C}, which is similar to the channel size of 4~MHz.
+The burst energy is calculated from the flux density in 5~ms and integrating over the optimal Gaussian spectral model.
 
-To better understand the spectra, we extracted dynamic radio spectra (time versus frequency) for 2d modeling with the MCMC sampler \emph{emcee} \citep{2013PASP..125..306F}.
-We modeled the dynamic spectra with a broad gaussian envelope (amplitude, center, width), a time delay according to the $\nu^2$\ dispersion law, and a temporal width.
-The 6-dimensional models were sampled with 100 walkers taking 500 steps; we ignored the first 200 steps to allow the walkers to properly sample the posterior distributions.
+To better understand the spectra, we used a Markov chain Monte Carlo (MCMC) method to model the dynamic radio spectra (time versus frequency).
+We used the Goodman and Weare affine invariant sampler \citep{goodman2010ensemble} as implemented in \emph{emcee} \citep{2013PASP..125..306F}.
+The dynamic spectra were modeled with a broad Gaussian envelope (amplitude, center, width), a time delay according to the $\nu^2$\ dispersion law, and a square pulse of temporal width.
+We use a log likelihood function $\ln \mathcal{L}=(-1/2)\ \sum_i (S_i - S_{i, \rm{model}})^2/\sigma_s^2$, where $S_i$\ refers to the measured and modeled flux density in a single pixel of the dynamic spectrum and $\sigma_s\approx 70\ \mu$Jy is the measured off-burst noise per 5~ms integration and 4~MHz channel.
 A flat prior was used over all ranges with valid data with the requirement that the integrated signal must have a detection significance higher than 8$\sigma$.
-The inter-channel modulation (scintillation) was ignored in the model.
-The measured, off-burst noise value was typically 70 mJy per 5~ms integration and 4~MHz channel.
+The 6-dimensional models were sampled with 100 chains taking 700 steps; we ignored the first 200 steps to properly sample the posterior distributions.
+
+**discuss goodness of fit?**
+... The inter-channel modulation was ignored in the model...
 
 The parameters for the best model of the dynamic spectrum are given in Table \ref{tab:spec} and the resulting Gaussian model overlaid on Figure \ref{fig:spec}.
-The typical burst has a spectral width of 500~MHz.
+The typical burst has a spectral width FWHM of 500~MHz.
 All but two of the best-fit Gaussians are centered inside the 3~GHz band and some appear contained by the 1~GHz wide band.
@@
  \end{minipage}
-\caption{Spectra and best-fit model for nine bursts seen by the VLA from 2.5 to 3.5~GHz.
+\caption{Spectra and best-fit model for nine bursts seen by the VLA from 2.5 to 3.5~GHz in the peak, dedispersed 5~ms integration.
 Starting at the top left (moving right and then down), they correspond to bursts on MJDs 57623, 57633.68, 57633.70, 57638, 57643, 57645, 57646, 57648, and 57649.
-The solid line is a best-fit Gaussian model found through MCMC modeling.
-Note that bursts are detected in 5~ms images generated from dedispersed visibilities.
+The solid line is a best-fit Gaussian model found through modeling.
 \label{fig:spec}}
@@
 This analysis differs from traditional analysis in that it simultaneously models the spectral and temporal evolution of the burst.
-Since the burst crosses many time-frequency pixel boundaries, the temporal modeling is sensitive to temporal properties smaller than the 5~ms integration time.
-Table \ref{tab:spec} shows that the typical burst width is measured as $2\pm1$~ms (95\% confidence interval); the brightest burst (57633.68) has a temporal width of $2.05\pm0.02$~ms.
-The burst arrival times are typically measured with a precision of 1~ms; the brightest burst arrival time is measured with a precision of $\sim50\mu$s.
+A typical \frb\ burst takes $\sim180$~ms or 36 integrations to cross the observing band from 2.5 to 3.5~GHz.
+The effect of a finite pulse width is visible as the burst moves from one integration to the next, even for widths narrower than the integration time of 5~ms.
+Table \ref{tab:spec} shows that the typical burst width is measured as $2\pm1$~ms (95\% confidence interval); the inter-channel dispersion smearing ranges from 0.4 to 1.1~ms across this band.
+The brightest burst (57633.68) is modeled with a temporal width of $2.05\pm0.02$~ms and its burst arrival time is measured with a precision of $\sim50\mu$s.
 Note that these errors are only accurate to the degree that the model represents the data.
 One potential bias in the model is that we do not model scintillation effects.
-
-**how does interchannel DM smearing compare to measured width?**
 
@@
 The equivalent plot for the other bursts show normally-distributed samples, but this burst shows significant structure in the samples.
+The parameters ``Amp'', ``Center'', and ``$\sigma_ch$'' refer to the Gaussian spectral shape, while ``DM'', ``int'', and ``dint'' refer to the temporal shape.
+The parameters are given in units of channels (4 MHz) and integrations (5 ms).
 \label{fig:corner}}
@@
 Two clusters of samples are identified for this burst: one narrow, low-DM and one wide, high-DM.
-Assuming that the model is appropriate, this implies that it can be decomposed into two bursts.
+Assuming that the model is appropriate, this implies that the burst can be decomposed into two subbursts.
 
@@
 The VLA data demonstrate that the burst-dependent DM effect is visible at frequencies near 3~GHz.
-Assuming a ``true'' DM of 560.5 pc cm$^{-3}$, the excess DM can be thought of as a frequency-dependent delay that varies between bursts with a delay rate up to 2~ms GHz$^{-1}$ or an effective DM of $\sim5$~pc cm$^{-3}$.
+Assuming a ``true'' DM of 560.5 pc cm$^{-3}$, the excess DM can be interpreted as a frequency-dependent delay that varies between bursts with a delay rate up to 2~ms GHz$^{-1}$ or an effective DM of $\sim5$~pc cm$^{-3}$.
 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{dmmodel}
-
 \includegraphics[width=\columnwidth]{burst_dmdt}
-
-\caption{(Top) DM as a function of time for nine 3~GHz bursts detected by the VLA.
+\caption{(Top) Burst time versus DM for nine 3~GHz bursts detected by the VLA.
 The 68\% confidence interval on DM is shown with a bar and the dahsed line shows the best-fit DM$=560.5$\ pc cm$^{-3}$ inferred for Arecibo observations at 1.4~GHz.
-(Bottom) Burst DM versus temporal width for all nine VLA bursts.
+(Bottom) Temporal width versus burst DM for the same nine VLA bursts.
 \label{fig:dmmodel}}
@@
 Rather than trying to estimate a completeness limit for each energy distribution, we assume an effective detection limit of 0.9 times the weakest burst detected; the best-fit slope is weakly dependent on this, but general conclusions are robust.
-We directly sampled the likelihood distribution to estimate a best slope of $\alpha_{\rm{VLA}}=-0.7^{+0.3}_{-0.4}$, $\alpha_{\rm{AO}}=-0.8^{+0.3}_{-0.5}$, and $\alpha_{\rm{GBT}}=-0.8^{+0.4}_{-0.5}$ (68\% confidence interval).
-Expressed as a powerlaw function in $dN/dE$, the slope index is approximately --1.7.
+We directly sampled the likelihood distribution to estimate a best slope of $\alpha_{\rm{VLA}}=-0.7^{+0.3}_{-0.4}$, $\alpha_{\rm{Arecibo}}=-0.8^{+0.3}_{-0.5}$, and $\alpha_{\rm{GBT}}=-0.8^{+0.4}_{-0.5}$ (68\% confidence interval).
+Expressed as a power law function in $dN/dE$, the slope index is approximately --1.7.
 
@@
 We present the first simultaneous detection of an FRB with multiple telescopes and over frequencies from 1.2 to 3.5~GHz.
-The Arecibo burst flux density is an order of magntude less than that seen by the VLA.
+The flux density of the Arecibo burst detected on MJD 57648 is an order of magntude less than that seen by the VLA.
 At the same time, three other bursts from \frb\ had similar observing coverage but were not detected simultaneously.
 This is consistent with the spectral structure observed within the 3~GHz VLA band, which is typically limited to a Gaussian envelope with width of roughly 500~MHz.
-The center frequency of this envelope is a unique property of each burst and does not show an obvious pattern between bursts.
+The center frequency of this envelope varies from burst to burst with no obvious pattern.
 
-If \frb\ burst spectra are typical of the larger FRB population, then population models need to be generalized beyond the assumption of a spectral powerlaw.
+If \frb\ burst spectra are typical of the larger FRB population, then population models need to be generalized beyond the assumption of a spectral power law.
 Most obviously, \frb\ implies that future multi-telescope searches for bursts are unlikely to simultaneously detect bursts in different bands.
@@
 The simultaneous VLA/Arecibo burst also shows that this excess is evident in an individual burst at 1.2 to 3.5~GHz.
+
+**How to use Hessels et al results on sub bursts and DM?**
 
@@
 
-The refined analysis shows that \frb\ has even higher isotropic energies than previously reported for \frb, reaching energies $E_{\rm{max}}\approx10^{40}$\ erg.
+Our refined analysis shows that \frb\ has even higher isotropic energies than previously reported for \frb, reaching energies $E_{\rm{max}}\approx10^{40}$\ erg.
 \frb\ has isotropic energies orders of magnitude higher than the strongest Crab giant pulses ($\sim10^{35}$~erg) and comparable brightness temperatures \citep[$T_{b,\rm{Crab}}\sim10^{41}$~K versus $T_{b, \rm{FRB 121102}}\sim10^{38}$~K;][]{2003Natur.422..141H,2014PhRvD..89j3009K}.
@@
 In \S \ref{sec:disn} we compare the energy distribution of the 9 VLA bursts to those reported earlier by Arecibo and the GBT.
-All three energy distributions can be characterized as a powerlaw in $dN/dE$ with slope $\sim-1.7$.
+All three energy distributions can be characterized as a power law in $dN/dE$ with slope $\sim-1.7$.
 This slope is seen even though the burst rate varies by almost an order of magnitude between observations and frequencies cover both 1.4 and 3~GHz bands.
 This suggests that the slope is related to the underlying physical process, rather than the burst detection rate at any given time.
-The value of the energy distribution slope is similar to that observed in gamma-ray fluence of bursts from soft-gamma repeaters \citep{2000ApJ...532L.121G, 2011ApJ...739...94S}.
+The value of the energy distribution slope is similar to that observed in magnetars \citep{2000ApJ...532L.121G, 2011ApJ...739...94S}.
 This similarity has been used to argue that bursts are driven by self-regulated critical phenomena \citep[slope$=-5/3$;][]{2011SoPh..274...99A}.
@@
 While the surprising brightness of new FRB discoveries was once seen as a cause for concern (i.e., a sign of terrestrial interference), we may be able to use this to infer properties of the overall population \citep{2007Sci...318..777L, 2016arXiv161105758R}.
-When modeling the flux distribution as a powerlaw, an isotropic distribution of sources will have a powerlaw index, $\alpha$, of --1.5 \citep[the ``Euclidean distribution'';][]{2016MNRAS.462..941L}.
+When modeling the flux distribution as a power law, an isotropic distribution of sources will have a power law index, $\alpha$, of --1.5 \citep[the ``Euclidean distribution'';][]{2017arXiv170208040C}.
 Prior to the measurement of the first GRB redshift, deviations from the Euclidean distribution were used to infer their cosmological distribution \citep[e.g., the $V/V_{\rm{max}}$\ test;][]{1992ApJ...388L..45M, 1995ApJ...453...25F}.
 Multiple studies have suggested that FRBs have a sub-Euclidean flux distribution \citep[$-0.5<\alpha<-0.9$;][]{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}.
-Others have noted that the flux distribution is not well modeled as a powerlaw, such that $\alpha$\ is effectively sensitivity (and telescope) dependent \citep{2016MNRAS.461..984O, 2017arXiv170208040C}.
+Others have noted that the flux distribution is not well modeled as a power law, such that $\alpha$\ is effectively sensitivity (and telescope) dependent \citep{2016MNRAS.461..984O, 2017arXiv170208040C}.
 
@@
 Rather than using wide band burst spectra to measure a single spectral index, we now must measure the burst rate as a function of frequency.
-These need to be measured at similar times to insure they represent a similar state of activitity of the FRB.
+These need to be measured at similar times to ensure they represent a similar state of the FRB.
 
@@
 A major outstanding question is whether this time-variable rate is driven by an intrinsic process \citep{2016ApJ...826..226K} or extrinsic (propagation) effects in the host galaxy or intergalactic medium \citep{CORDES}.
-However, the temporal distribution of VLA detections alone shows that \frb\ has significant correlation on short timescales.
-That is, detecting a burst predicts that you are more likely to find another burst soon thereafter and not detecting a burst predicts you will likey not detect another burst soon thereafter.
-While this is sometimes referred to as a ``red spectrum'' \citep{2016MNRAS.458L..89C}, the observations presented here are only sensitive to timescales of days (time between observations) and months (time between campaigns).
+However, the temporal distribution of VLA detections alone shows that \frb\ burst rate is significantly correlated on short timescales.
+That is, detecting a burst predicts that you are more likely to find another burst soon thereafter and not detecting a burst predicts you will likely not detect another burst soon thereafter.
+
+The burst time distribution is consistent with a ``red spectrum'' \citep{2016MNRAS.458L..89C}, although the observations presented here are only sensitive to timescales of days (time between observations) and months (time between campaigns).
 As has been noted elsewhere, this statistical property would weaken previous constraints on repetition \citep{2015MNRAS.454..457P,2015ApJ...807...16L}.
+If this statistical property describes other FRBs, then wide, shallow surveys are the preferred strategy for blind detection of FRBs.
+Also, since ``bursts predict bursts'', many short observations are more likely to detect an FRB than a single long observation of the same total length and all new FRB detections should be immediately and intensively followed up.
 
-If this statistical property describes other FRBs, then wide, shallow surveys are the preferred strategy for blind detection of FRBs.
-Also, since ``bursts predict bursts'', many short observations are more likely to detect an FRB than a single long observation of the same total length.
-
-\subsection{Revised Volumetric Rate}
+\subsection{Volumetric Rate of FRB Sources}
 
@@
 %The calculation of a volumetric rate has been used to study classes of optical and high-energy transient \citep{2006ARA&A..44..507W}. 
-\citet{2013Sci...341...53T} estimated an isotropic FRB rate of $10^{-3}$\ galaxy$^{-1}$\ yr$^{-1}$ by calculating the number of Milky Way-type galaxies out to a distance implied by assming all extragalactic DM originates in the IGM \citep[$z\approx0.9$\ for DM$\approx z\times900 \rm{pc}\ \rm{cm}^{-3}$;][]{2003ApJ...598L..79I,2004MNRAS.348..999I}.
-This rate is high \citep[comparable to the rate of core-collapse supernovae;][]{2006Natur.439...45D}, which has been used to argue that FRBs are likely not associated with other classes of transient, such as LGRBs or rarer SNe \citep{2006ARA&A..44..507W}.
-This challenges models for FRBs based on magnetars or young, fast pulsars, which are believed to power these rarer subclasses of optical/gamma-ray transient.
-However, since the FRB rate estimate depends on the telescope sensitivity, it is not appropriate to compare to other estimates based on source counts.
+\citet{2013Sci...341...53T} estimated an isotropic rate of FRB events of $10^{-3}$\ galaxy$^{-1}$\ yr$^{-1}$ by calculating the number of Milky Way-type galaxies out to a distance implied by assming all extragalactic DM originates in the IGM \citep[$z\approx0.9$\ for DM$\approx z\times900 \rm{pc}\ \rm{cm}^{-3}$;][]{2003ApJ...598L..79I,2004MNRAS.348..999I}.
+This rate is high \citep[comparable to the rate of core-collapse supernovae;][]{2006Natur.439...45D}, which has been used to argue that FRBs are likely not associated with other classes of transient, such as LGRBs or rare subclasses of SNe \citep{2006ARA&A..44..507W}.
+However, since this rate depends on telescope sensitivity, it is not appropriate to compare to other estimates based on source counts.
 
-Here, we reevaluate the FRB volumetric rate by assuming \frb\ is a prototype of the class.
-First, we recast the estimate as volumetric rate of FRB sources by including beaming and repetition effects.
-The volumetric birth rate of FRB sources is $R_{\rm{FRB}} = R_p /(N_r \Omega_b V (z))$, where $R_p$\ is the projected FRB rate, $N_r$\ is the number of bursts per source, $\Omega_b$\ is the beaming fraction, and $V(z)$\ is the comoving volume out to redshift $z$.
+Here, we reevaluate the FRB volumetric rate by assuming \frb\ is a prototype of the class and recasting it as a volumetric rate of FRB sources (i.e., a birth rate).
+The volumetric rate of FRB sources is $R_{\rm{FRB}} = R_p /(N_r \Omega_b V (z))$, where $R_p$\ is the projected FRB rate, $N_r$\ is the number of bursts per source, $\Omega_b$\ is the beaming fraction, and $V(z)$\ is the comoving volume out to redshift $z$.
 The newest estimates of the projected FRB rate are lower by a factor of 5 \citep[$2\times10^3\ \rm{sky}^{-1} \rm{day}^{-1}$\ at high Galactic latitudes and flux densities brighter than 1~Jy~ms; ][]{2016arXiv161100458L, 2016MNRAS.460L..30C, 2016MNRAS.455.2207R}.
+There is relatively little constraint on the beaming factor, but Galactic pulsars have values on the order of 10\% \citep{1998MNRAS.298..625T}.
 
-\frb\ has an absolute energy scale that can be used to convert the observation-dependent fluence limit into a characteristic FRB distance.
+\frb\ has an absolute energy scale that can be used to convert the observation-dependent fluence limit into a FRB horizon scale.
 At the typical Parkes survey parameters \citep[e.g.,][]{2016MNRAS.460L..30C}, a survey with a fluence limit of 1~Jy~ms can detect \frb\ at $z\approx1$.
-The distance inferred from the largest DMs observed \citep[$\sim1500$\ pc cm$^{-3}$;][]{2016MNRAS.460L..30C} is somewhat higher, but that likely overestimates distance since DM will have significant contributions from the host galaxy and intervening galaxies \citep{OPT, 2014ApJ...780L..33M}.
+The distance inferred from the largest DMs observed \citep[$\sim1500$\ pc cm$^{-3}$;][]{2016MNRAS.460L..30C} is somewhat higher, but that likely overestimates distance since DM is expected to have significant contributions from the host galaxy and intervening galaxies \citep{OPT, 2014ApJ...780L..33M}.
 %For reference, we note that cosmic star formation rate peaks between redshift of 2 and 3\citep{2014ARA&A..52..415M}.
@@
 Using an assumed horizon redshift of 1, we estimate a rate of $R_{\rm{FRB}} \approx 5\times10^{-5} N_r^{-1} (0.1/\Omega_b)$\ Mpc$^{-3}$\ yr$^{-1}$.
-The narrow burst spectral structure seen for \frb\ implies that observations have undercounted the rate by a factor of a few by ignoring bursts outside the band.
-There is also relatively little constraint on the beaming factor \citep[$\sim0.1$ for pulsars;][]{1998MNRAS.298..625T}.
+This calculation ignores time dilation, which underestimates the burst rate by a factor of 2 at the redshift horizon.
+The narrow burst spectral structure seen for \frb\ also suggests that the FRB rate is understated by a factor of a few by ignoring bursts that fall outside the observing band.
 Finally, we note that this estimate assumes that propagation effects do not significantly affect the detectability of FRBs, although scintillation and scattering likely play significant roles \citep{2015MNRAS.451.3278M, CORDES}.
 
-Despite its many assumptions, this is the first volumetric rate appropriate for comparison to rates used for other classes of transient.
+Despite its many assumptions, this volumetric rate is more appropriate for comparison to rates used for other classes of transient.
 The LGRB and SLSN-I rates are $10^{-7}$\ and $10^{-8}$\ Mpc$^{-3}$\ yr$^{-1}$, respectively \citep{2007ApJ...657L..73G,2012Sci...337..927G}.
-Comparing the FRB rate to these rates implies that FRB-emitting sources can be generated in LGRBs and SLSN-I if FRBs repeat $5\times10^2$\ and $5\times10^3$, respectively (assuming burst energies of $10^{40}$\ erg).
+Comparing the FRB rate to these rates implies that FRB-emitting sources can be generated in LGRBs and SLSN-I if FRBs repeat $5\times10^2$\ and $5\times10^3$\ times, respectively (assuming burst energies of $10^{40}$\ erg).
 \citet{2017arXiv170102370M} use the young magnetar model for FRBs to calculate the maximum number of bursts that can be powered its magnetic field as $\approx300$.
-Assuming this model for FRBs, LGRBs, and SLSN-I, the rate comparison suggests that the LGRB rate is most consistent with the FRB rate, although there might be multiple channels to producing FRB sources.
+Assuming this model for FRBs, LGRBs, and SLSN-I, the rate comparison suggests that the LGRB rate is most consistent with the FRB rate, although there is significant room for adjustment in the models and rate estimate.
+
+\citet{2017arXiv170400022N} made a similar estimate as this...
 
@@
 With its cosmological distance firmly established, \frb\ now serves as a new kind of standard by which FRBs are defined.
-That fact, combined with an abundance of data collected during its high activity state, allows us to apply this source to more general questions about the FRB population.
+That fact, combined with an abundance of data collected during its active state, allows us to apply this source to more general questions about the FRB population.
 
@@
 However, the energy of that burst was dominated by the VLA 3~GHz observing band and three other VLA bursts are undetected by Arecibo.
-That demonstrates the burst spectra cannot be characterized by a spectral index.
-Independently, we modelled dynamic spectra within the VLA 3~GHz band and show that most burst can be characterized by a Gaussian envelope of width $\sim500$\ MHz.
-This modeling also shows that the apparent DM changes from burst to burst.
-DM values are biased above the long-term average, which argues that bursts have intrinsic spectrotemporal structure that mimics DM.
-This confirms analysis of high-resolution Arecibo dynamic spectra and extends this phenomenology to the 3~GHz band.
+This demonstrates the burst spectra are poorly described by a power law with a single spectral index.
+Independently, we modelled dynamic spectra within the VLA 3~GHz band and show that most bursts can be characterized by a Gaussian envelope of width $\sim500$\ MHz.
+This modeling also shows that the apparent DM changes from burst to burst and that DM is biased above the long-term average measured at 1.4~GHz.
+This argues that bursts have intrinsic spectrotemporal structure that mimics DM, as seen in high-resolution Arecibo dynamic spectra (Hessels et al, in prep).
 
 With a characteristic width of a spectrum, we can estimate total (apparent) radio energy per bust.
-The cumulative energy distribution is characterized by a powerlaw in $dN/dE$ with slope of $\sim-1.7$.
-The amplitude of this powerlaw changes significantly between observational campaigns.
+The cumulative energy distribution is characterized by a power law in $dN/dE$ with slope of $\sim-1.7$.
+The amplitude of this power law changes significantly between observational campaigns.
 The stochastic nature of the burst rate suggestts that past constraints on FRB repetition are weaker than previously inferred.
@@
 We estimate a volumetric rate of FRB sources of $R_{\rm{FRB}} \approx 5\times10^{-5} (0.1/\Omega_b)$\ Mpc$^{-3}$\ yr$^{-1}$, which is appropriate for \frb-like energies of $10^{40}$\ erg that are detectable out to $z=1$.
-This rate is broadly consistent with models of FRBs from young magnetars or fast pulsars if the typical FRB repeats on the order of $10^3$\ times in its life.
+This rate is broadly consistent with models of FRBs from young magnetars or pulsars if the typical FRB repeats on the order of $10^3$\ times in its life.
 
@@
 
-\bibliographystyle{apj}
+\bibliographystyle{yahapj}
 
@@
 The AMI-LA telescope gratefully acknowledges support from the European Research Council under grant ERC-2012- StG-307215 LODESTONE, the UK Science and Technology Facilities Council (STFC) and the University of Cambridge.
+PS holds a Covington Fellowship at DRAO.
 

### 2017-04-11 timeline.py

@@ -39,21 +39,21 @@ rc('font', serif='Times New Roman')
 rc('font', size=16)
 
 def putdot(ax, i):
-	pltx = obsdate[i]
-	plty = offset[tel[i]]
-	if int(burst[i]):
-		ax.scatter(pltx, plty, marker='o', s=400, linewidth=2, facecolor='none', edgecolor='k')
-		if int(burst[i]) > 1:
-			ax.scatter(pltx, plty, marker='o', s=800, linewidth=2, facecolor='none', edgecolor='k')
-			if int(burst[i]) > 2:
-				ax.scatter(pltx, plty, marker='o', s=1200, linewidth=2, facecolor='none', edgecolor='k')
-	if tel[i] == 'AMI':
-		s = 250
-	else:
-		s = 80
-#	ax.plot_date(pltx, plty)#, s=band[i], verticalalignment='center', horizontalalignment='center')
-	ax.text(pltx, plty, s=band[i], verticalalignment='center', horizontalalignment='center')
-#	ax.scatter(pltx, plty, marker=psym[tel[i]], s=s, linewidth=3, facecolor=pcol[tel[i]], edgecolor='none')
+    pltx = obsdate[i]
+    plty = offset[tel[i]]
+    if int(burst[i]) > 1:
+        linewidth=3
+    else:
+        linewidth=2
+
+    if int(burst[i]):
+        ax.scatter(pltx, plty, marker='o', s=400, linewidth=linewidth, facecolor='none', edgecolor='k')
+
+    if tel[i] == 'AMI':
+        s = 250
+    else:
+        s = 80
+    ax.text(pltx, plty, s=band[i], verticalalignment='center', horizontalalignment='center')
 
 def d2n(yyyy, mm, dd):
 	return( date2num(datetime.date(yyyy, mm, dd)) )

### 2017-04-11 repeater-vladata.tex
working on new questions

@@
 \section{Introduction}
+
+**
+Open issues:
+- How to discuss Arecibo weird burst results and "true" DM
+-- earlier results are better stated as a change in profile shape with frequency.
+Just as for precision timing of pulsars.
+Could go with that for VLA.
+Error in estimate of DM caused by freq-dep pulse shape.
+"frequency evolution".
+-- how to motivate use of dm=560.5? no real need to if we focus on broad band result over delta dm.
+- Jason's Arecibo burst flux seems low
+-- radiometer eqn for for peak flux averaged over 5 ms. 2 ms diluted to 5 ms, so peak flux down by 2/5.
+- Frequency-dependent burst rate would be cool, but needs Arecibo L-band burst energies
+-- burst rate is best for daniele's paper. laura and others too.
+- How much detail in a table of obs times?
+-- put as much in as feasible. consider long term utility
+- GBT and other observations useful to include if no overlap?
 

### 2017-04-12 repeater-vladata.tex
flux density scale issue discussed better

@@
 We assumed a DM of 560.5 pc cm$^{-3}$ (Hessels et al., in prep) to calculate a dispersion delay of 189 and 734~ms from the top of the VLA and Arecibo bands, respectively.
-We used PRESTO \citep{2001PhDT.......123R} to calculate a barycentric time offset of 3.8~ms between the VLA and Arecibo data.
+We used PRESTO \citep{2001PhDT.......123R} to calculate a barycentric time offset of 3.8~ms between the VLA and Arecibo at the time of observation.
 
@@
 
-**integrated flux is assuming 5 ms width!**
-
-**confirm arecibo integrated flux and sensitivity**
+**redo multispec figure and comparison of \alpha**
 
 Figure \ref{fig:multi} shows spectra built from integrated flux densities measured (or limited) during three burst with multi-telescope observing coverage.
-The burst on 17 Sep 2016 was detected with VLA and Arecibo with significances of 25$\sigma$\ and 39$\sigma$\ with integrated flux densities of 111 mJy and 14 mJy at 3 and 1.4~GHz, respectively.
-The VLA integration time of 5~ms underresolves the pulse and the true integrated flux density would be 280 mJy for an assumed pulse width of 2~ms.
-% correct the followign for estimated integrated flux
+The burst on 17 Sep 2016 was detected with VLA and Arecibo with significances of 25$\sigma$\ and 39$\sigma$, which corresponds to peak flux densities of in 5~ms of 111 mJy and 14 mJy at 3 and 1.4~GHz, respectively.
+Here we assume a typical pulse width of 2~ms and measure VLA and Arecibo integrated flux densities of **xx and yy mJy** at 3 and 1.4~GHz, respectively.
 Assuming a power law flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha=2.7$.
@@
 
-To better understand the spectra, we used a Markov chain Monte Carlo (MCMC) method to model the dynamic radio spectra (time versus frequency).
+We used a Markov chain Monte Carlo (MCMC) method to model the dynamic radio spectra (time versus frequency).
 We used the Goodman and Weare affine invariant sampler \citep{goodman2010ensemble} as implemented in \emph{emcee} \citep{2013PASP..125..306F}.

### 2017-04-13 repeater-vladata.tex
draft ready for circulation

--- 2017-04-11 repeater-vladata.tex
@@
 Of the nine bursts detected by the Very Large Array at 3~GHz, three had simultaneous observing coverage at other observatories, of which one was detected by the Arecibo Observatory at 1.4~GHz.
-We use multi-observatory detection and constraints with modeling of bursts only seen at 3~GHz to confirm earlier results showing that burst spectra are not well characterized by a power law.
+We use multi-observatory constraints and modeling of bursts only seen at 3~GHz to confirm earlier results showing that burst spectra are not well characterized by a power law.
 We characterize burst spectra with a $\sim500$~MHz envelope and apparent radio energy as high as $10^{40}$\ erg.
-The dispersion measure apparently changes significantly between bursts, which suggests that bursts have spectral structure that randomly biases the estimate of DM by as much as 5 pc cm$^{-3}$.
+The dispersion measure apparently changes significantly between bursts, which suggests that bursts have frequency-dependent profiles that randomly bias the estimate of DM by up to 1\%.
 We use \frb\ as a prototype of the FRB class to estimate a volumetric birth rate of FRB sources $R_{\rm{FRB}} \approx 5\times10^{-5}$\ Mpc$^{-3}$\ yr$^{-1}$ for the cosmic volume out to redshift of 1.
@@
 \frb, also known as the ``repeating FRB'', was first detected in November 2012 by the Arecibo Observatory \citep{2014ApJ...790..101S}.
-In mid 2015, new Arecibo observations revealed a series of bursts at the same DM ($\sim559$\ pc cm$^{-3}$) and sky position that rules out cataclymic models for this source \citep{2016Natur.531..202S}.
+In mid 2015, new Arecibo observations revealed a series of bursts at a similar DM and sky position that rules out
+cataclymic models for this source \citep{2016Natur.531..202S}.
+The typical DM measured by early Arecibo Observations was 559 pc cm$^{-3}$ \citep{2016arXiv160308880S}, although somewhat higher value have been seen in more recent observations (560.5 pc cm$^{-3}$; Hessels et al., in prep).
+
 Beginning in August of 2015 (MJD 57623), we made the first of nine detections of \frb\ with the Karl G.\ Jansky Very Large Array \citep[VLA;][]{LOC} and localized it with a precision of 0.1\arcsec.
-Deep optical observing with the Gemini Observatory associated the FRB with a host galaxy at $z=0.193$\ \citep{OPT} and the European VLBI Network detected four more bursts to localize the source with a precision of 0.01\arcsec\ \citep[$\sim40$\ pc]{EVN}.
-
-\frb\ has now been localized four orders of magnitude better than any other FRB and placed at a cosmological distance.
-Its lookback and luminosity distances are 746 and 972 Mpc, assuming a concordance cosmology with parameters given by \citet{2016A&A...594A..13P}.
-This association means that \frb\ is orders of magnitude more luminous than any other millisecond transient and that its DM traces both the host and intergalactic medium \citep{OPT}.
+Deep optical observing with the Gemini Observatory associated the FRB with a host galaxy at $z=0.193$\ \citep{OPT} and the European VLBI Network detected four more bursts to localize the source with a precision of 0.01\arcsec, four orders of magnitude better than any other FRB \citep[$\sim40$\ pc]{EVN}.
+The lookback and luminosity distances for \frb\ are 746 and 972 Mpc, assuming a concordance cosmology with parameters given by \citet{2016A&A...594A..13P}.
+At this distance, \frb\ is orders of magnitude more luminous than any other millisecond transient.
 If \frb\ is representative of all FRBs, then we should expect them to be useful as probes of the intergalactic medium and their host galaxies.
@@
 \label{sec:obs}
+
 \begin{figure*}[t]
@@
 The data presented here were obtained from multiple programs and telescopes with a goal of interferometrically localizing \frb\ with the VLA.
-We coordinated observing between the VLA, Arecibo, Effelsberg, and AMI-LA telescopes, as shown in Figure \ref{fig:sched}.
+We coordinated observing between the VLA, Arecibo, Effelsberg, and AMI-LA telescopes, as shown in Figure \ref{fig:sched} and Table \ref{tab:obs}.
 Below, we summarize these observations, with a focus on those conducted simultaneously with VLA burst detections from \frb.
@@
 Original VLA visibility data are available under NRAO program codes 16A-459 and 16A-496 and can be downloaded at \url{http://archive.nrao.edu}.
+
+\begin{table*}
+\tiny
+\caption{Table of Observations}
+\centering
+\begin{tabular}{lcccccc}
+Day & Start time & Duration & Band & VLA Detections & Coverage & Detections \\
+(yyyy-mm-dd) & (hh:mm:ss) & (minutes) & & & &  \\ \hline
+2015-11-25 & 3:25:29 & 60 & L & 0 &  & \\
+2015-12-01 & 5:31:31 & 60 & L & 0 &  &  \\
+2015-12-03 & 2:53:57 & 60 & L & 0 &  &  \\
+2015-12-05 & 4:45:44 & 60 & L & 0 &  &  \\
+2015-12-07 & 4:37:50 & 60 & L & 0 &  &  \\
+2015-12-09 & 9:29:25 & 60 & L & 0 &  &  \\
+2015-12-11 & 9:22:27 & 60 & L & 0 &  &  \\
+2015-12-13 & 9:13:7 & 60 & L & 0 &  &  \\
+2015-12-15 & 9:6:16 & 60 & L & 0 &  &  \\
+2015-12-17 & 8:57:51 & 60 & L & 0 &  &  \\
+2016-04-25 & 15:39:33 & 42 & S & 0 &  &  \\
+2016-04-26 & 21:49:35 & 15 & S & 0 &  &  \\
+2016-04-30 & 19:14:46 & 60 & S & 0 &  &  \\
+2016-05-01 & 18:8:21 & 60 & S & 0 &  &  \\
+2016-05-03 & 22:53:26 & 60 & S & 0 &  &  \\
+2016-05-04 & 22:50:30 & 60 & S & 0 &  &  \\
+2016-05-06 & 18:25:12 & 60 & S & 0 &  &  \\
+2016-05-07 & 19:34:13 & 60 & S & 0 &  &  \\
+2016-05-08 & 19:30:20 & 60 & S & 0 &  &  \\
+2016-05-13 & 17:12:48 & 135 & S & 0 &  &  \\
+2016-05-14 & 17:14:11 & 135 & S & 0 &  &  \\
+2016-05-15 & 17:15:26 & 135 & S & 0 &  &  \\
+2016-05-16 & 16:59:52 & 135 & S & 0 &  &  \\
+2016-05-20 & 16:45:46 & 135 & S & 0 &  &  \\
+2016-05-21 & 16:44:6 & 135 & S & 0 &  &  \\
+2016-05-22 & 16:43:53 & 135 & S & 0 &  &  \\
+2016-05-23 & 16:44:11 & 135 & S & 0 &  &  \\
+2016-05-27 & 16:29:34 & 135 & S & 0 &  &  \\
+2016-08-23 & 17:26:28 & 54 & S & 1 &  &  \\
+2016-09-02 & 15:52:17 & 54 & S & 2 &  &  \\
+2016-09-07 & 10:14:50 & 120 & S & 1 &  &  \\
+2016-09-08 & 10:14:40 & 120 & S & 0 &  &  \\
+2016-09-10 & 9:59:36 & 120 & S & 0 &  &  \\
+2016-09-11 & 9:59:49 & 120 & S & 0 &  &  \\
+2016-09-12 & 9:15:19 & 120 & S & 1 & AMI-LA &  \\
+2016-09-13 & 9:23:59 & 120 & S & 0 &  &  \\
+2016-09-14 & 9:20:23 & 120 & S & 1 & Arecibo,AMI-LA &  \\
+2016-09-15 & 9:16:29 & 120 & S & 1 &  &  \\
+2016-09-16 & 9:11:23 & 120 & S & 0 &  &  \\
+2016-09-17 & 8:59:20 & 120 & S & 1 & Arecibo,Effelsberg,AMI-LA & Arecibo \\
+2016-09-18 & 8:59:27 & 120 & S & 1 & Arecibo,Effelsberg,AMI-LA &  \\
+2016-09-19 & 8:44:32 & 120 & S & 0 &  &  \\
+2016-09-20 & 8:44:33 & 120 & S & 0 &  &  \\
+2016-09-20 & 17:19:3 & 120 & C & 0 &  &  \\
+2016-09-21 & 9:13:57 & 120 & C & 0 &  &  \\
+2016-09-22 & 9:12:24 & 120 & C & 0 &  &  \\
+\end{tabular}
+%\tablenotetext{a}{}
+\label{tab:obs}
+\end{table*}
 
@@
 Images were formed for each integration with DMs of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$ and a time resampling grid of 5, 10, 20, 40, and 80 ms.
-This DM grid was chosen to maintain 90\% sensitivity to the nominal DM range of 540--570 pc cm$^{-3}$, which includes the known \frb\ DM of 559 pc cm$^{-3}$ \citep{2016arXiv160308880S}.
+This DM grid was chosen to maintain 90\% sensitivity to the nominal DM range of 540--570 pc cm$^{-3}$.
 Gain calibration was made from observations of J0555+3948 by an automated system (telcal), which uses phase-only calibration.
@@
 Four of the VLA bursts were observed simultaneously with either Arecibo, Effelsberg, or AMI-LA, and two were observed simultaneously with all four observatories (Figure \ref{fig:sched}).
-Of these bursts, only one VLA burst (on 17 Sep 2016) was simultaneously detected by another observatory (Arecibo).
+Of these bursts, only one VLA burst (on MJD 57648) was simultaneously detected by another observatory (Arecibo).
 
@@
 The temporal resolution of the VLA data (5~ms) is much coarser than that of Arecibo, so data were resampled to the Arecibo temporal grid after correcting for barycentric and dispersion measure offsets.
-We assumed a DM of 560.5 pc cm$^{-3}$ (Hessels et al., in prep) to calculate a dispersion delay of 189 and 734~ms from the top of the VLA and Arecibo bands, respectively.
-We used PRESTO \citep{2001PhDT.......123R} to calculate a barycentric time offset of 3.8~ms between the VLA and Arecibo data.
+We assumed a DM of 560.5 pc cm$^{-3}$ (Hessels et al., in prep) to calculate a dispersion delay of 189 and 734~ms from infinite frequency to the top of the VLA and Arecibo bands, respectively.
+We used PRESTO \citep{2001PhDT.......123R} to calculate a barycentric time offset of 3.8~ms between the VLA and Arecibo at the time of observation.
 
@@
 
-**integrated flux is assuming 5 ms width!**
-
-**confirm arecibo integrated flux and sensitivity**
-
-Figure \ref{fig:multi} shows spectra built from integrated flux densities measured (or limited) during three burst with multi-telescope observing coverage.
-The burst on 17 Sep 2016 was detected with VLA and Arecibo with significances of 25$\sigma$\ and 39$\sigma$\ with integrated flux densities of 111 mJy and 14 mJy at 3 and 1.4~GHz, respectively.
-The VLA integration time of 5~ms underresolves the pulse and the true integrated flux density would be 280 mJy for an assumed pulse width of 2~ms.
-% correct the followign for estimated integrated flux
-Assuming a power law flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha=2.7$.
-This is inconsistent with the spectral index limit implied by the Effelsberg nondetection at 4.5~GHz ($\alpha<0.6$\ for a 2~ms burst and $5\sigma$ limit).
+Figure \ref{fig:multi} shows coarse spectra built from integrated flux densities measured (or limited) for three burst with multi-telescope observing coverage.
+The burst on MJD 57648 was detected with VLA and Arecibo with significances of 25$\sigma$\ and 39$\sigma$, which corresponds to peak flux densities in 5~ms of 111 mJy and 14 mJy at 3 and 1.4~GHz, respectively.
+Here we assume a typical pulse width of 2~ms to measure VLA and Arecibo integrated flux densities of 278 and 64 mJy at 3 and 1.4~GHz, respectively.
+Assuming a power law flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha=1.9$.
+This is inconsistent with the spectral index limit implied by the Effelsberg nondetection at 4.5~GHz ($\alpha<-1.7$\ for a 2~ms burst and $5\sigma$ limit).
 
@@
 Two Arecibo nondetections and two Effelsberg nondetections of VLA bursts place mutually inconsistent lower and upper limits on the spectral index.
-The Arecibo upper limits at 1.4~GHz imply that burst spectral indices $\alpha_{1.4/3}>+3.7$, while at Effelsberg the flux limits require $\alpha_{3/4.5}<-0.4$.
-The strictest limits on $\alpha_{1.4/3}$\ and $\alpha_{3/4.5}$\ are both derived from the burst on 18 Sep 2016, which shows that a power law model is inappropriate even for a single burst.
+The Arecibo upper limits at 1.4~GHz imply that burst spectral indices $\alpha_{1.4/3}>+4.8$, while at Effelsberg the flux limits require $\alpha_{3/4.5}<-2.7$.
+The strictest limits on $\alpha_{1.4/3}$\ and $\alpha_{3/4.5}$\ are both derived from the burst on MJD 57649, which shows that a power law model is inappropriate even for a single burst.
 % could note that these limits are understated by VLA integrated flux underestimate
@@
 Upper limits assume a pulse width of 2~ms and a $5\sigma$ detection threshold.
-Overlapping points are offset by a few tens of MHz in frequency for visualization.
+Overlapping points are offset by tens of MHz in frequency for visualization.
  \label{fig:multi}}
@@
 
-To better understand the spectra, we used a Markov chain Monte Carlo (MCMC) method to model the dynamic radio spectra (time versus frequency).
+We used a Markov chain Monte Carlo (MCMC) method to model the dynamic radio spectra (time versus frequency).
 We used the Goodman and Weare affine invariant sampler \citep{goodman2010ensemble} as implemented in \emph{emcee} \citep{2013PASP..125..306F}.
 The dynamic spectra were modeled with a broad Gaussian envelope (amplitude, center, width), a time delay according to the $\nu^2$\ dispersion law, and a square pulse of temporal width.
+The inter-channel amplitude modulation was ignored in the model.
+
 We use a log likelihood function $\ln \mathcal{L}=(-1/2)\ \sum_i (S_i - S_{i, \rm{model}})^2/\sigma_s^2$, where $S_i$\ refers to the measured and modeled flux density in a single pixel of the dynamic spectrum and $\sigma_s\approx 70\ \mu$Jy is the measured off-burst noise per 5~ms integration and 4~MHz channel.
@@
 The 6-dimensional models were sampled with 100 chains taking 700 steps; we ignored the first 200 steps to properly sample the posterior distributions.
-
-**discuss goodness of fit?**
-... The inter-channel modulation was ignored in the model...
 
@@
 The effect of a finite pulse width is visible as the burst moves from one integration to the next, even for widths narrower than the integration time of 5~ms.
-Table \ref{tab:spec} shows that the typical burst width is measured as $2\pm1$~ms (95\% confidence interval); the inter-channel dispersion smearing ranges from 0.4 to 1.1~ms across this band.
+Table \ref{tab:spec} shows that the typical burst width is measured as $2\pm0.5$~ms (68\% confidence interval); the inter-channel dispersion smearing ranges from 0.4 to 1.1~ms across this band.
 The brightest burst (57633.68) is modeled with a temporal width of $2.05\pm0.02$~ms and its burst arrival time is measured with a precision of $\sim50\mu$s.
@@
 
-The top panel of Figure \ref{fig:dmmodel} shows the 68\% confidence intervals on the DM for all nine VLA bursts as a function of burst time.
-The burst DMs are not consistent with any single value and tend to be larger than the long-term average of 560.5 pc cm$^{-3}$.
-The range and variance in DM observed by the VLA is similar to that reported for Arecibo observations of \frb\ in \citet{2016arXiv160308880S}.
-As noted before, this is consistent with the idea that the DM measured at low temporal resolution (e.g., by the VLA or by single-dish observatories without coherent dedispersion) is determined by extrinsic (an electron column) dispersion and some spectrotemporal structure that changes between bursts.
-The VLA data demonstrate that the burst-dependent DM effect is visible at frequencies near 3~GHz.
-Assuming a ``true'' DM of 560.5 pc cm$^{-3}$, the excess DM can be interpreted as a frequency-dependent delay that varies between bursts with a delay rate up to 2~ms GHz$^{-1}$ or an effective DM of $\sim5$~pc cm$^{-3}$.
+Figure \ref{fig:dmmodel} compares the 68\% confidence intervals on the DM for all nine VLA bursts against detection time (top panel) and the modeled burst temporal width (bottom panel).
+The error weighted mean burst DM is 567.8$\pm$0.1 pc cm$^{-3}$, significantly larger than the long-term average of 560.5 pc cm$^{-3}$ seen by Arecibo during this campaign.
+However, we note that the 95\% confidence intervals in DM for multiple bursts are not consistent with this mean nor each other, which suggests that some burst-specific property can bias the measured DM.
+The variation in DM observed by the VLA at 3~GHz is similar to that reported for Arecibo observations of \frb\ in \citet{2016arXiv160308880S}.
+%As noted before, this is consistent with the idea that the DM measured at low temporal resolution (e.g., by the VLA or by single-dish observatories without coherent dedispersion) is determined by extrinsic (an electron column) dispersion and some spectrotemporal structure that changes between bursts.
 
@@
 \caption{(Top) Burst time versus DM for nine 3~GHz bursts detected by the VLA.
-The 68\% confidence interval on DM is shown with a bar and the dahsed line shows the best-fit DM$=560.5$\ pc cm$^{-3}$ inferred for Arecibo observations at 1.4~GHz.
+The DM scale for both panels is shown at the bottom.
+The 68\% confidence interval on DM is shown with a bar and the dahsed line shows the best-fit DM$=560.5$\ pc cm$^{-3}$ inferred from Arecibo observations at 1.4~GHz (Hessels et al, in prep).
 (Bottom) Temporal width versus burst DM for the same nine VLA bursts.
@@
 This is consistent with the spectral structure observed within the 3~GHz VLA band, which is typically limited to a Gaussian envelope with width of roughly 500~MHz.
-The center frequency of this envelope varies from burst to burst with no obvious pattern.
+This confirms earlier results at 1.4~GHz \citep{2016Natur.531..202S,2016arXiv160308880S} with a wider bandwidth and extends the presence of this phenomenon to 3~GHz.
 
@@
 Second, since burst spectra have limited bands, the burst detection rate at one frequency may not represent that at another.
-That will require rate estimates for the FRB population to be made explicitly frequency-dependent.
-Finally, we note that the odds of detecting a burst will improve with bandwidth beyond the gain in sensitivity, since bandwidths wider than the FRB characteristic width can find otherwise undetectable bursts.
+Rate estimates for the FRB population will need to explicitly account for the frequency-dependent rate.
+Finally, we note that the odds of detecting a burst will improve with bandwidth beyond the gain in sensitivity, since bandwidths wider than the FRB characteristic width are more likley to cover the burst envelope.
 However, this does require that FRB search algorithms search for bursts with a width equal to the characteristic width.
@@
 After correcting for barycentric and typical dispersion delays, the VLA/Arecibo burst spectrum shows a residual temporal drift.
-This drift can be interpreted as an excess DM of roughly 5 pc cm$^{-3}$.
-We also measure a burst-to-burst variation in DM within the whole sample of VLA 3~GHz bursts of a similar scale.
+This drift can be interpreted as an excess DM, but contemporaneous observations at 1.4~GHz measured a significantly lower DM (560.5 pc cm$^{-3}$; Hessels et al, in prep).
+This excess DM is comparable to the burst-to-burst variation in DM within the whole sample of VLA 3~GHz bursts.
 This variation had been noted in earlier 1.4~GHz Arecibo observations of \frb\ \citep{2016arXiv160308880S}, but the VLA bursts demonstrate that this burst-specific DM is seen up to 3~GHz.
-The simultaneous VLA/Arecibo burst also shows that this excess is evident in an individual burst at 1.2 to 3.5~GHz.
 
-**How to use Hessels et al results on sub bursts and DM?**
-
-These features are generally consistent with intrinsic burst properties described in \citet{WEIRD}.
-That work uses bright, coherently-dedispersed bursts to identify sub-bursts that preferentially drift to lower frequencies at later times.
-With high-resolution dynamic spectra, one can define a heuristic that distinguishes between a burst-specific dispersion-like effect and a more stable (``true'') dispersion.
-Since the sub-bursts tend to drift to lower frequencies, they systematically bias DM measurements made with low-resolution data (like the VLA and earlier Arecibo and GBT obsrevaitons).
-Interestingly, our modeling of the VLA burst dynamic spectra show a weak correlation between larger apparent DM and pulse width.
-This could be a signature of blending of many unresovled sub-bursts in a single VLA burst spectrum.
+One interpretation for the burst-dependent DM is that the bursts have a frequency-dependent pulse shape.
+Pulsar pulse shapes evolve with frequency on GHz frequency scales, presumably due to changes in the beam shape \citep{1988MNRAS.234..477L}.
+The burst-dependent DM changes are on the order of 1\% of the total DM (equivalent to a delay rate up to 2~ms GHz$^{-1}$), which is much larger than typically observed \citep{2017MNRAS.466.3706L}.
+The systematic offset of the VLA 3~GHz DM from that observed by Arecibo suggests that any such burst frequency evolution must be larger at higher frequencies.
+Our modeling of the VLA burst dynamic spectra show a weak correlation between larger apparent DM and pulse width.
+This could be a signature unresovled spectrotemporal structure in the VLA burst spectra that biases the measured DM.
 
@@
 To this complex scene, we add the fact that \frb\ burst spectra are not defined by a spectral index, which suggests that k-corrections are likely to be very difficult to calculate in practice.
-Rather than using wide band burst spectra to measure a single spectral index, we now must measure the burst rate as a function of frequency.
-These need to be measured at similar times to ensure they represent a similar state of the FRB.
-
-**how to include new result on freq-dependent burst rate?**
-
-If we assume \frb\ is representative of the FRB population, we can estimate this frequency-dependent burst rate.
-The VLA and Arecibo observed intensively in a coordinated fashion during the late-2016 campaign.
-A complete search for bursts from the Arecibo is ongoing, but early results suggest that the burst rate at a fixed energy is much higher at 1.4~GHz than at 3~GHz. 
-This suggests that high-redshift FRBs will have an apparently lower rate that flattens the $dN/dF$\ distribution in a manner similar to a k-correction.
-We can only infer the presence of this effect for observations near 1.4~GHz, since we have no estimate of the \frb\ burst rate outside the frequency range from 1.4 to 3~GHz in the observed frame.
-Propagation effects suggest that the rate will be lower at sub-GHz frequencies \citep{2017MNRAS.465.2286R, 2017arXiv170107457C}.
-If so, the tension between constraints on $\alpha$\ near 800~MHz and 1.4~GHz may be resolved by a frequency-dependent FRB rate that peaks near 1.4~GHz.
+If the FRB burst rate is higher at low (rest) radio frequencies, then high-redshift FRBs will have an lower (redshifted) rate that flattens the $dN/dF$\ distribution in a manner similar to a k-correction.
+However, propagation effects are expected to suppress the FRB rate at sub-GHz frequencies \citep{2017MNRAS.465.2286R, 2017arXiv170107457C} as well.
+The VLA and Arecibo observed intensively in a coordinated fashion during the late-2016 campaign and a comparison of their relative rates will be presented elsewhere.
 
@@
 
-**correct for time dilation?**
-
 %The calculation of a volumetric rate has been used to study classes of optical and high-energy transient \citep{2006ARA&A..44..507W}. 
@@
 Here, we reevaluate the FRB volumetric rate by assuming \frb\ is a prototype of the class and recasting it as a volumetric rate of FRB sources (i.e., a birth rate).
-The volumetric rate of FRB sources is $R_{\rm{FRB}} = R_p /(N_r \Omega_b V (z))$, where $R_p$\ is the projected FRB rate, $N_r$\ is the number of bursts per source, $\Omega_b$\ is the beaming fraction, and $V(z)$\ is the comoving volume out to redshift $z$.
-The newest estimates of the projected FRB rate are lower by a factor of 5 \citep[$2\times10^3\ \rm{sky}^{-1} \rm{day}^{-1}$\ at high Galactic latitudes and flux densities brighter than 1~Jy~ms; ][]{2016arXiv161100458L, 2016MNRAS.460L..30C, 2016MNRAS.455.2207R}.
-There is relatively little constraint on the beaming factor, but Galactic pulsars have values on the order of 10\% \citep{1998MNRAS.298..625T}.
+Crudely, the volumetric rate of FRB sources can be defined as $R_{\rm{FRB}} = R_p /(N_r \Omega_b V (z))$, where $R_p$\ is the projected FRB rate, $N_r$\ is the number of bursts per source, $\Omega_b$\ is the beaming fraction, and $V(z)$\ is the comoving volume out to redshift $z$.
+The newest estimates of the projected FRB rate are $2\times10^3\ \rm{sky}^{-1} \rm{day}^{-1}$\ at high Galactic latitudes and flux densities brighter than 1~Jy~ms \citep{2016arXiv161100458L, 2016MNRAS.460L..30C, 2016MNRAS.455.2207R}.
+There is relatively little constraint on the beaming factor, but Galactic pulsars have beaming solid angle fractions on the order of 10\% \citep{1998MNRAS.298..625T}.
 
-\frb\ has an absolute energy scale that can be used to convert the observation-dependent fluence limit into a FRB horizon scale.
+\frb\ has an absolute energy scale that can be used to estimate a horizon scale for the typical FRB survey sensitivity.
 At the typical Parkes survey parameters \citep[e.g.,][]{2016MNRAS.460L..30C}, a survey with a fluence limit of 1~Jy~ms can detect \frb\ at $z\approx1$.
@@
 The LGRB and SLSN-I rates are $10^{-7}$\ and $10^{-8}$\ Mpc$^{-3}$\ yr$^{-1}$, respectively \citep{2007ApJ...657L..73G,2012Sci...337..927G}.
-Comparing the FRB rate to these rates implies that FRB-emitting sources can be generated in LGRBs and SLSN-I if FRBs repeat $5\times10^2$\ and $5\times10^3$\ times, respectively (assuming burst energies of $10^{40}$\ erg).
+Comparing the FRB rate to these rates implies that FRB-emitting sources can be generated in LGRBs and SLSN-I if FRBs repeat $5\times10^2$\ and $5\times10^3$\ times\footnote{\citet{2017arXiv170400022N} provide a similar estimate of FRB birth rate and reach a similar conclusion.}, respectively (assuming burst energies of $10^{40}$\ erg).
 \citet{2017arXiv170102370M} use the young magnetar model for FRBs to calculate the maximum number of bursts that can be powered its magnetic field as $\approx300$.
 Assuming this model for FRBs, LGRBs, and SLSN-I, the rate comparison suggests that the LGRB rate is most consistent with the FRB rate, although there is significant room for adjustment in the models and rate estimate.
-
-\citet{2017arXiv170400022N} made a similar estimate as this...
 
@@
 With its cosmological distance firmly established, \frb\ now serves as a new kind of standard by which FRBs are defined.
-That fact, combined with an abundance of data collected during its active state, allows us to apply this source to more general questions about the FRB population.
+That fact, combined with a rich data set of many bursts, allows us to apply this source to more general questions about the FRB population.
 
@@
 This modeling also shows that the apparent DM changes from burst to burst and that DM is biased above the long-term average measured at 1.4~GHz.
-This argues that bursts have intrinsic spectrotemporal structure that mimics DM, as seen in high-resolution Arecibo dynamic spectra (Hessels et al, in prep).
+The nature of this DM change is not known, but could be explained by strong frequency-dependent profile evolution or unresolved spectrotemporal in the bursts.
 
-With a characteristic width of a spectrum, we can estimate total (apparent) radio energy per bust.
+With a characteristic burst spectrum, we can estimate total (apparent) radio energy per burst.
 The cumulative energy distribution is characterized by a power law in $dN/dE$ with slope of $\sim-1.7$.
 The amplitude of this power law changes significantly between observational campaigns.
-The stochastic nature of the burst rate suggestts that past constraints on FRB repetition are weaker than previously inferred.
-The relatively narrow spectral structure, flat energy distribution, and variable burst rate of \frb\ suggests that repeated observations, wide bandwidth, and large instantaneous field of view all improve the chance of making new FRB detections.
+The stochastic nature of the burst rate suggests that past constraints on FRB repetition are weaker than previously inferred.
+The relatively narrow spectral structure, flat energy distribution, and variable burst rate of \frb\ suggests that repeated observations, wide bandwidth, and large instantaneous field of view all improve the odds of FRB discovery.
 
-Assuming that \frb\ is reprentative of the FRB population, its burst energy distribution makes it possible to calculate the first volumetric FRB rate that does not depend on telescope sensitivity.
-We estimate a volumetric rate of FRB sources of $R_{\rm{FRB}} \approx 5\times10^{-5} (0.1/\Omega_b)$\ Mpc$^{-3}$\ yr$^{-1}$, which is appropriate for \frb-like energies of $10^{40}$\ erg that are detectable out to $z=1$.
+Assuming that \frb\ is reprentative of the FRB population, we calculate a volumetric birth rate of FRB sources that does not depend on telescope sensitivity.
+We estimate a volumetric rate of FRB sources of $R_{\rm{FRB}} \approx 5\times10^{-5} (0.1/\Omega_b)$\ Mpc$^{-3}$\ yr$^{-1}$, which is appropriate for \frb-like burst energies of $10^{40}$\ erg that are detectable out to $z=1$.
 This rate is broadly consistent with models of FRBs from young magnetars or pulsars if the typical FRB repeats on the order of $10^3$\ times in its life.

### 2017-04-25 repeater-vladata.tex
comments in as notes for all in but for jim

@@
 We present results of the coordinated observing campaign that made the first arcsecond localization of a Fast Radio Burst, FRB 121102.
-Of the nine bursts detected by the Very Large Array at 3~GHz, three had simultaneous observing coverage at other observatories, of which one was detected by the Arecibo Observatory at 1.4~GHz.
-We use multi-observatory constraints and modeling of bursts only seen at 3~GHz to confirm earlier results showing that burst spectra are not well characterized by a power law.
+Of the nine bursts detected by the Very Large Array at 3~GHz, three had simultaneous observing coverage at other observatories.
+Only one VLA burst was detected by another observatory, the Arecibo Observatory at 1.4~GHz.
+We use multi-observatory constraints and modeling of bursts seen only at 3~GHz to confirm earlier results showing that burst spectra are not well characterized by a power law.
 We characterize burst spectra with a $\sim500$~MHz envelope and apparent radio energy as high as $10^{40}$\ erg.
-The dispersion measure apparently changes significantly between bursts, which suggests that bursts have frequency-dependent profiles that randomly bias the estimate of DM by up to 1\%.
+We attribute significant changes in the apparent dispersion between bursts to frequency-dependent profiles that add a systematic random to the estimate of DM by up to 1\%.
 We use \frb\ as a prototype of the FRB class to estimate a volumetric birth rate of FRB sources $R_{\rm{FRB}} \approx 5\times10^{-5}$\ Mpc$^{-3}$\ yr$^{-1}$ for the cosmic volume out to redshift of 1.
 This rate is broadly consistent with models of FRBs from young magnetars or pulsars, if the typical FRB repeats on the order of $10^3$\ times in its life.
+
+% ** be sure future high-burst rate paper from Arecibo doesn't rule this out **
+
 \end{abstract}
@@
 Fast Radio Bursts (FRBs) were discovered ten years ago with the detection of a millisecond-duration radio transient with an anomalously high dispersion measure \citep{2007Sci...318..777L}.
-There are now 21 FRBs publicly known \footnote{See \url{http://www.astronomy.swin.edu.au/pulsar/frbcat}.} with dispersion measures (DMs) as high as 1600 pc cm$^{-3}$ and intrinsic temporal widths of order 2~ms.
 The large measured DM implied that FRBs originated outside of our Galaxy, potentially at cosmological distances, and were orders of magnitude more luminous than any other millisecond radio transient \citep{2013Sci...341...53T}.
+There are now 21 FRBs publicly known \footnote{See \url{http://www.astronomy.swin.edu.au/pulsar/frbcat}.} with dispersion measures (DMs) as high as 1600 pc cm$^{-3}$ and intrinsic temporal widths of order milliseconds.
 Both their energetics and distance have inspired a wide variety of models and astrophysical applications \citep[e.g.,][]{2014ApJ...780L..33M, 2014ApJ...797...70K, 2015MNRAS.450L..71F, 2016MNRAS.458L..19C, 2016MNRAS.457..232C, 2016MNRAS.462L..16P}.
@@
 cataclymic models for this source \citep{2016Natur.531..202S}.
-The typical DM measured by early Arecibo Observations was 559 pc cm$^{-3}$ \citep{2016arXiv160308880S}, although somewhat higher value have been seen in more recent observations (560.5 pc cm$^{-3}$; Hessels et al., in prep).
+The typical DM measured by early Arecibo observations was 559 pc cm$^{-3}$ \citep{2016arXiv160308880S}, although somewhat higher values have been seen in more recent observations (560.5 pc cm$^{-3}$; Hessels et al., in prep).
 
 Beginning in August of 2015 (MJD 57623), we made the first of nine detections of \frb\ with the Karl G.\ Jansky Very Large Array \citep[VLA;][]{LOC} and localized it with a precision of 0.1\arcsec.
-Deep optical observing with the Gemini Observatory associated the FRB with a host galaxy at $z=0.193$\ \citep{OPT} and the European VLBI Network detected four more bursts to localize the source with a precision of 0.01\arcsec, four orders of magnitude better than any other FRB \citep[$\sim40$\ pc]{EVN}.
-The lookback and luminosity distances for \frb\ are 746 and 972 Mpc, assuming a concordance cosmology with parameters given by \citet{2016A&A...594A..13P}.
-At this distance, \frb\ is orders of magnitude more luminous than any other millisecond transient.
+Deep optical observing with the Gemini Observatory associated the FRB with a host galaxy at $z=0.193$\ \citep{OPT} and the European VLBI Network detected four more bursts to localize the source with a precision of 0.01\arcsec, four orders of magnitude better than any other FRB \citep[precision of $\sim40$\ pc in linear distance;][]{EVN}.
+The lookback and luminosity distances for \frb\ are 746 and 972 Mpc, respectively, assuming a concordance cosmology with parameters given by \citet{2016A&A...594A..13P}.
+At this distance, \frb\ is orders of magnitude more luminous than any other millisecond radio transient.
 If \frb\ is representative of all FRBs, then we should expect them to be useful as probes of the intergalactic medium and their host galaxies.
@@
 
-Several new models of FRB origin have been been developed in response to the localization of \frb\ \citep{2017arXiv170104815K, 2017arXiv170102370M, 2017arXiv170104094Z, 2017arXiv170102492D, 2017arXiv170208644B, 2017arXiv170300393T}.
+Many new models of FRB origin have been been developed in response to the localization of \frb\ \citep{2017arXiv170104815K, 2017arXiv170102370M, 2017arXiv170104094Z, 2017arXiv170102492D, 2017arXiv170208644B, 2017arXiv170300393T}.
 The association of \frb\ with a compact, persistent radio source is consistent with bursts coming from a young magnetar that powers a luminous pulsar wind nebula \citep{2017arXiv170104815K}.
@@
 
-If we assume that \frb\ is representative of all FRBs, we use it to constrain the physical processes at play in the overall FRB population.
-More data is needed to determine if bursts trace intrinsic processes, such as coherent, pulsar-like emission \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C} or if extrinsic effects also play a role \citep{2015MNRAS.451.3278M, CORDES}.
-The paper presents an analysis of the spectral properties of VLA bursts implied by simultaneous observing at Effelsberg, GBT, AMI-LA, and Arecibo, including the first simultaneous detection of an FRB at two observatories.
+This paper presents an analysis of the spectral properties of VLA bursts implied by simultaneous observing at Effelsberg, GBT, AMI-LA, and Arecibo, including the first simultaneous detection of an FRB at two observatories.
+If we assume that \frb\ is representative of all FRBs, we can use it to constrain the physical processes at play in the overall FRB population.
 The repetition of \frb\ also has strong implications for calculations of their rate of occurrence \citep{2016MNRAS.458L..89C} and comparison to other classes of transient, such as superluminous supernovae \citep{OPT}.
+%More data is needed to determine if bursts trace intrinsic processes, such as coherent, pulsar-like emission \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C} or if extrinsic effects also play a role \citep{2015MNRAS.451.3278M, CORDES}.
 
@@
 \caption{The top and bottom panels summarize the observations and detections of \frb\ in the 2015 and 2016 campaigns.
-Circles highlight observations that detected bursts from \frb with multiple burst detections indicated with a heavy line.
+Circles highlight observations that detected bursts from \frb\ with multiple burst detections indicated with a heavy line.
 The black dashed lines show the VLA burst detections with simultaneous coverage at other telescopes and the solid line shows the simultaneous burst detection.
 Circled observations with no line indicate observations on the same day that did not overlap.
-Symbols show days with observations with letters L, S, C, U referring to radio frequencies of 1.4, 3, 4.5, and 12~GHz, respectively.
+Symbols show days with observations with letters L, S, C, U referring to radio frequencies of 1.4, 3, 4.5, and 15~GHz, respectively.
 \label{fig:sched}}
@@
 
-Computational (Jupyter) notebooks to reproduce the transient detection, localization, and analysis presented here can be found at \url{https://github.com/caseyjlaw/FRB121102}.
+Computational (Jupyter) notebooks to reproduce the transient detection, localization, and analysis presented here can be found at \software{\url{https://github.com/caseyjlaw/FRB121102}}.
 Time cut-out visibility data and calibration products are available at \url{https://doi.org/10.7910/DVN/TLDKXG}.
 Original VLA visibility data are available under NRAO program codes 16A-459 and 16A-496 and can be downloaded at \url{http://archive.nrao.edu}.
-
-\begin{table*}
-\tiny
-\caption{Table of Observations}
-\centering
-\begin{tabular}{lcccccc}
-Day & Start time & Duration & Band & VLA Detections & Coverage & Detections \\
-(yyyy-mm-dd) & (hh:mm:ss) & (minutes) & & & &  \\ \hline
-2015-11-25 & 3:25:29 & 60 & L & 0 &  & \\
-2015-12-01 & 5:31:31 & 60 & L & 0 &  &  \\
-2015-12-03 & 2:53:57 & 60 & L & 0 &  &  \\
-2015-12-05 & 4:45:44 & 60 & L & 0 &  &  \\
-2015-12-07 & 4:37:50 & 60 & L & 0 &  &  \\
-2015-12-09 & 9:29:25 & 60 & L & 0 &  &  \\
-2015-12-11 & 9:22:27 & 60 & L & 0 &  &  \\
-2015-12-13 & 9:13:7 & 60 & L & 0 &  &  \\
-2015-12-15 & 9:6:16 & 60 & L & 0 &  &  \\
-2015-12-17 & 8:57:51 & 60 & L & 0 &  &  \\
-2016-04-25 & 15:39:33 & 42 & S & 0 &  &  \\
-2016-04-26 & 21:49:35 & 15 & S & 0 &  &  \\
-2016-04-30 & 19:14:46 & 60 & S & 0 &  &  \\
-2016-05-01 & 18:8:21 & 60 & S & 0 &  &  \\
-2016-05-03 & 22:53:26 & 60 & S & 0 &  &  \\
-2016-05-04 & 22:50:30 & 60 & S & 0 &  &  \\
-2016-05-06 & 18:25:12 & 60 & S & 0 &  &  \\
-2016-05-07 & 19:34:13 & 60 & S & 0 &  &  \\
-2016-05-08 & 19:30:20 & 60 & S & 0 &  &  \\
-2016-05-13 & 17:12:48 & 135 & S & 0 &  &  \\
-2016-05-14 & 17:14:11 & 135 & S & 0 &  &  \\
-2016-05-15 & 17:15:26 & 135 & S & 0 &  &  \\
-2016-05-16 & 16:59:52 & 135 & S & 0 &  &  \\
-2016-05-20 & 16:45:46 & 135 & S & 0 &  &  \\
-2016-05-21 & 16:44:6 & 135 & S & 0 &  &  \\
-2016-05-22 & 16:43:53 & 135 & S & 0 &  &  \\
-2016-05-23 & 16:44:11 & 135 & S & 0 &  &  \\
-2016-05-27 & 16:29:34 & 135 & S & 0 &  &  \\
-2016-08-23 & 17:26:28 & 54 & S & 1 &  &  \\
-2016-09-02 & 15:52:17 & 54 & S & 2 &  &  \\
-2016-09-07 & 10:14:50 & 120 & S & 1 &  &  \\
-2016-09-08 & 10:14:40 & 120 & S & 0 &  &  \\
-2016-09-10 & 9:59:36 & 120 & S & 0 &  &  \\
-2016-09-11 & 9:59:49 & 120 & S & 0 &  &  \\
-2016-09-12 & 9:15:19 & 120 & S & 1 & AMI-LA &  \\
-2016-09-13 & 9:23:59 & 120 & S & 0 &  &  \\
-2016-09-14 & 9:20:23 & 120 & S & 1 & Arecibo,AMI-LA &  \\
-2016-09-15 & 9:16:29 & 120 & S & 1 &  &  \\
-2016-09-16 & 9:11:23 & 120 & S & 0 &  &  \\
-2016-09-17 & 8:59:20 & 120 & S & 1 & Arecibo,Effelsberg,AMI-LA & Arecibo \\
-2016-09-18 & 8:59:27 & 120 & S & 1 & Arecibo,Effelsberg,AMI-LA &  \\
-2016-09-19 & 8:44:32 & 120 & S & 0 &  &  \\
-2016-09-20 & 8:44:33 & 120 & S & 0 &  &  \\
-2016-09-20 & 17:19:3 & 120 & C & 0 &  &  \\
-2016-09-21 & 9:13:57 & 120 & C & 0 &  &  \\
-2016-09-22 & 9:12:24 & 120 & C & 0 &  &  \\
-\end{tabular}
-%\tablenotetext{a}{}
-\label{tab:obs}
-\end{table*}
 
@@
 In the late-2016 campaign, the first 34 hours of VLA observations were made at 3~GHz, while the last 6 hours were observed at 6~GHz.
+These observing session times are inclusive of calibration and overhead, which typically amounts to 15\% of the total observing time.
 
@@
 The channel frequency width was set to maximize sensitivity to the known DM of \frb\ with the largest total bandwidth.
-The total bandwidth at L (1.4~GHz), S (3~GHz), and C (6~GHz) bands was 256~MHz, 1024~MHz, and 2048~MHz, respectively.
+The total bandwidths at L (1.4~GHz), S (3~GHz), and C (6~GHz) bands were 256~MHz, 1024~MHz, and 2048~MHz, respectively.
 The 3~GHz data were recorded data in eight spectral windows with 32 channels each and had sensitivity of 5~mJy in 5~ms ($1\sigma$).
 
-Observations in August and September were searched by a prototype version of \rf\footnote{See \url{http://realfast.io}.}.
+Observations in August and September were searched by a prototype version of \rf\ \citep[see \url{http://realfast.io};][]{2017AAS...22933002L}.
 \rf\ is a real-time, fast imaging transient search system.
-The current prototype runs on CPU-based hardware that is normally dedicated to the VLA correlator; for this experiment, it runs the transient search pipeline software called \emph{rtpipe}\footnote{See \url{https://github.com/caseyjlaw/rtpipe} and \citet{2015ApJ...807...16L}.}.
+The current prototype runs on CPU-based hardware that is normally dedicated to the VLA correlator; for this experiment, it runs the transient search pipeline software called \software{\emph{rtpipe}\footnote{See \url{https://github.com/caseyjlaw/rtpipe}} and \citet{2015ApJ...807...16L}.}.
 Images were formed for each integration with DMs of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$ and a time resampling grid of 5, 10, 20, 40, and 80 ms.
@@
 Gain calibration was made from observations of J0555+3948 by an automated system (telcal), which uses phase-only calibration.
-A flux scale was calculated for each spectral window from an observation of 3C48 and applied to all burst spectra.
+A flux scale was calculated for each spectral window from an observation of 3C48 and applied to all burst spectra and has an accuracy of about 10\%.
 
@@
 We recorded total full Stokes polarization intensity spectra with a time resolution of 10.24~$\mu$s.
-Each frequency channel was coherently dedispersed to 557~pc cm$^{-3}$, thereby eliminating intra-channel dispersion smearing.
+Each frequency channel was coherently dedispersed to 557~pc cm$^{-3}$, significantly reducing intra-channel dispersion smearing.
 The full width at half maximum (FWHM) beam size at band center is 3.3\arcmin.
@@
 In total, 11 Arecibo observations had some simultaneous coverage with the VLA.
-All of these observations were conducted while pointing at the location of \frb\ measured by the VLA.
+All of these observations were conducted after the VLA localization, so they were pointing directly at \frb.
 Three of those observations had simultaneous coverage of VLA bursts and one of those Arecibo observations detected the VLA burst.
@@
 
-Effelsberg observations were conducted with the S60mm receiver at an observing frequency of 4.6 to 5.1~GHz.
-Total intensity spectra were recorded by the PFFTS backend in pulsar search mode with a time resolution of 65.5~$\mu$s and 128 frequency channels.
-The receiver has a system equivalent flux density is 18 Jy and a FWHM beam size of 2.4\arcmin\ at 4.85~GHz.
+Effelsberg observations were conducted with the S60mm receiver and recorded total intensity spectra with the PFFTS backend in pulsar search mode.
+The observations had a time resolution of 65.5~$\mu$s and 128 frequency channels.
+The receiver has a system equivalent flux density of 18 Jy and a FWHM beam size of 2.4\arcmin\ at 4.85~GHz.
 
-Five Effelsberg observations were made pointing at the known location of \frb\ and had some simultaneous coverage with the VLA; two observations were simultaneous with VLA bursts.
-Unfortunately, due to a configuration error, a 100~MHz bandwidth filter centered at 4.85~GHz was in place for both of these sessions.
-The sensitivity was about 28 mJy in 2 ms ($1\sigma$), which is two times worse than the nominal value.
+Five Effelsberg observations were made pointing at the known location of \frb\ and had some simultaneous coverage with the VLA.
+Two of these observations were simultaneous with VLA bursts.
+The nominal receiver bandwidth is from 4.6 to 5.1~GHz, but a configuration error reduced effective bandwidth to 100~MHz centered at 4.85~GHz for both of these observations during VLA bursts.
+The sensitivity in these observations was about 28 mJy in 2 ms ($1\sigma$), which is two times worse than the full-bandwidth value.
 No burst was detected in either observation.
@@
 
-We inspected the calibrated visibilities, and did not find any signal above 30 mJy in the 1s samples at and in the vicinity of the detected bursts.
+We inspected the calibrated visibilities, and did not find any signal above 30 mJy in the 1~s samples at and in the vicinity of the detected bursts.
 This corresponds to a sensitivity of 15~Jy for an assumed pulse width of 2~ms.
@@
 
-Four of the VLA bursts were observed simultaneously with either Arecibo, Effelsberg, or AMI-LA, and two were observed simultaneously with all four observatories (Figure \ref{fig:sched}).
+Four of the VLA bursts had simultaneous observing coverage with either Arecibo, Effelsberg, or AMI-LA.
+Two of the VLA bursts had simultaneous observing coverage by all four observatories (Figure \ref{fig:sched}).
 Of these bursts, only one VLA burst (on MJD 57648) was simultaneously detected by another observatory (Arecibo).
+
+% ** uncertainties in dm delay? **
 
@@
 We assumed a DM of 560.5 pc cm$^{-3}$ (Hessels et al., in prep) to calculate a dispersion delay of 189 and 734~ms from infinite frequency to the top of the VLA and Arecibo bands, respectively.
-We used PRESTO \citep{2001PhDT.......123R} to calculate a barycentric time offset of 3.8~ms between the VLA and Arecibo at the time of observation.
+We used PRESTO \citep{2001PhDT.......123R} to calculate a relative barycentric time correction of 3.8~ms between the VLA and Arecibo at the time of observation.
 
@@
  \caption{Composite dynamic specrum for the burst from \frb\ on MJD 57648 with data from the VLA and Arecibo observatories.
-Both data sets have been barycentered and corrected for an assumed dispersion measure of 560.5 pc $^{-3}$.
-The thick black line separates data from the VLA (2.5 to 3.5~GHz) and Arecibo (1.1 to 1.8~GHz) and flagged data is grey.
+The time axis is measured in milliseconds relative to MJD 57648.437788874842 with times corrected to the barycenter and infinite frequency (assuming DM$=560.5$\ pc $^{-3}$).
+The thick black line separates data from the VLA (2.5 to 3.5~GHz) and Arecibo (1.1 to 1.8~GHz) and flagged data are grey.
 The amplitude scale is normalized by assuming the Arecibo to VLA gain ratio is 10.
@@
 
-Figure \ref{fig:multi} shows coarse spectra built from integrated flux densities measured (or limited) for three burst with multi-telescope observing coverage.
+% ** errorbars on flux densities?
+
+Figure \ref{fig:multi} shows coarse spectra built from integrated flux densities measured (or limited) for three bursts with multi-telescope observing coverage.
 The burst on MJD 57648 was detected with VLA and Arecibo with significances of 25$\sigma$\ and 39$\sigma$, which corresponds to peak flux densities in 5~ms of 111 mJy and 14 mJy at 3 and 1.4~GHz, respectively.
@@
 
-Overall, the bursts with simultaneous observing coverage are not consistent with a power law model for the burst spectra.
+Overall, the bursts with simultaneous observing coverage are not well described by a power-law model.
 Two Arecibo nondetections and two Effelsberg nondetections of VLA bursts place mutually inconsistent lower and upper limits on the spectral index.
-The Arecibo upper limits at 1.4~GHz imply that burst spectral indices $\alpha_{1.4/3}>+4.8$, while at Effelsberg the flux limits require $\alpha_{3/4.5}<-2.7$.
+The Arecibo and Effelsberg upper limits at 1.4 and 4.5~GHz, respectively, limit all burst spectral indices $\alpha_{1.4/3}>+4.8$ and $\alpha_{3/4.5}<-2.7$.
 The strictest limits on $\alpha_{1.4/3}$\ and $\alpha_{3/4.5}$\ are both derived from the burst on MJD 57649, which shows that a power law model is inappropriate even for a single burst.
@@
  \includegraphics[width=\columnwidth]{multispec.png}
- \caption{Broadband spectra for three bursts of \frb\ with simultaneous multi-telescope observing coverage.
+ \caption{Broadband spectral measurements and limits for three bursts of \frb\ with simultaneous multi-telescope observing coverage (Arecibo at 1.4~GHz, VLA at 3~GHz, and Effelsberg at 4.5~GHz).
 Measurements are shown with dots and upper limits with triangles.
@@
 Stokes V values estimated from the dual-circular feeds as $(RR-LL)/(RR+LL)\approx3\%$, which is comparble to the systematic error induced by the primary beam\footnote{See EVLA memo \#195 at \url{https://library.nrao.edu/public/memos/evla/EVLAM_195.pdf}.}.
-Given that systematic effects dominate the apparent circular polarization, this observation limits the fractional circular polarization is less than 3\%.
+Given that systematic effects dominate the apparent circular polarization, this observation limits the fractional circular polarization to less than 3\%.
 
@@
 \begin{tabular}{cc|rrr|ccrrrr}
-\multicolumn{2}{c|}{Time} & \multicolumn{3}{c|}{Observered properties} & \multicolumn{6}{c}{Modeled properties} \\ \hline
-Calendar day & Burst time   & S/N & $S_{\rm{I, 5~ms}}$	& $S_{\rm{V}}$ 	& DM 			& dt 			& $S_{\rm{I,peak}}$ & Center & FWHM & $E_{\rm{int}}$ \\
+\multicolumn{2}{c|}{Time} & \multicolumn{3}{c|}{Observed properties} & \multicolumn{6}{c}{Modeled properties} \\ \hline
+Calendar day & Burst time   & S/N & $S_{\rm{I, 5~ms}}$	& $S_{\rm{V}}$ 	& DM 			& W 			& $S_{\rm{I,peak}}$ & Center & FWHM & $E_{\rm{int}}$ \\
 (2016)       &  (MJD)     &   (image)    & (mJy) 			& (mJy) 		    & (pc cm$^{-3})$ 	& (ms) 			& (mJy) 			& (GHz)  & (MHz) & ($10^{38}$\ erg)\\ \hline
@@
 \end{tabular}
+\tablecomments{$S_{\rm{V}}$ is the measured circular polarization of the burst, which dominated by systematic effects. All error ranges represent 68\% confidence intervals.}
 \tablenotetext{a}{Simultaneously observed by either Arecibo, Effelsberg, or AMI-LA.}
@@
 We used the Goodman and Weare affine invariant sampler \citep{goodman2010ensemble} as implemented in \emph{emcee} \citep{2013PASP..125..306F}.
-The dynamic spectra were modeled with a broad Gaussian envelope (amplitude, center, width), a time delay according to the $\nu^2$\ dispersion law, and a square pulse of temporal width.
+The dynamic spectra were modeled with a broad Gaussian envelope (amplitude, center, width), a time delay according to the $\nu^2$\ dispersion law, and a square temporal width (W).
 The inter-channel amplitude modulation was ignored in the model.
@@
 The parameters for the best model of the dynamic spectrum are given in Table \ref{tab:spec} and the resulting Gaussian model overlaid on Figure \ref{fig:spec}.
-The typical burst has a spectral width FWHM of 500~MHz.
+The typical burst spectrum has a FWHM of 500~MHz.
 All but two of the best-fit Gaussians are centered inside the 3~GHz band and some appear contained by the 1~GHz wide band.
 This is consistent with previous detections of \frb\ by Arecibo, which showed quasi-broadband structure \citep{2016arXiv160308880S} and large variation in the implied spectral index \citep{2014ApJ...790..101S}.
+
+% ** quantify how much of model shape is actually inside the band **
+
+% ** confusion as to whether inter-channel modulation is signal or noise ** jim also to do noise analysis **
+
+% ** spectra plot modifications: **
+% y-axis scale not shown! 
+% add mjd to each plot
+% Need to make sure impression differs of noise and inter-channel modulation
 
@@
 Table \ref{tab:spec} shows that the typical burst width is measured as $2\pm0.5$~ms (68\% confidence interval); the inter-channel dispersion smearing ranges from 0.4 to 1.1~ms across this band.
-The brightest burst (57633.68) is modeled with a temporal width of $2.05\pm0.02$~ms and its burst arrival time is measured with a precision of $\sim50\mu$s.
+The brightest burst (on 57633.68) is modeled with a temporal width of $2.05\pm0.02$~ms and its arrival time is measured with a precision of $\sim50\mu$s.
 Note that these errors are only accurate to the degree that the model represents the data.
 One potential bias in the model is that we do not model scintillation effects.
+
+% ** fix plot to show "W" instead of "dint"
 
@@
 The equivalent plot for the other bursts show normally-distributed samples, but this burst shows significant structure in the samples.
-The parameters ``Amp'', ``Center'', and ``$\sigma_ch$'' refer to the Gaussian spectral shape, while ``DM'', ``int'', and ``dint'' refer to the temporal shape.
+The parameters ``Amp'', ``Center'', and ``$\sigma_{ch}$'' refer to the Gaussian spectral shape, while ``DM'', ``int'', and ``W'' refer to the temporal shape.
 The parameters are given in units of channels (4 MHz) and integrations (5 ms).
@@
 However, the uncertainty in the peak DM measurement is defined by the signal-to-noise of the burst and how this changes with DM.
-The MCMC modeling is more sophsticated in that it considers a wider range of parameters and models both data and observing effects (frequency-time pixel boundaries) simultaneously.
+The MCMC modeling is more sophisticated in that it considers a wider range of parameters and models both data and observing effects (frequency-time pixel boundaries) simultaneously.
 
@@
 The burst rate for \frb\ varied dramatically throughout the 2016 observing campaign (Figure \ref{fig:sched}).
-In the early-2016 campaign, we observed for 30 hours at S-band and no bursts were detected.
-In the late-2016 observing campaign, we observed for 27 hours at S-band an detected nine bursts.
-Overall, the data quality is uniform and high, so the inhomogeneous burst distribution shows that the burst detection probability was not stationary.
+In the early-2016 campaign, we observed for 30 hours at 3~GHz and no bursts were detected.
+In the late-2016 observing campaign, we observed for 27 hours at 3~GHz and detected nine bursts.
+Overall, the data quality is uniform and high, so the inhomogeneous burst distribution shows that the burst rate was not uniform.
 
-Assuming that the burst detection probability follows a Poisson distribution, the mean VLA burst rate is $R=0.16\pm0.05\ \rm{hr}^{-1}$ above a fluence of 0.2 Jy ms.
-The nondetection in the first half of S-band limits the FRB rate to $R<0.1$\ hour$^{-1}$\ (95\% confidence limit).
-The S-band burst rate was much higher during the late-2016 campaign, $R=0.3\pm0.1$\ hour$^{-1}$.
+Assuming that the burst detection probability follows a Poisson distribution, the mean VLA, 3~GHz burst rate is $R=0.16\pm0.05\ \rm{hr}^{-1}$ above a fluence of 0.2 Jy ms.
+The nondetection in the first half of 3~GHz observing limits the FRB rate to $R<0.1$\ hour$^{-1}$\ (95\% confidence limit).
+The 3~GHz burst rate was much higher during the late-2016 campaign, $R=0.3\pm0.1$\ hour$^{-1}$.
 
@@
 Some VLA burst spectra seem to be contained by the 2.5 to 3.5~GHz band and most of them seem to have Gaussian envelopes that are well modeled by the emission within that band.
-Assuming that the Gaussian shape defines the emission window, the mean S-band flux density can be converted to a total energy with no further assumptions about their spectral properties.
+Assuming that the Gaussian shape defines the full emission window, the mean 3~GHz flux density can be converted to a total energy with no further assumptions about the burst spectral properties.
 
@@
 The VLA distribution shown represents the 27-hour, late-2016 campaign, which is longer than the single-dish campaigns presented here.
-However, since the VLA observations have a relatively coarse time resolution, it is not as sensitive as Arecibo and the GBT, so no bursts were detected weaker than $3\times10^{38}$~erg.
+However, since the VLA observations have a relatively coarse time resolution, it is not as sensitive as Arecibo and the GBT, so no bursts with energiest less than $3\times10^{38}$~erg were detected.
 The rate upper limit (95\% confidence) from the early-2016 VLA campaign shows that even identical observing campaigns have different detection rates.
@@
 \includegraphics[width=\columnwidth]{energy_disn}
-\caption{The cumulative burst energy distributions for the VLA, Arecibo, and GBT are shown with dots connected by solid, dashed, and dotted lines, respectively.
+\caption{The cumulative burst energy distributions for the VLA, Arecibo, and GBT bursts are shown with dots connected by solid, dashed, and dotted lines, respectively.
 The Arecibo distribution is derived from the 11 1.4~GHz bursts reported in \citet{2016Natur.531..202S} and the GBT distribution is derived from the 5 1.4~GHz bursts reported in \citet{2016arXiv160308880S}.
@@
 If \frb\ burst spectra are typical of the larger FRB population, then population models need to be generalized beyond the assumption of a spectral power law.
-Most obviously, \frb\ implies that future multi-telescope searches for bursts are unlikely to simultaneously detect bursts in different bands.
+Most obviously, \frb\ implies that future multi-telescope searches for bursts are unlikely to simultaneously detect bursts in different bands \citep[c.f.][]{1999ApJ...517..460S}.
 Second, since burst spectra have limited bands, the burst detection rate at one frequency may not represent that at another.
@@
 Finally, we note that the odds of detecting a burst will improve with bandwidth beyond the gain in sensitivity, since bandwidths wider than the FRB characteristic width are more likley to cover the burst envelope.
-However, this does require that FRB search algorithms search for bursts with a width equal to the characteristic width.
+However, FRB search algorithms will need to be modified to search for bursts with spectral width less than the full bandwidth.
 
@@
 Our modeling of the VLA burst dynamic spectra show a weak correlation between larger apparent DM and pulse width.
-This could be a signature unresovled spectrotemporal structure in the VLA burst spectra that biases the measured DM.
+This could be a signature of unresolved spectrotemporal structure in the VLA burst spectra that biases the measured DM.
+
+% ** expand on implication of spectral envelope in scintillation models **
 
@@
 Radio waves can be modified in a variety of ways (e.g., scintillation, scattering) and the duration of the emission in the source frame is not known \citep{2016arXiv160505890C}.
-\citet{CORDES} describe a model where plasma lensing near the source of an FRB can magnify radio emission by orders of mangitude.
+\citet{CORDES} describe a model where plasma lensing near the source of an FRB can magnify radio emission by orders of magnitude.
 That model argues that the simultaneous appearance of a burst from 1.2 to 3.5~GHz requires a lens with the focal frequency be $\gtrsim 3.5$~GHz.
@@
 A lens placed at $d_{sl}\approx1$~kpc is consistent with typical properties of the interstellar medium.
-Lenses that are influenced by the source would be much nearer to the source $d_{\sl} \ll 1$~kpc, requiring large values of $\frac{\rm DM_0}{a_{\rm AU}^2}$.
+Lenses that are influenced by the source would be much nearer to the source $d_{\sl} \ll 1$~kpc, requiring large values of $\rm{DM_0}/a_{\rm AU}^2$.
 
 \subsection{Energy Distribution}
+
+% ** discuss beaming **
 
@@
 While the surprising brightness of new FRB discoveries was once seen as a cause for concern (i.e., a sign of terrestrial interference), we may be able to use this to infer properties of the overall population \citep{2007Sci...318..777L, 2016arXiv161105758R}.
-When modeling the flux distribution as a power law, an isotropic distribution of sources will have a power law index, $\alpha$, of --1.5 \citep[the ``Euclidean distribution'';][]{2017arXiv170208040C}.
-Prior to the measurement of the first GRB redshift, deviations from the Euclidean distribution were used to infer their cosmological distribution \citep[e.g., the $V/V_{\rm{max}}$\ test;][]{1992ApJ...388L..45M, 1995ApJ...453...25F}.
+When modeling the flux distribution as a power law, an isotropic distribution of sources will have a power law index, $\alpha$, of --1.5.
+Prior to the measurement of the first GRB redshift, deviations from this Euclidean distribution were used to infer their cosmological distribution \citep[e.g., the $V/V_{\rm{max}}$\ test;][]{1992ApJ...388L..45M, 1995ApJ...453...25F}.
 Multiple studies have suggested that FRBs have a sub-Euclidean flux distribution \citep[$-0.5<\alpha<-0.9$;][]{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}.
@@
 A major outstanding question is whether this time-variable rate is driven by an intrinsic process \citep{2016ApJ...826..226K} or extrinsic (propagation) effects in the host galaxy or intergalactic medium \citep{CORDES}.
-However, the temporal distribution of VLA detections alone shows that \frb\ burst rate is significantly correlated on short timescales.
+However, the temporal distribution of VLA detections alone shows that the \frb\ burst rate is significantly correlated on short timescales.
 That is, detecting a burst predicts that you are more likely to find another burst soon thereafter and not detecting a burst predicts you will likely not detect another burst soon thereafter.
@@
 %The calculation of a volumetric rate has been used to study classes of optical and high-energy transient \citep{2006ARA&A..44..507W}. 
-\citet{2013Sci...341...53T} estimated an isotropic rate of FRB events of $10^{-3}$\ galaxy$^{-1}$\ yr$^{-1}$ by calculating the number of Milky Way-type galaxies out to a distance implied by assming all extragalactic DM originates in the IGM \citep[$z\approx0.9$\ for DM$\approx z\times900 \rm{pc}\ \rm{cm}^{-3}$;][]{2003ApJ...598L..79I,2004MNRAS.348..999I}.
+\citet{2013Sci...341...53T} estimated an isotropic rate of FRB events of $10^{-3}$\ galaxy$^{-1}$\ yr$^{-1}$ by calculating the number of Milky Way-type galaxies out to a distance implied by assming all extragalactic DM originates in the IGM \citep[$z\approx0.9$\ for DM$\approx z\times900\ \rm{pc}\ \rm{cm}^{-3}$;][]{2003ApJ...598L..79I,2004MNRAS.348..999I}.
 This rate is high \citep[comparable to the rate of core-collapse supernovae;][]{2006Natur.439...45D}, which has been used to argue that FRBs are likely not associated with other classes of transient, such as LGRBs or rare subclasses of SNe \citep{2006ARA&A..44..507W}.
@@
 Here, we reevaluate the FRB volumetric rate by assuming \frb\ is a prototype of the class and recasting it as a volumetric rate of FRB sources (i.e., a birth rate).
-Crudely, the volumetric rate of FRB sources can be defined as $R_{\rm{FRB}} = R_p /(N_r \Omega_b V (z))$, where $R_p$\ is the projected FRB rate, $N_r$\ is the number of bursts per source, $\Omega_b$\ is the beaming fraction, and $V(z)$\ is the comoving volume out to redshift $z$.
+Crudely, the volumetric rate of FRB sources can be defined as $R_{\rm{FRB}} = R_p /(N_r \Omega_b V (z))$, where $R_p$\ is the projected FRB rate, $N_r$\ is the number of bursts per source in a typical lifetime, $\Omega_b$\ is the beaming fraction, and $V(z)$\ is the comoving volume out to redshift $z$.
 The newest estimates of the projected FRB rate are $2\times10^3\ \rm{sky}^{-1} \rm{day}^{-1}$\ at high Galactic latitudes and flux densities brighter than 1~Jy~ms \citep{2016arXiv161100458L, 2016MNRAS.460L..30C, 2016MNRAS.455.2207R}.
@@
 The narrow burst spectral structure seen for \frb\ also suggests that the FRB rate is understated by a factor of a few by ignoring bursts that fall outside the observing band.
-Finally, we note that this estimate assumes that propagation effects do not significantly affect the detectability of FRBs, although scintillation and scattering likely play significant roles \citep{2015MNRAS.451.3278M, CORDES}.
+Finally, we note that this estimate assumes that Galactic latitude and propagation effects do not significantly affect the detectability of FRBs, although scintillation and scattering likely play significant roles \citep{2015MNRAS.451.3278M, CORDES}.
 
@@
 The LGRB and SLSN-I rates are $10^{-7}$\ and $10^{-8}$\ Mpc$^{-3}$\ yr$^{-1}$, respectively \citep{2007ApJ...657L..73G,2012Sci...337..927G}.
-Comparing the FRB rate to these rates implies that FRB-emitting sources can be generated in LGRBs and SLSN-I if FRBs repeat $5\times10^2$\ and $5\times10^3$\ times\footnote{\citet{2017arXiv170400022N} provide a similar estimate of FRB birth rate and reach a similar conclusion.}, respectively (assuming burst energies of $10^{40}$\ erg).
+Comparing the FRB rate to these rates implies that FRB-emitting sources can be generated in LGRBs and SLSN-I if FRBs repeat $5\times10^2$\ and $5\times10^3$\ times\footnote{\citet{2017arXiv170400022N} provide a similar estimate of FRB birth rate and reach a similar conclusion.}, respectively (assuming burst energies of $\sim10^{40}$\ erg).
 \citet{2017arXiv170102370M} use the young magnetar model for FRBs to calculate the maximum number of bursts that can be powered its magnetic field as $\approx300$.
-Assuming this model for FRBs, LGRBs, and SLSN-I, the rate comparison suggests that the LGRB rate is most consistent with the FRB rate, although there is significant room for adjustment in the models and rate estimate.
+Assuming this model for FRBs, LGRBs, and SLSN-I, the rate comparison suggest that the LGRB rate is most consistent with the FRB rate, although there is significant room for adjustment in the models and rate estimate.
 
@@
 
-Assuming that \frb\ is reprentative of the FRB population, we calculate a volumetric birth rate of FRB sources that does not depend on telescope sensitivity.
+Assuming that \frb\ is representative of the FRB population, we calculate a volumetric birth rate of FRB sources that does not depend on telescope sensitivity.
 We estimate a volumetric rate of FRB sources of $R_{\rm{FRB}} \approx 5\times10^{-5} (0.1/\Omega_b)$\ Mpc$^{-3}$\ yr$^{-1}$, which is appropriate for \frb-like burst energies of $10^{40}$\ erg that are detectable out to $z=1$.
-This rate is broadly consistent with models of FRBs from young magnetars or pulsars if the typical FRB repeats on the order of $10^3$\ times in its life.
+This rate is broadly consistent with models of FRBs from young magnetars or pulsars if the typical FRB repeats on the order of $10^3$\ times over its lifetime.
 
@@
 This platform will search a TB/hour data stream in real time in parallel with ongoing VLA observations, potentially detecting and localizing multiple FRBs per year.
+
+\appendix
+
+% ** add mjd colum **
+% ** use footnotes instead of last two cols? **
+
+\section{Table of Observations}
+
+\startlongtable
+\begin{deluxetable*}{lcccccc}
+\small
+\tablecaption{Table of Observations \label{tab:obs}}
+%\centering
+%\begin{tabular}{lcccccc}
+\startdata
+Day & Start time & Duration & Band & VLA Detections & Other Coverage & Other Detections \\
+(yyyy-mm-dd; UT) & (hh:mm:ss; UT) & (minutes) & & & &  \\ \hline
+2015-11-25 & 3:25:29 & 60 & 1.4~GHz & 0 &  & \\
+2015-12-01 & 5:31:31 & 60 & 1.4~GHz & 0 &  &  \\
+2015-12-03 & 2:53:57 & 60 & 1.4~GHz & 0 &  &  \\
+2015-12-05 & 4:45:44 & 60 & 1.4~GHz & 0 &  &  \\
+2015-12-07 & 4:37:50 & 60 & 1.4~GHz & 0 &  &  \\
+2015-12-09 & 9:29:25 & 60 & 1.4~GHz & 0 &  &  \\
+2015-12-11 & 9:22:27 & 60 & 1.4~GHz & 0 &  &  \\
+2015-12-13 & 9:13:7 & 60 & 1.4~GHz & 0 &  &  \\
+2015-12-15 & 9:6:16 & 60 & 1.4~GHz & 0 &  &  \\
+2015-12-17 & 8:57:51 & 60 & 1.4~GHz & 0 &  &  \\
+2016-04-25 & 15:39:33 & 42 & 3~GHz & 0 &  &  \\
+2016-04-26 & 21:49:35 & 15 & 3~GHz & 0 &  &  \\
+2016-04-30 & 19:14:46 & 60 & 3~GHz & 0 &  &  \\
+2016-05-01 & 18:8:21 & 60 & 3~GHz & 0 &  &  \\
+2016-05-03 & 22:53:26 & 60 & 3~GHz & 0 &  &  \\
+2016-05-04 & 22:50:30 & 60 & 3~GHz & 0 &  &  \\
+2016-05-06 & 18:25:12 & 60 & 3~GHz & 0 &  &  \\
+2016-05-07 & 19:34:13 & 60 & 3~GHz & 0 &  &  \\
+2016-05-08 & 19:30:20 & 60 & 3~GHz & 0 &  &  \\
+2016-05-13 & 17:12:48 & 135 & 3~GHz & 0 &  &  \\
+2016-05-14 & 17:14:11 & 135 & 3~GHz & 0 &  &  \\
+2016-05-15 & 17:15:26 & 135 & 3~GHz & 0 &  &  \\
+2016-05-16 & 16:59:52 & 135 & 3~GHz & 0 &  &  \\
+2016-05-20 & 16:45:46 & 135 & 3~GHz & 0 &  &  \\
+2016-05-21 & 16:44:6 & 135 & 3~GHz & 0 &  &  \\
+2016-05-22 & 16:43:53 & 135 & 3~GHz & 0 &  &  \\
+2016-05-23 & 16:44:11 & 135 & 3~GHz & 0 &  &  \\
+2016-05-27 & 16:29:34 & 135 & 3~GHz & 0 &  &  \\
+2016-08-23 & 17:26:28 & 54 & 3~GHz & 1 &  &  \\
+2016-09-02 & 15:52:17 & 54 & 3~GHz & 2 &  &  \\
+2016-09-07 & 10:14:50 & 120 & 3~GHz & 1 &  &  \\
+2016-09-08 & 10:14:40 & 120 & 3~GHz & 0 &  &  \\
+2016-09-10 & 9:59:36 & 120 & 3~GHz & 0 &  &  \\
+2016-09-11 & 9:59:49 & 120 & 3~GHz & 0 &  &  \\
+2016-09-12 & 9:15:19 & 120 & 3~GHz & 1 & AMI-LA &  \\
+2016-09-13 & 9:23:59 & 120 & 3~GHz & 0 &  &  \\
+2016-09-14 & 9:20:23 & 120 & 3~GHz & 1 & Arecibo, AMI-LA &  \\
+2016-09-15 & 9:16:29 & 120 & 3~GHz & 1 &  &  \\
+2016-09-16 & 9:11:23 & 120 & 3~GHz & 0 &  &  \\
+2016-09-17 & 8:59:20 & 120 & 3~GHz & 1 & Arecibo, Effelsberg, AMI-LA & Arecibo \\
+2016-09-18 & 8:59:27 & 120 & 3~GHz & 1 & Arecibo, Effelsberg, AMI-LA &  \\
+2016-09-19 & 8:44:32 & 120 & 3~GHz & 0 &  &  \\
+2016-09-20 & 8:44:33 & 120 & 3~GHz & 0 &  &  \\
+2016-09-20 & 17:19:3 & 120 & 6~GHz & 0 &  &  \\
+2016-09-21 & 9:13:57 & 120 & 6~GHz & 0 &  &  \\
+2016-09-22 & 9:12:24 & 120 & 6~GHz & 0 &  &  \\
+\enddata
+\tablecomments{Arecibo, Effelsberg, and AMI-LA observations were conducted at 1.4, 4.5, and 15~GHz, respectively.}
+%\end{tabular}
+%\tablenotetext{a}{}
+%\label{tab:obs}
+\end{deluxetable*}
 
@@
 The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc..
+Part of this research was carried out at the Jet Propulsion Laboratory, California Institute of Technology, under a contract with the National Aeronautics and Space Administration.
 % systems
@@
 PS holds a Covington Fellowship at DRAO.
+VMK acknowledges support from NSERC, CIFAR, the Canada Research Chair Program and from the Lorne Trottier Chair in Astrophysics \& Cosmology.
 

### 2017-04-26 repeater-vladata.tex
got jim comments in

@@
 
-\title{The \frb\ Campaign: A Multi-Telescope Burst Detection and Implications for the FRB Population}
+\title{A Multi-telescope Campaign on \frb: Implications for the FRB Population}
 \shorttitle{\frb\ Observing Campaign}
@@
 \begin{abstract}
-We present results of the coordinated observing campaign that made the first arcsecond localization of a Fast Radio Burst, FRB 121102.
+We present results of the coordinated observing campaign that made the first subarcsecond localization of a Fast Radio Burst, FRB 121102.
 Of the nine bursts detected by the Very Large Array at 3~GHz, three had simultaneous observing coverage at other observatories.
@@
 We use multi-observatory constraints and modeling of bursts seen only at 3~GHz to confirm earlier results showing that burst spectra are not well characterized by a power law.
-We characterize burst spectra with a $\sim500$~MHz envelope and apparent radio energy as high as $10^{40}$\ erg.
+We find that burst spectra are characterized by a $\sim500$~MHz envelope and apparent radio energy as high as $10^{40}$\ erg.
 We attribute significant changes in the apparent dispersion between bursts to frequency-dependent profiles that add a systematic random to the estimate of DM by up to 1\%.
-We use \frb\ as a prototype of the FRB class to estimate a volumetric birth rate of FRB sources $R_{\rm{FRB}} \approx 5\times10^{-5}$\ Mpc$^{-3}$\ yr$^{-1}$ for the cosmic volume out to redshift of 1.
-This rate is broadly consistent with models of FRBs from young magnetars or pulsars, if the typical FRB repeats on the order of $10^3$\ times in its life.
+We use \frb\ as a prototype of the FRB class to estimate a volumetric birth rate of FRB sources $R_{\rm{FRB}} \approx 5\times10^{-5}/N_r$\ Mpc$^{-3}$\ yr$^{-1}$, where $N_r$\ is the number of bursts per source over its lifetime.
+This rate is broadly consistent with models of FRBs from young pulsars or magnetars born in superluminous supernovae or long gamma-ray bursts, if the typical FRB repeats on the order of $10^3$\ times during its lifetime.
 
@@
 Fast Radio Bursts (FRBs) were discovered ten years ago with the detection of a millisecond-duration radio transient with an anomalously high dispersion measure \citep{2007Sci...318..777L}.
-The large measured DM implied that FRBs originated outside of our Galaxy, potentially at cosmological distances, and were orders of magnitude more luminous than any other millisecond radio transient \citep{2013Sci...341...53T}.
+The largest measured DMs imply that FRBs originate outside of our Galaxy, potentially at cosmological distances, and are orders of magnitude more luminous than pulses from Galactic pulsars \citep{2013Sci...341...53T}.
 There are now 21 FRBs publicly known \footnote{See \url{http://www.astronomy.swin.edu.au/pulsar/frbcat}.} with dispersion measures (DMs) as high as 1600 pc cm$^{-3}$ and intrinsic temporal widths of order milliseconds.
@@
 This paper is part of a series based on the first localization of an FRB and its unambiguous association to an extragalactic host \citep{LOC, OPT, EVN}.
-\frb, also known as the ``repeating FRB'', was first detected in November 2012 by the Arecibo Observatory \citep{2014ApJ...790..101S}.
-In mid 2015, new Arecibo observations revealed a series of bursts at a similar DM and sky position that rules out
-cataclymic models for this source \citep{2016Natur.531..202S}.
+\frb, also known as the ``repeating FRB'', was discovered \citep{2014ApJ...790..101S} in data acquired in 2012 as part of the PALFA survey of the Arecibo Observatory \citep{2006ApJ...637..446C}.
+In mid 2015, new Arecibo observations revealed a series of bursts at a similar DM and sky position that rules out cataclymic models for this source \citep{2016Natur.531..202S}.
 The typical DM measured by early Arecibo observations was 559 pc cm$^{-3}$ \citep{2016arXiv160308880S}, although somewhat higher values have been seen in more recent observations (560.5 pc cm$^{-3}$; Hessels et al., in prep).
@@
 The lookback and luminosity distances for \frb\ are 746 and 972 Mpc, respectively, assuming a concordance cosmology with parameters given by \citet{2016A&A...594A..13P}.
-At this distance, \frb\ is orders of magnitude more luminous than any other millisecond radio transient.
 If \frb\ is representative of all FRBs, then we should expect them to be useful as probes of the intergalactic medium and their host galaxies.
@@
 
-Many new models of FRB origin have been been developed in response to the localization of \frb\ \citep{2017arXiv170104815K, 2017arXiv170102370M, 2017arXiv170104094Z, 2017arXiv170102492D, 2017arXiv170208644B, 2017arXiv170300393T}.
+Many new models for the origin of FRBs have been developed in response to the localization of \frb\ \citep{2017arXiv170104815K, 2017arXiv170102370M, 2017arXiv170104094Z, 2017arXiv170102492D, 2017arXiv170208644B, 2017arXiv170300393T}.
 The association of \frb\ with a compact, persistent radio source is consistent with bursts coming from a young magnetar that powers a luminous pulsar wind nebula \citep{2017arXiv170104815K}.
@@
 In Section \ref{sec:obs}, we describe the multi-telescope observing campaign and a refined analysis of the nine VLA bursts.
-Section \ref{sec:res} presents the first spectrum of an FRB simultaneously detected at multiple telescopes and show that burst spectra cannot be modeled with a single spectral index.
+Section \ref{sec:res} presents the first spectrum of an FRB simultaneously detected at multiple telescopes and confirm that burst spectra cannot be modeled with a single spectral index.
 We then model the dynamic spectra to characterize the burst spectra, energies, and dispersion properties.
@@
 
-Computational (Jupyter) notebooks to reproduce the transient detection, localization, and analysis presented here can be found at \software{\url{https://github.com/caseyjlaw/FRB121102}}.
+Computational (Jupyter) notebooks to reproduce the transient detection, localization, and analysis presented here can be found at \url{https://github.com/caseyjlaw/FRB121102}.
 Time cut-out visibility data and calibration products are available at \url{https://doi.org/10.7910/DVN/TLDKXG}.
 Original VLA visibility data are available under NRAO program codes 16A-459 and 16A-496 and can be downloaded at \url{http://archive.nrao.edu}.
+
+% ** add mjd colum **
+
+\startlongtable
+\begin{deluxetable}{lcccc}
+\small
+\tablecaption{Table of VLA Observations \label{tab:obs}}
+%\centering
+%\begin{tabular}{lcccccc}
+\startdata
+Day & Start time & Duration & Freq. & Bursts \\% & Other Coverage & Other Detections \\
+(yyyy-mm-dd) & (hh:mm:ss) & (min) & (GHz) & \\ \hline
+2015-11-25 & 3:25:29 & 60 & 1.4 & 0 \\
+2015-12-01 & 5:31:31 & 60 & 1.4 & 0 \\
+2015-12-03 & 2:53:57 & 60 & 1.4 & 0 \\
+2015-12-05 & 4:45:44 & 60 & 1.4 & 0 \\
+2015-12-07 & 4:37:50 & 60 & 1.4 & 0 \\
+2015-12-09 & 9:29:25 & 60 & 1.4 & 0 \\
+2015-12-11 & 9:22:27 & 60 & 1.4 & 0 \\
+2015-12-13 & 9:13:7 & 60 & 1.4 & 0 \\
+2015-12-15 & 9:6:16 & 60 & 1.4 & 0 \\
+2015-12-17 & 8:57:51 & 60 & 1.4 & 0 \\
+2016-04-25 & 15:39:33 & 42 & 3 & 0  \\
+2016-04-26 & 21:49:35 & 15 & 3 & 0  \\
+2016-04-30 & 19:14:46 & 60 & 3 & 0  \\
+2016-05-01 & 18:8:21 & 60 & 3 & 0  \\
+2016-05-03 & 22:53:26 & 60 & 3 & 0  \\
+2016-05-04 & 22:50:30 & 60 & 3 & 0  \\
+2016-05-06 & 18:25:12 & 60 & 3 & 0  \\
+2016-05-07 & 19:34:13 & 60 & 3 & 0  \\
+2016-05-08 & 19:30:20 & 60 & 3 & 0  \\
+2016-05-13 & 17:12:48 & 135 & 3 & 0  \\
+2016-05-14 & 17:14:11 & 135 & 3 & 0  \\
+2016-05-15 & 17:15:26 & 135 & 3 & 0  \\
+2016-05-16 & 16:59:52 & 135 & 3 & 0  \\
+2016-05-20 & 16:45:46 & 135 & 3 & 0  \\
+2016-05-21 & 16:44:6 & 135 & 3 & 0  \\
+2016-05-22 & 16:43:53 & 135 & 3 & 0  \\
+2016-05-23 & 16:44:11 & 135 & 3 & 0  \\
+2016-05-27 & 16:29:34 & 135 & 3 & 0  \\
+2016-08-23 & 17:26:28 & 54 & 3 & 1  \\
+2016-09-02 & 15:52:17 & 54 & 3 & 2  \\
+2016-09-07 & 10:14:50 & 120 & 3 & 1  \\
+2016-09-08 & 10:14:40 & 120 & 3 & 0  \\
+2016-09-10 & 9:59:36 & 120 & 3 & 0  \\
+2016-09-11 & 9:59:49 & 120 & 3 & 0  \\
+2016-09-12 & 9:15:19 & 120 & 3 & 1\tablenotemark{a} \\ 
+2016-09-13 & 9:23:59 & 120 & 3 & 0  \\
+2016-09-14 & 9:20:23 & 120 & 3 & 1\tablenotemark{a,b} \\
+2016-09-15 & 9:16:29 & 120 & 3 & 1  \\
+2016-09-16 & 9:11:23 & 120 & 3 & 0  \\
+2016-09-17 & 8:59:20 & 120 & 3 & 1\tablenotemark{a,b,*,c} \\ 
+2016-09-18 & 8:59:27 & 120 & 3 & 1\tablenotemark{a,b,c} \\
+2016-09-19 & 8:44:32 & 120 & 3 & 0  \\
+2016-09-20 & 8:44:33 & 120 & 3 & 0  \\
+2016-09-20 & 17:19:3 & 120 & 6 & 0  \\
+2016-09-21 & 9:13:57 & 120 & 6 & 0  \\
+2016-09-22 & 9:12:24 & 120 & 6 & 0  \\
+\enddata
+\tablecomments{Times are in UT. Frequency is the approximate center of the bandwidth.}
+\tablenotetext{a}{AMI-LA coverage at 15~GHz.}
+\tablenotetext{b}{Arecibo coverage at 1.4~GHz.}
+\tablenotetext{*}{Arecibo detection at 1.4~GHz.}
+\tablenotetext{c}{Effelsberg coverage at 4.5~GHz.}
+%\end{tabular}
+%\tablenotetext{a}{}
+%\label{tab:obs}
+\end{deluxetable}
 
@@
 
-Observations in August and September were searched by a prototype version of \rf\ \citep[see \url{http://realfast.io};][]{2017AAS...22933002L}.
+Observations in August and September were searched by a prototype version of \rf\footnote{See \url{http://realfast.io} and \citep{2017AAS...22933002L}.}.
 \rf\ is a real-time, fast imaging transient search system.
-The current prototype runs on CPU-based hardware that is normally dedicated to the VLA correlator; for this experiment, it runs the transient search pipeline software called \software{\emph{rtpipe}\footnote{See \url{https://github.com/caseyjlaw/rtpipe}} and \citet{2015ApJ...807...16L}.}.
+The current prototype runs on CPU-based hardware that is normally dedicated to the VLA correlator; for this experiment, it runs the transient search pipeline software called \emph{rtpipe}\footnote{See \url{https://github.com/caseyjlaw/rtpipe} and \citet{2015ApJ...807...16L}.}.
 Images were formed for each integration with DMs of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$ and a time resampling grid of 5, 10, 20, 40, and 80 ms.
@@
 
-Burst detections and localizations were made within hours of data being recorded.
+Burst detections and localizations were made within 5--10 hours of data being recorded.
 The transient search starts when data are recorded and proceeds slower than real-time, so we refer to it as ``quasi real-time''.
@@
 \begin{table*}
-\caption{Properties of Bursts from \frb}
+\caption{Properties of \frb\ Bursts at 3~GHz}
 \centering
@@
 We used the Goodman and Weare affine invariant sampler \citep{goodman2010ensemble} as implemented in \emph{emcee} \citep{2013PASP..125..306F}.
-The dynamic spectra were modeled with a broad Gaussian envelope (amplitude, center, width), a time delay according to the $\nu^2$\ dispersion law, and a square temporal width (W).
+The dynamic spectra were modeled prior to dispersion correction.
+The spectral structure was modeled as a broad Gaussian envelope (parameters of amplitude, center, width), while the time evolution was modeled by a $\nu^2$\ dispersion law (parameters of starting integration, DM).
+Finally, the pulses were assumed to have an intrinsically square temporal width (parameter W).
+This 6-parameter model defined the intrinsic signal that was then distributed over a fixed time-frequency observing grid.
 The inter-channel amplitude modulation was ignored in the model.
@@
 % ** confusion as to whether inter-channel modulation is signal or noise ** jim also to do noise analysis **
+% ** could quantify deviations from Gaussian model relative to noise. An SNR relative to envelope.
 
@@
 
-% ** expand on implication of spectral envelope in scintillation models **
+% ** expand on implication of spectral envelope in context of scintillation interpretation of FRB brightness **
 
@@
 We estimate a volumetric rate of FRB sources of $R_{\rm{FRB}} \approx 5\times10^{-5} (0.1/\Omega_b)$\ Mpc$^{-3}$\ yr$^{-1}$, which is appropriate for \frb-like burst energies of $10^{40}$\ erg that are detectable out to $z=1$.
-This rate is broadly consistent with models of FRBs from young magnetars or pulsars if the typical FRB repeats on the order of $10^3$\ times over its lifetime.
+This rate is broadly consistent with models of FRBs from young pulsars or magnetars born in superluminous supernovae or long gamma-ray bursts, if the typical FRB repeats on the order of $10^3$\ times over its lifetime.
 
@@
 This platform will search a TB/hour data stream in real time in parallel with ongoing VLA observations, potentially detecting and localizing multiple FRBs per year.
-
-\appendix
-
-% ** add mjd colum **
-% ** use footnotes instead of last two cols? **
-
-\section{Table of Observations}
-
-\startlongtable
-\begin{deluxetable*}{lcccccc}
-\small
-\tablecaption{Table of Observations \label{tab:obs}}
-%\centering
-%\begin{tabular}{lcccccc}
-\startdata
-Day & Start time & Duration & Band & VLA Detections & Other Coverage & Other Detections \\
-(yyyy-mm-dd; UT) & (hh:mm:ss; UT) & (minutes) & & & &  \\ \hline
-2015-11-25 & 3:25:29 & 60 & 1.4~GHz & 0 &  & \\
-2015-12-01 & 5:31:31 & 60 & 1.4~GHz & 0 &  &  \\
-2015-12-03 & 2:53:57 & 60 & 1.4~GHz & 0 &  &  \\
-2015-12-05 & 4:45:44 & 60 & 1.4~GHz & 0 &  &  \\
-2015-12-07 & 4:37:50 & 60 & 1.4~GHz & 0 &  &  \\
-2015-12-09 & 9:29:25 & 60 & 1.4~GHz & 0 &  &  \\
-2015-12-11 & 9:22:27 & 60 & 1.4~GHz & 0 &  &  \\
-2015-12-13 & 9:13:7 & 60 & 1.4~GHz & 0 &  &  \\
-2015-12-15 & 9:6:16 & 60 & 1.4~GHz & 0 &  &  \\
-2015-12-17 & 8:57:51 & 60 & 1.4~GHz & 0 &  &  \\
-2016-04-25 & 15:39:33 & 42 & 3~GHz & 0 &  &  \\
-2016-04-26 & 21:49:35 & 15 & 3~GHz & 0 &  &  \\
-2016-04-30 & 19:14:46 & 60 & 3~GHz & 0 &  &  \\
-2016-05-01 & 18:8:21 & 60 & 3~GHz & 0 &  &  \\
-2016-05-03 & 22:53:26 & 60 & 3~GHz & 0 &  &  \\
-2016-05-04 & 22:50:30 & 60 & 3~GHz & 0 &  &  \\
-2016-05-06 & 18:25:12 & 60 & 3~GHz & 0 &  &  \\
-2016-05-07 & 19:34:13 & 60 & 3~GHz & 0 &  &  \\
-2016-05-08 & 19:30:20 & 60 & 3~GHz & 0 &  &  \\
-2016-05-13 & 17:12:48 & 135 & 3~GHz & 0 &  &  \\
-2016-05-14 & 17:14:11 & 135 & 3~GHz & 0 &  &  \\
-2016-05-15 & 17:15:26 & 135 & 3~GHz & 0 &  &  \\
-2016-05-16 & 16:59:52 & 135 & 3~GHz & 0 &  &  \\
-2016-05-20 & 16:45:46 & 135 & 3~GHz & 0 &  &  \\
-2016-05-21 & 16:44:6 & 135 & 3~GHz & 0 &  &  \\
-2016-05-22 & 16:43:53 & 135 & 3~GHz & 0 &  &  \\
-2016-05-23 & 16:44:11 & 135 & 3~GHz & 0 &  &  \\
-2016-05-27 & 16:29:34 & 135 & 3~GHz & 0 &  &  \\
-2016-08-23 & 17:26:28 & 54 & 3~GHz & 1 &  &  \\
-2016-09-02 & 15:52:17 & 54 & 3~GHz & 2 &  &  \\
-2016-09-07 & 10:14:50 & 120 & 3~GHz & 1 &  &  \\
-2016-09-08 & 10:14:40 & 120 & 3~GHz & 0 &  &  \\
-2016-09-10 & 9:59:36 & 120 & 3~GHz & 0 &  &  \\
-2016-09-11 & 9:59:49 & 120 & 3~GHz & 0 &  &  \\
-2016-09-12 & 9:15:19 & 120 & 3~GHz & 1 & AMI-LA &  \\
-2016-09-13 & 9:23:59 & 120 & 3~GHz & 0 &  &  \\
-2016-09-14 & 9:20:23 & 120 & 3~GHz & 1 & Arecibo, AMI-LA &  \\
-2016-09-15 & 9:16:29 & 120 & 3~GHz & 1 &  &  \\
-2016-09-16 & 9:11:23 & 120 & 3~GHz & 0 &  &  \\
-2016-09-17 & 8:59:20 & 120 & 3~GHz & 1 & Arecibo, Effelsberg, AMI-LA & Arecibo \\
-2016-09-18 & 8:59:27 & 120 & 3~GHz & 1 & Arecibo, Effelsberg, AMI-LA &  \\
-2016-09-19 & 8:44:32 & 120 & 3~GHz & 0 &  &  \\
-2016-09-20 & 8:44:33 & 120 & 3~GHz & 0 &  &  \\
-2016-09-20 & 17:19:3 & 120 & 6~GHz & 0 &  &  \\
-2016-09-21 & 9:13:57 & 120 & 6~GHz & 0 &  &  \\
-2016-09-22 & 9:12:24 & 120 & 6~GHz & 0 &  &  \\
-\enddata
-\tablecomments{Arecibo, Effelsberg, and AMI-LA observations were conducted at 1.4, 4.5, and 15~GHz, respectively.}
-%\end{tabular}
-%\tablenotetext{a}{}
-%\label{tab:obs}
-\end{deluxetable*}
 
@@
 
-We thank Liam Connor for useful feedback and the VLA staff for their support of \rf\ development.
+We thank the VLA staff for their support of \rf\ development and Liam Connor for useful feedback.
 We acknowledge partial support from the Research Corporation for Scientific Advancement (RCSA) for participation in the meeting Fast Radio Bursts: New Probes of Fundamental Physics and Cosmology at the Aspen Center for Physics (February 12-17, 2017).
+
+\software{\emph{rtpipe}, \emph{realfast}}
 

### 2017-04-26 repeater-vladata.tex
modified obs table

@@
 
+\author{K.~Stovall}
+\affiliation{National Radio Astronomy Observatory, Socorro, NM 87801, USA}
+
 \author{S.~P.~Tendulkar}
@@
 This rate is broadly consistent with models of FRBs from young pulsars or magnetars born in superluminous supernovae or long gamma-ray bursts, if the typical FRB repeats on the order of $10^3$\ times during its lifetime.
-
-% ** be sure future high-burst rate paper from Arecibo doesn't rule this out **
 
@@
 The association of \frb\ with a compact, persistent radio source is consistent with bursts coming from a young magnetar that powers a luminous pulsar wind nebula \citep{2017arXiv170104815K}.
-At the same time, \frb\ is found in a low-metallicity dwarf galaxy \citep{OPT, 2017arXiv170102370M}, which is not a prediction of models that scale with stellar mass or star formation \citep{2017arXiv170400022N}.
+At the same time, \frb\ is found in a low-metallicity dwarf galaxy \citep{OPT, 2017arXiv170102370M}, which was not predicted by origin models that scale with stellar mass or star formation \citep{2017arXiv170400022N}.
 These galaxies are the preferred environment for long GRBs and Type-I superluminous supernovae (LGRB and SLSN-I, respectively), which have been suggested are signatures of the magnetar birth \citep{2008AJ....135.1136M, 2014ApJ...787..138L}.
 
-%Also, it has not been demonstrated that \frb\ is representative of the overall FRB population.
-In fact, the repetition of its bursts is unique among all FRBs \citep{2015MNRAS.454..457P}, so it is natural to ask whether \frb\ is representative.
-An important first step is to demonstrate that the properties of \frb\ are consistent with the significant body of facts for the overall population \citep{2015MNRAS.451.3278M, 2016MPLA...3130013K}.
-The repeating nature of \frb\ provides us with a sample of bursts covering a range of spectral properties, temporal properties, and luminosities that can be used to test its connection to the larger FRB population.
-
-This paper presents an analysis of the spectral properties of VLA bursts implied by simultaneous observing at Effelsberg, GBT, AMI-LA, and Arecibo, including the first simultaneous detection of an FRB at two observatories.
+This paper presents an analysis of the spectral properties of VLA bursts implied by simultaneous observing at Arecibo, Effelsberg, the Long-Wavelength Array (LWA), and the Arcminute Microkelvin Imager Large Array (AMI-LA).
+This includes the first simultaneous detection of an FRB at two observatories, between the VLA and Arecibo.
 If we assume that \frb\ is representative of all FRBs, we can use it to constrain the physical processes at play in the overall FRB population.
 The repetition of \frb\ also has strong implications for calculations of their rate of occurrence \citep{2016MNRAS.458L..89C} and comparison to other classes of transient, such as superluminous supernovae \citep{OPT}.
-%More data is needed to determine if bursts trace intrinsic processes, such as coherent, pulsar-like emission \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C} or if extrinsic effects also play a role \citep{2015MNRAS.451.3278M, CORDES}.
 
@@
 Symbols show days with observations with letters L, S, C, U referring to radio frequencies of 1.4, 3, 4.5, and 15~GHz, respectively.
+% ** add LWA as "V" for VHF?
 \label{fig:sched}}
@@
 The data presented here were obtained from multiple programs and telescopes with a goal of interferometrically localizing \frb\ with the VLA.
-We coordinated observing between the VLA, Arecibo, Effelsberg, and AMI-LA telescopes, as shown in Figure \ref{fig:sched} and Table \ref{tab:obs}.
+We coordinated observing between the VLA, Arecibo, Effelsberg, LWA, and AMI-LA telescopes, as shown in Figure \ref{fig:sched} and Table \ref{tab:obs}.
 Below, we summarize these observations, with a focus on those conducted simultaneously with VLA burst detections from \frb.
@@
 Original VLA visibility data are available under NRAO program codes 16A-459 and 16A-496 and can be downloaded at \url{http://archive.nrao.edu}.
-
-% ** add mjd colum **
 
@@
 \startdata
-Day & Start time & Duration & Freq. & Bursts \\% & Other Coverage & Other Detections \\
-(yyyy-mm-dd) & (hh:mm:ss) & (min) & (GHz) & \\ \hline
-2015-11-25 & 3:25:29 & 60 & 1.4 & 0 \\
-2015-12-01 & 5:31:31 & 60 & 1.4 & 0 \\
-2015-12-03 & 2:53:57 & 60 & 1.4 & 0 \\
-2015-12-05 & 4:45:44 & 60 & 1.4 & 0 \\
-2015-12-07 & 4:37:50 & 60 & 1.4 & 0 \\
-2015-12-09 & 9:29:25 & 60 & 1.4 & 0 \\
-2015-12-11 & 9:22:27 & 60 & 1.4 & 0 \\
-2015-12-13 & 9:13:7 & 60 & 1.4 & 0 \\
-2015-12-15 & 9:6:16 & 60 & 1.4 & 0 \\
-2015-12-17 & 8:57:51 & 60 & 1.4 & 0 \\
-2016-04-25 & 15:39:33 & 42 & 3 & 0  \\
-2016-04-26 & 21:49:35 & 15 & 3 & 0  \\
-2016-04-30 & 19:14:46 & 60 & 3 & 0  \\
-2016-05-01 & 18:8:21 & 60 & 3 & 0  \\
-2016-05-03 & 22:53:26 & 60 & 3 & 0  \\
-2016-05-04 & 22:50:30 & 60 & 3 & 0  \\
-2016-05-06 & 18:25:12 & 60 & 3 & 0  \\
-2016-05-07 & 19:34:13 & 60 & 3 & 0  \\
-2016-05-08 & 19:30:20 & 60 & 3 & 0  \\
-2016-05-13 & 17:12:48 & 135 & 3 & 0  \\
-2016-05-14 & 17:14:11 & 135 & 3 & 0  \\
-2016-05-15 & 17:15:26 & 135 & 3 & 0  \\
-2016-05-16 & 16:59:52 & 135 & 3 & 0  \\
-2016-05-20 & 16:45:46 & 135 & 3 & 0  \\
-2016-05-21 & 16:44:6 & 135 & 3 & 0  \\
-2016-05-22 & 16:43:53 & 135 & 3 & 0  \\
-2016-05-23 & 16:44:11 & 135 & 3 & 0  \\
-2016-05-27 & 16:29:34 & 135 & 3 & 0  \\
-2016-08-23 & 17:26:28 & 54 & 3 & 1  \\
-2016-09-02 & 15:52:17 & 54 & 3 & 2  \\
-2016-09-07 & 10:14:50 & 120 & 3 & 1  \\
-2016-09-08 & 10:14:40 & 120 & 3 & 0  \\
-2016-09-10 & 9:59:36 & 120 & 3 & 0  \\
-2016-09-11 & 9:59:49 & 120 & 3 & 0  \\
-2016-09-12 & 9:15:19 & 120 & 3 & 1\tablenotemark{a} \\ 
-2016-09-13 & 9:23:59 & 120 & 3 & 0  \\
-2016-09-14 & 9:20:23 & 120 & 3 & 1\tablenotemark{a,b} \\
-2016-09-15 & 9:16:29 & 120 & 3 & 1  \\
-2016-09-16 & 9:11:23 & 120 & 3 & 0  \\
-2016-09-17 & 8:59:20 & 120 & 3 & 1\tablenotemark{a,b,*,c} \\ 
-2016-09-18 & 8:59:27 & 120 & 3 & 1\tablenotemark{a,b,c} \\
-2016-09-19 & 8:44:32 & 120 & 3 & 0  \\
-2016-09-20 & 8:44:33 & 120 & 3 & 0  \\
-2016-09-20 & 17:19:3 & 120 & 6 & 0  \\
-2016-09-21 & 9:13:57 & 120 & 6 & 0  \\
-2016-09-22 & 9:12:24 & 120 & 6 & 0  \\
+MJD & Date/time & Duration & Freq. & Bursts \\
+ & (ymd/hms) & (min) & (GHz) & \\ \hline
+57351 & 2015-11-25/3:25:29 & 60 & 1.4 & 0 \\
+57357 & 2015-12-01/5:31:31 & 60 & 1.4 & 0 \\
+57359 & 2015-12-03/2:53:57 & 60 & 1.4 & 0 \\
+57361 & 2015-12-05/4:45:44 & 60 & 1.4 & 0 \\
+57363 & 2015-12-07/4:37:50 & 60 & 1.4 & 0 \\
+57365 & 2015-12-09/9:29:25 & 60 & 1.4 & 0 \\
+57367 & 2015-12-11/9:22:27 & 60 & 1.4 & 0 \\
+57369 & 2015-12-13/9:13:7 & 60 & 1.4 & 0 \\
+57371 & 2015-12-15/9:6:16 & 60 & 1.4 & 0 \\
+57373 & 2015-12-17/8:57:51 & 60 & 1.4 & 0 \\
+57503 & 2016-04-25/15:39:33 & 42 & 3 & 0  \\
+57504 & 2016-04-26/21:49:35 & 15 & 3 & 0  \\
+% ** symbols in the plot here. missing something from archive?
+57508 & 2016-04-30/19:14:46 & 60 & 3 & 0  \\
+57509 & 2016-05-01/18:8:21 & 60 & 3 & 0  \\
+57511 & 2016-05-03/22:53:26 & 60 & 3 & 0  \\
+57512 & 2016-05-04/22:50:30 & 60 & 3 & 0  \\
+57514 & 2016-05-06/18:25:12 & 60 & 3 & 0  \\
+57515 & 2016-05-07/19:34:13 & 60 & 3 & 0  \\
+57516 & 2016-05-08/19:30:20 & 60 & 3 & 0  \\
+57521 & 2016-05-13/17:12:48 & 135 & 3 & 0  \\
+57522 & 2016-05-14/17:14:11 & 135 & 3 & 0  \\
+57523 & 2016-05-15/17:15:26 & 135 & 3 & 0  \\
+57524 & 2016-05-16/16:59:52 & 135 & 3 & 0  \\
+57528 & 2016-05-20/16:45:46 & 135 & 3 & 0  \\
+57529 & 2016-05-21/16:44:6 & 135 & 3 & 0  \\
+57530 & 2016-05-22/16:43:53 & 135 & 3 & 0  \\
+57531 & 2016-05-23/16:44:11 & 135 & 3 & 0  \\
+57535 & 2016-05-27/16:29:34 & 135 & 3 & 0  \\
+57523 & 2016-08-23/17:26:28 & 54 & 3 & 1  \\
+57533 & 2016-09-02/15:52:17 & 54 & 3 & 2  \\
+57538 & 2016-09-07/10:14:50 & 120 & 3 & 1  \\
+57539 & 2016-09-08/10:14:40 & 120 & 3 & 0  \\
+57541 & 2016-09-10/9:59:36 & 120 & 3 & 0  \\
+57542 & 2016-09-11/9:59:49 & 120 & 3 & 0  \\
+57543 & 2016-09-12/9:15:19 & 120 & 3 & 1\tablenotemark{d} \\ 
+57544 & 2016-09-13/9:23:59 & 120 & 3 & 0  \\
+57545 & 2016-09-14/9:20:23 & 120 & 3 & 1\tablenotemark{a,d} \\
+57546 & 2016-09-15/9:16:29 & 120 & 3 & 1  \\
+57547 & 2016-09-16/9:11:23 & 120 & 3 & 0  \\
+57548 & 2016-09-17/8:59:20 & 120 & 3 & 1\tablenotemark{a,*,b,d} \\ 
+57549 & 2016-09-18/8:59:27 & 120 & 3 & 1\tablenotemark{a,b,d} \\
+57550 & 2016-09-19/8:44:32 & 120 & 3 & 0  \\
+57551 & 2016-09-20/8:44:33 & 120 & 3 & 0  \\
+57551 & 2016-09-20/17:19:3 & 120 & 6 & 0  \\
+57552 & 2016-09-21/9:13:57 & 120 & 6 & 0  \\
+57553 & 2016-09-22/9:12:24 & 120 & 6 & 0  \\ \hline
 \enddata
 \tablecomments{Times are in UT. Frequency is the approximate center of the bandwidth.}
-\tablenotetext{a}{AMI-LA coverage at 15~GHz.}
-\tablenotetext{b}{Arecibo coverage at 1.4~GHz.}
+\tablenotetext{a}{Arecibo coverage at 1.4~GHz.}
 \tablenotetext{*}{Arecibo detection at 1.4~GHz.}
-\tablenotetext{c}{Effelsberg coverage at 4.5~GHz.}
+\tablenotetext{b}{Effelsberg coverage at 4.5~GHz.}
+\tablenotetext{c}{LWA coverage at **xx** MHz.}
+\tablenotetext{d}{AMI-LA coverage at 15~GHz.}
 %\end{tabular}
@@
 
-% ** uncertainties in dm delay? **
-
 Figure \ref{fig:sgram} shows a dynamic spectrum for this burst with both VLA and Arecibo data.
@@
 We assumed a DM of 560.5 pc cm$^{-3}$ (Hessels et al., in prep) to calculate a dispersion delay of 189 and 734~ms from infinite frequency to the top of the VLA and Arecibo bands, respectively.
+An error in the DM of 1 pc cm$^{-3}$\ corresponds to a delay time correction error of 0.3 and 1.4~ms for the VLA and Arecibo bands, respectively.
 We used PRESTO \citep{2001PhDT.......123R} to calculate a relative barycentric time correction of 3.8~ms between the VLA and Arecibo at the time of observation.
@@
 
-% ** errorbars on flux densities?
-
 Figure \ref{fig:multi} shows coarse spectra built from integrated flux densities measured (or limited) for three bursts with multi-telescope observing coverage.
-The burst on MJD 57648 was detected with VLA and Arecibo with significances of 25$\sigma$\ and 39$\sigma$, which corresponds to peak flux densities in 5~ms of 111 mJy and 14 mJy at 3 and 1.4~GHz, respectively.
-Here we assume a typical pulse width of 2~ms to measure VLA and Arecibo integrated flux densities of 278 and 64 mJy at 3 and 1.4~GHz, respectively.
+The burst on MJD 57648 was detected with VLA and Arecibo with significances of 25$\sigma$\ and 39$\sigma$, which corresponds to peak flux densities in 5~ms of $111\pm5$\ mJy and $14\pm0.4$\ mJy at 3 and 1.4~GHz, respectively.
+The VLA observations underresolve the pulses in time, so to compare these values, we assume a typical pulse width of 2~ms.
+Under this assumption, the VLA and Arecibo integrated flux densities are $278\pm13$\ and $64\pm2$\ mJy at 3 and 1.4~GHz, respectively.
 Assuming a power law flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha=1.9$.
@@
 The strictest limits on $\alpha_{1.4/3}$\ and $\alpha_{3/4.5}$\ are both derived from the burst on MJD 57649, which shows that a power law model is inappropriate even for a single burst.
-% could note that these limits are understated by VLA integrated flux underestimate
 
@@
 Upper limits assume a pulse width of 2~ms and a $5\sigma$ detection threshold.
-Overlapping points are offset by tens of MHz in frequency for visualization.
+Errors in flux density are comparable to the symbol size and are not shown.
+Overlapping points are offset by tens of MHz in frequency for clarity.
+ % ** useful to add LWA?
  \label{fig:multi}}
@@
 \begin{table*}
-\caption{Properties of \frb\ Bursts at 3~GHz}
+\caption{Properties of \frb\ Bursts Seen by VLA at 3~GHz}
 \centering
@@
 The initial VLA detections were made with a matched-filter approach that allowed inter-DM sensitivity losses up to roughly 10\% \citep[$\Delta \rm{DM}=10\ \rm{pc}\ \rm{cm}^{-3}$][]{2003ApJ...596.1142C}.
-%In optimizing detection significance over a fine DM grid, we find optimal DM values range from 552 to 572 pc cm$^{-3}$.
-However, the uncertainty in the peak DM measurement is defined by the signal-to-noise of the burst and how this changes with DM.
 The MCMC modeling is more sophisticated in that it considers a wider range of parameters and models both data and observing effects (frequency-time pixel boundaries) simultaneously.
@@
 The variation in DM observed by the VLA at 3~GHz is similar to that reported for Arecibo observations of \frb\ in \citet{2016arXiv160308880S}.
-%As noted before, this is consistent with the idea that the DM measured at low temporal resolution (e.g., by the VLA or by single-dish observatories without coherent dedispersion) is determined by extrinsic (an electron column) dispersion and some spectrotemporal structure that changes between bursts.
+% This is consistent with the idea that the DM measured at low temporal resolution (e.g., by the VLA or by single-dish observatories without coherent dedispersion) is determined by extrinsic (an electron column) dispersion and some spectrotemporal structure that changes between bursts.
 

### 2017-04-27 repeater-vladata.tex
waiting on jim and kevin additions

@@
 The dynamic spectra were modeled prior to dispersion correction.
-The spectral structure was modeled as a broad Gaussian envelope (parameters of amplitude, center, width), while the time evolution was modeled by a $\nu^2$\ dispersion law (parameters of starting integration, DM).
+The spectral structure was modeled as a broad Gaussian envelope (parameters of amplitude, center, $\sigma$), while the time evolution was modeled by a $\nu^2$\ dispersion law (parameters of starting integration, DM).
 Finally, the pulses were assumed to have an intrinsically square temporal width (parameter W).
@@
 The parameters for the best model of the dynamic spectrum are given in Table \ref{tab:spec} and the resulting Gaussian model overlaid on Figure \ref{fig:spec}.
-The typical burst spectrum has a FWHM of 500~MHz.
-All but two of the best-fit Gaussians are centered inside the 3~GHz band and some appear contained by the 1~GHz wide band.
-This is consistent with previous detections of \frb\ by Arecibo, which showed quasi-broadband structure \citep{2016arXiv160308880S} and large variation in the implied spectral index \citep{2014ApJ...790..101S}.
+Two of the best-fit Gaussians are centered at the boundary of the 3~GHz band, so parameter estimates are actually limits.
+The other seven best-fit models appear contained by the 1~GHz wide band ($>90$\% of the modeled flux is within the 3~GHz band).
+In all cases, the typical burst spectrum has a FWHM of approximately 500~MHz.
+This confirms previous reports based on Arecibo and GBT data \citep{2016arXiv160308880S} with the wider (1~GHz) VLA bandwidth and extends this phenomenon to 3~GHz.
 
-% ** quantify how much of model shape is actually inside the band **
-
-% ** confusion as to whether inter-channel modulation is signal or noise ** jim also to do noise analysis **
-% ** could quantify deviations from Gaussian model relative to noise. An SNR relative to envelope.
-
-% ** spectra plot modifications: **
-% y-axis scale not shown! 
-% add mjd to each plot
-% Need to make sure impression differs of noise and inter-channel modulation
+% ** signal or noise analysis offered by jim **
 
@@
 \caption{Spectra and best-fit model for nine bursts seen by the VLA from 2.5 to 3.5~GHz in the peak, dedispersed 5~ms integration.
-Starting at the top left (moving right and then down), they correspond to bursts on MJDs 57623, 57633.68, 57633.70, 57638, 57643, 57645, 57646, 57648, and 57649.
 The solid line is a best-fit Gaussian model found through modeling.
+The typical flux density error per channel is 70~mJy, which is shown at the top right of each panel next to the MJD label.
 \label{fig:spec}}
@@
 
-% ** fix plot to show "W" instead of "dint"
-
 \begin{figure*}[htb]
@@
 The equivalent plot for the other bursts show normally-distributed samples, but this burst shows significant structure in the samples.
-The parameters ``Amp'', ``Center'', and ``$\sigma_{ch}$'' refer to the Gaussian spectral shape, while ``DM'', ``int'', and ``W'' refer to the temporal shape.
+The parameters ``amplitude'', ``center'', and ``$\sigma_{ch}$'' refer to the Gaussian spectral shape, while ``DM'', ``integration'', and ``W$_{int}$'' refer to the temporal shape.
 The parameters are given in units of channels (4 MHz) and integrations (5 ms).
@@
 
-Figure \ref{fig:ed} shows the \frb\ burst energy cumulative distribution as seen by the VLA and calculated from prior observations by Arecibo and the GBT \citep{2016Natur.531..202S,2016arXiv160308880S}.
+Figure \ref{fig:ed} shows the \frb\ burst energy cumulative distribution as seen by the VLA and calculated from prior observations by Arecibo and the Green Bank Telescope \citep{2016Natur.531..202S,2016arXiv160308880S}.
 The latter two energy distributions are scaled from the fluence by assuming that all burst energy is included by the observation.
@@
 Radio waves can be modified in a variety of ways (e.g., scintillation, scattering) and the duration of the emission in the source frame is not known \citep{2016arXiv160505890C}.
-\citet{CORDES} describe a model where plasma lensing near the source of an FRB can magnify radio emission by orders of magnitude.
+\citet{2017arXiv170306580C} describe a model where plasma lensing near the source of an FRB can magnify radio emission by orders of magnitude.
 That model argues that the simultaneous appearance of a burst from 1.2 to 3.5~GHz requires a lens with the focal frequency be $\gtrsim 3.5$~GHz.
@@
 
-% ** discuss beaming **
-
 Our refined analysis shows that \frb\ has even higher isotropic energies than previously reported for \frb, reaching energies $E_{\rm{max}}\approx10^{40}$\ erg.
-\frb\ has isotropic energies orders of magnitude higher than the strongest Crab giant pulses ($\sim10^{35}$~erg) and comparable brightness temperatures \citep[$T_{b,\rm{Crab}}\sim10^{41}$~K versus $T_{b, \rm{FRB 121102}}\sim10^{38}$~K;][]{2003Natur.422..141H,2014PhRvD..89j3009K}.
-%While this emission is coherent and strongly beamed \citep{2016Natur.531..202S, WEIRD}, the energy scale is still larger than any known Galactic radio transient and requires either a new process or dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}.
+While this emission is coherent and beamed, the apparent energy is larger than Galactic analogues such as the giant pulses from the Crab pulsar \citep[$\sim10^{35}$~erg, $T_{b,\rm{Crab}}\sim10^{41}$~K;][]{2003Natur.422..141H,2014PhRvD..89j3009K}.
+Radio bursts from \frb\ require either dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C} or strong amplification by propagation effects \citep{2017arXiv170306580C}.
 
@@
 
-%While the \frb\ burst energy distribution is consistent with the overall FRB population, this simulation ignores many observational biases (scattering, observing coverage) and the effects of galaxy evolution, which is likely significant over the range of redshifts to which \frb\ is detectable \citep[e.g.,][]{2010ApJ...709..644I}.
-The burst energies are estimated from observations from 2.5 to 3.5~GHz, which may be a biased selection of all bursts or may not include all burst emission.
-If the simulation is revealing a connection between \frb\ and the broader FRB population, it does not explain the physical mechanism that drives it.
-The burst energy distribution of the population could be dominated by intrinsic or extrinsic effects \citep{2015MNRAS.451.3278M,2016Natur.531..202S,CORDES}.
-More FRB detections will improve the quality of this inference as sample variance drops, while more burst detetions from \frb\ will improve the measurement of the intrinsic energy distribution.
-
 \subsection{Repetition}
@@
 The chance of detecting a burst from \frb\ with the VLA changes substantially on day--month timescales.
-A major outstanding question is whether this time-variable rate is driven by an intrinsic process \citep{2016ApJ...826..226K} or extrinsic (propagation) effects in the host galaxy or intergalactic medium \citep{CORDES}.
+A major outstanding question is whether this time-variable rate is driven by an intrinsic process \citep{2016ApJ...826..226K} or extrinsic (propagation) effects in the host galaxy or intergalactic medium \citep{2017arXiv170306580C}.
 However, the temporal distribution of VLA detections alone shows that the \frb\ burst rate is significantly correlated on short timescales.
@@
 The narrow burst spectral structure seen for \frb\ also suggests that the FRB rate is understated by a factor of a few by ignoring bursts that fall outside the observing band.
-Finally, we note that this estimate assumes that Galactic latitude and propagation effects do not significantly affect the detectability of FRBs, although scintillation and scattering likely play significant roles \citep{2015MNRAS.451.3278M, CORDES}.
+Finally, we note that this estimate assumes that Galactic latitude and propagation effects do not significantly affect the detectability of FRBs, although scintillation and scattering likely play significant roles \citep{2015MNRAS.451.3278M, 2017arXiv170306580C}.
 

### 2017-05-02 repeater-vladata.tex
working in lwa data. fixed bug in dates of table.

@@
 \affiliation{National Radio Astronomy Observatory, Socorro, NM 87801, USA}
+
+\author{Jayce Dowell}
+\affiliation{University of New Mexico, Albuquerque, NM, USA}
 
@@
 \affiliation{National Radio Astronomy Observatory, Socorro, NM 87801, USA}
+\affiliation{University of New Mexico, Albuquerque, NM, USA}
 
@@
 
-This paper presents an analysis of the spectral properties of VLA bursts implied by simultaneous observing at Arecibo, Effelsberg, the Long-Wavelength Array (LWA), and the Arcminute Microkelvin Imager Large Array (AMI-LA).
+This paper presents an analysis of the spectral properties of VLA bursts implied by simultaneous observing at Arecibo, Effelsberg, the Long-Wavelength Array \citep[LWA; ][]{2013ITAP...61.2540E}, and the Arcminute Microkelvin Imager Large Array \citep[AMI-LA; ][]{2008MNRAS.391.1545Z}.
 This includes the first simultaneous detection of an FRB at two observatories, between the VLA and Arecibo.
@@
 Circled observations with no line indicate observations on the same day that did not overlap.
-Symbols show days with observations with letters L, S, C, U referring to radio frequencies of 1.4, 3, 4.5, and 15~GHz, respectively.
-% ** add LWA as "V" for VHF?
+Symbols show days with observations with letters V, L, S, C, U referring to radio frequencies of 70~MHz, 1.4, 3, 4.5, and 15~GHz, respectively.
 \label{fig:sched}}
@@
 57373 & 2015-12-17/8:57:51 & 60 & 1.4 & 0 \\
-57503 & 2016-04-25/15:39:33 & 42 & 3 & 0  \\
-57504 & 2016-04-26/21:49:35 & 15 & 3 & 0  \\
-% ** symbols in the plot here. missing something from archive?
+57503 & 2016-04-25/23:21:39 & 240 & 3 & 0  \\
+57504 & 2016-04-26/23:14:31 & 120 & 3 & 0  \\
+57505 & 2016-04-27/23:26:09 & 120 & 3 & 0  \\
+57506 & 2016-04-28/22:41:31 & 120 & 3 & 0  \\
+57507 & 2016-04-29/22:37:34 & 120 & 3 & 0  \\
 57508 & 2016-04-30/19:14:46 & 60 & 3 & 0  \\
-57509 & 2016-05-01/18:8:21 & 60 & 3 & 0  \\
+57510 & 2016-05-02/23:14:18 & 60 & 3 & 0 \\
 57511 & 2016-05-03/22:53:26 & 60 & 3 & 0  \\
-57512 & 2016-05-04/22:50:30 & 60 & 3 & 0  \\
 57514 & 2016-05-06/18:25:12 & 60 & 3 & 0  \\
@@
 57535 & 2016-05-27/16:29:34 & 135 & 3 & 0  \\
-57523 & 2016-08-23/17:26:28 & 54 & 3 & 1  \\
-57533 & 2016-09-02/15:52:17 & 54 & 3 & 2  \\
-57538 & 2016-09-07/10:14:50 & 120 & 3 & 1  \\
-57539 & 2016-09-08/10:14:40 & 120 & 3 & 0  \\
-57541 & 2016-09-10/9:59:36 & 120 & 3 & 0  \\
-57542 & 2016-09-11/9:59:49 & 120 & 3 & 0  \\
-57543 & 2016-09-12/9:15:19 & 120 & 3 & 1\tablenotemark{d} \\ 
-57544 & 2016-09-13/9:23:59 & 120 & 3 & 0  \\
-57545 & 2016-09-14/9:20:23 & 120 & 3 & 1\tablenotemark{a,d} \\
-57546 & 2016-09-15/9:16:29 & 120 & 3 & 1  \\
-57547 & 2016-09-16/9:11:23 & 120 & 3 & 0  \\
-57548 & 2016-09-17/8:59:20 & 120 & 3 & 1\tablenotemark{a,*,b,d} \\ 
-57549 & 2016-09-18/8:59:27 & 120 & 3 & 1\tablenotemark{a,b,d} \\
-57550 & 2016-09-19/8:44:32 & 120 & 3 & 0  \\
-57551 & 2016-09-20/8:44:33 & 120 & 3 & 0  \\
-57551 & 2016-09-20/17:19:3 & 120 & 6 & 0  \\
-57552 & 2016-09-21/9:13:57 & 120 & 6 & 0  \\
-57553 & 2016-09-22/9:12:24 & 120 & 6 & 0  \\ \hline
+57623 & 2016-08-23/17:26:28 & 54 & 3 & 1  \\
+57633 & 2016-09-02/15:52:17 & 54 & 3 & 2  \\
+57638 & 2016-09-07/10:14:50 & 120 & 3 & 1  \\
+57639 & 2016-09-08/10:14:40 & 120 & 3 & 0  \\
+57641 & 2016-09-10/9:59:36 & 120 & 3 & 0  \\
+57642 & 2016-09-11/9:59:49 & 120 & 3 & 0  \\
+57643 & 2016-09-12/9:15:19 & 120 & 3 & 1\tablenotemark{d} \\ 
+57644 & 2016-09-13/9:23:59 & 120 & 3 & 0  \\
+57645 & 2016-09-14/9:20:23 & 120 & 3 & 1\tablenotemark{a,d} \\
+57646 & 2016-09-15/9:16:29 & 120 & 3 & 1  \\
+57647 & 2016-09-16/9:11:23 & 120 & 3 & 0  \\
+57648 & 2016-09-17/8:59:20 & 120 & 3 & 1\tablenotemark{a,*,b,c,d} \\ 
+57649 & 2016-09-18/8:59:27 & 120 & 3 & 1\tablenotemark{a,b,c,d} \\
+57650 & 2016-09-19/8:44:32 & 120 & 3 & 0  \\
+57651 & 2016-09-20/8:44:33 & 120 & 3 & 0  \\
+57651 & 2016-09-20/17:19:3 & 120 & 6 & 0  \\
+57652 & 2016-09-21/9:13:57 & 120 & 6 & 0  \\
+57653 & 2016-09-22/9:12:24 & 120 & 6 & 0  \\ \hline
 \enddata
@@
 \tablenotetext{b}{Effelsberg coverage at 4.5~GHz.}
-\tablenotetext{c}{LWA coverage at **xx** MHz.}
+\tablenotetext{c}{LWA coverage near 70~MHz.}
 \tablenotetext{d}{AMI-LA coverage at 15~GHz.}
@@
 
+\subsection{LWA}
+
+Beginning in April 2016, VLA observations of \frb were simultaneously observed with the first station of the LWA\footnote{This LWA station is located at the VLA site and is the first to be deployed.
+It is sometimes referred to as ``LWA1'', but we use ``LWA'' here.} when possible.
+The LWA observations consisted of single phased-array beam centered on the location of \frb with two 4096-channel spectral windows spanning frequencies from 52.2--71.8~MHz and 68.2--87.8~MHz.
+The observations were taken in LWA's spectrometer mode with a channel size of 4.8~kHz and a sample time of 160~ms.
+
+Two of the VLA detected pulses, on 2016 September 17 and 18 had simultaneous coverage with LWA.
+The SEFD of the LWA is dependent on zenith angle, for these two bursts the estimated SEFD is 9.5 kJy and 8.7 kJy, respectively.
+The data were de-dispersed into time series with DMs ranging from 500 to 600 pc cm$^{-3}$\ using a step size of 1.0 pc cm$^{-3}$.
+All DMs were searched using PRESTO \citep{2001PhDT.......123R} with a boxcar matched-filtering width from the native time resolution up to 48 seconds.
+We also visually inspected the dedispersed time series for the DM range 557 to 560 pc cm$^{-3}$.
+
+No dispersed pulses were found with significance greater than $10\sigma$\, equivalent to a flux density limit of $\sim60$\ Jy for a width of 160~ms.
+The time resolution was set to be roughly equal to the dispersion smearing in a single channel for DM$\approx560$\ pc cm$^{-3}$...
+
 \subsection{AMI-LA}
 
-We observed \frb\ with the Arcminute MicroKelvin Imager Large Array (AMI-LA; Zwart et al.
-2008) for 3 hours each on four epochs starting at MJDs 57638, 57643, 57645, 57646, 57648, and 57649.
+We observed \frb\ with AMI-LA for 3 hours each on four epochs starting at MJDs 57638, 57643, 57645, 57646, 57648, and 57649.
 Observations were made with the new digital correlator having 4096 channels across a 5~GHz bandwidth between 13--18~GHz with a 1~s integration time.
@@
 An error in the DM of 1 pc cm$^{-3}$\ corresponds to a delay time correction error of 0.3 and 1.4~ms for the VLA and Arecibo bands, respectively.
-We used PRESTO \citep{2001PhDT.......123R} to calculate a relative barycentric time correction of 3.8~ms between the VLA and Arecibo at the time of observation.
+We used PRESTO to calculate a relative barycentric time correction of 3.8~ms between the VLA and Arecibo at the time of observation.
 

### 2017-05-02 timeline.py

@@ -22,13 +22,9 @@ for i in range(len(obs)):
 obsdate = list(map(lambda od: datetime.datetime.strptime(od, "%Y-%m-%d"), ymds))
 
 # Define an offset and symbol type for each telescope
-telescopes = ['Arecibo', 'VLA', 'Effelsberg', 'AMI-LA']
-offs = [3, 2, 1, 0]
+telescopes = ['LWA', 'Arecibo', 'VLA', 'Effelsberg', 'AMI-LA']
+offs = [2, 4, 3, 1, 0]
 offset = dict(zip(telescopes, offs))
-psyms = ['+', 'v', 'x', '.']
-psym = dict(zip(telescopes, psyms))
-pcols = ['g','r','b','y']
-pcol = dict(zip(telescopes, pcols))
 
 if obsdate[0].year == 2015:
     telescopes = telescopes[:-1]
@@ -61,16 +57,16 @@ def d2n(yyyy, mm, dd):
 # Paint on all dots, then fiddle
 
 def labeltelleft(ax, num):
-	for teln in telescopes:
-		yval = offset[teln]
-		xval = xl[num] - 0.5
-   		ax.text(xval, yval, teln, horizontalalignment='right', verticalalignment='center')
+    for teln in telescopes:
+        yval = offset[teln]
+        xval = xl[num] - 0.5
+        ax.text(xval, yval, teln, horizontalalignment='right', verticalalignment='center')
 
 def labeltelright(ax, num):
-	for teln in telescopes:
-		yval = offset[teln]
-		xval = xr[num] + 0.5
-   		ax.text(xval, yval, teln, horizontalalignment='left', verticalalignment='center')
+    for teln in telescopes:
+        yval = offset[teln]
+        xval = xr[num] + 0.5
+        ax.text(xval, yval, teln, horizontalalignment='left', verticalalignment='center')
 
 if obsdate[0].year == 2016:
     xl = [d2n(2016, 8, 22)]
@@ -101,21 +97,21 @@ for ax in axs:
     ax.fmt_xdata = DateFormatter('%Y-%m-%d %H:%M:%S')
 
     if obsdate[0].year == 2016:
-        ax.set_ylim( (-0.4, 3.4) )
+        ax.set_ylim( (-0.4, 4.4) )
         ax.set_xlim( (xl[0], xr[0]) )
     else:
-        ax.set_ylim( (0.6, 3.4) )
[…]

### 2017-05-03 repeater-vladata.tex
moved to pdf figures for vector graphics quality

@@
 
-\author{Jayce Dowell}
-\affiliation{University of New Mexico, Albuquerque, NM, USA}
+\author{J.~Dowell}
+\affiliation{Department of Physics and Astronomy, University of New Mexico, Albuquerque, NM 87131, USA}
 
@@
 \author{J.~Hickish}
-\affiliation{Dept of Astronomy and Radio Astronomy Lab, University of California, Berkeley, CA 94720, USA}
+\affiliation{Department of Astronomy and Radio Astronomy Lab, University of California, Berkeley, CA 94720, USA}
 \affiliation{Astrophysics Group, Cavendish Laboratory, 19 J. J. Thomson Avenue, Cambridge CB3 0HE, UK}
@@
 \affiliation{National Radio Astronomy Observatory, Socorro, NM 87801, USA}
-\affiliation{University of New Mexico, Albuquerque, NM, USA}
+\affiliation{Department of Physics and Astronomy, University of New Mexico, Albuquerque, NM 87131, USA}
 
@@
 \begin{center}
-\includegraphics[width=2\columnwidth]{timeline0}
+\includegraphics[width=2\columnwidth]{timeline0.pdf}
 
-\includegraphics[width=2\columnwidth]{timeline}
+\includegraphics[width=2\columnwidth]{timeline.pdf}
 \caption{The top and bottom panels summarize the observations and detections of \frb\ in the 2015 and 2016 campaigns.
@@
 The observations were taken in LWA's spectrometer mode with a channel size of 4.8~kHz and a sample time of 160~ms.
+The integration time was set to be equal to the dispersion smearing across a single channel at 50~MHz for DM$\approx560$\ pc cm$^{-3}$.
 
-Two of the VLA detected pulses, on 2016 September 17 and 18 had simultaneous coverage with LWA.
-The SEFD of the LWA is dependent on zenith angle, for these two bursts the estimated SEFD is 9.5 kJy and 8.7 kJy, respectively.
+Two of the VLA detected pulses, on MJD 57648 and 57649, had simultaneous coverage with LWA.
+We use the modeled LWA antenna sensitivity as a function of zenith angle to estimate an system equivalent flux density of 9.5 kJy and 8.7 kJy for the two bursts, respectively.
 The data were de-dispersed into time series with DMs ranging from 500 to 600 pc cm$^{-3}$\ using a step size of 1.0 pc cm$^{-3}$.
-All DMs were searched using PRESTO \citep{2001PhDT.......123R} with a boxcar matched-filtering width from the native time resolution up to 48 seconds.
+Each spectral window was searched using PRESTO \citep{2001PhDT.......123R} with a boxcar matched-filtering width from the native time resolution up to 48 seconds.
 We also visually inspected the dedispersed time series for the DM range 557 to 560 pc cm$^{-3}$.
@@
 No dispersed pulses were found with significance greater than $10\sigma$\, equivalent to a flux density limit of $\sim60$\ Jy for a width of 160~ms.
-The time resolution was set to be roughly equal to the dispersion smearing in a single channel for DM$\approx560$\ pc cm$^{-3}$...
+The system equivalent flux density does not change much between the two windows.
+The effective sensitivity to a typical 2~ms pulse width is 4.8~kJy.
 
@@
 Concatenating and imaging the 12 hours of calibrated data with the CASA tasks {\it concat} and {\it clean} also does not yield any significant detection at the FRB location.
-Although the statistical $3\sigma$\ upper limit is 60 $\mu$Jy, extended mJy-level sources in the field cause sidelobe confusion (the AMI-LA angular resolution is $\sim$30\arcsec), and the actual upper limit is larger.
-We introduced artificial point sources at the FRB location using the CASA {\it sm} tool, and found that these sources can be recovered at $3\sigma$\ as long as their peak flux densities are more than $\sim100\mu$Jy.
-Hence, we place an upper limit of $100\pm10 \mu$Jy on any quiescent or possible radio flaring on $\sim$days timescales from the FRB.
+Although the statistical $3\sigma$\ upper limit is 60~$\mu$Jy, extended mJy-level sources in the field cause sidelobe confusion (the AMI-LA angular resolution is $\sim$30\arcsec), and the actual upper limit is larger.
+We introduced artificial point sources at the FRB location using the CASA {\it sm} tool, and found that these sources can be recovered at $3\sigma$\ as long as their peak flux densities are more than $\sim100~\mu$Jy.
+Hence, we place an upper limit of $100\pm10~\mu$Jy on any quiescent or possible radio flaring on $\sim$days timescales from the FRB.
 This limit is similar to the flux density measured by the VLA at 12~GHz for the persistent source \citep{LOC}.
@@
 \begin{center}
- \includegraphics[width=\columnwidth]{aovla_spec.png}
+ \includegraphics[trim=250 400 250 80, clip, width=\columnwidth]{aovla_spec.pdf}
  \caption{Composite dynamic specrum for the burst from \frb\ on MJD 57648 with data from the VLA and Arecibo observatories.
@@
 \begin{center}
- \includegraphics[width=\columnwidth]{multispec.png}
- \caption{Broadband spectral measurements and limits for three bursts of \frb\ with simultaneous multi-telescope observing coverage (Arecibo at 1.4~GHz, VLA at 3~GHz, and Effelsberg at 4.5~GHz).
-Measurements are shown with dots and upper limits with triangles.
+ \includegraphics[width=\columnwidth]{multispec.pdf}
+ \caption{Broadband spectral measurements and limits for three bursts of \frb\ with simultaneous multi-telescope observing coverage.
 Upper limits assume a pulse width of 2~ms and a $5\sigma$ detection threshold.
+Measurements (dots) and limits (triangles) are shown for Arecibo, VLA, and Effelsberg at 1.4, 3, and 4.5~GHz, respectively; limits from LWA and AMI-LA are not visible on this scale.
 Errors in flux density are comparable to the symbol size and are not shown.
 Overlapping points are offset by tens of MHz in frequency for clarity.
- % ** useful to add LWA?
  \label{fig:multi}}
@@
 \caption{Properties of \frb\ Bursts Seen by VLA at 3~GHz}
-\centering
+%\centering
 \begin{tabular}{cc|rrr|ccrrrr}
@@
 \tablecomments{$S_{\rm{V}}$ is the measured circular polarization of the burst, which dominated by systematic effects. All error ranges represent 68\% confidence intervals.}
-\tablenotetext{a}{Simultaneously observed by either Arecibo, Effelsberg, or AMI-LA.}
+\tablenotetext{a}{Simultaneously observed by either Arecibo, Effelsberg, LWA, or AMI-LA.}
 \tablenotetext{b}{Detected simultaneously with Arecibo.}
@@
 
-We use a log likelihood function $\ln \mathcal{L}=(-1/2)\ \sum_i (S_i - S_{i, \rm{model}})^2/\sigma_s^2$, where $S_i$\ refers to the measured and modeled flux density in a single pixel of the dynamic spectrum and $\sigma_s\approx 70\ \mu$Jy is the measured off-burst noise per 5~ms integration and 4~MHz channel.
+We use a log likelihood function $\ln \mathcal{L}=(-1/2)\ \sum_i (S_i - S_{i, \rm{model}})^2/\sigma_s^2$, where $S_i$\ refers to the measured and modeled flux density in a single pixel of the dynamic spectrum and $\sigma_s\approx 70~\mu$Jy is the measured off-burst noise per 5~ms integration and 4~MHz channel.
 A flat prior was used over all ranges with valid data with the requirement that the integrated signal must have a detection significance higher than 8$\sigma$.
@@
  \begin{minipage}{2\columnwidth}
-  \includegraphics[width=0.5\columnwidth]{spec_57623.png}
-  \includegraphics[width=0.5\columnwidth]{spec_57633_scan7.png}
+  \includegraphics[width=0.5\columnwidth]{spec_57623.pdf}
+  \includegraphics[width=0.5\columnwidth]{spec_57633.6.pdf}
  \end{minipage}
@@
  \begin{minipage}{2\columnwidth}
-  \includegraphics[width=0.5\columnwidth]{spec_57633_scan13.png}
-  \includegraphics[width=0.5\columnwidth]{spec_57638.png}
+  \includegraphics[width=0.5\columnwidth]{spec_57633.8.pdf}
+  \includegraphics[width=0.5\columnwidth]{spec_57638.pdf}
  \end{minipage}
@@
  \begin{minipage}{2\columnwidth}
-  \includegraphics[width=0.5\columnwidth]{spec_57643.png}
-  \includegraphics[width=0.5\columnwidth]{spec_57645.png}
+  \includegraphics[width=0.5\columnwidth]{spec_57643.pdf}
+  \includegraphics[width=0.5\columnwidth]{spec_57645.pdf}
  \end{minipage}
@@
  \begin{minipage}{2\columnwidth}
-  \includegraphics[width=0.5\columnwidth]{spec_57646.png}
-  \includegraphics[width=0.5\columnwidth]{spec_57648.png}
+  \includegraphics[width=0.5\columnwidth]{spec_57646.pdf}
+  \includegraphics[width=0.5\columnwidth]{spec_57648.pdf}
  \end{minipage}
@@
  \begin{minipage}{2\columnwidth}
-  \includegraphics[width=0.5\columnwidth]{spec_57649.png}
+  \includegraphics[width=0.5\columnwidth]{spec_57649.pdf}
  \end{minipage}
@@
 Table \ref{tab:spec} shows that the typical burst width is measured as $2\pm0.5$~ms (68\% confidence interval); the inter-channel dispersion smearing ranges from 0.4 to 1.1~ms across this band.
-The brightest burst (on 57633.68) is modeled with a temporal width of $2.05\pm0.02$~ms and its arrival time is measured with a precision of $\sim50\mu$s.
+The brightest burst (on 57633.68) is modeled with a temporal width of $2.05\pm0.02$~ms and its arrival time is measured with a precision of $\sim50~\mu$s.
 Note that these errors are only accurate to the degree that the model represents the data.
@@
 \begin{center}
-\includegraphics[width=2\columnwidth]{corner57646}
+\includegraphics[width=2\columnwidth]{corner57646.pdf}
 \caption{A scatterplot matrix that shows the correlation of every pair of parameters in the MCMC run for burst 57646.
@@
 
-Figure \ref{fig:dmmodel} compares the 68\% confidence intervals on the DM for all nine VLA bursts against detection time (top panel) and the modeled burst temporal width (bottom panel).
+Figure \ref{fig:dmdt} compares the 68\% confidence intervals on the DM for all nine VLA bursts against detection time (top panel) and the modeled burst temporal width (bottom panel).
 The error weighted mean burst DM is 567.8$\pm$0.1 pc cm$^{-3}$, significantly larger than the long-term average of 560.5 pc cm$^{-3}$ seen by Arecibo during this campaign.
@@
 
-The bottom panel of Figure \ref{fig:dmmodel} compares the DM to the modeled temporal width of the bursts.
+The bottom panel of Figure \ref{fig:dmdt} compares the DM to the modeled temporal width of the bursts.
 There is a weak correlation between burst width and apparent DM.
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{burst_dmdt}
+\includegraphics[width=\columnwidth]{burst_dmdt.pdf}
 \caption{(Top) Burst time versus DM for nine 3~GHz bursts detected by the VLA.
@@
 (Bottom) Temporal width versus burst DM for the same nine VLA bursts.
-\label{fig:dmmodel}}
+\label{fig:dmdt}}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{energy_disn}
+\includegraphics[width=\columnwidth]{energy_disn.pdf}
 \caption{The cumulative burst energy distributions for the VLA, Arecibo, and GBT bursts are shown with dots connected by solid, dashed, and dotted lines, respectively.
@@
 %individuals
-CJL is supported by the University of California Office of the President under Lab Fees Research Program Award 237863 and NSF award 1611606.
-MAM is supported by NSF award \#1458952.
+CJL is supported by the University of California Office of the President under Lab Fees Research Program Award 237863 and NSF award 1611606. MAM is supported by NSF award 1458952. 
 KPM's research is supported by the Oxford Centre for Astrophysical Surveys which is funded through the Hintze Family Charitable Foundation.
@@
 PS holds a Covington Fellowship at DRAO. 
+The LWA1 station is supported by the National Science Foundation under grant 1139974 of the University Radio Observatory program.
 VMK acknowledges support from NSERC, CIFAR, the Canada Research Chair Program and from the Lorne Trottier Chair in Astrophysics \& Cosmology.

### 2017-05-03 timeline.py

@@ -137,4 +137,4 @@ fig.autofmt_xdate()
 
 #show()
 pngsuff = '0' if '0' in sys.argv[1] else ''
-savefig('timeline{0}.png'.format(pngsuff))
+savefig('timeline{0}.pdf'.format(pngsuff), format='pdf')

### 2017-05-04 repeater-vladata.tex
include jayce comments and lwa1 naming.

@@
 \begin{abstract}
-We present results of the coordinated observing campaign that made the first subarcsecond localization of a Fast Radio Burst, FRB 121102.
+We present results of the coordinated observing campaign that made the first subarcsecond localization of a Fast Radio Burst, \frb.
 Of the nine bursts detected by the Very Large Array at 3~GHz, three had simultaneous observing coverage at other observatories.
@@
 We find that burst spectra are characterized by a $\sim500$~MHz envelope and apparent radio energy as high as $10^{40}$\ erg.
-We attribute significant changes in the apparent dispersion between bursts to frequency-dependent profiles that add a systematic random to the estimate of DM by up to 1\%.
+We attribute significant changes in the apparent dispersion between bursts to frequency-dependent profiles that add a random error to the estimate of DM by up to 1\%.
 We use \frb\ as a prototype of the FRB class to estimate a volumetric birth rate of FRB sources $R_{\rm{FRB}} \approx 5\times10^{-5}/N_r$\ Mpc$^{-3}$\ yr$^{-1}$, where $N_r$\ is the number of bursts per source over its lifetime.
@@
 \frb, also known as the ``repeating FRB'', was discovered \citep{2014ApJ...790..101S} in data acquired in 2012 as part of the PALFA survey of the Arecibo Observatory \citep{2006ApJ...637..446C}.
-In mid 2015, new Arecibo observations revealed a series of bursts at a similar DM and sky position that rules out cataclymic models for this source \citep{2016Natur.531..202S}.
+In mid 2015, new Arecibo observations revealed a series of bursts at a similar DM and sky position that rules out cataclysmic models for this source \citep{2016Natur.531..202S}.
 The typical DM measured by early Arecibo observations was 559 pc cm$^{-3}$ \citep{2016arXiv160308880S}, although somewhat higher values have been seen in more recent observations (560.5 pc cm$^{-3}$; Hessels et al., in prep).
@@
 
-This paper presents an analysis of the spectral properties of VLA bursts implied by simultaneous observing at Arecibo, Effelsberg, the Long-Wavelength Array \citep[LWA; ][]{2013ITAP...61.2540E}, and the Arcminute Microkelvin Imager Large Array \citep[AMI-LA; ][]{2008MNRAS.391.1545Z}.
+This paper presents an analysis of the spectral properties of VLA bursts implied by simultaneous observing at Arecibo, Effelsberg, the first station of the Long-Wavelength Array \citep[LWA1; ][]{2013ITAP...61.2540E}, and the Arcminute Microkelvin Imager Large Array \citep[AMI-LA; ][]{2008MNRAS.391.1545Z}.
 This includes the first simultaneous detection of an FRB at two observatories, between the VLA and Arecibo.
@@
 Circled observations with no line indicate observations on the same day that did not overlap.
-Symbols show days with observations with letters V, L, S, C, U referring to radio frequencies of 70~MHz, 1.4, 3, 4.5, and 15~GHz, respectively.
+Days with observations are indicated with radio band designations 4, L, S, C, U referring to radio frequencies of 70~MHz, 1.4, 3, 4.5, and 15~GHz, respectively.
 \label{fig:sched}}
@@
 The data presented here were obtained from multiple programs and telescopes with a goal of interferometrically localizing \frb\ with the VLA.
-We coordinated observing between the VLA, Arecibo, Effelsberg, LWA, and AMI-LA telescopes, as shown in Figure \ref{fig:sched} and Table \ref{tab:obs}.
+We coordinated observing between the VLA, Arecibo, Effelsberg, LWA1, and AMI-LA telescopes, as shown in Figure \ref{fig:sched} and Table \ref{tab:obs}.
 Below, we summarize these observations, with a focus on those conducted simultaneously with VLA burst detections from \frb.
@@
 \tablenotetext{b}{Effelsberg coverage at 4.5~GHz.}
-\tablenotetext{c}{LWA coverage near 70~MHz.}
+\tablenotetext{c}{LWA1 coverage near 62 and 78~MHz.}
 \tablenotetext{d}{AMI-LA coverage at 15~GHz.}
@@
 
-\subsection{LWA}
+\subsection{LWA1}
 
-Beginning in April 2016, VLA observations of \frb were simultaneously observed with the first station of the LWA\footnote{This LWA station is located at the VLA site and is the first to be deployed.
-It is sometimes referred to as ``LWA1'', but we use ``LWA'' here.} when possible.
-The LWA observations consisted of single phased-array beam centered on the location of \frb with two 4096-channel spectral windows spanning frequencies from 52.2--71.8~MHz and 68.2--87.8~MHz.
-The observations were taken in LWA's spectrometer mode with a channel size of 4.8~kHz and a sample time of 160~ms.
+Beginning in April 2016, VLA observations of \frb were simultaneously observed with LWA1 when possible.
+The LWA1 observations were automatically scheduled through the Heuristic Automation for LWA1 (HAL) system.
+Briefly, the HAL system receives messages via the internet that signal the start of a VLA observation.
+If the source is visible and there are no high priority LWA1 observations scheduled, the HAL system automatically generates an observing schedule, re-configures the telescope, and alerts the observatory staff of the change.
+The time delay from HAL receiving a message to starting an observation is typically one to two minutes.
+
+The LWA1 observations consisted of single phased-array beam centered on the location of \frb with two 4096-channel spectral windows spanning frequencies from 52.2--71.8~MHz and 68.2--87.8~MHz.
+The observations were taken in a spectrometer mode with a channel size of 4.8~kHz and a sample time of 160~ms.
 The integration time was set to be equal to the dispersion smearing across a single channel at 50~MHz for DM$\approx560$\ pc cm$^{-3}$.
 
-Two of the VLA detected pulses, on MJD 57648 and 57649, had simultaneous coverage with LWA.
-We use the modeled LWA antenna sensitivity as a function of zenith angle to estimate an system equivalent flux density of 9.5 kJy and 8.7 kJy for the two bursts, respectively.
+Two of the VLA detected pulses, on MJD 57648 and 57649, had simultaneous coverage with LWA1.
+We use the modeled LWA1 antenna sensitivity as a function of zenith angle to estimate an system equivalent flux density of 9.5 kJy and 8.7 kJy for the two bursts, respectively.
 The data were de-dispersed into time series with DMs ranging from 500 to 600 pc cm$^{-3}$\ using a step size of 1.0 pc cm$^{-3}$.
@@
 The Arecibo and Effelsberg upper limits at 1.4 and 4.5~GHz, respectively, limit all burst spectral indices $\alpha_{1.4/3}>+4.8$ and $\alpha_{3/4.5}<-2.7$.
+These are consistent with limits from the LWA1 and AMI-LA, which require $\alpha_{0.07/3}>-2.4$\ and $\alpha_{3/15}<1.5$ for bursts on MJD 57643 and 57649 (the brightest VLA bursts with observing coverage), respectively.
 The strictest limits on $\alpha_{1.4/3}$\ and $\alpha_{3/4.5}$\ are both derived from the burst on MJD 57649, which shows that a power law model is inappropriate even for a single burst.
@@
 Upper limits assume a pulse width of 2~ms and a $5\sigma$ detection threshold.
-Measurements (dots) and limits (triangles) are shown for Arecibo, VLA, and Effelsberg at 1.4, 3, and 4.5~GHz, respectively; limits from LWA and AMI-LA are not visible on this scale.
+Measurements (dots) and limits (triangles) are shown for Arecibo, VLA, and Effelsberg at 1.4, 3, and 4.5~GHz, respectively; limits from LWA1 and AMI-LA are not visible on this scale.
 Errors in flux density are comparable to the symbol size and are not shown.
@@
 \tablecomments{$S_{\rm{V}}$ is the measured circular polarization of the burst, which dominated by systematic effects. All error ranges represent 68\% confidence intervals.}
-\tablenotetext{a}{Simultaneously observed by either Arecibo, Effelsberg, LWA, or AMI-LA.}
+\tablenotetext{a}{Simultaneously observed by either Arecibo, Effelsberg, LWA1, or AMI-LA.}
 \tablenotetext{b}{Detected simultaneously with Arecibo.}
@@
 The DM scale for both panels is shown at the bottom.
-The 68\% confidence interval on DM is shown with a bar and the dahsed line shows the best-fit DM$=560.5$\ pc cm$^{-3}$ inferred from Arecibo observations at 1.4~GHz (Hessels et al, in prep).
+The 68\% confidence interval on DM is shown with a bar and the dashed line shows the best-fit DM$=560.5$\ pc cm$^{-3}$ inferred from Arecibo observations at 1.4~GHz (Hessels et al, in prep).
 (Bottom) Temporal width versus burst DM for the same nine VLA bursts.
@@
 That model argues that the simultaneous appearance of a burst from 1.2 to 3.5~GHz requires a lens with the focal frequency be $\gtrsim 3.5$~GHz.
-This gives a constraint on the combination
-$$\frac{\rm DM_0}{a_{\rm AU}^2} \frac{d_{sl}d_{lo}/d_{so}}{1\, \rm kpc} \gtrsim (3.5 / 39.1)^2$$
-where DM$_0$, $a$, and $d_{sl, lo, so}$\ are the electron column density of the lens, size of the lens, and lensing distances, respectively.
+%This gives a constraint on the combination 
+%$$\frac{\rm DM_0}{a_{\rm AU}^2} \frac{d_{sl}d_{lo}/d_{so}}{1\, \rm kpc} \gtrsim (3.5 / 39.1)^2$$
+%where DM$_0$, $a$, and $d_{sl, lo, so}$\ are the electron column density of the lens, size of the lens, and lensing distances, respectively.
 A lens placed at $d_{sl}\approx1$~kpc is consistent with typical properties of the interstellar medium.
@@
 This modeling also shows that the apparent DM changes from burst to burst and that DM is biased above the long-term average measured at 1.4~GHz.
-The nature of this DM change is not known, but could be explained by strong frequency-dependent profile evolution or unresolved spectrotemporal in the bursts.
+The nature of this DM change is not known, but could be explained by strong frequency-dependent profile evolution or unresolved spectrotemporal structure in the bursts.
 

### 2017-05-18 repeater-vladata.tex
added pwkit cite
working through jim comments. rescaled vla energies but vla limit seems off

@@
 We present results of the coordinated observing campaign that made the first subarcsecond localization of a Fast Radio Burst, \frb.
-Of the nine bursts detected by the Very Large Array at 3~GHz, three had simultaneous observing coverage at other observatories.
-Only one VLA burst was detected by another observatory, the Arecibo Observatory at 1.4~GHz.
+During this campaign, we made the first detection of an FRB burst by multiple telescopes: the VLA at 3~GHz and the Arecibo Observatory at 1.4~GHz.
+Of the nine bursts detected by the Very Large Array at 3~GHz, four had simultaneous observing coverage at other observatories.
 We use multi-observatory constraints and modeling of bursts seen only at 3~GHz to confirm earlier results showing that burst spectra are not well characterized by a power law.
 We find that burst spectra are characterized by a $\sim500$~MHz envelope and apparent radio energy as high as $10^{40}$\ erg.
-We attribute significant changes in the apparent dispersion between bursts to frequency-dependent profiles that add a random error to the estimate of DM by up to 1\%.
+We measure significant changes in the apparent dispersion between bursts that can be attributed to frequency-dependent profiles or some other intrinsic burst structure that adds a random error to the estimate of DM by up to 1\%.
 We use \frb\ as a prototype of the FRB class to estimate a volumetric birth rate of FRB sources $R_{\rm{FRB}} \approx 5\times10^{-5}/N_r$\ Mpc$^{-3}$\ yr$^{-1}$, where $N_r$\ is the number of bursts per source over its lifetime.
@@
 The black dashed lines show the VLA burst detections with simultaneous coverage at other telescopes and the solid line shows the simultaneous burst detection.
-Circled observations with no line indicate observations on the same day that did not overlap.
+Circled observations with no line indicate bursts that did not have simultaneous observing coverage at the VLA.
 Days with observations are indicated with radio band designations 4, L, S, C, U referring to radio frequencies of 70~MHz, 1.4, 3, 4.5, and 15~GHz, respectively.
@@
 All VLA fast-sampled data were observed with 5~ms sampling, 256 channels, and dual-circular polarization \citep{2015ApJ...807...16L}.
-The channel frequency width was set to maximize sensitivity to the known DM of \frb\ with the largest total bandwidth.
-The total bandwidths at L (1.4~GHz), S (3~GHz), and C (6~GHz) bands were 256~MHz, 1024~MHz, and 2048~MHz, respectively.
+The total bandwidths at L (1.4~GHz), S (3~GHz), and C (6~GHz) bands were 256, 1024, and 2048~MHz, respectively, corresponding to channel bandwidths of  1, 4, and 8~MHz.
+The dispersion smearing across a channel is $\sim1.7$, 0.7, and 0.2~ms in the same respective bands.
 The 3~GHz data were recorded data in eight spectral windows with 32 channels each and had sensitivity of 5~mJy in 5~ms ($1\sigma$).
@@
 
-During the late-2016 campaign, Arecibo observed with the L-wide receiver using the PUPPI pulsar backend.
+Arecibo observed with the L-wide receiver using the PUPPI pulsar backend.
 The observational frequency range was 1.15 to 1.73~GHz and frequency resolution was 1.5625~MHz, which has a typical sensitivity of 2~mJy in 2~ms ($1\sigma$).
@@
 The phase calibrator, J0518+3306, was observed every 12 minutes for about 1.5 minutes.
-The AMI-LA data were binned to eight 0.625~GHz channels and processed (RFI excision and calibration) with a fully-automated pipeline, AMI-REDUCE \citep[e.g.,][]{2013MNRAS.429.3330P}.
+The AMI-LA data were binned to eight 0.625~GHz channels and processed (interference excision and calibration) with a fully-automated pipeline, AMI-REDUCE \citep[e.g.,][]{2013MNRAS.429.3330P}.
 Daily measurements of 3C48 and 3C286 were used for the absolute flux calibration, which is good to about 10\%.
@@
 
-Four of the VLA bursts had simultaneous observing coverage with either Arecibo, Effelsberg, or AMI-LA.
-Two of the VLA bursts had simultaneous observing coverage by all four observatories (Figure \ref{fig:sched}).
-Of these bursts, only one VLA burst (on MJD 57648) was simultaneously detected by another observatory (Arecibo).
+Figure \ref{fig:sgram} shows a dynamic spectrum for the first FRB burst to be detected simultaneously at two telescopes.
+This burst, on MJD 57648, was detected both by the VLA and Arecibo while upper limits were measured by simultaneous observations at the other three telescopes.
+In total, four of the VLA bursts had simultaneous observing coverage with either Arecibo, Effelsberg, LWA1, or AMI-LA.
+Two of the VLA bursts had simultaneous observing coverage by all four observatories, including the burst detected by Arecibo (Figure \ref{fig:sched}).
 
-Figure \ref{fig:sgram} shows a dynamic spectrum for this burst with both VLA and Arecibo data.
-The temporal resolution of the VLA data (5~ms) is much coarser than that of Arecibo, so data were resampled to the Arecibo temporal grid after correcting for barycentric and dispersion measure offsets.
+To generate the multi-telescope dynamic spectrum, the VLA data were resampled to the Arecibo temporal grid after correcting for barycentric and dispersion measure offsets.
 We assumed a DM of 560.5 pc cm$^{-3}$ (Hessels et al., in prep) to calculate a dispersion delay of 189 and 734~ms from infinite frequency to the top of the VLA and Arecibo bands, respectively.
@@
 The thick black line separates data from the VLA (2.5 to 3.5~GHz) and Arecibo (1.1 to 1.8~GHz) and flagged data are grey.
-The amplitude scale is normalized by assuming the Arecibo to VLA gain ratio is 10.
+For clarity, the VLA and Arecibo data are independently normalized to units of S/N per pixel; Arecibo is 5 times more sensitive than the VLA.
  \label{fig:sgram}}
@@
 
-Figure \ref{fig:multi} shows coarse spectra built from integrated flux densities measured (or limited) for three bursts with multi-telescope observing coverage.
+Figure \ref{fig:multi} shows coarse spectra built from integrated flux densities measured (or limited) for the three VLA bursts with observing coverage by Arecibo or Effelsberg.
 The burst on MJD 57648 was detected with VLA and Arecibo with significances of 25$\sigma$\ and 39$\sigma$, which corresponds to peak flux densities in 5~ms of $111\pm5$\ mJy and $14\pm0.4$\ mJy at 3 and 1.4~GHz, respectively.
@@
  \includegraphics[width=\columnwidth]{multispec.pdf}
- \caption{Broadband spectral measurements and limits for three bursts of \frb\ with simultaneous multi-telescope observing coverage.
+ \caption{Broadband spectral measurements and limits for three bursts of \frb\ with observing coverage by Arecibo or Effelsberg.
 Upper limits assume a pulse width of 2~ms and a $5\sigma$ detection threshold.
@@
 \subsection{VLA Bursts}
-\subsubsection{Spectral Modeling}
+
+\subsubsection{Spectrotemporal Modeling}
 \label{sec:spec}
@@
 
-Table \ref{tab:spec} summarizes the properties of all nine VLA bursts.
+Table \ref{tab:spec} summarizes the spectrotemporal properties of all nine VLA bursts.
 Parameters such as integrated flux density, S/N, and Stokes V were measured from the burst properties integrated in frequency.
-Stokes V values estimated from the dual-circular feeds as $(RR-LL)/(RR+LL)\approx3\%$, which is comparble to the systematic error induced by the primary beam\footnote{See EVLA memo \#195 at \url{https://library.nrao.edu/public/memos/evla/EVLAM_195.pdf}.}.
+Stokes V values were estimated from the dual-circular feeds as $(RR-LL)/(RR+LL)\approx3\%$, which is comparble to the systematic error expected from beam squint at this location in the primary beam \footnote{See EVLA memo \#195 at \url{https://library.nrao.edu/public/memos/evla/EVLAM_195.pdf}.}.
 Given that systematic effects dominate the apparent circular polarization, this observation limits the fractional circular polarization to less than 3\%.
@@
 (2016)       &  (MJD)     &   (image)    & (mJy) 			& (mJy) 		    & (pc cm$^{-3})$ 	& (ms) 			& (mJy) 			& (GHz)  & (MHz) & ($10^{38}$\ erg)\\ \hline
-23 Aug & 57623.74402686      & 38 		& 194			& +3				& 567$\pm2$ 		& 2.0$\pm0.2$	 		& 690 		& 2.8 		& 290 & 11 			\\
-2 Sep & 57633.67986367      & 179 		& 1500			& --35 				& 568.2$\pm0.2$ 	& 2.05$\pm0.02$			& 3340 		& 3.2 		& 510 & 98				\\
-2 Sep\tablenotemark{c} & 57633.69515938 & 15 & 69		& +2				& 562$^{+4}_{-6}$ 	& 2.5$^{+0.9}_{-0.6}$	& $>$430 	& $<$2.5	& $<$290 & 7  			\\
-7 Sep & 57638.49937435      & 12 		& 55			& +5 				& 567$^{+7}_{-9}$ 	& 1.3$^{+1.4}_{-0.8}$	& 130 		& 3.1 		& 420 & 3  			\\
-12 Sep\tablenotemark{a} & 57643.45730263  & 100 		& 508 & --5 		& 565.6$^{+0.6}_{-0.5}$ & 1.9$\pm0.1$		& 1170 		& 2.8 		& 510 & 34 			\\
-14 Sep\tablenotemark{a} & 57645.42958602   & 13 		& 64 & +3			& 563$^{+5}_{-4}$ 	& 1.1$\pm0.7$		 	& 170 		& 2.8 		& 380 & 4  			\\
-15 Sep\tablenotemark{c} & 57646.46600650 & 20 & 87		& +1				& 569$\pm5$ 		& 2.5$^{+0.9}_{-1.4}$	& $>$420 	& $<$2.5 	& $<$430 & 10 			\\	
-17 Sep\tablenotemark{a,b} & 57648.43691490 & 25 & 111	& +9				& 564$\pm2$ 		& 1.4$^{+0.3}_{-0.4}$	& 260 		& 2.8 		& 470 & 7  			\\
-18 Sep\tablenotemark{a} & 57649.45175697   & 36 		& 167 & +1			& 567$\pm2$ 		& 2.1$\pm0.5$		 	& 290 		& 3.0 		& 690 & 12 			\\ \hline
+23 Aug & 57623.74402686      & 38 		& 194			& +3				& 567$\pm2$ 		& 2.0$\pm0.2$	 		& 690 		& 2.8 		& 290 & 4.6 	\\
+2 Sep & 57633.67986367      & 179 		& 1500			& --35 				& 568.2$\pm0.2$ 	& 2.05$\pm0.02$			& 3340 		& 3.2 		& 510 & 40		\\
+2 Sep\tablenotemark{c} & 57633.69515938 & 15 & 69		& +2				& 562$^{+4}_{-6}$ 	& 2.5$^{+0.9}_{-0.6}$	& $>$430 	& $<$2.5	& $<$290 & 3.6 	\\
+7 Sep & 57638.49937435      & 12 		& 55			& +5 				& 567$^{+7}_{-9}$ 	& 1.3$^{+1.4}_{-0.8}$	& 130 		& 3.1 		& 420 & 0.8  	\\
+12 Sep\tablenotemark{a} & 57643.45730263  & 100 		& 508 & --5 		& 565.6$^{+0.6}_{-0.5}$ & 1.9$\pm0.1$		& 1170 		& 2.8 		& 510 & 13 		\\
+14 Sep\tablenotemark{a} & 57645.42958602   & 13 		& 64 & +3			& 563$^{+5}_{-4}$ 	& 1.1$\pm0.7$		 	& 170 		& 2.8 		& 380 & 0.8  	\\
+15 Sep\tablenotemark{c} & 57646.46600650 & 20 & 87		& +1				& 569$\pm5$ 		& 2.5$^{+0.9}_{-1.4}$	& $>$420 	& $<$2.5 	& $<$430 & 5.0 	\\	
+17 Sep\tablenotemark{a,b} & 57648.43691490 & 25 & 111	& +9				& 564$\pm2$ 		& 1.4$^{+0.3}_{-0.4}$	& 260 		& 2.8 		& 470 & 2.0  	\\
+18 Sep\tablenotemark{a} & 57649.45175697   & 36 		& 167 & +1			& 567$\pm2$ 		& 2.1$\pm0.5$		 	& 290 		& 3.0 		& 690 & 4.9 	\\ \hline
 \end{tabular}
@@
 This 6-parameter model defined the intrinsic signal that was then distributed over a fixed time-frequency observing grid.
-The inter-channel amplitude modulation was ignored in the model.
 
@@
 This confirms previous reports based on Arecibo and GBT data \citep{2016arXiv160308880S} with the wider (1~GHz) VLA bandwidth and extends this phenomenon to 3~GHz.
-
-% ** signal or noise analysis offered by jim **
 
@@
   \includegraphics[width=0.5\columnwidth]{spec_57649.pdf}
+  \includegraphics[width=0.5\columnwidth]{specAO_57648.pdf}
  \end{minipage}
-\caption{Spectra and best-fit model for nine bursts seen by the VLA from 2.5 to 3.5~GHz in the peak, dedispersed 5~ms integration.
-The solid line is a best-fit Gaussian model found through modeling.
-The typical flux density error per channel is 70~mJy, which is shown at the top right of each panel next to the MJD label.
+\caption{Ten panels show spectra for nine VLA bursts and one Arecibo burst (bottom right).
+The VLA spectra are drawn from flux-calibrated, dedispersed 5~ms integrations.
+The Arecibo spectrum is drawn from a 2.7~ms window with 3.125~MHz channels and the flux scale is esimated using the radiometer equation.
+The solid line shown with VLA spectra is a best-fit Gaussian model found through modeling.
+The typical VLA flux density error per channel is 70~mJy, which is shown at the top right of each panel next to the MJD label.
 \label{fig:spec}}
@@
 
-This analysis differs from traditional analysis in that it simultaneously models the spectral and temporal evolution of the burst.
+Our approach simultaneously models the spectral and temporal evolution of the burst.
 A typical \frb\ burst takes $\sim180$~ms or 36 integrations to cross the observing band from 2.5 to 3.5~GHz.
@@
 Table \ref{tab:spec} shows that the typical burst width is measured as $2\pm0.5$~ms (68\% confidence interval); the inter-channel dispersion smearing ranges from 0.4 to 1.1~ms across this band.
-The brightest burst (on 57633.68) is modeled with a temporal width of $2.05\pm0.02$~ms and its arrival time is measured with a precision of $\sim50~\mu$s.
+The brightest burst (on MJD 57633.68) is modeled with a temporal width of $2.05\pm0.02$~ms and its arrival time is measured with a precision of $\sim50~\mu$s.
 Note that these errors are only accurate to the degree that the model represents the data.
@@
 
-The initial VLA detections were made with a matched-filter approach that allowed inter-DM sensitivity losses up to roughly 10\% \citep[$\Delta \rm{DM}=10\ \rm{pc}\ \rm{cm}^{-3}$][]{2003ApJ...596.1142C}.
-The MCMC modeling is more sophisticated in that it considers a wider range of parameters and models both data and observing effects (frequency-time pixel boundaries) simultaneously.
-
+The spectrotemporal modeling presented in \S \ref{sec:spec} provides marginalized posterior distributions for burst DM and pulse width.
 Figure \ref{fig:dmdt} compares the 68\% confidence intervals on the DM for all nine VLA bursts against detection time (top panel) and the modeled burst temporal width (bottom panel).
 The error weighted mean burst DM is 567.8$\pm$0.1 pc cm$^{-3}$, significantly larger than the long-term average of 560.5 pc cm$^{-3}$ seen by Arecibo during this campaign.
-However, we note that the 95\% confidence intervals in DM for multiple bursts are not consistent with this mean nor each other, which suggests that some burst-specific property can bias the measured DM.
+Furthermore, several of the 95\% confidence intervals in DM are not consistent with this mean nor each other, which suggests that some burst-specific property can bias the measured DM.
 The variation in DM observed by the VLA at 3~GHz is similar to that reported for Arecibo observations of \frb\ in \citet{2016arXiv160308880S}.
-% This is consistent with the idea that the DM measured at low temporal resolution (e.g., by the VLA or by single-dish observatories without coherent dedispersion) is determined by extrinsic (an electron column) dispersion and some spectrotemporal structure that changes between bursts.
 
@@
 \includegraphics[width=\columnwidth]{burst_dmdt.pdf}
-\caption{(Top) Burst time versus DM for nine 3~GHz bursts detected by the VLA.
+\caption{(Top) Burst epoch versus DM for nine 3~GHz bursts detected by the VLA.
 The DM scale for both panels is shown at the bottom.
@@
 
-\subsection{Temporal Statistics}
-\label{sec:temp}
+\subsubsection{Fine Spectral Structure}
 
-The burst rate for \frb\ varied dramatically throughout the 2016 observing campaign (Figure \ref{fig:sched}).
+The spectral fits in Figure \ref{fig:spec} have residuals that include single samples that deviate by many standard deviations, particularly in the bursts on MJDs 57623,  57633.6, and 57643.
+These do not appear to be caused by terrestrial interference.
+They are most likely spectral variations from diffractive interstellar scintillations that, as noted previously, have characteristic frequency widths slightly larger than the 4~MHz channel bandwidth.
+Scintillation variations are multiplicative and have a one-sided exponential probability distributino function that can yield occasional large-amplitude ``scintles'' that are several times the mean scintle amplitude of unity.
+
+The spectral variations could in principle also include contributions from self noise in the source but to be significant, intrinsic fine structure in the burst would have to be on microsecond scales.
+
+\subsection{Temporal, Energy, and Brightness Distributions of Bursts}
+\label{sec:disn}
+
+The burst rate for \frb\ varied dramatically throughout the 2016 observing campaign.
 In the early-2016 campaign, we observed for 30 hours at 3~GHz and no bursts were detected.
@@
 
-\subsection{Energy and Brightness Distribution}
-\label{sec:disn}
+% ** clean this up
+The integrated burst flux density is calculated by integrating the burst spectral model (Table \ref{tab:spec}) in frequency and time.
+Some VLA burst spectra seem to be contained by the 2.5 to 3.5~GHz band and most of them seem to have Gaussian envelopes that are well modeled by the emission within that band.
+Assuming that the Gaussian shape defines the full emission window, the integrated 3~GHz flux density can be converted to a total energy with no further assumptions about the burst spectral properties as:
 
-Knowing the source distance, we calculate the burst energy by integrating flux in time and frequency (Table \ref{tab:spec}).
-Some VLA burst spectra seem to be contained by the 2.5 to 3.5~GHz band and most of them seem to have Gaussian envelopes that are well modeled by the emission within that band.
-Assuming that the Gaussian shape defines the full emission window, the mean 3~GHz flux density can be converted to a total energy with no further assumptions about the burst spectral properties.
+\begin{equation}
+E_{\rm{int}} = 10^{-23} \rm{dt} (4\pi L_d^2) \rm{amplitude} 2.355 \sigma \rm{erg}
+\end{equation}
+\noindent where...
 
@@
 The VLA distribution shown represents the 27-hour, late-2016 campaign, which is longer than the single-dish campaigns presented here.
-However, since the VLA observations have a relatively coarse time resolution, it is not as sensitive as Arecibo and the GBT, so no bursts with energiest less than $3\times10^{38}$~erg were detected.
+However, since the VLA observations have a relatively coarse time resolution, it is not as sensitive as Arecibo and the GBT, so no bursts with energies less than $3\times10^{38}$~erg were detected.
 The rate upper limit (95\% confidence) from the early-2016 VLA campaign shows that even identical observing campaigns have different detection rates.
@@
 Rather than trying to estimate a completeness limit for each energy distribution, we assume an effective detection limit of 0.9 times the weakest burst detected; the best-fit slope is weakly dependent on this, but general conclusions are robust.
-We directly sampled the likelihood distribution to estimate a best slope of $\alpha_{\rm{VLA}}=-0.7^{+0.3}_{-0.4}$, $\alpha_{\rm{Arecibo}}=-0.8^{+0.3}_{-0.5}$, and $\alpha_{\rm{GBT}}=-0.8^{+0.4}_{-0.5}$ (68\% confidence interval).
+We directly sampled the likelihood distribution to estimate a best slope of $\alpha_{\rm{VLA}}=-0.6^{+0.2}_{-0.3}$, $\alpha_{\rm{Arecibo}}=-0.8^{+0.3}_{-0.5}$, and $\alpha_{\rm{GBT}}=-0.8^{+0.4}_{-0.5}$ (68\% confidence interval).
 Expressed as a power law function in $dN/dE$, the slope index is approximately --1.7.
+We caution that propagation effects can potentially modulate the intrinsic flux density and significantly affect any interpretation about burst amplitudes.
 
@@
 
-After correcting for barycentric and typical dispersion delays, the VLA/Arecibo burst spectrum shows a residual temporal drift.
+After correcting for barycentric and typical dispersion delays, the burst spectra at the VLA and at Arecibo show a residual temporal drift.
 This drift can be interpreted as an excess DM, but contemporaneous observations at 1.4~GHz measured a significantly lower DM (560.5 pc cm$^{-3}$; Hessels et al, in prep).
 This excess DM is comparable to the burst-to-burst variation in DM within the whole sample of VLA 3~GHz bursts.
-This variation had been noted in earlier 1.4~GHz Arecibo observations of \frb\ \citep{2016arXiv160308880S}, but the VLA bursts demonstrate that this burst-specific DM is seen up to 3~GHz.
+This variation had been noted in earlier 1.4~GHz Arecibo observations of \frb\ \citep{2016arXiv160308880S}, but the VLA bursts demonstrate that this burst-specific DM is seen simltaneously from 1.4 to 3~GHz.
 
@@
 The burst-dependent DM changes are on the order of 1\% of the total DM (equivalent to a delay rate up to 2~ms GHz$^{-1}$), which is much larger than typically observed \citep{2017MNRAS.466.3706L}.
-The systematic offset of the VLA 3~GHz DM from that observed by Arecibo suggests that any such burst frequency evolution must be larger at higher frequencies.
 Our modeling of the VLA burst dynamic spectra show a weak correlation between larger apparent DM and pulse width.
@@
 \citet{2017arXiv170306580C} describe a model where plasma lensing near the source of an FRB can magnify radio emission by orders of magnitude.
-That model argues that the simultaneous appearance of a burst from 1.2 to 3.5~GHz requires a lens with the focal frequency be $\gtrsim 3.5$~GHz.
-%This gives a constraint on the combination 
-%$$\frac{\rm DM_0}{a_{\rm AU}^2} \frac{d_{sl}d_{lo}/d_{so}}{1\, \rm kpc} \gtrsim (3.5 / 39.1)^2$$
-%where DM$_0$, $a$, and $d_{sl, lo, so}$\ are the electron column density of the lens, size of the lens, and lensing distances, respectively.
-A lens placed at $d_{sl}\approx1$~kpc is consistent with typical properties of the interstellar medium.
-Lenses that are influenced by the source would be much nearer to the source $d_{\sl} \ll 1$~kpc, requiring large values of $\rm{DM_0}/a_{\rm AU}^2$.
+Plasma lensing can also produce multiple burst images separated by time scales from microseconds to tens of milliseconds or longer.
+These burst images would also have slightly different DMs.
+Lensing amplifications have a complicated frequency dependence that includes spikes, plateaus, and troughs.
+The simultaneous detection of burst MJD 57648 with both Arecibo (L band) and the VLA (S band up to 3.2~GHz) suggests requires a focal frequency $\gtrsim 3.2$ GHz and sufficient amplification in both bands.
 
@@
 
-While the surprising brightness of new FRB discoveries was once seen as a cause for concern (i.e., a sign of terrestrial interference), we may be able to use this to infer properties of the overall population \citep{2007Sci...318..777L, 2016arXiv161105758R}.
+New FRB discoveries have often surprised observers with their remarkable brightness \citep{2007Sci...318..777L, 2016arXiv161105758R}.
 When modeling the flux distribution as a power law, an isotropic distribution of sources will have a power law index, $\alpha$, of --1.5.
@@
 
-We now know that \frb\ is detectable with the VLA out to $z=0.7$, which suggests that cosmological effects are even more important for understanding properites of the FRB population.
+We now know that \frb\ would be detectable with the VLA out to $z=0.7$, which suggests that cosmological effects are even more important for understanding properites of the FRB population.
 \citet{2017arXiv170208040C} demonstrate how redshift space distortions, time dilation, and spectral index (``k-correction'') effects can flatten the flux distribution.
@@
 That is, detecting a burst predicts that you are more likely to find another burst soon thereafter and not detecting a burst predicts you will likely not detect another burst soon thereafter.
+
+% ** jim does not like red spectrum. recast using new paper?
 
@@
 By detecting this burst from 1.2 to 3.5~GHz, we have demonstrated that some bursts have broad spectral structure.
-However, the energy of that burst was dominated by the VLA 3~GHz observing band and three other VLA bursts are undetected by Arecibo.
+However, the energy of that burst was dominated by the VLA 3~GHz observing band and two other VLA bursts are undetected by Arecibo.
 This demonstrates the burst spectra are poorly described by a power law with a single spectral index.
@@
 
-\software{\emph{rtpipe}, \emph{realfast}}
+\software{\emph{rtpipe}, \emph{realfast}, pwkit \citep{2017ascl.soft04001W}}
 

### 2017-05-18 repeater-vladata.tex
circulating for final review

@@
 
-Beginning in April 2016, VLA observations of \frb were simultaneously observed with LWA1 when possible.
+Beginning in April 2016, VLA observations of \frb\ were simultaneously observed with LWA1 when possible.
 The LWA1 observations were automatically scheduled through the Heuristic Automation for LWA1 (HAL) system.
@@
 
-The LWA1 observations consisted of single phased-array beam centered on the location of \frb with two 4096-channel spectral windows spanning frequencies from 52.2--71.8~MHz and 68.2--87.8~MHz.
+The LWA1 observations consisted of single phased-array beam centered on the location of \frb\ with two 4096-channel spectral windows spanning frequencies from 52.2--71.8~MHz and 68.2--87.8~MHz.
 The observations were taken in a spectrometer mode with a channel size of 4.8~kHz and a sample time of 160~ms.
@@
 (2016)       &  (MJD)     &   (image)    & (mJy) 			& (mJy) 		    & (pc cm$^{-3})$ 	& (ms) 			& (mJy) 			& (GHz)  & (MHz) & ($10^{38}$\ erg)\\ \hline
-23 Aug & 57623.74402686      & 38 		& 194			& +3				& 567$\pm2$ 		& 2.0$\pm0.2$	 		& 690 		& 2.8 		& 290 & 4.6 	\\
-2 Sep & 57633.67986367      & 179 		& 1500			& --35 				& 568.2$\pm0.2$ 	& 2.05$\pm0.02$			& 3340 		& 3.2 		& 510 & 40		\\
-2 Sep\tablenotemark{c} & 57633.69515938 & 15 & 69		& +2				& 562$^{+4}_{-6}$ 	& 2.5$^{+0.9}_{-0.6}$	& $>$430 	& $<$2.5	& $<$290 & 3.6 	\\
-7 Sep & 57638.49937435      & 12 		& 55			& +5 				& 567$^{+7}_{-9}$ 	& 1.3$^{+1.4}_{-0.8}$	& 130 		& 3.1 		& 420 & 0.8  	\\
-12 Sep\tablenotemark{a} & 57643.45730263  & 100 		& 508 & --5 		& 565.6$^{+0.6}_{-0.5}$ & 1.9$\pm0.1$		& 1170 		& 2.8 		& 510 & 13 		\\
-14 Sep\tablenotemark{a} & 57645.42958602   & 13 		& 64 & +3			& 563$^{+5}_{-4}$ 	& 1.1$\pm0.7$		 	& 170 		& 2.8 		& 380 & 0.8  	\\
-15 Sep\tablenotemark{c} & 57646.46600650 & 20 & 87		& +1				& 569$\pm5$ 		& 2.5$^{+0.9}_{-1.4}$	& $>$420 	& $<$2.5 	& $<$430 & 5.0 	\\	
-17 Sep\tablenotemark{a,b} & 57648.43691490 & 25 & 111	& +9				& 564$\pm2$ 		& 1.4$^{+0.3}_{-0.4}$	& 260 		& 2.8 		& 470 & 2.0  	\\
-18 Sep\tablenotemark{a} & 57649.45175697   & 36 		& 167 & +1			& 567$\pm2$ 		& 2.1$\pm0.5$		 	& 290 		& 3.0 		& 690 & 4.9 	\\ \hline
+23 Aug & 57623.74402686      & 38 		& 194			& +3				& 567$\pm2$ 		& 2.0$\pm0.2$	 		& 690 		& 2.8 		& 290 & 12 	\\
+2 Sep & 57633.67986367      & 179 		& 1500			& --35 				& 568.2$\pm0.2$ 	& 2.05$\pm0.02$			& 3340 		& 3.2 		& 510 & 98		\\
+2 Sep\tablenotemark{c} & 57633.69515938 & 15 & 69		& +2				& 562$^{+4}_{-6}$ 	& 2.5$^{+0.9}_{-0.6}$	& $>$430 	& $<$2.5	& $<$290 & 7 	\\
+7 Sep & 57638.49937435      & 12 		& 55			& +5 				& 567$^{+7}_{-9}$ 	& 1.3$^{+1.4}_{-0.8}$	& 130 		& 3.1 		& 420 & 3  	\\
+12 Sep\tablenotemark{a} & 57643.45730263  & 100 		& 508 & --5 		& 565.6$^{+0.6}_{-0.5}$ & 1.9$\pm0.1$		& 1170 		& 2.8 		& 510 & 34 		\\
+14 Sep\tablenotemark{a} & 57645.42958602   & 13 		& 64 & +3			& 563$^{+5}_{-4}$ 	& 1.1$\pm0.7$		 	& 170 		& 2.8 		& 380 & 4  	\\
+15 Sep\tablenotemark{c} & 57646.46600650 & 20 & 87		& +1				& 569$\pm5$ 		& 2.5$^{+0.9}_{-1.4}$	& $>$420 	& $<$2.5 	& $<$430 & 10 	\\	
+17 Sep\tablenotemark{a,b} & 57648.43691490 & 25 & 111	& +9				& 564$\pm2$ 		& 1.4$^{+0.3}_{-0.4}$	& 260 		& 2.8 		& 470 & 7  	\\
+18 Sep\tablenotemark{a} & 57649.45175697   & 36 		& 167 & +1			& 567$\pm2$ 		& 2.1$\pm0.5$		 	& 290 		& 3.0 		& 690 & 12 	\\ \hline
 \end{tabular}
@@
 
-We used a Markov chain Monte Carlo (MCMC) method to model the dynamic radio spectra (time versus frequency).
+The dynamic radio spectra (time versus frequency) were modeled using a Markov chain Monte Carlo (MCMC) method.
 We used the Goodman and Weare affine invariant sampler \citep{goodman2010ensemble} as implemented in \emph{emcee} \citep{2013PASP..125..306F}.
 The dynamic spectra were modeled prior to dispersion correction.
-The spectral structure was modeled as a broad Gaussian envelope (parameters of amplitude, center, $\sigma$), while the time evolution was modeled by a $\nu^2$\ dispersion law (parameters of starting integration, DM).
-Finally, the pulses were assumed to have an intrinsically square temporal width (parameter W).
+The spectral structure was modeled as a broad Gaussian envelope as a function of channel ``ch'' as:
+\begin{equation}
+G(\rm{ch}) = \frac{\rm{amp}}{\sqrt{2\pi}} \exp{\left[-\frac{1}{2} \left(\frac{\rm{ch} - \rm{center}}{\sigma_{ch}}\right)^2\right]}
+\end{equation}
+\noindent where ``amp'' is in mJy per 5~ms integration, ``center'' is the Gaussian center channel, and $\sigma_{ch}$\ is its width.
+The arrival time was modeled with a cold plasma dispersion law with the arrival time in units of integrations of:
+\begin{equation}
+\rm{i} (\rm{ch}) = \rm{i0} + 4.1488\times10^{-3}\ \rm{DM} \left[f(\rm{ch})^{-2} - f(\rm{ch0})^{-2}\right]/(5 \rm{ms})
+\end{equation}
+\noindent where ``i0'' is the arrival time at the highest frequency, ``ch0'', and function ``f'' maps the channel to a frequency in units of GHz.
+Finally, the pulses were assumed to have an intrinsically square temporal width (parameter $W_{int}$).
 This 6-parameter model defined the intrinsic signal that was then distributed over a fixed time-frequency observing grid.
@@
 The equivalent plot for the other bursts show normally-distributed samples, but this burst shows significant structure in the samples.
-The parameters ``amplitude'', ``center'', and ``$\sigma_{ch}$'' refer to the Gaussian spectral shape, while ``DM'', ``integration'', and ``W$_{int}$'' refer to the temporal shape.
+The parameters ``amp'', ``center'', and ``$\sigma_{ch}$'' refer to the Gaussian spectral shape, while ``DM'', ``i0'', and ``W$_{int}$'' refer to the temporal shape.
 The parameters are given in units of channels (4 MHz) and integrations (5 ms).
@@
 
-% ** clean this up
 The integrated burst flux density is calculated by integrating the burst spectral model (Table \ref{tab:spec}) in frequency and time.
@@
 Assuming that the Gaussian shape defines the full emission window, the integrated 3~GHz flux density can be converted to a total energy with no further assumptions about the burst spectral properties as:
-
 \begin{equation}
-E_{\rm{int}} = 10^{-23} \rm{dt} (4\pi L_d^2) \rm{amplitude} 2.355 \sigma \rm{erg}
+E_{\rm{int}} = (\rm{amp}\ 5\ \rm{ms}) ( \sigma_{ch}\ 2.355 4\ \rm{MHz}) 10^{-23} (4\pi L_d^2)\ \rm{erg}
 \end{equation}
-\noindent where...
+\noindent where the first term represents the burst fluence, the second term represents the integral of the burst spectrum, and $L_d$\ is the luminosity distance to the source.
 
@@
 The latter two energy distributions are scaled from the fluence by assuming that all burst energy is included by the observation.
-This likely underestimates the burst energy for some bursts by a factor of a few, but should not affect the slope of the distribution.
-
-Broadly, the range of energies shown in Figure \ref{fig:ed} is defined by the sensitivity of the telescope and the duration of the observing campaign.
-The VLA distribution shown represents the 27-hour, late-2016 campaign, which is longer than the single-dish campaigns presented here.
-However, since the VLA observations have a relatively coarse time resolution, it is not as sensitive as Arecibo and the GBT, so no bursts with energies less than $3\times10^{38}$~erg were detected.
-The rate upper limit (95\% confidence) from the early-2016 VLA campaign shows that even identical observing campaigns have different detection rates.
+This likely underestimates the burst energy for some bursts, but should not affect the slope of the distribution.
+The VLA distribution represents a relatively long campaign, so it is sensitive to lower event rates, but is less sensitive than the single-dish campaigns shown (minimum $E_{\rm{int}}\approx3\times10^{38}$\ erg).
+We also show the rate upper limit (95\% confidence) from the early-2016 VLA campaign to demonstrate that even identical observing campaigns have different detection rates.
 
@@
 
-% ** expand on implication of spectral envelope in context of scintillation interpretation of FRB brightness **
-
 The burst-specific DM structure could be intrinsic to the emission mechanism or induced during propagation.
@@
 This suggests that the slope is related to the underlying physical process, rather than the burst detection rate at any given time.
-The value of the energy distribution slope is similar to that observed in magnetars \citep{2000ApJ...532L.121G, 2011ApJ...739...94S}.
-This similarity has been used to argue that bursts are driven by self-regulated critical phenomena \citep[slope$=-5/3$;][]{2011SoPh..274...99A}.
+The value of the energy distribution slope is similar to that derived from high-energy bursts from magnetars \citep{2000ApJ...532L.121G, 2011ApJ...739...94S}, which may be examples of self-regulated critical phenomena \citep[slope$=-5/3$;][]{2011SoPh..274...99A}.
+This is consistent with the idea that magnetar bursts can generate both the millisecond-duration bursts and persistent radio emission from \frb\ \citep{2017arXiv170208644B}.
 
@@
 
-% ** jim does not like red spectrum. recast using new paper?
-
-The burst time distribution is consistent with a ``red spectrum'' \citep{2016MNRAS.458L..89C}, although the observations presented here are only sensitive to timescales of days (time between observations) and months (time between campaigns).
-As has been noted elsewhere, this statistical property would weaken previous constraints on repetition \citep{2015MNRAS.454..457P,2015ApJ...807...16L}.
-If this statistical property describes other FRBs, then wide, shallow surveys are the preferred strategy for blind detection of FRBs.
+The clustering of burst times for the whole FRB population has been modeled as a ``red spectrum'' \citep{2016MNRAS.458L..89C}, while recent work has modeled \frb\ burst times with a modified Poisson distribution \citep{oppermann}.
+Both temporal models imply that existing observational constraints on repetition are weaker than expected from Poissonian statistics \citep{2015MNRAS.454..457P, 2015ApJ...807...16L}.
+If the clustered bursts are typical of the FRB population, then wide, shallow surveys are the preferred strategy for blind detection of FRBs.
 Also, since ``bursts predict bursts'', many short observations are more likely to detect an FRB than a single long observation of the same total length and all new FRB detections should be immediately and intensively followed up.
@@
 By detecting this burst from 1.2 to 3.5~GHz, we have demonstrated that some bursts have broad spectral structure.
-However, the energy of that burst was dominated by the VLA 3~GHz observing band and two other VLA bursts are undetected by Arecibo.
+However, the energy of that burst was dominated by the VLA 3~GHz observing band and three other VLA bursts are undetected by simultaneous observations at other telescopes.
 This demonstrates the burst spectra are poorly described by a power law with a single spectral index.
-Independently, we modelled dynamic spectra within the VLA 3~GHz band and show that most bursts can be characterized by a Gaussian envelope of width $\sim500$\ MHz.
+We also modelled dynamic spectra within the VLA 3~GHz band and show that most bursts can be characterized by a Gaussian envelope of width $\sim500$\ MHz.
 This modeling also shows that the apparent DM changes from burst to burst and that DM is biased above the long-term average measured at 1.4~GHz.

### 2017-05-19 repeater-vladata.tex
through cees comments

@@
 \author{C.~G.~Bassa}
-\affiliation{ASTRON, Netherlands Institute for Radio Astronomy, Postbus 2, 7990 AA, Dwingeloo, The Netherlands}
+\affiliation{ASTRON, The Netherlands Institute for Radio Astronomy, Postbus 2, NL-7990 AA, Dwingeloo, The Netherlands}
 
@@
 \author{J.~W.~T.~Hessels}
-\affiliation{ASTRON, Netherlands Institute for Radio Astronomy, Postbus 2, 7990 AA, Dwingeloo, The Netherlands}
+\affiliation{ASTRON, The Netherlands Institute for Radio Astronomy, Postbus 2, NL-7990 AA, Dwingeloo, The Netherlands}
 \affiliation{Anton Pannekoek Institute for Astronomy, University of Amsterdam, Science Park 904, 1098 XH Amsterdam, The Netherlands}
@@
 \author{D.~Michilli}
-\affiliation{ASTRON, Netherlands Institute for Radio Astronomy, Postbus 2, 7990 AA, Dwingeloo, The Netherlands}
+\affiliation{ASTRON, The Netherlands Institute for Radio Astronomy, Postbus 2, NL-7990 AA, Dwingeloo, The Netherlands}
 \affiliation{Anton Pannekoek Institute for Astronomy, University of Amsterdam, Science Park 904, 1098 XH Amsterdam, The Netherlands}
@@
 Of the nine bursts detected by the Very Large Array at 3~GHz, four had simultaneous observing coverage at other observatories.
-We use multi-observatory constraints and modeling of bursts seen only at 3~GHz to confirm earlier results showing that burst spectra are not well characterized by a power law.
+We use multi-observatory constraints and modeling of bursts seen only at 3~GHz to confirm earlier results showing that burst spectra are not well modeled by a power law.
 We find that burst spectra are characterized by a $\sim500$~MHz envelope and apparent radio energy as high as $10^{40}$\ erg.
@@
 This rate is broadly consistent with models of FRBs from young pulsars or magnetars born in superluminous supernovae or long gamma-ray bursts, if the typical FRB repeats on the order of $10^3$\ times during its lifetime.
+\end{abstract}
 
-\end{abstract}
+\keywords{stars: neutron, radio continuum: stars, techniques: interferometric, supernovae: general}
 
@@
 The largest measured DMs imply that FRBs originate outside of our Galaxy, potentially at cosmological distances, and are orders of magnitude more luminous than pulses from Galactic pulsars \citep{2013Sci...341...53T}.
-There are now 21 FRBs publicly known \footnote{See \url{http://www.astronomy.swin.edu.au/pulsar/frbcat}.} with dispersion measures (DMs) as high as 1600 pc cm$^{-3}$ and intrinsic temporal widths of order milliseconds.
+There are now 22 FRBs publicly known \footnote{See \url{http://www.astronomy.swin.edu.au/pulsar/frbcat} \citep{2016PASA...33...45P}.} with dispersion measures (DMs) as high as 1600 pc cm$^{-3}$ and intrinsic temporal widths of order milliseconds.
 Both their energetics and distance have inspired a wide variety of models and astrophysical applications \citep[e.g.,][]{2014ApJ...780L..33M, 2014ApJ...797...70K, 2015MNRAS.450L..71F, 2016MNRAS.458L..19C, 2016MNRAS.457..232C, 2016MNRAS.462L..16P}.
@@
 
-Beginning in August of 2015 (MJD 57623), we made the first of nine detections of \frb\ with the Karl G.\ Jansky Very Large Array \citep[VLA;][]{LOC} and localized it with a precision of 0.1\arcsec.
-Deep optical observing with the Gemini Observatory associated the FRB with a host galaxy at $z=0.193$\ \citep{OPT} and the European VLBI Network detected four more bursts to localize the source with a precision of 0.01\arcsec, four orders of magnitude better than any other FRB \citep[precision of $\sim40$\ pc in linear distance;][]{EVN}.
+Beginning in August 2016 (MJD 57623), we made the first of nine detections of \frb\ with the Karl G.\ Jansky Very Large Array \citep[VLA;][]{LOC} and localized it with a precision of 0\farcs1.
+Deep optical observations with the Gemini Observatory associated the FRB with a host galaxy at $z=0.193$\ \citep{OPT} and the European VLBI Network detected four more bursts to localize the source with a precision of 0.01\arcsec, four orders of magnitude better than any other FRB \citep[precision of $\sim40$\ pc in linear distance;][]{EVN}.
 The lookback and luminosity distances for \frb\ are 746 and 972 Mpc, respectively, assuming a concordance cosmology with parameters given by \citet{2016A&A...594A..13P}.
@@
 The association of \frb\ with a compact, persistent radio source is consistent with bursts coming from a young magnetar that powers a luminous pulsar wind nebula \citep{2017arXiv170104815K}.
-At the same time, \frb\ is found in a low-metallicity dwarf galaxy \citep{OPT, 2017arXiv170102370M}, which was not predicted by origin models that scale with stellar mass or star formation \citep{2017arXiv170400022N}.
+At the same time, \frb\ is found in a low-metallicity dwarf galaxy \citep{OPT}, which was not predicted by origin models that scale with stellar mass or star formation \citep{2017arXiv170400022N}.
 These galaxies are the preferred environment for long GRBs and Type-I superluminous supernovae (LGRB and SLSN-I, respectively), which have been suggested are signatures of the magnetar birth \citep{2008AJ....135.1136M, 2014ApJ...787..138L}.
@@
 Parameters such as integrated flux density, S/N, and Stokes V were measured from the burst properties integrated in frequency.
-Stokes V values were estimated from the dual-circular feeds as $(RR-LL)/(RR+LL)\approx3\%$, which is comparble to the systematic error expected from beam squint at this location in the primary beam \footnote{See EVLA memo \#195 at \url{https://library.nrao.edu/public/memos/evla/EVLAM_195.pdf}.}.
+Stokes V values were estimated from the dual-circular feeds as $(RR-LL)/(RR+LL)\approx3\%$, which is comparable to the systematic error expected from beam squint at this location in the primary beam \footnote{See EVLA memo \#195 at \url{https://library.nrao.edu/public/memos/evla/EVLAM_195.pdf}.}.
 Given that systematic effects dominate the apparent circular polarization, this observation limits the fractional circular polarization to less than 3\%.
@@
 The dynamic spectra were modeled prior to dispersion correction.
-The spectral structure was modeled as a broad Gaussian envelope as a function of channel ``ch'' as:
+The spectral structure was modeled as a broad Gaussian envelope as:
 \begin{equation}
-G(\rm{ch}) = \frac{\rm{amp}}{\sqrt{2\pi}} \exp{\left[-\frac{1}{2} \left(\frac{\rm{ch} - \rm{center}}{\sigma_{ch}}\right)^2\right]}
+G(\nu) = \frac{\rm{A}}{\sqrt{2\pi} \sigma} \exp{\left[-\frac{1}{2} \left(\frac{\nu - \nu_0}{\sigma}\right)^2\right]}
 \end{equation}
-\noindent where ``amp'' is in mJy per 5~ms integration, ``center'' is the Gaussian center channel, and $\sigma_{ch}$\ is its width.
+\noindent where ``A'' is in mJy per 5~ms integration, $\nu_0$\ is the Gaussian center frequency, and $\sigma$\ is its width.
 The arrival time was modeled with a cold plasma dispersion law with the arrival time in units of integrations of:
 \begin{equation}
-\rm{i} (\rm{ch}) = \rm{i0} + 4.1488\times10^{-3}\ \rm{DM} \left[f(\rm{ch})^{-2} - f(\rm{ch0})^{-2}\right]/(5 \rm{ms})
+\rm{i} (\nu) = \rm{i0} + 4.1488\times10^{-3}\ \rm{DM} \left(\nu^{-2} - \nu_0^{-2}\right)/(5 \rm{ms})
 \end{equation}
-\noindent where ``i0'' is the arrival time at the highest frequency, ``ch0'', and function ``f'' maps the channel to a frequency in units of GHz.
+\noindent where ``i0'' is the arrival integration at the highest frequency and $\nu$\ is in units of GHz.
 Finally, the pulses were assumed to have an intrinsically square temporal width (parameter $W_{int}$).
-This 6-parameter model defined the intrinsic signal that was then distributed over a fixed time-frequency observing grid.
+These 6 parameters defined the intrinsic signal that was then distributed over a fixed time-frequency observing grid.
 
@@
 \begin{equation}
-E_{\rm{int}} = (\rm{amp}\ 5\ \rm{ms}) ( \sigma_{ch}\ 2.355 4\ \rm{MHz}) 10^{-23} (4\pi L_d^2)\ \rm{erg}
+E_{\rm{int}} = (\rm{A}\ 5\ \rm{ms}) ( \sigma_{ch}\ 2.355 4\ \rm{MHz}) 10^{-23} (4\pi L_d^2)\ \rm{erg}
 \end{equation}
-\noindent where the first term represents the burst fluence, the second term represents the integral of the burst spectrum, and $L_d$\ is the luminosity distance to the source.
+\noindent where the first term represents the burst fluence, the second term represents the integral of the burst spectrum, 2.355 scales $\sigma$\ to FWHM, and $L_d$\ is the luminosity distance to the source.
 
@@
 
-After correcting for barycentric and typical dispersion delays, the burst spectra at the VLA and at Arecibo show a residual temporal drift.
+After correcting for barycentric and typical dispersion delays, the VLA+AO burst spectrum has a residual temporal drift.
 This drift can be interpreted as an excess DM, but contemporaneous observations at 1.4~GHz measured a significantly lower DM (560.5 pc cm$^{-3}$; Hessels et al, in prep).
@@
 \section*{Acknowledgements}
+We thank the VLA staff for their support of \rf\ development and Liam Connor for useful feedback.
+We acknowledge partial support from the Research Corporation for Scientific Advancement (RCSA) for participation in the meeting Fast Radio Bursts: New Probes of Fundamental Physics and Cosmology at the Aspen Center for Physics (February 12-17, 2017).
+
 % observatories
@@
 CJL is supported by the University of California Office of the President under Lab Fees Research Program Award 237863 and NSF award 1611606. MAM is supported by NSF award 1458952. 
+JWTH and CGB acknowledge support from the European Research Council under the European Union's Seventh Framework Programme (FP/2007-2013) / ERC Grant Agreement nr.\ 337062 (DRAGNET; PI Hessels).
 KPM's research is supported by the Oxford Centre for Astrophysical Surveys which is funded through the Hintze Family Charitable Foundation.
@@
 
-We thank the VLA staff for their support of \rf\ development and Liam Connor for useful feedback.
-We acknowledge partial support from the Research Corporation for Scientific Advancement (RCSA) for participation in the meeting Fast Radio Bursts: New Probes of Fundamental Physics and Cosmology at the Aspen Center for Physics (February 12-17, 2017).
+\facility{EVLA, Arecibo, Effelsberg, LWA, AMI}
 

### 2017-05-21 repeater-vladata.tex
changed gaussian norm in equation
final run of notebooks

@@
 The VLA observations underresolve the pulses in time, so to compare these values, we assume a typical pulse width of 2~ms.
-Under this assumption, the VLA and Arecibo integrated flux densities are $278\pm13$\ and $64\pm2$\ mJy at 3 and 1.4~GHz, respectively.
-Assuming a power law flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha=1.9$.
+Under this assumption, the VLA and Arecibo integrated flux densities are $278\pm13$\ and $57\pm2$\ mJy at 3 and 1.4~GHz, respectively.
+Assuming a power law flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha=2.1$.
 This is inconsistent with the spectral index limit implied by the Effelsberg nondetection at 4.5~GHz ($\alpha<-1.7$\ for a 2~ms burst and $5\sigma$ limit).
@@
 Two Arecibo nondetections and two Effelsberg nondetections of VLA bursts place mutually inconsistent lower and upper limits on the spectral index.
-The Arecibo and Effelsberg upper limits at 1.4 and 4.5~GHz, respectively, limit all burst spectral indices $\alpha_{1.4/3}>+4.8$ and $\alpha_{3/4.5}<-2.7$.
+The Arecibo and Effelsberg upper limits at 1.4 and 4.5~GHz, respectively, limit all burst spectral indices $\alpha_{1.4/3}>+4.9$ and $\alpha_{3/4.5}<-2.7$.
 These are consistent with limits from the LWA1 and AMI-LA, which require $\alpha_{0.07/3}>-2.4$\ and $\alpha_{3/15}<1.5$ for bursts on MJD 57643 and 57649 (the brightest VLA bursts with observing coverage), respectively.
@@
 \begin{equation}
-G(\nu) = \frac{\rm{A}}{\sqrt{2\pi} \sigma} \exp{\left[-\frac{1}{2} \left(\frac{\nu - \nu_0}{\sigma}\right)^2\right]}
+G(\nu) = \rm{A} \exp{\left[-\frac{1}{2} \left(\frac{\nu - \nu_0}{\sigma}\right)^2\right]}
 \end{equation}

### 2017-05-21 repeater-vladata.tex
through all comments but jason

@@
 \affiliation{Centre for Astrophysical Surveys, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford OX1 3RH, UK}
+
+\author{K.~Gourdji}
+\affiliation{Anton Pannekoek Institute for Astronomy, University of Amsterdam, Science Park 904, 1098 XH Amsterdam, The Netherlands}
 
@@
 At the same time, \frb\ is found in a low-metallicity dwarf galaxy \citep{OPT}, which was not predicted by origin models that scale with stellar mass or star formation \citep{2017arXiv170400022N}.
-These galaxies are the preferred environment for long GRBs and Type-I superluminous supernovae (LGRB and SLSN-I, respectively), which have been suggested are signatures of the magnetar birth \citep{2008AJ....135.1136M, 2014ApJ...787..138L}.
+These galaxies are the preferred environment for long GRBs and Type-I superluminous supernovae (LGRB and SLSN-I, respectively), which have been suggested are signatures of magnetar birth \citep{2008AJ....135.1136M, 2014ApJ...787..138L}.
 
@@
 In Section \ref{sec:obs}, we describe the multi-telescope observing campaign and a refined analysis of the nine VLA bursts.
-Section \ref{sec:res} presents the first spectrum of an FRB simultaneously detected at multiple telescopes and confirm that burst spectra cannot be modeled with a single spectral index.
+Section \ref{sec:res} presents the first spectrum of an FRB simultaneously detected at multiple telescopes, confirming that burst spectra cannot be modeled with a single spectral index.
 We then model the dynamic spectra to characterize the burst spectra, energies, and dispersion properties.
-Section \ref{sec:disc} discusses the properties of \frb\ bursts and its impact on inferences about the birth rate of FRB sources and strategies to find and/or localize new FRBs.
+Section \ref{sec:disc} discusses the properties of \frb\ bursts and their impact on inferences about the birth rate of FRB sources and strategies to find and/or localize new FRBs.
 
@@
 The dispersion smearing across a channel is $\sim1.7$, 0.7, and 0.2~ms in the same respective bands.
-The 3~GHz data were recorded data in eight spectral windows with 32 channels each and had sensitivity of 5~mJy in 5~ms ($1\sigma$).
+The 3~GHz data were recorded in eight spectral windows with 32 channels each and had a sensitivity of 5~mJy in 5~ms ($1\sigma$).
 
@@
 The observational frequency range was 1.15 to 1.73~GHz and frequency resolution was 1.5625~MHz, which has a typical sensitivity of 2~mJy in 2~ms ($1\sigma$).
-We recorded total full Stokes polarization intensity spectra with a time resolution of 10.24~$\mu$s.
+We recorded intnsities of the each of the two orthogonal linear polarization signals and their cross product.
+Full Stokes polarization intensity spectra can then be generated with a time resolution of 10.24~$\mu$s.
 Each frequency channel was coherently dedispersed to 557~pc cm$^{-3}$, significantly reducing intra-channel dispersion smearing.
@@
 The LWA1 observations were automatically scheduled through the Heuristic Automation for LWA1 (HAL) system.
-Briefly, the HAL system receives messages via the internet that signal the start of a VLA observation.
+Briefly, the HAL system receives messages via the internet that signals the start of a VLA observation.
 If the source is visible and there are no high priority LWA1 observations scheduled, the HAL system automatically generates an observing schedule, re-configures the telescope, and alerts the observatory staff of the change.
@@
 
-No dispersed pulses were found with significance greater than $10\sigma$\, equivalent to a flux density limit of $\sim60$\ Jy for a width of 160~ms.
+No dispersed pulses were found with significance greater than $10\sigma$, equivalent to a flux density limit of $\sim60$\ Jy for a width of 160~ms.
 The system equivalent flux density does not change much between the two windows.
@@
 In total, four of the VLA bursts had simultaneous observing coverage with either Arecibo, Effelsberg, LWA1, or AMI-LA.
-Two of the VLA bursts had simultaneous observing coverage by all four observatories, including the burst detected by Arecibo (Figure \ref{fig:sched}).
+Two of the VLA bursts had simultaneous observing coverage by all four observatories, including the burst detected by Arecibo.
 
@@
 Two clusters of samples are identified for this burst: one narrow, low-DM and one wide, high-DM.
-Assuming that the model is appropriate, this implies that the burst can be decomposed into two subbursts.
+This shows that the model is not appropriate for this burst and could indicate that the burst can be decomposed into two subbursts.
 
@@
 They are most likely spectral variations from diffractive interstellar scintillations that, as noted previously, have characteristic frequency widths slightly larger than the 4~MHz channel bandwidth.
-Scintillation variations are multiplicative and have a one-sided exponential probability distributino function that can yield occasional large-amplitude ``scintles'' that are several times the mean scintle amplitude of unity.
+Scintillation variations are multiplicative and have a one-sided exponential probability distribution function that can yield occasional large-amplitude ``scintles'' that are several times the mean scintle amplitude of unity.
 
@@
 Lensing amplifications have a complicated frequency dependence that includes spikes, plateaus, and troughs.
-The simultaneous detection of burst MJD 57648 with both Arecibo (L band) and the VLA (S band up to 3.2~GHz) suggests requires a focal frequency $\gtrsim 3.2$ GHz and sufficient amplification in both bands.
+The simultaneous detection of burst MJD 57648 with both Arecibo (L band) and the VLA (S band up to 3.2~GHz) requires a focal frequency $\gtrsim 3.2$ GHz and sufficient amplification in both bands.
 
@@
 However, the temporal distribution of VLA detections alone shows that the \frb\ burst rate is significantly correlated on short timescales.
-That is, detecting a burst predicts that you are more likely to find another burst soon thereafter and not detecting a burst predicts you will likely not detect another burst soon thereafter.
+That is, detecting a burst implies a higher likelihood of detecting another burst soon thereafter, and not detecting a burst also implies a higher likelihood of not detecting another burst soon thereafter.
 
@@
 Comparing the FRB rate to these rates implies that FRB-emitting sources can be generated in LGRBs and SLSN-I if FRBs repeat $5\times10^2$\ and $5\times10^3$\ times\footnote{\citet{2017arXiv170400022N} provide a similar estimate of FRB birth rate and reach a similar conclusion.}, respectively (assuming burst energies of $\sim10^{40}$\ erg).
-\citet{2017arXiv170102370M} use the young magnetar model for FRBs to calculate the maximum number of bursts that can be powered its magnetic field as $\approx300$.
+\citet{2017arXiv170102370M} use the young magnetar model for FRBs to calculate the maximum number of bursts that can be powered by its magnetic field as $\approx300$.
 Assuming this model for FRBs, LGRBs, and SLSN-I, the rate comparison suggest that the LGRB rate is most consistent with the FRB rate, although there is significant room for adjustment in the models and rate estimate.

### 2017-05-21 timeline.py

@@ -23,7 +23,8 @@ obsdate = list(map(lambda od: datetime.datetime.strptime(od, "%Y-%m-%d"), ymds))
 
 # Define an offset and symbol type for each telescope
 telescopes = ['LWA', 'Arecibo', 'VLA', 'Effelsberg', 'AMI-LA']
-offs = [2, 4, 3, 1, 0]
+#offs = [2, 4, 3, 1, 0]
+offs = [4, 3, 2, 1, 0]
 offset = dict(zip(telescopes, offs))
 
 if obsdate[0].year == 2015:
@@ -107,10 +108,10 @@ for ax in axs:
 # boxes for simultaneous coverage of VLA bursts
 for ax in axs:
     if obsdate[0].year == 2016:
-        axhspan(0.1, 2.8, 0.657, 0.657, fill=False, linestyle='dashed') # 57643
-        axhspan(0.1, 3.9, 0.718, 0.718, fill=False, linestyle='dashed') # 57645
+        axhspan(0.1, 1.8, 0.657, 0.657, fill=False, linestyle='dashed') # 57643
+        axhspan(0.1, 2.8, 0.718, 0.718, fill=False, linestyle='dashed') # 57645
         axhspan(0.1, 3.9, 0.813, 0.813, fill=False, linestyle='dashed') # 57648 57649
-        axhspan(3.1, 3.9, 0.813, 0.813, fill=False, lw=3, linestyle='solid') # 57648 57649
+        axhspan(2.2, 2.8, 0.813, 0.813, fill=False, lw=3, linestyle='solid') # 57648 57649
         axhspan(0.1, 3.9, 0.844, 0.844, fill=False, linestyle='dashed') # 57648 57649
         ax.set_yticks( [0, 1, 2, 3] )
     else:

### 2017-05-21 repeater-vladata.tex
mostly through jason comments.

@@
 \affiliation{Arecibo Observatory, HC3 Box 53995, Arecibo, PR 00612, USA}
-\affiliation{Max-Planck-Institut f\"ur Radioastronomie, Auf dem H\"ugel 69, D-53121 Bonn, Germany}
 
@@
 We present results of the coordinated observing campaign that made the first subarcsecond localization of a Fast Radio Burst, \frb.
-During this campaign, we made the first detection of an FRB burst by multiple telescopes: the VLA at 3~GHz and the Arecibo Observatory at 1.4~GHz.
+During this campaign, we made the first simultaneous detection of an FRB burst by multiple telescopes: the VLA at 3~GHz and the Arecibo Observatory at 1.4~GHz.
 Of the nine bursts detected by the Very Large Array at 3~GHz, four had simultaneous observing coverage at other observatories.
@@
 We find that burst spectra are characterized by a $\sim500$~MHz envelope and apparent radio energy as high as $10^{40}$\ erg.
-We measure significant changes in the apparent dispersion between bursts that can be attributed to frequency-dependent profiles or some other intrinsic burst structure that adds a random error to the estimate of DM by up to 1\%.
+We measure significant changes in the apparent dispersion between bursts that can be attributed to frequency-dependent profiles or some other intrinsic burst structure that adds a systematic error to the estimate of DM by up to 1\%.
 We use \frb\ as a prototype of the FRB class to estimate a volumetric birth rate of FRB sources $R_{\rm{FRB}} \approx 5\times10^{-5}/N_r$\ Mpc$^{-3}$\ yr$^{-1}$, where $N_r$\ is the number of bursts per source over its lifetime.
@@
 
-Fast Radio Bursts (FRBs) were discovered ten years ago with the detection of a millisecond-duration radio transient with an anomalously high dispersion measure \citep{2007Sci...318..777L}.
-The largest measured DMs imply that FRBs originate outside of our Galaxy, potentially at cosmological distances, and are orders of magnitude more luminous than pulses from Galactic pulsars \citep{2013Sci...341...53T}.
-There are now 22 FRBs publicly known \footnote{See \url{http://www.astronomy.swin.edu.au/pulsar/frbcat} \citep{2016PASA...33...45P}.} with dispersion measures (DMs) as high as 1600 pc cm$^{-3}$ and intrinsic temporal widths of order milliseconds.
+Fast Radio Bursts (FRBs) were discovered ten years ago with the detection of a millisecond-duration radio transient with an anomalously high dispersion measure \citep[DM;][]{2007Sci...318..777L}.
+The large DMs imply that FRBs originate outside of our Galaxy, potentially at cosmological distances, and are orders of magnitude more luminous than pulses from Galactic pulsars \citep{2013Sci...341...53T}.
+There are now 22 FRBs publicly known \footnote{See \url{http://www.astronomy.swin.edu.au/pulsar/frbcat} \citep{2016PASA...33...45P}.} with DMs as high as 1600 pc cm$^{-3}$ and temporal widths of order milliseconds.
 Both their energetics and distance have inspired a wide variety of models and astrophysical applications \citep[e.g.,][]{2014ApJ...780L..33M, 2014ApJ...797...70K, 2015MNRAS.450L..71F, 2016MNRAS.458L..19C, 2016MNRAS.457..232C, 2016MNRAS.462L..16P}.
@@
 This paper is part of a series based on the first localization of an FRB and its unambiguous association to an extragalactic host \citep{LOC, OPT, EVN}.
-\frb, also known as the ``repeating FRB'', was discovered \citep{2014ApJ...790..101S} in data acquired in 2012 as part of the PALFA survey of the Arecibo Observatory \citep{2006ApJ...637..446C}.
+\frb, also known as the ``repeating FRB'', was discovered \citep{2014ApJ...790..101S} in data acquired in 2012 as part of the PALFA survey of the Arecibo Observatory \citep{2006ApJ...637..446C, lazarus}.
 In mid 2015, new Arecibo observations revealed a series of bursts at a similar DM and sky position that rules out cataclysmic models for this source \citep{2016Natur.531..202S}.
@@
 The lookback and luminosity distances for \frb\ are 746 and 972 Mpc, respectively, assuming a concordance cosmology with parameters given by \citet{2016A&A...594A..13P}.
-If \frb\ is representative of all FRBs, then we should expect them to be useful as probes of the intergalactic medium and their host galaxies.
+If \frb\ is representative of all FRBs, then we should expect them to be useful as probes of the intergalactic medium and their host galaxies \citep{2015MNRAS.451.3278M}.
 Thus, the confirmation of a cosmological distance for \frb\ has begun to fulfil the promise implied by the first FRB detection.
@@
 At the same time, \frb\ is found in a low-metallicity dwarf galaxy \citep{OPT}, which was not predicted by origin models that scale with stellar mass or star formation \citep{2017arXiv170400022N}.
-These galaxies are the preferred environment for long GRBs and Type-I superluminous supernovae (LGRB and SLSN-I, respectively), which have been suggested are signatures of magnetar birth \citep{2008AJ....135.1136M, 2014ApJ...787..138L}.
+These galaxies are the preferred environment for long GRBs and hydrogen-poor superluminous supernovae (LGRB and SLSN-I, respectively), which have been suggested are signatures of magnetar birth \citep{2008AJ....135.1136M, 2014ApJ...787..138L}.
 
@@
 \enddata
-\tablecomments{Times are in UT. Frequency is the approximate center of the bandwidth.}
+\tablecomments{Times are in UT. Duration includes overhead, which is typically 15\%. Frequency is the approximate center of the bandwidth.}
 \tablenotetext{a}{Arecibo coverage at 1.4~GHz.}
@@
 The sensitivity in these observations was about 28 mJy in 2 ms ($1\sigma$), which is two times worse than the full-bandwidth value.
-No burst was detected in either observation.
+No burst was detected in either of the two observations that were simultaneous with a VLA burst detection.
 
@@
 
-The LWA1 observations consisted of single phased-array beam centered on the location of \frb\ with two 4096-channel spectral windows spanning frequencies from 52.2--71.8~MHz and 68.2--87.8~MHz.
+The LWA1 observations consisted of a single phased-array beam centered on the location of \frb\ with two 4096-channel spectral windows spanning frequencies from 52.2--71.8~MHz and 68.2--87.8~MHz.
 The observations were taken in a spectrometer mode with a channel size of 4.8~kHz and a sample time of 160~ms.
@@
 
-We observed \frb\ with AMI-LA for 3 hours each on four epochs starting at MJDs 57638, 57643, 57645, 57646, 57648, and 57649.
+We observed \frb\ with AMI-LA for 3 hours each on six epochs starting at MJDs 57638, 57643, 57645, 57646, 57648, and 57649.
 Observations were made with the new digital correlator having 4096 channels across a 5~GHz bandwidth between 13--18~GHz with a 1~s integration time.
@@
 
-To generate the multi-telescope dynamic spectrum, the VLA data were resampled to the Arecibo temporal grid after correcting for barycentric and dispersion measure offsets.
-We assumed a DM of 560.5 pc cm$^{-3}$ (Hessels et al., in prep) to calculate a dispersion delay of 189 and 734~ms from infinite frequency to the top of the VLA and Arecibo bands, respectively.
+To generate the multi-telescope dynamic spectrum, the VLA and Arecibo data were resampled to the same temporal grid relative to the start time of the Arecibo data.
+We corrected for barycentric and dispersion measure offsets by assuming a DM of 560.5 pc cm$^{-3}$ (Hessels et al., in prep).
+The dispersion delay was 189 and 734~ms from infinite frequency to the top of the VLA and Arecibo bands, respectively.
 An error in the DM of 1 pc cm$^{-3}$\ corresponds to a delay time correction error of 0.3 and 1.4~ms for the VLA and Arecibo bands, respectively.
@@
  \includegraphics[trim=250 400 250 80, clip, width=\columnwidth]{aovla_spec.pdf}
- \caption{Composite dynamic specrum for the burst from \frb\ on MJD 57648 with data from the VLA and Arecibo observatories.
+ \caption{Composite dynamic spectrum for the burst from \frb\ on MJD 57648 with data from the VLA and Arecibo observatories.
 The time axis is measured in milliseconds relative to MJD 57648.437788874842 with times corrected to the barycenter and infinite frequency (assuming DM$=560.5$\ pc $^{-3}$).
@@
 The burst on MJD 57648 was detected with VLA and Arecibo with significances of 25$\sigma$\ and 39$\sigma$, which corresponds to peak flux densities in 5~ms of $111\pm5$\ mJy and $14\pm0.4$\ mJy at 3 and 1.4~GHz, respectively.
-The VLA observations underresolve the pulses in time, so to compare these values, we assume a typical pulse width of 2~ms.
+The VLA observations under-resolve the pulses in time, so to compare these values, we assume a typical pulse width of 2~ms.
 Under this assumption, the VLA and Arecibo integrated flux densities are $278\pm13$\ and $57\pm2$\ mJy at 3 and 1.4~GHz, respectively.
@@
 \end{tabular}
-\tablecomments{$S_{\rm{V}}$ is the measured circular polarization of the burst, which dominated by systematic effects. All error ranges represent 68\% confidence intervals.}
-\tablenotetext{a}{Simultaneously observed by either Arecibo, Effelsberg, LWA1, or AMI-LA.}
+\tablecomments{Burst times are topocentric at the VLA at 3.5~GHz.
+$S_{\rm{V}}$ is the measured circular polarization of the burst, which dominated by systematic effects.
+All error ranges represent 68\% confidence intervals.}
+\tablenotetext{a}{Simultaneously observing coverage with either Arecibo, Effelsberg, LWA1, or AMI-LA.}
 \tablenotetext{b}{Detected simultaneously with Arecibo.}
@@
 Figure \ref{fig:spec} shows that the Stokes I spectra are generally characterized by a broad, Gaussian shape with inter-channel modulation as high as 100\%.
-Diffractive scintillation from the Milky Way has a typical bandwidth of 7~MHz along this line of sight \citep{2002astro.ph..7156C}, which is similar to the channel size of 4~MHz.
+Diffractive scintillation from the Milky Way has a typical bandwidth of 7~MHz at a reference frequency of 3~GHz along this line of sight \citep{2002astro.ph..7156C}, which is similar to the channel size of 4~MHz.
 The burst energy is calculated from the flux density in 5~ms and integrating over the optimal Gaussian spectral model.
@@
 In all cases, the typical burst spectrum has a FWHM of approximately 500~MHz.
-This confirms previous reports based on Arecibo and GBT data \citep{2016arXiv160308880S} with the wider (1~GHz) VLA bandwidth and extends this phenomenon to 3~GHz.
+This confirms previous reports based on Arecibo and GBT data \citep{2016Natur.531..202S, 2016arXiv160308880S} with the wider (1~GHz) VLA bandwidth and extends this phenomenon to 3~GHz.
 
@@
 The effect of a finite pulse width is visible as the burst moves from one integration to the next, even for widths narrower than the integration time of 5~ms.
-Table \ref{tab:spec} shows that the typical burst width is measured as $2\pm0.5$~ms (68\% confidence interval); the inter-channel dispersion smearing ranges from 0.4 to 1.1~ms across this band.
+Table \ref{tab:spec} shows that the typical burst width is measured as $2\pm0.5$~ms (68\% confidence interval); the intra-channel dispersion smearing ranges from 0.4 to 1.1~ms across this band.
 The brightest burst (on MJD 57633.68) is modeled with a temporal width of $2.05\pm0.02$~ms and its arrival time is measured with a precision of $\sim50~\mu$s.
 Note that these errors are only accurate to the degree that the model represents the data.
-One potential bias in the model is that we do not model scintillation effects.
+One potential bias in the model is that we do not model scintillation effects or frequency-dependent temporal width.
 
@@
 Furthermore, several of the 95\% confidence intervals in DM are not consistent with this mean nor each other, which suggests that some burst-specific property can bias the measured DM.
-The variation in DM observed by the VLA at 3~GHz is similar to that reported for Arecibo observations of \frb\ in \citet{2016arXiv160308880S}.
+The variation in DM observed by the VLA at 3~GHz is similar to that reported for Arecibo observations of \frb\ in \citet{2016Natur.531..202S, 2016arXiv160308880S}.
 
@@
 There is a weak correlation between burst width and apparent DM.
+It is not clear that whether this correlation is driven by intrinsic structure or unmodeled effects, such as frequency-dependent temporal width.
 A change in width of $\sim1$~ms correlates with a change in apparent DM of approximately $5$~pc cm$^{-3}$.
@@
 These do not appear to be caused by terrestrial interference.
-They are most likely spectral variations from diffractive interstellar scintillations that, as noted previously, have characteristic frequency widths slightly larger than the 4~MHz channel bandwidth.
+They are most likely spectral variations from diffractive Galactic scintillations that, as noted previously, have characteristic frequency widths slightly larger than the 4~MHz channel bandwidth.
 Scintillation variations are multiplicative and have a one-sided exponential probability distribution function that can yield occasional large-amplitude ``scintles'' that are several times the mean scintle amplitude of unity.
@@
 Some VLA burst spectra seem to be contained by the 2.5 to 3.5~GHz band and most of them seem to have Gaussian envelopes that are well modeled by the emission within that band.
-Assuming that the Gaussian shape defines the full emission window, the integrated 3~GHz flux density can be converted to a total energy with no further assumptions about the burst spectral properties as:
+Assuming that the Gaussian shape defines the full emission window, the integrated 3~GHz flux density can be converted to a total isotropic energy with no further assumptions about the burst spectral properties as:
 \begin{equation}
@@
 \includegraphics[width=\columnwidth]{energy_disn.pdf}
-\caption{The cumulative burst energy distributions for the VLA, Arecibo, and GBT bursts are shown with dots connected by solid, dashed, and dotted lines, respectively.
+\caption{The cumulative burst isotropic energy distributions for the VLA, Arecibo, and GBT bursts are shown with dots connected by solid, dashed, and dotted lines, respectively.
 The Arecibo distribution is derived from the 11 1.4~GHz bursts reported in \citet{2016Natur.531..202S} and the GBT distribution is derived from the 5 1.4~GHz bursts reported in \citet{2016arXiv160308880S}.
@@
 We present the first simultaneous detection of an FRB with multiple telescopes and over frequencies from 1.2 to 3.5~GHz.
-The flux density of the Arecibo burst detected on MJD 57648 is an order of magntude less than that seen by the VLA.
+The flux density of the Arecibo burst detected on MJD 57648 is an order of magnitude less than that seen by the VLA.
 At the same time, three other bursts from \frb\ had similar observing coverage but were not detected simultaneously.
@@
 
-After correcting for barycentric and typical dispersion delays, the VLA+AO burst spectrum has a residual temporal drift.
+After correcting for barycentric and dispersion delays, the VLA+AO burst spectrum has a residual temporal drift.
 This drift can be interpreted as an excess DM, but contemporaneous observations at 1.4~GHz measured a significantly lower DM (560.5 pc cm$^{-3}$; Hessels et al, in prep).
 This excess DM is comparable to the burst-to-burst variation in DM within the whole sample of VLA 3~GHz bursts.
-This variation had been noted in earlier 1.4~GHz Arecibo observations of \frb\ \citep{2016arXiv160308880S}, but the VLA bursts demonstrate that this burst-specific DM is seen simltaneously from 1.4 to 3~GHz.
+This variation had been noted in earlier 1.4~GHz Arecibo observations of \frb\ \citep{2016Natur.531..202S
+, 2016arXiv160308880S}, but the VLA bursts demonstrate that this burst-specific DM is seen simultaneously from 1.4 to 3~GHz.
 
@@
 
-Our refined analysis shows that \frb\ has even higher isotropic energies than previously reported for \frb, reaching energies $E_{\rm{max}}\approx10^{40}$\ erg.
+Our refined analysis shows that \frb\ has isotropic energies as high as $E_{\rm{max}}\approx10^{40}$\ erg.
 While this emission is coherent and beamed, the apparent energy is larger than Galactic analogues such as the giant pulses from the Crab pulsar \citep[$\sim10^{35}$~erg, $T_{b,\rm{Crab}}\sim10^{41}$~K;][]{2003Natur.422..141H,2014PhRvD..89j3009K}.
-Radio bursts from \frb\ require either dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C} or strong amplification by propagation effects \citep{2017arXiv170306580C}.
+Radio bursts from \frb\ require either dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C} and/or strong amplification by propagation effects \citep{2017arXiv170306580C}.
 
@@
 All three energy distributions can be characterized as a power law in $dN/dE$ with slope $\sim-1.7$.
-This slope is seen even though the burst rate varies by almost an order of magnitude between observations and frequencies cover both 1.4 and 3~GHz bands.
+This slope is seen even though the burst rate varies by almost an order of magnitude between campaigns and the observing frequencies cover both 1.4 and 3~GHz bands.
 This suggests that the slope is related to the underlying physical process, rather than the burst detection rate at any given time.
@@
 New FRB discoveries have often surprised observers with their remarkable brightness \citep{2007Sci...318..777L, 2016arXiv161105758R}.
-When modeling the flux distribution as a power law, an isotropic distribution of sources will have a power law index, $\alpha$, of --1.5.
+When modeling the flux distribution as a power law, a uniform, isotropic distribution of sources will have a power law index, $\alpha$, of --1.5.
 Prior to the measurement of the first GRB redshift, deviations from this Euclidean distribution were used to infer their cosmological distribution \citep[e.g., the $V/V_{\rm{max}}$\ test;][]{1992ApJ...388L..45M, 1995ApJ...453...25F}.
@@
 Crudely, the volumetric rate of FRB sources can be defined as $R_{\rm{FRB}} = R_p /(N_r \Omega_b V (z))$, where $R_p$\ is the projected FRB rate, $N_r$\ is the number of bursts per source in a typical lifetime, $\Omega_b$\ is the beaming fraction, and $V(z)$\ is the comoving volume out to redshift $z$.
-The newest estimates of the projected FRB rate are $2\times10^3\ \rm{sky}^{-1} \rm{day}^{-1}$\ at high Galactic latitudes and flux densities brighter than 1~Jy~ms \citep{2016arXiv161100458L, 2016MNRAS.460L..30C, 2016MNRAS.455.2207R}.
-There is relatively little constraint on the beaming factor, but Galactic pulsars have beaming solid angle fractions on the order of 10\% \citep{1998MNRAS.298..625T}.
+The latest estimates of the projected FRB rate are $2\times10^3\ \rm{sky}^{-1} \rm{day}^{-1}$\ at high Galactic latitudes and flux densities brighter than 1~Jy~ms \citep{2016arXiv161100458L, 2016MNRAS.460L..30C, 2016MNRAS.455.2207R}.
+There is little constraint on the beaming factor, but Galactic pulsars have beaming solid angle fractions on the order of 10\% \citep{1998MNRAS.298..625T}.
 
 \frb\ has an absolute energy scale that can be used to estimate a horizon scale for the typical FRB survey sensitivity.
-At the typical Parkes survey parameters \citep[e.g.,][]{2016MNRAS.460L..30C}, a survey with a fluence limit of 1~Jy~ms can detect \frb\ at $z\approx1$.
+At the typical Parkes survey parameters \citep[e.g.,][]{2016MNRAS.460L..30C}, a survey with a fluence limit of 1~Jy~ms can detect \frb\ at $z\approx1$ (i.e., for isotropic energy of $\approx10^{40}$~erg).
 The distance inferred from the largest DMs observed \citep[$\sim1500$\ pc cm$^{-3}$;][]{2016MNRAS.460L..30C} is somewhat higher, but that likely overestimates distance since DM is expected to have significant contributions from the host galaxy and intervening galaxies \citep{OPT, 2014ApJ...780L..33M}.
@@
 
-Despite its many assumptions, this volumetric rate is more appropriate for comparison to rates used for other classes of transient.
+Despite its many assumptions, this volumetric birth rate is more appropriate for comparison to rates used for other classes of transient.
 The LGRB and SLSN-I rates are $10^{-7}$\ and $10^{-8}$\ Mpc$^{-3}$\ yr$^{-1}$, respectively \citep{2007ApJ...657L..73G,2012Sci...337..927G}.
-Comparing the FRB rate to these rates implies that FRB-emitting sources can be generated in LGRBs and SLSN-I if FRBs repeat $5\times10^2$\ and $5\times10^3$\ times\footnote{\citet{2017arXiv170400022N} provide a similar estimate of FRB birth rate and reach a similar conclusion.}, respectively (assuming burst energies of $\sim10^{40}$\ erg).
-\citet{2017arXiv170102370M} use the young magnetar model for FRBs to calculate the maximum number of bursts that can be powered by its magnetic field as $\approx300$.
-Assuming this model for FRBs, LGRBs, and SLSN-I, the rate comparison suggest that the LGRB rate is most consistent with the FRB rate, although there is significant room for adjustment in the models and rate estimate.
+Comparing the FRB rate to these rates implies that FRB-emitting sources can be generated in LGRBs and SLSN-I if FRBs repeat $5\times10^2$\ and $5\times10^3$\ times\footnote{\citet{2017arXiv170400022N} provide a similar estimate of FRB birth rate and reach a similar conclusion.}, respectively.
+This assumes isotropic burst energies of $\sim10^{40}$~erg or intrinsic energies of $\sim10^{39} (\Omega_b/0.1)$~erg.
+\citet{2017arXiv170102370M} use the young magnetar model for FRBs to calculate the maximum number of bursts that can be powered by its magnetic field as **$\approx3000 (0.1/\Omega_b)$.
+This rate comparison suggests that the SLSN-I rate is most consistent with the FRB rate, although there is significant room for adjustment in the models and rate estimate.
 
@@
 
-With a characteristic burst spectrum, we can estimate total (apparent) radio energy per burst.
+With a characteristic burst spectrum, we can estimate total isotropic radio energy per burst.
 The cumulative energy distribution is characterized by a power law in $dN/dE$ with slope of $\sim-1.7$.
@@
 We estimate a volumetric rate of FRB sources of $R_{\rm{FRB}} \approx 5\times10^{-5} (0.1/\Omega_b)$\ Mpc$^{-3}$\ yr$^{-1}$, which is appropriate for \frb-like burst energies of $10^{40}$\ erg that are detectable out to $z=1$.
-This rate is broadly consistent with models of FRBs from young pulsars or magnetars born in superluminous supernovae or long gamma-ray bursts, if the typical FRB repeats on the order of $10^3$\ times over its lifetime.
+This rate is broadly consistent with models of FRBs from young pulsars or magnetars born in SLSN-I or LGRB, if the typical FRB repeats on the order of $10^3$\ times over its lifetime.
 
@@
 CJL is supported by the University of California Office of the President under Lab Fees Research Program Award 237863 and NSF award 1611606. MAM is supported by NSF award 1458952. 
-JWTH and CGB acknowledge support from the European Research Council under the European Union's Seventh Framework Programme (FP/2007-2013) / ERC Grant Agreement nr.\ 337062 (DRAGNET; PI Hessels).
+JWTH, CGB, and DM acknowledge support from the European Research Council under the European Union's Seventh Framework Programme (FP/2007-2013) / ERC Grant Agreement nr.\ 337062 (DRAGNET; PI Hessels).
+JWTH also acknowledges funding from an NWO Vidi fellowship.
 KPM's research is supported by the Oxford Centre for Astrophysical Surveys which is funded through the Hintze Family Charitable Foundation.

### 2017-05-22 repeater-vladata.tex
shriharsh comments in

@@
 We use \frb\ as a prototype of the FRB class to estimate a volumetric birth rate of FRB sources $R_{\rm{FRB}} \approx 5\times10^{-5}/N_r$\ Mpc$^{-3}$\ yr$^{-1}$, where $N_r$\ is the number of bursts per source over its lifetime.
-This rate is broadly consistent with models of FRBs from young pulsars or magnetars born in superluminous supernovae or long gamma-ray bursts, if the typical FRB repeats on the order of $10^3$\ times during its lifetime.
+This rate is broadly consistent with models of FRBs from young pulsars or magnetars born in superluminous supernovae or long gamma-ray bursts, if the typical FRB repeats on the order of thousands of times during its lifetime.
 \end{abstract}
@@
 This paper is part of a series based on the first localization of an FRB and its unambiguous association to an extragalactic host \citep{LOC, OPT, EVN}.
-\frb, also known as the ``repeating FRB'', was discovered \citep{2014ApJ...790..101S} in data acquired in 2012 as part of the PALFA survey of the Arecibo Observatory \citep{2006ApJ...637..446C, lazarus}.
+\frb, also known as the ``repeating FRB'', was discovered \citep{2014ApJ...790..101S} in data acquired in 2012 as part of the PALFA survey of the Arecibo Observatory \citep{2006ApJ...637..446C, 2015ApJ...812...81L}.
 In mid 2015, new Arecibo observations revealed a series of bursts at a similar DM and sky position that rules out cataclysmic models for this source \citep{2016Natur.531..202S}.
@@
 
-Observations in August and September were searched by a prototype version of \rf\footnote{See \url{http://realfast.io} and \citep{2017AAS...22933002L}.}.
+Observations in August and September were searched by a prototype version of \rf\footnote{See \url{http://realfast.io} \citep{2017AAS...22933002L}.}.
 \rf\ is a real-time, fast imaging transient search system.
-The current prototype runs on CPU-based hardware that is normally dedicated to the VLA correlator; for this experiment, it runs the transient search pipeline software called \emph{rtpipe}\footnote{See \url{https://github.com/caseyjlaw/rtpipe} and \citet{2015ApJ...807...16L}.}.
+The current prototype runs on CPU-based hardware that is normally dedicated to the VLA correlator; for this experiment, it runs the transient search pipeline software called \emph{rtpipe}\footnote{See \url{https://github.com/caseyjlaw/rtpipe} \citep{2015ApJ...807...16L}.}.
 Images were formed for each integration with DMs of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$ and a time resampling grid of 5, 10, 20, 40, and 80 ms.
@@
 Parameters such as integrated flux density, S/N, and Stokes V were measured from the burst properties integrated in frequency.
-Stokes V values were estimated from the dual-circular feeds as $(RR-LL)/(RR+LL)\approx3\%$, which is comparable to the systematic error expected from beam squint at this location in the primary beam \footnote{See EVLA memo \#195 at \url{https://library.nrao.edu/public/memos/evla/EVLAM_195.pdf}.}.
+The circular polarization fraction (Stokes V/I) was estimated as $(RR-LL)/(RR+LL)\approx3\%$, which is comparable to the systematic error expected from beam squint at this location in the primary beam \footnote{See EVLA memo \#195 at \url{https://library.nrao.edu/public/memos/evla/EVLAM_195.pdf}.}.
 Given that systematic effects dominate the apparent circular polarization, this observation limits the fractional circular polarization to less than 3\%.
@@
 The VLA spectra are drawn from flux-calibrated, dedispersed 5~ms integrations.
-The Arecibo spectrum is drawn from a 2.7~ms window with 3.125~MHz channels and the flux scale is esimated using the radiometer equation.
-The solid line shown with VLA spectra is a best-fit Gaussian model found through modeling.
+The Arecibo spectrum is drawn from a 2.7~ms window with 3.125~MHz channels and the flux scale is estimated using the radiometer equation.
+The solid line shown with VLA spectra is a best-fit Gaussian model found through modeling; no comparable modeling is done for the Arecibo spectrum.
 The typical VLA flux density error per channel is 70~mJy, which is shown at the top right of each panel next to the MJD label.
@@
 The 3~GHz burst rate was much higher during the late-2016 campaign, $R=0.3\pm0.1$\ hour$^{-1}$.
+This confirms recent analysis of published bursts from \frb\ \citep{2017arXiv170504881O}.
 
@@
 \begin{equation}
-E_{\rm{int}} = (\rm{A}\ 5\ \rm{ms}) ( \sigma_{ch}\ 2.355 4\ \rm{MHz}) 10^{-23} (4\pi L_d^2)\ \rm{erg}
+E_{\rm{int}} = (\rm{A} \times 5\ \rm{ms}) ( 2.355 \sigma_{ch}\ \times 4\ \rm{MHz}) 10^{-23} (4\pi L_d^2)\ \rm{erg}
 \end{equation}
@@
 
-Figure \ref{fig:ed} shows the \frb\ burst energy cumulative distribution as seen by the VLA and calculated from prior observations by Arecibo and the Green Bank Telescope \citep{2016Natur.531..202S,2016arXiv160308880S}.
+Figure \ref{fig:ed} shows the \frb\ burst energy cumulative distribution as seen by the VLA and calculated from prior observations by Arecibo and the Green Bank Telescope \citep{2016Natur.531..202S, 2016arXiv160308880S}.
 The latter two energy distributions are scaled from the fluence by assuming that all burst energy is included by the observation.
@@
 This is consistent with the spectral structure observed within the 3~GHz VLA band, which is typically limited to a Gaussian envelope with width of roughly 500~MHz.
-This confirms earlier results at 1.4~GHz \citep{2016Natur.531..202S,2016arXiv160308880S} with a wider bandwidth and extends the presence of this phenomenon to 3~GHz.
+This confirms earlier results at 1.4~GHz \citep{2016Natur.531..202S, 2016arXiv160308880S} with a wider bandwidth and extends the presence of this phenomenon to 3~GHz.
 
@@
 This excess DM is comparable to the burst-to-burst variation in DM within the whole sample of VLA 3~GHz bursts.
-This variation had been noted in earlier 1.4~GHz Arecibo observations of \frb\ \citep{2016Natur.531..202S
-, 2016arXiv160308880S}, but the VLA bursts demonstrate that this burst-specific DM is seen simultaneously from 1.4 to 3~GHz.
+This variation had been noted in earlier 1.4~GHz Arecibo observations of \frb\ \citep{2016Natur.531..202S,2016arXiv160308880S}, but the VLA bursts demonstrate that this burst-specific DM is seen simultaneously from 1.4 to 3~GHz.
 
@@
 
-The clustering of burst times for the whole FRB population has been modeled as a ``red spectrum'' \citep{2016MNRAS.458L..89C}, while recent work has modeled \frb\ burst times with a modified Poisson distribution \citep{oppermann}.
+The clustering of burst times for the whole FRB population has been modeled as a ``red spectrum'' \citep{2016MNRAS.458L..89C}, while recent work has modeled \frb\ burst times with a modified Poisson distribution \citep{2017arXiv170504881O}.
 Both temporal models imply that existing observational constraints on repetition are weaker than expected from Poissonian statistics \citep{2015MNRAS.454..457P, 2015ApJ...807...16L}.
@@
 This assumes isotropic burst energies of $\sim10^{40}$~erg or intrinsic energies of $\sim10^{39} (\Omega_b/0.1)$~erg.
-\citet{2017arXiv170102370M} use the young magnetar model for FRBs to calculate the maximum number of bursts that can be powered by its magnetic field as **$\approx3000 (0.1/\Omega_b)$.
+\citet{2017arXiv170102370M} use the young magnetar model for FRBs to calculate the maximum number of bursts that can be powered by its magnetic field as $\approx3000 (0.1/\Omega_b)$.
 This rate comparison suggests that the SLSN-I rate is most consistent with the FRB rate, although there is significant room for adjustment in the models and rate estimate.
@@
 JWTH also acknowledges funding from an NWO Vidi fellowship.
+SPT acknowledges support from the McGill Astrophysics Fellowship.
 KPM's research is supported by the Oxford Centre for Astrophysical Surveys which is funded through the Hintze Family Charitable Foundation.

### 2017-07-14 referee_response.txt
bumping up the nondetection coverage

Responses start with ">>>"

==================

The authors should tag their DataVerse DOI with the \dataset mark up in AASTeX v6.0

http://journals.aas.org/authors/aastex/aasguide60.html#celestial_objects

Please also use the full references for the items noted under the \software command, e.g.

emcee (Foreman-Mackey et al. 2013)

>>> Done.

=======
Referee Report
Reviewer's Comments:
This paper presents a multi-year observing campaign with the VLA telescope to study the repeating pulses from FRB 121102. Many VLA observations were also simultaneous with observations at radio telescopes observing at other frequencies. In some cases pulses detected at the VLA were not detected at higher or lower frequencies and in one case a pulse was detected with both the VLA and the Arecibo Observatory and this information as well as the pulse spectra from the VLA can be used to constrain the emission properties of this source as well as a burst rate. This work is very interesting, and well-presented, and crucial for our understanding of FRB 121102 in specific, but also the possible properties of fast radio bursts in general.

I think this work is worthy of publication in the journal with moderate revision of the manuscript. Some moderate revision of the text is needed (see below) as well as some structural and conceptual changes. I have included my comments on the manuscript below with general large comments (1, 2, 3..) on the paper at the beginning, and major (A, B, C,...) and minor (i, ii, iii,...) comments per section.

General comments on the manuscript:

1. Throughout the text it is mentioned that this is the first simultaneous detection of an FRB pulse at multiple observatories, but I don't believe this is correct. The observations detailed in Marcote et al. 2017 include VLBI observations of individual pulses from FRB 121102 detected at different observatories. In that sense, this paper does not present the first simultaneous detection. Perhaps the authors mean first simultaneous detection at multiple radio frequencies, but if this is the case this statement should be revised throughout the manuscript.

>>> I do believe the VLA+AO burst is the first of its kind both as a multi-frequency and as a multi-telescope detection. I see two ways to show this:
>>> 1. The first VLA+Arecibo burst was detected on 17 September, while the bursts reported in Marcote et al were detected on 20 September.
>>> 2. Marcote et al was published simultaneously with Chatterjee et al; the latter paper made the first report of this coincident VLA+AO burst.
>>> I would prefer to keep the current wording.

2. While the simultaneous detection of an FRB pulse at multiple frequencies is indeed quite interesting I would argue that the _non-detections_ while observing with the VLA and other telescopes is also extremely important and stick out to me as a key result of this paper. This isn't well highlighted in the abstract or the text of the paper and throughout the manuscript these non-detections are not presented in a straightforward way. The observations are reported as "simultaneous coverage" without mention of detection or non-detection (although non-detection is implied). In a revised version of the manuscript it would be valuable to see these non-detections presented more centrally and directly -- see individual sections for locations where this would be particularly helpful to the reader.

>>> Thank you for helping highlight the most interesting part of the analysis. We will work to raise the profile of the nondetection results.

3. In the text it is written that the Arecibo data are recorded with full Stokes polarization intensity. A bright (39-sigma) pulse was detected at Arecibo in this observing mode but no pulse polarization information is presented here. If pulse polarization information is available for this burst it should absolutely be included in this paper! If for some reason the polarization could not be calibrated or cannot be presented here the reason should be included somewhere in the manuscript.

>>> There is indeed a lot of work to be done on the Arecibo data. That observing campaign is in fact ongoing and multiple students are working on it. We defer detailed Arecibo analysis for future work, as noted here as "Michilli et al, in prep". This paper focused largely on the VLA data analysis and the timing and spectral information derived from comparison to other observatories.

Abstract:

i. "simultaneous observing coverage at other observatories." : Please also mention that these observatories were observing at different radio frequencies and how many VLA pulses were detected and not detected at other observatories.

Introduction:

i. "22 FRBs" : Now 23 with the publication of the ASKAP detection

ii. $0\farcs1$ and $0.01\arcsec$ : Please check for consistency in the placement of the arcseconds symbol throughout the manuscript

Observations:

Figure 1: This figure is very busy and difficult to parse. I would suggest the following changes:
- Change the symbols for each observing epoch to the number of bursts detected in that observation (0, 1, 2, etc)
- Create two extra rows and plot the VLA observations at L-band, S-band, and C-band separately
- Next to the name of each telescope on the right hand side of the figure (or replacing the name of the telescope) provide the observing frequency, e.g. LWA (70 MHz), VLA (1.4 GHz), VLA (3 GHz), VLA (4.5 GHz), etc.
- Use circles to indicate overlapping frequency coverage and dispense with bold circles and dashed lines
- Use a solid line to indicate the observation where a burst was detected at both VLA and Arecibo

Table 1: All times should be in the format HH:MM:SS, e.g. 03:25:29
Table 1: Footnote ordering: Footnotes should be labeled in the order in which they appear, so footnote d should be relabeled as b and so on
Table 1: Footnote wording: This relates to comment #2 at the beginning of this report. I believe it would be better to label these as "detection" and "non-detection" since this is what is implied by "coverage" and the lack of a * icon indicating detection.

2.1 VLA:

A. It would be nice to see the details contained in paragraph 2 of this subsection (as well as the observing setup description paragraphs of other subsections) summarized in a table with information like center observing frequency, bandwidth, time resolution, frequency resolution, dispersion smearing, sensitivity, FWHM, etc.

i. "256 channels" : 256 frequency channels

ii. "prototype version of \textit{realfast}. \textit{realfast} is a" : prototype version of \textit{realfast}, a

iii. "The transient search starts ... and proceeds slower than real-time" : please state how much slower than real-time the search is. If this speed is RFI- or array configuration-dependent provide a range.

2.2 Arecibo:

i. Please include a citation for the PUPPI pulsar backend if there is one.

ii. "Three of those observations ... coverage of VLA bursts and one of those Arecibo observations detected the VLA burst" : This is unclear as it is currently written. It would be better to write up front how many simultaneous observations detected no coincident pulses and how many observations did.

2.3 Effelsberg:

i. Please include a citation for the S60mm receiver if there is one.

ii. Please provide the width of the frequency channels in the Effelsberg setup (in the text and in an observing details table).

2.4 LWA:

i. "Briefly, ..." : Remove this opening word.

ii. "signals" : signal

iii. "Two of the VLA ... had simultaneous coverage with the LWA1" : Here again please be clear about the non-detection with the LWA1.

iv. "up to 48 seconds" : What is the motivation for searching up to 48 seconds in width? Are there physical justifications for searching for such long duration signals in time?

2.5 AMI-LA:

i. "MJDs 57638, ... 57649." : Refer to Figure 1 here.

Results:

It would be nice to see an introductory paragraph before Section 3.1 detailing the main results that will be presented in the following sub-sections: How many VLA pulses were detected in total, how many of those were not detected at other observatories, how many of them were detected at other observatories, what kinds of frequency structure were observed etc. This is a long and complex section of the paper and a preamble might help to guide the reader through the upcoming interesting results.

3.1 Multi-Observatory Burst Spectrum:

Figure 2: Why plot from MJD 57648.437788874842? The justification behind this start time is not given in the text or the caption.
Figure 2: "DM = 560.5 pc $^{-3}$" : missing unit here

Figure 3: Make this figure a little bit bigger so it fills the available column space

3.2 VLA Bursts:

3.2.1 Spectrotemporal Modeling:

Equation 1: A is typically used for a unitless amplitude, but in this case is given in units of flux density. If this value is indeed meant to be the flux density of the pulse then $S$ should be used as the symbol for flux density instead of A.

A. Paragraph beginning "The parameters for the best model ... " : Your fits to the pulse spectra seem to indicate that all but two of the VLA burst detections are well-modeled by a Gaussian envelope completely contained within the 3 GHz band. How likely is this? It seems to be implying that 3 GHz was the perfect frequency at which to center your observations. While this seems fortunate it doesn't make immediate physical sense to me. I might have expected some uniformly broadband pulses, some with an envelope within your observing band, and some with an envelope that extends beyond the observing band, but you find that most are described by an entirely in-band envelope. Is this physical or could this be an artefact of the model fits you have applied to the data? If you believe that this is indeed an intrinsic effect I would like to see more discussion of the physical mechanism behind the very fortunate 3 GHz observing window.

Table 2: Footnote labeling: The labeling here is not consistent with the labeling used in Table 1.

i. "While most bursts are modeled ... into two subbursts." : This particular burst may be an outlier in this sample of bursts but it is not unique among the bursts detected from FRB 121102 which has many bursts that seem to be composed of interesting substructure. A sentence or two putting this particular pulse in that context would be useful.

Figure 4: Are each of the bursts plotted here dedispersed to the best-fit DM given in Table 2 or dedispersed to the best-fit DM of FRB 121102 of 560.5 pc/cm^3? If the former, what effect does it have on the spectrum of each pulse to force them all to a DM = 560.5 pc/cm^3? Is the structure you are seeing in the spectrum highly dependent on the DM fit?

3.2.2 Dispersion:

i. "There is a weak correlation between ... temporal width." : It would be useful information in this section if you could elaborate on how sensitive your observations are or aren't to substructure within each pulse that may be hindering DM fitting? For example, if there was a pulse with substructure within a single 5ms VLA time sample can you estimate the error this would propagate to the DM fit?

3.3 Temporal, Energy, and Brightness Distributions of Bursts:

i. For clarity, please label the rates at different observing frequencies in the text as $R_{3 GHZ}$ etc.

ii. Equation 3: Similar to Equation 1, A is given in units of flux density and should therefore be represented by the symbol $S$.

iii. dN/d logE : Elsewhere in the text this is written as dN/dE. Please be consistent in notation.

Figure 7: Please make this figure larger to fill the available column space. Axis labels and tick labels should be given in a larger font as well.

Discussion:

4.1 Burst Spectra:

A. I do not find the explanation or investigation here into the drastic DM change to be sufficient. The DM is changing (or being measured to change) by many units and disagrees with the best-fit DM at 1.4 GHz. This disagreement between 1.4 GHz and 3 GHz is either intrinsic or extrinsic (or both, I suppose). In the intrinsic case this is of enormous interest. Although an extrinsic explanation would be less physically interesting it would nonetheless provide some helpful answers. Paragraph 6 of this section gives some attention to this issue although it doesn't address the impact that some propagation effects might have on the pulse at different radio frequencies. Given the unique multi-radio-frequency aspect of this work, such a discussion would be valuable. An additional bit of text dedicated to this topic would be illuminating.

i. "We present the first ... to 3.5 GHz." : See comment #1 at the beginning of this report. Statements like these throughout the paper should either be re-worded or removed.

ii. dN/dE : See comment from 3.2.2.

4.3. Flux Distribution:

i. "an lower (redshifted) rate" : a lower (redshifted) rate

4.4 Repetition:

A. A general caution for this section of the manuscript is in applying the lessons of FRB 121102 too widely. There needs to be some caveat in this discussion about how other FRBs have not been seen to repeat, particularly for FRBs that have been followed up as much as FRB 121102. Here you present results from 57 hours of observing with the VLA; some others have been observed for >100 hours without additional pulses and some mention of this should be included here. While indeed at the moment there is no conclusive evidence for multiple sub-populations so it makes sense to generalize a bit, but please also include a statement that not all FRBs might be like this.

i. "day-month" : day-to-month or day and month?

ii. "At the typical Parkes ... at $z \approx 1$" : Please clarify this statement. Do you mean that a Parkes survey could detect the brightest pulse from FRB 121102? The brightest X pulses? The discovery pulse (I think this one was too weak for Parkes)? The "average" pulse?

iii. "understated by a factor of a few by ignoring bursts that fall outside the observing band" : The data presented in this paper are the best currently available to actually constrain this factor. Would it be possible to provide an estimate of this factor using the detections/non-detections from these observations?

iv. "$5 \times 10^2$ and $5 \times 10^3$ times" : Is this range of repetition times sufficient for the repeater? In the observations from just the past 1 year this FRB has emitted O[100] pulses, I believe, and was active at least back to 2012, possibly much longer. Have you or others in the FRB 121102 team attempted to estimate the total number of pulses this FRB may have given off assuming this activity? In doing this does this particular source still fall in the range you've given here? If so, it is worth mentioning where you believe FRB 121102 falls in this range.

Conclusions:

i. "astrophysical source." : astrophysical sources.

ii. "FRB 121102 now serves as a new kind of standard by which FRBs are defined." : In a sense this is true, but this is a very strong statement given the unknown relation between FRB 121102 and the other FRBs that have not been seen to repeat. Please soften or remove this statement.

iii. "That fact, ... about the FRB population." : If they are all the same. I reiterate my caution from Section 4.4 about generalizing this source too much at such an early stage in our understanding of the FRB population.

iv. dN/dE : See comment from 3.2.2

### 2017-07-14 repeater-vladata.tex
fixed aastex bug
adding mattthew a acknowledgements
bumping up the nondetection coverage

@@
+\pdfoutput=1
 \documentclass[twocolumn]{aastex61}
-%\documentclass{emulateapj}
-\usepackage{hyperref} 
-\usepackage{graphicx,natbib}
-\citestyle{aa}
 \usepackage[space]{grffile}
-\usepackage{latexsym}
 \usepackage{amsfonts,amsmath,amssymb}
 \usepackage{url}
+\usepackage{latexsym}
+\usepackage{hyperref} 
+\usepackage{graphicx}
+\usepackage{natbib}
+\citestyle{aa}
 \usepackage[utf8]{inputenc}
@@
 
-\title{A Multi-telescope Campaign on \frb: Implications for the FRB Population}
+\title{A Multi-telescope Campaign on FRB 121102: Implications for the FRB Population}
 \shorttitle{\frb\ Observing Campaign}
@@
 Of the nine bursts detected by the Very Large Array at 3~GHz, four had simultaneous observing coverage at other observatories.
-We use multi-observatory constraints and modeling of bursts seen only at 3~GHz to confirm earlier results showing that burst spectra are not well modeled by a power law.
+We use multi-observatory detections and non-detections of bursts seen at 3~GHz to confirm earlier results showing that burst spectra are not well modeled by a power law.
 We find that burst spectra are characterized by a $\sim500$~MHz envelope and apparent radio energy as high as $10^{40}$\ erg.
@@
 This paper is part of a series based on the first localization of an FRB and its unambiguous association to an extragalactic host \citep{LOC, OPT, EVN}.
-\frb, also known as the ``repeating FRB'', was discovered \citep{2014ApJ...790..101S} in data acquired in 2012 as part of the PALFA survey of the Arecibo Observatory \citep{2006ApJ...637..446C, 2015ApJ...812...81L}.
+\objectname[FRB+121102]{FRB 121102}, also known as the ``repeating FRB'', was discovered \citep{2014ApJ...790..101S} in data acquired in 2012 as part of the PALFA survey of the Arecibo Observatory \citep{2006ApJ...637..446C, 2015ApJ...812...81L}.
 In mid 2015, new Arecibo observations revealed a series of bursts at a similar DM and sky position that rules out cataclysmic models for this source \citep{2016Natur.531..202S}.
@@
 
-This paper presents an analysis of the spectral properties of VLA bursts implied by simultaneous observing at Arecibo, Effelsberg, the first station of the Long-Wavelength Array \citep[LWA1; ][]{2013ITAP...61.2540E}, and the Arcminute Microkelvin Imager Large Array \citep[AMI-LA; ][]{2008MNRAS.391.1545Z}.
+This paper presents an analysis of the spectral properties of VLA bursts implied by detections and nondetections during observing at Arecibo, Effelsberg, the first station of the Long-Wavelength Array \citep[LWA1; ][]{2013ITAP...61.2540E}, and the Arcminute Microkelvin Imager Large Array \citep[AMI-LA; ][]{2008MNRAS.391.1545Z}.
 This includes the first simultaneous detection of an FRB at two observatories, between the VLA and Arecibo.
@@
 Computational (Jupyter) notebooks to reproduce the transient detection, localization, and analysis presented here can be found at \url{https://github.com/caseyjlaw/FRB121102}.
-Time cut-out visibility data and calibration products are available at \url{https://doi.org/10.7910/DVN/TLDKXG}.
+Time cut-out visibility data and calibration products are available at \dataset[http://dx.doi.org/10.7910/DVN/TLDKXG]{https://doi.org/10.7910/DVN/TLDKXG}.
 Original VLA visibility data are available under NRAO program codes 16A-459 and 16A-496 and can be downloaded at \url{http://archive.nrao.edu}.
@@
 All of these observations were conducted after the VLA localization, so they were pointing directly at \frb.
-Three of those observations had simultaneous coverage of VLA bursts and one of those Arecibo observations detected the VLA burst.
+Three of those Arecibo observations made no burst detection coincident with the VLA bursts, while one detected the VLA burst.
 % During the first VLA burst with Arecibo coverage (MJD 57643), the PUPPI 1.4~GHz recording system failed so data were recorded at C band with the mock spectrometer.
@@
 
-Overall, the bursts with simultaneous observing coverage are not well described by a power-law model.
+Overall, the burst detections and nondetections show that burst spectra are not well described by a power-law model.
 Two Arecibo nondetections and two Effelsberg nondetections of VLA bursts place mutually inconsistent lower and upper limits on the spectral index.
@@
 
-\bibliographystyle{yahapj}
+%\bibliographystyle{yahapj}
+\bibliographystyle{apj}
 
@@
 PS holds a Covington Fellowship at DRAO. 
+MWA was a participant in the 2016 Research Experience for Undergraduates in Astronomy and Astrophysics at Cornell University program, supported by grant NSF/AST-1156780.
 The LWA1 station is supported by the National Science Foundation under grant 1139974 of the University Radio Observatory program.
@@
 
-\software{\emph{rtpipe}, \emph{realfast}, pwkit \citep{2017ascl.soft04001W}}
+\software{\emph{rtpipe}, \emph{realfast}, pwkit \citep{2017ascl.soft04001W}, emcee \citep{2013PASP..125..306F}}
 

### 2017-07-15 referee_response.txt
into discussion section

@@
+General comments:
+- We left the latex shortcut for the source name ("\frb") in the title during submission. That has been changed to the full name, "FRB 121102".
+
 Responses start with ">>>"
@@
 
->>> Done.
+>>> Done. Thanks for the reminder.
 
@@
 
->>> I do believe the VLA+AO burst is the first of its kind both as a multi-frequency and as a multi-telescope detection. I see two ways to show this:
->>> 1. The first VLA+Arecibo burst was detected on 17 September, while the bursts reported in Marcote et al were detected on 20 September.
->>> 2. Marcote et al was published simultaneously with Chatterjee et al; the latter paper made the first report of this coincident VLA+AO burst.
->>> I would prefer to keep the current wording.
+>>> I do believe the VLA+AO burst is the first of its kind both as a multi-frequency and as a multi-telescope detection.
+The first VLA+Arecibo burst was detected on 17 September, while the bursts reported in Marcote et al were detected on 20 September.
+The publication date of the VLA+AO (discussed in Chatterjee et al 2017) and EVN bursts were simultaneous, so it is not even true that one was published first.
+I would prefer to keep the current wording.
 
@@
 
+>>> Done.
+
 Introduction:
@@
 ii. $0\farcs1$ and $0.01\arcsec$ : Please check for consistency in the placement of the arcseconds symbol throughout the manuscript
+
+>>> Done.
 
@@
 
+>>> I agree that Figure 1 is fairly dense and takes time to interpret.
+I confess that it's design is limited also by my understanding of our plotting library.
+Some features that you suggest, such as the circles (squared ellipses?) that span multiple rows are beyond my skill to create.
+Would it help the current design to add a frequency label along with the telescope name on the right column?
+
 Table 1: All times should be in the format HH:MM:SS, e.g. 03:25:29
@@
 I believe it would be better to label these as "detection" and "non-detection" since this is what is implied by "coverage" and the lack of a * icon indicating detection.
+
+>>> Done. The last point was a bit unclear to me. After rewording, I decided to use a letter footnote symbol for all nondetections and keep the * symbol to denote the Arecibo detection.
 
@@
 
+>>>
+
 i. "256 channels" : 256 frequency channels
 
+>>> Done
+
 ii. "prototype version of \textit{realfast}. \textit{realfast} is a" : prototype version of \textit{realfast}, a
+
+>>> Done
 
@@
 
+>>> Done. Many factors determine the speed of the pipeline, but antenna configuration tends to dominate.
+
 2.2 Arecibo:
@@
 i. Please include a citation for the PUPPI pulsar backend if there is one.
+
+>>>
 
@@
 
+>>> Done.
+
 2.3 Effelsberg:
@@
 
+>>> No publication exists for the S60mm receiver.
+
 ii. Please provide the width of the frequency channels in the Effelsberg setup (in the text and in an observing details table).
+
+>>>
 
@@
 
+>>> Done. On the last point, the long search duration is standard for the search pipeline, but is more appropriate for other kinds of transients.
+
 2.5 AMI-LA:
@@
 i. "MJDs 57638, ... 57649." : Refer to Figure 1 here.
+
+>>> Done.
 
@@
 
+>>>
+
 3.1 Multi-Observatory Burst Spectrum:
@@
 
+>>> Fixed. Figure 2 is merely centered on the burst in time. Absolute time provided to be explicit.
+
 Figure 3: Make this figure a little bit bigger so it fills the available column space
+
+>>> Done. Glad you like it!
 
@@
 If this value is indeed meant to be the flux density of the pulse then $S$ should be used as the symbol for flux density instead of A.
+
+>>> Done.
 
@@
 
+>>> My interpretation is that this is a detection bias and has no physical meaning.
+If the bursts have a peak spectrum, then it is easiest to detect bursts with a peak inside the observing band.
+Spectral peaks outside or at the edge of the band have reduced measured flux and lower significance.
+I'm not sure how to discuss this in the text, but I'd welcome suggestions.
+
 Table 2: Footnote labeling: The labeling here is not consistent with the labeling used in Table 1.
+
+>>> The addition of the last footnote requires this set of footnotes to be in a different order than in Table 1.
+I don't see a way to include all this information with the same footnote marks as in Table 1.
 
@@
 
+>>> The present paper is constrained to discuss published results on the bursts detected from FRB 121102.
+There have been some results presenting preliminary results on substructure seen in Arecibo bursts.
+However, there is nothing citable to discuss.
+For now, this paragraph will need to be stand on its own.
+
 Figure 4: Are each of the bursts plotted here dedispersed to the best-fit DM given in Table 2 or dedispersed to the best-fit DM of FRB 121102 of 560.5 pc/cm^3?
@@
 Is the structure you are seeing in the spectrum highly dependent on the DM fit?
+
+>>> The spectra are extracted at the best-fit (SNR maximizing) DM, which indeed varies from burst to burst.
+Forcing to a single DM would effectively cut some flux out, so the bursts would become narrower in frequency.
+In that sense, the spectrum is sensitive to the DM.
+Our method is intended to extract and model all flux from the burst.
 
@@
 For example, if there was a pulse with substructure within a single 5ms VLA time sample can you estimate the error this would propagate to the DM fit?
+
+>>> A sentence in the previous section ("Our approach simultanesously models...") attempts to give some context for what the modeling can do.
+The Bayesian approach cannot say anything about the appropriateness of the model, only what can be inferred by assuming the model is correct.
+Substructure within the pulses is not modeled in this analysis, but one could imagine extending the modeling in that way.
+I'll add a comment on that.
+>>> On a related note, I've reworded the second to last sentence in this paragraph to distinguish between "DM" and "apparent DM".
 
@@
 
+>>> Done. On the last point, we were referring to different trends/slopes, so the distinction between dN/d logE and dN/dE was deliberate.
+
 Figure 7: Please make this figure larger to fill the available column space. Axis labels and tick labels should be given in a larger font as well.
+
+>>> Done
 
@@
 
+>>>
+
 i. "We present the first ... to 3.5 GHz." : See comment #1 at the beginning of this report. Statements like these throughout the paper should either be re-worded or removed.
@@
 
+>>> We've left the text unchanged, based on arguments given above.
+
 4.3. Flux Distribution:
@@
 i. "an lower (redshifted) rate" : a lower (redshifted) rate
+
+>>> Done
 
@@
 
+>>> The second paragraph, first sentence has been modified to include this caveat.
+
 i. "day-month" : day-to-month or day and month?
+
+>>> Changed to "day to month"
 
@@
 The "average" pulse?
+
+>>> Reworded. The largest burst energy detected by the VLA was 10^40, which is detectable by the typical Parkes survey at z=1.
 

### 2017-07-15 repeater-vladata.tex
into discussion section

@@
 
-\newcommand{\rf}{\emph{realfast}}
 \newcommand{\frb}{FRB 121102}
@@
 During this campaign, we made the first simultaneous detection of an FRB burst by multiple telescopes: the VLA at 3~GHz and the Arecibo Observatory at 1.4~GHz.
-Of the nine bursts detected by the Very Large Array at 3~GHz, four had simultaneous observing coverage at other observatories.
-We use multi-observatory detections and non-detections of bursts seen at 3~GHz to confirm earlier results showing that burst spectra are not well modeled by a power law.
+Of the nine bursts detected by the Very Large Array at 3~GHz, four had simultaneous observing coverage at other observatories at frequencies from 70~MHz to 15~GHz.
+The one multi-observatory detection and three non-detections of bursts seen at 3~GHz confirm earlier results showing that burst spectra are not well modeled by a power law.
 We find that burst spectra are characterized by a $\sim500$~MHz envelope and apparent radio energy as high as $10^{40}$\ erg.
@@
 We use \frb\ as a prototype of the FRB class to estimate a volumetric birth rate of FRB sources $R_{\rm{FRB}} \approx 5\times10^{-5}/N_r$\ Mpc$^{-3}$\ yr$^{-1}$, where $N_r$\ is the number of bursts per source over its lifetime.
-This rate is broadly consistent with models of FRBs from young pulsars or magnetars born in superluminous supernovae or long gamma-ray bursts, if the typical FRB repeats on the order of thousands of times during its lifetime.
+This rate is broadly consistent with models of FRBs from young pulsars or magnetars born in superluminous supernovae or long gamma-ray bursts if the typical FRB repeats on the order of thousands of times during its lifetime.
 \end{abstract}
@@
 The large DMs imply that FRBs originate outside of our Galaxy, potentially at cosmological distances, and are orders of magnitude more luminous than pulses from Galactic pulsars \citep{2013Sci...341...53T}.
-There are now 22 FRBs publicly known \footnote{See \url{http://www.astronomy.swin.edu.au/pulsar/frbcat} \citep{2016PASA...33...45P}.} with DMs as high as 1600 pc cm$^{-3}$ and temporal widths of order milliseconds.
+There are now 23 FRBs publicly known \footnote{See \url{http://www.astronomy.swin.edu.au/pulsar/frbcat} \citep{2016PASA...33...45P}.} with DMs as high as 1600 pc cm$^{-3}$ and temporal widths of order milliseconds.
 Both their energetics and distance have inspired a wide variety of models and astrophysical applications \citep[e.g.,][]{2014ApJ...780L..33M, 2014ApJ...797...70K, 2015MNRAS.450L..71F, 2016MNRAS.458L..19C, 2016MNRAS.457..232C, 2016MNRAS.462L..16P}.
@@
 Beginning in August 2016 (MJD 57623), we made the first of nine detections of \frb\ with the Karl G.\ Jansky Very Large Array \citep[VLA;][]{LOC} and localized it with a precision of 0\farcs1.
-Deep optical observations with the Gemini Observatory associated the FRB with a host galaxy at $z=0.193$\ \citep{OPT} and the European VLBI Network detected four more bursts to localize the source with a precision of 0.01\arcsec, four orders of magnitude better than any other FRB \citep[precision of $\sim40$\ pc in linear distance;][]{EVN}.
+Deep optical observations with the Gemini Observatory associated the FRB with a host galaxy at $z=0.193$\ \citep{OPT} and the European VLBI Network detected four more bursts to localize the source with a precision of 0\farcs01, four orders of magnitude better than any other FRB \citep[precision of $\sim40$\ pc in linear distance;][]{EVN}.
 The lookback and luminosity distances for \frb\ are 746 and 972 Mpc, respectively, assuming a concordance cosmology with parameters given by \citet{2016A&A...594A..13P}.
@@
  & (ymd/hms) & (min) & (GHz) & \\ \hline
-57351 & 2015-11-25/3:25:29 & 60 & 1.4 & 0 \\
-57357 & 2015-12-01/5:31:31 & 60 & 1.4 & 0 \\
-57359 & 2015-12-03/2:53:57 & 60 & 1.4 & 0 \\
-57361 & 2015-12-05/4:45:44 & 60 & 1.4 & 0 \\
-57363 & 2015-12-07/4:37:50 & 60 & 1.4 & 0 \\
-57365 & 2015-12-09/9:29:25 & 60 & 1.4 & 0 \\
-57367 & 2015-12-11/9:22:27 & 60 & 1.4 & 0 \\
-57369 & 2015-12-13/9:13:7 & 60 & 1.4 & 0 \\
-57371 & 2015-12-15/9:6:16 & 60 & 1.4 & 0 \\
-57373 & 2015-12-17/8:57:51 & 60 & 1.4 & 0 \\
+57351 & 2015-11-25/03:25:29 & 60 & 1.4 & 0 \\
+57357 & 2015-12-01/05:31:31 & 60 & 1.4 & 0 \\
+57359 & 2015-12-03/02:53:57 & 60 & 1.4 & 0 \\
+57361 & 2015-12-05/04:45:44 & 60 & 1.4 & 0 \\
+57363 & 2015-12-07/04:37:50 & 60 & 1.4 & 0 \\
+57365 & 2015-12-09/09:29:25 & 60 & 1.4 & 0 \\
+57367 & 2015-12-11/09:22:27 & 60 & 1.4 & 0 \\
+57369 & 2015-12-13/09:13:07 & 60 & 1.4 & 0 \\
+57371 & 2015-12-15/09:06:16 & 60 & 1.4 & 0 \\
+57373 & 2015-12-17/08:57:51 & 60 & 1.4 & 0 \\
 57503 & 2016-04-25/23:21:39 & 240 & 3 & 0  \\
@@
 57528 & 2016-05-20/16:45:46 & 135 & 3 & 0  \\
-57529 & 2016-05-21/16:44:6 & 135 & 3 & 0  \\
+57529 & 2016-05-21/16:44:06 & 135 & 3 & 0  \\
 57530 & 2016-05-22/16:43:53 & 135 & 3 & 0  \\
@@
 57639 & 2016-09-08/10:14:40 & 120 & 3 & 0  \\
-57641 & 2016-09-10/9:59:36 & 120 & 3 & 0  \\
-57642 & 2016-09-11/9:59:49 & 120 & 3 & 0  \\
-57643 & 2016-09-12/9:15:19 & 120 & 3 & 1\tablenotemark{d} \\ 
-57644 & 2016-09-13/9:23:59 & 120 & 3 & 0  \\
-57645 & 2016-09-14/9:20:23 & 120 & 3 & 1\tablenotemark{a,d} \\
-57646 & 2016-09-15/9:16:29 & 120 & 3 & 1  \\
-57647 & 2016-09-16/9:11:23 & 120 & 3 & 0  \\
-57648 & 2016-09-17/8:59:20 & 120 & 3 & 1\tablenotemark{a,*,b,c,d} \\ 
-57649 & 2016-09-18/8:59:27 & 120 & 3 & 1\tablenotemark{a,b,c,d} \\
-57650 & 2016-09-19/8:44:32 & 120 & 3 & 0  \\
-57651 & 2016-09-20/8:44:33 & 120 & 3 & 0  \\
-57651 & 2016-09-20/17:19:3 & 120 & 6 & 0  \\
-57652 & 2016-09-21/9:13:57 & 120 & 6 & 0  \\
-57653 & 2016-09-22/9:12:24 & 120 & 6 & 0  \\ \hline
+57641 & 2016-09-10/09:59:36 & 120 & 3 & 0  \\
+57642 & 2016-09-11/09:59:49 & 120 & 3 & 0  \\
+57643 & 2016-09-12/09:15:19 & 120 & 3 & 1\tablenotemark{a} \\ 
+57644 & 2016-09-13/09:23:59 & 120 & 3 & 0  \\
+57645 & 2016-09-14/09:20:23 & 120 & 3 & 1\tablenotemark{a,b} \\
+57646 & 2016-09-15/09:16:29 & 120 & 3 & 1  \\
+57647 & 2016-09-16/09:11:23 & 120 & 3 & 0  \\
+57648 & 2016-09-17/08:59:20 & 120 & 3 & 1\tablenotemark{a,*,c,d} \\ 
+57649 & 2016-09-18/08:59:27 & 120 & 3 & 1\tablenotemark{a,b,c,d} \\
+57650 & 2016-09-19/08:44:32 & 120 & 3 & 0  \\
+57651 & 2016-09-20/08:44:33 & 120 & 3 & 0  \\
+57651 & 2016-09-20/17:19:03 & 120 & 6 & 0  \\
+57652 & 2016-09-21/09:13:57 & 120 & 6 & 0  \\
+57653 & 2016-09-22/09:12:24 & 120 & 6 & 0  \\ \hline
 \enddata
 \tablecomments{Times are in UT. Duration includes overhead, which is typically 15\%. Frequency is the approximate center of the bandwidth.}
-\tablenotetext{a}{Arecibo coverage at 1.4~GHz.}
+\tablenotetext{a}{AMI-LA nondetection at 15~GHz.}
+\tablenotetext{b}{Arecibo nondetection at 1.4~GHz.}
 \tablenotetext{*}{Arecibo detection at 1.4~GHz.}
-\tablenotetext{b}{Effelsberg coverage at 4.5~GHz.}
-\tablenotetext{c}{LWA1 coverage near 62 and 78~MHz.}
-\tablenotetext{d}{AMI-LA coverage at 15~GHz.}
+\tablenotetext{c}{Effelsberg nondetection at 4.5~GHz.}
+\tablenotetext{d}{LWA1 nondetection near 62 and 78~MHz.}
 %\end{tabular}
@@
 
-All VLA fast-sampled data were observed with 5~ms sampling, 256 channels, and dual-circular polarization \citep{2015ApJ...807...16L}.
+All VLA fast-sampled data were observed with 5~ms sampling, 256 frequency channels, and dual-circular polarization \citep{2015ApJ...807...16L}.
 The total bandwidths at L (1.4~GHz), S (3~GHz), and C (6~GHz) bands were 256, 1024, and 2048~MHz, respectively, corresponding to channel bandwidths of  1, 4, and 8~MHz.
@@
 
-Observations in August and September were searched by a prototype version of \rf\footnote{See \url{http://realfast.io} \citep{2017AAS...22933002L}.}.
-\rf\ is a real-time, fast imaging transient search system.
+Observations in August and September were searched by a prototype version of \textit{realfast}\footnote{See \url{http://realfast.io} \citep{2017AAS...22933002L}.}, a real-time, fast imaging transient search system.
 The current prototype runs on CPU-based hardware that is normally dedicated to the VLA correlator; for this experiment, it runs the transient search pipeline software called \emph{rtpipe}\footnote{See \url{https://github.com/caseyjlaw/rtpipe} \citep{2015ApJ...807...16L}.}.
@@
 Burst detections and localizations were made within 5--10 hours of data being recorded.
-The transient search starts when data are recorded and proceeds slower than real-time, so we refer to it as ``quasi real-time''.
+The transient search starts when data are recorded and proceeds at anywhere from 1 to 30 times slower than real-time, depending on the number of compute nodes available, array configuration, and number of DMs searched.
 For each trial DM, integration, and time scale, we form an image and calculate the S/N ratio for the peak pixel in the dirty image.
 We empirically identified S/N thresholds of 6.4 and 7.4 as useful to capture data quality statistics and candidates for inspection, respectively.
-The higher threshold is relatively unlikely to be triggered by thermal noise in this configuration, so \rf\ generates a more detailed (and computationally intensive) candidate visualization that includes an image and spectrum.
+The higher threshold is relatively unlikely to be triggered by thermal noise in this configuration, so \textit{realfast} generates a more detailed (and computationally intensive) candidate visualization that includes an image and spectrum.
 All visibilities are recorded so detailed analysis, including improved calibration and localization, can be conducted offline.
@@
 All of these observations were conducted after the VLA localization, so they were pointing directly at \frb.
-Three of those Arecibo observations made no burst detection coincident with the VLA bursts, while one detected the VLA burst.
+Three of those Arecibo observations detected no burst coincident with the VLA bursts, while one Arecibo observation detected a burst coincident with the VLA burst.
 % During the first VLA burst with Arecibo coverage (MJD 57643), the PUPPI 1.4~GHz recording system failed so data were recorded at C band with the mock spectrometer.
@@
 The LWA1 observations were automatically scheduled through the Heuristic Automation for LWA1 (HAL) system.
-Briefly, the HAL system receives messages via the internet that signals the start of a VLA observation.
+The HAL system receives messages via the internet that signal the start of a VLA observation.
 If the source is visible and there are no high priority LWA1 observations scheduled, the HAL system automatically generates an observing schedule, re-configures the telescope, and alerts the observatory staff of the change.
@@
 
-Two of the VLA detected pulses, on MJD 57648 and 57649, had simultaneous coverage with LWA1.
+Two of the VLA detected pulses, on MJD 57648 and 57649, were not detected during simultaneous observations with LWA1.
 We use the modeled LWA1 antenna sensitivity as a function of zenith angle to estimate an system equivalent flux density of 9.5 kJy and 8.7 kJy for the two bursts, respectively.
@@
 
-We observed \frb\ with AMI-LA for 3 hours each on six epochs starting at MJDs 57638, 57643, 57645, 57646, 57648, and 57649.
+We observed \frb\ with AMI-LA for 3 hours each on six epochs starting at MJDs 57638, 57643, 57645, 57646, 57648, and 57649 (see Figure \ref{fig:sched}).
 Observations were made with the new digital correlator having 4096 channels across a 5~GHz bandwidth between 13--18~GHz with a 1~s integration time.
@@
  \caption{Composite dynamic spectrum for the burst from \frb\ on MJD 57648 with data from the VLA and Arecibo observatories.
-The time axis is measured in milliseconds relative to MJD 57648.437788874842 with times corrected to the barycenter and infinite frequency (assuming DM$=560.5$\ pc $^{-3}$).
+The time axis is centered on the burst and starts at MJD 57648.437788874842, corrected to the barycenter and infinite frequency assuming DM$=560.5$\ pc cm$^{-3}$.
 The thick black line separates data from the VLA (2.5 to 3.5~GHz) and Arecibo (1.1 to 1.8~GHz) and flagged data are grey.
@@
 
-\begin{figure}[htb]
+\begin{figure*}[htb]
 \begin{center}
- \includegraphics[width=\columnwidth]{multispec.pdf}
+ \includegraphics[width=2\columnwidth]{multispec.pdf}
  \caption{Broadband spectral measurements and limits for three bursts of \frb\ with observing coverage by Arecibo or Effelsberg.
@@
 \tablecomments{Burst times are topocentric at the VLA at 3.5~GHz.
-$S_{\rm{V}}$ is the measured circular polarization of the burst, which dominated by systematic effects.
+$S_{\rm{V}}$ is the measured circular polarization of the burst, which is dominated by systematic effects.
 All error ranges represent 68\% confidence intervals.}
-\tablenotetext{a}{Simultaneously observing coverage with either Arecibo, Effelsberg, LWA1, or AMI-LA.}
-\tablenotetext{b}{Detected simultaneously with Arecibo.}
+\tablenotetext{a}{Simultaneously observed with either Arecibo, Effelsberg, LWA1, or AMI-LA.}
+\tablenotetext{b}{Detected with Arecibo.}
 \tablenotetext{c}{Best-fit Gaussian is not centered in 3~GHz band, so spectral parameters are limits.}
@@
 \begin{equation}
-G(\nu) = \rm{A} \exp{\left[-\frac{1}{2} \left(\frac{\nu - \nu_0}{\sigma}\right)^2\right]}
+G(\nu) = \rm{S}_{I,peak} \exp{\left[-\frac{1}{2} \left(\frac{\nu - \nu_0}{\sigma}\right)^2\right]}
 \end{equation}
-\noindent where ``A'' is in mJy per 5~ms integration, $\nu_0$\ is the Gaussian center frequency, and $\sigma$\ is its width.
+\noindent where $\rm{S}_{I,peak}$ is the peak flux density in mJy per 5~ms integration, $\nu_0$\ is the Gaussian center frequency, and $\sigma$\ is its width.
 The arrival time was modeled with a cold plasma dispersion law with the arrival time in units of integrations of:
@@
 \end{equation}
-\noindent where ``i0'' is the arrival integration at the highest frequency and $\nu$\ is in units of GHz.
+\noindent where i0 is the arrival integration at the highest frequency and $\nu$\ is in units of GHz.
 Finally, the pulses were assumed to have an intrinsically square temporal width (parameter $W_{int}$).
@@
 The error weighted mean burst DM is 567.8$\pm$0.1 pc cm$^{-3}$, significantly larger than the long-term average of 560.5 pc cm$^{-3}$ seen by Arecibo during this campaign.
-Furthermore, several of the 95\% confidence intervals in DM are not consistent with this mean nor each other, which suggests that some burst-specific property can bias the measured DM.
+Furthermore, several of the 95\% confidence intervals in DM are not consistent with this mean nor each other, which suggests that we measure an apparent DM that is biased by some burst-specific property.
 The variation in DM observed by the VLA at 3~GHz is similar to that reported for Arecibo observations of \frb\ in \citet{2016Natur.531..202S, 2016arXiv160308880S}.
@@
 There is a weak correlation between burst width and apparent DM.
+A change in width of $\sim1$~ms correlates with a change in apparent DM of approximately $5$~pc cm$^{-3}$.
 It is not clear that whether this correlation is driven by intrinsic structure or unmodeled effects, such as frequency-dependent temporal width.
-A change in width of $\sim1$~ms correlates with a change in apparent DM of approximately $5$~pc cm$^{-3}$.
+Future modeling could use a more complex (e.g., multi-component) model to distinguish between these possibilities.
 
@@
 
-Assuming that the burst detection probability follows a Poisson distribution, the mean VLA, 3~GHz burst rate is $R=0.16\pm0.05\ \rm{hr}^{-1}$ above a fluence of 0.2 Jy ms.
-The nondetection in the first half of 3~GHz observing limits the FRB rate to $R<0.1$\ hour$^{-1}$\ (95\% confidence limit).
-The 3~GHz burst rate was much higher during the late-2016 campaign, $R=0.3\pm0.1$\ hour$^{-1}$.
+Assuming that the burst detection probability follows a Poisson distribution, the mean VLA burst rate is $R_{3\rm{GHz}}=0.16\pm0.05\ \rm{hr}^{-1}$ above a fluence of 0.2 Jy ms.
+The nondetection in the first half of VLA observing limits the FRB rate to $R_{3\rm{GHz}}<0.1$\ hour$^{-1}$\ (95\% confidence limit).
+This rate was much higher during the late-2016 campaign, $R_{3\rm{GHz}}=0.3\pm0.1$\ hour$^{-1}$.
 This confirms recent analysis of published bursts from \frb\ \citep{2017arXiv170504881O}.
@@
 \begin{equation}
-E_{\rm{int}} = (\rm{A} \times 5\ \rm{ms}) ( 2.355 \sigma_{ch}\ \times 4\ \rm{MHz}) 10^{-23} (4\pi L_d^2)\ \rm{erg}
+E_{\rm{int}} = (\rm{S}_{I,peak} \times 5\ \rm{ms}) ( 2.355 \sigma_{ch}\ \times 4\ \rm{MHz}) 10^{-23} (4\pi L_d^2)\ \rm{erg}
 \end{equation}
@@
 
-\begin{figure}[htb]
+\begin{figure*}[htb]
 \begin{center}
-\includegraphics[width=\columnwidth]{energy_disn.pdf}
+\includegraphics[width=2\columnwidth]{energy_disn.pdf}
 \caption{The cumulative burst isotropic energy distributions for the VLA, Arecibo, and GBT bursts are shown with dots connected by solid, dashed, and dotted lines, respectively.
@@
 To this complex scene, we add the fact that \frb\ burst spectra are not defined by a spectral index, which suggests that k-corrections are likely to be very difficult to calculate in practice.
-If the FRB burst rate is higher at low (rest) radio frequencies, then high-redshift FRBs will have an lower (redshifted) rate that flattens the $dN/dF$\ distribution in a manner similar to a k-correction.
+If the FRB burst rate is higher at low (rest) radio frequencies, then high-redshift FRBs will have a lower (redshifted) rate that flattens the $dN/dF$\ distribution in a manner similar to a k-correction.
 However, propagation effects are expected to suppress the FRB rate at sub-GHz frequencies \citep{2017MNRAS.465.2286R, 2017arXiv170107457C} as well.
@@
 
-The chance of detecting a burst from \frb\ with the VLA changes substantially on day--month timescales.
+The chance of detecting a burst from \frb\ with the VLA changes substantially on day to month timescales.
 A major outstanding question is whether this time-variable rate is driven by an intrinsic process \citep{2016ApJ...826..226K} or extrinsic (propagation) effects in the host galaxy or intergalactic medium \citep{2017arXiv170306580C}.
@@
 
-The clustering of burst times for the whole FRB population has been modeled as a ``red spectrum'' \citep{2016MNRAS.458L..89C}, while recent work has modeled \frb\ burst times with a modified Poisson distribution \citep{2017arXiv170504881O}.
+If \frb\ is representative of the larger FRB population, then recent modeling of their temporal distribution as a ``red spectrum'' \citep{2016MNRAS.458L..89C} or a modified Poisson distribution \citep{2017arXiv170504881O} will be important to interpreting survey results.
 Both temporal models imply that existing observational constraints on repetition are weaker than expected from Poissonian statistics \citep{2015MNRAS.454..457P, 2015ApJ...807...16L}.
@@
 \frb\ has an absolute energy scale that can be used to estimate a horizon scale for the typical FRB survey sensitivity.
-At the typical Parkes survey parameters \citep[e.g.,][]{2016MNRAS.460L..30C}, a survey with a fluence limit of 1~Jy~ms can detect \frb\ at $z\approx1$ (i.e., for isotropic energy of $\approx10^{40}$~erg).
+At the typical Parkes survey parameters \citep[e.g.,][]{2016MNRAS.460L..30C}, a survey with a fluence limit of 1~Jy~ms can detect the brightest burst from \frb\ at $z\approx1$ (i.e., for isotropic energy of $\approx10^{40}$~erg).
 The distance inferred from the largest DMs observed \citep[$\sim1500$\ pc cm$^{-3}$;][]{2016MNRAS.460L..30C} is somewhat higher, but that likely overestimates distance since DM is expected to have significant contributions from the host galaxy and intervening galaxies \citep{OPT, 2014ApJ...780L..33M}.
@@
 New, arcsecond-scale localizations will be critical to refining the picture presented here and constraining models of FRB origin.
-\frb\ was localized within hours by a prototype version of \rf\ and an expanded \rf\ system is now under construction.
+\frb\ was localized within hours by a prototype version of \textit{realfast} and an expanded \textit{realfast} system is now under construction.
 This platform will search a TB/hour data stream in real time in parallel with ongoing VLA observations, potentially detecting and localizing multiple FRBs per year.
@@
 \section*{Acknowledgements}
-We thank the VLA staff for their support of \rf\ development and Liam Connor for useful feedback.
+We thank the VLA staff for their support of \textit{realfast} development and Liam Connor for useful feedback.
 We acknowledge partial support from the Research Corporation for Scientific Advancement (RCSA) for participation in the meeting Fast Radio Bursts: New Probes of Fundamental Physics and Cosmology at the Aspen Center for Physics (February 12-17, 2017).

### 2017-07-16 referee_response.txt
working through stickier poitns

@@
 General comments:
-- We left the latex shortcut for the source name ("\frb") in the title during submission. That has been changed to the full name, "FRB 121102".
+
+We thank the referee for a thorough review and suggestions for improvement.
 
@@
 
+==================
+Responses to the editors
 ==================
@@
 
-=======
+>>> We left the latex shortcut for the source name ("\frb") in the title during submission. That has been changed to the full name, "FRB 121102".
+
+============
+Responses to the referee
+============
+
 Referee Report
@@
 The first VLA+Arecibo burst was detected on 17 September, while the bursts reported in Marcote et al were detected on 20 September.
-The publication date of the VLA+AO (discussed in Chatterjee et al 2017) and EVN bursts were simultaneous, so it is not even true that one was published first.
+The publication date of the VLA+AO (discussed in Chatterjee et al 2017) and EVN bursts were simultaneous, so it is also not true that one was published first.
 I would prefer to keep the current wording.
@@
 Would it help the current design to add a frequency label along with the telescope name on the right column?
+
+>>>
 
@@
 >>> My interpretation is that this is a detection bias and has no physical meaning.
-If the bursts have a peak spectrum, then it is easiest to detect bursts with a peak inside the observing band.
+If the bursts have a peak in their spectrum, then it is easiest to detect bursts with a peak inside the observing band.
 Spectral peaks outside or at the edge of the band have reduced measured flux and lower significance.
-I'm not sure how to discuss this in the text, but I'd welcome suggestions.
+>>> I'm not sure how to discuss this in the text, but I'd welcome suggestions.
 
@@
 
->>> Done. On the last point, we were referring to different trends/slopes, so the distinction between dN/d logE and dN/dE was deliberate.
+>>> Done.
+On the last point, the distinction between dN/d logE and dN/dE was deliberate, but we tried to avoid confusing readers.
+The issue is that we modeled the distribution in log space, but these kinds of results are typically discussed in linear space.
+Since the analysis is publicly available (Jupyter notebooks on github), I wanted to maintain some reference to the details of the analysis in the text.
+I can't do that without redoing the analysis approach entirely, as shown in the notebook.
 
@@
 
+>>> I do not believe that these data can address this question.
+We have identified a quasi-broadband structure for burst spectra and have shown that detection of a burst at one frequency does not predict the detection of that same burst at another frequency.
+As we discuss, an implication of this is that the burst rate cannot be defined from any single observing band.
+>>> We are working on a comprehensive analysis of the Arecibo data (at 1.4 GHz) during this observing period.
+The joint consideration of the VLA and AO burst rates, along with their time and luminosity distributions, will be required to estimate this "true" burst rate.
+
 iv.
@@
 
+>>> Good point. We've split the last paragraph in two and added some discussion on this point.
+
 Conclusions:
@@
 i. "astrophysical source." : astrophysical sources.
+
+>>> Done.
 
@@
 
+>>> Reworded.
+
 iv. dN/dE : See comment from 3.2.2
+
+>>> Discussed above.

### 2017-07-16 repeater-vladata.tex
working through stickier poitns

@@
 This is consistent with the spectral structure observed within the 3~GHz VLA band, which is typically limited to a Gaussian envelope with width of roughly 500~MHz.
-This confirms earlier results at 1.4~GHz \citep{2016Natur.531..202S, 2016arXiv160308880S} with a wider bandwidth and extends the presence of this phenomenon to 3~GHz.
+This confirms earlier results at 1.4~GHz \citep{2016Natur.531..202S, 2016arXiv160308880S} with a wider bandwidth and extends the existence of this phenomenon to 3~GHz.
 
@@
 The LGRB and SLSN-I rates are $10^{-7}$\ and $10^{-8}$\ Mpc$^{-3}$\ yr$^{-1}$, respectively \citep{2007ApJ...657L..73G,2012Sci...337..927G}.
-Comparing the FRB rate to these rates implies that FRB-emitting sources can be generated in LGRBs and SLSN-I if FRBs repeat $5\times10^2$\ and $5\times10^3$\ times\footnote{\citet{2017arXiv170400022N} provide a similar estimate of FRB birth rate and reach a similar conclusion.}, respectively.
-This assumes isotropic burst energies of $\sim10^{40}$~erg or intrinsic energies of $\sim10^{39} (\Omega_b/0.1)$~erg.
+Comparing the FRB rate to these rates implies that FRB-emitting sources can be generated in LGRBs and SLSN-I if FRBs repeat $5\times10^2$\ and $5\times10^3$\ times.
+This is consistent with a related rate comparison presented in \citet{2017arXiv170400022N}.
+Here, we have assumed isotropic burst energies of $\sim10^{40}$~erg or intrinsic energies of $\sim10^{39} (\Omega_b/0.1)$~erg.
+
 \citet{2017arXiv170102370M} use the young magnetar model for FRBs to calculate the maximum number of bursts that can be powered by its magnetic field as $\approx3000 (0.1/\Omega_b)$.
 This rate comparison suggests that the SLSN-I rate is most consistent with the FRB rate, although there is significant room for adjustment in the models and rate estimate.
+Under that model, \frb\ could emit bursts for roughly 400 days at the peak burst rate measured by the VLA.
+Continued monitoring of \frb\ bursts will continue to be useful in testing models for FRB origin.
 
@@
 
-The recent precision localization of \frb\ has helped identify a host galaxy, measure its distance, and establish it as a member of a truly new class of astrophysical source.
-With its cosmological distance firmly established, \frb\ now serves as a new kind of standard by which FRBs are defined.
-That fact, combined with a rich data set of many bursts, allows us to apply this source to more general questions about the FRB population.
+The recent precision localization of \frb\ has helped identify a host galaxy, measure its distance, and establish it as a member of a truly new class of astrophysical sources.
+With its cosmological distance firmly established and a rich data set of many bursts, \frb\ serves as a prototype that can be used to infer properties of the larger FRB population.
 

### 2017-07-18 referee_response.txt
added table of obs configs

@@
 
-We thank the referee for a thorough review and suggestions for improvement.
+We thank the referee for a thoughtful review and suggestions for improvement.
 
@@
 >>> Done. Thanks for the reminder.
-
->>> We left the latex shortcut for the source name ("\frb") in the title during submission. That has been changed to the full name, "FRB 121102".
+>>> We accidentally left the latex shortcut for the source name ("\frb") in the title during submission. That has been changed to the full name, "FRB 121102".
 
@@
 
->>> Thank you for helping highlight the most interesting part of the analysis. We will work to raise the profile of the nondetection results.
+>>> Thank you for helping highlight the most interesting part of the analysis. We will work to raise the profile of the nondetection results as suggested.
 
@@
 
->>> Done. The last point was a bit unclear to me. After rewording, I decided to use a letter footnote symbol for all nondetections and keep the * symbol to denote the Arecibo detection.
+>>> Done. The last comment was a bit unclear to me. After rewording, I decided to use a letter footnote symbol for all nondetections and keep the * symbol to denote the Arecibo detection.
 
@@
 
->>>
+>>> We have added a new table that summarizes the observing setup for all telescopes discussed here.
+We also made some small cuts to the text that summarized the observing setup to improve readability and remove some redundancy with this new table.
 
@@
 
->>>
+>>> Done.
 

### 2017-07-18 repeater-vladata.tex
added table of obs configs

@@
 We coordinated observing between the VLA, Arecibo, Effelsberg, LWA1, and AMI-LA telescopes, as shown in Figure \ref{fig:sched} and Table \ref{tab:obs}.
-Below, we summarize these observations, with a focus on those conducted simultaneously with VLA burst detections from \frb.
+Table \ref{tab:setup} summarizes the instrument configurations for all observations presented here.
 
@@
 \small
-\tablecaption{Table of VLA Observations \label{tab:obs}}
+\tablecaption{VLA Observations of \frb\ \label{tab:obs}}
 %\centering
 %\begin{tabular}{lcccccc}
+\tablehead{
+\colhead{MJD} & \colhead{Date/time} & \colhead{Duration} & \colhead{Freq.} & \colhead{Bursts} \\
+\colhead{} & \colhead{(ymd/hms)} & \colhead{(min)} & \colhead{(GHz)} & \colhead{}
+}
 \startdata
-MJD & Date/time & Duration & Freq. & Bursts \\
- & (ymd/hms) & (min) & (GHz) & \\ \hline
 57351 & 2015-11-25/03:25:29 & 60 & 1.4 & 0 \\
@@
 All VLA fast-sampled data were observed with 5~ms sampling, 256 frequency channels, and dual-circular polarization \citep{2015ApJ...807...16L}.
-The total bandwidths at L (1.4~GHz), S (3~GHz), and C (6~GHz) bands were 256, 1024, and 2048~MHz, respectively, corresponding to channel bandwidths of  1, 4, and 8~MHz.
-The dispersion smearing across a channel is $\sim1.7$, 0.7, and 0.2~ms in the same respective bands.
-The 3~GHz data were recorded in eight spectral windows with 32 channels each and had a sensitivity of 5~mJy in 5~ms ($1\sigma$).
+As shown in Table \ref{tab:setup}, the L (1.4~GHz), S (3~GHz), and C (6~GHz) bands were used with channel resolutions that kept dispersion smearing well below the temporal resolution.
+All detections were made in the 3~GHz data, which were recorded in eight spectral windows with 32 channels each and had a sensitivity of 4~mJy in 5~ms ($1\sigma$).
 
@@
 
+\begin{deluxetable*}{lcccccc}
+\tablecaption{Observing Configurations \label{tab:setup}}
+\startdata
+\tablehead{
+\colhead{Telescope} & \colhead{Freq. Center} & \colhead{Freq. Bandwidth} & \colhead{Freq. Resolution} & \colhead{Time resolution} & \colhead{DM smearing\tablenotemark{a}} & \colhead{Sensitivity} \\
+\colhead{}     & \colhead{(GHz)} & \colhead{(MHz)} & \colhead{(MHz)} & \colhead{(ms)} & \colhead{(ms)} & \colhead{($1\sigma$; Jy ms)}
+}
+LWA        & 0.062/0.078\tablenotemark{b} & 19.6 & 0.0048 & 160 & 83/43 & 9600 \\
+Arecibo    & 1.44 & 580 & 1.5625 & 0.01024 & 0.0\tablenotemark{c} & 0.004 \\
+VLA        & 1.4  & 256  & 1     & 5       & 1.7 & 0.050 \\
+VLA        & 3.0  & 1024 & 4     & 5       & 0.7 & 0.020 \\
+VLA        & 6.0  & 2048 & 8     & 5       & 0.2 & 0.013 \\
+Effelsberg & 4.85 & 100  & 0.8   & 0.0655 & 0.032 & 0.056 \\
+AMI-LA     & 15   & 5000 & 625   & 1e3     & 0.0 & 30 \\ \hline
+\enddata
+%\tablecomments{}
+\tablenotetext{a}{DM smearing calculated for nominal \frb\ DM of 560.5 pc cm$^{-3}$ at the center frequency.}
+\tablenotetext{b}{LWA1 observed with two independent bands with identical configurations and sensitivities.}
+\tablenotetext{c}{Arecibo data are coherently dedispersed to 560.5 pc cm$^{-3}$, so DM smearing is effectively eliminated.}
+\end{deluxetable*}
+
 \subsection{Arecibo}
 
-Arecibo observed with the L-wide receiver using the PUPPI pulsar backend.
+Arecibo observed with the L-wide receiver using the PUPPI pulsar backend \citep{2008SPIE.7019E..1DD,2010SPIE.7740E..0AF}.
 The observational frequency range was 1.15 to 1.73~GHz and frequency resolution was 1.5625~MHz, which has a typical sensitivity of 2~mJy in 2~ms ($1\sigma$).
@@
 
-Effelsberg observations were conducted with the S60mm receiver and recorded total intensity spectra with the PFFTS backend in pulsar search mode.
-The observations had a time resolution of 65.5~$\mu$s and 128 frequency channels.
+Effelsberg observations were conducted with the S60mm receiver and recorded total intensity spectra with the PFFTS backend in pulsar search mode with a time resolution of 65.5~$\mu$s.
 The receiver has a system equivalent flux density of 18 Jy and a FWHM beam size of 2.4\arcmin\ at 4.85~GHz.
@@
 Five Effelsberg observations were made pointing at the known location of \frb\ and had some simultaneous coverage with the VLA.
-Two of these observations were simultaneous with VLA bursts.
+Two of these observations were simultaneous with VLA bursts, but made no detection.
 The nominal receiver bandwidth is from 4.6 to 5.1~GHz, but a configuration error reduced effective bandwidth to 100~MHz centered at 4.85~GHz for both of these observations during VLA bursts.
@@
 The LWA1 observations consisted of a single phased-array beam centered on the location of \frb\ with two 4096-channel spectral windows spanning frequencies from 52.2--71.8~MHz and 68.2--87.8~MHz.
-The observations were taken in a spectrometer mode with a channel size of 4.8~kHz and a sample time of 160~ms.
-The integration time was set to be equal to the dispersion smearing across a single channel at 50~MHz for DM$\approx560$\ pc cm$^{-3}$.
+The sample time of 160~ms was set to be equal to the dispersion smearing across a single channel at 50~MHz for DM$\approx560$\ pc cm$^{-3}$.
 

### 2017-07-19 referee_response.txt
through comments. sending to team

@@
 We thank the referee for a thoughtful review and suggestions for improvement.
+We have made almost all the recommended changes.
+In some cases, the intent of the comment was not clear, so we made changes while requesting clarification.
+In a few cases, we have responded with an explanation of why no change was made.
 
@@
 
->>> I do believe the VLA+AO burst is the first of its kind both as a multi-frequency and as a multi-telescope detection.
+>>> We do believe the VLA+AO burst is the first of its kind both as a multi-frequency and as a multi-telescope detection.
 The first VLA+Arecibo burst was detected on 17 September, while the bursts reported in Marcote et al were detected on 20 September.
 The publication date of the VLA+AO (discussed in Chatterjee et al 2017) and EVN bursts were simultaneous, so it is also not true that one was published first.
-I would prefer to keep the current wording.
+We would prefer to keep the current wording.
 
@@
 
->>> I agree that Figure 1 is fairly dense and takes time to interpret.
-I confess that it's design is limited also by my understanding of our plotting library.
-Some features that you suggest, such as the circles (squared ellipses?) that span multiple rows are beyond my skill to create.
+>>> Figure 1 is fairly dense and takes time to interpret.
+We must confess that it's design is limited also by our understanding of the plotting library.
+Some features that you suggest, such as the circles (squared ellipses?) that span multiple rows are beyond our skill to create.
 Would it help the current design to add a frequency label along with the telescope name on the right column?
-
->>>
 
@@
 
->>> Done. The last comment was a bit unclear to me. After rewording, I decided to use a letter footnote symbol for all nondetections and keep the * symbol to denote the Arecibo detection.
+>>> Done. The last comment was a bit unclear to me. After rewording, we decided to use a letter footnote symbol for all nondetections and keep the * symbol to denote the Arecibo detection.
 
@@
 
->>>
+>>> We have added a paragraph as suggested.
 
@@
 
->>> My interpretation is that this is a detection bias and has no physical meaning.
+>>> Our interpretation is that this is a detection bias and has no physical meaning.
 If the bursts have a peak in their spectrum, then it is easiest to detect bursts with a peak inside the observing band.
 Spectral peaks outside or at the edge of the band have reduced measured flux and lower significance.
->>> I'm not sure how to discuss this in the text, but I'd welcome suggestions.
+>>> It is not clear how to discuss this in the text, but we'd welcome suggestions.
 
@@
 >>> The addition of the last footnote requires this set of footnotes to be in a different order than in Table 1.
-I don't see a way to include all this information with the same footnote marks as in Table 1.
+It is not clear how to include all this information with the same footnote marks as in Table 1.
 
@@
 Substructure within the pulses is not modeled in this analysis, but one could imagine extending the modeling in that way.
-I'll add a comment on that.
->>> On a related note, I've reworded the second to last sentence in this paragraph to distinguish between "DM" and "apparent DM".
+We will add a comment on that.
+>>> On a related note, we've reworded the second to last sentence in this paragraph to distinguish between "DM" and "apparent DM".
 
@@
 The issue is that we modeled the distribution in log space, but these kinds of results are typically discussed in linear space.
-Since the analysis is publicly available (Jupyter notebooks on github), I wanted to maintain some reference to the details of the analysis in the text.
-I can't do that without redoing the analysis approach entirely, as shown in the notebook.
+Since the analysis is publicly available (Jupyter notebooks on github), we wanted to maintain some reference to the details of the analysis in the text.
+We can't do that without redoing the analysis approach entirely, as shown in the notebook.
 
@@
 
->>>
+>>> We have expanded the discussion of the burst DMs in this section. A new paragraph discusses intrinsic structure more explicitly.
 
@@
 
->>> I do not believe that these data can address this question.
+>>> We do not believe that these data can address this question.
 We have identified a quasi-broadband structure for burst spectra and have shown that detection of a burst at one frequency does not predict the detection of that same burst at another frequency.
@@
 
->>> Good point. We've split the last paragraph in two and added some discussion on this point.
+>>> Good point. We've split this paragraph in two and added some discussion on this point. We've also added a sentence to the conclusion on this point.
 

### 2017-07-19 repeater-vladata.tex
through comments. sending to team

@@
 
+Here we present the analysis of the VLA bursts detected toward \frb\ with a focus on constraints from coordinated radio observations.
+In total, nine bursts were detected by the VLA.
+Three of those bursts had observing coverage by other telescopes, yet were not detected.
+One of the VLA bursts was detected by another telescope, Arecibo.
+In \S \ref{sec:vlaao}, we describe the spectral properties implied by multi-frequency detections and nondetections of VLA bursts at 3~GHz.
+Section \ref{sec:vla} presents a deeper study of the VLA bursts alone, including a spectrotemporal modeling of the bursts, their energies, and their temporal distribution.
+
 \subsection{Multi-Observatory Burst Spectrum}
+\label{sec:vlaao}
 
@@
 \subsection{VLA Bursts}
+\label{sec:vla}
 
@@
 \label{sec:disc}
+
 \subsection{Burst Spectra}
@@
 Most obviously, \frb\ implies that future multi-telescope searches for bursts are unlikely to simultaneously detect bursts in different bands \citep[c.f.][]{1999ApJ...517..460S}.
-Second, since burst spectra have limited bands, the burst detection rate at one frequency may not represent that at another.
+Second, since burst spectra have limited envelopes, the burst detection rate at one frequency may not represent that at another.
 Rate estimates for the FRB population will need to explicitly account for the frequency-dependent rate.
 Finally, we note that the odds of detecting a burst will improve with bandwidth beyond the gain in sensitivity, since bandwidths wider than the FRB characteristic width are more likley to cover the burst envelope.
-However, FRB search algorithms will need to be modified to search for bursts with spectral width less than the full bandwidth.
+However, to benefit from this effect, FRB search algorithms will need to search for bursts with spectral width less than the full bandwidth.
 
 After correcting for barycentric and dispersion delays, the VLA+AO burst spectrum has a residual temporal drift.
-This drift can be interpreted as an excess DM, but contemporaneous observations at 1.4~GHz measured a significantly lower DM (560.5 pc cm$^{-3}$; Hessels et al, in prep).
-This excess DM is comparable to the burst-to-burst variation in DM within the whole sample of VLA 3~GHz bursts.
+This drift can be interpreted as dispersion in excess of the nominal value inferred from contemporaneous observations at 1.4~GHz (560.5 pc cm$^{-3}$; Hessels et al, in prep).
+However, the VLA+AO burst is not the only one with an apparent excess DM; most burst DM measurements are inconsistent with the nominal DM (Figure \ref{fig:dmdt}).
+The scale of this excess DM is comparable to the burst-to-burst variation in DM within the whole sample of VLA 3~GHz bursts.
 This variation had been noted in earlier 1.4~GHz Arecibo observations of \frb\ \citep{2016Natur.531..202S,2016arXiv160308880S}, but the VLA bursts demonstrate that this burst-specific DM is seen simultaneously from 1.4 to 3~GHz.
@@
 One interpretation for the burst-dependent DM is that the bursts have a frequency-dependent pulse shape.
-Pulsar pulse shapes evolve with frequency on GHz frequency scales, presumably due to changes in the beam shape \citep{1988MNRAS.234..477L}.
-The burst-dependent DM changes are on the order of 1\% of the total DM (equivalent to a delay rate up to 2~ms GHz$^{-1}$), which is much larger than typically observed \citep{2017MNRAS.466.3706L}.
+Pulsar pulse shapes evolve with frequency on GHz frequency scales, presumably due to changes in the pulsar beam shape \citep{1988MNRAS.234..477L}.
+The burst-dependent DM changes are on the order of 1\% of the total DM (equivalent to a delay rate up to 2~ms GHz$^{-1}$), which is much larger than typically observed for pulsars \citep{2017MNRAS.466.3706L}.
+
+Another possibility is that there is intrinsic structure to the pulses from \frb.
+Figure \ref{fig:corner} shows how the spectrotemporal distribution of one burst was not well modeled by a single component.
+This is consistent with more complex burst structure seen toward \frb\ and other FRBs \citep{2016Natur.531..202S,2016MNRAS.460L..30C}.
 Our modeling of the VLA burst dynamic spectra show a weak correlation between larger apparent DM and pulse width.
 This could be a signature of unresolved spectrotemporal structure in the VLA burst spectra that biases the measured DM.
+If so, then the systematic measurement of higher DMs by the VLA ($\sim5$~pc cm$^{-3}$ higher than nominal) requires that the intrinsic structure evolve toward lower frequencies during the burst.
 
@@
 
-\citet{2017arXiv170102370M} use the young magnetar model for FRBs to calculate the maximum number of bursts that can be powered by its magnetic field as $\approx3000 (0.1/\Omega_b)$.
+\citet{2017arXiv170102370M} use the young magnetar model for FRBs to calculate the maximum number of bursts that can be powered by its magnetic field as $\approx3000 (0.1/\Omega_b)$ for an isotropic energy of $10^{40}$~erg.
 This rate comparison suggests that the SLSN-I rate is most consistent with the FRB rate, although there is significant room for adjustment in the models and rate estimate.
-Under that model, \frb\ could emit bursts for roughly 400 days at the peak burst rate measured by the VLA.
-Continued monitoring of \frb\ bursts will continue to be useful in testing models for FRB origin.
+The VLA observations of \frb\ imply that roughly 200 bursts of this energy were emitted during the momth of peak activity.
+This suggests that \frb\ data could be in tension with the young magnetar model, if this level of activity were sustained for roughly a year.
 
@@
 Assuming that \frb\ is representative of the FRB population, we calculate a volumetric birth rate of FRB sources that does not depend on telescope sensitivity.
-We estimate a volumetric rate of FRB sources of $R_{\rm{FRB}} \approx 5\times10^{-5} (0.1/\Omega_b)$\ Mpc$^{-3}$\ yr$^{-1}$, which is appropriate for \frb-like burst energies of $10^{40}$\ erg that are detectable out to $z=1$.
+We estimate a volumetric rate of FRB sources of $R_{\rm{FRB}} \approx 5\times10^{-5} (0.1/\Omega_b)$\ Mpc$^{-3}$\ yr$^{-1}$, which is appropriate for \frb-like isotropic burst energies of $10^{40}$\ erg that are detectable out to $z=1$.
 This rate is broadly consistent with models of FRBs from young pulsars or magnetars born in SLSN-I or LGRB, if the typical FRB repeats on the order of $10^3$\ times over its lifetime.
+However, if \frb\ continues to produce energetic bursts at a high rate, it may argue that extrinsic effects amplify the bursts \citep{2017arXiv170306580C}.
 
@@
 
-%\bibliographystyle{yahapj}
 \bibliographystyle{apj}

### 2017-07-25 repeater-vladata.tex
laura comments. changed eff freq to 4.85 from 4.5. need to check spectral index values

@@
 Circled observations with no line indicate bursts that did not have simultaneous observing coverage at the VLA.
-Days with observations are indicated with radio band designations 4, L, S, C, U referring to radio frequencies of 70~MHz, 1.4, 3, 4.5, and 15~GHz, respectively.
+Days with observations are indicated with radio band designations 4, L, S, C, U referring to radio frequencies of 70~MHz, 1.4, 3, 4.85, and 15~GHz, respectively.
 \label{fig:sched}}
@@
 \tablenotetext{*}{Arecibo detection at 1.4~GHz.}
-\tablenotetext{c}{Effelsberg nondetection at 4.5~GHz.}
+\tablenotetext{c}{Effelsberg nondetection at 4.85~GHz.}
 \tablenotetext{d}{LWA1 nondetection near 62 and 78~MHz.}
@@
 VLA        & 6.0  & 2048 & 8     & 5       & 0.2 & 0.013 \\
-Effelsberg & 4.85 & 100  & 0.8   & 0.0655 & 0.032 & 0.056 \\
+Effelsberg & 4.85 & 500\tablenotemark{d}  & 3.4   & 0.0655 & 0.032 & 0.056 \\
 AMI-LA     & 15   & 5000 & 625   & 1e3     & 0.0 & 30 \\ \hline
@@
 \tablenotetext{c}{Arecibo data are coherently dedispersed to 560.5 pc cm$^{-3}$, so DM smearing is effectively eliminated.}
+\tablenotetext{d}{Effelsberg recorded 500~MHz of bandwidth, but a filter reduced the effective bandwidth to 100~GHz for the two days with coincident VLA FRB detections (MJD 57648 and 57649).}
 \end{deluxetable*}
@@
 Assuming a power law flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha=2.1$.
-This is inconsistent with the spectral index limit implied by the Effelsberg nondetection at 4.5~GHz ($\alpha<-1.7$\ for a 2~ms burst and $5\sigma$ limit).
+This is inconsistent with the spectral index limit implied by the Effelsberg nondetection at 4.85~GHz ($\alpha<-1.7$\ for a 2~ms burst and $5\sigma$ limit).
 
@@
 Two Arecibo nondetections and two Effelsberg nondetections of VLA bursts place mutually inconsistent lower and upper limits on the spectral index.
-The Arecibo and Effelsberg upper limits at 1.4 and 4.5~GHz, respectively, limit all burst spectral indices $\alpha_{1.4/3}>+4.9$ and $\alpha_{3/4.5}<-2.7$.
+The Arecibo and Effelsberg upper limits at 1.4 and 4.85~GHz, respectively, limit all burst spectral indices $\alpha_{1.4/3}>+4.9$ and $\alpha_{3/4.85}<-2.7$.
 These are consistent with limits from the LWA1 and AMI-LA, which require $\alpha_{0.07/3}>-2.4$\ and $\alpha_{3/15}<1.5$ for bursts on MJD 57643 and 57649 (the brightest VLA bursts with observing coverage), respectively.
-The strictest limits on $\alpha_{1.4/3}$\ and $\alpha_{3/4.5}$\ are both derived from the burst on MJD 57649, which shows that a power law model is inappropriate even for a single burst.
+The strictest limits on $\alpha_{1.4/3}$\ and $\alpha_{3/4.85}$\ are both derived from the burst on MJD 57649, which shows that a power law model is inappropriate even for a single burst.
 
@@
 Upper limits assume a pulse width of 2~ms and a $5\sigma$ detection threshold.
-Measurements (dots) and limits (triangles) are shown for Arecibo, VLA, and Effelsberg at 1.4, 3, and 4.5~GHz, respectively; limits from LWA1 and AMI-LA are not visible on this scale.
+Measurements (dots) and limits (triangles) are shown for Arecibo, VLA, and Effelsberg at 1.4, 3, and 4.85~GHz, respectively; limits from LWA1 and AMI-LA are not visible on this scale.
 Errors in flux density are comparable to the symbol size and are not shown.

### 2017-07-26 repeater-vladata.tex
fixed spec index for proper effelsberg freq

@@
 Assuming a power law flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha=2.1$.
-This is inconsistent with the spectral index limit implied by the Effelsberg nondetection at 4.85~GHz ($\alpha<-1.7$\ for a 2~ms burst and $5\sigma$ limit).
+This is inconsistent with the spectral index limit implied by the Effelsberg nondetection at 4.85~GHz ($\alpha<-1.4$\ for a 2~ms burst and $5\sigma$ limit).
 
@@
 Two Arecibo nondetections and two Effelsberg nondetections of VLA bursts place mutually inconsistent lower and upper limits on the spectral index.
-The Arecibo and Effelsberg upper limits at 1.4 and 4.85~GHz, respectively, limit all burst spectral indices $\alpha_{1.4/3}>+4.9$ and $\alpha_{3/4.85}<-2.7$.
+The Arecibo and Effelsberg upper limits at 1.4 and 4.85~GHz, respectively, limit all burst spectral indices $\alpha_{1.4/3}>+4.9$ and $\alpha_{3/4.85}<-2.3$.
 These are consistent with limits from the LWA1 and AMI-LA, which require $\alpha_{0.07/3}>-2.4$\ and $\alpha_{3/15}<1.5$ for bursts on MJD 57643 and 57649 (the brightest VLA bursts with observing coverage), respectively.

### 2017-08-07 referee_response.txt
ready to resubmit

@@
 We have made almost all the recommended changes.
-In some cases, the intent of the comment was not clear, so we made changes while requesting clarification.
-In a few cases, we have responded with an explanation of why no change was made.
+In a few cases, we have responded with an explanation of why no change was made or given our interpretation of the suggestion for a change.
 
@@
 The publication date of the VLA+AO (discussed in Chatterjee et al 2017) and EVN bursts were simultaneous, so it is also not true that one was published first.
-We would prefer to keep the current wording.
+We would prefer to keep the current wording, but we have made small changes to highlight the novelty of multi-frequency detections, as suggested below.
 
@@
 
->>> Thank you for helping highlight the most interesting part of the analysis. We will work to raise the profile of the nondetection results as suggested.
+>>> We will work to raise the profile of the nondetection results as suggested. We have done that throughout the text by modifying the use of "simultaneous" and "detection/non-detection".
 
@@
 
->>> There is indeed a lot of work to be done on the Arecibo data.
-That observing campaign is in fact ongoing and multiple students are working on it.
+>>> There is indeed a lot of work to be done on the Arecibo data and we wish to treat that as a whole.
+That observing campaign is ongoing and multiple students are working on it.
 We defer detailed Arecibo analysis for future work, as noted here as "Michilli et al, in prep".
@@
 
->>> Figure 1 is fairly dense and takes time to interpret.
-We must confess that it's design is limited also by our understanding of the plotting library.
-Some features that you suggest, such as the circles (squared ellipses?) that span multiple rows are beyond our skill to create.
-Would it help the current design to add a frequency label along with the telescope name on the right column?
+>>> Figure 1 is fairly dense and takes time to interpret, but we feel it best represents the complexity of the observing campaign at a birds eye view.
+The main point is to highight the amount of observing (over time and frequency) and when/where detections were made.
+The addition of a new table of observing set up should also help in interpretation of this figure.
 
@@
 
->>> Done. The last comment was a bit unclear to me. After rewording, we decided to use a letter footnote symbol for all nondetections and keep the * symbol to denote the Arecibo detection.
+>>> Done. The last comment was a bit unclear. After rewording, we decided to use a letter footnote symbol for all nondetections and keep the * symbol to denote the Arecibo detection.
 
@@
 
->>> Done. On the last point, the long search duration is standard for the search pipeline, but is more appropriate for other kinds of transients.
+>>> Done. On the last point, the long search duration is standard for the search pipeline and may detect highly-scattered bursts. However, it is more appropriate for other kinds of transients.
 
@@
 
->>> Done. Glad you like it!
+>>> Done.
 
@@
 Spectral peaks outside or at the edge of the band have reduced measured flux and lower significance.
->>> It is not clear how to discuss this in the text, but we'd welcome suggestions.
+This was also noted in the pre-localization papers on FRB 121102 by Spitler et al and Scholz et al.
 
@@
 >>> The addition of the last footnote requires this set of footnotes to be in a different order than in Table 1.
-It is not clear how to include all this information with the same footnote marks as in Table 1.
+It is not possible to include all this information with the same footnote marks as in Table 1.
 
@@
 
->>> The present paper is constrained to discuss published results on the bursts detected from FRB 121102.
-There have been some results presenting preliminary results on substructure seen in Arecibo bursts.
-However, there is nothing citable to discuss.
-For now, this paragraph will need to be stand on its own.
+>>> We have added a reference to Spitler et al and Scholz et al, which noted multi-burst structure. Other references are possible in unpublished Arecibo data, but there is nothing citable to discuss.
 
@@
 
->>> The spectra are extracted at the best-fit (SNR maximizing) DM, which indeed varies from burst to burst.
-Forcing to a single DM would effectively cut some flux out, so the bursts would become narrower in frequency.
-In that sense, the spectrum is sensitive to the DM.
-Our method is intended to extract and model all flux from the burst.
+>>> The spectra are extracted from a single integration at the best-fit (SNR maximizing) DM for plotting purposes.
+Since this varies from burst to burst, using a single DM would effectively cut some flux out from the peak integration.
+In that sense, the plotted spectrum is sensitive to the DM.
+For modeling purposes, we use the full dynamic spectrum, so all flux from the burst is included.
 
@@
 Substructure within the pulses is not modeled in this analysis, but one could imagine extending the modeling in that way.
-We will add a comment on that.
+We have added a comment to make that point.
 >>> On a related note, we've reworded the second to last sentence in this paragraph to distinguish between "DM" and "apparent DM".

### 2017-08-07 repeater-vladata.tex
ready to resubmit

@@
 Observations in August and September were searched by a prototype version of \textit{realfast}\footnote{See \url{http://realfast.io} \citep{2017AAS...22933002L}.}, a real-time, fast imaging transient search system.
-The current prototype runs on CPU-based hardware that is normally dedicated to the VLA correlator; for this experiment, it runs the transient search pipeline software called \emph{rtpipe}\footnote{See \url{https://github.com/caseyjlaw/rtpipe} \citep{2015ApJ...807...16L}.}.
+The current prototype runs on CPU-based hardware that is normally dedicated to the VLA correlator; for this experiment, it runs the transient search pipeline software called \emph{rtpipe} \citep{2017ascl.soft06002L}.
 Images were formed for each integration with DMs of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$ and a time resampling grid of 5, 10, 20, 40, and 80 ms.
@@
 Two clusters of samples are identified for this burst: one narrow, low-DM and one wide, high-DM.
-This shows that the model is not appropriate for this burst and could indicate that the burst can be decomposed into two subbursts.
+This shows that the model is not appropriate for this burst and could indicate that the burst can be decomposed into two subbursts, as has been noted before for \frb\ \citet{2016Natur.531..202S, 2016arXiv160308880S}.
 
@@
 
-\software{\emph{rtpipe}, \emph{realfast}, pwkit \citep{2017ascl.soft04001W}, emcee \citep{2013PASP..125..306F}}
+\software{\emph{rtpipe} \citep{2017ascl.soft06002L}, \emph{realfast}, pwkit \citep{2017ascl.soft04001W}, emcee \citep{2013PASP..125..306F}}
 
